### 2024-02-09 code/process.Rmd
work on stuff

---
title: "251 Rescues"
output:
  html_document: 
    toc: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning=F, message=F)
knitr::opts_chunk$set(dev = "png", dev.args = list(type = "cairo-png"))
options(knitr.table.format = "html")
knitr::opts_chunk$set(echo = F)
library(tidyverse)
library(viridis)
library(Replicate)
library(metafor)
library(esc)
library(here)
library(brms)
library(rstan)
library(googledrive)
library(glmnet)
library(tidybayes)
library(ggstance)
library("lattice")
library(reshape2)
library(ggrepel)
library(ggthemes)
library(knitr)
rstan_options(auto_write = TRUE)
options(mc.cores = parallel::detectCores())

theme_set(theme_bw())

model_location="code/models"
```

# Pull data

Download

```{r, eval=F}
f <- googledrive::as_dribble("https://docs.google.com/spreadsheets/d/12A4DblSbX_0tHP1mTVJhjNboI1YDngidkNWiSy0sN0g/edit#gid=0")
googledrive::drive_download(f, path=here("data","raw_data.xlsx"), overwrite=T)

raw_expts <- readxl::read_xlsx(here("data","raw_data.xlsx"), sheet="expt-level", skip=0)

raw_orig <- readxl::read_xlsx(here("data", "raw_data.xlsx"), sheet="original")

ready <- raw_expts |> left_join(raw_orig) |> write_csv(here("data", "combined_data.csv"))

```

Read in cache.

```{r}
d <- read_csv(here("data", "combined_data.csv")) |> 
  select(target_lastauthor_year, type, on_turk, repeated_measure, N, raw_stat, 
         same_direction, replication_score, closeness, subfield, target_year, stanford_internal, 
         open_data, open_materials, within_between, single_vignette)

```

# Parsing

We parse out values from the raw stats.

```{r}
source(here("code","helper","parse_stats.R"))
```

```{r}
parsed_d <- d |> 
  mutate(raw_stat=gsub(" ","",raw_stat),
         calc=pmap(list(raw_stat, within_between,N), do_parsing)) |> 
  unnest(cols=c(calc), names_sep="_") |> 
    mutate(
    calc_d_calc=case_when(
      type=="original" ~ abs(calc_d_calc),
      same_direction=="yes" ~ abs(calc_d_calc),
      same_direction=="no" ~ -abs(calc_d_calc),
      T ~ as.numeric(NA)
      ),
    calc_ES=case_when(
      type=="original" ~ abs(calc_ES),
      same_direction=="yes" ~ abs(calc_ES),
      same_direction=="no" ~ -abs(calc_ES),
      T ~ as.numeric(NA)
      ),
    type=factor(type, levels=c("rescue", "additional", "rep1", "original"))
    ) |> 
  rowwise()
```

## what didn't parse

Check that nothing that has a stat input and doesn't get an ES out.

```{r}

parsed_d |> filter(is.na(calc_ES)&(is.na(calc_d_calc))) |>  select(target_lastauthor_year, type, raw_stat)

parsed_d |> filter(is.na(calc_SE)&(is.na(calc_d_calc_se))) |>  select(target_lastauthor_year, type, raw_stat)

```

# Draft plot

```{r}
#test on just one

for_plotting <- parsed_d |> filter(is.na(calc_d_calc)&!is.na(calc_ES)) |> 
  mutate(point=calc_ES, low=calc_ES-1.96*calc_SE, high=calc_ES+1.96*calc_SE)

for_plotting_d <- parsed_d |> filter(!is.na(calc_d_calc)) |> 
  mutate(point=calc_d_calc, low=calc_d_calc-1.96*calc_d_calc_se, high=calc_d_calc+1.96*calc_d_calc_se)
ggplot(for_plotting,aes(x=type,y=point,ymin=low,ymax=high))+
  geom_errorbar(colour='darkgray',size=.5,width=.25)+
  geom_point()+
  coord_flip()+
  scale_size_area()+
  geom_hline(yintercept=0,color="black")+
  theme(legend.position = "none")+
  labs(y="Effect size original scale", x="")+
  facet_wrap(~target_lastauthor_year)

ggplot(for_plotting_d,aes(x=target_lastauthor_year,y=point,ymin=low,ymax=high, color=type, group=type))+
  geom_errorbar(size=.5,width=.25, position=position_dodge(width=.4))+
  geom_point(position=position_dodge(width=.4))+
  coord_flip()+
  scale_size_area()+
  geom_hline(yintercept=0,color="black")+
  theme(legend.position = "bottom")+
  labs(y="Effect size SMD", x="")
```
# PredInt and P_orig

```{r}
source(here("code","helper","stats.R"))
```

Compute prediction intervals and p_orig, write processed data to file.

### 2024-02-09 code/helper/parse_stats.R
helper code

@@ -1,0 +1,342 @@
+# considered using the effectsize package but afaik we don't care about estimating CI's here and there were optim problems with that
+# https://training.cochrane.org/handbook/current/chapter-06 may be relevant
+
+parse_t <- function(tval, within_between) {
+  df=str_extract(tval, "\\(.*\\)") |> str_sub(2,-2) |> as.numeric()
+  val=str_extract(tval, "=.*") |> str_sub(2,-1) |> as.numeric() |> abs()
+  pval=pt(q=abs(val), df=df, lower.tail=FALSE)*2
+  d_calc=NA
+  N_from_df=NA
+  if(within_between=="between"){
+    d_calc=2*val/(sqrt(df+2)) # this is a simplification for equal groups
+    N_from_df=df+2 # between so add 2
+  }
+  else{
+    d_calc=val/sqrt(df+1)
+    N_from_df=df+1
+  }
+  # note this and future instances of it are from taking the delta formula 
+  # and then assuming (two) equal groups and simplifying 
+  se=4/N_from_df+d_calc**2/(2*N_from_df) 
+  return(data.frame("df_1"=NA, "df_2"=df,"tstat"=val, "fstat"=NA, "p_calc"=pval, "d_calc"=d_calc, "d_calc_se"=se, "N_calc"=N_from_df, "ES"=NA, "SE"=NA))
+}
+
+parse_f <- function(fval, within_between){
+  df_1 =str_extract(fval, "\\(.*,") |> str_sub(2,-2) |> as.numeric()
+  df_2 =str_extract(fval, ",.*\\)") |> str_sub(2,-2) |> as.numeric()
+  val=str_extract(fval, "=.*") |> str_sub(2,-1) |> as.numeric() |> abs()
+  pval=pf(q=val, df1=df_1, df2=df_2, lower.tail=FALSE)
+  d_calc=NA
+  N_from_df=df_1+df_2+1
+  if(!is.na(df_1)&&df_1==1){
+    if(within_between=="between"){
[…]

### 2024-02-09 code/helper/stats.R

@@ -1,0 +1,58 @@
+#helper function for pooling when needed
+pool_m_sd <- function(m1, sd1, n1, m2, sd2, n2){
+  m=(m1*n1+m2*n2)/(n1+n2)
+  var=(n1*(sd1**2+m1**2)+n2*(sd2**2+m2**2))/(n1+n2)-m**2
+  sd=sqrt(var)
+  return(c(m,sd))
+  
+}
+
+
+
+
+do_pred_int <- function(target_ES, target_SE, rep_ES, rep_SE){
+  if(!is.na(target_ES)&!is.na(rep_ES)&!is.na(target_SE)&!is.na(rep_SE)){
+    return(Replicate::pred_int(target_ES, target_SE**2, rep_ES, rep_SE**2)$rep.inside)
+  }
+  return(NA)
+}
+
+do_pred_int_sens <- function(target_ES, target_SE, rep_ES, rep_SE){
+  if(!is.na(target_ES)&!is.na(rep_ES)&!is.na(target_SE)&!is.na(rep_SE)){
+    yio=target_ES
+    vio=target_SE**2
+    yir=rep_ES
+    vir=rep_SE**2
+    t2=.21**2
+    pooled.SE = sqrt(vio + vir + t2)
+    PILo.sens = yio - qnorm(0.975) * pooled.SE
+    PIHi.sens = yio + qnorm(0.975) * pooled.SE
+    PIinside.sens = (yir > PILo.sens) & (yir < PIHi.sens)
+    return(PIinside.sens)
+  }
+  return(NA)
+}
+
+
+
+do_p_orig <- function(target_ES, target_SE, rep_ES, rep_SE){
+  if(!is.na(target_ES)&!is.na(rep_ES)&!is.na(target_SE)&!is.na(rep_SE)){
+    return(Replicate::p_orig(target_ES, target_SE**2,rep_ES, t2=0, rep_SE**2))
+  }
+  return(NA)
+}
+
+do_p_orig_sens <- function(target_ES, target_SE, rep_ES, rep_SE){
+  if(!is.na(target_ES)&!is.na(rep_ES)&!is.na(target_SE)&!is.na(rep_SE)){
+    return(Replicate::p_orig(target_ES, target_SE**2,rep_ES, t2=0.21**2, rep_SE**2))
+  }
+  return(NA)
+}
+
+do_subjective_rep <- function(replicated_instructor_code, replicated_report_code, adjudicated_replication_code){
+  if (is.na(replicated_instructor_code)){return(as.numeric(NA))}
[…]

### 2024-02-16 code/process.Rmd
work on analysis

@@
 library(knitr)
+library(cowplot)
 rstan_options(auto_write = TRUE)
@@
       ),
-    type=factor(type, levels=c("rescue", "additional", "rep1", "original"))
+    type=factor(type, levels=c("original", "rep1", "rescue", "additional"))
     ) |> 
@@
 
-# Draft plot
+# Draft plot of effect sizes
 
-```{r}
+* We will compare the original, 1st replication, and re-replication effect sizes, as well as any effect sizes coming from independent replications (where effect size can be computed)
+
+```{r, fig.height=6, fig.width=8}
 #test on just one
-
+colors <- c("original"="black", "rep1"="#377EB8", "rescue"="#E41A1C", "additional"="#984EA3")
 for_plotting <- parsed_d |> filter(is.na(calc_d_calc)&!is.na(calc_ES)) |> 
@@
   mutate(point=calc_d_calc, low=calc_d_calc-1.96*calc_d_calc_se, high=calc_d_calc+1.96*calc_d_calc_se)
-ggplot(for_plotting,aes(x=type,y=point,ymin=low,ymax=high))+
-  geom_errorbar(colour='darkgray',size=.5,width=.25)+
-  geom_point()+
-  coord_flip()+
+
+orig_scale <- ggplot(for_plotting,aes(x=target_lastauthor_year,y=point,ymin=low,ymax=high, color=type, shape=type, group=desc(type)))+
+  geom_errorbar(size=.5,width=.25, position=position_dodge(width=.4))+
+  geom_point(position=position_dodge(width=.4))+
+  coord_flip(ylim=c(-1.1,2))+
   scale_size_area()+
   geom_hline(yintercept=0,color="black")+
-  theme(legend.position = "none")+
-  labs(y="Effect size original scale", x="")+
-  facet_wrap(~target_lastauthor_year)
+  theme(legend.position = "none",
+        panel.grid.major.x = element_blank(), 
+        panel.grid.minor.x=element_blank()
+        )+
+  scale_color_manual(values=colors)+
+  labs(y="effect size on original scale", x="")
 
-ggplot(for_plotting_d,aes(x=target_lastauthor_year,y=point,ymin=low,ymax=high, color=type, group=type))+
-  geom_errorbar(size=.5,width=.25, position=position_dodge(width=.4))+
-  geom_point(position=position_dodge(width=.4))+
-  coord_flip()+
+smd_scale <- ggplot(for_plotting_d,aes(x=target_lastauthor_year,y=point,ymin=low,ymax=high,shape=type, color=type, group=desc(type)))+
+  geom_errorbar(size=.5,width=0, position=position_dodge(width=.5))+
+  geom_point(position=position_dodge(width=.5))+
+  coord_flip(ylim=c(-1.1,2))+
   scale_size_area()+
   geom_hline(yintercept=0,color="black")+
-  theme(legend.position = "bottom")+
-  labs(y="Effect size SMD", x="")
+    scale_color_manual(values=colors)+
+  theme(legend.position = "bottom", 
+        panel.grid.major.x = element_blank(), 
+        panel.grid.minor.x=element_blank()
+        )+
+  labs(y="Standarized mean difference", x="")
+
+plot_grid(orig_scale, smd_scale, nrow=2, rel_heights=c(.3,1))
+
+```
+# Subjective
+* We will report the distribution of subjective replication success in our rescue sample
+
+```{r}
+subj <- parsed_d |> filter(type=="rescue") |> mutate(binary_success=ifelse(replication_score>.5,1,0))
+
+subj |> group_by(replication_score) |> tally()
+
+success <- filter(subj, binary_success==1)
+
+```
+* We will report the distribution of subjective replication success in our rescue sample
+
+Of a total of `r nrow(subj)` replication, `r nrow(success)` succeeding at mostly or fully replicating the original results.
+
+## We correlate all the things with subjective replication success
+
+* The predictors used in https://osf.io/preprints/psyarxiv/dpyn6/ for exploratory analyses (the ones that need to be calculated)
+
+```{r}
+original <- parsed_d |> filter(type=="original") |> 
+  rename_with(~str_c("original_",.), .cols=-target_lastauthor_year)
+
+rep1 <- parsed_d |> filter(type=="rep1") |> select(target_lastauthor_year, rep_N=N)
+
+for_cor <- subj |> left_join(original) |> left_join(rep1) |> 
+  mutate(
+  social=ifelse(subfield=="social", 1,0),
+  other_psych=ifelse(subfield=="other-psych",1,0), 
+  is_within=ifelse(within_between=="within", 1,0), 
+  change_platform=ifelse(on_turk==original_on_turk, 0,1),
+  log_trials=log(repeated_measure),
+  log_sample=log(N),
+  log_ratio_ss=log(N/original_N),
+  rep_1_log_sample=log(rep_N),
+  log_ratio_rep1_orig=log(rep_N/original_N),
+  log_ratio_rescue_rep1=log(N/rep_N),
+  open_data=ifelse(open_data=="yes",1,0),
+  open_mat=ifelse(open_materials=="yes", 1,0),
+  stanford=ifelse(stanford_internal=="yes",1,0)) |> 
+  filter(!is.na(replication_score))
+
+sub_cor <- function(var, stat = "estimate") {
+  if (stat == "estimate") {
+    cor.test(for_cor$replication_score, pull(for_cor, {{var}}))$estimate
+  } else {
+    cor.test(for_cor$replication_score, pull(for_cor, {{var}}))$p.value
+  }
+}
+
+preds <- c("open_data",  "open_mat", "stanford", "change_platform", 
+           "log_ratio_ss", "is_within", "single_vignette", "log_sample", 
+           "log_trials", "social", "other_psych", "rep_1_log_sample", "log_ratio_rep1_orig", "log_ratio_rescue_rep1")
+
+cors <- tibble(preds = preds) |>
+  mutate(r = sapply(preds, function(x) sub_cor(x, stat = "estimate")),
+         p = sapply(preds, function(x) sub_cor(x, stat = "p"))) |>
+
+  mutate(Predictors=factor(preds, levels=c("social", "other_psych", "is_within", "single_vignette", "change_platform", "open_data", "open_mat", "stanford", "pub_year", "log_trials", "log_sample", "log_ratio_ss", "rep_1_log_sample", "log_ratio_rep1_orig", "log_ratio_rescue_rep1"), labels=c("Social", "Other psych", "Within subjects", "Single vignette", "Switch to online", "Open data", "Open materials", "Stanford", "Publication year", "Log trials", "Log original sample size", "Log rep/orig sample", "rep_1_log_sample", "log_ratio_rep1_orig", "log_ratio_rescue_rep1"))) |> arrange(Predictors) |> select(Predictors, r, p)
+
+library(kableExtra)
+knitr::kable(cors, digits = 3, align='rcc') |> kable_styling(full_width=F, htmltable_class = "lightable-classic-2", font_size=40) 
+#cors
+```
+* If there is a mixture of projects that succeed and fail to replicate the original results, we will qualitatively describe differences that may have played a role.
+
+It looks like the ones with poor replication sample (due to inflated effect size, or exclusion/attrition/etc issues) where the rescue recruited more is the only sorta strong predictor
+
+# table of expts by sample sizes & closenesses
+
+```{r}
+parsed_d |> select(target_lastauthor_year, type, N, closeness, replication_score) |> 
+  filter(type!="additional") |> 
+  pivot_wider(names_from="type", values_from=c(N, closeness, replication_score)) |> 
+  select(paper=target_lastauthor_year, replication_score=replication_score_rescue, N_original, N_rep1, N_rescue,
+         closeness_rep1, closeness_rescue) |> arrange(replication_score |> desc())
+
 ```
@@
 Compute prediction intervals and p_orig, write processed data to file.
+
+```{r}
+do_rma <- function(df) {
+  if(!any(is.na(df$es))){
+  r<- rma(yi=df$es, sei=df$es_se, slab=df$type)
+  return(tibble(rma_est=r$beta[,1],rma_se=r$se))
+  }
+  return(tibble(rma_est=NA, rma_se=NA))
+}
+
+do_d_rma <- function(df) {
+  if(!any(is.na(df$d))){
+  r<- rma(yi=df$d, sei=df$d_se, slab=df$type)
+  return(tibble(rma_d_est=r$beta[,1], rma_d_se=r$se))
+  }
+  return(tibble(rma_d_est=NA, rma_d_se=NA))
+
+}
+
+orig <- parsed_d |> filter(type=="original") |> select(target_lastauthor_year, d=calc_d_calc, d_se=calc_d_calc_se, es=calc_ES, es_se=calc_SE)
+
+do_p_orig <- function(es, es_se, rep_es, rep_se){
+  if(!is.na(es)&!is.na(es_se)&!is.na(rep_es)&!is.na(rep_se)){
+    return(Replicate::p_orig(es, es_se**2,rep_es, t2=0.21**2, rep_se**2))
+  }
+  return(NA)
+}
+foo <- parsed_d |> select(target_lastauthor_year, type, d=calc_d_calc, d_se=calc_d_calc_se, es=calc_ES, es_se=calc_SE) |> 
+  filter(type!="original") |> 
+  group_by(target_lastauthor_year) |> 
+  nest() |> 
+  mutate(rma_result=map(data, do_rma),
+         d_rma_result=map(data, do_d_rma)) |> 
+  unnest_wider(rma_result) |> 
+  unnest_wider(d_rma_result) |> 
+  left_join(orig) |> 
+  rowwise() |> 
+  mutate(p_orig=do_p_orig(es, es_se, rma_est, rma_se),
+         d_p_orig=do_p_orig(d, d_se, rma_d_est, rma_d_se))
+
+```
+
+* We will use p-original to evaluate how consistent the original effect size is with the totality of replications.
+We expect there to be a small number of replications, so we will impute the heterogeneity value as in https://osf.io/preprints/psyarxiv/dpyn6/.
+
+## Secondary TODO you are here!
+
+a) p-original between just the original and rescue,
+
+b) p-original between the original and all replications except the rescue (in the case where no replications are found in the literature, this is the same as done in https://osf.io/preprints/psyarxiv/dpyn6/)
+
+c) p-original between the rescue and all other replications.
+
+We will visualize the consistency between original, 1st replication, rescue, and any other replications by plotting effect size and prediction interval for each.

### 2024-02-16 manuscript/manuscript.Rmd
ms stuff

---
title: "TODO"
author:
  - name: Veronica Boyce
    affiliation: Stanford
    footnote:
      - corresp
  - name: TODO
    affiliation: Stanford
  - name: Michael C. Frank
    affiliation: Stanford
address:
  - code: Stanford
    address: Stanford University
footnote:
  - code: corresp
    text: "Corresponding author. Email: vboyce@stanford.edu"
bibliography: ["251rescue.bib"] # Replace with one or more of your own bibtex files. Better BibTeX for Zotero is your friend
csl: vancouver.csl # Use any CSL style. See https://www.zotero.org/styles for a good list. Ignored if citation_package: natbib
link-citations: TRUE
output:
  bookdown::pdf_document2:
    toc: FALSE
    keep_tex: TRUE
    template: generic_article_template.tex
    #md_extensions: "-autolink_bare_uris"
    number_sections: TRUE
    citation_package: default # Can also be "natbib"
lang: en # Main document language in BCP47 format
geometry: "margin=25mm"
papersize: a4
#linestretch: 2 # for double spacing
endfloat: FALSE # Set to TRUE to turn on latex endfloat package to place figures and tables at end of document
# endfloatoption: # See endfloat documentation for more possibilities
#   - tablesfirst # Default
#   - nomarkers # Default
numberlines: FALSE
authblk: TRUE # FALSE = author affiliations in footnotes; TRUE = author affiliations in a block below author names
footnotehyper: FALSE # TRUE will give you enhanced table footnote capabilities. Set to FALSE to be able to use French blocks. Needed due to what appears to be a latex bug.
urlcolor: blue
linkcolor: blue
citecolor: blue
graphics: TRUE # Needed to be able to include images
tables: TRUE # Needed to be able to include tables
# fancyhdr:
#   first:
#     #headleft: "REPORT-NO-XXXX"
#     headright: "Kaplan et al. (2021)"
#     headrulewidth: 0pt
#     #footleft: A left foot
#     footrulewidth: 0pt
#   subsequent:
#     #headleft: "NEXT-PAGE-HEADER-LEFT"
#     headright: "Kaplan et al. (2021)"
#     headrulewidth: 1pt
#     footrulewidth: 0pt

header-includes:
 - \usepackage{tikz}
 - \usetikzlibrary{positioning,chains}
 - \usepackage{setspace}\singlespacing
 - \renewcommand{\textfraction}{0.00}
 - \renewcommand{\topfraction}{1}
 - \renewcommand{\bottomfraction}{1}
 - \renewcommand{\floatpagefraction}{1}
 - \setcounter{topnumber}{3}
 - \setcounter{bottomnumber}{3}
 - \setcounter{totalnumber}{4}

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE) # By default, hide code; set to TRUE to see code
#knitr::opts_chunk$set(fig.pos = 'th') # Places figures at top or here
knitr::opts_chunk$set(out.width = '100%', dpi=300,
                      fig.width=8, fig.width=8) # Figure resolution and size
knitr::opts_chunk$set(fig.env="figure") # Latex figure environment

options(knitr.table.format="latex") # For kable tables to work without setting format option

knitr::opts_chunk$set(echo=F, warning=F, message=F)#dev = "png", dev.args = list(type = "cairo-png")
 library("papaja")
library("bookdown")
library("rticles")
 library(here)
 library(tidyverse)
 library(brms)
library(tidybayes)
library(kableExtra)
library(viridis)
library(cowplot)
library(ggthemes)
library(reshape2)
#r_refs("r-references.bib", append=F)
theme_set(theme_bw())
options(knitr.table.format = "pdf")

model_location="code/models"

```

<!---------------------- Abstract --------------------->

::: {.abstract data-latex="" lang=en}

TODO abstract
:::

# Introduction

How definitive are failed replications?

TODO cite the MB whatever that tried this.

Well, it depends on what you're trying to measure. From the perspective of learning from the field as a whole things are complicated and may depend also on a priori information from other related studies, the beleivability of the results, the relative rigor and sample sizes of the original and replication (TODO perhaps cite the time invariant).

Researchers do care about that from theory-building perspectives, but there's also a more local reason. Given that a student or lab has attempted a direct replication and that replication has not gotten the desired results of the original, what should they do? Should they try to replicate it again (potentially learning something about how to improve their experiment from the unsuccessful replication)? Or should they concluded that for them, given the resources they have, it isn't worth pursuing that particular experimental design?

## Why replication failure? 
A replication can have different results from the original study for a number of different potential reasons. The original result may have been a fluke, through chance or p-hacking. The original result might be of much less generalizability than is assumed, and very sensitive to the exact conditions and time it was run in ("hidden moderators"). The original could have an inflated effect size, due to some combination of heterogeneity, p-hacking, luck, and publication bias. The replication could have been underpowered due to any of inflated original effect size, attrition in sample, or the original also being underpowered. A manipulation might have failed in the replication (this is a proximate cause that also raises the question of why the manipulation check failed). There might have been a difference in materials or instructions between the two, that turns out to matter (more likely if materials are not available). The experiment might not port well to online due to some details. A change in sample (ie. to online) may decrease data quality without sufficient attention checks. The replication might have made changes (for convenience or a new sample) that turn out to matter.

[list reasons] While one can theorize after the fact about potential causes, in most circumstances it is hard to diagnose for certain what made for the difference in the results. An exception might be if a specific error in one study or the other is found, such that the results were not what was thought (analytic error) or the data was not what was thought (experimental error).

What would these potential causes of replication failure suggest would happen in another replication? For our purposes, we're considering another replication with roughly the same environment, knowledge, and resources of the first replication, but with the benefit of hindsight on the first replication.

Heterogeneity and lack-of-generalizability reasons mostly suggest another failed replication, as the second replication is likely to be closer to the first replication than to the original in these random factors. CITE THAT PAPER about types of heterogeneity and which was they would fall

P-hacking and luck reasons are likely to suggest another failed replication.

Manipulation check failure may not be fixable, but it might at least be diagnosable.

Underpoweredness and inflated effect size may be recoverable depending on the extent -- if the effect size was inflated and the first replication powered for the effect, a better powered (but not huge) replication may be able to recover a smaller, but still convincing effect.

Changes between original and replication may or may not be fixable -- if the original materials are still unavailable, a second replication is no better off. If a second replication can get closer to the original, it might get more similar results.

Sensitivity to environment or not working well online are unlikely to be fixable if the replications remain constrained to using online methods.

These are pragmatic judgments related to how a lab might treat a failed replication as a sign that they cannot do cumulative science on a particular paradigm. In some cases, especially related to changes-in-population or changes-to-online, replications, and thus cumulative work on the paradigm, might be possible for other groups who have different resources.

The question is, having a failed replication, and not knowing which reasons might have caused the different results -- should a scientist try again?

## Current study

Here we report the results of TODO N re-replication "rescue" projects which each re-replicated a study which had a failed or only partially-successful replication in TODO CITE BOYCE. This is a non-random sample, and given the small number of projects, we discuss qualitatively TODO

# Methods
PSYCH 251 is a graduate-level experimental methods class taught by MCF. In previous years, students have conducted replication projects, which were analyzed for replication rate and properties in TODO CITE BOYCE. In Fall 2023, students in PSYCH 251 were offered the option to do a "rescue" project where they re-replicated one of the unsuccessful replications from a previous year (students could also opt to do a normal replication instead). We report on the result of $N rescue projects that opted to be part of the paper and completed data collection.

LOts of stuff is available at LINK.

## Sample

```{r}

library(tidyverse)
library(testthat)
all_projects <- read_csv("https://raw.githubusercontent.com/vboyce/251-254-MA/main/data/raw_data.csv")

filtered <- all_projects |>
  mutate(sub_rep=ifelse(replicated_instructor_code==replicated_report_code, 
                 replicated_report_code, 
                 adjudicated_replication_code)) |> 
  filter(sub_rep %in% c(0,.25, .5)) |> 
  filter(include!="no") |> 
  filter(target_N <=200) |> 
  filter(academic_year %in% c("2015-2016", "2016-2017", "2017-2018", "2018-2019", 
                              "2019-2020", "2020-2021","2021-2022", "2022-2023")) 
# what we really want is whether there was a github, but that column is private and so not in the public raw data
# but 2015 is the first year where we have github links

#test_that("number of rows in filtered", {expect_equal(nrow(filtered),49)})

#given this sample, we then sought original replicator permission, 
#since it would involve sharing their repo and write-up with a new student
#which wouldn't have been anticipated at original classtime

#we heard back from 29 students of the 49 we attempted to contact 
#(1 we couldn't contact due to email bouncing) 
#2 responses were negative, rest were positive, for 27 options

approved <- c("krauss2003","yeshurun2003", "daffner2000", "ngo2019",
              "child2018", "schechtman2010", "payne2008", "paxton2012",
              "hart2018", "lewis2015", "tarampi2016", "jara-ettinger2022",
              "porter_2016_1", "hopkins2016", "birch2007_2", "gong2019",
              "correll2007", "pilditch2019", "daw2011", "dehaene2009",
              "sofer2015", "todd2016_1", "chou2016", "mani2013", 
              "haimovitz2016_2", "haimovitz2016_1", "craig2014")
options <- filtered |> filter(target_lastauthor_year %in% approved)

#test_that("number of rows in options", {expect_equal(nrow(options),27)})

# students were then given this list and the opportunity to choose what to do

# projects that we believe are being rescued (as of Oct 23)

chosen <- c("sofer2015", "birch2007_2", "jara-ettinger2022", "porter_2016_1",
            "hopkins2016", "yeshurun2003", "craig2014", "tarampi2016", 
            "mani2013", "krauss2003", "schechtman2010", "child2018",
            "haimovitz2016_1", "todd2016_1", "haimovitz2016_2", "payne2008", 
            "paxton2012", "dehaene2009", "chou2016", "ngo2019", "gong2019")

rescue_started <- options |> filter(target_lastauthor_year %in% chosen)

#test_that("number of rows in final sample", {expect_equal(nrow(final_sample),21)})

```

We created an initial list of `r nrow(filtered)` rescue-eligible studies that were were in the sample reported in TODO CITE BOYCE, had received a subjective replication success score of 0, .25 or .5 (on a 0-1 scale), had a github repository available (github repos were used in the class starting in academic year 2015-2016), and where the original experiment had 200 or fewer participants (for feasibility reasons if we needed to increase power) . We then contacted the project authors for permission to share their report and github with a new student and include it as a supplement on a resulting paper. This left `r nrow(approved)` options that were offered to the students. `r nrow(chosen)` students chose to do rescue projects; $N students took an incomplete or did not indicate interest in being part of the rescue paper, leaving a final sample of N rescue projects.

## Procedure 
Students conducted their rescue projects over the course of the 10-week class. Once they had chosen a project we gave them access to the original replicators write-up and repo, which often included the data, experiment code, and analytic code. Students were required to think of reasons the original replication might not have worked, and address them if they could. A list of possible reasons and solutions LINK was given to students. Once students experimental designs and analytic plans were approved by TAs (VB and BP), students pre-registered and ran their samples.

With one exception, samples were collected on Prolific (the rescue of TODO ran in-person on the student subject pool) . We tried to power studies adequately (with a target of 2.5x original if possible), but due to cost constraints, not all studies were powered at this level. Across the N-1 studies, we spent $money, for an average of blah blah.

Constraints on budget, timeline, and primarily online studies obviously constrain how closely and well some studies could be replicated. However, these are representative of the sort of limitations on early-career researchers.

## Pre-registration
Our analysis plan was pre-registered after students had selected projects, but before final data collection on the projects (CHECK IF TRUE). Each project was also individually pre-registered by the student conducting it. The overall analysis is at LINK, individual pre-registrations are linked from LINK.

## Analysis of rescue success
We roughly followed TODO CITE BOYCE

Similar to TODO CITE, each project was rated on the basis of subjective replication success both by MCF and by one of VB and BP. Disagreements were resolved through discussion.

We used the same key measures of interest as in TODO CITE BOYCE. We also recorded the measures of foobar for original, replication, and rescue (these were already rated for original and replication).

# Results

## Overall replication rate 
* We will report the distribution of subjective replication success in our rescue sample

* If there is a mixture of projects that succeed and fail to replicate the original results, we will qualitatively describe differences that may have played a role.

Across the N replication, we rated blah blah blah, for an overall replication score of blah.

(Krauss) One of the rescues that went from a replication with score of Y to a rescue with score of Z was FOOBAR. This study looked at the influence of a guided thinking on whether or not people gave correct justifications for their answer on the Monty Hall problem. The original had X/Y and Z/Y. The replication struggled to recruit participants who were naive to the problem, allowed only written (versus written or drawn) responses, and had 0/N, 0/M. While we can't know for sure what caused the non-replication, there were clear issues that could be addressed. The rescue added a pre-screen for naivete, switched the name, and had participants upload drawings (bringing the rescue closer). This resulted in a sample size much more comparable to the original, with Z/Q and Y/H. The rescue effect is smaller, but the overall result is rescued, and the adaptation feels like it could be built on.

(other success)

Not all small replications were rescued. To do mention how sleep one wasn't because of continued recruitment issues getting a sample again. May not be feasible to do given the constraints.

TODO some table of correlations between measures of rescue success rate!! The predictors used in https://osf.io/preprints/psyarxiv/dpyn6/ for exploratory analyses (the ones that need to be calculated)

## Effect size of key measure

* We will compare the original, 1st replication, and re-replication effect sizes, as well as any effect sizes coming from independent replications (where effect size can be computed)

## Key measures 
Cite that statistical consistency and replicating the claimed result are not the same thing

* We will use p-original to evaluate how consistent the original effect size is with the totality of replications. We expect there to be a small number of replications, so we will impute the heterogeneity value as in https://osf.io/preprints/psyarxiv/dpyn6/.

## Secondary

a) p-original between just the original and rescue,

b) p-original between the original and all replications except the rescue (in the case where no replications are found in the literature, this is the same as done in https://osf.io/preprints/psyarxiv/dpyn6/)

c) p-original between the rescue and all other replications.

We will visualize the consistency between original, 1st replication, rescue, and any other replications by plotting effect size and prediction interval for each. TODO how to actually do this!

# Acknowledgements {-}

# Author Contributions {-}

# References {-}

<!-- Use this magic to place references here. -->
<div id="refs"></div>

### 2024-02-16 code/process.Rmd
finish first pass analysis

@@
 
-subj |> group_by(replication_score) |> tally()
+tallied <- subj|> group_by(replication_score) |> tally()
 
+tallied 
 success <- filter(subj, binary_success==1)
 
+d <- read_csv(here("data", "combined_data.csv")) |> filter(type=="rescue")
+
+irr <- cor.test(d$TA_rep_score, d$MCF_rep_score, method="spearman")$estimate
+irr
 ```
@@
 
-Of a total of `r nrow(subj)` replication, `r nrow(success)` succeeding at mostly or fully replicating the original results.
+Of a total of `r nrow(subj)` replication, `r nrow(success)` succeeding at mostly or fully replicating the original results (`r pluck(tallied,2,1)` with a score of 0, `r pluck(tallied, 2,2)` with a score of .75, and `r pluck(tallied, 2,3)` with a score of 1).
+The interrater reliability was `r irr |> round(2)`.
 
@@
 
-Compute prediction intervals and p_orig, write processed data to file.
+NOTE: can't do p-orig not on SMD scale here b/c tau imputation is in SMD units!!!
 
+## orig v all on p-orig
 ```{r}
@@
 
-orig <- parsed_d |> filter(type=="original") |> select(target_lastauthor_year, d=calc_d_calc, d_se=calc_d_calc_se, es=calc_ES, es_se=calc_SE)
-
 do_p_orig <- function(es, es_se, rep_es, rep_se){
@@
 }
-foo <- parsed_d |> select(target_lastauthor_year, type, d=calc_d_calc, d_se=calc_d_calc_se, es=calc_ES, es_se=calc_SE) |> 
+
+```
+
+```{r}
+
+orig <- parsed_d |> filter(type=="original") |> select(target_lastauthor_year, d=calc_d_calc, d_se=calc_d_calc_se, es=calc_ES, es_se=calc_SE)
+
+orig_v_others <- parsed_d |> select(target_lastauthor_year, type, d=calc_d_calc, d_se=calc_d_calc_se, es=calc_ES, es_se=calc_SE) |> 
   filter(type!="original") |> 
@@
   rowwise() |> 
-  mutate(p_orig=do_p_orig(es, es_se, rma_est, rma_se),
-         d_p_orig=do_p_orig(d, d_se, rma_d_est, rma_d_se))
+  mutate(d_p_orig=do_p_orig(d, d_se, rma_d_est, rma_d_se))
+
+orig_v_others |> select(target_lastauthor_year, d_p_orig)
 
@@
 
+## secondary, original and rescue
 a) p-original between just the original and rescue,
 
+```{r}
+orig_v_rescue <- parsed_d |>   filter(type=="rescue") |> 
+  select(target_lastauthor_year, type, res_d=calc_d_calc, res_d_se=calc_d_calc_se, res_es=calc_ES, res_es_se=calc_SE) |>
+
+  left_join(orig) |> 
+  rowwise() |> 
+  mutate(d_p_orig=do_p_orig(d, d_se, res_d, res_d_se))
+
+orig_v_rescue  |> select(target_lastauthor_year, d_p_orig)
+
+```
+
+## original v !rescue
 b) p-original between the original and all replications except the rescue (in the case where no replications are found in the literature, this is the same as done in https://osf.io/preprints/psyarxiv/dpyn6/)
 
+```{r}
+orig_v_not_rescue <- parsed_d |> select(target_lastauthor_year, type, d=calc_d_calc, d_se=calc_d_calc_se, es=calc_ES, es_se=calc_SE) |> 
+  filter(type!="original", type!="rescue") |> 
+  filter(target_lastauthor_year!="krauss2003") |> # have to avoid the divide by 0 error
+  group_by(target_lastauthor_year) |> 
+  nest() |> 
+  mutate(rma_result=map(data, do_rma),
+         d_rma_result=map(data, do_d_rma)) |> 
+  unnest_wider(rma_result) |> 
+  unnest_wider(d_rma_result) |> 
+  left_join(orig) |> 
+  rowwise() |> 
+  mutate(d_p_orig=do_p_orig(d, d_se, rma_d_est, rma_d_se))
+
+orig_v_not_rescue  |> select(target_lastauthor_year, d_p_orig)
+
+```
+
+## rescue v reps
 c) p-original between the rescue and all other replications.
 
+```{r}
+rescue_only <- parsed_d |> filter(type=="rescue") |> select(target_lastauthor_year, d=calc_d_calc, d_se=calc_d_calc_se, es=calc_ES, es_se=calc_SE)
+
+rescue_v_reps <- parsed_d |> select(target_lastauthor_year, type, d=calc_d_calc, d_se=calc_d_calc_se, es=calc_ES, es_se=calc_SE) |> 
+  filter(type!="original", type!="rescue") |> 
+  filter(target_lastauthor_year!="krauss2003") |> # have to avoid the divide by 0 error
+  group_by(target_lastauthor_year) |> 
+  nest() |> 
+  mutate(rma_result=map(data, do_rma),
+         d_rma_result=map(data, do_d_rma)) |> 
+  unnest_wider(rma_result) |> 
+  unnest_wider(d_rma_result) |> 
+  left_join(rescue_only) |> 
+  rowwise() |> 
+  mutate(d_p_orig=do_p_orig(d, d_se, rma_d_est, rma_d_se))
+
+rescue_v_reps |> select(target_lastauthor_year, d_p_orig)
+
+```
+
+## some predint viz! (this is currently with *no* hetereogeneity, idk what we actually want)
 We will visualize the consistency between original, 1st replication, rescue, and any other replications by plotting effect size and prediction interval for each.
+
+```{r}
+do_predInt <- function(df){
+  if(!is.na(df$es)&!is.na(df$es_se)&!is.na(df$rep_es)&!is.na(df$rep_es_se)){
+    a <- Replicate::pred_int(df$es, df$es_se**2,df$rep_es, df$rep_es_se**2)
+    return(tibble(low=a$int.lo, high=a$int.hi, inside=a$rep.inside))
+  }
+  return(tibble(low=NA,high=NA, inside=NA))
+}
+
+do_d_predInt <- function(df){
+  if(!is.na(df$d)&!is.na(df$d_se)&!is.na(df$rep_d)&!is.na(df$rep_d_se)){
+    a <- Replicate::pred_int(df$d, df$d_se**2,df$rep_d, df$rep_d_se**2)
+    return(tibble(d_low=a$int.lo, d_high=a$int.hi, d_inside=a$rep.inside))
+  }
+  return(tibble(d_low=NA,d_high=NA, d_inside=NA))
+}
+
+```
+
+```{r}
+orig <- parsed_d |> filter(type=="original") |> select(target_lastauthor_year, d=calc_d_calc, d_se=calc_d_calc_se, es=calc_ES, es_se=calc_SE)
+
+predInts <- parsed_d |> 
+  filter(type!="original") |> 
+  group_by(target_lastauthor_year) |> 
+  select(target_lastauthor_year, type, rep_d=calc_d_calc, rep_d_se=calc_d_calc_se, rep_es=calc_ES, rep_es_se=calc_SE) |> 
+  left_join(orig) |> 
+  group_by(target_lastauthor_year,type) |> 
+  nest() |> 
+  mutate(pred_int=map(data, do_predInt),
+         d_pred_int=map(data,do_d_predInt)) |> 
+  unnest_wider(pred_int) |> 
+  unnest_wider(d_pred_int) |> 
+  unnest_wider(data)
+
+```
+
+### viz attempts
+```{r, fig.height=8, fig.width=6}
+colors <- c("original"="black", "rep1"="#377EB8", "rescue"="#E41A1C", "additional"="#984EA3")
+
+orig_scale <- ggplot(predInts |> filter(is.na(d_inside)&!is.na(inside)), aes(x=target_lastauthor_year, y=rep_es, ymin=low, ymax=high, color=type, group=desc(type), shape=type))+
+  geom_errorbar(size=.5,width=.25, position=position_dodge(width=.4), color="black")+
+  geom_point(position=position_dodge(width=.4))+
+  geom_point(aes(y=es), color="black", position=position_dodge(width=.4), shape=1)+
+  coord_flip()+
+  scale_size_area()+
+  geom_hline(yintercept=0,color="black")+
+  theme(legend.position = "none",
+        panel.grid.major.x = element_blank(), 
+        panel.grid.minor.x=element_blank()
+        )+
+  scale_color_manual(values=colors)+
+  labs(y="predInts on original scale", x="")
+
+smd_scale <- ggplot(predInts |> filter(!is.na(d_inside)), aes(x=target_lastauthor_year, y=rep_d, ymin=d_low, ymax=d_high, color=type, group=desc(type), shape=type))+
+  geom_errorbar(size=.5,width=.25, position=position_dodge(width=.4), color="black")+
+  geom_point(position=position_dodge(width=.4))+
+  geom_point(aes(y=d), color="black", position=position_dodge(width=.4), shape=1)+
+  coord_flip()+
+  scale_size_area()+
+  geom_hline(yintercept=0,color="black")+
+  theme(legend.position = "none",
+        panel.grid.major.x = element_blank(), 
+        panel.grid.minor.x=element_blank()
+        )+
+  scale_color_manual(values=colors)+
+  labs(y="predInts on SMD scale", x="")
+
+plot_grid(orig_scale, smd_scale, nrow=2, rel_heights=c(.3,1))
+
+```
+## predInt with heterogeneity
+
+```{r}
+do_d_predInt_het <- function(df){
+  if(!is.na(df$d)&!is.na(df$d_se)&!is.na(df$rep_d)&!is.na(df$rep_d_se)){
+    yio=df$d
+    vio=df$d_se**2
+    yir=df$rep_d
+    vir=df$rep_d_se**2
+    t2=.21**2
+    pooled.SE = sqrt(vio + vir + t2)
+    PILo.sens = yio - qnorm(0.975) * pooled.SE
+    PIHi.sens = yio + qnorm(0.975) * pooled.SE
+    PIinside.sens = (yir > PILo.sens) & (yir < PIHi.sens)
+    return(tibble(d_low=PILo.sens, d_high=PIHi.sens, d_inside=PIinside.sens))
+  }
+  return(tibble(d_low=NA,d_high=NA, d_inside=NA))
+}
+
+```
+
+```{r}
+orig <- parsed_d |> filter(type=="original") |> select(target_lastauthor_year, d=calc_d_calc, d_se=calc_d_calc_se, es=calc_ES, es_se=calc_SE)
+
+predInts_het <- parsed_d |> 
+  filter(type!="original") |> 
+  group_by(target_lastauthor_year) |> 
+  select(target_lastauthor_year, type, rep_d=calc_d_calc, rep_d_se=calc_d_calc_se, rep_es=calc_ES, rep_es_se=calc_SE) |> 
+  left_join(orig) |> 
+  group_by(target_lastauthor_year,type) |> 
+  nest() |> 
+  mutate(d_pred_int=map(data,do_d_predInt_het)) |> 
+  unnest_wider(d_pred_int) |> 
+  unnest_wider(data)
+
+```
+
+### viz attempts
+```{r, fig.height=8, fig.width=6}
+colors <- c("original"="black", "rep1"="#377EB8", "rescue"="#E41A1C", "additional"="#984EA3")
+
+ ggplot(predInts_het |> filter(!is.na(d_inside)), aes(x=target_lastauthor_year, y=rep_d, ymin=d_low, ymax=d_high, color=type, group=desc(type), shape=type))+
+  geom_errorbar(size=.5,width=.25, position=position_dodge(width=.4), color="black")+
+  geom_point(position=position_dodge(width=.4))+
+  geom_point(aes(y=d), color="black", position=position_dodge(width=.4), shape=1)+
+  coord_flip()+
+  scale_size_area()+
+  geom_hline(yintercept=0,color="black")+
+  theme(legend.position = "none",
+        panel.grid.major.x = element_blank(), 
+        panel.grid.minor.x=element_blank()
+        )+
+  scale_color_manual(values=colors)+
+  labs(y="predInts on SMD scale", x="")
+
+```

### 2024-02-16 code/process.Rmd
making print better

@@
 ```
+
 # Subjective
+
 * We will report the distribution of subjective replication success in our rescue sample
@@
 ```
-* We will report the distribution of subjective replication success in our rescue sample
 
 Of a total of `r nrow(subj)` replication, `r nrow(success)` succeeding at mostly or fully replicating the original results (`r pluck(tallied,2,1)` with a score of 0, `r pluck(tallied, 2,2)` with a score of .75, and `r pluck(tallied, 2,3)` with a score of 1).
-The interrater reliability was `r irr |> round(2)`.
+The interrater reliability was `r irr |> round(3)`.
 
@@
 library(kableExtra)
-knitr::kable(cors, digits = 3, align='rcc') |> kable_styling(full_width=F, htmltable_class = "lightable-classic-2", font_size=40) 
+knitr::kable(cors, digits = 3, align='rcc') |> kable_styling(full_width=F, htmltable_class = "lightable-classic-2") 
 #cors
@@
 
-It looks like the ones with poor replication sample (due to inflated effect size, or exclusion/attrition/etc issues) where the rescue recruited more is the only sorta strong predictor
+It looks like the ones with poor replication sample (due to inflated effect size, or exclusion/attrition/etc issues) where the rescue recruited more is the only sorta strong predictor.
+(I added a couple non-pre-reg'd relative sample size of rep1 measures)
 
@@
   pivot_wider(names_from="type", values_from=c(N, closeness, replication_score)) |> 
-  select(paper=target_lastauthor_year, replication_score=replication_score_rescue, N_original, N_rep1, N_rescue,
-         closeness_rep1, closeness_rescue) |> arrange(replication_score |> desc())
+  select(paper=target_lastauthor_year, rescue_score=replication_score_rescue, N_original, N_rep1, N_rescue,
+         closeness_rep1, closeness_rescue) |> arrange(rescue_score |> desc())
 
@@
 
-orig_v_others |> select(target_lastauthor_year, d_p_orig)
-
 ```
@@
 We expect there to be a small number of replications, so we will impute the heterogeneity value as in https://osf.io/preprints/psyarxiv/dpyn6/.
-
-## Secondary TODO you are here!
 
@@
   mutate(d_p_orig=do_p_orig(d, d_se, res_d, res_d_se))
-
-orig_v_rescue  |> select(target_lastauthor_year, d_p_orig)
 
@@
   mutate(d_p_orig=do_p_orig(d, d_se, rma_d_est, rma_d_se))
-
-orig_v_not_rescue  |> select(target_lastauthor_year, d_p_orig)
 
@@
 
-rescue_v_reps |> select(target_lastauthor_year, d_p_orig)
+```
+
+## show p_origs
+
+```{r}
+ all <- orig_v_others |> select(target_lastauthor_year, orig_v_other=d_p_orig) |> 
+  left_join(orig_v_rescue |> select(target_lastauthor_year, orig_v_rescue=d_p_orig)) |> 
+  left_join(orig_v_not_rescue |> select(target_lastauthor_year, orig_v_not_rescue=d_p_orig)) |> 
+  left_join(rescue_v_reps |> select(target_lastauthor_year, rescue_v_reps=d_p_orig)) |> 
+  rename(paper=target_lastauthor_year)
+
+all
 
@@
 ```
+
 ## predInt with heterogeneity

### 2024-02-16 manuscript/manuscript.Rmd
stuff

@@
 library(reshape2)
+library(knitr)
+library(kableExtra)
 #r_refs("r-references.bib", append=F)
@@
 
+```{r}
+d <- read_csv(here("data", "combined_data.csv")) |> 
+  select(target_lastauthor_year, type, on_turk, repeated_measure, N, raw_stat, 
+         same_direction, replication_score, closeness, subfield, target_year, stanford_internal, 
+         open_data, open_materials, within_between, single_vignette)
+
+source(here("code","helper","parse_stats.R"))
+
+parsed_d <- d |> 
+  mutate(raw_stat=gsub(" ","",raw_stat),
+         calc=pmap(list(raw_stat, within_between,N), do_parsing)) |> 
+  unnest(cols=c(calc), names_sep="_") |> 
+    mutate(
+    calc_d_calc=case_when(
+      type=="original" ~ abs(calc_d_calc),
+      same_direction=="yes" ~ abs(calc_d_calc),
+      same_direction=="no" ~ -abs(calc_d_calc),
+      T ~ as.numeric(NA)
+      ),
+    calc_ES=case_when(
+      type=="original" ~ abs(calc_ES),
+      same_direction=="yes" ~ abs(calc_ES),
+      same_direction=="no" ~ -abs(calc_ES),
+      T ~ as.numeric(NA)
+      ),
+    type=factor(type, levels=c("original", "rep1", "rescue", "additional"))
+    ) |> 
+  rowwise()
+
+```
+
+```{r}
+subj <- parsed_d |> filter(type=="rescue") |> mutate(binary_success=ifelse(replication_score>.5,1,0))
+
+tallied <- subj|> group_by(replication_score) |> tally()
+
+success <- filter(subj, binary_success==1)
+
+d <- read_csv(here("data", "combined_data.csv")) |> filter(type=="rescue")
+
+irr <- cor.test(d$TA_rep_score, d$MCF_rep_score, method="spearman")$estimate
+```
+
 ## Overall replication rate 
-* We will report the distribution of subjective replication success in our rescue sample
+<!--* We will report the distribution of subjective replication success in our rescue sample-->
 
@@
 
-Across the N replication, we rated blah blah blah, for an overall replication score of blah.
+Across the `r nrow(subj)` replications,  `r nrow(success)` succeeding at mostly or fully replicating the original results.
+`r pluck(tallied,2,1)` had a rating of 0, `r pluck(tallied, 2,2)` got a rating of  .75, and `r pluck(tallied, 2,3)` got a rating of 1.
+All projects were rated both by the instructor (MCF) and by one of the TAs (VB or BP); the interrater reliability was `r irr |> round(3)`.
 
-(Krauss) One of the rescues that went from a replication with score of Y to a rescue with score of Z was FOOBAR.
-This study looked at the influence of a guided thinking on whether or not people gave correct justifications for their answer on the Monty Hall problem.
-The original had X/Y and Z/Y.
-The replication struggled to recruit participants who were naive to the problem, allowed only written (versus written or drawn) responses, and had 0/N, 0/M.
-While we can't know for sure what caused the non-replication, there were clear issues that could be addressed.
-The rescue added a pre-screen for naivete, switched the name, and had participants upload drawings (bringing the rescue closer).
-This resulted in a sample size much more comparable to the original, with Z/Q and Y/H.
+Since we have a mix of successful and unsuccessful rescues, we discuss some differences that may have played a role. This is observational and speculative.
+
+One of the rescues that went from a replication with score of 0 to a rescue with score of 1 was the rescue of CITE KRAUSS.
+This study looked at the influence of a guided thinking on whether or not people gave correct justifications (drawn or written) for their answer on the Monty Hall problem.
+The original paper reported correct justification from 2/67 (`r round(2/67*100)`%) in the control condition and 13/34 (`r round(13/34*100)`%) in the guided thinking condition.
+The replication allowed only written responses.
+It struggled to recruit participants who were naive to the problem (an exclusion criter) and had many participants give very short text responses.
+The replication found 0/8 correct justifications in the control and 0/11 in the guided thinking condition.
+While we can't know for sure what caused the non-replication, there were clear issues that occurred.
+The rescue added a pre-screen for naivete, switched the name of the problem, and had participants upload drawings for their justifications, which brought the rescue closer to the original design.
+The rescue had  1/40 (`r round(1/40*100)`%) correct justifications in the control group and 6/35 (`r round(6/35*100)`%) in the guided group.
 The rescue effect is smaller, but the overall result is rescued, and the adaptation feels like it could be built on.
 
-(other success)
+Another successful replication was that of CITE NGO2019.
+Here, the original study had a large effect, and so the replication, powering for 80% power on the reported effect, recruited a small sample of 12 people, and failed to find the effect.
+The rescue, powered using 2.5x the original sample (as recommended by TODO SMALL TELESCOPES CITE), recovered a clear effect (albeit a much smaller one).
+There are reasons to think that some effect sizes in the literature may be inflated CITATIONS, and separately potential reasons that slight changes to experiments, or swtiches to online, could result in noisier samples (and thus smaller effect sizes).
+Thus, replications with smaller samples than the original (even if powered to the original effect size), may not be that diagnostic, and could potentially benefit from a re-replication.
 
-Not all small replications were rescued. To do mention how sleep one wasn't because of continued recruitment issues getting a sample again. May not be feasible to do given the constraints.
+Not all rescues of small replication succeeded, however.
+TODO CITE PAYNE was a study of the effects of sleep versus wake on memory consolidation that showed participants a number of images and then hours later (after either sleep or no sleep) measured their recall for parts of the images.
+The first replication struggled to recruit participants and only got 23 (the original had 48).
+The rescue attempted to recruit a larger sample (target 88), but due to difficulties getting participants to complete the second part 12 hours after the first, the rescue only managed to recruit 23 people.
+The lesson here may be that sleep research is difficult to conduct online.
 
-TODO some table of correlations between measures of rescue success rate!! The predictors used in https://osf.io/preprints/psyarxiv/dpyn6/ for exploratory analyses (the ones that need to be calculated)
+(other successes)
+
+## Correlates of rescue success
+
+<!-- TODO some table of correlations between measures of rescue success rate!!
+The predictors used in https://osf.io/preprints/psyarxiv/dpyn6/ for exploratory analyses (the ones that need to be calculated) -->
+```{r}
+
+original <- parsed_d |> filter(type=="original") |> 
+  rename_with(~str_c("original_",.), .cols=-target_lastauthor_year)
+
+rep1 <- parsed_d |> filter(type=="rep1") |> select(target_lastauthor_year, rep_N=N)
+
+for_cor <- subj |> left_join(original) |> left_join(rep1) |> 
+  mutate(
+  social=ifelse(subfield=="social", 1,0),
+  other_psych=ifelse(subfield=="other-psych",1,0), 
+  is_within=ifelse(within_between=="within", 1,0), 
+  change_platform=ifelse(on_turk==original_on_turk, 0,1),
+  log_trials=log(repeated_measure),
+  log_sample=log(N),
+  log_ratio_ss=log(N/original_N),
+  rep_1_log_sample=log(rep_N),
+  log_ratio_rep1_orig=log(rep_N/original_N),
+  log_ratio_rescue_rep1=log(N/rep_N),
+  open_data=ifelse(open_data=="yes",1,0),
+  open_mat=ifelse(open_materials=="yes", 1,0),
+  stanford=ifelse(stanford_internal=="yes",1,0)) |> 
+  filter(!is.na(replication_score))
+
+sub_cor <- function(var, stat = "estimate") {
+  if (stat == "estimate") {
+    cor.test(for_cor$replication_score, pull(for_cor, {{var}}))$estimate
+  } else {
+    cor.test(for_cor$replication_score, pull(for_cor, {{var}}))$p.value
+  }
+}
+
+preds <- c("open_data",  "open_mat", "stanford", "change_platform", 
+           "log_ratio_ss", "is_within", "single_vignette", "log_sample", 
+           "log_trials", "social", "other_psych", "rep_1_log_sample", "log_ratio_rep1_orig", "log_ratio_rescue_rep1")
+
+cors <- tibble(preds = preds) |>
+  mutate(r = sapply(preds, function(x) sub_cor(x, stat = "estimate")),
+         p = sapply(preds, function(x) sub_cor(x, stat = "p"))) |>
+
+  mutate(Predictors=factor(preds, levels=c("social", "other_psych", "is_within", "single_vignette", "change_platform", "open_data", "open_mat", "stanford", "pub_year", "log_trials", "log_sample", "log_ratio_ss", "rep_1_log_sample", "log_ratio_rep1_orig", "log_ratio_rescue_rep1"), labels=c("Social", "Other psych", "Within subjects", "Single vignette", "Switch to online", "Open data", "Open materials", "Stanford", "Publication year", "Log trials", "Log original sample size", "Log rep/orig sample", "rep_1_log_sample", "log_ratio_rep1_orig", "log_ratio_rescue_rep1"))) |> arrange(Predictors) |> select(Predictors, r, p)
+
+library(kableExtra)
+knitr::kable(cors, digits = 3, align='rcc', format="latex") #|> kable_styling(full_width=F, htmltable_class = "lightable-classic-2") 
+#cors
+```
+
+We ran correlations between a the set of predictor variables used in (TODO CITE BOYCE) and the subjective rescue success (TABLE WHATEVER).
+As the number of rescues is small, and many of these predictors are correlated, this should be taken suggestive only.
+
+We also added predictors related to the first replication sample size and the relative sizes of the samples (post-hoc, not pre-registered) because this seemed like a potentially important factor in a couple of the successful replications.
+Likely driven by these two, metrics related to original replication size were strong (TODO MATH).
+
+This is correlational, and we know that small replication samples relative to original and rescue could be due both to a) aiming for a small replication sample due to aiming for power for a reported large effect size or b) difficulties with recruitment or high exclusion rates leading to a smaller than intended sample.
+
+Two factors that seem like they would matter are relative sample size and replication closeness (CITE LEBEL). So here they are in a table.
+
+```{r}
+parsed_d |> select(target_lastauthor_year, type, N, closeness, replication_score) |> 
+  filter(type!="additional") |> 
+  pivot_wider(names_from="type", values_from=c(N, closeness, replication_score)) |> 
+  select(paper=target_lastauthor_year, rescue_score=replication_score_rescue, N_original, N_rep1, N_rescue,
+         closeness_rep1, closeness_rescue) |> arrange(rescue_score |> desc())
+
+```
 

### 2024-02-20 manuscript/manuscript.Rmd
poke at methods

@@
 ---
-title: "TODO"
+title: "TODO (re-replication) (student) (cumulative science) (failure to replicate) "
 author:
@@
 
+While individual studies are not definitive when it comes to scientific evidence, they often influence what scientists pursue -- it worked -- keep going that direction, it didn't, possibly try again, or switch to a different question or method.
+
 TODO cite the MB whatever that tried this.
@@
 
+Somewhere in here we should acknowledge that there's current discussion around replication rates and interpretation and so forth. 
 ## Why replication failure? 
@@
 
+## Re-replication
 What would these potential causes of replication failure suggest would happen in another replication?
@@
 ## Current study
-
-Here we report the results of TODO N re-replication "rescue" projects which each re-replicated a study which had a failed or only partially-successful replication in TODO CITE BOYCE.
-This is a non-random sample, and given the small number of projects, we discuss qualitatively TODO
-
-# Methods
-PSYCH 251 is a graduate-level experimental methods class taught by MCF.
-In previous years, students have conducted replication projects, which were analyzed for replication rate and properties in TODO CITE BOYCE.
-In Fall 2023, students in PSYCH 251 were offered the option to do a "rescue" project where they re-replicated one of the unsuccessful replications from a previous year (students could also opt to do a normal replication instead).
-We report on the result of $N rescue projects that opted to be part of the paper and completed data collection.
-
-LOts of stuff is available at LINK.
-
-## Sample
-
 ```{r}
@@
 
-We created an initial list of `r nrow(filtered)` rescue-eligible studies that were were in the sample reported in TODO CITE BOYCE, had received a subjective replication success score of 0, .25 or .5 (on a 0-1 scale), had a github repository available (github repos were used in the class starting in academic year 2015-2016), and where the original experiment had 200 or fewer participants (for feasibility reasons if we needed to increase power) .
-We then contacted the project authors for permission to share their report and github with a new student and include it as a supplement on a resulting paper.
-This left `r nrow(approved)` options that were offered to the students.
-`r nrow(chosen)` students chose to do rescue projects; $N students took an incomplete or did not indicate interest in being part of the rescue paper, leaving a final sample of N rescue projects.
-
-## Procedure 
-Students conducted their rescue projects over the course of the 10-week class.
-Once they had chosen a project we gave them access to the original replicators write-up and repo, which often included the data, experiment code, and analytic code.
-Students were required to think of reasons the original replication might not have worked, and address them if they could.
-A list of possible reasons and solutions LINK was given to students.
-Once students experimental designs and analytic plans were approved by TAs (VB and BP), students pre-registered and ran their samples.
-
-With one exception, samples were collected on Prolific (the rescue of TODO ran in-person on the student subject pool) .
-We tried to power studies adequately (with a target of 2.5x original if possible), but due to cost constraints, not all studies were powered at this level.
-Across the N-1 studies, we spent $money, for an average of blah blah.
-
-Constraints on budget, timeline, and primarily online studies obviously constrain how closely and well some studies could be replicated.
-However, these are representative of the sort of limitations on early-career researchers.
-
-## Pre-registration
-Our analysis plan was pre-registered after students had selected projects, but before final data collection on the projects (CHECK IF TRUE).
-Each project was also individually pre-registered by the student conducting it.
-The overall analysis is at LINK, individual pre-registrations are linked from LINK.
-
-## Analysis of rescue success
-We roughly followed TODO CITE BOYCE
-
-Similar to TODO CITE, each project was rated on the basis of subjective replication success both by MCF and by one of VB and BP. Disagreements were resolved through discussion.
-
-We used the same key measures of interest as in TODO CITE BOYCE. We also recorded the measures of foobar for original, replication, and rescue (these were already rated for original and replication).
-
-# Results
-
 ```{r}
@@
          same_direction, replication_score, closeness, subfield, target_year, stanford_internal, 
-         open_data, open_materials, within_between, single_vignette)
+         open_data, open_materials, within_between, single_vignette, cost)
 
@@
 
+num_proj <- parsed_d |> filter(type=="rescue") |> nrow()
+
+cost <- parsed_d |> filter(type=="rescue") |> ungroup() |>  summarize(total=sum(cost, na.rm=T))
 ```
+
+Here we report the results of `r num_proj` re-replication "rescue" projects which each re-replicated a study which had a failed or only partially-successful replication in @boyce2023.
+This is a non-random sample, and given the small number of projects, we provide descriptive statistics and discuss qualitatively some potential sources of differential re-replication outcomes.
+
+# Methods
+PSYCH 251 is a graduate-level experimental methods class taught by MCF.
+In previous years, students have conducted replication projects, which were analyzed for replication rate and properties in @boyce2023.
+In Fall 2023, students in PSYCH 251 were offered the option to do a "rescue" project where they re-replicated one of the unsuccessful replications from a previous year (students could also opt to do a normal replication instead).
+We report on the result of `r num_proj` rescue projects that opted to be part of the paper and completed data collection.
+
+A spreadsheet of projects, individual project write-ups (both replications and rescues), links to individual project data and analyses for rescue projects, and the analytic code for this paper are all available at OSF LINK GOES HERE.
+
+## Sample
+The experiments that were re-replicated were a non-random sample of studies from @boyce2023. 
+We created an initial list of `r nrow(filtered)` rescue-eligible studies that had received a subjective replication success score of 0, .25 or .5 (on a 0-1 scale) in @boyce2023, where the replication had a github repository available (github repositories were used starting in academic year 2015-2016), and where the original experiment had 200 or fewer participants (for feasibility reasons if we needed to increase power).
+We then contacted the replication project authors for permission to share their report and github repository with a new student and include it as a supplement on a resulting paper.
+This left `r nrow(approved)` options that were offered to the students.
+`r nrow(chosen)` students chose to do rescue projects; `r nrow(chosen)-num_proj` students took an incomplete or did not indicate interest in being part of the rescue paper, leaving a final sample of `r num_proj` rescue projects.
+
+## Procedure 
+Students conducted their rescue projects over the course of the 10-week class.
+Once they had chosen a project we gave them access to the original replicators write-up and repository, which often included the data, experiment code, and analytic code.
+In many cases, students were also given the contact information of the original replicator (a few original replicators opted not to be contacted by students).
+
+Students were required to think of reasons the original replication might not have worked, and address them if they could.
+A list of possible reasons and solutions LINK was given to students.
+Once students experimental designs and analytic plans were approved by TAs (VB and BP), students pre-registered and ran their samples.
+
+With one exception, samples were collected on Prolific (the rescue of TODO ran in-person on the Stanford student subject pool).
+We tried to power studies adequately (with a target of 2.5x original if possible), but due to cost constraints, not all studies were powered at this level (See table TODO for post-exclusion sample sizes of original, replication, and rescues).
+Across the `r num_proj-1` studies, we spent $`r pluck(cost,1,1) |> round()`, for an average of $`r (pluck(cost,1,1)/(num_proj-1)) |> round()` per project.
+
+Constraints on budget, timeline, and primarily online studies obviously constrain how closely and well some studies could be replicated.
+However, these are representative of the sort of limitations on early-career researchers.
+
+## Pre-registration
+Our analysis plan was pre-registered after students had selected projects, but before final data collection on the projects (CHECK IF TRUE).
+Each project was also individually pre-registered by the student conducting it.
+The overall analysis is at LINK, individual pre-registrations are linked from LINK.
+
+## Analysis of rescue success
+We followed @boyce2023 in what study properties we measured and what measures of replication success we used.
+
+Each project was rated on the basis of subjective replication success both by MCF and by one of VB and BP. Disagreements were resolved through discussion.
+
+We used the same key measures of interest as in @boyce2023.
+We also recorded the same set of potential correlates that were used in @boyce2023 for original, replication, and rescue (these were already rated for original and replication).
+
+As the number of project is much smaller, we do not model success in terms of the potential correlates, but merely report the correlation of each property with the subjective outcome variable.
+
+# Results
 

### 2024-02-20 manuscript/manuscript.Rmd
results

@@
 ## Overall replication rate 
-<!--* We will report the distribution of subjective replication success in our rescue sample-->
+<!--* We will report the distribution of subjective replication success in our rescue sample
 
-* If there is a mixture of projects that succeed and fail to replicate the original results, we will qualitatively describe differences that may have played a role.
+* If there is a mixture of projects that succeed and fail to replicate the original results, we will qualitatively describe differences that may have played a role. -->
+All rescue projects were rated holistically for how well they replicated the original results.
+We thought about this in terms of how confident one would be to build on this line of work given the replication results, rather than focusing on any singular numeric result or significance cut-off.
+All projects were rated both by the instructor (MCF) and by one of the TAs (VB or BP); the interrater reliability was `r irr |> round(3)`.
+Across the `r nrow(subj)` replications,  `r nrow(success)` mostly or fully replicated the original results according to the subjective replication ratings.
+`r pluck(tallied,2,1)` had a rating of 0, `r pluck(tallied, 2,2)` got a rating of  .75, and `r pluck(tallied, 2,3)` got a rating of 1.
 
-Across the `r nrow(subj)` replications,  `r nrow(success)` succeeding at mostly or fully replicating the original results.
-`r pluck(tallied,2,1)` had a rating of 0, `r pluck(tallied, 2,2)` got a rating of  .75, and `r pluck(tallied, 2,3)` got a rating of 1.
-All projects were rated both by the instructor (MCF) and by one of the TAs (VB or BP); the interrater reliability was `r irr |> round(3)`.
+Given the mix of successful and unsuccessful rescues, we discuss a few projects where we have speculations about why they turned out the way they did.
 
-Since we have a mix of successful and unsuccessful rescues, we discuss some differences that may have played a role. This is observational and speculative.
-
-One of the rescues that went from a replication with score of 0 to a rescue with score of 1 was the rescue of CITE KRAUSS.
+One of the rescues that went from a replication with score of 0 to a rescue with score of 1 was the rescue of @krauss2003.
 This study looked at the influence of a guided thinking on whether or not people gave correct justifications (drawn or written) for their answer on the Monty Hall problem.
 The original paper reported correct justification from 2/67 (`r round(2/67*100)`%) in the control condition and 13/34 (`r round(13/34*100)`%) in the guided thinking condition.
-The replication allowed only written responses.
-It struggled to recruit participants who were naive to the problem (an exclusion criter) and had many participants give very short text responses.
+The  first replication struggled to recruit participants who were naive to the problem (an exclusion criterion), and many participants give very short text responses in the provided text box (only textual responses were allowed).
 The replication found 0/8 correct justifications in the control and 0/11 in the guided thinking condition.
-While we can't know for sure what caused the non-replication, there were clear issues that occurred.
-The rescue added a pre-screen for naivete, switched the name of the problem, and had participants upload drawings for their justifications, which brought the rescue closer to the original design.
-The rescue had  1/40 (`r round(1/40*100)`%) correct justifications in the control group and 6/35 (`r round(6/35*100)`%) in the guided group.
-The rescue effect is smaller, but the overall result is rescued, and the adaptation feels like it could be built on.
+While we can't know for sure what caused the non-replication, there were clear problems observable from the small final sample and low-quality responses.
+The rescue targeted these issues by adding a pre-screen for naivete to the Monty Hall problem, switched the name of the problem (to reduce googling for answers), and had participants upload drawings for their justifications.
+Collectively, these changes brought the rescue closer to the intent of the original.
+The rescue had  1/40 (`r round(1/40*100)`%) correct justifications in the control group and 6/35 (`r round(6/35*100)`%) in the guided thinking group.
+The rescue effect is smaller, but the overall pattern of results replicated, and the online adaptation in the rescue feels like it could be built on.
 
-Another successful replication was that of CITE NGO2019.
-Here, the original study had a large effect, and so the replication, powering for 80% power on the reported effect, recruited a small sample of 12 people, and failed to find the effect.
-The rescue, powered using 2.5x the original sample (as recommended by TODO SMALL TELESCOPES CITE), recovered a clear effect (albeit a much smaller one).
-There are reasons to think that some effect sizes in the literature may be inflated CITATIONS, and separately potential reasons that slight changes to experiments, or swtiches to online, could result in noisier samples (and thus smaller effect sizes).
+Another successful replication was that of @ngo2019.
+Here, the original study found a large effect, and so the first replication, powering for 80% power on the reported effect, recruited a small sample of 12 people, and then failed to find the effect.
+The rescue, powered using 2.5x the original sample (as recommended by @simonsohn2015a), recovered a clear effect (albeit a much smaller one).
+There are reasons to think that some effect sizes in the literature may be inflated CITATIONS, and separately potential reasons that slight changes to experiments, or switches to online, could result in noisier samples (and thus smaller effect sizes).
 Thus, replications with smaller samples than the original (even if powered to the original effect size), may not be that diagnostic, and could potentially benefit from a re-replication.
 
-Not all rescues of small replication succeeded, however.
-TODO CITE PAYNE was a study of the effects of sleep versus wake on memory consolidation that showed participants a number of images and then hours later (after either sleep or no sleep) measured their recall for parts of the images.
+Not all rescues of small replications succeeded, however.
+@payne2008 was a study of the effects of sleep versus wake on memory consolidation that showed participants a number of images and then hours later (after either sleep or no sleep) measured their recall for parts of the images.
 The first replication struggled to recruit participants and only got 23 (the original had 48).
-The rescue attempted to recruit a larger sample (target 88), but due to difficulties getting participants to complete the second part 12 hours after the first, the rescue only managed to recruit 23 people.
+The rescue attempted to recruit a larger sample (target 88), but due to difficulties getting participants to complete the second part of the experiment 12 hours after the first, the rescue only managed to recruit 23 people.
 The lesson here may be that sleep research is difficult to conduct online.
 
-(other successes)
+(TODO other successes? )
 
@@
 #cors
+
 ```
 
-We ran correlations between a the set of predictor variables used in (TODO CITE BOYCE) and the subjective rescue success (TABLE WHATEVER).
-As the number of rescues is small, and many of these predictors are correlated, this should be taken suggestive only.
+We ran correlations between the set of predictor variables used in @boyce2023 and the subjective replication scores of the rescues (TABLE WHATEVER).
+As the number of rescues is small, and many of these predictors are correlated, these correlations should not be overinterpreted.
 
-We also added predictors related to the first replication sample size and the relative sizes of the samples (post-hoc, not pre-registered) because this seemed like a potentially important factor in a couple of the successful replications.
-Likely driven by these two, metrics related to original replication size were strong (TODO MATH).
+Given that a couple of the successful rescues seemed to succeed in part because of larger sample sizes, we also added predictors related to the first replication sample size and the relative sizes of the samples (post-hoc, not pre-registered).
+Likely driven by the two rescues discussed above, metrics related to original replication size were some of the strongest correlates of rescue replication success.
 
@@
 
-Two factors that seem like they would matter are relative sample size and replication closeness (CITE LEBEL). So here they are in a table.
+Two factors that seem like they would matter are relative sample size and replication closeness (using the classification scheme in @lebel), which are shown in TABLE TODO.
 
@@
 
-* We will compare the original, 1st replication, and re-replication effect sizes, as well as any effect sizes coming from independent replications (where effect size can be computed)
+In addition to looking at replication success overall, we also statistically compared the rescue, original replication, and original study on a "key effect" (we follow @boyce2023 in the determination of a key effect).
+When we were aware of additional direct replications (either from other class projects, or external replications), we also include these.
+
+TODO some of the error bars here don't look entirely consistent? 
+<!--* We will compare the original, 1st replication, and re-replication effect sizes, as well as any effect sizes coming from independent replications (where effect size can be computed)-->
+
+```{r, fig.cap="TODO"}
+
+#test on just one
+colors <- c("original"="black", "rep1"="#377EB8", "rescue"="#E41A1C", "additional"="#984EA3")
+for_plotting <- parsed_d |> filter(is.na(calc_d_calc)&!is.na(calc_ES)) |> 
+  mutate(point=calc_ES, low=calc_ES-1.96*calc_SE, high=calc_ES+1.96*calc_SE)
+
+for_plotting_d <- parsed_d |> filter(!is.na(calc_d_calc)) |> 
+  mutate(point=calc_d_calc, low=calc_d_calc-1.96*calc_d_calc_se, high=calc_d_calc+1.96*calc_d_calc_se)
+
+orig_scale <- ggplot(for_plotting,aes(x=target_lastauthor_year,y=point,ymin=low,ymax=high, color=type, shape=type, group=desc(type)))+
+  geom_errorbar(size=.5,width=.25, position=position_dodge(width=.4))+
+  geom_point(position=position_dodge(width=.4))+
+  coord_flip(ylim=c(-1.1,2))+
+  scale_size_area()+
+  geom_hline(yintercept=0,color="black")+
+  theme(legend.position = "none",
+        panel.grid.major.x = element_blank(), 
+        panel.grid.minor.x=element_blank()
+        )+
+  scale_color_manual(values=colors)+
+  labs(y="effect size on original scale", x="")
+
+smd_scale <- ggplot(for_plotting_d,aes(x=target_lastauthor_year,y=point,ymin=low,ymax=high,shape=type, color=type, group=desc(type)))+
+  geom_errorbar(size=.5,width=0, position=position_dodge(width=.5))+
+  geom_point(position=position_dodge(width=.5))+
+  coord_flip(ylim=c(-1.1,2))+
+  scale_size_area()+
+  geom_hline(yintercept=0,color="black")+
+    scale_color_manual(values=colors)+
+  theme(legend.position = "bottom", 
+        panel.grid.major.x = element_blank(), 
+        panel.grid.minor.x=element_blank()
+        )+
+  labs(y="Standarized mean difference", x="")
+
+plot_grid(orig_scale, smd_scale, nrow=2, rel_heights=c(.3,1))
+```
 
 ## Key measures 
-Cite that statistical consistency and replicating the claimed result are not the same thing
+TODO Cite that statistical consistency and replicating the claimed result are not the same thing.
+It is possible for results to be statistically consistent, especially given a certain level of heterogeneity, and to have them differ in whether they provide evidence for the effect in question.
 
-* We will use p-original to evaluate how consistent the original effect size is with the totality of replications.
+On the key measure, we use some statistics to compare how consistent the effects are.
+
+First, we will use p-original to evaluate how consistent the original effect size is with the totality of replications (first replication, rescue, and additional if found).
+Because of the small number of replications, we impute the heterogeneity value of TODO as in CITE.
+P-original measure the p-value on the null hypothesis that the original effect and the replications come from the same distribution.
+
+TODO should say what the # of <.05 / IQR / median are
+<!--* We will use p-original to evaluate how consistent the original effect size is with the totality of replications.
 We expect there to be a small number of replications, so we will impute the heterogeneity value as in https://osf.io/preprints/psyarxiv/dpyn6/.
+-->
 

### 2024-02-21 code/process.Rmd
poking

@@
          same_direction, replication_score, closeness, subfield, target_year, stanford_internal, 
-         open_data, open_materials, within_between, single_vignette)
+         open_data, open_materials, within_between, single_vignette, name_pretty)
 
@@
   geom_point(position=position_dodge(width=.4))+
-  coord_flip(ylim=c(-1.1,2))+
+  coord_flip()+
   scale_size_area()+
@@
   geom_point(position=position_dodge(width=.5))+
-  coord_flip(ylim=c(-1.1,2))+
+  coord_flip(ylim=c(-1.1,1.5))+
   scale_size_area()+

### 2024-02-21 manuscript/manuscript.Rmd
poking

@@
          same_direction, replication_score, closeness, subfield, target_year, stanford_internal, 
-         open_data, open_materials, within_between, single_vignette, cost)
+         open_data, open_materials, within_between, single_vignette, cost, name_pretty)
 
@@
 
-  mutate(Predictors=factor(preds, levels=c("social", "other_psych", "is_within", "single_vignette", "change_platform", "open_data", "open_mat", "stanford", "pub_year", "log_trials", "log_sample", "log_ratio_ss", "rep_1_log_sample", "log_ratio_rep1_orig", "log_ratio_rescue_rep1"), labels=c("Social", "Other psych", "Within subjects", "Single vignette", "Switch to online", "Open data", "Open materials", "Stanford", "Publication year", "Log trials", "Log original sample size", "Log rep/orig sample", "rep_1_log_sample", "log_ratio_rep1_orig", "log_ratio_rescue_rep1"))) |> arrange(Predictors) |> select(Predictors, r, p)
+  mutate(Predictors=factor(preds, levels=c("social", "other_psych", "is_within", "single_vignette", "change_platform", "open_data", "open_mat", "stanford", "pub_year", "log_trials", "log_sample", "log_ratio_ss", "rep_1_log_sample", "log_ratio_rep1_orig", "log_ratio_rescue_rep1"), labels=c("Social", "Other psych", "Within subjects", "Single vignette", "Switch to online", "Open data", "Open materials", "Stanford", "Publication year", "Log trials", "Log original sample size", "Log rescue/original sample size", "Log replication sample size", "Log replication/original sample size", "Log rescue/replication sample size"))) |> arrange(Predictors) |> select(Predictors, r, p)
 
 library(kableExtra)
-knitr::kable(cors, digits = 3, align='rcc', format="latex") #|> kable_styling(full_width=F, htmltable_class = "lightable-classic-2") 
+knitr::kable(cors, digits = 3, align='rcc', format="latex") |> kable_styling(full_width=F, htmltable_class = "lightable-classic-2") 
 #cors
@@
 ```{r}
-parsed_d |> select(target_lastauthor_year, type, N, closeness, replication_score) |> 
+parsed_d |> select(name_pretty, type, N, closeness, replication_score) |> 
   filter(type!="additional") |> 
   pivot_wider(names_from="type", values_from=c(N, closeness, replication_score)) |> 
-  select(paper=target_lastauthor_year, rescue_score=replication_score_rescue, N_original, N_rep1, N_rescue,
-         closeness_rep1, closeness_rescue) |> arrange(rescue_score |> desc())
+  select(paper=name_pretty, replication_score_rescue, N_original, N_rep1, N_rescue,
+         "Replication \\\\  closeness"=closeness_rep1, closeness_rescue) |> arrange(replication_score_rescue|> desc()) |> knitr::kable(align="lllll", format="latex", col.names=c("", "", "Original", "Replication", "Rescue", "Replication", "Rescue")) |> add_header_above(c("Paper"=1, "Score"=1, "N"=3, "closeness"=2))  |>kable_classic()
 
@@
 TODO some of the error bars here don't look entirely consistent?
+
+One issue with comparing on SMD scale is that noisier measures make the effect smaller even if the units are the same on the original scale. 
 <!--* We will compare the original, 1st replication, and re-replication effect sizes, as well as any effect sizes coming from independent replications (where effect size can be computed)-->
@@
 colors <- c("original"="black", "rep1"="#377EB8", "rescue"="#E41A1C", "additional"="#984EA3")
+
 for_plotting <- parsed_d |> filter(is.na(calc_d_calc)&!is.na(calc_ES)) |> 
   mutate(point=calc_ES, low=calc_ES-1.96*calc_SE, high=calc_ES+1.96*calc_SE) 
-
 for_plotting_d <- parsed_d |> filter(!is.na(calc_d_calc)) |> 
@@
 
-orig_scale <- ggplot(for_plotting,aes(x=target_lastauthor_year,y=point,ymin=low,ymax=high, color=type, shape=type, group=desc(type)))+
+orig_scale <- ggplot(for_plotting,aes(x=reorder(name_pretty, point, FUN=max), y,y=point,ymin=low,ymax=high, color=type, shape=type, group=desc(type)))+
   geom_errorbar(size=.5,width=.25, position=position_dodge(width=.4))+
   geom_point(position=position_dodge(width=.4))+
-  coord_flip(ylim=c(-1.1,2))+
+  coord_flip()+
   scale_size_area()+
@@
 
-smd_scale <- ggplot(for_plotting_d,aes(x=target_lastauthor_year,y=point,ymin=low,ymax=high,shape=type, color=type, group=desc(type)))+
+smd_scale <- ggplot(for_plotting_d,aes(x=reorder(name_pretty, point, FUN=max),y=point,ymin=low,ymax=high,shape=type, color=type, group=desc(type)))+
   geom_errorbar(size=.5,width=0, position=position_dodge(width=.5))+
   geom_point(position=position_dodge(width=.5))+
-  coord_flip(ylim=c(-1.1,2))+
+  coord_flip(ylim=c(-1.1,1.5))+
   scale_size_area()+
@@
 
+```{r}
+do_d_predInt_het <- function(df){
+  if(!is.na(df$d)&!is.na(df$d_se)&!is.na(df$rep_d)&!is.na(df$rep_d_se)){
+    yio=df$d
+    vio=df$d_se**2
+    yir=df$rep_d
+    vir=df$rep_d_se**2
+    t2=.21**2
+    pooled.SE = sqrt(vio + vir + t2)
+    PILo.sens = yio - qnorm(0.975) * pooled.SE
+    PIHi.sens = yio + qnorm(0.975) * pooled.SE
+    PIinside.sens = (yir > PILo.sens) & (yir < PIHi.sens)
+    return(tibble(d_low=PILo.sens, d_high=PIHi.sens, d_inside=PIinside.sens))
+  }
+  return(tibble(d_low=NA,d_high=NA, d_inside=NA))
+}
+
+```
+
+```{r}
+orig <- parsed_d |> filter(type=="original") |> select(target_lastauthor_year, d=calc_d_calc, d_se=calc_d_calc_se, es=calc_ES, es_se=calc_SE)
+
+predInts_het <- parsed_d |> 
+  filter(type!="original") |> 
+  group_by(target_lastauthor_year, name_pretty) |> 
+  select(target_lastauthor_year, type, rep_d=calc_d_calc, rep_d_se=calc_d_calc_se, rep_es=calc_ES, rep_es_se=calc_SE) |> 
+  left_join(orig) |> 
+  group_by(target_lastauthor_year,type) |> 
+  nest() |> 
+  mutate(d_pred_int=map(data,do_d_predInt_het)) |> 
+  unnest_wider(d_pred_int) |> 
+  unnest_wider(data)
+
+```
+
+```{r, fig.height=6, fig.width=6}
+colors <- c("original"="black", "rep1"="#377EB8", "rescue"="#E41A1C", "additional"="#984EA3")
+
+ ggplot(predInts_het |> filter(!is.na(d_inside)), aes(x=reorder(name_pretty, d, FUN=max), y=rep_d, ymin=d_low, ymax=d_high, color=type, group=desc(type), shape=type))+
+  geom_errorbar(size=.5,width=.25, position=position_dodge(width=.4), color="black", alpha=.5)+
+  geom_point(aes(y=d), color="black", position=position_dodge(width=.3), shape=1, alpha=.5)+
+     geom_point(size=2.5, position=position_dodge(width=.4))+
+
+  coord_flip()+
+  scale_size_area()+
+  geom_hline(yintercept=0,color="black")+
+  theme(legend.position="bottom", 
+        panel.grid.major.x = element_blank(), 
+        panel.grid.minor.x=element_blank()
+        )+
+  scale_color_manual(values=colors)+
+  labs(y="predInts on SMD scale", x="")
+
+```
+
 # Acknowledgements {-}

### 2024-02-22 manuscript/manuscript.Rmd
poking

@@
 bibliography: ["251rescue.bib"] # Replace with one or more of your own bibtex files. Better BibTeX for Zotero is your friend
-csl: vancouver.csl # Use any CSL style. See https://www.zotero.org/styles for a good list. Ignored if citation_package: natbib
+csl: apa6.csl # Use any CSL style. See https://www.zotero.org/styles for a good list. Ignored if citation_package: natbib
 link-citations: TRUE
@@
 ## Pre-registration
-Our analysis plan was pre-registered after students had selected projects, but before final data collection on the projects (CHECK IF TRUE).
+Our analysis plan was pre-registered after students had selected projects, but before final data collection on the projects.
 Each project was also individually pre-registered by the student conducting it.
@@
 library(kableExtra)
-knitr::kable(cors, digits = 3, align='rcc', format="latex") |> kable_styling(full_width=F, htmltable_class = "lightable-classic-2") 
-#cors
+knitr::kable(cors, digits = 3, align='rcc', format="latex", booktabs=T, linesep="", caption="TODO CAPTION")
 
@@
 Given that a couple of the successful rescues seemed to succeed in part because of larger sample sizes, we also added predictors related to the first replication sample size and the relative sizes of the samples (post-hoc, not pre-registered).
-Likely driven by the two rescues discussed above, metrics related to original replication size were some of the strongest correlates of rescue replication success.
+While not signficant, the strongest correlates of rescue success were open materials, a small sample size on the first replication, a small sample size on the first replication relative to the original sample size, and a large rescue sample size relative to the first replication.
 
-This is correlational, and we know that small replication samples relative to original and rescue could be due both to a) aiming for a small replication sample due to aiming for power for a reported large effect size or b) difficulties with recruitment or high exclusion rates leading to a smaller than intended sample.
+Small replication samples relative to original and rescue could be due both to a) aiming for a small replication sample due to aiming for power for a reported large effect size or b) difficulties with recruitment or high exclusion rates leading to a smaller than intended sample.
 
-Two factors that seem like they would matter are relative sample size and replication closeness (using the classification scheme in @lebel), which are shown in TABLE TODO.
+Two measures associated with how satisfying a replication attempt was are its sample size (relative to the original) and how close the replication was to the original.
+We show these measures (using the classification scheme of @lebel for closeness) in TABLE TODO.
 
@@
   select(paper=name_pretty, replication_score_rescue, N_original, N_rep1, N_rescue,
-         "Replication \\\\  closeness"=closeness_rep1, closeness_rescue) |> arrange(replication_score_rescue|> desc()) |> knitr::kable(align="lllll", format="latex", col.names=c("", "", "Original", "Replication", "Rescue", "Replication", "Rescue")) |> add_header_above(c("Paper"=1, "Score"=1, "N"=3, "closeness"=2))  |>kable_classic()
+         "Replication \\\\  closeness"=closeness_rep1, closeness_rescue) |> arrange(replication_score_rescue|> desc()) |> knitr::kable(align="lllll", format="latex", booktabs=T, linesep="", caption="TODOCAPTION", col.names=c("", "", "Original", "Replication", "Rescue", "Replication", "Rescue")) |> add_header_above(c("Paper"=1, "Score"=1, "N"=3, "closeness"=2))
 
@@
 When we were aware of additional direct replications (either from other class projects, or external replications), we also include these.
-
-TODO some of the error bars here don't look entirely consistent?
 

### 2024-02-23 manuscript/manuscript.Rmd
work on results

@@
 library(kableExtra)
+library(metafor)
 #r_refs("r-references.bib", append=F)
@@
 Somewhere in here we should acknowledge that there's current discussion around replication rates and interpretation and so forth.
+
 ## Why replication failure? 
@@
 
-chosen <- c("sofer2015", "birch2007_2", "jara-ettinger2022", "porter_2016_1",
+chosen <- c("birch2007_2", "jara-ettinger2022", "porter_2016_1",
             "hopkins2016", "yeshurun2003", "craig2014", "tarampi2016", 
@@
 PSYCH 251 is a graduate-level experimental methods class taught by MCF.
-In previous years, students have conducted replication projects, which were analyzed for replication rate and properties in @boyce2023.
+In previous years, students have conducted replication projects, as reported in @boyce2023.
 In Fall 2023, students in PSYCH 251 were offered the option to do a "rescue" project where they re-replicated one of the unsuccessful replications from a previous year (students could also opt to do a normal replication instead).
@@
 We then contacted the replication project authors for permission to share their report and github repository with a new student and include it as a supplement on a resulting paper.
-This left `r nrow(approved)` options that were offered to the students.
-`r nrow(chosen)` students chose to do rescue projects; `r nrow(chosen)-num_proj` students took an incomplete or did not indicate interest in being part of the rescue paper, leaving a final sample of `r num_proj` rescue projects.
+This left `r length(approved)` options that were offered to the students.
+`r length(chosen)` students chose to do rescue projects; `r length(chosen)-num_proj` students took an incomplete or did not indicate interest in being part of the rescue paper, leaving a final sample of `r num_proj` rescue projects.
 
@@
 Students conducted their rescue projects over the course of the 10-week class.
-Once they had chosen a project we gave them access to the original replicators write-up and repository, which often included the data, experiment code, and analytic code.
+Once they had chosen a project we gave them access to the original replicators' write-up and repository, which often included the data, experiment code, and analytic code.
 In many cases, students were also given the contact information of the original replicator (a few original replicators opted not to be contacted by students).
@@
 
-With one exception, samples were collected on Prolific (the rescue of TODO ran in-person on the Stanford student subject pool).
-We tried to power studies adequately (with a target of 2.5x original if possible), but due to cost constraints, not all studies were powered at this level (See table TODO for post-exclusion sample sizes of original, replication, and rescues).
+With one exception, samples were collected on Prolific (the rescue of @yeshurun2003 ran in-person on the Stanford student subject pool).
+We tried to power studies adequately (with a target of 2.5x original following @simonsohn2015), but due to cost constraints, not all studies were powered at this level.
+(See table TODO for post-exclusion sample sizes of original, replication, and rescues).
 Across the `r num_proj-1` studies, we spent $`r pluck(cost,1,1) |> round()`, for an average of $`r (pluck(cost,1,1)/(num_proj-1)) |> round()` per project.
-
-Constraints on budget, timeline, and primarily online studies obviously constrain how closely and well some studies could be replicated.
-However, these are representative of the sort of limitations on early-career researchers.
 
@@
 
-## Analysis of rescue success
+## Coding of results
 We followed @boyce2023 in what study properties we measured and what measures of replication success we used.
 
-Each project was rated on the basis of subjective replication success both by MCF and by one of VB and BP. Disagreements were resolved through discussion.
+Each project was rated on the basis of subjective replication success both by MCF and by one of VB and BP.
+Disagreements were resolved through discussion.
+As a compliment to the overall subjective rating of success, we followed @boyce2023 in also doing a statistical comparison on one key measure of interest for each study.
 
-We used the same key measures of interest as in @boyce2023.
  We also recorded the same set of potential correlates that were used in @boyce2023 for original, replication, and rescue (these were already rated for original and replication).
+These potential correlates included features of the original study including the subfield of the study (cognitive v social v other psychology), it's publication year,  experimental design features including whether it was a within- or between- subject design, whether each condition was instantiated with one vignette or multiple, and how many items each participant saw, and whether there were open materials and open data.
 
-As the number of project is much smaller, we do not model success in terms of the potential correlates, but merely report the correlation of each property with the subjective outcome variable.
+For the original study and each replication, we recorded the number of participants post-exclusions.
+For studies where some extra conditions were dropped, we count only the participants in the key conditions all replications had for comparability.
+For instance, if an original study compared between two critical conditions but also had a baseline control, we would not count the participants in the baseline condition if a replication did not include this condition.
+We also recorded whether each study was conducted online with a crowdsourced platform or not.
 
 # Results
+
+Our primary question of interest is how many of these `r num_proj` rescue projects succeeded at replicating the results in the original study.
+When a replication fails to obtain the same results, one may have intuitions about what may have gone wrong -- these rescue projects test whether addressing these potential issues in fact works.
 
@@
 `r pluck(tallied,2,1)` had a rating of 0, `r pluck(tallied, 2,2)` got a rating of  .75, and `r pluck(tallied, 2,3)` got a rating of 1.
+Thus, a first pass answer to the question "how often can a failed replication be salvaged?" is `r round(nrow(success)/nrow(subj)*100)`% of the time.
+TODO DO WE WANT TO BOOTSTRAP A CI ON THIS?
 
@@
 
-(TODO other successes? )
+(TODO other successes or failures we want to discuss? )
 
@@
 
-## Effect size of key measure
-
-In addition to looking at replication success overall, we also statistically compared the rescue, original replication, and original study on a "key effect" (we follow @boyce2023 in the determination of a key effect).
-When we were aware of additional direct replications (either from other class projects, or external replications), we also include these.
-
-One issue with comparing on SMD scale is that noisier measures make the effect smaller even if the units are the same on the original scale. 
-<!--* We will compare the original, 1st replication, and re-replication effect sizes, as well as any effect sizes coming from independent replications (where effect size can be computed)-->
+Aside from the suggestion that fixing sample size issues may have helped, it's unclear why some projects replicated this time and most did not.
 
@@
 
-## Key measures 
-TODO Cite that statistical consistency and replicating the claimed result are not the same thing.
-It is possible for results to be statistically consistent, especially given a certain level of heterogeneity, and to have them differ in whether they provide evidence for the effect in question.
+## Effect sizes
 
-On the key measure, we use some statistics to compare how consistent the effects are.
+In addition to looking at replication success overall, we also statistically compared the rescue, original replication, and original study on a key effect (we follow @boyce2023 in the determination of a key effect).
+When we were aware of additional direct replications (either from other class projects, or external replications in the literature), we also include these.
 
-First, we will use p-original to evaluate how consistent the original effect size is with the totality of replications (first replication, rescue, and additional if found).
-Because of the small number of replications, we impute the heterogeneity value of TODO as in CITE.
-P-original measure the p-value on the null hypothesis that the original effect and the replications come from the same distribution.
+We first compare the original and replications effect sizes on the key effect of interest.
+Where possible, we report this comparison in standardized mean difference (SMD) units, although the reporting of a few studies makes comparison only possible in the original units.
+One potential issue with comparisons using SMD is that noisier measures will have smaller standardized effect sizes even if the effect on the original scale is the same.
+The effect sizes are shown in FIGURE TODO.
+In general, the replication and rescue effect sizes were smaller than the original effect sizes, and in a couple cases the effects were in the opposite direction.
 
-TODO should say what the # of <.05 / IQR / median are
+```{r}
+do_rma <- function(df) {
+  if(!any(is.na(df$es))){
+  r<- rma(yi=df$es, sei=df$es_se, slab=df$type)
+  return(tibble(rma_est=r$beta[,1],rma_se=r$se))
+  }
+  return(tibble(rma_est=NA, rma_se=NA))
+}
+
+do_d_rma <- function(df) {
+  if(!any(is.na(df$d))){
+  r<- rma(yi=df$d, sei=df$d_se, slab=df$type)
+  return(tibble(rma_d_est=r$beta[,1], rma_d_se=r$se))
+  }
+  return(tibble(rma_d_est=NA, rma_d_se=NA))
+
+}
+
+do_p_orig <- function(es, es_se, rep_es, rep_se){
+  if(!is.na(es)&!is.na(es_se)&!is.na(rep_es)&!is.na(rep_se)){
+    return(Replicate::p_orig(es, es_se**2,rep_es, t2=0.21**2, rep_se**2))
+  }
+  return(NA)
+}
+
+orig <- parsed_d |> filter(type=="original") |> select(target_lastauthor_year, d=calc_d_calc, d_se=calc_d_calc_se, es=calc_ES, es_se=calc_SE)
+
+orig_v_others <- parsed_d |> select(target_lastauthor_year, type, d=calc_d_calc, d_se=calc_d_calc_se, es=calc_ES, es_se=calc_SE) |> 
+  filter(type!="original") |> 
+  group_by(target_lastauthor_year) |> 
+  nest() |> 
+  mutate(rma_result=map(data, do_rma),
+         d_rma_result=map(data, do_d_rma)) |> 
+  unnest_wider(rma_result) |> 
+  unnest_wider(d_rma_result) |> 
+  left_join(orig) |> 
+  rowwise() |> 
+  mutate(d_p_orig=do_p_orig(d, d_se, rma_d_est, rma_d_se))
+
+orig_v_rescue <- parsed_d |>   filter(type=="rescue") |> 
+  select(target_lastauthor_year, type, res_d=calc_d_calc, res_d_se=calc_d_calc_se, res_es=calc_ES, res_es_se=calc_SE) |>
+
+  left_join(orig) |> 
+  rowwise() |> 
+  mutate(d_p_orig=do_p_orig(d, d_se, res_d, res_d_se))
+
+orig_v_not_rescue <- parsed_d |> select(target_lastauthor_year, type, d=calc_d_calc, d_se=calc_d_calc_se, es=calc_ES, es_se=calc_SE) |> 
+  filter(type!="original", type!="rescue") |> 
+  filter(target_lastauthor_year!="krauss2003") |> # have to avoid the divide by 0 error
+  group_by(target_lastauthor_year) |> 
+  nest() |> 
+  mutate(rma_result=map(data, do_rma),
+         d_rma_result=map(data, do_d_rma)) |> 
+  unnest_wider(rma_result) |> 
+  unnest_wider(d_rma_result) |> 
+  left_join(orig) |> 
+  rowwise() |> 
+  mutate(d_p_orig=do_p_orig(d, d_se, rma_d_est, rma_d_se))
+
+rescue_only <- parsed_d |> filter(type=="rescue") |> select(target_lastauthor_year, d=calc_d_calc, d_se=calc_d_calc_se, es=calc_ES, es_se=calc_SE)
+
+rescue_v_reps <- parsed_d |> select(target_lastauthor_year, type, d=calc_d_calc, d_se=calc_d_calc_se, es=calc_ES, es_se=calc_SE) |> 
+  filter(type!="original", type!="rescue") |> 
+  filter(target_lastauthor_year!="krauss2003") |> # have to avoid the divide by 0 error
+  group_by(target_lastauthor_year) |> 
+  nest() |> 
+  mutate(rma_result=map(data, do_rma),
+         d_rma_result=map(data, do_d_rma)) |> 
+  unnest_wider(rma_result) |> 
+  unnest_wider(d_rma_result) |> 
+  left_join(rescue_only) |> 
+  rowwise() |> 
+  mutate(d_p_orig=do_p_orig(d, d_se, rma_d_est, rma_d_se))
+
+ all <- orig_v_others |> select(target_lastauthor_year, orig_v_other=d_p_orig) |> 
+  left_join(orig_v_rescue |> select(target_lastauthor_year, orig_v_rescue=d_p_orig)) |> 
+  left_join(orig_v_not_rescue |> select(target_lastauthor_year, orig_v_not_rescue=d_p_orig)) |> 
+  left_join(rescue_v_reps |> select(target_lastauthor_year, rescue_v_reps=d_p_orig)) |> 
+  rename(paper=target_lastauthor_year)
+
+main_summ <- all |> ungroup() |> select(orig_v_other) |>
+  summarize(median=median(orig_v_other, na.rm=T),
+            low=quantile(orig_v_other, .25, na.rm=T),
+            high=quantile(orig_v_other, .75, na.rm=T),
+            less_than=sum(orig_v_other<.05, na.rm=T)/sum(!is.na(orig_v_other)))
+
+rescue_summ <- all |> ungroup() |> select(orig_v_rescue) |>
+  summarize(median=median(orig_v_rescue, na.rm=T),
+            low=quantile(orig_v_rescue, .25, na.rm=T),
+            high=quantile(orig_v_rescue, .75, na.rm=T),
+            less_than=sum(orig_v_rescue<.05, na.rm=T)/sum(!is.na(orig_v_rescue)))
+
+rep_summ <- all |> ungroup() |> select(orig_v_not_rescue) |>
+  summarize(median=median(orig_v_not_rescue, na.rm=T),
+            low=quantile(orig_v_not_rescue, .25, na.rm=T),
+            high=quantile(orig_v_not_rescue, .75, na.rm=T),
+            less_than=sum(orig_v_not_rescue<.05, na.rm=T)/sum(!is.na(orig_v_not_rescue)))
+
+rescue_rep_summ <- all |> ungroup() |> select(rescue_v_reps) |>
+  summarize(median=median(rescue_v_reps, na.rm=T),
+            low=quantile(rescue_v_reps, .25, na.rm=T),
+            high=quantile(rescue_v_reps, .75, na.rm=T),
+            less_than=sum(rescue_v_reps<.05, na.rm=T)/sum(!is.na(rescue_v_reps)))
+```
+## Consistency of effects 
+We statistically compared the original effects with the replication effect sizes to determine their level of statistical consistency, that is whether these effects were likely to be drawn from the same distribution, given a certain level of heterogeneity.
+
+We note that CITE!
+statistical consistency does not always align with our intuitions of replication or with whether an effect provides support for the hypothesis.
+A replication may be statistically consistent with the original effect but not provide any evidence for the claimed result.
+
+We use p-original to evaluate how consistent the original effect size is with the totality of replications (first replication, rescue, and additional if found).
+Because of the small number of replications, we impute the heterogeneity value of $\tau=.21$ SMD, which is the average level of heterogeneity found by @olsson2020 in prior multi-site replications in psychology.
+P-original measures the p-value on the null hypothesis that the original effect and the replications come from the same distribution.
+
+The median value of p_original was `r main_summ$median |> round(2)` [IQR: `r main_summ$low |> round(2)` - `r main_summ$high |> round(2)`].
+`r round(main_summ$less_than*100)`% of the p_original values were less than .05, indicating by conventional thresholds a rejection of the null hypothesis that the original and the replications came from the same distribution for the given imputed level of heterogeneity.
+
+As secondary measures, we also calculated the p-original values for a) the original and the rescue, b) the original and non-rescue replications, and c) between the rescue and other replications. 
+For a) the rescue versus the original, median value of p_original was `r rescue_summ$median |> round(2)` [IQR: `r rescue_summ$low |> round(2)` - `r rescue_summ$high|> round(2)`], and  `r round(rescue_summ$less_than*100)`% of the p_original values were less than .05.
+For b) the non-rescue replications versus the original, median value of p_original was `r rep_summ$median |> round(2)` [IQR: `r rep_summ$low |> round(2)` - `r rep_summ$high |> round(2)`], and  `r round(rep_summ$less_than*100)`% of the p_original values were less than .05.
+For c) the rescue versus the other replications, median value of p_original was `r rescue_rep_summ$median |> round(2)` [IQR: `r rescue_rep_summ$low |> round(2)` - `r rescue_rep_summ$high |> round(2)`], and  `r round(rescue_rep_summ$less_than*100)`% of the p_original values were less than .05.
+
+NOTE THERE ARE A LOT OF MISSING DATA HERE!!!
+
 <!--* We will use p-original to evaluate how consistent the original effect size is with the totality of replications.
@@
 -->
-
-## Secondary
-
-a) p-original between just the original and rescue,
-
-b) p-original between the original and all replications except the rescue (in the case where no replications are found in the literature, this is the same as done in https://osf.io/preprints/psyarxiv/dpyn6/)
-
-c) p-original between the rescue and all other replications.
 
@@
 
+# Discussion
+We don't have qualitative or quantitive explanations for why some replicated and some didn't.
+We can't predict what replication failures are likely to resolve given another try (or a more thoughtful try), beyond that suggestion that glaring problems and low samples may sometimes be resolvable.
+
+So, if you have a replication that failed, in a topic you're interested in pursuing cumulative science on, should you drop it, or try again?
+Our sample says that the odds of a re-replication working are low, so especially if there isn't a super clear failure mode to point to, another try probably won't fix it.
+
+Something about how even the "successes" have diminished effect sizes 
+## Limitations
+it's a small sample size and non-random 
+Constraints on budget, timeline, and primarily online studies obviously constrain how closely and well some studies could be replicated.
+However, these are representative of the sort of limitations on early-career researchers.
 # Acknowledgements {-}

### 2024-02-23 manuscript/manuscript.Rmd
smdification, plot futzing

@@
 
-```{r, fig.cap="TODO"}
+```{r, fig.cap="Standardized effect sizes of original studies, first replications, rescues, and additional replications if available.
+Due to the large effect size of a couple studies, large effect studies are shown in a separate panel.
+"}
 
@@
 colors <- c("original"="black", "rep1"="#377EB8", "rescue"="#E41A1C", "additional"="#984EA3")
+shape <- c("original"=21,"rep1"=22,"rescue"=23,"additional"=24)
 
-for_plotting <- parsed_d |> filter(is.na(calc_d_calc)&!is.na(calc_ES)) |> 
-  mutate(point=calc_ES, low=calc_ES-1.96*calc_SE, high=calc_ES+1.96*calc_SE) 
+big <- parsed_d |> filter(type=="original") |> filter(calc_d_calc>1) |> select(target_lastauthor_year)
 for_plotting_d <- parsed_d |> filter(!is.na(calc_d_calc)) |> 
@@
 
-orig_scale <- ggplot(for_plotting,aes(x=reorder(name_pretty, point, FUN=max), y,y=point,ymin=low,ymax=high, color=type, shape=type, group=desc(type)))+
-  geom_errorbar(size=.5,width=.25, position=position_dodge(width=.4))+
-  geom_point(position=position_dodge(width=.4))+
+smd_scale_small <- ggplot(for_plotting_d |> anti_join(big),aes(x=reorder(name_pretty, point, FUN=max),y=point,ymin=low,ymax=high,shape=type, color=type, fill=type, group=desc(type)))+
+  geom_errorbar(size=.5,width=0, position=position_dodge(width=.5))+
+  geom_point(position=position_dodge(width=.5))+
  coord_flip()+
@@
   geom_hline(yintercept=0,color="black")+
-  theme(legend.position = "none",
-        panel.grid.major.x = element_blank(), 
-        panel.grid.minor.x=element_blank()
-        )+
-  scale_color_manual(values=colors)+
-  labs(y="effect size on original scale", x="")
-
-smd_scale <- ggplot(for_plotting_d,aes(x=reorder(name_pretty, point, FUN=max),y=point,ymin=low,ymax=high,shape=type, color=type, group=desc(type)))+
-  geom_errorbar(size=.5,width=0, position=position_dodge(width=.5))+
-  geom_point(position=position_dodge(width=.5))+
-  coord_flip(ylim=c(-1.1,1.5))+
-  scale_size_area()+
-  geom_hline(yintercept=0,color="black")+
-    scale_color_manual(values=colors)+
+    scale_color_manual(values=colors, aesthetics=c("color", "fill"))+
+  scale_shape_manual(values=shape)+
   theme(legend.position = "bottom", 
@@
 
-plot_grid(orig_scale, smd_scale, nrow=2, rel_heights=c(.3,1))
+smd_scale_big <- ggplot(for_plotting_d |> inner_join(big),aes(x=reorder(name_pretty, point, FUN=max),y=point,ymin=low,ymax=high,shape=type, color=type, fill=type, group=desc(type)))+
+  geom_errorbar(size=.5,width=0, position=position_dodge(width=.5))+
+  geom_point(position=position_dodge(width=.5))+
+ coord_flip()+
+  scale_size_area()+
+  geom_hline(yintercept=0,color="black")+
+    scale_color_manual(values=colors, aesthetics=c("color", "fill"))+
+    scale_shape_manual(values=shape)+
+  theme(legend.position = "none", 
+        panel.grid.major.x = element_blank(), 
+        panel.grid.minor.x=element_blank()
+        )+
+  labs(y="Standarized mean difference", x="")
+
+#smd_scale_big
+#smd_scale_small
+
+plot_grid(smd_scale_big, smd_scale_small, rel_heights=c(.3,1), nrow=2)
 ```
@@
 colors <- c("original"="black", "rep1"="#377EB8", "rescue"="#E41A1C", "additional"="#984EA3")
+shape <- c("original"=21,"rep1"=22,"rescue"=23,"additional"=24)
+col_code <- c("TRUE"="darkgreen", "FALSE"="black")
 
- ggplot(predInts_het |> filter(!is.na(d_inside)), aes(x=reorder(name_pretty, d, FUN=max), y=rep_d, ymin=d_low, ymax=d_high, color=type, group=desc(type), shape=type))+
-  geom_errorbar(size=.5,width=.25, position=position_dodge(width=.4), color="black", alpha=.5)+
-  geom_point(aes(y=d), color="black", position=position_dodge(width=.3), shape=1, alpha=.5)+
-     geom_point(size=2.5, position=position_dodge(width=.4))+
+big <- predInts_het |> filter(d>1) |> select(target_lastauthor_year)
 
+small_predInt <-  ggplot(predInts_het |> filter(!is.na(d_inside)) |> anti_join(big), aes(x=reorder(name_pretty, d, FUN=max), y=rep_d, ymin=d_low, ymax=d_high, fill=type, color=d_inside, group=desc(type), shape=type))+
+  geom_errorbar(size=.5, width=.25, position=position_dodge(width=.4), alpha=.5)+
+  geom_point(aes(y=d), position=position_dodge(width=.4), shape=1, alpha=.5)+
+     geom_point(size=2.5, position=position_dodge(width=.4), color="transparent")+
   coord_flip()+
@@
         )+
-  scale_color_manual(values=colors)+
+  scale_fill_manual(values=colors)+
+  scale_shape_manual(values=shape)+
+  scale_color_manual(values=col_code)+
   labs(y="predInts on SMD scale", x="")
+
+big_predInt <-  ggplot(predInts_het |> filter(!is.na(d_inside)) |> inner_join(big), aes(x=reorder(name_pretty, d, FUN=max), y=rep_d, ymin=d_low, ymax=d_high, color=d_inside, fill=type, group=desc(type), shape=type))+
+  geom_errorbar(size=.5,width=.25, position=position_dodge(width=.4), alpha=.5)+
+  geom_point(aes(y=d), position=position_dodge(width=.4), shape=1, alpha=.5)+
+     geom_point(size=2.5, position=position_dodge(width=.4), color="transparent")+
+  coord_flip()+
+  scale_size_area()+
+  geom_hline(yintercept=0,color="black")+
+  theme(legend.position="none", 
+        panel.grid.major.x = element_blank(), 
+        panel.grid.minor.x=element_blank()
+        )+
+  scale_fill_manual(values=colors)+
+  scale_shape_manual(values=shape)+
+  scale_color_manual(values=col_code)+
+  labs(y="predInts on SMD scale", x="")
+
+plot_grid(big_predInt, small_predInt, nrow=2, rel_heights = c(.3,1))
 

### 2024-02-23 code/helper/parse_stats.R

@@ -60,20 +60,37 @@ parse_prop <- function(propval){
   est2_var <- est2*(1-est2)/den2
   diff <- est1-est2
   diff_var <- est1_var+est2_var
-  return(data.frame("df_1"=NA, "df_2"=NA,"tstat"=NA, "fstat"=NA, "p_calc"=NA, "d_calc"=NA, "d_calc_se"=NA, "N_calc"=NA, "ES"=diff, "SE"=sqrt(diff_var)))
+  OR_result<- escalc(ai=num1, ci=num2, n1i=den1, n2i=den2, measure="OR")
+  #following https://training.cochrane.org/handbook/current/chapter-10#section-10-6 for conversion!
+  OR <- OR_result$yi
+  se_OR <- OR_result$vi**.5 #SE is sqrt variance in this context
+  d_calc=sqrt(3)/3.14159*OR
+  d_calc_se=sqrt(3)/3.14159*se_OR
+  return(data.frame("df_1"=NA, "df_2"=NA,"tstat"=NA, "fstat"=NA, "p_calc"=NA, "d_calc"=d_calc, "d_calc_se"=d_calc_se, "N_calc"=NA, "ES"=diff, "SE"=sqrt(diff_var)))
 }
+#parse_prop(ex)
+
 #parse_prop(ex)
 
 
 # for one proportion
-#ex <- "raw prop : 10 / 18"
+#ex <- "raw prop : 10 / 18, chance= 1/3"
 parse_raw_prop <- function(propval){
   val <- str_extract_all(propval, "[0-9]+")[[1]]
+  chance <- str_extract(propval, "chance=.*")
+  chance_val <- str_extract_all(chance, "[0-9]+")[[1]]
+  chance_rate <- as.numeric(chance_val[1])/as.numeric(chance_val[2])
   num1 <- val[1] |> as.numeric()
   den1 <- val[2] |> as.numeric()
   est1 <- num1/den1
   est1_var <- est1*(1-est1)/den1
-  return(data.frame("df_1"=NA, "df_2"=NA,"tstat"=NA, "fstat"=NA, "p_calc"=NA, "d_calc"=NA, "d_calc_se"=NA,"N_calc"=NA, "ES"=est1, "SE"=sqrt(est1_var)))
+  d_calc <- (est1-chance_rate)/sqrt(est1_var)
+  d_se <- (1 / den1) + (d_calc ^ 2 / (2 * den1)) 
[…]

### 2024-02-24 manuscript/manuscript.Rmd
mostly full very rough draft

@@
 ---
-title: "TODO (re-replication) (student) (cumulative science) (failure to replicate) "
+title: "TODO (re-replication) (student) (cumulative science) (try again) (replication failure) "
 author:
@@
 TODO abstract
+* cumulative science requires being able to replicate results
+* given one failed replication, is a second attempt at replication likely to succeed?
+We re-replicated 17 experiments that had previously had a failed student replication, reported in Boyce et al.
+(2023).
+In N/17 of these rescue projects (TODO %), the results mostly or fully replicated.
+We discuss the relative effect sizes and levels of statistical consistency between original effect sizes and replication effect sizes.
+While a few studies with failed replications were rescued with larger sample sizes and experimental tweaks, our overall results indicate that most failed replications stayed failed.
+If the goal is to do cumulative science, one may wish to stop after one failed replication.
+TODO MAKE THIS ABSTRACT BETTER!
 :::
@@
 
-How definitive are failed replications?
+Imagine the scenario where you are a new graduate student, and you run a replication of a study in the literature that you are interested in building upon in your research.
+The replication fails.
+Should you try again, running another replication, perhaps with a larger sample or other tweaks to possibly fix the replication?
+Or should you give up on replicating that specific study, and find a different study to replicate and build upon?
 
-While individual studies are not definitive when it comes to scientific evidence, they often influence what scientists pursue -- it worked -- keep going that direction, it didn't, possibly try again, or switch to a different question or method.
+There has been much discussion in the literature about how we should interpret replication results in terms of the existence of a true effect or effect size. TODO CITATIONS
 
-TODO cite the MB whatever that tried this.
+<!--Well, it depends on what you're trying to measure.
+From the perspective of learning from the field as a whole things are complicated and may depend also on a priori information from other related studies, the beleivability of the results, the relative rigor and sample sizes of the original and replication (TODO perhaps cite the time invariant).
+-->
+We take a different angle on replications, and instead focus scientists decisions on what studies to run.
+Individual studies (and replications) are rarely definitive when it comes to scientific evidence, but they often influence what studies a scientist conducts.
+If a study works, scientists are likely to continue to purse that result, but if a study doesn't work, scientists have to choose whether to try again, or switch to a different study.
 
-Well, it depends on what you're trying to measure.
-From the perspective of learning from the field as a whole things are complicated and may depend also on a priori information from other related studies, the beleivability of the results, the relative rigor and sample sizes of the original and replication (TODO perhaps cite the time invariant).
+How definitive is a replication failure?
+That is, if a study fails to replicate, what are the chances that an additional replication succeeds.
+After CITE OSF found an overall replication rate of WHATEVER, concerns were raised about some potential problems with some of the replications, that might have contributed to the replicaiton failures.
+TO address this ManyLABSWHATEVER NUMBER re-replicated N of these both independently and with ...
 
-Researchers do care about that from theory-building perspectives, but there's also a more local reason.
-Given that a student or lab has attempted a direct replication and that replication has not gotten the desired results of the original, what should they do?
-Should they try to replicate it again (potentially learning something about how to improve their experiment from the unsuccessful replication)?
-Or should they concluded that for them, given the resources they have, it isn't worth pursuing that particular experimental design?
-
-Somewhere in here we should acknowledge that there's current discussion around replication rates and interpretation and so forth.
+TODO READ THAT MANY LABS PAPER AGAIN.
 
 ## Why replication failure? 
+The idea of replication failure implies a certain time direction: first a "successful" study and (later) a "failed" replication.
+(CITE TIME INVARIANCE) We can also consider this as two very-related studies that got different results, and thus the question is what difference between these two studies could account for the differing results.
+
+[not sure if it would be better to structure this differently]
+
 A replication can have different results from the original study for a number of different potential reasons.
@@
 The original could have an inflated effect size, due to some combination of heterogeneity, p-hacking, luck, and publication bias.
+
 The replication could have been underpowered due to any of inflated original effect size, attrition in sample, or the original also being underpowered.
@@
 
-[list reasons] While one can theorize after the fact about potential causes, in most circumstances it is hard to diagnose for certain what made for the difference in the results.
+While one can theorize after the fact about potential causes, in most circumstances it is hard to diagnose for certain what made for the difference in the results.
 An exception might be if a specific error in one study or the other is found, such that the results were not what was thought (analytic error) or the data was not what was thought (experimental error).
@@
 Heterogeneity and lack-of-generalizability reasons mostly suggest another failed replication, as the second replication is likely to be closer to the first replication than to the original in these random factors.
-CITE THAT PAPER about types of heterogeneity and which was they would fall
+CITE THAT PAPER about types of heterogeneity and which way they would fall
 
-P-hacking and luck reasons are likely to suggest another failed replication.
+If the original result was p-hacked or a luck false positive, then another replication is also likely to fail.
 
@@
 Changes between original and replication may or may not be fixable -- if the original materials are still unavailable, a second replication is no better off.
-If a second replication can get closer to the original, it might get more similar results.
+If a second replication can get closer to the original, either by using closer materials, or better adapting the study to a new environment, the rescue might succeed at better approximating the results of the original.
 
 Sensitivity to environment or not working well online are unlikely to be fixable if the replications remain constrained to using online methods.
+Similarly, if the result is specific to a special population, then a new replication is also likely to fail, unless it has gained access to this population.
 
-These are pragmatic judgments related to how a lab might treat a failed replication as a sign that they cannot do cumulative science on a particular paradigm.
+<!--These are pragmatic judgments related to how a lab might treat a failed replication as a sign that they cannot do cumulative science on a particular paradigm.
 In some cases, especially related to changes-in-population or changes-to-online, replications, and thus cumulative work on the paradigm, might be possible for other groups who have different resources.
 
-The question is, having a failed replication, and not knowing which reasons might have caused the different results -- should a scientist try again?
+The question is, having a failed replication, and not knowing which reasons might have caused the different results -- should a scientist try again? -->
+
+Overall, it seems that there are both potential causes of replication failure that may be resolvable even with a similar level of resources and potential causes that are not resolvable, either at all, or given resource constraints.
 
 ## Current study
+
 ```{r}
@@
 
-Here we report the results of `r num_proj` re-replication "rescue" projects which each re-replicated a study which had a failed or only partially-successful replication in @boyce2023.
+[Probably needs a better transition in] Here we report the results of `r num_proj` re-replication "rescue" projects which each re-replicated a study which had a failed or only partially-successful replication in @boyce2023.
 This is a non-random sample, and given the small number of projects, we provide descriptive statistics and discuss qualitatively some potential sources of differential re-replication outcomes.
@@
 
+(could discuss tarampi as an example where there were potential issues, we fixed them and it still didn't work?)
+
 ## Correlates of rescue success
@@
 library(kableExtra)
-knitr::kable(cors, digits = 3, align='rcc', format="latex", booktabs=T, linesep="", caption="TODO CAPTION")
+knitr::kable(cors, digits = 3, align='rcc', format="latex", booktabs=T, linesep="", caption="Correlations between an individual predictor and the subjective replication score of the rescue project.")
 
@@
 Given that a couple of the successful rescues seemed to succeed in part because of larger sample sizes, we also added predictors related to the first replication sample size and the relative sizes of the samples (post-hoc, not pre-registered).
-While not signficant, the strongest correlates of rescue success were open materials, a small sample size on the first replication, a small sample size on the first replication relative to the original sample size, and a large rescue sample size relative to the first replication.
+While not significant, the strongest correlates of rescue success were open materials, a small sample size on the first replication, a small sample size on the first replication relative to the original sample size, and a large rescue sample size relative to the first replication.
 
@@
   select(paper=name_pretty, replication_score_rescue, N_original, N_rep1, N_rescue,
-         "Replication \\\\  closeness"=closeness_rep1, closeness_rescue) |> arrange(replication_score_rescue|> desc()) |> knitr::kable(align="lllll", format="latex", booktabs=T, linesep="", caption="TODOCAPTION", col.names=c("", "", "Original", "Replication", "Rescue", "Replication", "Rescue")) |> add_header_above(c("Paper"=1, "Score"=1, "N"=3, "closeness"=2))
+         "Replication \\\\  closeness"=closeness_rep1, closeness_rescue) |> arrange(replication_score_rescue|> desc()) |> knitr::kable(align="lllll", format="latex", booktabs=T, linesep="", caption="Comparison of sample size for original, replication, and rescue samples and measures of closeness for replication and rescue samples.", col.names=c("", "", "Original", "Replication", "Rescue", "Replication", "Rescue")) |> add_header_above(c("Paper"=1, "Score"=1, "N"=3, "closeness"=2))
 
@@
 
+```{r, include=F, fig.cap="Standardized effect sizes of original studies, first replications, rescues, and additional replications if available.
+Due to the large effect size of a couple studies, large effect studies are shown in a separate panel.
+"}
+
+#test on just one
+colors <- c("original"="black", "rep1"="#377EB8", "rescue"="#E41A1C", "additional"="#984EA3")
+shape <- c("original"=21,"rep1"=22,"rescue"=23,"additional"=24)
+
+smd_scale <- ggplot(for_plotting_d,aes(x=reorder(name_pretty, point, FUN=max),y=point,ymin=low,ymax=high,shape=type, color=type, fill=type, group=desc(type)))+
+  geom_errorbar(size=.5,width=0, position=position_dodge(width=.5))+
+  geom_point(position=position_dodge(width=.5))+
+ coord_flip()+
+  scale_size_area()+
+  geom_hline(yintercept=0,color="black")+
+    scale_color_manual(values=colors, aesthetics=c("color", "fill"))+
+  scale_shape_manual(values=shape)+
+  theme(legend.position = "bottom", 
+        panel.grid.major.x = element_blank(), 
+        panel.grid.minor.x=element_blank()
+        )+
+  labs(y="Standarized mean difference", x="")
+
+smd_scale
+
+```
+
 ## Effect sizes
@@
 We first compare the original and replications effect sizes on the key effect of interest.
-Where possible, we report this comparison in standardized mean difference (SMD) units, although the reporting of a few studies makes comparison only possible in the original units.
+We report this comparison in standardized mean difference (SMD) units.
 One potential issue with comparisons using SMD is that noisier measures will have smaller standardized effect sizes even if the effect on the original scale is the same.
@@
   left_join(orig_v_not_rescue |> select(target_lastauthor_year, orig_v_not_rescue=d_p_orig)) |> 
-  left_join(rescue_v_reps |> select(target_lastauthor_year, rescue_v_reps=d_p_orig)) |> 
-  rename(paper=target_lastauthor_year)
+  left_join(rescue_v_reps |> select(target_lastauthor_year, rescue_v_reps=d_p_orig))
 
@@
 ```
+
+```{r}
+names <- parsed_d |> select(target_lastauthor_year, name_pretty) |> unique()
+
+all |> ungroup() |>  left_join(names) |> select(Paper=name_pretty, `All reps`=orig_v_other, "Rescue" = orig_v_rescue, "Non-rescue"=orig_v_not_rescue, "Other reps"=rescue_v_reps) |> knitr::kable(format="latex", booktabs=T, linesep="", caption="P-original values between different sets of experiments.
+The primary analysis is between the original result and the meta-analytic aggregation of all replications.
+All p-originals assume an imputed heterogeneity value of tau=.21.", digits=3) |>
+  add_header_above(c(" "=1, "Original and"=3, "Rescue and"=1)) |> add_header_above(c(" "=1, "P-original comparing between"=4))
+
+```
+
 ## Consistency of effects 
@@
 
-We note that CITE!
-statistical consistency does not always align with our intuitions of replication or with whether an effect provides support for the hypothesis.
+We note that statistical consistency does not always align with our intuitions of replication or with whether an effect provides support for the hypothesis [@patil2016].
 A replication may be statistically consistent with the original effect but not provide any evidence for the claimed result.
@@
 
+P-original values are shown in TABLE TODO.
 The median value of p_original was `r main_summ$median |> round(2)` [IQR: `r main_summ$low |> round(2)` - `r main_summ$high |> round(2)`].
@@
 
+Visualizations of the statistical consistency between the original and each replication are shown in TODO FIGURE.
+The range around the open circle is the 95% predictive interval, representing the interval where, assuming that both are drawn from the same distribution, the replication will fall 95% of the time, given the precision (standard deviation) of the replication [@patil2016].
+We again impute a heterogeneity value of $\tau=.21$ SMD for the construction of the prediction intervals.
+
 <!--* We will use p-original to evaluate how consistent the original effect size is with the totality of replications.
@@
 -->
-
-We will visualize the consistency between original, 1st replication, rescue, and any other replications by plotting effect size and prediction interval for each. TODO how to actually do this!
+Overall, a number of these rescues and replications are not statistically consistent with the original effects allowing for this level of heterogeneity.
 
@@
 
-```{r, fig.height=6, fig.width=6}
+```{r, fig.caption="Plot of the prediction intervals of the original studies compared to replication results.
+The open circles are SMD effect sizes from the original studies, error bars are the prediction intervals, and filled shapes denote replication effect sizes.
+Prediction intervals in green contain the replication effect, those in grey do not.
+The largest effect sizes are separated in a separate panel to allow better visualization.
+"}
 colors <- c("original"="black", "rep1"="#377EB8", "rescue"="#E41A1C", "additional"="#984EA3")
@@
 # Discussion
-We don't have qualitative or quantitive explanations for why some replicated and some didn't.
-We can't predict what replication failures are likely to resolve given another try (or a more thoughtful try), beyond that suggestion that glaring problems and low samples may sometimes be resolvable.
+We presented the results of `r num_proj` new replications that attempted to "rescue" previous failed replications reported in @boyce2023 by identifying possible causes of non-replication and ameliorating them.
+`r nrow(success)` of these replications (`r round(nrow(success)/num_proj*100)`%) mostly or fully replicated.
 
-So, if you have a replication that failed, in a topic you're interested in pursuing cumulative science on, should you drop it, or try again?
-Our sample says that the odds of a re-replication working are low, so especially if there isn't a super clear failure mode to point to, another try probably won't fix it.
+We don't have qualitative or quantitative explanations for why some replicated and some didn't.
+In a couple cases, increasing sample size and fixing internal validity issues in the replication seems to have led to a successful rescue (although we can't establish causality even in these cases).
+However, there were other studies that had small replication samples, or implementational deviations in the replication, and rescues were still unsuccessful.
+We can't predict what replication failures are likely to resolve given another try (or a more thoughtful try), beyond that suggestion that glaring problems and low samples may sometimes (but not always) be resolvable.
 
-Something about how even the "successes" have diminished effect sizes 
+Another pattern we observed was that the effect sizes of even the successful replications tended to be substantially smaller than the original effect.
+
+[SAY something about statistical consistency]
+
 ## Limitations
-it's a small sample size and non-random 
-Constraints on budget, timeline, and primarily online studies obviously constrain how closely and well some studies could be replicated.
-However, these are representative of the sort of limitations on early-career researchers.
+The reported rescue projects are a small sample of replications, and the effects explored are non-random, as they have been doubly selected by student interest.
+The authors of the rescue projects put substantial effort into trying to set up rescues that had a good chance of success, but projects were constrained by budget limitations, a short timeline, and primarily running online studies.
+These limitations are representative of the sort of resource limitations often faced by early-career researchers.
+That said, it is possible that different results might be obtained in better-resourced settings.
+
+We opened this paper with a question about what an early-career researcher should do given a failed replication.
+Should one try again or move on?
+From our sample of testing the "try again" approach, it seems that the odds of a re-replication working are low, so especially if there isn't a super clear failure mode to point to, another try probably won't fix it.
+
 # Acknowledgements {-}

### 2024-02-27 code/hopkins_es.Rmd
calculate raw mean sd for hopkins and reps

---
title: "Hopkins M & SD"
output: html_notebook
---

```{r}
library(tidyverse)
library(here)
```
Key effect is that explantion level predicts rating (this is in an lm, but we're doing it outside for SMD here)

# Original

```{r}
dat <- read_csv(here("hopkins_raw.csv")) |>  # this has 147 unique IDs so seems likely to be the mturk sample post attention check?
  select(ID, rating, condition) |> 
  group_by(ID, condition) |> 
  summarize(rating=mean(rating)) |> 
  group_by(condition) |> 
  summarize(m=mean(rating), s=sd(rating))

  dat
```
# First rep
```{r}
## FROM https://github.com/psych251/hopkins2016/blob/master/writeup/hopkins2016_writeup.Rmd
raw_data <- read_csv("https://raw.githubusercontent.com/psych251/hopkins2016/master/writeup/data/hopkins2016_replication_data.csv")

#delete junk rows
raw_data <- raw_data[-c(1),]
raw_data <- raw_data[-c(1),]

#delete junk columns
raw_data <- raw_data %>%
  select(-(StartDate:Consent))
#add participant numbers
data_num <- raw_data %>%
  mutate(ID = 1:nrow(raw_data))

data_num <- data_num %>%
  select(-('Year':'Feedback'))
data_num <- data_num %>%
  select(Att_1, everything())

#convert to long format
data_long <- data_num %>%
  pivot_longer(cols = 'P1-HG_1':'S4-RB_1', names_to = "full_item", values_to = "rating", values_drop_na=TRUE)

#specify item attributes
data_long <- data_long %>%
  mutate(science = substr(full_item, start=1, stop=1))

data_long <- data_long %>%
  mutate(item = substr(full_item, start=1, stop=2))

data_long <- data_long %>%
  mutate(quality = substr(full_item, start=5, stop=5))

data_long <- data_long %>%
  select(-full_item)

data_long <- data_long %>%
  filter(rating!="")

#recode item names
data_long$quality <- ifelse(data_long$quality=="G", "good", "bad")

data_long$science <- ifelse(data_long$science=="P", "physics", data_long$science)
data_long$science <- ifelse(data_long$science=="C", "chemistry", data_long$science)
data_long$science <- ifelse(data_long$science=="B", "biology", data_long$science)
data_long$science <- ifelse(data_long$science=="N", "neuroscience", data_long$science)
data_long$science <- ifelse(data_long$science=="Y", "psychology", data_long$science)
data_long$science <- ifelse(data_long$science=="S", "social", data_long$science)

#convert columns to intended data types for analysis
data_long$rating <- as.integer(as.character(data_long$rating))

data_long$science <- factor(data_long$science, 
                  levels = c("physics", "chemistry", "biology", "neuroscience", "psychology", "social"),
                  labels = c("physics", "chemistry", "biology", "neuroscience", "psychology", "social"))
data_long$quality <- factor(data_long$quality, 
                  levels = c("good", "bad"),
                  labels = c("good", "bad"))
data_long$condition <- factor(data_long$Condition, 
                  levels = c("H", "R"),
                  labels = c("Horizontal", "Reductive"))

#exclude participants who failed attention check 1
data_excluded_both <- data_long %>%
  filter(Slider1_1==0)

#exclude participants who failed attention check 2
data_excluded_both <- data_excluded_both %>%
  filter(Att_1==3)
```
```{r}
data_excluded_both |>  select(ID, rating, condition) |> 
  group_by(ID, condition) |> 
  summarize(rating=mean(rating)) |> 
  group_by(condition) |> 
  summarize(m=mean(rating), s=sd(rating))
```
# Rescue

```{r}
raw_data <- read_csv("https://raw.githubusercontent.com/psych251/hopkins2016_rescue/main/data/replicationfull.csv")
## FROM https://github.com/psych251/hopkins2016/blob/master/writeup/hopkins2016_writeup.Rmd

#delete junk rows
raw_data <- raw_data[-c(1),]
raw_data <- raw_data[-c(1),]

#add participant numbers
data_num <- raw_data %>%
  mutate(ID = 1:nrow(raw_data))

data_num <- data_num %>%
  select(Att_1, everything())

#convert to long format
data_long <- data_num %>%
  pivot_longer(cols = 'P1-HG_1':'S4-RB_1', names_to = "full_item", values_to = "rating", values_drop_na=TRUE)

#specify item attributes
data_long <- data_long %>%
  mutate(science = substr(full_item, start=1, stop=1))

data_long <- data_long %>%
  mutate(item = substr(full_item, start=1, stop=2))

data_long <- data_long %>%
  mutate(quality = substr(full_item, start=5, stop=5))

data_long <- data_long %>%
  select(-full_item)

data_long <- data_long %>%
  filter(rating!="")

#recode item names
data_long$quality <- ifelse(data_long$quality=="G", "good", "bad")

data_long$science <- ifelse(data_long$science=="P", "physics", data_long$science)
data_long$science <- ifelse(data_long$science=="C", "chemistry", data_long$science)
data_long$science <- ifelse(data_long$science=="B", "biology", data_long$science)
data_long$science <- ifelse(data_long$science=="N", "neuroscience", data_long$science)
data_long$science <- ifelse(data_long$science=="Y", "psychology", data_long$science)
data_long$science <- ifelse(data_long$science=="S", "social", data_long$science)

#convert columns to intended data types for analysis
data_long$rating <- as.integer(as.character(data_long$rating))

data_long$science <- factor(data_long$science, 
                  levels = c("physics", "chemistry", "biology", "neuroscience", "psychology", "social"),
                  labels = c("physics", "chemistry", "biology", "neuroscience", "psychology", "social"))
data_long$quality <- factor(data_long$quality, 
                  levels = c("good", "bad"),
                  labels = c("good", "bad"))
data_long$condition <- factor(data_long$Condition, 
                  levels = c("H", "R"),
                  labels = c("Horizontal", "Reductive"))

#exclude participants who failed attention check 1
data_excluded_both <- data_long %>%
  filter(Slider1_1==0)

#exclude participants who failed attention check 2
data_excluded_both <- data_excluded_both %>%
  filter(Att_1==3)
```

```{r}
data_excluded_both |>  select(ID, rating, condition) |> 
  group_by(ID, condition) |> 
  summarize(rating=mean(rating)) |> 
  group_by(condition) |> 
  summarize(m=mean(rating), s=sd(rating))
```

### 2024-02-28 code/schechtman_es.Rmd
work on original schechtman ES

---
title: "Hopkins M & SD"
output: html_notebook
---

```{r}
library(tidyverse)
library(here)
library(R.matlab)
```
Key effect is that explantion level predicts rating (this is in an lm, but we're doing it outside for SMD here)

# Original

```{r}

dematlabify <- function(stuff) {
  foo <- stuff|> 
    as_tibble() |> 
    slice(2:n()) |> 
    mutate(across(everything(), ~map_vec(., ~ifelse(is.null(.), NA, .[[1]]))))

  names <- stuff[1,]|> map_vec(~.[[1]])
  colnames(foo) <- names

  return(foo)
}

# paper reports 39, but partway through reports "loss aversion" with 14, so I think maybe 25 in main analysis? That matches how many we have in thing1 at least

thing1 <- readMat(here("DataTest1.mat"))

ids <- dematlabify(thing1$BasicInfo)

dat1 <- dematlabify(thing1$DataStage1) # acquisition?

dat2 <- dematlabify(thing1$DataStage2) # testing

thing2 <- readMat(here("DataTest2.mat"))

ids2 <- dematlabify(thing2$BasicInfo) # has 6 22 13 2 11

dat3 <- dematlabify(thing2$DataSheet)

thing3 <- readMat(here("DataTest1_cases 4 13 18 omitted.mat")) # has 1-22

ids3 <- dematlabify(thing3$BasicInfo)

dat4 <- dematlabify(thing3$DataStage1) #acquisition

dat5 <- dematlabify(thing3$DataStage2) # testing

# not sure why 4 13 and 18 got excluded, but that seems to be what's reported in paper
```

```{r}
df <- dat5 |> left_join(ids3 |> select(IDNUM, `Tone Assignment nu.`)) |> 
  mutate(goodtone=ifelse(`Tone Assignment nu.`==1, 300,700),
         badtone=ifelse(`Tone Assignment nu.`==1, 700, 300)) |> 
  mutate(closest_distance=ifelse(abs(`absolute freq`-goodtone) > abs(`absolute freq`-badtone),abs(`absolute freq`-badtone), abs(`absolute freq`-goodtone) )) |> 
  filter(closest_distance<101) |> 
  mutate(closest_sound=ifelse(abs(`absolute freq`-goodtone) > abs(`absolute freq`-badtone),badtone, goodtone ),
         abs_diff=abs(closest_sound-`absolute freq`),
         generalized=ifelse(`Users choice: 1=positive 2=negative 3=other`==`closest sound: 1=good, 2=bad, 3=neither was closer than 200 Hz`,1,0),
         close_tone = ifelse(`closest sound: 1=good, 2=bad, 3=neither was closer than 200 Hz`==1, "good", "bad")) |> 
  select(IDNUM, goodtone, badtone, closest_sound, close_tone, abs_diff, generalized)

df |> nrow() #1584

# so 22 people, 3 rounds, 16 / round = 8 neg and 8 pos, if we exclude 0s
# or +4 in each category if we include 0s

#for rep 1420ish/20 = 71 so that's the same 72 if we include 0s

# for rescue

```

```{r}

mod <- lm(generalized ~ abs_diff*close_tone, df)

summary(mod)
```

```{r}

# figure out rescue
full_data <- read_csv(here("subject_data_final_full_processed.csv"))

# get all control questions
control_data = full_data %>%
  filter(trial_type == 'audio-button-response')

# check which participants did not answer "I can hear this" to 2 or more questions (button_pressed = 0)
exclude = control_data %>%
  filter(button_pressed != 0) %>%
  mutate(run_id = as.integer(run_id))

run_id_counts <- exclude %>%
  count(run_id)

run_id_counts_fin <- run_id_counts %>%
  filter(n != 1)

exclusion_participants = unique(run_id_counts_fin$run_id)

res <- full_data|> filter(run_id!=26) |> 
  filter(stage=="generalization") #|>
  #select(negative_tone, positive_tone, valence_match, distance, tone, key_responses, stimulus, run_id) |> 
  #filter(!is.na(distance))

nrow(res) #1512
```

### 2024-02-28 manuscript/manuscript.Rmd
title ideas? abstract

@@
 ::: {.abstract data-latex="" lang=en}
+Title ideas:
 
-TODO abstract
-* cumulative science requires being able to replicate results
-* given one failed replication, is a second attempt at replication likely to succeed?
+Can failed replications be rescued? Evidence from N re-replication experiments suggests rarely.
+
+Try again? Attempts to rescue failed replications were generally unsuccessful
+
+A low rate of successfully replicating experiments with a prior unsuccessful replication
+
+Once is probably enough. Low replication rates when re-replicating N studies with failed replications.
+
+* may want to include "student" or "class"
+
+Abstract:
+
+In order to do cumulative science, results need to be replicable.
+However, an individual direct replication could get a different result than an original ("replication failure") for a number of reasons, which vary in whether they would apply to a potential second replication.
+Given one failed replication, how likely is a second attempt at replication to succeed?
+As a pragmatic matter, when a replication fails, scientists have to decide: do they make a second attempt at replication, or move on?
+
 We re-replicated 17 experiments that had previously had a failed student replication, reported in Boyce et al.
@@
 We discuss the relative effect sizes and levels of statistical consistency between original effect sizes and replication effect sizes.
+
 While a few studies with failed replications were rescued with larger sample sizes and experimental tweaks, our overall results indicate that most failed replications stayed failed.
 If the goal is to do cumulative science, one may wish to stop after one failed replication.
+
 TODO MAKE THIS ABSTRACT BETTER!
+
 :::
@@
 That is, if a study fails to replicate, what are the chances that an additional replication succeeds.
-After CITE OSF found an overall replication rate of WHATEVER, concerns were raised about some potential problems with some of the replications, that might have contributed to the replicaiton failures.
-TO address this ManyLABSWHATEVER NUMBER re-replicated N of these both independently and with ...
-
-TODO READ THAT MANY LABS PAPER AGAIN.
+After CITE OSF found an overall replication rate of WHATEVER, concerns were raised by @gilbert that method differences were the problem.
+In 11 of the OSF studies, there had been concerns about protocol fidelity raised by original authors prior to data-collection.
+10 out of these 11 failed to obtain significant results in the replication.
+In a follow-up, @ebersole2020 re-replicated 10 of these 11 in large samples, using both the RP:P protocol and a new protocol revised under advise of the original authors or other experts.
+None of the RP:P protocols found significant results, 2 of the 10 revised did (but not the 1 that was significant in the original RP:P sample).
+The replication effect size was much smaller CITE NUMBER.
+We could frame @ebersole2020 as an attempt to rescue the original effects of the 9 studies with significant original effects and non-significant RP:P effects by a combination of high power and design tweaks.
 
@@
 
-A replication can have different results from the original study for a number of different potential reasons.
+A replication can have different results from the original study for a number of different potential reasons (see also @ebersole2020).
 The original result may have been a fluke, through chance or p-hacking.
@@
 The replication might have made changes (for convenience or a new sample) that turn out to matter.
+
+[ maybe try to make the point here that if there are changes in time/place/population, you want a good *translation* of the experiment not an identical copy]
 
@@
 The reported rescue projects are a small sample of replications, and the effects explored are non-random, as they have been doubly selected by student interest.
+However, this non-random may be a useful selection bias as it is correlated with  how students choose what to work on.
+
 The authors of the rescue projects put substantial effort into trying to set up rescues that had a good chance of success, but projects were constrained by budget limitations, a short timeline, and primarily running online studies.
@@
 That said, it is possible that different results might be obtained in better-resourced settings.
+Thus, we do not make statements about whether these studies are "true" or "false-positives", merely that they do not support cumulative research by early-career researchers under these conditions.
 
@@
 Should one try again or move on?
-From our sample of testing the "try again" approach, it seems that the odds of a re-replication working are low, so especially if there isn't a super clear failure mode to point to, another try probably won't fix it.
+From our sample of testing the "try again" approach, it seems that the odds of a re-replication working are low (consistent with @ebersole2020), so especially if there isn't a super clear failure mode to point to, another try probably won't fix it.
 

### 2024-03-06 manuscript/manuscript.Rmd
edit pass on results

@@
 ---
-title: "TODO (re-replication) (student) (cumulative science) (try again) (replication failure) "
+title: "Estimating the likelihood of student replication success after an initial failure to replicate"
 author:
@@
 ::: {.abstract data-latex="" lang=en}
-Title ideas:
+<!-- In order to do cumulative science, results need to be replicable.
+However, an individual direct replication could get a different result than an original ("replication failure") for a number of reasons, which vary in whether they would apply to a potential second replication.
+Given one failed replication, how likely is a second attempt at replication to succeed?-->
+
+As a pragmatic matter, when a replication fails, scientists have to decide: do they make a second attempt at replication, or move on?
+
+We re-replicated 17 experiments that had previously had a failed student replication, reported in Boyce et al.
+(2023).
+In 5/17 of these rescue projects (29%), the results mostly or fully replicated.
+We discuss the relative effect sizes and levels of statistical consistency between original effect sizes and replication effect sizes.
+
+While a few studies with failed replications were rescued with larger sample sizes and experimental tweaks, our overall results indicate that most failed replications stayed failed.
+If the goal is to do cumulative science, one may wish to stop after one failed replication.
+
+:::
+
+<!-- Other Title ideas:
 
@@
 
-Abstract:
+Estimating the replicability of experiments with a prior unsuccessful replication
 
-In order to do cumulative science, results need to be replicable.
-However, an individual direct replication could get a different result than an original ("replication failure") for a number of reasons, which vary in whether they would apply to a potential second replication.
-Given one failed replication, how likely is a second attempt at replication to succeed?
-As a pragmatic matter, when a replication fails, scientists have to decide: do they make a second attempt at replication, or move on?
-
-We re-replicated 17 experiments that had previously had a failed student replication, reported in Boyce et al.
-(2023).
-In N/17 of these rescue projects (TODO %), the results mostly or fully replicated.
-We discuss the relative effect sizes and levels of statistical consistency between original effect sizes and replication effect sizes.
-
-While a few studies with failed replications were rescued with larger sample sizes and experimental tweaks, our overall results indicate that most failed replications stayed failed.
-If the goal is to do cumulative science, one may wish to stop after one failed replication.
-
-TODO MAKE THIS ABSTRACT BETTER!
-
-:::
-
+Estimating the likelihood of [student] replication success after an initial failure to replicate
+--> 
 # Introduction
 
+imagine a scenario when this happens (motivating example).
 Imagine the scenario where you are a new graduate student, and you run a replication of a study in the literature that you are interested in building upon in your research.
 The replication fails.
-Should you try again, running another replication, perhaps with a larger sample or other tweaks to possibly fix the replication?
+TODO elaborate -- some hints of the effect yo hoped for or maybe the effect is close to null.
+(or maybe the pattern is off even if one part is suggestive)  Should you try again, running another replication, perhaps with a larger sample or other tweaks to possibly fix the replication?
 Or should you give up on replicating that specific study, and find a different study to replicate and build upon?
 
-There has been much discussion in the literature about how we should interpret replication results in terms of the existence of a true effect or effect size. TODO CITATIONS
-
-<!--Well, it depends on what you're trying to measure.
-From the perspective of learning from the field as a whole things are complicated and may depend also on a priori information from other related studies, the beleivability of the results, the relative rigor and sample sizes of the original and replication (TODO perhaps cite the time invariant).
--->
+we focus on scientists’ decisions… (spelling out why they might be replicating and hence why they might want to re-replicate) 
+TODO maybe instead of starting with p(true), start with “We focus on scientists’ decisions about what studies to run and how to expend their limited resources in the face of an uncertain literature.” THEN you can come back to “this perspective differs from the standard approach to replication, which has been concerned with the proportion of true effects in the literature.
 We take a different angle on replications, and instead focus scientists decisions on what studies to run.
@@
 
-How definitive is a replication failure?
-That is, if a study fails to replicate, what are the chances that an additional replication succeeds.
-After CITE OSF found an overall replication rate of WHATEVER, concerns were raised by @gilbert that method differences were the problem.
-In 11 of the OSF studies, there had been concerns about protocol fidelity raised by original authors prior to data-collection.
-10 out of these 11 failed to obtain significant results in the replication.
-In a follow-up, @ebersole2020 re-replicated 10 of these 11 in large samples, using both the RP:P protocol and a new protocol revised under advise of the original authors or other experts.
-None of the RP:P protocols found significant results, 2 of the 10 revised did (but not the 1 that was significant in the original RP:P sample).
-The replication effect size was much smaller CITE NUMBER.
-We could frame @ebersole2020 as an attempt to rescue the original effects of the 9 studies with significant original effects and non-significant RP:P effects by a combination of high power and design tweaks.
+this situation comes up a lot because replication is an important issue. (review meta-science literature on replication - you have to do this)
 
-## Why replication failure? 
-The idea of replication failure implies a certain time direction: first a "successful" study and (later) a "failed" replication.
+replications can fail for many reasons (move up this material) The idea of replication failure implies a certain time direction: first a "successful" study and (later) a "failed" replication.
 (CITE TIME INVARIANCE) We can also consider this as two very-related studies that got different results, and thus the question is what difference between these two studies could account for the differing results.
@@
 
-## Re-replication
+but re-replication has not been studied as much (except MB5 - use this paragraph to describe) How definitive is a replication failure?
+That is, if a study fails to replicate, what are the chances that an additional replication succeeds.
+After CITE OSF found an overall replication rate of WHATEVER, concerns were raised by @gilbert that method differences were the problem.
+In 11 of the OSF studies, there had been concerns about protocol fidelity raised by original authors prior to data-collection.
+10 out of these 11 failed to obtain significant results in the replication.
+In a follow-up, @ebersole2020 re-replicated 10 of these 11 in large samples, using both the RP:P protocol and a new protocol revised under advise of the original authors or other experts.
+None of the RP:P protocols found significant results, 2 of the 10 revised did (but not the 1 that was significant in the original RP:P sample).
+The replication effect size was much smaller CITE NUMBER.
+We could frame @ebersole2020 as an attempt to rescue the original effects of the 9 studies with significant original effects and non-significant RP:P effects by a combination of high power and design tweaks.
+
+re-replication could be a strategy to implement best practices that have been hypothesized to be positive (might need a paragraph here on sample size for replications, can use the references in Experimentology sampling chapter, there is a box on this topic)
+
+<!--There has been much discussion in the literature about how we should interpret replication results in terms of the existence of a true effect or effect size. TODO CITATIONS-->
+
+<!--Well, it depends on what you're trying to measure.
+From the perspective of learning from the field as a whole things are complicated and may depend also on a priori information from other related studies, the beleivability of the results, the relative rigor and sample sizes of the original and replication (TODO perhaps cite the time invariant).
+-->
+
 What would these potential causes of replication failure suggest would happen in another replication?
@@
 
-## Current study
+the current study
 
@@
 
+do we have something to say about the range of interventions that went into replications? e.g., larger sample size, manipulation check, etc.
+
 With one exception, samples were collected on Prolific (the rescue of @yeshurun2003 ran in-person on the Stanford student subject pool).
@@
 (See table TODO for post-exclusion sample sizes of original, replication, and rescues).
-Across the `r num_proj-1` studies, we spent $`r pluck(cost,1,1) |> round()`, for an average of $`r (pluck(cost,1,1)/(num_proj-1)) |> round()` per project.
+TODO  should say something about average power or average sample size as a multiplier on original or something - basically, a summary stat beyond a pointer to the table.
+Across the `r num_proj-1` Prolific studies, we spent $`r pluck(cost,1,1) |> round()`, for an average of $`r (pluck(cost,1,1)/(num_proj-1)) |> round()` per project.
 
@@
 The overall analysis is at LINK, individual pre-registrations are linked from LINK.
+
+We note one deviation from our pre-registration here: we pre-registered visual comparisons between original, first replication, and rescue projects.
+Prediction intervals depend on both the original effect size and variance CITATION TODO, and also the variance of the comparison (replication) study.
+Thus we cannot show *the* prediction interval for the original study, but would have to show a prediction interval between each pair of studies, which we thought would not offer clarity.
 
@@
 Our primary question of interest is how many of these `r num_proj` rescue projects succeeded at replicating the results in the original study.
-When a replication fails to obtain the same results, one may have intuitions about what may have gone wrong -- these rescue projects test whether addressing these potential issues in fact works.
+When a replication fails to obtain the same results, one may have intuitions about what may have gone wrong -- these rescue projects test how often addressing these potential issues in fact works.
 
@@
 irr <- cor.test(d$TA_rep_score, d$MCF_rep_score, method="spearman")$estimate
+
+bootstrap <- subj$binary_success |> Hmisc::smean.cl.boot()
+```
+
+```{r}
+boyce2023_sample <- read_csv(here("data/boyce_2023_data.csv")) |> select(sub_rep)
+
+percent_rep <- boyce2023_sample |> mutate(is_rep=ifelse(sub_rep>.5,1,0)) |> summarize(m=mean(is_rep))
+
+overall <- (percent_rep[1])+(1-percent_rep[1])*nrow(success)/nrow(subj)
 ```
@@
 All rescue projects were rated holistically for how well they replicated the original results.
-We thought about this in terms of how confident one would be to build on this line of work given the replication results, rather than focusing on any singular numeric result or significance cut-off.
+We thought about replication in terms of how confident one would be to build on the line of work given the replication results, rather than focusing on any singular numeric result or significance cut-off.
 All projects were rated both by the instructor (MCF) and by one of the TAs (VB or BP); the interrater reliability was `r irr |> round(3)`.
+
 Across the `r nrow(subj)` replications,  `r nrow(success)` mostly or fully replicated the original results according to the subjective replication ratings.
 `r pluck(tallied,2,1)` had a rating of 0, `r pluck(tallied, 2,2)` got a rating of  .75, and `r pluck(tallied, 2,3)` got a rating of 1.
-Thus, a first pass answer to the question "how often can a failed replication be salvaged?" is `r round(nrow(success)/nrow(subj)*100)`% of the time.
-TODO DO WE WANT TO BOOTSTRAP A CI ON THIS?
+Thus, a first pass answer to the question "how often can a failed replication be salvaged?" is `r round(nrow(success)/nrow(subj)*100)`% (bootstrapped 95% CI: `r round(bootstrap[2]*100)`% - `r round(bootstrap[3]*100)`%) of the time.
+
+In the original replication sample from @boyce2023, `r boyce2023_sample |> filter(sub_rep>.5) |> nrow()` out of `r boyce2023_sample |> nrow()` replications  (`r round(percent_rep*100)`%) mostly or fully replicated (i.e.
+received a subjective replication score of .75 or 1).
+Note that @boyce2023 report the average replication score as a percent success (49%), but given that we considered studies with a subjective score of .5 as eligible to be rescued, we recomputed the success rate when scores of 0-.5 as failures and .75 and 1 as successes.
+If the re-replication rate in our sample is representative of the re-replication rate for the initially non-replication studies, then the combined chance of mostly or fully replicating in a first replication or a follow-up replication is `r round(overall*100)`%.
 
@@
 The rescue, powered using 2.5x the original sample (as recommended by @simonsohn2015a), recovered a clear effect (albeit a much smaller one).
-There are reasons to think that some effect sizes in the literature may be inflated CITATIONS, and separately potential reasons that slight changes to experiments, or switches to online, could result in noisier samples (and thus smaller effect sizes).
+There are reasons to think that some effect sizes in the literature may be inflated TODO CITATIONS, and separately potential reasons that slight changes to experiments, or switches to online, could result in noisier samples (and thus smaller effect sizes).
 Thus, replications with smaller samples than the original (even if powered to the original effect size), may not be that diagnostic, and could potentially benefit from a re-replication.
@@
 The lesson here may be that sleep research is difficult to conduct online.
+However, an online replication by @denis2022 with a much larger sample found qualitatively similar results to @payne2008, albeit with a much smaller effect size.
+TODO confirm once denis is reanalysed
 
@@
 
-<!-- TODO some table of correlations between measures of rescue success rate!!
-The predictors used in https://osf.io/preprints/psyarxiv/dpyn6/ for exploratory analyses (the ones that need to be calculated) -->
 ```{r}
@@
 
-We ran correlations between the set of predictor variables used in @boyce2023 and the subjective replication scores of the rescues (TABLE WHATEVER).
-As the number of rescues is small, and many of these predictors are correlated, these correlations should not be overinterpreted.
+We ran correlations between the set of predictor variables used in @boyce2023 and the subjective replication scores of the rescues.
+We also added some (non-preregistered) predictors related to the sample size of the first replication, after seeing the successful re-replications of @ngo2019 and @krauss2003.
 
-Given that a couple of the successful rescues seemed to succeed in part because of larger sample sizes, we also added predictors related to the first replication sample size and the relative sizes of the samples (post-hoc, not pre-registered).
-While not significant, the strongest correlates of rescue success were open materials, a small sample size on the first replication, a small sample size on the first replication relative to the original sample size, and a large rescue sample size relative to the first replication.
+All of the correlations are presented in Figure TODO.
+As the number of rescues is small, and many of these predictors are correlated, we caution against over-interpretation.
+The strongest correlates of rescue success were open materials, a small sample size on the first replication, a small sample size on the first replication relative to the original sample size, and a large rescue sample size relative to the first replication.
+None of these effects meet the conventional significance threshold.
 
 Small replication samples relative to original and rescue could be due both to a) aiming for a small replication sample due to aiming for power for a reported large effect size or b) difficulties with recruitment or high exclusion rates leading to a smaller than intended sample.
+Since relative sizes of the studies may play a role in replication success and how probitive replications are, we show the sample sizes in TABLE TODO.
 
-Two measures associated with how satisfying a replication attempt was are its sample size (relative to the original) and how close the replication was to the original.
-We show these measures (using the classification scheme of @lebel for closeness) in TABLE TODO.
+An additional factor that influences the interpretation of a replication is how close the replication's methods were to the original.
+In the rescue projects, we aimed to have methods be as close as was feasible or appropriate.
+(As discussed above, changes in time, population, or setting may necessitate adaptation of a study to maximize fidelity.) However, rescue projects varied in how close the re-replications actually were, often due to limitations in the availability of original stimuli and original instructions, in addition to the use of primarily online subject pools.
+TABLE TODO shows the closeness of each re-replication according to the classification scheme from @lebel.
 
@@
 
-Aside from the suggestion that fixing sample size issues may have helped, it's unclear why some projects replicated this time and most did not.
+Overall, we do not have a clear picture of why certain studies replicated in the rescue sample and others did not, aside from a couple cases where fixing sample size issues may have helped.
 
@@
 
-In addition to looking at replication success overall, we also statistically compared the rescue, original replication, and original study on a key effect (we follow @boyce2023 in the determination of a key effect).
-When we were aware of additional direct replications (either from other class projects, or external replications in the literature), we also include these.
+As a complement to the holistic, qualitative replication ratings used above, we also statistically compared the effect sizes of the rescue, original replication, and original study on one key measure per study.
+We followed @boyce2023 in the determination of a key measure for each study.
+When we were aware of additional direct replications (either from other class projects, or external replications in the literature), we also consider the effect sizes obtained in these additional replications.
 
-We first compare the original and replications effect sizes on the key effect of interest.
-We report this comparison in standardized mean difference (SMD) units.
+We standardized all effect sizes into standardized mean difference (SMD) units.
 One potential issue with comparisons using SMD is that noisier measures will have smaller standardized effect sizes even if the effect on the original scale is the same.
-The effect sizes are shown in FIGURE TODO.
-In general, the replication and rescue effect sizes were smaller than the original effect sizes, and in a couple cases the effects were in the opposite direction.
+In general, the replication and rescue effect sizes were smaller than the original effect sizes, and in a couple cases the effects were in the opposite direction (FIGURE TODO).
 
 ```{r}
-do_rma <- function(df) {
-  if(!any(is.na(df$es))){
-  r<- rma(yi=df$es, sei=df$es_se, slab=df$type)
-  return(tibble(rma_est=r$beta[,1],rma_se=r$se))
-  }
-  return(tibble(rma_est=NA, rma_se=NA))
-}
 
@@
 
-orig <- parsed_d |> filter(type=="original") |> select(target_lastauthor_year, d=calc_d_calc, d_se=calc_d_calc_se, es=calc_ES, es_se=calc_SE)
+orig <- parsed_d |> filter(type=="original") |> select(target_lastauthor_year, d=calc_d_calc, d_se=calc_d_calc_se)
 
-orig_v_others <- parsed_d |> select(target_lastauthor_year, type, d=calc_d_calc, d_se=calc_d_calc_se, es=calc_ES, es_se=calc_SE) |> 
+orig_v_others <- parsed_d |> select(target_lastauthor_year, type, d=calc_d_calc, d_se=calc_d_calc_se) |> 
   filter(type!="original") |> 
@@
   nest() |> 
-  mutate(rma_result=map(data, do_rma),
-         d_rma_result=map(data, do_d_rma)) |> 
-  unnest_wider(rma_result) |> 
+  mutate(d_rma_result=map(data, do_d_rma)) |> 
   unnest_wider(d_rma_result) |> 
@@
 orig_v_rescue <- parsed_d |>   filter(type=="rescue") |> 
-  select(target_lastauthor_year, type, res_d=calc_d_calc, res_d_se=calc_d_calc_se, res_es=calc_ES, res_es_se=calc_SE) |>
-
+  select(target_lastauthor_year, type, res_d=calc_d_calc, res_d_se=calc_d_calc_se) |> 
   left_join(orig) |> 
@@
 
-orig_v_not_rescue <- parsed_d |> select(target_lastauthor_year, type, d=calc_d_calc, d_se=calc_d_calc_se, es=calc_ES, es_se=calc_SE) |> 
+orig_v_not_rescue <- parsed_d |> select(target_lastauthor_year, type, d=calc_d_calc, d_se=calc_d_calc_se) |> 
   filter(type!="original", type!="rescue") |> 
-  filter(target_lastauthor_year!="krauss2003") |> # have to avoid the divide by 0 error
   group_by(target_lastauthor_year) |> 
   nest() |> 
-  mutate(rma_result=map(data, do_rma),
-         d_rma_result=map(data, do_d_rma)) |> 
-  unnest_wider(rma_result) |> 
+  mutate(d_rma_result=map(data, do_d_rma)) |> 
   unnest_wider(d_rma_result) |> 
@@
 
-rescue_only <- parsed_d |> filter(type=="rescue") |> select(target_lastauthor_year, d=calc_d_calc, d_se=calc_d_calc_se, es=calc_ES, es_se=calc_SE)
+rescue_only <- parsed_d |> filter(type=="rescue") |> select(target_lastauthor_year, d=calc_d_calc, d_se=calc_d_calc_se)
 
-rescue_v_reps <- parsed_d |> select(target_lastauthor_year, type, d=calc_d_calc, d_se=calc_d_calc_se, es=calc_ES, es_se=calc_SE) |> 
+rescue_v_reps <- parsed_d |> select(target_lastauthor_year, type, d=calc_d_calc, d_se=calc_d_calc_se) |> 
   filter(type!="original", type!="rescue") |> 
-  filter(target_lastauthor_year!="krauss2003") |> # have to avoid the divide by 0 error
   group_by(target_lastauthor_year) |> 
   nest() |> 
-  mutate(rma_result=map(data, do_rma),
-         d_rma_result=map(data, do_d_rma)) |> 
-  unnest_wider(rma_result) |> 
+  mutate(d_rma_result=map(data, do_d_rma)) |> 
   unnest_wider(d_rma_result) |> 
@@
 
-## Consistency of effects 
-We statistically compared the original effects with the replication effect sizes to determine their level of statistical consistency, that is whether these effects were likely to be drawn from the same distribution, given a certain level of heterogeneity.
+Our intuitions of replication and intuitions of whether an effect provides support for a hypothesis (including heuristic cutoffs like p<.05) don't always align with measures of statistical consistency [@patil2016].
+For instance, two studies may both find that condition 1 results in a significantly higher outcome measure than condition 2, but the effect magnitudes may be sufficiently different that they are statistically unlikely to have come from the same population.
+On the other side, one study may find a statistically significant, but imprecisely estimated effect in a small sample, and second study may find a near-zero (null) effect, but the effect estimates from the two studies may be statistically compatible, despite one supporting a hypothesized difference and the other not.
 
-We note that statistical consistency does not always align with our intuitions of replication or with whether an effect provides support for the hypothesis [@patil2016].
-A replication may be statistically consistent with the original effect but not provide any evidence for the claimed result.
+Here, we measure statistical consistency using $p$-original, the $p$-value on the null hypothesis that two effects come from the same distribution.
+As our primary comparison, we compare the effect size of the original study to the meta-analytic effect of the totality of the replications (first replication, rescue, and additional if found).
+Because we have few replication for any study, we impute the heterogeneity value of $\tau=.21$ SMD, which is the average level of heterogeneity found by @olsson2020 in prior multi-site replications in psychology.
 
-We use p-original to evaluate how consistent the original effect size is with the totality of replications (first replication, rescue, and additional if found).
-Because of the small number of replications, we impute the heterogeneity value of $\tau=.21$ SMD, which is the average level of heterogeneity found by @olsson2020 in prior multi-site replications in psychology.
-P-original measures the p-value on the null hypothesis that the original effect and the replications come from the same distribution.
+The median value of $p$-original between an original study and its replications was `r main_summ$median |> round(2)` [IQR: `r main_summ$low |> round(2)` - `r main_summ$high |> round(2)`].
+`r round(main_summ$less_than*100)`% of the $p$-original values were less than .05, indicating by conventional thresholds a rejection of the null hypothesis that the original and the replications came from the same distribution for the given imputed level of heterogeneity.
+Individual $p$-original values for each study are shown in TABLE TODO.
 
-P-original values are shown in TABLE TODO.
-The median value of p_original was `r main_summ$median |> round(2)` [IQR: `r main_summ$low |> round(2)` - `r main_summ$high |> round(2)`].
-`r round(main_summ$less_than*100)`% of the p_original values were less than .05, indicating by conventional thresholds a rejection of the null hypothesis that the original and the replications came from the same distribution for the given imputed level of heterogeneity.
+As secondary measures, we also calculated the $p$-original values for a) the original and the rescue, b) the original and non-rescue replications, and c) between the rescue and other replications. 
+For a) the rescue versus the original, median value of $p$-original was `r rescue_summ$median |> round(2)` [IQR: `r rescue_summ$low |> round(2)` - `r rescue_summ$high|> round(2)`], and  `r round(rescue_summ$less_than*100)`% of the $p$-original values were less than .05.
+For b) the non-rescue replications versus the original, median value of $p$-original was `r rep_summ$median |> round(2)` [IQR: `r rep_summ$low |> round(2)` - `r rep_summ$high |> round(2)`], and  `r round(rep_summ$less_than*100)`% of the $p$-original values were less than .05.
+For c) the rescue versus the other replications, median value of $p$-original was `r rescue_rep_summ$median |> round(2)` [IQR: `r rescue_rep_summ$low |> round(2)` - `r rescue_rep_summ$high |> round(2)`], and  `r round(rescue_rep_summ$less_than*100)`% of the $p$-original values were less than .05.
 
-As secondary measures, we also calculated the p-original values for a) the original and the rescue, b) the original and non-rescue replications, and c) between the rescue and other replications. 
-For a) the rescue versus the original, median value of p_original was `r rescue_summ$median |> round(2)` [IQR: `r rescue_summ$low |> round(2)` - `r rescue_summ$high|> round(2)`], and  `r round(rescue_summ$less_than*100)`% of the p_original values were less than .05.
-For b) the non-rescue replications versus the original, median value of p_original was `r rep_summ$median |> round(2)` [IQR: `r rep_summ$low |> round(2)` - `r rep_summ$high |> round(2)`], and  `r round(rep_summ$less_than*100)`% of the p_original values were less than .05.
-For c) the rescue versus the other replications, median value of p_original was `r rescue_rep_summ$median |> round(2)` [IQR: `r rescue_rep_summ$low |> round(2)` - `r rescue_rep_summ$high |> round(2)`], and  `r round(rescue_rep_summ$less_than*100)`% of the p_original values were less than .05.
-
-NOTE THERE ARE A LOT OF MISSING DATA HERE!!!
-
-Visualizations of the statistical consistency between the original and each replication are shown in TODO FIGURE.
+<!--Visualizations of the statistical consistency between the original and each replication are shown in TODO FIGURE.
 The range around the open circle is the 95% predictive interval, representing the interval where, assuming that both are drawn from the same distribution, the replication will fall 95% of the time, given the precision (standard deviation) of the replication [@patil2016].
-We again impute a heterogeneity value of $\tau=.21$ SMD for the construction of the prediction intervals.
+We again impute a heterogeneity value of $\tau=.21$ SMD for the construction of the prediction intervals.-->
 
@@
 -->
-Overall, a number of these rescues and replications are not statistically consistent with the original effects allowing for this level of heterogeneity.
+Overall, allowing for a heterogeneity level of $\tau$=.21 SMD, a number of rescues and replications are not statistically consistent with the original effects.
+The pattern of inconsistency does not align with which studies were rated as having replicated.
+In all cases, the point estimate of the re-replication is smaller than (or in the opposite direction) of the original effect on the key measure of interest.
 
@@
 
-```{r, fig.caption="Plot of the prediction intervals of the original studies compared to replication results.
+```{r, include=F,  fig.caption="Plot of the prediction intervals of the original studies compared to replication results.
 The open circles are SMD effect sizes from the original studies, error bars are the prediction intervals, and filled shapes denote replication effect sizes.

### 2024-03-06 manuscript/manuscript.Rmd
work on methods

@@
 
+```
+
+```{r}
+
+library(tidyverse)
+library(testthat)
+all_projects <- read_csv("https://raw.githubusercontent.com/vboyce/251-254-MA/main/data/raw_data.csv")
+
+filtered <- all_projects |>
+  mutate(sub_rep=ifelse(replicated_instructor_code==replicated_report_code, 
+                 replicated_report_code, 
+                 adjudicated_replication_code)) |> 
+  filter(sub_rep %in% c(0,.25, .5)) |> 
+  filter(include!="no") |> 
+  filter(target_N <=200) |> 
+  filter(academic_year %in% c("2015-2016", "2016-2017", "2017-2018", "2018-2019", 
+                              "2019-2020", "2020-2021","2021-2022", "2022-2023")) 
+# what we really want is whether there was a github, but that column is private and so not in the public raw data
+# but 2015 is the first year where we have github links
+
+#test_that("number of rows in filtered", {expect_equal(nrow(filtered),49)})
+
+#given this sample, we then sought original replicator permission, 
+#since it would involve sharing their repo and write-up with a new student
+#which wouldn't have been anticipated at original classtime
+
+#we heard back from 29 students of the 49 we attempted to contact 
+#(1 we couldn't contact due to email bouncing) 
+#2 responses were negative, rest were positive, for 27 options
+
+approved <- c("krauss2003","yeshurun2003", "daffner2000", "ngo2019",
+              "child2018", "schechtman2010", "payne2008", "paxton2012",
+              "hart2018", "lewis2015", "tarampi2016", "jara-ettinger2022",
+              "porter_2016_1", "hopkins2016", "birch2007_2", "gong2019",
+              "correll2007", "pilditch2019", "daw2011", "dehaene2009",
+              "sofer2015", "todd2016_1", "chou2016", "mani2013", 
+              "haimovitz2016_2", "haimovitz2016_1", "craig2014")
+options <- filtered |> filter(target_lastauthor_year %in% approved)
+
+#test_that("number of rows in options", {expect_equal(nrow(options),27)})
+
+# students were then given this list and the opportunity to choose what to do
+
+# projects that we believe are being rescued (as of Oct 23)
+
+chosen <- c("birch2007_2", "jara-ettinger2022", "porter_2016_1",
+            "hopkins2016", "yeshurun2003", "craig2014", "tarampi2016", 
+            "mani2013", "krauss2003", "schechtman2010", "child2018",
+            "haimovitz2016_1", "todd2016_1", "haimovitz2016_2", "payne2008", 
+            "paxton2012", "dehaene2009", "chou2016", "ngo2019", "gong2019")
+
+rescue_started <- options |> filter(target_lastauthor_year %in% chosen)
+
+#test_that("number of rows in final sample", {expect_equal(nrow(final_sample),21)})
+
+```
+
+```{r}
+d <- read_csv(here("data", "combined_data.csv")) |> 
+  select(target_lastauthor_year, type, on_turk, repeated_measure, N, raw_stat, 
+         same_direction, replication_score, closeness, subfield, target_year, stanford_internal, 
+         open_data, open_materials, within_between, single_vignette, cost, name_pretty)
+
+source(here("code","helper","parse_stats.R"))
+
+parsed_d <- d |> 
+  mutate(raw_stat=gsub(" ","",raw_stat),
+         calc=pmap(list(raw_stat, within_between,N), do_parsing)) |> 
+  unnest(cols=c(calc), names_sep="_") |> 
+    mutate(
+    calc_d_calc=case_when(
+      type=="original" ~ abs(calc_d_calc),
+      same_direction=="yes" ~ abs(calc_d_calc),
+      same_direction=="no" ~ -abs(calc_d_calc),
+      T ~ as.numeric(NA)
+      ),
+    calc_ES=case_when(
+      type=="original" ~ abs(calc_ES),
+      same_direction=="yes" ~ abs(calc_ES),
+      same_direction=="no" ~ -abs(calc_ES),
+      T ~ as.numeric(NA)
+      ),
+    type=factor(type, levels=c("original", "rep1", "rescue", "additional"))
+    ) |> 
+  rowwise()
+
+num_proj <- parsed_d |> filter(type=="rescue") |> nrow()
+
+cost <- parsed_d |> filter(type=="rescue") |> ungroup() |>  summarize(total=sum(cost, na.rm=T))
 ```
@@
 
-```{r}
-
-library(tidyverse)
-library(testthat)
-all_projects <- read_csv("https://raw.githubusercontent.com/vboyce/251-254-MA/main/data/raw_data.csv")
-
-filtered <- all_projects |>
-  mutate(sub_rep=ifelse(replicated_instructor_code==replicated_report_code, 
-                 replicated_report_code, 
-                 adjudicated_replication_code)) |> 
-  filter(sub_rep %in% c(0,.25, .5)) |> 
-  filter(include!="no") |> 
-  filter(target_N <=200) |> 
-  filter(academic_year %in% c("2015-2016", "2016-2017", "2017-2018", "2018-2019", 
-                              "2019-2020", "2020-2021","2021-2022", "2022-2023")) 
-# what we really want is whether there was a github, but that column is private and so not in the public raw data
-# but 2015 is the first year where we have github links
-
-#test_that("number of rows in filtered", {expect_equal(nrow(filtered),49)})
-
-#given this sample, we then sought original replicator permission, 
-#since it would involve sharing their repo and write-up with a new student
-#which wouldn't have been anticipated at original classtime
-
-#we heard back from 29 students of the 49 we attempted to contact 
-#(1 we couldn't contact due to email bouncing) 
-#2 responses were negative, rest were positive, for 27 options
-
-approved <- c("krauss2003","yeshurun2003", "daffner2000", "ngo2019",
-              "child2018", "schechtman2010", "payne2008", "paxton2012",
-              "hart2018", "lewis2015", "tarampi2016", "jara-ettinger2022",
-              "porter_2016_1", "hopkins2016", "birch2007_2", "gong2019",
-              "correll2007", "pilditch2019", "daw2011", "dehaene2009",
-              "sofer2015", "todd2016_1", "chou2016", "mani2013", 
-              "haimovitz2016_2", "haimovitz2016_1", "craig2014")
-options <- filtered |> filter(target_lastauthor_year %in% approved)
-
-#test_that("number of rows in options", {expect_equal(nrow(options),27)})
-
-# students were then given this list and the opportunity to choose what to do
-
-# projects that we believe are being rescued (as of Oct 23)
-
-chosen <- c("birch2007_2", "jara-ettinger2022", "porter_2016_1",
-            "hopkins2016", "yeshurun2003", "craig2014", "tarampi2016", 
-            "mani2013", "krauss2003", "schechtman2010", "child2018",
-            "haimovitz2016_1", "todd2016_1", "haimovitz2016_2", "payne2008", 
-            "paxton2012", "dehaene2009", "chou2016", "ngo2019", "gong2019")
-
-rescue_started <- options |> filter(target_lastauthor_year %in% chosen)
-
-#test_that("number of rows in final sample", {expect_equal(nrow(final_sample),21)})
-
-```
-
-```{r}
-d <- read_csv(here("data", "combined_data.csv")) |> 
-  select(target_lastauthor_year, type, on_turk, repeated_measure, N, raw_stat, 
-         same_direction, replication_score, closeness, subfield, target_year, stanford_internal, 
-         open_data, open_materials, within_between, single_vignette, cost, name_pretty)
-
-source(here("code","helper","parse_stats.R"))
-
-parsed_d <- d |> 
-  mutate(raw_stat=gsub(" ","",raw_stat),
-         calc=pmap(list(raw_stat, within_between,N), do_parsing)) |> 
-  unnest(cols=c(calc), names_sep="_") |> 
-    mutate(
-    calc_d_calc=case_when(
-      type=="original" ~ abs(calc_d_calc),
-      same_direction=="yes" ~ abs(calc_d_calc),
-      same_direction=="no" ~ -abs(calc_d_calc),
-      T ~ as.numeric(NA)
-      ),
-    calc_ES=case_when(
-      type=="original" ~ abs(calc_ES),
-      same_direction=="yes" ~ abs(calc_ES),
-      same_direction=="no" ~ -abs(calc_ES),
-      T ~ as.numeric(NA)
-      ),
-    type=factor(type, levels=c("original", "rep1", "rescue", "additional"))
-    ) |> 
-  rowwise()
-
-num_proj <- parsed_d |> filter(type=="rescue") |> nrow()
-
-cost <- parsed_d |> filter(type=="rescue") |> ungroup() |>  summarize(total=sum(cost, na.rm=T))
-```
-
 [Probably needs a better transition in] Here we report the results of `r num_proj` re-replication "rescue" projects which each re-replicated a study which had a failed or only partially-successful replication in @boyce2023.
@@
 
+```{r}
+rel_size <- parsed_d |> filter(type %in% c("original", "rescue")) |> select(target_lastauthor_year, type, N)  |> 
+  pivot_wider(names_from=type, values_from=N) |> mutate(multiplier=rescue/original)
+
+lowest <- quantile(rel_size$multiplier, 0)
+low <- quantile(rel_size$multiplier, .25)
+mid <- quantile(rel_size$multiplier, .5)
+m <- mean(rel_size$multiplier)
+high <- quantile(rel_size$multiplier, .75)
+highest <- quantile(rel_size$multiplier, 1)
+
+```
+
 ## Procedure 
@@
 Students were required to think of reasons the original replication might not have worked, and address them if they could.
-A list of possible reasons and solutions LINK was given to students.
+A list of possible reasons and solutions TODO LINK was given to students.
+In general, we encouraged students to add manipulation checks as appropriate, and better adapt materials to online studies.
+For instance, TODO rescue switched from using the CRT which is overused in online samples for the newer TODO.
+TODO rescue discovered that the replication had accidentally used the drawn version of the stimuli rather than the photographic stimuli used in the original and reverted to the photographic stimuli.
+TODO @tarampi original had participants indicate their answers (left or right) on a piece of paper in a timed navigation task, the replication had them indicate by clicking a drop down, and rescue went with press keyboard keys to indicate.
+TODO others to note?
 Once students experimental designs and analytic plans were approved by TAs (VB and BP), students pre-registered and ran their samples.
-
-do we have something to say about the range of interventions that went into replications? e.g., larger sample size, manipulation check, etc.
 
@@
 We tried to power studies adequately (with a target of 2.5x original following @simonsohn2015), but due to cost constraints, not all studies were powered at this level.
-(See table TODO for post-exclusion sample sizes of original, replication, and rescues).
-TODO  should say something about average power or average sample size as a multiplier on original or something - basically, a summary stat beyond a pointer to the table.
+The rescues had on average `r round(m,2)` times the original sample post-exclusion (median: `r round(mid,2)`, IQR: `r round(low,2)` - `r round(high,2)`, minimum: `r round(lowest, 2)`, maximum: `r round(highest,2)`, see TABLE TODO for all sample sizes).
 Across the `r num_proj-1` Prolific studies, we spent $`r pluck(cost,1,1) |> round()`, for an average of $`r (pluck(cost,1,1)/(num_proj-1)) |> round()` per project.
@@
 As a compliment to the overall subjective rating of success, we followed @boyce2023 in also doing a statistical comparison on one key measure of interest for each study.
+In order to statistically compare the key measures, we needed effect sizes reported in the same way within each original-replication cluster.
+When effects were not reported in consistent ways across original and replications, we recalculated effects from raw data when necessary to obtain comparable values.
 
 We also recorded the same set of potential correlates that were used in @boyce2023 for original, replication, and rescue (these were already rated for original and replication).
-These potential correlates included features of the original study including the subfield of the study (cognitive v social v other psychology), it's publication year,  experimental design features including whether it was a within- or between- subject design, whether each condition was instantiated with one vignette or multiple, and how many items each participant saw, and whether there were open materials and open data.
+These potential correlates included features of the original study including the subfield of the study (cognitive v social v other psychology), its publication year, experimental design features including whether it was a within- or between- subject design, whether each condition was instantiated with one vignette or multiple, and how many items each participant saw, and whether there were open materials and open data.
 
@@
 The lesson here may be that sleep research is difficult to conduct online.
-However, an online replication by @denis2022 with a much larger sample found qualitatively similar results to @payne2008, albeit with a much smaller effect size.
-TODO confirm once denis is reanalysed
+However, an online replication by @denis2022 reports qualitatively similar (but quantitatively smaller) results to @payne2008 on related but not identical measures.
 

### 2024-03-08 manuscript/manuscript.Rmd
welp, I wanted to put citations in the tables, but that only works in format markdown and the headers only work with format latex ugh
a rough editing pass over everything

@@
       - corresp
-  - name: TODO
+  - name: TODO x a lot
     affiliation: Stanford
@@
 bibliography: ["251rescue.bib"] # Replace with one or more of your own bibtex files. Better BibTeX for Zotero is your friend
-csl: apa6.csl # Use any CSL style. See https://www.zotero.org/styles for a good list. Ignored if citation_package: natbib
+csl: apa7.csl # Use any CSL style. See https://www.zotero.org/styles for a good list. Ignored if citation_package: natbib
 link-citations: TRUE
@@
 As a pragmatic matter, when a replication fails, scientists have to decide: do they make a second attempt at replication, or move on? 
-
-We re-replicated 17 experiments that had previously had a failed student replication, reported in Boyce et al.
+Given the relatively low rates of replication success reported in large scale replication projects, this choice point is one facing many scientists in psychology who attempt to replicate a study before building on it.
+Here, we report on 17 re-replications of experiments with failed replicated reported in  Boyce et al.
 (2023).
-In 5/17 of these rescue projects (29%), the results mostly or fully replicated.
-We discuss the relative effect sizes and levels of statistical consistency between original effect sizes and replication effect sizes.
-
+In 5/17 of these rescue projects (29%), the re-replication mostly or fully replicated the original results, albeit with smaller effect sizes.
 While a few studies with failed replications were rescued with larger sample sizes and experimental tweaks, our overall results indicate that most failed replications stayed failed.
@@
 Imagine the scenario where you are a new graduate student, and you run a replication of a study in the literature that you are interested in building upon in your research.
-The replication fails.
-TODO elaborate -- some hints of the effect yo hoped for or maybe the effect is close to null.
-(or maybe the pattern is off even if one part is suggestive)  Should you try again, running another replication, perhaps with a larger sample or other tweaks to possibly fix the replication?
-Or should you give up on replicating that specific study, and find a different study to replicate and build upon?
+The replication fails: perhaps the interaction you hoped for is directionally correct, but the point estimate is small and the confidence interval definitely overlaps 0, with a p-value of .3.
+Or perhaps the interaction is numerically in the wrong direction, and also the main effects look different.
+Or perhaps the main effect of interest is null, but you found a significant effect on the interaction that wasn't hypothesized.
+Whatever the details of the replication failure, you are left with a question: Should you *try again* and run a re-replication, or should you *give up* and pick a different study to replicate and build on?
 
-we focus on scientists’ decisions… (spelling out why they might be replicating and hence why they might want to re-replicate) 
-TODO maybe instead of starting with p(true), start with “We focus on scientists’ decisions about what studies to run and how to expend their limited resources in the face of an uncertain literature.” THEN you can come back to “this perspective differs from the standard approach to replication, which has been concerned with the proportion of true effects in the literature.
-We take a different angle on replications, and instead focus scientists decisions on what studies to run.
-Individual studies (and replications) are rarely definitive when it comes to scientific evidence, but they often influence what studies a scientist conducts.
-If a study works, scientists are likely to continue to purse that result, but if a study doesn't work, scientists have to choose whether to try again, or switch to a different study.
+We focus on scientists’ decisions about what studies to run and how to expend their limited resources in the face of an uncertain literature.
+Scientists may replicate studies for a variety of reasons, including calibrating their equipment, confirming a result before building on it, and engaging in meta-scientific practices [other reasons to highlight?
+is there any citation for this?].
+We focus on this middle motivation, where a scientist wants to build on a result, and thus wants it to succeed, but does not have strong reasons to believe or disbelieve the finding: it isn't a robust, well-tested effect, nor is it something they have particular suspicions about.
+However, in an uncertain literature, we might not want to commit resources to building on an effect without first checking that we, with our resources and participant sample, can get the core effect we wish to build on.
+Thus, scientists may want to re-replicate failed replications if the re-replication is likely to work and is indicative that future experiments in this tradition are likely to be informative.
 
-this situation comes up a lot because replication is an important issue. (review meta-science literature on replication - you have to do this)
+This scientist-decision focused angle is different from the standard approach to replication which has take then the meta-scientific approach which has been primarily concerned with estimating the proportion of true effects in the literature.
+Large-scale replication studies indicate that the literature is unreliable.
 
-replications can fail for many reasons (move up this material) The idea of replication failure implies a certain time direction: first a "successful" study and (later) a "failed" replication.
-(CITE TIME INVARIANCE) We can also consider this as two very-related studies that got different results, and thus the question is what difference between these two studies could account for the differing results.
+In psychology, large scale replication projects have tended to find replicability rates around half.
+Across 100 studies with positive results, RP:P replicated 36 - 47% depending on the metric for replication success [@openscienceconsortium].
+With large multi-site samples, Many Labs 1 replicated 11/13  effects (84.6%), Many Labs 2 replicated 14/28 effects (50%), and Many Labs 3 replicated 3/10 effects (30%) [@klein2014; @klein2018; @ebersole2016].
+@camerer2018 included 21 behavioral social science studies and replicated 12-14 of them (57%-67%) depending on the metric used.
+@boyce2023 reports an average replication score of 49% for 176 replications primary in psychology.
+Psychology is not the only discipline where not everything replicates.
+Large scale replication projects in other disciplines have found 39/97 (40%) for positive effects in cancer biology [@errington2021], 11/18 (61%) in economics [@camerer2016], and 31/40 (78%) for experimental philosophy [@cova2021].
 
-[not sure if it would be better to structure this differently]
+TODO DISCUSSION OF THE LITERATURE
+What these replication rates say about the truth of the literature is beyond our scope, but these rates do indicate that scientists are far from guaranteed at being able to replicate effects from the literature in their own labs.
+Thus, the question of what to do with a failed replication is a practical one that comes up frequently.
 
-A replication can have different results from the original study for a number of different potential reasons (see also @ebersole2020).
-The original result may have been a fluke, through chance or p-hacking.
-The original result might be of much less generalizability than is assumed, and very sensitive to the exact conditions and time it was run in ("hidden moderators").
-The original could have an inflated effect size, due to some combination of heterogeneity, p-hacking, luck, and publication bias.
+Replications can fail for many reasons.
+Replication failure implies a certain time direction: first a "successful" study, usually one that got a certain statistically significant result, and (later) a "failed" replication that did not get this statistically significant result.
+The replication failure framing implies a time direction (TODO THERE IS A CITATION FOR THIS IDEA RIGHT OF PRECEDENCE).
+Taking out the time component, we can instead analyse a replication failure as two very-related studies with differing results.
+Under this frame, the question becomes: what is different between these two studies that could account for the differing results?
 
-The replication could have been underpowered due to any of inflated original effect size, attrition in sample, or the original also being underpowered.
-A manipulation might have failed in the replication (this is a proximate cause that also raises the question of why the manipulation check failed).
-There might have been a difference in materials or instructions between the two, that turns out to matter (more likely if materials are not available).
-The experiment might not port well to online due to some details.
-A change in sample (ie.
-to online) may decrease data quality without sufficient attention checks.
-The replication might have made changes (for convenience or a new sample) that turn out to matter.
+[query: should I try to frame this as two that are symmetric , or should I stick to an original / rep framing? I'm torn]
 
-[ maybe try to make the point here that if there are changes in time/place/population, you want a good *translation* of the experiment not an identical copy]
+There are many potential reasons for differing results (see also @ebersole2020).
+One option is that one of the studies had a statistically unlikely result (either through chance or p-hacking).
+The result could be sensitive to some of the exact conditions and time when the two studies were run ("hidden moderators") and lack generalizability.
+Reported effect sizes might be biased estimates due to some combination of heterogeneity, p-hacking, luck, underpowering, and publication bias.
+One or both studies might be underpowered, potentially due to believing the effect was larger, or unexpected attrition in the sample.
 
-While one can theorize after the fact about potential causes, in most circumstances it is hard to diagnose for certain what made for the difference in the results.
+Studies might differ in how they instantiated the question of interest, and this might cause different results.
+For example if a manipulation check failed, that could be a proximate cause of difference, which also raises questions about why the manipulation check failed.
+Differences in materials or instructions might turn out to be crucial to the effect.
+A difference in experiment platforms (ex.
+online versus in-person) might mean that an implementation doesn't fit the platform, or the data quality controls and attention checks may not be appropriate to the sample population.
+Some trivial changes intended to adapt the experimental question to the setting might actually change the result.
+If there are differences in time, place, or subject population between the two studies, there may need to be differences in the materials, instructions, or procedure to provide a good *translation* -- too many changes could cause differing results, but so could not enough changes.
+
+While one can theorize after the fact about potential causes of replication failure, in most circumstances it is hard to diagnose for certain what made for the difference in the results.
 An exception might be if a specific error in one study or the other is found, such that the results were not what was thought (analytic error) or the data was not what was thought (experimental error).
+Re-replication could serve as a way of triangulating on reasons for replication failure, as well as another chance for a scientist to get a working protocol that picks up the effect of interest.
+However, re-replication has not been studied much, so it is uncertain how definitive a replication failure is.
+That is, conditioned on a failed replication, how likely is a re-replication to succeed?
+Re-replication was tested in a sample of 10 psychology studies in @ebersole2020.
+After @openscienceconsortium published their results with a replication rate of TODO, @gilbert2016  raised concerns that methodological differences were the problem.
+In 11 of the OSF studies, concerns about protocol fidelity had been raised by original authors prior to data-collection (and thus not contingent on results).
+Of these 11 with concerns, 10 failed to obtain significant results in the RP:P replication [@openscienceconsortium].
+In a follow-up, @ebersole2020 re-replicated 10 of these 11 in larger samples, using both the RP:P protocol and a new protocol revised under advice of the original authors or other experts, thus testing whether larger sample sizes and/or "better" methodologies would "rescue" the failed RP:P replications.
+The result: 0 of the RP:P protocols found significant results, 2 of the 10 revised protocols did (but not the 1 that had a significant result in the original RP:P sample).
+The replication effect size was much smaller CITE NUMBER [@ebersole2020].
+We could frame @ebersole2020 as an attempt to rescue the original effects of the 9 studies with significant original effects and non-significant RP:P effects by a combination of high power and design tweaks.
+This suggests a successful re-replication rate of 2/9 (22%) for studies with non-significant first replications, under fairly favorable, high resource circumstances.
 
-but re-replication has not been studied as much (except MB5 - use this paragraph to describe) How definitive is a replication failure?
-That is, if a study fails to replicate, what are the chances that an additional replication succeeds.
-After CITE OSF found an overall replication rate of WHATEVER, concerns were raised by @gilbert that method differences were the problem.
-In 11 of the OSF studies, there had been concerns about protocol fidelity raised by original authors prior to data-collection.
-10 out of these 11 failed to obtain significant results in the replication.
-In a follow-up, @ebersole2020 re-replicated 10 of these 11 in large samples, using both the RP:P protocol and a new protocol revised under advise of the original authors or other experts.
-None of the RP:P protocols found significant results, 2 of the 10 revised did (but not the 1 that was significant in the original RP:P sample).
-The replication effect size was much smaller CITE NUMBER.
-We could frame @ebersole2020 as an attempt to rescue the original effects of the 9 studies with significant original effects and non-significant RP:P effects by a combination of high power and design tweaks.
+Returning to the question of potential causes of non-replication, what do reasons for replication failure say about the success of another replication?
+For our purposes, we're considering another replication with roughly the same environment, knowledge, and resources of the first replication, but with the benefit of hindsight on the first replication, as this is the situation scientists considering doing a re-replicaton for cumulative science are in.
 
-re-replication could be a strategy to implement best practices that have been hypothesized to be positive (might need a paragraph here on sample size for replications, can use the references in Experimentology sampling chapter, there is a box on this topic)
-
-<!--There has been much discussion in the literature about how we should interpret replication results in terms of the existence of a true effect or effect size. TODO CITATIONS-->
-
-<!--Well, it depends on what you're trying to measure.
-From the perspective of learning from the field as a whole things are complicated and may depend also on a priori information from other related studies, the beleivability of the results, the relative rigor and sample sizes of the original and replication (TODO perhaps cite the time invariant).
--->
-
-What would these potential causes of replication failure suggest would happen in another replication?
-For our purposes, we're considering another replication with roughly the same environment, knowledge, and resources of the first replication, but with the benefit of hindsight on the first replication.
-
-Heterogeneity and lack-of-generalizability reasons mostly suggest another failed replication, as the second replication is likely to be closer to the first replication than to the original in these random factors.
-CITE THAT PAPER about types of heterogeneity and which way they would fall
-
-If the original result was p-hacked or a luck false positive, then another replication is also likely to fail.
-
-Manipulation check failure may not be fixable, but it might at least be diagnosable.
-
-Underpoweredness and inflated effect size may be recoverable depending on the extent -- if the effect size was inflated and the first replication powered for the effect, a better powered (but not huge) replication may be able to recover a smaller, but still convincing effect.
-
-Changes between original and replication may or may not be fixable -- if the original materials are still unavailable, a second replication is no better off.
-If a second replication can get closer to the original, either by using closer materials, or better adapting the study to a new environment, the rescue might succeed at better approximating the results of the original.
-
+Factors that suggest another failure include heterogeneity and lack-of-generalizability ("hidden moderator"), as the second replication is likely to be closer to the first replication than to the original in these random factors.
+TODO CITE THAT PAPER about types of heterogeneity and which way they would fall An original result due to p-hacking or a lucky false positive is unlikely to re-replicate.
 Sensitivity to environment or not working well online are unlikely to be fixable if the replications remain constrained to using online methods.
@@
 
-<!--These are pragmatic judgments related to how a lab might treat a failed replication as a sign that they cannot do cumulative science on a particular paradigm.
-In some cases, especially related to changes-in-population or changes-to-online, replications, and thus cumulative work on the paradigm, might be possible for other groups who have different resources.
+Factors that may be fixable include sample size issues with the replication, assuming the re-replication can recruit a larger sample or reduce attrition.
+It may be possible to fix underpoweredness and inflated effect size, at least to an extent.
+If the effect size was inflated and the first replication powered for the effect, a better powered (but not huge) replication may be able to recover a smaller, but still convincing effect.
+Failures due to differences between the materials may or may not be fixable.
+If the original materials are still unavailable, a second replication is no better off.
+If a second replication can get closer to the original, either by using closer materials, or better adapting the study to a new environment, the rescue might succeed at better approximating the results of the original.
+A failed manipulation check failure may not be fixable, but it might at least be diagnoseable.
 
-The question is, having a failed replication, and not knowing which reasons might have caused the different results -- should a scientist try again? -->
+Overall, there are some potential causes of replication failure that may be resolvable with a similar level of resources, and also some potential causes of replication failure that are not resolvable, either at all, or given resource constraints.
 
-Overall, it seems that there are both potential causes of replication failure that may be resolvable even with a similar level of resources and potential causes that are not resolvable, either at all, or given resource constraints.
+After a failed replication, we might speculate on what caused the replication result, and what that would mean for future work on the topic.
+As the @gilbert2016 and @ebersole2020 example showed, these speculations on causes and thus re-replication outcomes are not always correct.
 
-the current study
+While @ebersole2020 looked at re-replication success rate in a high resource setting with access to large, multi-site samples and expert input, most early career scientists do not have those kinds of resources to devote to re-replication attempts.
+On the other hand, early career researchers may also be prone to a different distribution of causes of initial replication failure.
 
-[Probably needs a better transition in] Here we report the results of `r num_proj` re-replication "rescue" projects which each re-replicated a study which had a failed or only partially-successful replication in @boyce2023.
+Here, we investigate re-replication in the context of graduate student replications.
+Students in a graduate methods class on experimental methods were learning about best practices for experimental research.
+One option for their class project was to "rescue" an experiment that a student in a prior year had previously failed to replicate (reported in @boyce2023).
+Thus, students were likely to be looking at both the original paper and the failed replication through the lens of best practices to see what they could fix.
+[TODO Mike mentioned something about a sampling side box on experimentology that VB is having trouble finding]
+
+In the present paper, we report the results of `r num_proj` re-replication "rescue" projects which each re-replicated a study which had a failed or only partially-successful replication in @boyce2023.
 This is a non-random sample, and given the small number of projects, we provide descriptive statistics and discuss qualitatively some potential sources of differential re-replication outcomes.
+[possibly drop last sentence?]
 
@@
 
-A spreadsheet of projects, individual project write-ups (both replications and rescues), links to individual project data and analyses for rescue projects, and the analytic code for this paper are all available at OSF LINK GOES HERE.
+A spreadsheet of projects, individual project write-ups (both replications and rescues), links to individual project data and analyses for rescue projects, and the analytic code for this paper are all available at TODO OSF LINK GOES HERE.
 
@@
 In general, we encouraged students to add manipulation checks as appropriate, and better adapt materials to online studies.
-For instance, TODO rescue switched from using the CRT which is overused in online samples for the newer TODO.
-TODO rescue discovered that the replication had accidentally used the drawn version of the stimuli rather than the photographic stimuli used in the original and reverted to the photographic stimuli.
-TODO @tarampi original had participants indicate their answers (left or right) on a piece of paper in a timed navigation task, the replication had them indicate by clicking a drop down, and rescue went with press keyboard keys to indicate.
+For instance, the rescue of @paxton2012 switched from using the CRT which is overused in online samples for the newer TODO.
+The rescue of @jara-ettinger2022 discovered that the replication had accidentally used the drawn version of the stimuli rather than the photographic stimuli used in the original and reverted to the photographic stimuli.
+@tarampi2016 original had participants indicate their answers (left or right) on a piece of paper in a timed navigation task, the replication had them indicate by clicking a drop down, and rescue went with press keyboard keys to indicate.
 TODO others to note?
@@
 We tried to power studies adequately (with a target of 2.5x original following @simonsohn2015), but due to cost constraints, not all studies were powered at this level.
-The rescues had on average `r round(m,2)` times the original sample post-exclusion (median: `r round(mid,2)`, IQR: `r round(low,2)` - `r round(high,2)`, minimum: `r round(lowest, 2)`, maximum: `r round(highest,2)`, see TABLE TODO for all sample sizes).
+The rescues had on average `r round(m,2)` times the original sample post-exclusion (median: `r round(mid,2)`, IQR: `r round(low,2)` - `r round(high,2)`, minimum: `r round(lowest, 2)`, maximum: `r round(highest,2)`, see Table \@ref(tab:tab-size) for all sample sizes).
 Across the `r num_proj-1` Prolific studies, we spent $`r pluck(cost,1,1) |> round()`, for an average of $`r (pluck(cost,1,1)/(num_proj-1)) |> round()` per project.
@@
 Here, the original study found a large effect, and so the first replication, powering for 80% power on the reported effect, recruited a small sample of 12 people, and then failed to find the effect.
-The rescue, powered using 2.5x the original sample (as recommended by @simonsohn2015a), recovered a clear effect (albeit a much smaller one).
+The rescue, powered using 2.5x the original sample (as recommended by @simonsohn2015), recovered a clear effect (albeit a much smaller one).
 There are reasons to think that some effect sizes in the literature may be inflated TODO CITATIONS, and separately potential reasons that slight changes to experiments, or switches to online, could result in noisier samples (and thus smaller effect sizes).
@@
 
-```{r}
+```{r cor-table}
 
@@
 
-All of the correlations are presented in Figure TODO.
+All of the correlations are presented in Figure \@ref(tab:cor-table).
 As the number of rescues is small, and many of these predictors are correlated, we caution against over-interpretation.
@@
 Small replication samples relative to original and rescue could be due both to a) aiming for a small replication sample due to aiming for power for a reported large effect size or b) difficulties with recruitment or high exclusion rates leading to a smaller than intended sample.
-Since relative sizes of the studies may play a role in replication success and how probitive replications are, we show the sample sizes in TABLE TODO.
+Since relative sizes of the studies may play a role in replication success and how probitive replications are, we show the sample sizes in Table \@ref(tab:tab-size).
 
@@
 (As discussed above, changes in time, population, or setting may necessitate adaptation of a study to maximize fidelity.) However, rescue projects varied in how close the re-replications actually were, often due to limitations in the availability of original stimuli and original instructions, in addition to the use of primarily online subject pools.
-TABLE TODO shows the closeness of each re-replication according to the classification scheme from @lebel.
+Table \@ref(tab:tab-size) shows the closeness of each re-replication according to the classification scheme from @lebel2018.
 
-```{r}
+```{r tab-size}
 parsed_d |> select(name_pretty, type, N, closeness, replication_score) |> 
@@
 
-```{r, fig.cap="Standardized effect sizes of original studies, first replications, rescues, and additional replications if available.
+```{r smd, fig.cap="Standardized effect sizes of original studies, first replications, rescues, and additional replications if available.
 Due to the large effect size of a couple studies, large effect studies are shown in a separate panel.
@@
 
-```{r, include=F, fig.cap="Standardized effect sizes of original studies, first replications, rescues, and additional replications if available.
+```{r , include=F, fig.cap="Standardized effect sizes of original studies, first replications, rescues, and additional replications if available.
 Due to the large effect size of a couple studies, large effect studies are shown in a separate panel.
@@
 One potential issue with comparisons using SMD is that noisier measures will have smaller standardized effect sizes even if the effect on the original scale is the same.
-In general, the replication and rescue effect sizes were smaller than the original effect sizes, and in a couple cases the effects were in the opposite direction (FIGURE TODO).
+In general, the replication and rescue effect sizes were smaller than the original effect sizes, and in a couple cases the effects were in the opposite direction (Figure \@ref(fig:smd)).
 
@@
 
-```{r}
+```{r tab-porig}
 names <- parsed_d |> select(target_lastauthor_year, name_pretty) |> unique()
@@
 As our primary comparison, we compare the effect size of the original study to the meta-analytic effect of the totality of the replications (first replication, rescue, and additional if found).
-Because we have few replication for any study, we impute the heterogeneity value of $\tau=.21$ SMD, which is the average level of heterogeneity found by @olsson2020 in prior multi-site replications in psychology.
+Because we have few replication for any study, we impute the heterogeneity value of $\tau=.21$ SMD, which is the average level of heterogeneity found by @olsson-collentine2020 in prior multi-site replications in psychology.
+
+[ query: should we bootstrap any of the following? ]
 
@@
 `r round(main_summ$less_than*100)`% of the $p$-original values were less than .05, indicating by conventional thresholds a rejection of the null hypothesis that the original and the replications came from the same distribution for the given imputed level of heterogeneity.
-Individual $p$-original values for each study are shown in TABLE TODO.
+Individual $p$-original values for each study are shown in Table \@ref(tab:tab-porig).
 
@@
 # Discussion
-We presented the results of `r num_proj` new replications that attempted to "rescue" previous failed replications reported in @boyce2023 by identifying possible causes of non-replication and ameliorating them.
-`r nrow(success)` of these replications (`r round(nrow(success)/num_proj*100)`%) mostly or fully replicated.
+We presented the results of `r num_proj` new replications that attempted to "rescue" previous failed replications reported in @boyce2023 by identifying possible causes of non-replication and ameliorating them in the re-replication.
+`r nrow(success)` of these re-replications (`r round(nrow(success)/num_proj*100)`%) mostly or fully replicated.
 
-We don't have qualitative or quantitative explanations for why some replicated and some didn't.
+We don't have qualitative or quantitative explanations for why the specific studies did or did not replicate.
 In a couple cases, increasing sample size and fixing internal validity issues in the replication seems to have led to a successful rescue (although we can't establish causality even in these cases).
-However, there were other studies that had small replication samples, or implementational deviations in the replication, and rescues were still unsuccessful.
-We can't predict what replication failures are likely to resolve given another try (or a more thoughtful try), beyond that suggestion that glaring problems and low samples may sometimes (but not always) be resolvable.
+However, there were other cases where the original replications had issues with a small sample or deviations in the implementation, and the re-replication addressed these issues but still failed to replicate the original results.
+We can't predict what replication failures are likely to resolve given another, more thoughtful try, beyond that suggestion that glaring problems and low samples may sometimes (but not always) be resolvable.
 
-Another pattern we observed was that the effect sizes of even the successful replications tended to be substantially smaller than the original effect.
+Across all the re-replications, regardless of whether the pattern of effects replicated or not, the effect sizes were smaller than the original effect, often by a substantial amount.
+In a substantial minority of the replications, the replication effect sizes (taken as a whole) were statistically inconsistent with the original effect, even allowing for some heterogeneity between studies.
+These diminished and inconsistent effects suggest that even if a re-replication "works", it may be difficult to build upon as follow-up studies will need large samples to detect the small effects.
 
-[SAY something about statistical consistency]
-
-## Limitations
-The reported rescue projects are a small sample of replications, and the effects explored are non-random, as they have been doubly selected by student interest.
-However, this non-random may be a useful selection bias as it is correlated with  how students choose what to work on.
+The reported rescue projects are a small sample of replications, and the effects explored are non-random, as they have been doubly selected for by student interest.
+However, this selection bias is likely to correlate with how graduate students choose what topics to work on and what studies to build on.
+Nonetheless, with a small sample all our estimates are highly uncertain.
 
@@
 These limitations are representative of the sort of resource limitations often faced by early-career researchers.
-That said, it is possible that different results might be obtained in better-resourced settings.
-Thus, we do not make statements about whether these studies are "true" or "false-positives", merely that they do not support cumulative research by early-career researchers under these conditions.
+That said, it is possible that different results might be obtained in better-resourced settings, by scientists with more expertise and more time.
+Thus, we do not make statements about whether the original results are "true" or "false-positives", we merely claim they do not support cumulative research by early-career researchers under the constrained conditions we tested.
 
-We opened this paper with a question about what an early-career researcher should do given a failed replication.
-Should one try again or move on?
-From our sample of testing the "try again" approach, it seems that the odds of a re-replication working are low (consistent with @ebersole2020), so especially if there isn't a super clear failure mode to point to, another try probably won't fix it.
+We opened this paper with a question about what an early-career psychology researcher should do given a failed replication: should they try again or move on?
+From our sample of testing the "try again" approach, it seems that the odds of a re-replication working are low (consistent with @ebersole2020), so especially if there isn't a super clear failure mode to point to, another try probably won't rescue the original results.
 

### 2024-03-12 manuscript/manuscript.Rmd

@@
 # endfloatoption: # See endfloat documentation for more possibilities
-#   - tablesfirst # Default
-#   - nomarkers # Default
 numberlines: FALSE
@@
 #     footrulewidth: 0pt
-
 header-includes:
@@
  - \setcounter{totalnumber}{4}
-
+editor_options: 
+  markdown: 
+    wrap: sentence
 ---
@@
 
-::: {.abstract data-latex="" lang=en}
+::: {.abstract data-latex="" lang="en"}
 <!-- In order to do cumulative science, results need to be replicable.
@@
 Given the relatively low rates of replication success reported in large scale replication projects, this choice point is one facing many scientists in psychology who attempt to replicate a study before building on it.
-Here, we report on 17 re-replications of experiments with failed replicated reported in  Boyce et al.
-(2023).
+Here, we report on 17 re-replications of experiments with failed replicated reported in Boyce et al. (2023).
 In 5/17 of these rescue projects (29%), the re-replication mostly or fully replicated the original results, albeit with smaller effect sizes.
@@
 If the goal is to do cumulative science, one may wish to stop after one failed replication.
-
 :::
 
+```{=html}
 <!-- Other Title ideas:
@@
 -->
+```
 # Introduction
 
-imagine a scenario when this happens (motivating example).
 Imagine the scenario where you are a new graduate student, and you run a replication of a study in the literature that you are interested in building upon in your research.
@@
 Or perhaps the interaction is numerically in the wrong direction, and also the main effects look different.
-Or perhaps the main effect of interest is null, but you found a significant effect on the interaction that wasn't hypothesized.
+Alternatively the main effect of interest may be null, but you found a significant effect interaction that wasn't hypothesized.
 Whatever the details of the replication failure, you are left with a question: Should you *try again* and run a re-replication, or should you *give up* and pick a different study to replicate and build on?
 
-We focus on scientists’ decisions about what studies to run and how to expend their limited resources in the face of an uncertain literature.
-Scientists may replicate studies for a variety of reasons, including calibrating their equipment, confirming a result before building on it, and engaging in meta-scientific practices [other reasons to highlight?
-is there any citation for this?].
+Running studies can be costly, so scientists must decide how to allocate their limited resources in the face of an uncertain literature.
+Attempting to replicate existing studies is a common choice.
+Scientists replicate studies for a variety of reasons, including calibrating their equipment, confirming a result before building on it, and engaging in meta-scientific practices [other reasons to highlight?
+is there any citation for this?]
+.
 We focus on this middle motivation, where a scientist wants to build on a result, and thus wants it to succeed, but does not have strong reasons to believe or disbelieve the finding: it isn't a robust, well-tested effect, nor is it something they have particular suspicions about.
-However, in an uncertain literature, we might not want to commit resources to building on an effect without first checking that we, with our resources and participant sample, can get the core effect we wish to build on.
+In an uncertain literature, we might not want to commit resources to building on an effect without first checking that we, with our resources and participant sample, can get the core effect we wish to build on.
 Thus, scientists may want to re-replicate failed replications if the re-replication is likely to work and is indicative that future experiments in this tradition are likely to be informative.
@@
 
-TODO DISCUSSION OF THE LITERATURE
-What these replication rates say about the truth of the literature is beyond our scope, but these rates do indicate that scientists are far from guaranteed at being able to replicate effects from the literature in their own labs.
+TODO DISCUSSION OF THE LITERATURE What these replication rates say about the truth of the literature is beyond our scope, but these rates do indicate that scientists are far from guaranteed at being able to replicate effects from the literature in their own labs.
 Thus, the question of what to do with a failed replication is a practical one that comes up frequently.
@@
 
-[query: should I try to frame this as two that are symmetric , or should I stick to an original / rep framing? I'm torn]
+[query: should I try to frame this as two that are symmetric , or should I stick to an original / rep framing?
+I'm torn]
 
@@
 # Methods
+
 PSYCH 251 is a graduate-level experimental methods class taught by MCF.
 In previous years, students have conducted replication projects, as reported in @boyce2023.
-In Fall 2023, students in PSYCH 251 were offered the option to do a "rescue" project where they re-replicated one of the unsuccessful replications from a previous year (students could also opt to do a normal replication instead).
+In Fall 2023, students in PSYCH 251 were offered the option to do a "rescue" project where they re-replicated one of the unsuccessful replications from a previous year.
+Students could also opt to do a normal replication instead.
 We report on the result of `r num_proj` rescue projects that opted to be part of the paper and completed data collection.
@@
 ## Sample
-The experiments that were re-replicated were a non-random sample of studies from @boyce2023. 
-We created an initial list of `r nrow(filtered)` rescue-eligible studies that had received a subjective replication success score of 0, .25 or .5 (on a 0-1 scale) in @boyce2023, where the replication had a github repository available (github repositories were used starting in academic year 2015-2016), and where the original experiment had 200 or fewer participants (for feasibility reasons if we needed to increase power).
+
+The experiments that were re-replicated were chosen from studies that failed to replicate in @boyce2023.
+We created an initial list of `r nrow(filtered)` rescue-eligible studies that had received a subjective replication success score of 0, .25 or .5 (on a 0-1 scale) in @boyce2023, where the replication had a github repository available (github repositories were used starting in academic year 2015-2016), and where the original experiment had 200 or fewer participants (to ensure we could afford to increase the sample size).
 We then contacted the replication project authors for permission to share their report and github repository with a new student and include it as a supplement on a resulting paper.
-This left `r length(approved)` options that were offered to the students.
-`r length(chosen)` students chose to do rescue projects; `r length(chosen)-num_proj` students took an incomplete or did not indicate interest in being part of the rescue paper, leaving a final sample of `r num_proj` rescue projects.
+This left `r length(approved)` options for the students to choose from.
+`r length(chosen)` students chose to do rescue projects.
+`r length(chosen)-num_proj` students took an incomplete or did not indicate interest in being part of the rescue paper, leaving a final sample of `r num_proj` rescue projects.
 
@@
 ## Procedure
+
 Students conducted their rescue projects over the course of the 10-week class.
@@
 The rescues had on average `r round(m,2)` times the original sample post-exclusion (median: `r round(mid,2)`, IQR: `r round(low,2)` - `r round(high,2)`, minimum: `r round(lowest, 2)`, maximum: `r round(highest,2)`, see Table \@ref(tab:tab-size) for all sample sizes).
-Across the `r num_proj-1` Prolific studies, we spent $`r pluck(cost,1,1) |> round()`, for an average of $`r (pluck(cost,1,1)/(num_proj-1)) |> round()` per project.
+Across the `r num_proj-1` Prolific studies, we spent \$`r pluck(cost,1,1) |> round()`, for an average of \$`r (pluck(cost,1,1)/(num_proj-1)) |> round()` per project.
 
 ## Pre-registration
+
 Our analysis plan was pre-registered after students had selected projects, but before final data collection on the projects.
@@
 ## Coding of results
-We followed @boyce2023 in what study properties we measured and what measures of replication success we used.
+
+We followed @boyce2023 in the properties of the studies we measure and how we quantify replication success.
 
@@
 Disagreements were resolved through discussion.
-As a compliment to the overall subjective rating of success, we followed @boyce2023 in also doing a statistical comparison on one key measure of interest for each study.
-In order to statistically compare the key measures, we needed effect sizes reported in the same way within each original-replication cluster.
+As a compliment to the subjective rating of overall success, we stastically compared one key measure of interest for each study, following @boyce2023.
+In order to statistically compare the key measures, we needed effect sizes reported in the same way for each original study, replication, and re-replication.
 When effects were not reported in consistent ways across original and replications, we recalculated effects from raw data when necessary to obtain comparable values.
@@
 We also recorded the same set of potential correlates that were used in @boyce2023 for original, replication, and rescue (these were already rated for original and replication).
-These potential correlates included features of the original study including the subfield of the study (cognitive v social v other psychology), its publication year, experimental design features including whether it was a within- or between- subject design, whether each condition was instantiated with one vignette or multiple, and how many items each participant saw, and whether there were open materials and open data.
+These potential correlates included the subfield of the study (cognitive, social, or other psychology), its publication year, experimental design features including whether it was a within- or between- subject design, whether each condition was instantiated with one vignette or multiple, how many items each participant saw, and whether there were open materials and open data.
 
@@
 ## Overall replication rate
+
+```{=html}
 <!--* We will report the distribution of subjective replication success in our rescue sample
@@
 * If there is a mixture of projects that succeed and fail to replicate the original results, we will qualitatively describe differences that may have played a role. -->
+```
 All rescue projects were rated holistically for how well they replicated the original results.
@@
 Another successful replication was that of @ngo2019.
-Here, the original study found a large effect, and so the first replication, powering for 80% power on the reported effect, recruited a small sample of 12 people, and then failed to find the effect.
+Here, the original study found a large effect.
+The first replication, powering for 80% power on the reported effect, recruited a small sample of 12 people.
+It failed to find the effect.
 The rescue, powered using 2.5x the original sample (as recommended by @simonsohn2015), recovered a clear effect (albeit a much smaller one).
-There are reasons to think that some effect sizes in the literature may be inflated TODO CITATIONS, and separately potential reasons that slight changes to experiments, or switches to online, could result in noisier samples (and thus smaller effect sizes).
-Thus, replications with smaller samples than the original (even if powered to the original effect size), may not be that diagnostic, and could potentially benefit from a re-replication.
+There are reasons to think that some effect sizes in the literature may be inflated TODO CITATIONS, and separate reasons that slight changes to experiments or switches to online could result in noisier samples and thus smaller effect sizes.
+Therefore, replications with smaller samples than the original (even if powered to the original effect size), may not be very diagnostic, and could potentially benefit from a re-replication.
 
@@
 
-(TODO other successes or failures we want to discuss? )
+(TODO other successes or failures we want to discuss?
+) (Ben: Emily's project was interesting: the rescue succeeded but with big stimulus-level random effects.
+Verity's project was also interesting: the previous replication, as well as another in the literature, showed similar but smaller findings and it really looked like she could get the effect with a bigger sample, but she ended up finding totally different results.)
 
@@
 
-Small replication samples relative to original and rescue could be due both to a) aiming for a small replication sample due to aiming for power for a reported large effect size or b) difficulties with recruitment or high exclusion rates leading to a smaller than intended sample.
-Since relative sizes of the studies may play a role in replication success and how probitive replications are, we show the sample sizes in Table \@ref(tab:tab-size).
+Small replication samples relative to original and rescue could be due to both a) powering a replication according to a reported large effect size or b) difficulties with recruitment or high exclusion rates leading to a smaller than intended sample.
+Since relative sizes of the studies may play a role in replication success and how probative replications are, we show the sample sizes in Table \@ref(tab:tab-size).
 
@@
 
-Overall, we do not have a clear picture of why certain studies replicated in the rescue sample and others did not, aside from a couple cases where fixing sample size issues may have helped.
+Overall, we do not have a clear picture of why certain studies replicated in the rescue sample and others did not, other than a few cases where fixing sample size issues may have helped.
 
@@
 As a complement to the holistic, qualitative replication ratings used above, we also statistically compared the effect sizes of the rescue, original replication, and original study on one key measure per study.
-We followed @boyce2023 in the determination of a key measure for each study.
+We followed @boyce2023 in determining a key measure for each study.
 When we were aware of additional direct replications (either from other class projects, or external replications in the literature), we also consider the effect sizes obtained in these additional replications.
@@
 One potential issue with comparisons using SMD is that noisier measures will have smaller standardized effect sizes even if the effect on the original scale is the same.
-In general, the replication and rescue effect sizes were smaller than the original effect sizes, and in a couple cases the effects were in the opposite direction (Figure \@ref(fig:smd)).
+In general, the replication and rescue effect sizes were smaller than the original effect sizes, and in a few cases the effects were in the opposite direction (Figure \@ref(fig:smd)).
 
@@
 
-Our intuitions of replication and intuitions of whether an effect provides support for a hypothesis (including heuristic cutoffs like p<.05) don't always align with measures of statistical consistency [@patil2016].
+Scientists' intuitions about whether a replication is successful and whether an effect provides support for a hypothesis (including heuristic cutoffs like p\<.05) do not always align with measures of statistical consistency [@patil2016].
 For instance, two studies may both find that condition 1 results in a significantly higher outcome measure than condition 2, but the effect magnitudes may be sufficiently different that they are statistically unlikely to have come from the same population.
-On the other side, one study may find a statistically significant, but imprecisely estimated effect in a small sample, and second study may find a near-zero (null) effect, but the effect estimates from the two studies may be statistically compatible, despite one supporting a hypothesized difference and the other not.
+On the other hand, one study may find a statistically significant, but imprecisely estimated effect in a small sample, and second study may find a near-zero (null) effect, but the effect estimates from the two studies may be statistically compatible, despite one supporting a hypothesized difference and the other not.
+
+[Ben: I think the paragraph below could use more explanation about what $p$-original is, but I'm not confident enough in my understanding of it to write it myself.]
 
@@
 As our primary comparison, we compare the effect size of the original study to the meta-analytic effect of the totality of the replications (first replication, rescue, and additional if found).
-Because we have few replication for any study, we impute the heterogeneity value of $\tau=.21$ SMD, which is the average level of heterogeneity found by @olsson-collentine2020 in prior multi-site replications in psychology.
+Because there is only a small number of replications per study, we impute the heterogeneity value of $\tau=.21$ SMD, which is the average level of heterogeneity found by @olsson-collentine2020 in prior multi-site replications in psychology.
 
-[ query: should we bootstrap any of the following? ]
+[ query: should we bootstrap any of the following?
+]
 
@@
 
-As secondary measures, we also calculated the $p$-original values for a) the original and the rescue, b) the original and non-rescue replications, and c) between the rescue and other replications. 
+As secondary measures, we calculated the $p$-original values between a) the original and the rescue, b) the original and non-rescue replications, and c) the rescue and other replications.
 For a) the rescue versus the original, median value of $p$-original was `r rescue_summ$median |> round(2)` [IQR: `r rescue_summ$low |> round(2)` - `r rescue_summ$high|> round(2)`], and `r round(rescue_summ$less_than*100)`% of the $p$-original values were less than .05.
@@
 -->
+
 Overall, allowing for a heterogeneity level of $\tau$=.21 SMD, a number of rescues and replications are not statistically consistent with the original effects.
 The pattern of inconsistency does not align with which studies were rated as having replicated.
-In all cases, the point estimate of the re-replication is smaller than (or in the opposite direction) of the original effect on the key measure of interest.
+In all cases, the point estimate of the re-replication is smaller than, or in the opposite direction of, the original effect on the key measure of interest.
 
@@
 # Discussion
-We presented the results of `r num_proj` new replications that attempted to "rescue" previous failed replications reported in @boyce2023 by identifying possible causes of non-replication and ameliorating them in the re-replication.
+
+We presented the results of `r num_proj` new replications that attempted to "rescue" previous failed replications reported in @boyce2023 by identifying and ameliorating possible causes of non-replication.
 `r nrow(success)` of these re-replications (`r round(nrow(success)/num_proj*100)`%) mostly or fully replicated.
@@
 We don't have qualitative or quantitative explanations for why the specific studies did or did not replicate.
-In a couple cases, increasing sample size and fixing internal validity issues in the replication seems to have led to a successful rescue (although we can't establish causality even in these cases).
+In some cases, increasing sample size and fixing internal validity issues in the replication seems to have led to a successful rescue (although we can't establish causality even in these cases).
 However, there were other cases where the original replications had issues with a small sample or deviations in the implementation, and the re-replication addressed these issues but still failed to replicate the original results.
-We can't predict what replication failures are likely to resolve given another, more thoughtful try, beyond that suggestion that glaring problems and low samples may sometimes (but not always) be resolvable.
+We can't predict what replication failures are likely to resolve given another, more thoughtful try, beyond that suggestion that glaring problems and low samples may sometimes be resolvable.
 
-Across all the re-replications, regardless of whether the pattern of effects replicated or not, the effect sizes were smaller than the original effect, often by a substantial amount.
-In a substantial minority of the replications, the replication effect sizes (taken as a whole) were statistically inconsistent with the original effect, even allowing for some heterogeneity between studies.
-These diminished and inconsistent effects suggest that even if a re-replication "works", it may be difficult to build upon as follow-up studies will need large samples to detect the small effects.
+The re-replications all showed smaller effect sizes than their original studies, regardless of whether the pattern of effects replicated.
+A large minority of replications had effect sizes that were statistically inconsistent with the original effect, even allowing for some heterogeneity between studies.
+These diminished and inconsistent effects suggest that even if a re-replication "works", it may be difficult to build upon as follow-up studies will need large samples to detect small effects.
 
-The reported rescue projects are a small sample of replications, and the effects explored are non-random, as they have been doubly selected for by student interest.
+The reported rescue projects are a small sample of replications.
+They are also chosen non-randomly, as they have been selected for twice by student interest.
 However, this selection bias is likely to correlate with how graduate students choose what topics to work on and what studies to build on.
@@
 We opened this paper with a question about what an early-career psychology researcher should do given a failed replication: should they try again or move on?
-From our sample of testing the "try again" approach, it seems that the odds of a re-replication working are low (consistent with @ebersole2020), so especially if there isn't a super clear failure mode to point to, another try probably won't rescue the original results.
+From our sample of testing the "try again" approach, it seems that the odds of a re-replication working are low (consistent with @ebersole2020).
+Especially if there is not a clear, identifiable reason for the first replication's failure, another try is unlikely to rescue the original result.
 
-# Acknowledgements {-}
+# Acknowledgements {.unnumbered}
 
-# Author Contributions {-}
+# Author Contributions {.unnumbered}
 
-# References {-}
+# References {.unnumbered}
 
 <!-- Use this magic to place references here. -->
-<div id="refs"></div>
+
+::: {#refs}
+:::

### 2024-03-13 manuscript/manuscript.Rmd
assorted edits, plot fix

@@
 ---
-title: "Estimating the likelihood of student replication success after an initial failure to replicate"
+title: "Estimating the replicability of psychology experiments after an initial failure to replicate"
 author:
   - name: Veronica Boyce
-    affiliation: Stanford
+    affiliation: Psych
     footnote:
       - corresp
-  - name: TODO x a lot
-    affiliation: Stanford
+  - name: Ben Prystawski
+    affiliation: Psych
+  - name: Adani Abutto
+    affiliation: Psych
+  - name: Emily Chen
+    affiliation: Psych
+  - name: Ziwen Chen
+    affiliation: GSB
+  - name: Howard Chiu
+    affiliation: Edu
+  - name: Irmak Ergin
+    affiliation: Psych
+  - name: Anmol Gupta
+    affiliation: Psych
+  - name: Chuqi Hu
+    affiliation: Symsys
+  - name: Bendix Kemmann
+    affiliation: Philosophy
+  - name: Nastasia Klevak
+    affiliation: Psych
+  - name: Verity Y. Q. Lua
+    affiliation: Psych
+  - name: Mateus M. Mazzaferro
+    affiliation: Edu
+  - name: Khaing Mon
+    affiliation: Symsys
+  - name: Dan Ogunbamowo
+    affiliation: Psych
+  - name: Alexander Pereira
+    affiliation: Philosophy
+  - name: Jordan Troutman
+    affiliation: CS
+  - name: Sarah Tung
+    affiliation: Psych
+  - name: Raphael Uricher
+    affiliation: Psych
   - name: Michael C. Frank
-    affiliation: Stanford
+    affiliation: Psych
 address:
-  - code: Stanford
-    address: Stanford University
+  - code: Psych
+    address: Department of Psychology, Stanford University
+  - code: GSB
+    address: Graduate School of Business, Stanford University
+  - code: Edu
+    address: Graduate School of Education, Stanford University
+  - code: Symsys
+    address: Symbolic Systems Program, Stanford University
+  - code: Philosophy
+    address: Department of Philosophy, Stanford University
+  - code: CS
+    address: Department of Computer Science, Stanford University
 footnote:
@@
 ::: {.abstract data-latex="" lang="en"}
-<!-- In order to do cumulative science, results need to be replicable.
-However, an individual direct replication could get a different result than an original ("replication failure") for a number of reasons, which vary in whether they would apply to a potential second replication.
-Given one failed replication, how likely is a second attempt at replication to succeed?-->
+When a replication fails, scientists have to decide whether to make a second attempt or move on.
+Researchers who attempt to replicate studies before building on them often face this decision, given the relatively low rates of replication success in psychology.
+Here, we report on 17 re-replications of experiments with failed replications reported in Boyce et al.
+(2023).
+In 5/17 of these "rescue" projects (29%), the re-replication mostly or fully replicated the original results, albeit with smaller effect sizes.
+While a few replications were rescued with larger sample sizes and minor methodological changes, most re-replications failed again.
+In many situations, it may be most efficient to stop pursuing an effect after a single failed replication.
+:::
+TODO FIX CITATION / BIB INFO
 
-As a pragmatic matter, when a replication fails, scientists have to decide: do they make a second attempt at replication, or move on?
-Given the relatively low rates of replication success reported in large scale replication projects, this choice point is one facing many scientists in psychology who attempt to replicate a study before building on it.
-Here, we report on 17 re-replications of experiments with failed replicated reported in Boyce et al. (2023).
-In 5/17 of these rescue projects (29%), the re-replication mostly or fully replicated the original results, albeit with smaller effect sizes.
-While a few studies with failed replications were rescued with larger sample sizes and experimental tweaks, our overall results indicate that most failed replications stayed failed.
-If the goal is to do cumulative science, one may wish to stop after one failed replication.
-:::
-
-```{=html}
-<!-- Other Title ideas:
-
-Can failed replications be rescued? Evidence from N re-replication experiments suggests rarely.
-
-Try again? Attempts to rescue failed replications were generally unsuccessful
-
-A low rate of successfully replicating experiments with a prior unsuccessful replication
-
-Once is probably enough. Low replication rates when re-replicating N studies with failed replications.
-
-* may want to include "student" or "class"
-
-Estimating the replicability of experiments with a prior unsuccessful replication
-
-Estimating the likelihood of [student] replication success after an initial failure to replicate
--->
-```
 # Introduction
@@
 Whatever the details of the replication failure, you are left with a question: Should you *try again* and run a re-replication, or should you *give up* and pick a different study to replicate and build on?
+
+In psychology, large scale replication projects have tended to find replicability rates around half.
+Across 100 studies with positive results, RP:P replicated 36 - 47% depending on the metric for replication success [@openscienceconsortium].
+With large multi-site samples, Many Labs 1 replicated 11/13 effects (84.6%), Many Labs 2 replicated 14/28 effects (50%), and Many Labs 3 replicated 3/10 effects (30%) [@klein2014; @klein2018; @ebersole2016].
+@camerer2018 included 21 behavioral social science studies and replicated 12-14 of them (57%-67%) depending on the metric used.
+@boyce2023 reports an average replication score of 49% for 176 replications primary in psychology.
+Psychology is not the only discipline where not everything replicates.
+Large scale replication projects in other disciplines have found 39/97 (40%) for positive effects in cancer biology [@errington2021], 11/18 (61%) in economics [@camerer2016], and 31/40 (78%) for experimental philosophy [@cova2021].
+
+____
+TODO VB IS UNSURE WHAT EXACTLY THE PROPOSED REORDERING IS
 
@@
 
-In psychology, large scale replication projects have tended to find replicability rates around half.
-Across 100 studies with positive results, RP:P replicated 36 - 47% depending on the metric for replication success [@openscienceconsortium].
-With large multi-site samples, Many Labs 1 replicated 11/13 effects (84.6%), Many Labs 2 replicated 14/28 effects (50%), and Many Labs 3 replicated 3/10 effects (30%) [@klein2014; @klein2018; @ebersole2016].
-@camerer2018 included 21 behavioral social science studies and replicated 12-14 of them (57%-67%) depending on the metric used.
-@boyce2023 reports an average replication score of 49% for 176 replications primary in psychology.
-Psychology is not the only discipline where not everything replicates.
-Large scale replication projects in other disciplines have found 39/97 (40%) for positive effects in cancer biology [@errington2021], 11/18 (61%) in economics [@camerer2016], and 31/40 (78%) for experimental philosophy [@cova2021].
-
-TODO DISCUSSION OF THE LITERATURE What these replication rates say about the truth of the literature is beyond our scope, but these rates do indicate that scientists are far from guaranteed at being able to replicate effects from the literature in their own labs.
+ What these replication rates say about the truth of the literature is beyond our scope, but these rates do indicate that scientists are far from guaranteed at being able to replicate effects from the literature in their own labs.
 Thus, the question of what to do with a failed replication is a practical one that comes up frequently.
@@
 The replication effect size was much smaller CITE NUMBER [@ebersole2020].
-We could frame @ebersole2020 as an attempt to rescue the original effects of the 9 studies with significant original effects and non-significant RP:P effects by a combination of high power and design tweaks.
+We could frame @ebersole2020 as an attempt to recover the original effects of the 9 studies with significant original effects and non-significant RP:P effects by a combination of high power and design tweaks.
 This suggests a successful re-replication rate of 2/9 (22%) for studies with non-significant first replications, under fairly favorable, high resource circumstances.
@@
 If the original materials are still unavailable, a second replication is no better off.
-If a second replication can get closer to the original, either by using closer materials, or better adapting the study to a new environment, the rescue might succeed at better approximating the results of the original.
+If a second replication can get closer to the original, either by using closer materials, or better adapting the study to a new environment, the second replication might succeed at better approximating the results of the original.
 A failed manipulation check failure may not be fixable, but it might at least be diagnoseable.
@@
 In the present paper, we report the results of `r num_proj` re-replication "rescue" projects which each re-replicated a study which had a failed or only partially-successful replication in @boyce2023.
-This is a non-random sample, and given the small number of projects, we provide descriptive statistics and discuss qualitatively some potential sources of differential re-replication outcomes.
-[possibly drop last sentence?]
+TODO PREVIEW RESULTS??
 
@@
 
-A spreadsheet of projects, individual project write-ups (both replications and rescues), links to individual project data and analyses for rescue projects, and the analytic code for this paper are all available at TODO OSF LINK GOES HERE.
+A spreadsheet of projects, individual project write-ups (both first replications and rescues), links to individual project data and analyses for rescue projects, and the analytic code for this paper are all available at TODO OSF LINK GOES HERE.
+
+Our analysis plan was pre-registered after students had selected projects, but before final data collection on the projects.
+Each project was also individually pre-registered by the student conducting it.
+The overall analysis is at LINK, individual pre-registrations are linked from LINK.
+
+We note one deviation from our pre-registration here: we pre-registered visual comparisons between original, first replication, and rescue projects using prediction intervals.
+Prediction intervals depend on both the original effect size and variance CITATION TODO, and also the variance of the comparison (replication or rescue) study.
+Thus we cannot show *the* prediction interval for the original study, but would have to show a prediction interval between each pair of studies, which we thought would not offer clarity.
 
@@
 `r length(chosen)` students chose to do rescue projects.
-`r length(chosen)-num_proj` students took an incomplete or did not indicate interest in being part of the rescue paper, leaving a final sample of `r num_proj` rescue projects.
+`r length(chosen)-num_proj` students took an incomplete or did not indicate interest in being part of this paper, leaving a final sample of `r num_proj` rescue projects.
 
@@
 
-Students were required to think of reasons the original replication might not have worked, and address them if they could.
+Students were required to think of reasons the first replication might not have worked, and address them if they could.
 A list of possible reasons and solutions TODO LINK was given to students.
@@
 The rescue of @jara-ettinger2022 discovered that the replication had accidentally used the drawn version of the stimuli rather than the photographic stimuli used in the original and reverted to the photographic stimuli.
-@tarampi2016 original had participants indicate their answers (left or right) on a piece of paper in a timed navigation task, the replication had them indicate by clicking a drop down, and rescue went with press keyboard keys to indicate.
+@tarampi2016 original had participants indicate their answers (left or right) on a piece of paper in a timed navigation task, the replication had them indicate by clicking a drop down, and rescue went with pressing keyboard keys to indicate the direction of the a turn.
 TODO others to note?
@@
 
-## Pre-registration
-
-Our analysis plan was pre-registered after students had selected projects, but before final data collection on the projects.
-Each project was also individually pre-registered by the student conducting it.
-The overall analysis is at LINK, individual pre-registrations are linked from LINK.
-
-We note one deviation from our pre-registration here: we pre-registered visual comparisons between original, first replication, and rescue projects.
-Prediction intervals depend on both the original effect size and variance CITATION TODO, and also the variance of the comparison (replication) study.
-Thus we cannot show *the* prediction interval for the original study, but would have to show a prediction interval between each pair of studies, which we thought would not offer clarity.
-
 ## Coding of results
@@
 As a compliment to the subjective rating of overall success, we stastically compared one key measure of interest for each study, following @boyce2023.
-In order to statistically compare the key measures, we needed effect sizes reported in the same way for each original study, replication, and re-replication.
+In order to statistically compare the key measures, we needed effect sizes reported in the same way for each original study, first replication, and rescue.
 When effects were not reported in consistent ways across original and replications, we recalculated effects from raw data when necessary to obtain comparable values.
 
-We also recorded the same set of potential correlates that were used in @boyce2023 for original, replication, and rescue (these were already rated for original and replication).
+We also recorded the same set of potential correlates that were used in @boyce2023 for original, first replication, and rescue (these were already rated for original and first replication).
 These potential correlates included the subfield of the study (cognitive, social, or other psychology), its publication year, experimental design features including whether it was a within- or between- subject design, whether each condition was instantiated with one vignette or multiple, how many items each participant saw, and whether there were open materials and open data.
@@
 
-Across the `r nrow(subj)` replications, `r nrow(success)` mostly or fully replicated the original results according to the subjective replication ratings.
+Across the `r nrow(subj)` rescue projects, `r nrow(success)` mostly or fully replicated the original results according to the subjective replication ratings.
 `r pluck(tallied,2,1)` had a rating of 0, `r pluck(tallied, 2,2)` got a rating of .75, and `r pluck(tallied, 2,3)` got a rating of 1.
@@
 Note that @boyce2023 report the average replication score as a percent success (49%), but given that we considered studies with a subjective score of .5 as eligible to be rescued, we recomputed the success rate when scores of 0-.5 as failures and .75 and 1 as successes.
-If the re-replication rate in our sample is representative of the re-replication rate for the initially non-replication studies, then the combined chance of mostly or fully replicating in a first replication or a follow-up replication is `r round(overall*100)`%.
+If the re-replication rate in our sample is representative of the re-replication rate for the initially non-replicating studies, then the combined chance of mostly or fully replicating in a first replication or one follow-up replication is `r round(overall*100)`%.
 
-Given the mix of successful and unsuccessful rescues, we discuss a few projects where we have speculations about why they turned out the way they did.
-
-One of the rescues that went from a replication with score of 0 to a rescue with score of 1 was the rescue of @krauss2003.
-This study looked at the influence of a guided thinking on whether or not people gave correct justifications (drawn or written) for their answer on the Monty Hall problem.
-The original paper reported correct justification from 2/67 (`r round(2/67*100)`%) in the control condition and 13/34 (`r round(13/34*100)`%) in the guided thinking condition.
-The first replication struggled to recruit participants who were naive to the problem (an exclusion criterion), and many participants give very short text responses in the provided text box (only textual responses were allowed).
-The replication found 0/8 correct justifications in the control and 0/11 in the guided thinking condition.
-While we can't know for sure what caused the non-replication, there were clear problems observable from the small final sample and low-quality responses.
-The rescue targeted these issues by adding a pre-screen for naivete to the Monty Hall problem, switched the name of the problem (to reduce googling for answers), and had participants upload drawings for their justifications.
-Collectively, these changes brought the rescue closer to the intent of the original.
-The rescue had 1/40 (`r round(1/40*100)`%) correct justifications in the control group and 6/35 (`r round(6/35*100)`%) in the guided thinking group.
-The rescue effect is smaller, but the overall pattern of results replicated, and the online adaptation in the rescue feels like it could be built on.
-
-Another successful replication was that of @ngo2019.
-Here, the original study found a large effect.
-The first replication, powering for 80% power on the reported effect, recruited a small sample of 12 people.
-It failed to find the effect.
-The rescue, powered using 2.5x the original sample (as recommended by @simonsohn2015), recovered a clear effect (albeit a much smaller one).
-There are reasons to think that some effect sizes in the literature may be inflated TODO CITATIONS, and separate reasons that slight changes to experiments or switches to online could result in noisier samples and thus smaller effect sizes.
-Therefore, replications with smaller samples than the original (even if powered to the original effect size), may not be very diagnostic, and could potentially benefit from a re-replication.
-
-Not all rescues of small replications succeeded, however.
-@payne2008 was a study of the effects of sleep versus wake on memory consolidation that showed participants a number of images and then hours later (after either sleep or no sleep) measured their recall for parts of the images.
-The first replication struggled to recruit participants and only got 23 (the original had 48).
-The rescue attempted to recruit a larger sample (target 88), but due to difficulties getting participants to complete the second part of the experiment 12 hours after the first, the rescue only managed to recruit 23 people.
-The lesson here may be that sleep research is difficult to conduct online.
-However, an online replication by @denis2022 reports qualitatively similar (but quantitatively smaller) results to @payne2008 on related but not identical measures.
-
-(TODO other successes or failures we want to discuss?
-) (Ben: Emily's project was interesting: the rescue succeeded but with big stimulus-level random effects.
-Verity's project was also interesting: the previous replication, as well as another in the literature, showed similar but smaller findings and it really looked like she could get the effect with a bigger sample, but she ended up finding totally different results.)
-
-(could discuss tarampi as an example where there were potential issues, we fixed them and it still didn't work?)
-
-## Correlates of rescue success
-
-```{r cor-table}
-
-original <- parsed_d |> filter(type=="original") |> 
-  rename_with(~str_c("original_",.), .cols=-target_lastauthor_year)
-
-rep1 <- parsed_d |> filter(type=="rep1") |> select(target_lastauthor_year, rep_N=N)
-
-for_cor <- subj |> left_join(original) |> left_join(rep1) |> 
-  mutate(
-  social=ifelse(subfield=="social", 1,0),
-  other_psych=ifelse(subfield=="other-psych",1,0), 
-  is_within=ifelse(within_between=="within", 1,0), 
-  change_platform=ifelse(on_turk==original_on_turk, 0,1),
-  log_trials=log(repeated_measure),
-  log_sample=log(N),
-  log_ratio_ss=log(N/original_N),
-  rep_1_log_sample=log(rep_N),
-  log_ratio_rep1_orig=log(rep_N/original_N),
-  log_ratio_rescue_rep1=log(N/rep_N),
-  open_data=ifelse(open_data=="yes",1,0),
-  open_mat=ifelse(open_materials=="yes", 1,0),
-  stanford=ifelse(stanford_internal=="yes",1,0)) |> 
-  filter(!is.na(replication_score))
-
-sub_cor <- function(var, stat = "estimate") {
-  if (stat == "estimate") {
-    cor.test(for_cor$replication_score, pull(for_cor, {{var}}))$estimate
-  } else {
-    cor.test(for_cor$replication_score, pull(for_cor, {{var}}))$p.value
-  }
-}
-
-preds <- c("open_data",  "open_mat", "stanford", "change_platform", 
-           "log_ratio_ss", "is_within", "single_vignette", "log_sample", 
-           "log_trials", "social", "other_psych", "rep_1_log_sample", "log_ratio_rep1_orig", "log_ratio_rescue_rep1")
-
-cors <- tibble(preds = preds) |>
-  mutate(r = sapply(preds, function(x) sub_cor(x, stat = "estimate")),
-         p = sapply(preds, function(x) sub_cor(x, stat = "p"))) |>
-
-  mutate(Predictors=factor(preds, levels=c("social", "other_psych", "is_within", "single_vignette", "change_platform", "open_data", "open_mat", "stanford", "pub_year", "log_trials", "log_sample", "log_ratio_ss", "rep_1_log_sample", "log_ratio_rep1_orig", "log_ratio_rescue_rep1"), labels=c("Social", "Other psych", "Within subjects", "Single vignette", "Switch to online", "Open data", "Open materials", "Stanford", "Publication year", "Log trials", "Log original sample size", "Log rescue/original sample size", "Log replication sample size", "Log replication/original sample size", "Log rescue/replication sample size"))) |> arrange(Predictors) |> select(Predictors, r, p)
-
-library(kableExtra)
-knitr::kable(cors, digits = 3, align='rcc', format="latex", booktabs=T, linesep="", caption="Correlations between an individual predictor and the subjective replication score of the rescue project.")
-
-```
-
-We ran correlations between the set of predictor variables used in @boyce2023 and the subjective replication scores of the rescues.
-We also added some (non-preregistered) predictors related to the sample size of the first replication, after seeing the successful re-replications of @ngo2019 and @krauss2003.
-
-All of the correlations are presented in Figure \@ref(tab:cor-table).
-As the number of rescues is small, and many of these predictors are correlated, we caution against over-interpretation.
-The strongest correlates of rescue success were open materials, a small sample size on the first replication, a small sample size on the first replication relative to the original sample size, and a large rescue sample size relative to the first replication.
-None of these effects meet the conventional significance threshold.
-
-Small replication samples relative to original and rescue could be due to both a) powering a replication according to a reported large effect size or b) difficulties with recruitment or high exclusion rates leading to a smaller than intended sample.
-Since relative sizes of the studies may play a role in replication success and how probative replications are, we show the sample sizes in Table \@ref(tab:tab-size).
-
-An additional factor that influences the interpretation of a replication is how close the replication's methods were to the original.
-In the rescue projects, we aimed to have methods be as close as was feasible or appropriate.
-(As discussed above, changes in time, population, or setting may necessitate adaptation of a study to maximize fidelity.) However, rescue projects varied in how close the re-replications actually were, often due to limitations in the availability of original stimuli and original instructions, in addition to the use of primarily online subject pools.
-Table \@ref(tab:tab-size) shows the closeness of each re-replication according to the classification scheme from @lebel2018.
-
-```{r tab-size}
-parsed_d |> select(name_pretty, type, N, closeness, replication_score) |> 
-  filter(type!="additional") |> 
-  pivot_wider(names_from="type", values_from=c(N, closeness, replication_score)) |> 
-  select(paper=name_pretty, replication_score_rescue, N_original, N_rep1, N_rescue,
-         "Replication \\\\  closeness"=closeness_rep1, closeness_rescue) |> arrange(replication_score_rescue|> desc()) |> knitr::kable(align="lllll", format="latex", booktabs=T, linesep="", caption="Comparison of sample size for original, replication, and rescue samples and measures of closeness for replication and rescue samples.", col.names=c("", "", "Original", "Replication", "Rescue", "Replication", "Rescue")) |> add_header_above(c("Paper"=1, "Score"=1, "N"=3, "closeness"=2))
-
-```
-
-Overall, we do not have a clear picture of why certain studies replicated in the rescue sample and others did not, other than a few cases where fixing sample size issues may have helped.
+## Effect sizes
 
@@
 Due to the large effect size of a couple studies, large effect studies are shown in a separate panel.
+In a few cases, the first replication's key effect was non-zero in the same direction as the original; however, in these cases the larger pattern of results was not fully consistent between original and first replication.
 "}
@@
 #test on just one
-colors <- c("original"="black", "rep1"="#377EB8", "rescue"="#E41A1C", "additional"="#984EA3")
-shape <- c("original"=21,"rep1"=22,"rescue"=23,"additional"=24)
+colors <- c("Original study"="black", "First replication"="#377EB8", "Rescue"="#E41A1C", "Additional replication"="#984EA3")
+shape <- c("Original study"=21,"First replication"=22,"Rescue"=23,"Additional replication"=24)
 
-big <- parsed_d |> filter(type=="original") |> filter(calc_d_calc>1) |> select(target_lastauthor_year)
+big <- parsed_d |> filter(type=="original") |> filter(calc_d_calc>1|target_lastauthor_year=="yeshurun2003") |> select(target_lastauthor_year)
 for_plotting_d <- parsed_d |> filter(!is.na(calc_d_calc)) |> 
-  mutate(point=calc_d_calc, low=calc_d_calc-1.96*calc_d_calc_se, high=calc_d_calc+1.96*calc_d_calc_se)
+  mutate(point=calc_d_calc, low=calc_d_calc-1.96*calc_d_calc_se, high=calc_d_calc+1.96*calc_d_calc_se) |> 
+  mutate(type=case_when(
+    type=="original" ~ "Original study",
+    type=="rep1" ~ "First replication",
+    type=="rescue" ~ "Rescue",
+    type=="additional" ~ "Additional replication"
+  ),
+  type=factor(type, levels=c("Original study", "First replication", "Rescue", "Additional replication")))
 
@@
 
-smd_scale_big <- ggplot(for_plotting_d |> inner_join(big),aes(x=reorder(name_pretty, point, FUN=max),y=point,ymin=low,ymax=high,shape=type, color=type, fill=type, group=desc(type)))+
+level_order = c("Yeshurun & Levy 2003",
+                "Ngo et al. 2019", 
+                 "Krauss & Wang 2003",
+                 "Jara-Ettinger et al 2022")
+smd_scale_big <- ggplot(for_plotting_d |> inner_join(big) |> 
+                          mutate(name_pretty=factor(name_pretty, levels=level_order)), aes(x=name_pretty,y=point,ymin=low,ymax=high,shape=type, color=type, fill=type, group=desc(type)))+
   geom_errorbar(size=.5,width=0, position=position_dodge(width=.5))+
@@
 
-plot_grid(smd_scale_big, smd_scale_small, rel_heights=c(.3,1), nrow=2)
+plot_grid(smd_scale_big, smd_scale_small, rel_heights=c(.4,1), nrow=2)
 ```
 
-```{r , include=F, fig.cap="Standardized effect sizes of original studies, first replications, rescues, and additional replications if available.
-Due to the large effect size of a couple studies, large effect studies are shown in a separate panel.
-"}
-
-#test on just one
-colors <- c("original"="black", "rep1"="#377EB8", "rescue"="#E41A1C", "additional"="#984EA3")
-shape <- c("original"=21,"rep1"=22,"rescue"=23,"additional"=24)
-
-smd_scale <- ggplot(for_plotting_d,aes(x=reorder(name_pretty, point, FUN=max),y=point,ymin=low,ymax=high,shape=type, color=type, fill=type, group=desc(type)))+
-  geom_errorbar(size=.5,width=0, position=position_dodge(width=.5))+
-  geom_point(position=position_dodge(width=.5))+
- coord_flip()+
-  scale_size_area()+
-  geom_hline(yintercept=0,color="black")+
-    scale_color_manual(values=colors, aesthetics=c("color", "fill"))+
-  scale_shape_manual(values=shape)+
-  theme(legend.position = "bottom", 
-        panel.grid.major.x = element_blank(), 
-        panel.grid.minor.x=element_blank()
-        )+
-  labs(y="Standarized mean difference", x="")
-
-smd_scale
-
-```
-
-## Effect sizes
-
-As a complement to the holistic, qualitative replication ratings used above, we also statistically compared the effect sizes of the rescue, original replication, and original study on one key measure per study.
+As a complement to the holistic, qualitative replication ratings used above, we also statistically compared the effect sizes of the rescue, first replication, and original study on one key measure per study.
 We followed @boyce2023 in determining a key measure for each study.
@@
 
-[Ben: I think the paragraph below could use more explanation about what $p$-original is, but I'm not confident enough in my understanding of it to write it myself.]
+[TODO Ben: I think the paragraph below could use more explanation about what $p$-original is, but I'm not confident enough in my understanding of it to write it myself.]
 
@@
 
-```{r, include=F,  fig.caption="Plot of the prediction intervals of the original studies compared to replication results.
-The open circles are SMD effect sizes from the original studies, error bars are the prediction intervals, and filled shapes denote replication effect sizes.
-Prediction intervals in green contain the replication effect, those in grey do not.
-The largest effect sizes are separated in a separate panel to allow better visualization.
-"}
-colors <- c("original"="black", "rep1"="#377EB8", "rescue"="#E41A1C", "additional"="#984EA3")
-shape <- c("original"=21,"rep1"=22,"rescue"=23,"additional"=24)
-col_code <- c("TRUE"="darkgreen", "FALSE"="black")
+## Correlates of rescue success
 
-big <- predInts_het |> filter(d>1) |> select(target_lastauthor_year)
+```{r cor-table}
 
-small_predInt <-  ggplot(predInts_het |> filter(!is.na(d_inside)) |> anti_join(big), aes(x=reorder(name_pretty, d, FUN=max), y=rep_d, ymin=d_low, ymax=d_high, fill=type, color=d_inside, group=desc(type), shape=type))+
-  geom_errorbar(size=.5, width=.25, position=position_dodge(width=.4), alpha=.5)+
-  geom_point(aes(y=d), position=position_dodge(width=.4), shape=1, alpha=.5)+
-     geom_point(size=2.5, position=position_dodge(width=.4), color="transparent")+
-  coord_flip()+
-  scale_size_area()+
-  geom_hline(yintercept=0,color="black")+
-  theme(legend.position="bottom", 
-        panel.grid.major.x = element_blank(), 
-        panel.grid.minor.x=element_blank()
-        )+
-  scale_fill_manual(values=colors)+
-  scale_shape_manual(values=shape)+
-  scale_color_manual(values=col_code)+
-  labs(y="predInts on SMD scale", x="")
+original <- parsed_d |> filter(type=="original") |> 
+  rename_with(~str_c("original_",.), .cols=-target_lastauthor_year)
 
-big_predInt <-  ggplot(predInts_het |> filter(!is.na(d_inside)) |> inner_join(big), aes(x=reorder(name_pretty, d, FUN=max), y=rep_d, ymin=d_low, ymax=d_high, color=d_inside, fill=type, group=desc(type), shape=type))+
-  geom_errorbar(size=.5,width=.25, position=position_dodge(width=.4), alpha=.5)+
-  geom_point(aes(y=d), position=position_dodge(width=.4), shape=1, alpha=.5)+
-     geom_point(size=2.5, position=position_dodge(width=.4), color="transparent")+
-  coord_flip()+
-  scale_size_area()+
-  geom_hline(yintercept=0,color="black")+
-  theme(legend.position="none", 
-        panel.grid.major.x = element_blank(), 
-        panel.grid.minor.x=element_blank()
-        )+
-  scale_fill_manual(values=colors)+
-  scale_shape_manual(values=shape)+
-  scale_color_manual(values=col_code)+
-  labs(y="predInts on SMD scale", x="")
+rep1 <- parsed_d |> filter(type=="rep1") |> select(target_lastauthor_year, rep_N=N)
 
-plot_grid(big_predInt, small_predInt, nrow=2, rel_heights = c(.3,1))
+for_cor <- subj |> left_join(original) |> left_join(rep1) |> 
+  mutate(
+  social=ifelse(subfield=="social", 1,0),
+  other_psych=ifelse(subfield=="other-psych",1,0), 
+  is_within=ifelse(within_between=="within", 1,0), 
+  change_platform=ifelse(on_turk==original_on_turk, 0,1),
+  log_trials=log(repeated_measure),
+  log_sample=log(N),
+  log_ratio_ss=log(N/original_N),
+  rep_1_log_sample=log(rep_N),
+  log_ratio_rep1_orig=log(rep_N/original_N),
+  log_ratio_rescue_rep1=log(N/rep_N),
+  open_data=ifelse(open_data=="yes",1,0),
+  open_mat=ifelse(open_materials=="yes", 1,0),
+  stanford=ifelse(stanford_internal=="yes",1,0)) |> 
+  filter(!is.na(replication_score))
+
+sub_cor <- function(var, stat = "estimate") {
+  if (stat == "estimate") {
+    cor.test(for_cor$replication_score, pull(for_cor, {{var}}))$estimate
+  } else {
+    cor.test(for_cor$replication_score, pull(for_cor, {{var}}))$p.value
+  }
+}
+
+preds <- c("open_data",  "open_mat", "stanford", "change_platform", 
+           "log_ratio_ss", "is_within", "single_vignette", "log_sample", 
+           "log_trials", "social", "other_psych", "rep_1_log_sample", "log_ratio_rep1_orig", "log_ratio_rescue_rep1")
+
+cors <- tibble(preds = preds) |>
+  mutate(r = sapply(preds, function(x) sub_cor(x, stat = "estimate")),
+         p = sapply(preds, function(x) sub_cor(x, stat = "p"))) |>
+
+  mutate(Predictors=factor(preds, levels=c("social", "other_psych", "is_within", "single_vignette", "change_platform", "open_data", "open_mat", "stanford", "pub_year", "log_trials", "log_sample", "log_ratio_ss", "rep_1_log_sample", "log_ratio_rep1_orig", "log_ratio_rescue_rep1"), labels=c("Social", "Other psych", "Within subjects", "Single vignette", "Switch to online", "Open data", "Open materials", "Stanford", "Publication year", "Log trials", "Log original sample size", "Log rescue/original sample size", "Log replication sample size", "Log replication/original sample size", "Log rescue/replication sample size"))) |> arrange(Predictors) |> select(Predictors, r, p)
+
+library(kableExtra)
+knitr::kable(cors, digits = 3, align='rcc', format="latex", booktabs=T, linesep="", caption="Correlations between an individual predictor and the subjective replication score of the rescue project.
+The first set of predictors were pre-registered based on the correlates used in Boyce et al.
+(2023).
+The last three predictors were added post-hoc.") |> row_spec(11, hline_after=T)
 
 ```
+
+We ran correlations between the set of predictor variables used in @boyce2023 and the subjective replication scores of the rescues.
+We also added some (non-preregistered) predictors related to the sample size of the first replication, after seeing the successful re-replications of @ngo2019 and @krauss2003, both studies with small replication samples.
+
+All of the correlations are presented in Figure \@ref(tab:cor-table).
+As the number of rescues is small, and many of these predictors are correlated, we caution against over-interpretation.
+The strongest correlates of rescue success were open materials, a small sample size on the first replication, a small sample size on the first replication relative to the original sample size, and a large rescue sample size relative to the first replication.
+None of the pre-registered correlates meet the conventional significance threshold; the two correlates based on ratios that reflect a relatively smaller replication sample size are marginally significant.
+
+Small replication samples relative to original and rescue could be due to both a) powering a replication according to a reported large effect size or b) difficulties with recruitment or high exclusion rates leading to a smaller than intended sample.
+Since relative sizes of the studies may play a role in replication success and how probitive replications are, we show the sample sizes in Table \@ref(tab:tab-size).
+
+An additional factor that influences the interpretation of a replication is how close the replication's methods were to the original.
+In the rescue projects, we aimed to have methods be as close as was feasible or appropriate.
+(As discussed above, changes in time, population, or setting may necessitate adaptation of a study to maximize fidelity.) However, rescue projects varied in how close the re-replications actually were, often due to limitations in the availability of original stimuli and original instructions, in addition to the use of primarily online subject pools.
+Table \@ref(tab:tab-size) shows the closeness of each first replication and rescue according to the classification scheme from @lebel2018.
+TODO CLOSENESS NUMBERS SHOULD BE DOUBLE CHECKED AND FIRST REPS REVISED AS NEEDED
+
+```{r tab-size}
+parsed_d |> select(name_pretty, type, N, closeness, replication_score) |> 
+  filter(type!="additional") |> 
+  pivot_wider(names_from="type", values_from=c(N, closeness, replication_score)) |> 
+  select(paper=name_pretty, replication_score_rescue, N_original, N_rep1, N_rescue,
+         "Replication \\\\  closeness"=closeness_rep1, closeness_rescue) |> arrange(replication_score_rescue|> desc()) |> knitr::kable(align="lllll", format="latex", booktabs=T, linesep="", caption="Comparison of sample size for original, replication, and rescue samples and measures of closeness for replication and rescue samples.", col.names=c("", "", "Original", "Replication", "Rescue", "Replication", "Rescue")) |> add_header_above(c("Paper"=1, "Score"=1, "N"=3, "closeness"=2))
+
+```
+
+Overall, we do not have a clear picture of why certain studies replicated in the rescue sample and others did not, other than a few cases where fixing sample size issues may have helped.
+
+# Case studies
+
+Given the mix of successful and unsuccessful rescues, we discuss a few projects where we have speculations about why they turned out the way they did.
+
+One of the rescues that went from a replication with score of 0 to a rescue with score of 1 was the rescue of @krauss2003.
+This study looked at the influence of a guided thinking on whether or not people gave correct justifications (drawn or written) for their answer on the Monty Hall problem.
+The original paper reported correct justification from 2/67 (`r round(2/67*100)`%) in the control condition and 13/34 (`r round(13/34*100)`%) in the guided thinking condition.
+The first replication struggled to recruit participants who were naive to the problem (an exclusion criterion), and many participants give very short text responses in the provided text box (only textual responses were allowed).
+The replication found 0/8 correct justifications in the control and 0/11 in the guided thinking condition.
+While we can't know for sure what caused the non-replication, there were clear problems observable from the small final sample and low-quality responses.
+The rescue targeted these issues by adding a pre-screen for naivete to the Monty Hall problem, switched the name of the problem (to reduce googling for answers), and had participants upload drawings for their justifications.
+Collectively, these changes brought the rescue closer to the intent of the original.
+The rescue had 1/40 (`r round(1/40*100)`%) correct justifications in the control group and 6/35 (`r round(6/35*100)`%) in the guided thinking group.
+The rescue effect is smaller, but the overall pattern of results replicated, and the online adaptation in the rescue feels like it could be built on.
+
+Another successful rescue was that of @ngo2019.
+Here, the original study found a large effect.
+The first replication, powering for 80% power on the reported effect, recruited a small sample of 12 people.
+It failed to find the effect.
+The rescue, powered using 2.5x the original sample (as recommended by @simonsohn2015), recovered a clear effect (albeit a much smaller one).
+There are reasons to think that some effect sizes in the literature may be inflated TODO CITATIONS, and separate reasons that slight changes to experiments or switches to online could result in noisier samples and thus smaller effect sizes.
+Therefore, replications with smaller samples than the original (even if powered to the original effect size), may not be very diagnostic, and could potentially benefit from a re-replication.
+
+Not all rescues of small replications succeeded, however.
+@payne2008 was a study of the effects of sleep versus wake on memory consolidation that showed participants a number of images and then hours later (after either sleep or no sleep) measured their recall for parts of the images.
+The first replication struggled to recruit participants and only got 23 (the original had 48).
+The rescue attempted to recruit a larger sample (target 88), but due to difficulties getting participants to complete the second part of the experiment 12 hours after the first, the rescue only managed to recruit 23 people.
+The lesson here may be that sleep research is difficult to conduct online.
+However, an online replication by @denis2022 reports qualitatively similar (but quantitatively smaller) results to @payne2008 on related but not identical measures.
+
+(TODO other successes or failures we want to discuss?
+) (Ben: Emily's project was interesting: the rescue succeeded but with big stimulus-level random effects.
+Verity's project was also interesting: the previous replication, as well as another in the literature, showed similar but smaller findings and it really looked like she could get the effect with a bigger sample, but she ended up finding totally different results.)
+
+(could discuss tarampi as an example where there were potential issues, we fixed them and it still didn't work?)
 
@@
 We presented the results of `r num_proj` new replications that attempted to "rescue" previous failed replications reported in @boyce2023 by identifying and ameliorating possible causes of non-replication.
-`r nrow(success)` of these re-replications (`r round(nrow(success)/num_proj*100)`%) mostly or fully replicated.
+`r nrow(success)` of these rescue projects (`r round(nrow(success)/num_proj*100)`%) mostly or fully replicated the original results.
 
@@
 In some cases, increasing sample size and fixing internal validity issues in the replication seems to have led to a successful rescue (although we can't establish causality even in these cases).
-However, there were other cases where the original replications had issues with a small sample or deviations in the implementation, and the re-replication addressed these issues but still failed to replicate the original results.
+However, there were other cases where the first replications had issues with a small sample or deviations in the implementation, and the rescue addressed these issues but still failed to replicate the original results.
 We can't predict what replication failures are likely to resolve given another, more thoughtful try, beyond that suggestion that glaring problems and low samples may sometimes be resolvable.
 
-The re-replications all showed smaller effect sizes than their original studies, regardless of whether the pattern of effects replicated.
+The rescues all showed smaller effect sizes than their original studies, regardless of whether the pattern of effects replicated.
 A large minority of replications had effect sizes that were statistically inconsistent with the original effect, even allowing for some heterogeneity between studies.
@@
 From our sample of testing the "try again" approach, it seems that the odds of a re-replication working are low (consistent with @ebersole2020).
-Especially if there is not a clear, identifiable reason for the first replication's failure, another try is unlikely to rescue the original result.
+Especially if there is not a clear, identifiable reason for the first replication's failure, another try is unlikely to recover the original result.
 

### 2024-03-14 manuscript/manuscript.Rmd
try to reorg intro

@@
 
-____
-TODO VB IS UNSURE WHAT EXACTLY THE PROPOSED REORDERING IS
+Replications can fail for any reason.
+In principle, the question of why a replication failed is the same as asking why did two closely related studies have different results, which could be due to any differences between the study.
+In the case of replication failure, there's an asymmetry where the original study happened first and set the methods and analyses and got the more significant result.
+[VB is struggling to articulate ideas here]
+One source of replication failure is that the result is fragile in some way: it could be a statistically unlikely result that was achieved through chance or p-hacking, or it could be sensitive to the exact conditions and time it was run under ("hidden moderators").
+The reported effect sizes might be biased estimates due to some combination of heterogeneity, p-hacking, luck, underpowering, and publication bias.
+The replication study could be underpowered to detect the effect, perhaps due to powering for the reported (inflated) effect size, or unexpected attrition in the replication sample.
 
-Running studies can be costly, so scientists must decide how to allocate their limited resources in the face of an uncertain literature.
-Attempting to replicate existing studies is a common choice.
-Scientists replicate studies for a variety of reasons, including calibrating their equipment, confirming a result before building on it, and engaging in meta-scientific practices [other reasons to highlight?
-is there any citation for this?]
-.
-We focus on this middle motivation, where a scientist wants to build on a result, and thus wants it to succeed, but does not have strong reasons to believe or disbelieve the finding: it isn't a robust, well-tested effect, nor is it something they have particular suspicions about.
+Replications might get different results from an original study due to differences in how the question of interest was instantiated; these differences in design could be intentional adaptations, or they could be unintentional if a replication recreates instructions or materials because the original ones are not available, or they could be trivial differences that turn out to be crucial to the effect.
+
+A difference in experiment platforms (ex.
+online versus in-person) might mean that an implementation doesn't fit the platform, or the data quality controls and attention checks are inadequate.
+If there are differences in time, place, or subject population between the two studies, there may need to be differences in the materials, instructions, or procedure to provide a good *translation* -- too many changes could cause differing results, but so could not enough changes.
+
+When replications fail, we generally do not know why they failed, although we often speculate on potential reasons.
+[TODO not sure how to transition here] The goal of most large-scale replication studies has been metascientific, with the aims of estimating the true proportion of effects in a literature or understanding the role of heterogeneity.
+For these purposes, it may not matter exactly why any individual replication failed because they are assessed as a whole.
+
+But when individual scientists attempt to replicate an effect with the goal of building on it, they do care about the individual failed replication.
 In an uncertain literature, we might not want to commit resources to building on an effect without first checking that we, with our resources and participant sample, can get the core effect we wish to build on.
-Thus, scientists may want to re-replicate failed replications if the re-replication is likely to work and is indicative that future experiments in this tradition are likely to be informative.
-
-This scientist-decision focused angle is different from the standard approach to replication which has take then the meta-scientific approach which has been primarily concerned with estimating the proportion of true effects in the literature.
-Large-scale replication studies indicate that the literature is unreliable.
-
- What these replication rates say about the truth of the literature is beyond our scope, but these rates do indicate that scientists are far from guaranteed at being able to replicate effects from the literature in their own labs.
-Thus, the question of what to do with a failed replication is a practical one that comes up frequently.
-
-Replications can fail for many reasons.
-Replication failure implies a certain time direction: first a "successful" study, usually one that got a certain statistically significant result, and (later) a "failed" replication that did not get this statistically significant result.
-The replication failure framing implies a time direction (TODO THERE IS A CITATION FOR THIS IDEA RIGHT OF PRECEDENCE).
-Taking out the time component, we can instead analyse a replication failure as two very-related studies with differing results.
-Under this frame, the question becomes: what is different between these two studies that could account for the differing results?
-
-[query: should I try to frame this as two that are symmetric , or should I stick to an original / rep framing?
-I'm torn]
-
-There are many potential reasons for differing results (see also @ebersole2020).
-One option is that one of the studies had a statistically unlikely result (either through chance or p-hacking).
-The result could be sensitive to some of the exact conditions and time when the two studies were run ("hidden moderators") and lack generalizability.
-Reported effect sizes might be biased estimates due to some combination of heterogeneity, p-hacking, luck, underpowering, and publication bias.
-One or both studies might be underpowered, potentially due to believing the effect was larger, or unexpected attrition in the sample.
-
-Studies might differ in how they instantiated the question of interest, and this might cause different results.
-For example if a manipulation check failed, that could be a proximate cause of difference, which also raises questions about why the manipulation check failed.
-Differences in materials or instructions might turn out to be crucial to the effect.
-A difference in experiment platforms (ex.
-online versus in-person) might mean that an implementation doesn't fit the platform, or the data quality controls and attention checks may not be appropriate to the sample population.
-Some trivial changes intended to adapt the experimental question to the setting might actually change the result.
-If there are differences in time, place, or subject population between the two studies, there may need to be differences in the materials, instructions, or procedure to provide a good *translation* -- too many changes could cause differing results, but so could not enough changes.
+Thus, it's very important whether the replication failure was caused by something fixable about the replication or whether it was caused by something not-fixable about the original result (ex.
+extreme lack of generalizability, p-hacking, etc).
 
@@
 An exception might be if a specific error in one study or the other is found, such that the results were not what was thought (analytic error) or the data was not what was thought (experimental error).
+Thus, we usually can't know whether the replication failure was caused by factors that could be feasibly addressed or not.
+
 Re-replication could serve as a way of triangulating on reasons for replication failure, as well as another chance for a scientist to get a working protocol that picks up the effect of interest.
-However, re-replication has not been studied much, so it is uncertain how definitive a replication failure is.
-That is, conditioned on a failed replication, how likely is a re-replication to succeed?
-Re-replication was tested in a sample of 10 psychology studies in @ebersole2020.
-After @openscienceconsortium published their results with a replication rate of TODO, @gilbert2016 raised concerns that methodological differences were the problem.
-In 11 of the OSF studies, concerns about protocol fidelity had been raised by original authors prior to data-collection (and thus not contingent on results).
-Of these 11 with concerns, 10 failed to obtain significant results in the RP:P replication [@openscienceconsortium].
-In a follow-up, @ebersole2020 re-replicated 10 of these 11 in larger samples, using both the RP:P protocol and a new protocol revised under advice of the original authors or other experts, thus testing whether larger sample sizes and/or "better" methodologies would "rescue" the failed RP:P replications.
-The result: 0 of the RP:P protocols found significant results, 2 of the 10 revised protocols did (but not the 1 that had a significant result in the original RP:P sample).
-The replication effect size was much smaller CITE NUMBER [@ebersole2020].
-We could frame @ebersole2020 as an attempt to recover the original effects of the 9 studies with significant original effects and non-significant RP:P effects by a combination of high power and design tweaks.
-This suggests a successful re-replication rate of 2/9 (22%) for studies with non-significant first replications, under fairly favorable, high resource circumstances.
+Thus, scientists may want to know both how often and when a re-replication is likely to work and detect an effect that is indicative that future experiments in this tradition are likely to be informative.
 
-Returning to the question of potential causes of non-replication, what do reasons for replication failure say about the success of another replication?
-For our purposes, we're considering another replication with roughly the same environment, knowledge, and resources of the first replication, but with the benefit of hindsight on the first replication, as this is the situation scientists considering doing a re-replicaton for cumulative science are in.
-
-Factors that suggest another failure include heterogeneity and lack-of-generalizability ("hidden moderator"), as the second replication is likely to be closer to the first replication than to the original in these random factors.
+<!--TODO THIS PARAGRAPH NEEDS HELP Factors that suggest another failure include heterogeneity and lack-of-generalizability ("hidden moderator"), as the second replication is likely to be closer to the first replication than to the original in these random factors.
 TODO CITE THAT PAPER about types of heterogeneity and which way they would fall An original result due to p-hacking or a lucky false positive is unlikely to re-replicate.
@@
 Similarly, if the result is specific to a special population, then a new replication is also likely to fail, unless it has gained access to this population.
-
 Factors that may be fixable include sample size issues with the replication, assuming the re-replication can recruit a larger sample or reduce attrition.
@@
 If a second replication can get closer to the original, either by using closer materials, or better adapting the study to a new environment, the second replication might succeed at better approximating the results of the original.
-A failed manipulation check failure may not be fixable, but it might at least be diagnoseable.
+A failed manipulation check failure may not be fixable, but it might at least be diagnoseable.-->
 
-Overall, there are some potential causes of replication failure that may be resolvable with a similar level of resources, and also some potential causes of replication failure that are not resolvable, either at all, or given resource constraints.
+Re-replication has not been studied much, so it is uncertain how definitive a replication failure is. 
+One study on re-replications was @bersole2020 which re-replicated 10 psychology studies that had failed replications reported in RP:P [@openscienceconsortium]. 
+After  @openscienceconsortium published their results with a replication rate around 40%, @gilbert2016 raised concerns that methodological differences were the reason for the low replication rate.
+In 11 of the OSF studies, concerns about protocol fidelity had been raised by original authors prior to data-collection (and thus not contingent on results).
+Of these 11 with concerns, 10 failed to obtain significant results in the RP:P replication [@openscienceconsortium].
+In a follow-up, @ebersole2020 re-replicated 10 of these 11 in larger samples, using both the RP:P protocol and a new protocol revised under advice of the original authors or other experts, thus testing whether larger sample sizes and/or "better" methodologies would "rescue" the failed RP:P replications.
+
+The result: 0 of the RP:P protocols found significant results, 2 of the 10 revised protocols did (but not the 1 that had a significant result in the original RP:P sample).
+The replication effect size was much smaller CITE NUMBER [@ebersole2020].
+We could frame @ebersole2020 as an attempt to recover the original effects of the 9 studies with significant original effects and non-significant RP:P effects by a combination of high power and design tweaks.
+This suggests a successful re-replication rate of 2/9 (22%) for studies with non-significant first replications, under fairly favorable, high resource circumstances.
 

### 2024-03-20 manuscript/manuscript.Rmd
finish editing pass

@@
 When a replication fails, scientists have to decide whether to make a second attempt or move on.
-Researchers who attempt to replicate studies before building on them often face this decision, given the relatively low rates of replication success in psychology.
+Psychology researchers who attempt to replicate studies before building on them often face this decision, given the relatively low rates of replication success in psychology.
 Here, we report on 17 re-replications of experiments with failed replications reported in Boyce et al.
@@
 :::
-TODO FIX CITATION / BIB INFO
+TODO FIX CITATION / BIB INFO (re OSC for RP:P but only after we unlink from zotero)
+
+TODO compile everything into OSF repo & link
+TODO link individual pre-reg's in repo
+TODO link overall pre-reg
+TODO include in repo & link the reasons for replication failure that were offered to students
+TODO redo/double check closeness scores for first rep and rescues 
+TODO add something about Verity's to case-study? 
+TODO author contributions, acknowledgements
 
@@
 Or perhaps the interaction is numerically in the wrong direction, and also the main effects look different.
-Alternatively the main effect of interest may be null, but you found a significant effect interaction that wasn't hypothesized.
+<!--Or maybe the main effect of interest may be null, but you found a significant effect interaction that wasn't hypothesized.-->
 Whatever the details of the replication failure, you are left with a question: Should you *try again* and run a re-replication, or should you *give up* and pick a different study to replicate and build on?
 
-In psychology, large scale replication projects have tended to find replicability rates around half.
+In psychology, large scale replication projects have found that around half the studies successfully replicate. 
 Across 100 studies with positive results, RP:P replicated 36 - 47% depending on the metric for replication success [@openscienceconsortium].
@@
 @camerer2018 included 21 behavioral social science studies and replicated 12-14 of them (57%-67%) depending on the metric used.
-@boyce2023 reports an average replication score of 49% for 176 replications primary in psychology.
-Psychology is not the only discipline where not everything replicates.
-Large scale replication projects in other disciplines have found 39/97 (40%) for positive effects in cancer biology [@errington2021], 11/18 (61%) in economics [@camerer2016], and 31/40 (78%) for experimental philosophy [@cova2021].
+@boyce2023 reported an average replication score of 49% for 176 replications primary in psychology.
+Psychology is not the only discipline where many studies do not replicate.
+Large scale replication projects in other disciplines have found 39/97 of studies with positive effects (40%) replicating in cancer biology [@errington2021], 11/18 studies (61%) replicating in economics [@camerer2016], and 31/40 studies (78%) replicating in experimental philosophy [@cova2021].
+Across these disciplines, and especially in psychology, large-scale replications indicate a substantial chance of scientists encountering failed replications if they try to replicate published findings.
 
-Replications can fail for any reason.
-In principle, the question of why a replication failed is the same as asking why did two closely related studies have different results, which could be due to any differences between the study.
-In the case of replication failure, there's an asymmetry where the original study happened first and set the methods and analyses and got the more significant result.
-[VB is struggling to articulate ideas here]
-One source of replication failure is that the result is fragile in some way: it could be a statistically unlikely result that was achieved through chance or p-hacking, or it could be sensitive to the exact conditions and time it was run under ("hidden moderators").
-The reported effect sizes might be biased estimates due to some combination of heterogeneity, p-hacking, luck, underpowering, and publication bias.
-The replication study could be underpowered to detect the effect, perhaps due to powering for the reported (inflated) effect size, or unexpected attrition in the replication sample.
+Replications can fail for many reasons.
+In principle, any difference between the original study and replication could be a root cause of the difference in their outcomes.
+In practice, the relationship is not symmetric, and many causes of replication failure can be attributed more to the original study or more to the replication.
+One potential reason for replication failure is that the original result is fragile in some way: it could be a statistically unlikely result that was achieved through chance or p-hacking, or it could be sensitive to the exact conditions and time it was run under ("hidden moderators").
+Another possibility is that the reported effect size might be inflated due to some combination of heterogeneity, p-hacking, low power, and publication bias.
+One consequence of inflated effect sizes is that replication studies might power for the reported effect size and then have too small a sample to reliably detect the (true) smaller effect.
+Replication studies might also end up underpowered due to unexpected attrition or noise in the replication sample.
 
-Replications might get different results from an original study due to differences in how the question of interest was instantiated; these differences in design could be intentional adaptations, or they could be unintentional if a replication recreates instructions or materials because the original ones are not available, or they could be trivial differences that turn out to be crucial to the effect.
+Replications could also get different results from an original study due to differences in how the question of interest was instantiated.
+These differences in design could be intentional adaptations, unavoidable changes from lack of access to the original instructions or materials, or changes that were not expected to be critical.
+A difference in experiment platforms (ex.
+online versus in-person) might mean that an implementation no longer is appropriate, or the data quality controls and attention checks are inadequate.
+If there are differences in time, place, or subject population between the two studies, corresponding changes to the materials, instructions, or procedure may be needed to provide a good *translation* -- too many changes could cause differing results, but so could not enough changes.
 
-A difference in experiment platforms (ex.
-online versus in-person) might mean that an implementation doesn't fit the platform, or the data quality controls and attention checks are inadequate.
-If there are differences in time, place, or subject population between the two studies, there may need to be differences in the materials, instructions, or procedure to provide a good *translation* -- too many changes could cause differing results, but so could not enough changes.
+When replications fail, we generally do not know why they failed, although we may speculate.
+For the metascientific goals of most large-scale replication projects, it doesn't matter why any particular study failed to replicate, because the aim is to estimate the true proportion of effects in a literature.
 
-When replications fail, we generally do not know why they failed, although we often speculate on potential reasons.
-[TODO not sure how to transition here] The goal of most large-scale replication studies has been metascientific, with the aims of estimating the true proportion of effects in a literature or understanding the role of heterogeneity.
-For these purposes, it may not matter exactly why any individual replication failed because they are assessed as a whole.
-
-But when individual scientists attempt to replicate an effect with the goal of building on it, they do care about the individual failed replication.
-In an uncertain literature, we might not want to commit resources to building on an effect without first checking that we, with our resources and participant sample, can get the core effect we wish to build on.
-Thus, it's very important whether the replication failure was caused by something fixable about the replication or whether it was caused by something not-fixable about the original result (ex.
-extreme lack of generalizability, p-hacking, etc).
+In contrast, when individual scientists attempt to replicate an effect with the goal of building on it, they do care about why an individual replication failed.
+In an uncertain literature, scientists might not want to commit resources to building on an effect without first checking that they, with their resources and participant sample, can get the core effect.
+In this case, it's very important whether the replication failure is due to something fixable about the replication or something not-fixable about the original result.
 
@@
 An exception might be if a specific error in one study or the other is found, such that the results were not what was thought (analytic error) or the data was not what was thought (experimental error).
-Thus, we usually can't know whether the replication failure was caused by factors that could be feasibly addressed or not.
+Aside from these rare cases, we usually can't know whether the replication failure is fixable just by looking at the replication failure itself.
 
-Re-replication could serve as a way of triangulating on reasons for replication failure, as well as another chance for a scientist to get a working protocol that picks up the effect of interest.
-Thus, scientists may want to know both how often and when a re-replication is likely to work and detect an effect that is indicative that future experiments in this tradition are likely to be informative.
+Instead, re-replication could serve as a way of triangulating on reasons for re-replication failure, as well as another chance for a scientist to get a working protocol that picks up the effect of interest.
+Thus, scientists may want to know what the chances are that a re-replication succeeds at detecting an effect that indicates future experiments with this protocol are worth pursuing.
 
-<!--TODO THIS PARAGRAPH NEEDS HELP Factors that suggest another failure include heterogeneity and lack-of-generalizability ("hidden moderator"), as the second replication is likely to be closer to the first replication than to the original in these random factors.
-TODO CITE THAT PAPER about types of heterogeneity and which way they would fall An original result due to p-hacking or a lucky false positive is unlikely to re-replicate.
-Sensitivity to environment or not working well online are unlikely to be fixable if the replications remain constrained to using online methods.
-Similarly, if the result is specific to a special population, then a new replication is also likely to fail, unless it has gained access to this population.
-Factors that may be fixable include sample size issues with the replication, assuming the re-replication can recruit a larger sample or reduce attrition.
-It may be possible to fix underpoweredness and inflated effect size, at least to an extent.
-If the effect size was inflated and the first replication powered for the effect, a better powered (but not huge) replication may be able to recover a smaller, but still convincing effect.
-Failures due to differences between the materials may or may not be fixable.
-If the original materials are still unavailable, a second replication is no better off.
-If a second replication can get closer to the original, either by using closer materials, or better adapting the study to a new environment, the second replication might succeed at better approximating the results of the original.
-A failed manipulation check failure may not be fixable, but it might at least be diagnoseable.-->
+Re-replication has not been studied much, so it is uncertain how often re-replications recover the results of an original study.
+That is, it is not well known how definitive a first replication failure is.
 
-Re-replication has not been studied much, so it is uncertain how definitive a replication failure is. 
-One study on re-replications was @bersole2020 which re-replicated 10 psychology studies that had failed replications reported in RP:P [@openscienceconsortium]. 
+One estimate of re-replication success rates comes from @ebersole2020 which re-replicated 10 psychology studies that had failed replications reported in RP:P [@openscienceconsortium]. 
 After @openscienceconsortium published their results with a replication rate around 40%, @gilbert2016 raised concerns that methodological differences were the reason for the low replication rate.
-In 11 of the OSF studies, concerns about protocol fidelity had been raised by original authors prior to data-collection (and thus not contingent on results).
+In 11 of the RP:P studies, the original authors had raised concerns about protocol fidelity prior to data-collection.
 Of these 11 with concerns, 10 failed to obtain significant results in the RP:P replication [@openscienceconsortium].
@@
 
-The result: 0 of the RP:P protocols found significant results, 2 of the 10 revised protocols did (but not the 1 that had a significant result in the original RP:P sample).
-The replication effect size was much smaller CITE NUMBER [@ebersole2020].
+The result was that 0 of the RP:P protocols found significant results, and 2 of the 10 revised protocols did (but not the 1 that had a significant result in the original RP:P sample).
+Even when a significant effect was recovered, the effect size was much diminished [@ebersole2020].
 We could frame @ebersole2020 as an attempt to recover the original effects of the 9 studies with significant original effects and non-significant RP:P effects by a combination of high power and design tweaks.
@@
 
-After a failed replication, we might speculate on what caused the replication result, and what that would mean for future work on the topic.
-As the @gilbert2016 and @ebersole2020 example showed, these speculations on causes and thus re-replication outcomes are not always correct.
+While it is tempting to speculate on the reasons for failed replications, the @gilbert2016 and @ebersole2020 example shows these speculations on causes of replication failure do not always pan out in re-replication outcomes.
 
@@
 On the other hand, early career researchers may also be prone to a different distribution of causes of initial replication failure.
+Thus, it is an open question what the re-replication rate is for failed replications of early career researchers, and estimating this rate could inform decisions on how to act after failed replications.
 
-Here, we investigate re-replication in the context of graduate student replications.
-Students in a graduate methods class on experimental methods were learning about best practices for experimental research.
-One option for their class project was to "rescue" an experiment that a student in a prior year had previously failed to replicate (reported in @boyce2023).
-Thus, students were likely to be looking at both the original paper and the failed replication through the lens of best practices to see what they could fix.
-[TODO Mike mentioned something about a sampling side box on experimentology that VB is having trouble finding]
-
+Here, we investigate re-replication in the context of graduate student replication class projects.
+Students in a graduate methods class on experimental methods were learning about best practices for experimental research and had the option to "rescue" an experiment that a student in a prior year had previously failed to replicate as their class project (first replications reported in @boyce2023).
+Thus, students looked at both the original paper and the failed replication through the lens of best practices to see what potential issues in the replication they could fix. 
 In the present paper, we report the results of `r num_proj` re-replication "rescue" projects which each re-replicated a study which had a failed or only partially-successful replication in @boyce2023.
-TODO PREVIEW RESULTS??
+We find that a minority of projects (5/17, 29%) successful recovered the original effect.
 
@@
 The overall analysis is at LINK, individual pre-registrations are linked from LINK.
-
 We note one deviation from our pre-registration here: we pre-registered visual comparisons between original, first replication, and rescue projects using prediction intervals.
-Prediction intervals depend on both the original effect size and variance CITATION TODO, and also the variance of the comparison (replication or rescue) study.
+Prediction intervals depend on both the original effect size and variance and the variance of the comparison (replication or rescue) study [@patil2016].
 Thus we cannot show *the* prediction interval for the original study, but would have to show a prediction interval between each pair of studies, which we thought would not offer clarity.
@@
 The experiments that were re-replicated were chosen from studies that failed to replicate in @boyce2023.
-We created an initial list of `r nrow(filtered)` rescue-eligible studies that had received a subjective replication success score of 0, .25 or .5 (on a 0-1 scale) in @boyce2023, where the replication had a github repository available (github repositories were used starting in academic year 2015-2016), and where the original experiment had 200 or fewer participants (to ensure we could afford to increase the sample size).
-We then contacted the replication project authors for permission to share their report and github repository with a new student and include it as a supplement on a resulting paper.
+We created an initial list of `r nrow(filtered)` rescue-eligible studies that had received a subjective replication success score of 0, .25 or .5 (on a 0-1 scale) in @boyce2023, where the replication had a Github repository available (github repositories were used starting in academic year 2015-2016), and where the original experiment had 200 or fewer participants (to ensure we could afford to increase the sample size).
+We then contacted the replication project authors for permission to share their report and repository with a new student and include it as a supplement on a resulting paper.
 This left `r length(approved)` options for the students to choose from.
-`r length(chosen)` students chose to do rescue projects.
+`r length(chosen)` students chose to do rescue projects, and
 `r length(chosen)-num_proj` students took an incomplete or did not indicate interest in being part of this paper, leaving a final sample of `r num_proj` rescue projects.
@@
 In general, we encouraged students to add manipulation checks as appropriate, and better adapt materials to online studies.
-For instance, the rescue of @paxton2012 switched from using the CRT which is overused in online samples for the newer TODO.
+For instance, the rescue of @paxton2012 switched from using the CRT which many online participants are overfamiliar with for the newer CRT-2 which is less overused but gets at the same construct [@thomson2016].
 The rescue of @jara-ettinger2022 discovered that the replication had accidentally used the drawn version of the stimuli rather than the photographic stimuli used in the original and reverted to the photographic stimuli.
-@tarampi2016 original had participants indicate their answers (left or right) on a piece of paper in a timed navigation task, the replication had them indicate by clicking a drop down, and rescue went with pressing keyboard keys to indicate the direction of the a turn.
-TODO others to note?
+@tarampi2016 had participants do a timed navigation task where they wrote L or R to indicate which way to turn at each intersection on a paper map.
+The replication ported this experiment online and had participants click a drop down to select left or write for each turn.
+The rescue switched for the unwieldy dropdown menus to having participants press keys on the keyboard to indicate the direction of a turn, which seemed like a more natural interface.
 Once students experimental designs and analytic plans were approved by TAs (VB and BP), students pre-registered and ran their samples.
@@
 Disagreements were resolved through discussion.
-As a compliment to the subjective rating of overall success, we stastically compared one key measure of interest for each study, following @boyce2023.
+As a complement to the subjective rating of overall success, we statistically compared one key measure of interest for each study, following @boyce2023.
 In order to statistically compare the key measures, we needed effect sizes reported in the same way for each original study, first replication, and rescue.
@@
 
-We also recorded the same set of potential correlates that were used in @boyce2023 for original, first replication, and rescue (these were already rated for original and first replication).
+We recorded the same set of potential correlates that were used in @boyce2023 for original, first replication, and rescue (these were already rated for original and first replication).
 These potential correlates included the subfield of the study (cognitive, social, or other psychology), its publication year, experimental design features including whether it was a within- or between- subject design, whether each condition was instantiated with one vignette or multiple, how many items each participant saw, and whether there were open materials and open data.
@@
 For the original study and each replication, we recorded the number of participants post-exclusions.
-For studies where some extra conditions were dropped, we count only the participants in the key conditions all replications had for comparability.
-For instance, if an original study compared between two critical conditions but also had a baseline control, we would not count the participants in the baseline condition if a replication did not include this condition.
-We also recorded whether each study was conducted online with a crowdsourced platform or not.
+For studies where some extra conditions were dropped in some replications, we counted only the participants in the key conditions all replications had for comparability.
+For instance, if an original study compared between two critical conditions but also had a baseline control, we did not count the participants in the baseline condition if a replication did not include this condition.
+We also recorded whether each study was conducted online using crowd-sourced platform or not.
 
@@
 
-Our primary question of interest is how many of these `r num_proj` rescue projects succeeded at replicating the results in the original study.
+Our primary question of interest was how many of the `r num_proj` rescue projects succeeded at replicating the results in the original study.
 When a replication fails to obtain the same results, one may have intuitions about what may have gone wrong -- these rescue projects test how often addressing these potential issues in fact works.
@@
 received a subjective replication score of .75 or 1).
-Note that @boyce2023 report the average replication score as a percent success (49%), but given that we considered studies with a subjective score of .5 as eligible to be rescued, we recomputed the success rate when scores of 0-.5 as failures and .75 and 1 as successes.
+Note that @boyce2023 report the average replication score as a percent success (49%), but given that we considered studies with a subjective score of .5 as eligible to be rescued, we recomputed the success rate where scores of 0, .25, and .5 are considered failures and .75 and 1 successes.
 If the re-replication rate in our sample is representative of the re-replication rate for the initially non-replicating studies, then the combined chance of mostly or fully replicating in a first replication or one follow-up replication is `r round(overall*100)`%.
@@
 
-[TODO Ben: I think the paragraph below could use more explanation about what $p$-original is, but I'm not confident enough in my understanding of it to write it myself.]
+Here, we measure statistical consistency using $p$-original, the $p$-value on the null hypothesis that one study's population effect comes from the same distribution of population effects as another study or studies [@mathurNewStatisticalMetrics2020a] If we assume no heterogeneity between studies, then this is the same as asking how consistent one study's estimate of the population-level effect is with another study's estimate of the population-level effect.
+However, meta-analyses of closely related studies, such as those from different sites of multi-site replications, indicate that there is often heterogeneity between studies.
+We cannot accurately estimate the level of heterogeneity for an effect meta-analytically as we have only a small number of replications per study.
+Instead, we impute a heterogeneity value of $\tau=.21$ SMD, which is the average level of heterogeneity found by @olsson-collentine2020 in prior multi-site replications in psychology.
 
-Here, we measure statistical consistency using $p$-original, the $p$-value on the null hypothesis that two effects come from the same distribution.
 As our primary comparison, we compare the effect size of the original study to the meta-analytic effect of the totality of the replications (first replication, rescue, and additional if found).
-Because there is only a small number of replications per study, we impute the heterogeneity value of $\tau=.21$ SMD, which is the average level of heterogeneity found by @olsson-collentine2020 in prior multi-site replications in psychology.
-
-[ query: should we bootstrap any of the following?
-]
+The value of $p$-original thus represents how likely an effect size equal to or more extreme than the original effect size is to occur if it comes from a distribution of population effect sizes defined by the mean and standard error of the replications (combined meta-analytically) with a between-population standard deviation of $\tau=.21$.
+That is, it $p$-original is a measure of the statistical consistency of the original result with the totality of the replications, assuming a given level of heterogeneity of effects between studies.
+Smaller $p$-original values indicate more inconsistency.
 
 The median value of $p$-original between an original study and its replications was `r main_summ$median |> round(2)` [IQR: `r main_summ$low |> round(2)` - `r main_summ$high |> round(2)`].
-`r round(main_summ$less_than*100)`% of the $p$-original values were less than .05, indicating by conventional thresholds a rejection of the null hypothesis that the original and the replications came from the same distribution for the given imputed level of heterogeneity.
+`r round(main_summ$less_than*100)`% of the $p$-original values were less than .05, indicating by conventional thresholds a rejection of the null hypothesis that the original comes from the same distribution of population effects as the replications.
 Individual $p$-original values for each study are shown in Table \@ref(tab:tab-porig).
@@
 As secondary measures, we calculated the $p$-original values between a) the original and the rescue, b) the original and non-rescue replications, and c) the rescue and other replications. 
-For a) the rescue versus the original, median value of $p$-original was `r rescue_summ$median |> round(2)` [IQR: `r rescue_summ$low |> round(2)` - `r rescue_summ$high|> round(2)`], and `r round(rescue_summ$less_than*100)`% of the $p$-original values were less than .05.
-For b) the non-rescue replications versus the original, median value of $p$-original was `r rep_summ$median |> round(2)` [IQR: `r rep_summ$low |> round(2)` - `r rep_summ$high |> round(2)`], and `r round(rep_summ$less_than*100)`% of the $p$-original values were less than .05.
+For a) the original versus the rescue, median value of $p$-original was `r rescue_summ$median |> round(2)` [IQR: `r rescue_summ$low |> round(2)` - `r rescue_summ$high|> round(2)`], and `r round(rescue_summ$less_than*100)`% of the $p$-original values were less than .05.
+For b) the original versus all the non-rescue replications, median value of $p$-original was `r rep_summ$median |> round(2)` [IQR: `r rep_summ$low |> round(2)` - `r rep_summ$high |> round(2)`], and `r round(rep_summ$less_than*100)`% of the $p$-original values were less than .05.
 For c) the rescue versus the other replications, median value of $p$-original was `r rescue_rep_summ$median |> round(2)` [IQR: `r rescue_rep_summ$low |> round(2)` - `r rescue_rep_summ$high |> round(2)`], and `r round(rescue_rep_summ$less_than*100)`% of the $p$-original values were less than .05.
@@
 
-Overall, allowing for a heterogeneity level of $\tau$=.21 SMD, a number of rescues and replications are not statistically consistent with the original effects.
+Overall, allowing for a heterogeneity level of $\tau$=.21 SMD, a number of original effects are not statistically consistent with rescues and replication effects. 
 The pattern of inconsistency does not align with which studies were rated as having replicated.
@@
 
-We ran correlations between the set of predictor variables used in @boyce2023 and the subjective replication scores of the rescues.
-We also added some (non-preregistered) predictors related to the sample size of the first replication, after seeing the successful re-replications of @ngo2019 and @krauss2003, both studies with small replication samples.
+Are there signals in the features of a study or it's replication that predict whether a re-replication will succeed?
+To address this question, we ran correlations between the set of predictor variables used in @boyce2023 and the subjective replication scores of the rescues.
+We also added some (non-preregistered) predictors related to the sample size of the first replication, after seeing the successful re-replications of @ngo2019 and @krauss2003, both of which had small replication samples.
 
-All of the correlations are presented in Figure \@ref(tab:cor-table).
-As the number of rescues is small, and many of these predictors are correlated, we caution against over-interpretation.
+The number of rescues is small, and many of these predictors are correlated, so we caution against over interpretation. All of the correlations are presented in Figure \@ref(tab:cor-table).
 The strongest correlates of rescue success were open materials, a small sample size on the first replication, a small sample size on the first replication relative to the original sample size, and a large rescue sample size relative to the first replication.
@@
 In the rescue projects, we aimed to have methods be as close as was feasible or appropriate.
-(As discussed above, changes in time, population, or setting may necessitate adaptation of a study to maximize fidelity.) However, rescue projects varied in how close the re-replications actually were, often due to limitations in the availability of original stimuli and original instructions, in addition to the use of primarily online subject pools.
+However, rescue projects varied in how close the re-replications actually were, often due to limitations in the availability of original stimuli and original instructions, in addition to the use of primarily online subject pools.
 Table \@ref(tab:tab-size) shows the closeness of each first replication and rescue according to the classification scheme from @lebel2018.
@@
 
-# Case studies
+## Case studies
 
@@
 The rescue, powered using 2.5x the original sample (as recommended by @simonsohn2015), recovered a clear effect (albeit a much smaller one).
-There are reasons to think that some effect sizes in the literature may be inflated TODO CITATIONS, and separate reasons that slight changes to experiments or switches to online could result in noisier samples and thus smaller effect sizes.
+There are reasons to think that some effect sizes in the literature may be inflated [@openscienceconsortium, @camerer2018], and it is also possible that changes to experiments or switches to online could result in noisier samples and thus smaller effect sizes.
 Therefore, replications with smaller samples than the original (even if powered to the original effect size), may not be very diagnostic, and could potentially benefit from a re-replication.
@@
 
-(could discuss tarampi as an example where there were potential issues, we fixed them and it still didn't work?)
-
 # Discussion
@@
 The rescues all showed smaller effect sizes than their original studies, regardless of whether the pattern of effects replicated.
-A large minority of replications had effect sizes that were statistically inconsistent with the original effect, even allowing for some heterogeneity between studies.
+A large minority of replications had effect sizes that were statistically inconsistent with the original effect, even accounting for expected levels of heterogeneity between studies.
 These diminished and inconsistent effects suggest that even if a re-replication "works", it may be difficult to build upon as follow-up studies will need large samples to detect small effects.
@@
 That said, it is possible that different results might be obtained in better-resourced settings, by scientists with more expertise and more time.
-Thus, we do not make statements about whether the original results are "true" or "false-positives", we merely claim they do not support cumulative research by early-career researchers under the constrained conditions we tested.
+Thus, where re-replications failed, we do not make any statements about whether the original results were false positives, we merely claim the original results do not support cumulative research by early-career researchers under the constrained conditions we tested.
 
-We opened this paper with a question about what an early-career psychology researcher should do given a failed replication: should they try again or move on?
-From our sample of testing the "try again" approach, it seems that the odds of a re-replication working are low (consistent with @ebersole2020).
-Especially if there is not a clear, identifiable reason for the first replication's failure, another try is unlikely to recover the original result.
+We opened this paper with a question about what an early-career psychology researcher should do given a failed replication: should they *try again* or *give up* and move on?
+From our sample of testing the *try again* approach, it seems that the odds of a re-replication working are low (consistent with @ebersole2020).
+Especially if there is not a clear, identifiable reason for the first replication's failure, another try is unlikely to recover the original result, and it may be more efficient to *give up* and build on a different result instead.
 
@@
 
+TODO
+
 # Author Contributions {.unnumbered}
+
+TODO
 

### 2024-03-21 manuscript/manuscript.Rmd
added paragraph on Verity's project and extra sentence about p-original

@@
 Psychology researchers who attempt to replicate studies before building on them often face this decision, given the relatively low rates of replication success in psychology.
-Here, we report on 17 re-replications of experiments with failed replications reported in Boyce et al.
-(2023).
+Here, we report on 17 re-replications of experiments with failed replications reported in Boyce et al. (2023).
 In 5/17 of these "rescue" projects (29%), the re-replication mostly or fully replicated the original results, albeit with smaller effect sizes.
@@
 :::
+
 TODO FIX CITATION / BIB INFO (re OSC for RP:P but only after we unlink from zotero)
 
-TODO compile everything into OSF repo & link
-TODO link individual pre-reg's in repo
-TODO link overall pre-reg
-TODO include in repo & link the reasons for replication failure that were offered to students
-TODO redo/double check closeness scores for first rep and rescues 
-TODO add something about Verity's to case-study? 
+TODO compile everything into OSF repo & link TODO link individual pre-reg's in repo TODO link overall pre-reg TODO include in repo & link the reasons for replication failure that were offered to students TODO redo/double check closeness scores for first rep and rescues TODO add something about Verity's to case-study?
 TODO author contributions, acknowledgements
@@
 Or perhaps the interaction is numerically in the wrong direction, and also the main effects look different.
-<!--Or maybe the main effect of interest may be null, but you found a significant effect interaction that wasn't hypothesized.-->
-Whatever the details of the replication failure, you are left with a question: Should you *try again* and run a re-replication, or should you *give up* and pick a different study to replicate and build on?
+<!--Or maybe the main effect of interest may be null, but you found a significant effect interaction that wasn't hypothesized.--> Whatever the details of the replication failure, you are left with a question: Should you *try again* and run a re-replication, or should you *give up* and pick a different study to replicate and build on?
 
@@
 These differences in design could be intentional adaptations, unavoidable changes from lack of access to the original instructions or materials, or changes that were not expected to be critical.
-A difference in experiment platforms (ex.
-online versus in-person) might mean that an implementation no longer is appropriate, or the data quality controls and attention checks are inadequate.
+A difference in experiment platforms (ex. online versus in-person) might mean that an implementation no longer is appropriate, or the data quality controls and attention checks are inadequate.
 If there are differences in time, place, or subject population between the two studies, corresponding changes to the materials, instructions, or procedure may be needed to provide a good *translation* -- too many changes could cause differing results, but so could not enough changes.
@@
 This left `r length(approved)` options for the students to choose from.
-`r length(chosen)` students chose to do rescue projects, and
-`r length(chosen)-num_proj` students took an incomplete or did not indicate interest in being part of this paper, leaving a final sample of `r num_proj` rescue projects.
+`r length(chosen)` students chose to do rescue projects, and `r length(chosen)-num_proj` students took an incomplete or did not indicate interest in being part of this paper, leaving a final sample of `r num_proj` rescue projects.
 
@@
 However, meta-analyses of closely related studies, such as those from different sites of multi-site replications, indicate that there is often heterogeneity between studies.
+$p$-original allows for such heterogeneity, as governed by a parameter $\tau$.
 We cannot accurately estimate the level of heterogeneity for an effect meta-analytically as we have only a small number of replications per study.
@@
 
-The number of rescues is small, and many of these predictors are correlated, so we caution against over interpretation. All of the correlations are presented in Figure \@ref(tab:cor-table).
+The number of rescues is small, and many of these predictors are correlated, so we caution against over interpretation.
+All of the correlations are presented in Figure \@ref(tab:cor-table).
 The strongest correlates of rescue success were open materials, a small sample size on the first replication, a small sample size on the first replication relative to the original sample size, and a large rescue sample size relative to the first replication.
@@
 
-(TODO other successes or failures we want to discuss?
-) (Ben: Emily's project was interesting: the rescue succeeded but with big stimulus-level random effects.
-Verity's project was also interesting: the previous replication, as well as another in the literature, showed similar but smaller findings and it really looked like she could get the effect with a bigger sample, but she ended up finding totally different results.)
+\@child2018 studied reading times for passages of text with different emotional valences written from either a third-person or second-person perspective.
+They found a significant interaction between perspective and valence: participants read positively-valenced passages faster than negatively-valenced passages, but only when they were written from a second-person perspective.
+The first replication used a similar sample size to the original study (40) and found an effect that trended in the same direction, but was substantially smaller.
+The rescuer identified several possible reasons for this failure, foremost among them that the replication was conducted online while the original was conducted in person.
+It is reasonable to expect online studies of reading time to be noisier than in-person studies because the environments participants completed the study in varied much more online.
+The rescue attempt was still online, but used a much larger sample size to account for noisier data.
+Still, the rescue found a non-significant effect that trended in the opposite direction from the original and first replication.
+Even though the first replication trended in the same direction and there was an identifiable reason for the smaller effect size, increasing sample size did not rescue the effect.
 

### 2024-03-25 manuscript/manuscript.Rmd
mcf pass

--- 2024-03-20 manuscript/manuscript.Rmd
@@
 When a replication fails, scientists have to decide whether to make a second attempt or move on.
-Psychology researchers who attempt to replicate studies before building on them often face this decision, given the relatively low rates of replication success in psychology.
-Here, we report on 17 re-replications of experiments with failed replications reported in Boyce et al.
-(2023).
-In 5/17 of these "rescue" projects (29%), the re-replication mostly or fully replicated the original results, albeit with smaller effect sizes.
-While a few replications were rescued with larger sample sizes and minor methodological changes, most re-replications failed again.
-In many situations, it may be most efficient to stop pursuing an effect after a single failed replication.
+Psychology researchers who attempt to replicate studies often face this decision, given the empirical rate of replication success in psychology, which is lower than desired.
+Here, we report 17 re-replications of experiments for which an original replication had failed.
+In 5/17 of these "rescue" projects (29%), the "rescue" study mostly or fully replicated the original results, albeit with a smaller effect size; in the other 12, the second replication was also judged to have failed.
+We speculate that successful rescue projects were due to larger sample sizes or methodological changes such as attention checks.
+In the absence of obvious weaknesses in a failed replication study's sample or procedure, however, it may be most efficient to stop pursuing an effect after a single failed replication.
 :::
-TODO FIX CITATION / BIB INFO (re OSC for RP:P but only after we unlink from zotero)
+<!-- TODO FIX CITATION / BIB INFO (re OSC for RP:P but only after we unlink from zotero) -->
 
-TODO compile everything into OSF repo & link
-TODO link individual pre-reg's in repo
-TODO link overall pre-reg
-TODO include in repo & link the reasons for replication failure that were offered to students
-TODO redo/double check closeness scores for first rep and rescues 
-TODO add something about Verity's to case-study? 
-TODO author contributions, acknowledgements
+<!-- TODO compile everything into OSF repo & link -->
+<!-- TODO link individual pre-reg's in repo -->
+<!-- TODO link overall pre-reg -->
+<!-- TODO include in repo & link the reasons for replication failure that were offered to students -->
+<!-- TODO redo/double check closeness scores for first rep and rescues  -->
+<!-- TODO add something about Verity's to case-study?  -->
+<!-- TODO author contributions, acknowledgements -->
 
@@
 
-Imagine the scenario where you are a new graduate student, and you run a replication of a study in the literature that you are interested in building upon in your research.
-The replication fails: perhaps the interaction you hoped for is directionally correct, but the point estimate is small and the confidence interval definitely overlaps 0, with a p-value of .3.
-Or perhaps the interaction is numerically in the wrong direction, and also the main effects look different.
+Imagine you are a graduate student, and you run a replication of a study that you are interested in building upon in your research.
+The replication fails. Perhaps the interaction you hoped for is directionally correct, but the point estimate is small and the confidence interval definitely overlaps 0, with a $p$-value of .3.
+Or perhaps the interaction is numerically in the wrong direction and the main effects look different.
 <!--Or maybe the main effect of interest may be null, but you found a significant effect interaction that wasn't hypothesized.-->
-Whatever the details of the replication failure, you are left with a question: Should you *try again* and run a re-replication, or should you *give up* and pick a different study to replicate and build on?
+Whatever the details of the replication failure, you are left with a question: Should you try again and run a re-replication, or should you give up and pick a different study to extend?
 
-In psychology, large scale replication projects have found that around half the studies successfully replicate. 
-Across 100 studies with positive results, RP:P replicated 36 - 47% depending on the metric for replication success [@openscienceconsortium].
+In psychology, large scale replication projects have found that around half of studies successfully replicate. 
+Across 100 studies with positive results, the reproducibility project in psychology (RP:P) replicated 36 - 47% depending on the metric for replication success [@openscienceconsortium].
 With large multi-site samples, Many Labs 1 replicated 11/13 effects (84.6%), Many Labs 2 replicated 14/28 effects (50%), and Many Labs 3 replicated 3/10 effects (30%) [@klein2014; @klein2018; @ebersole2016].
-@camerer2018 included 21 behavioral social science studies and replicated 12-14 of them (57%-67%) depending on the metric used.
-@boyce2023 reported an average replication score of 49% for 176 replications primary in psychology.
+@camerer2018 examined 21 behavioral social science studies and successfully replicated 12-14 of them (57%-67%) depending on the metric used.
+@boyce2023 reported an average subjective replication score of 49% for 176 replications primary in psychology.
+
 Psychology is not the only discipline where many studies do not replicate.
@@
 
-Replications can fail for many reasons.
-In principle, any difference between the original study and replication could be a root cause of the difference in their outcomes.
-In practice, the relationship is not symmetric, and many causes of replication failure can be attributed more to the original study or more to the replication.
-One potential reason for replication failure is that the original result is fragile in some way: it could be a statistically unlikely result that was achieved through chance or p-hacking, or it could be sensitive to the exact conditions and time it was run under ("hidden moderators").
-Another possibility is that the reported effect size might be inflated due to some combination of heterogeneity, p-hacking, low power, and publication bias.
-One consequence of inflated effect sizes is that replication studies might power for the reported effect size and then have too small a sample to reliably detect the (true) smaller effect.
+Replications can fail for many reasons, having to do with the original study or the replication. 
+<!-- In principle, any difference between the original study and replication could be a root cause of the difference in their outcomes.
+But in practice, the relationship between original and replication is not symmetric, and many causes of replication failure can be attributed either more to the original study or more to the replication.
+-->
+Starting with the original study, one potential reason for replication failure is that the original result is fragile in some way.
+It could be a statistically unlikely result that was achieved through chance or $p$-hacking, or it could be sensitive to the exact conditions and time it was run under ("hidden moderators").
+Another possibility is that the original reported effect size might be inflated due to some combination of heterogeneity, $p$-hacking, low power, and publication bias.
+A consequence of inflated effect sizes is that replication studies might select a sample size with appropriate sttaistical power for the reported effect size and then have too small a sample to reliably detect the (true) smaller effect.
 Replication studies might also end up underpowered due to unexpected attrition or noise in the replication sample.
 
-Replications could also get different results from an original study due to differences in how the question of interest was instantiated.
+Other reasons for replication failure are also primarily due to the replication study. 
+A replication could observe different results from the original due to methodological differences. 
 These differences in design could be intentional adaptations, unavoidable changes from lack of access to the original instructions or materials, or changes that were not expected to be critical. 
-A difference in experiment platforms (ex.
-online versus in-person) might mean that an implementation no longer is appropriate, or the data quality controls and attention checks are inadequate.
-If there are differences in time, place, or subject population between the two studies, corresponding changes to the materials, instructions, or procedure may be needed to provide a good *translation* -- too many changes could cause differing results, but so could not enough changes.
+A difference in the details of recruitment (e.g., online versus in-person) might mean that particular details of a study implementation would no longer be appropriate, or the data quality controls and attention checks might be inadequate.
+If there are differences in time, place, or subject population between the two studies, corresponding changes to the materials, instructions, or procedure could be needed to provide an adaptation of the experimental paradigm to a new context.
+Such adaptation creates yet more challenges in interpretation: too many changes could cause differing results, but so could not enough changes. 
+In sum, when replications fail, we generally do not know why they failed, although we may speculate.
 
-When replications fail, we generally do not know why they failed, although we may speculate.
-For the metascientific goals of most large-scale replication projects, it doesn't matter why any particular study failed to replicate, because the aim is to estimate the true proportion of effects in a literature.
+For the goals of large-scale replication projects, it doesn't matter why any particular study failed to replicate, because the aim is to estimate the proportion of replication effects in a literature.
+In contrast, howver, when individual scientists attempt to replicate an effect with the goal of building on it, they do care about why an individual replication failed.
+In an uncertain literature, scientists might not want to commit resources to studying extensions of an effect without first checking that they can measure that effect themselves.
+For those individual scientists, it is much more important whether the replication failure is due to a fixable issue with the the replication or an intrinsic feature of the original result.
 
-In contrast, when individual scientists attempt to replicate an effect with the goal of building on it, they do care about why an individual replication failed.
-In an uncertain literature, scientists might not want to commit resources to building on an effect without first checking that they, with their resources and participant sample, can get the core effect.
-In this case, it's very important whether the replication failure is due to something fixable about the replication or something not-fixable about the original result.
+Re-replication can serve as a way to test explanations for replication failure.
+While it's possible to speculate after the fact about potential causes of a single replication failure, in most circumstances these causes are hard to discern (absent clear evidence of errors).
+In contrast, a second replication provides a chance to test explanations by making modifications -- as well as giving another chance for researchers to measure an effect of interest.
+But what are the chances that a re-replication succeeds?
 
-While one can theorize after the fact about potential causes of replication failure, in most circumstances it is hard to diagnose for certain what made for the difference in the results.
+<!-- is hard to diagnose for certain what made for the difference in the results.
 An exception might be if a specific error in one study or the other is found, such that the results were not what was thought (analytic error) or the data was not what was thought (experimental error).
 Aside from these rare cases, we usually can't know whether the replication failure is fixable just by looking at the replication failure itself.
+-->
 
-Instead, re-replication could serve as a way of triangulating on reasons for re-replication failure, as well as another chance for a scientist to get a working protocol that picks up the effect of interest.
-Thus, scientists may want to know what the chances are that a re-replication succeeds at detecting an effect that indicates future experiments with this protocol are worth pursuing.
+<!-- Re-replication has not been studied much, so it is uncertain how often re-replications recover the results of an original study.
+That is, it is not well known how definitive a first replication failure is.
+-->
+Relatively few studies have estimated re-replication success. 
+One estimate comes from @ebersole2020.
+After the original RP:P result of a replication rate around 40% [@openscienceconsortium], @gilbert2016 raised concerns that methodological differences might explain low replication rate.
+In 11 of the RP:P studies, the original authors had raised concerns about protocol fidelity prior to data-collection.
+Of these 11 with concerns, 10 failed to obtain significant results in the RP:P replication. 
+Thus, @ebersole2020 re-replicated 10 of these 11 in larger samples, using both the RP:P protocol and a new protocol revised under advice of the original authors or other experts.
+This study thus tested whether larger sample sizes and/or "better" methodologies would "rescue" the failed RP:P replications.
+The result was that 2 of the 10 revised protocols found a significant result (but not the 1/11 that originally was successful).
+Even when a significant effect was recovered, the effect size was much diminished [@ebersole2020].
+<!-- We could frame @ebersole2020 as an attempt to recover the original effects of the 9 studies with significant original effects and non-significant RP:P effects by a combination of high power and design tweaks.
+-->
+The re-replication success rate was thus 2/9 (22%) for studies with non-significant first replications, under favorable, high-resource circumstances.
 
-Re-replication has not been studied much, so it is uncertain how often re-replications recover the results of an original study.
-That is, it is not well known how definitive a first replication failure is.
-
-One estimate of re-replication success rates comes from @ebersole2020 which re-replicated 10 psychology studies that had failed replications reported in RP:P [@openscienceconsortium]. 
-After @openscienceconsortium published their results with a replication rate around 40%, @gilbert2016 raised concerns that methodological differences were the reason for the low replication rate.
-In 11 of the RP:P studies, the original authors had raised concerns about protocol fidelity prior to data-collection.
-Of these 11 with concerns, 10 failed to obtain significant results in the RP:P replication [@openscienceconsortium].
-In a follow-up, @ebersole2020 re-replicated 10 of these 11 in larger samples, using both the RP:P protocol and a new protocol revised under advice of the original authors or other experts, thus testing whether larger sample sizes and/or "better" methodologies would "rescue" the failed RP:P replications.
-
-The result was that 0 of the RP:P protocols found significant results, and 2 of the 10 revised protocols did (but not the 1 that had a significant result in the original RP:P sample).
-Even when a significant effect was recovered, the effect size was much diminished [@ebersole2020].
-We could frame @ebersole2020 as an attempt to recover the original effects of the 9 studies with significant original effects and non-significant RP:P effects by a combination of high power and design tweaks.
-This suggests a successful re-replication rate of 2/9 (22%) for studies with non-significant first replications, under fairly favorable, high resource circumstances.
-
-While it is tempting to speculate on the reasons for failed replications, the @gilbert2016 and @ebersole2020 example shows these speculations on causes of replication failure do not always pan out in re-replication outcomes.
+<!-- While it is tempting to speculate on the reasons for failed replications, the @gilbert2016 and @ebersole2020 example shows these speculations on causes of replication failure do not always pan out in re-replication outcomes.
+-->
 
@@
 On the other hand, early career researchers may also be prone to a different distribution of causes of initial replication failure.
-Thus, it is an open question what the re-replication rate is for failed replications of early career researchers, and estimating this rate could inform decisions on how to act after failed replications.
+Thus, it is an open question what the re-replication rate is for failed replications of early career researchers.
+Further, estimating this rate could inform researhcers' decisions on what to do next after failed replications.
 
 Here, we investigate re-replication in the context of graduate student replication class projects.
-Students in a graduate methods class on experimental methods were learning about best practices for experimental research and had the option to "rescue" an experiment that a student in a prior year had previously failed to replicate as their class project (first replications reported in @boyce2023).
-Thus, students looked at both the original paper and the failed replication through the lens of best practices to see what potential issues in the replication they could fix. 
-In the present paper, we report the results of `r num_proj` re-replication "rescue" projects which each re-replicated a study which had a failed or only partially-successful replication in @boyce2023.
-We find that a minority of projects (5/17, 29%) successful recovered the original effect.
+Students in a graduate methods class on experimental methods in psychology were given the option to "rescue" an experiment that a student in a prior year had previously failed to replicate as their class project [first replications reported in @boyce2023].
+The focus of the class was best practices in experimental design; thus, students looked at both the original paper and the failed replication to examine potential issues in the replication that they could fix in their rescue project.
+In the present paper, we report the results of `r num_proj` re-replication rescue projects. We find that a minority of projects (5/17, 29%) successful recovered the original effect.
 
@@
 PSYCH 251 is a graduate-level experimental methods class taught by MCF.
-In previous years, students have conducted replication projects, as reported in @boyce2023.
-In Fall 2023, students in PSYCH 251 were offered the option to do a "rescue" project where they re-replicated one of the unsuccessful replications from a previous year.
+In previous years, students have conducted replication projects [as reported in @boyce2023 and @hawkins2018].
+In Fall 2023, students were offered the option to complete a "rescue" project where they re-replicated one of the unsuccessful replications from a previous year.
 Students could also opt to do a normal replication instead.
+If they opted for a rescue, they were given the option to participate in a collaborative meta-science project and earn authorship on the current paper based on 1) completing a rescue project, 2) reviewing another student's rescue project for analytic errors, and 3) reviewing and approving the final manuscript.
 We report on the result of `r num_proj` rescue projects that opted to be part of the paper and completed data collection.
@@
 Prediction intervals depend on both the original effect size and variance and the variance of the comparison (replication or rescue) study [@patil2016].
-Thus we cannot show *the* prediction interval for the original study, but would have to show a prediction interval between each pair of studies, which we thought would not offer clarity.
+Thus we cannot show a single prediction interval for the original study, but would have to show a prediction interval between each pair of studies.
+We thought this analysis would not offer additional clarity and hence we did not perform it.
 
@@
 The experiments that were re-replicated were chosen from studies that failed to replicate in @boyce2023.
-We created an initial list of `r nrow(filtered)` rescue-eligible studies that had received a subjective replication success score of 0, .25 or .5 (on a 0-1 scale) in @boyce2023, where the replication had a Github repository available (github repositories were used starting in academic year 2015-2016), and where the original experiment had 200 or fewer participants (to ensure we could afford to increase the sample size).
+We created an initial list of `r nrow(filtered)` rescue-eligible studies that 1) had received a subjective replication success score of 0, .25 or .5 (on a 0--1 scale) in @boyce2023, 2) had a Github repository available (github repositories were used in class starting in academic year 2015-2016), and 3) where the original experiment had 200 or fewer participants (to ensure we could afford to match or increase the sample size based on the class budget).
 We then contacted the replication project authors for permission to share their report and repository with a new student and include it as a supplement on a resulting paper.
@@
 `r length(chosen)` students chose to do rescue projects, and
-`r length(chosen)-num_proj` students took an incomplete or did not indicate interest in being part of this paper, leaving a final sample of `r num_proj` rescue projects.
+`r length(chosen)-num_proj` students did not finish their project or did not indicate interest in being part of this paper, leaving a final sample of `r num_proj` rescue projects.
 
@@
 A list of possible reasons and solutions TODO LINK was given to students.
-In general, we encouraged students to add manipulation checks as appropriate, and better adapt materials to online studies.
-For instance, the rescue of @paxton2012 switched from using the CRT which many online participants are overfamiliar with for the newer CRT-2 which is less overused but gets at the same construct [@thomson2016].
-The rescue of @jara-ettinger2022 discovered that the replication had accidentally used the drawn version of the stimuli rather than the photographic stimuli used in the original and reverted to the photographic stimuli.
+In general, we encouraged students to add manipulation checks as appropriate, and to adapt their materials to online studies, which may benefit from attention checks and/or shorter duration.
+For instance, the rescue of @paxton2012 switched from using the cognitive reflection task (CRT) which many online participants are over-familiar with for the newer CRT-2 which is less overused but attempts to measure the same construct [@thomson2016].
+The rescue of @jara-ettinger2022 discovered that the replication had accidentally used an illustrated version of the stimuli rather than the photographic stimuli used in the original and used the photographic stimuli instead.
 @tarampi2016 had participants do a timed navigation task where they wrote L or R to indicate which way to turn at each intersection on a paper map.
-The replication ported this experiment online and had participants click a drop down to select left or write for each turn.
-The rescue switched for the unwieldy dropdown menus to having participants press keys on the keyboard to indicate the direction of a turn, which seemed like a more natural interface.
-Once students experimental designs and analytic plans were approved by TAs (VB and BP), students pre-registered and ran their samples.
+The replication ported this experiment online and had participants click a drop down menu to select left or write for each turn.
+The rescue removed the unwieldy dropdown menus and opted to have participants press keys on the keyboard to indicate the direction of a turn, which seemed like a more natural interface.
+Once experimental designs and analytic plans were approved by class TAs (VB and BP), students pre-registered and ran their samples.
 
-With one exception, samples were collected on Prolific (the rescue of @yeshurun2003 ran in-person on the Stanford student subject pool).
-We tried to power studies adequately (with a target of 2.5x original following @simonsohn2015), but due to cost constraints, not all studies were powered at this level.
+With one exception, samples were collected on Prolific [the rescue of @yeshurun2003 ran in-person on the Stanford student subject pool].
+We tried to power studies adequately [with a target of 2.5x original following @simonsohn2015], but due to cost constraints, not all studies were powered at this level.
 The rescues had on average `r round(m,2)` times the original sample post-exclusion (median: `r round(mid,2)`, IQR: `r round(low,2)` - `r round(high,2)`, minimum: `r round(lowest, 2)`, maximum: `r round(highest,2)`, see Table \@ref(tab:tab-size) for all sample sizes).
@@
 We followed @boyce2023 in the properties of the studies we measure and how we quantify replication success. 
+Each project was rated on the basis of subjective replication success (on a 0--1 scale) by both MCF and one of VB and BP.
+We thought about replication in terms of general match in key study results (direction, magnitude, and significance), rather than focusing on any singular numeric result or significance cut-off.
+Interrater reliability was `r irr |> round(3)`; disagreements were minor (at no point greater than .25) and were resolved through discussion.
 
-Each project was rated on the basis of subjective replication success both by MCF and by one of VB and BP.
-Disagreements were resolved through discussion.
 As a complement to the subjective rating of overall success, we statistically compared one key measure of interest for each study, following @boyce2023.
@@
 We recorded the same set of potential correlates that were used in @boyce2023 for original, first replication, and rescue (these were already rated for original and first replication).
-These potential correlates included the subfield of the study (cognitive, social, or other psychology), its publication year, experimental design features including whether it was a within- or between- subject design, whether each condition was instantiated with one vignette or multiple, how many items each participant saw, and whether there were open materials and open data.
+These potential correlates included the subfield of the study (cognitive, social, or other psychology), its publication year, experimental design features including whether it was a within- or between-subject design, whether each condition was instantiated with one vignette or multiple, how many items each participant saw, and whether there were open materials and open data.
 
@@
 
-Our primary question of interest was how many of the `r num_proj` rescue projects succeeded at replicating the results in the original study.
-When a replication fails to obtain the same results, one may have intuitions about what may have gone wrong -- these rescue projects test how often addressing these potential issues in fact works.
+## Overall replication rate
+
+<!-- When a replication fails to obtain the same results, one may have intuitions about what may have gone wrong -- these rescue projects test how often addressing these potential issues in fact works.
+-->
 
@@
 
-## Overall replication rate
-
 ```{=html}
@@
 ```
-All rescue projects were rated holistically for how well they replicated the original results.
-We thought about replication in terms of how confident one would be to build on the line of work given the replication results, rather than focusing on any singular numeric result or significance cut-off.
-All projects were rated both by the instructor (MCF) and by one of the TAs (VB or BP); the interrater reliability was `r irr |> round(3)`.
 
+Our primary question of interest was how many of the `r num_proj` rescue projects succeeded at replicating the results in the original study.
 Across the `r nrow(subj)` rescue projects, `r nrow(success)` mostly or fully replicated the original results according to the subjective replication ratings.
@@
 
-## Effect sizes
+## Effect size comparison
 
@@
 
-As a complement to the holistic, qualitative replication ratings used above, we also statistically compared the effect sizes of the rescue, first replication, and original study on one key measure per study.
-We followed @boyce2023 in determining a key measure for each study.
-When we were aware of additional direct replications (either from other class projects, or external replications in the literature), we also consider the effect sizes obtained in these additional replications.
+As a complement to subjective replication ratings, we also statistically compared the effect sizes of the rescue, first replication, and original study on one preregistered key measure per study [again following @boyce2023].
+Though we did not conduct a systematic review of the literature to identify all possible replications, we also consider the effect sizes obtained in additional replications when we were aware of them (either from other class projects, or external replications in the literature),
 
@@
 On the other hand, one study may find a statistically significant, but imprecisely estimated effect in a small sample, and second study may find a near-zero (null) effect, but the effect estimates from the two studies may be statistically compatible, despite one supporting a hypothesized difference and the other not.
+
+<!-- MCF: I wonder if this para needs to go in the methods?  -->
 
@@
 
-Are there signals in the features of a study or it's replication that predict whether a re-replication will succeed?
-To address this question, we ran correlations between the set of predictor variables used in @boyce2023 and the subjective replication scores of the rescues.
-We also added some (non-preregistered) predictors related to the sample size of the first replication, after seeing the successful re-replications of @ngo2019 and @krauss2003, both of which had small replication samples.
+Are there signals in the features of original or replication studies that predict whether a re-replication will succeed?
+To address this question, we report correlations between the set of predictor variables used in @boyce2023 and the subjective replication scores of the rescues.
+We also added some (non-preregistered) predictors related to the sample size of the first replication, after seeing the successful re-replications of @ngo2019 and @krauss2003, both of which had small replication samples and larger rescue samples.
 
-The number of rescues is small, and many of these predictors are correlated, so we caution against over interpretation. All of the correlations are presented in Figure \@ref(tab:cor-table).
+All of the correlations are presented in Figure \@ref(tab:cor-table).
+The number of rescues is small, and many of these predictors are correlated, so we caution against over interpretation. 
 The strongest correlates of rescue success were open materials, a small sample size on the first replication, a small sample size on the first replication relative to the original sample size, and a large rescue sample size relative to the first replication.
@@
 Small replication samples relative to original and rescue could be due to both a) powering a replication according to a reported large effect size or b) difficulties with recruitment or high exclusion rates leading to a smaller than intended sample.
-Since relative sizes of the studies may play a role in replication success and how probitive replications are, we show the sample sizes in Table \@ref(tab:tab-size).
+Since relative sizes of the studies may play a role in replication success and how probative replications are, we show the sample sizes in Table \@ref(tab:tab-size).
 
@@
 Table \@ref(tab:tab-size) shows the closeness of each first replication and rescue according to the classification scheme from @lebel2018.
-TODO CLOSENESS NUMBERS SHOULD BE DOUBLE CHECKED AND FIRST REPS REVISED AS NEEDED
+<!-- TODO CLOSENESS NUMBERS SHOULD BE DOUBLE CHECKED AND FIRST REPS REVISED AS NEEDED -->
 
@@
 
-One of the rescues that went from a replication with score of 0 to a rescue with score of 1 was the rescue of @krauss2003.
+The rescue of @krauss2003 was successful despite an unsuccessful replication.
 This study looked at the influence of a guided thinking on whether or not people gave correct justifications (drawn or written) for their answer on the Monty Hall problem.
@@
 While we can't know for sure what caused the non-replication, there were clear problems observable from the small final sample and low-quality responses.
-The rescue targeted these issues by adding a pre-screen for naivete to the Monty Hall problem, switched the name of the problem (to reduce googling for answers), and had participants upload drawings for their justifications.
-Collectively, these changes brought the rescue closer to the intent of the original.
+The rescue targeted these issues by adding a pre-screening that ensured participants were not familiar with the Monty Hall problem, switched the name of the problem (to reduce googling for answers), and had participants upload drawings for their justifications.
+Collectively, we believe these changes brought the rescue closer to the intent of the original.
 The rescue had 1/40 (`r round(1/40*100)`%) correct justifications in the control group and 6/35 (`r round(6/35*100)`%) in the guided thinking group.
-The rescue effect is smaller, but the overall pattern of results replicated, and the online adaptation in the rescue feels like it could be built on.
+This effect was significant, though smaller than the effect in the original.
 
-Another successful rescue was that of @ngo2019.
-Here, the original study found a large effect.
-The first replication, powering for 80% power on the reported effect, recruited a small sample of 12 people.
-It failed to find the effect.
-The rescue, powered using 2.5x the original sample (as recommended by @simonsohn2015), recovered a clear effect (albeit a much smaller one).
+@ngo2019 was a second successful rescue.
+The original study found a large effect; hence the first replication, powering for 80% power on the reported effect, recruited a small sample of 12 people.
+This small study failed to find the original effect.
+The rescue, powered using 2.5x the original sample [as recommended by @simonsohn2015], recovered a clear effect (albeit a much smaller one).
 There are reasons to think that some effect sizes in the literature may be inflated [@openscienceconsortium, @camerer2018], and it is also possible that changes to experiments or switches to online could result in noisier samples and thus smaller effect sizes.
@@
 Not all rescues of small replications succeeded, however.
-@payne2008 was a study of the effects of sleep versus wake on memory consolidation that showed participants a number of images and then hours later (after either sleep or no sleep) measured their recall for parts of the images.
-The first replication struggled to recruit participants and only got 23 (the original had 48).
-The rescue attempted to recruit a larger sample (target 88), but due to difficulties getting participants to complete the second part of the experiment 12 hours after the first, the rescue only managed to recruit 23 people.
+@payne2008 was a study of the effects of sleep on memory consolidation.
+They  showed participants a number of images and then hours later (after either sleep or no sleep) measured their recall for parts of the images.
+The first replication struggled to recruit participants to complete a followup session after sleep and only reported a sample size of 23 (the original had 48).
+The rescue attempted to recruit a larger sample (target 88), but also experienced difficulties getting participants to complete the second part of the experiment 12 hours after the first, managing also only to recruit 23 people.
 The lesson here may be that sleep research is difficult to conduct online.
@@
 
-(TODO other successes or failures we want to discuss?
+<!-- (TODO other successes or failures we want to discuss?
 ) (Ben: Emily's project was interesting: the rescue succeeded but with big stimulus-level random effects.
-Verity's project was also interesting: the previous replication, as well as another in the literature, showed similar but smaller findings and it really looked like she could get the effect with a bigger sample, but she ended up finding totally different results.)
+Verity's project was also interesting: the previous replication, as well as another in the literature, showed similar but smaller findings and it really looked like she could get the effect with a bigger sample, but she ended up finding totally different results.) -->
 
@@
 
-We presented the results of `r num_proj` new replications that attempted to "rescue" previous failed replications reported in @boyce2023 by identifying and ameliorating possible causes of non-replication.
+Faced with a failed replication, should investigators devote more time to continued replications? There are limited data that inform this decision. 
+To address this gap, we presented the results of `r num_proj` new replications that attempted to "rescue" previous failed replications by identifying and ameliorating possible causes of non-replication.
 `r nrow(success)` of these rescue projects (`r round(nrow(success)/num_proj*100)`%) mostly or fully replicated the original results.
 
-We don't have qualitative or quantitative explanations for why the specific studies did or did not replicate.
 In some cases, increasing sample size and fixing internal validity issues in the replication seems to have led to a successful rescue (although we can't establish causality even in these cases).
 However, there were other cases where the first replications had issues with a small sample or deviations in the implementation, and the rescue addressed these issues but still failed to replicate the original results.
-We can't predict what replication failures are likely to resolve given another, more thoughtful try, beyond that suggestion that glaring problems and low samples may sometimes be resolvable.
+We can't predict what replication failures are likely to resolve given another, more thoughtful try, beyond the suggestion to review studies for best practices in experimental design and sampling [e.g., @frank2024].
 
@@
 
-The reported rescue projects are a small sample of replications.
-They are also chosen non-randomly, as they have been selected for twice by student interest.
-However, this selection bias is likely to correlate with how graduate students choose what topics to work on and what studies to build on.
-Nonetheless, with a small sample all our estimates are highly uncertain.
+The reported rescue projects are a small sample of replications, leading to highly uncertain estimates. 
+They are also chosen non-randomly, as they have been selected for twice based on student interest -- once for the original replication and again for the rescue.
+However, this selection bias is likely to correlate with how graduate students and other early career researchers choose what topics to work on and what studies to build on.
+Nevertheless, our estimate is still broadly consistent with that of ManyLabs 5 [29% vs. 22%; @ebersole20202]
 
-The authors of the rescue projects put substantial effort into trying to set up rescues that had a good chance of success, but projects were constrained by budget limitations, a short timeline, and primarily running online studies.
+In cases where re-replications failed, we do not believe any conclusions are licensed about the status of the original results.
+Students conducting rescue projects put substantial effort into trying to set up rescues that had a good chance of success, but projects were constrained by budget limitations, a short timeline, and the constraint that most data collection needed to occur online.
 These limitations are representative of the sort of resource limitations often faced by early-career researchers.
 That said, it is possible that different results might be obtained in better-resourced settings, by scientists with more expertise and more time.
-Thus, where re-replications failed, we do not make any statements about whether the original results were false positives, we merely claim the original results do not support cumulative research by early-career researchers under the constrained conditions we tested.
+<!-- were false positives, we merely claim the original results do not support cumulative research by early-career researchers under the constrained conditions we tested. -->
 
-We opened this paper with a question about what an early-career psychology researcher should do given a failed replication: should they *try again* or *give up* and move on?
-From our sample of testing the *try again* approach, it seems that the odds of a re-replication working are low (consistent with @ebersole2020).
-Especially if there is not a clear, identifiable reason for the first replication's failure, another try is unlikely to recover the original result, and it may be more efficient to *give up* and build on a different result instead.
+We opened  with a question about what an early-career psychology researcher should do given a failed replication: should they try again or give up and move on?
+In our sample, the odds of a re-replication working are low [consistent with @ebersole2020].
+Especially if there is not a clear, identifiable candidate for replication failure, it may be more efficient to select another result to build on.
 

### 2024-04-01 manuscript/manuscript.Rmd

@@
 <!-- TODO FIX CITATION / BIB INFO (re OSC for RP:P but only after we unlink from zotero) -->
+
+TODO FIX CITATION / BIB INFO (re OSC for RP:P but only after we unlink from zotero)
 
@@
 The number of rescues is small, and many of these predictors are correlated, so we caution against over interpretation.
+
 The strongest correlates of rescue success were open materials, a small sample size on the first replication, a small sample size on the first replication relative to the original sample size, and a large rescue sample size relative to the first replication.
@@
 
-<!-- (TODO other successes or failures we want to discuss?
-) (Ben: Emily's project was interesting: the rescue succeeded but with big stimulus-level random effects.
-Verity's project was also interesting: the previous replication, as well as another in the literature, showed similar but smaller findings and it really looked like she could get the effect with a bigger sample, but she ended up finding totally different results.) -->
+\@child2018 studied reading times for passages of text with different emotional valences written from either a third-person or second-person perspective.
+They found a significant interaction between perspective and valence: participants read positively-valenced passages faster than negatively-valenced passages, but only when they were written from a second-person perspective.
+The first replication used a similar sample size to the original study (40) and found an effect that trended in the same direction, but was substantially smaller.
+The rescuer identified several possible reasons for this failure, foremost among them that the replication was conducted online while the original was conducted in person.
+It is reasonable to expect online studies of reading time to be noisier than in-person studies because the environments participants completed the study in varied much more online.
+The rescue attempt was still online, but used a much larger sample size to account for noisier data.
+Still, the rescue found a non-significant effect that trended in the opposite direction from the original and first replication.
+Even though the first replication trended in the same direction and there was an identifiable reason for the smaller effect size, increasing sample size did not rescue the effect.
 

### 2024-04-01 manuscript/manuscript.Rmd
fix citations add contrib

@@
 <!-- TODO FIX CITATION / BIB INFO (re OSC for RP:P but only after we unlink from zotero) -->
-
-TODO FIX CITATION / BIB INFO (re OSC for RP:P but only after we unlink from zotero)
-
 <!-- TODO compile everything into OSF repo & link -->
@@
 <!-- TODO redo/double check closeness scores for first rep and rescues  -->
-<!-- TODO add something about Verity's to case-study?  -->
 <!-- TODO author contributions, acknowledgements -->
@@
 
+```{r}
+subj <- parsed_d |> filter(type=="rescue") |> mutate(binary_success=ifelse(replication_score>.5,1,0))
+
+tallied <- subj|> group_by(replication_score) |> tally()
+
+success <- filter(subj, binary_success==1)
+
+d <- read_csv(here("data", "combined_data.csv")) |> filter(type=="rescue")
+
+irr <- cor.test(d$TA_rep_score, d$MCF_rep_score, method="spearman")$estimate
+
+bootstrap <- subj$binary_success |> Hmisc::smean.cl.boot()
+```
+
+```{r}
+boyce2023_sample <- read_csv(here("data/boyce_2023_data.csv")) |> select(sub_rep)
+
+percent_rep <- boyce2023_sample |> mutate(is_rep=ifelse(sub_rep>.5,1,0)) |> summarize(m=mean(is_rep))
+
+overall <- (percent_rep[1])+(1-percent_rep[1])*nrow(success)/nrow(subj)
+```
 ## Procedure
@@
 
+We measure statistical consistency using $p$-original, the $p$-value on the null hypothesis that one study's population effect comes from the same distribution of population effects as another study or studies [@mathurNewStatisticalMetrics2020a] If we assume no heterogeneity between studies, then this is the same as asking how consistent one study's estimate of the population-level effect is with another study's estimate of the population-level effect.
+However, meta-analyses of closely related studies, such as those from different sites of multi-site replications, indicate that there is often heterogeneity between studies.
+$p$-original allows for such heterogeneity, as governed by a parameter $\tau$.
+We cannot accurately estimate the level of heterogeneity for an effect meta-analytically as we have only a small number of replications per study.
+Instead, we impute a heterogeneity value of $\tau=.21$ SMD, which is the average level of heterogeneity found by @olsson-collentine2020 in prior multi-site replications in psychology.
+
 We recorded the same set of potential correlates that were used in @boyce2023 for original, first replication, and rescue (these were already rated for original and first replication).
@@
 -->
-
-```{r}
-subj <- parsed_d |> filter(type=="rescue") |> mutate(binary_success=ifelse(replication_score>.5,1,0))
-
-tallied <- subj|> group_by(replication_score) |> tally()
-
-success <- filter(subj, binary_success==1)
-
-d <- read_csv(here("data", "combined_data.csv")) |> filter(type=="rescue")
-
-irr <- cor.test(d$TA_rep_score, d$MCF_rep_score, method="spearman")$estimate
-
-bootstrap <- subj$binary_success |> Hmisc::smean.cl.boot()
-```
-
-```{r}
-boyce2023_sample <- read_csv(here("data/boyce_2023_data.csv")) |> select(sub_rep)
-
-percent_rep <- boyce2023_sample |> mutate(is_rep=ifelse(sub_rep>.5,1,0)) |> summarize(m=mean(is_rep))
-
-overall <- (percent_rep[1])+(1-percent_rep[1])*nrow(success)/nrow(subj)
-```
-
-```{=html}
-<!--* We will report the distribution of subjective replication success in our rescue sample
-
-* If there is a mixture of projects that succeed and fail to replicate the original results, we will qualitatively describe differences that may have played a role. -->
-```
 
@@
 
-<!-- MCF: I wonder if this para needs to go in the methods?  -->
-
-Here, we measure statistical consistency using $p$-original, the $p$-value on the null hypothesis that one study's population effect comes from the same distribution of population effects as another study or studies [@mathurNewStatisticalMetrics2020a] If we assume no heterogeneity between studies, then this is the same as asking how consistent one study's estimate of the population-level effect is with another study's estimate of the population-level effect.
-However, meta-analyses of closely related studies, such as those from different sites of multi-site replications, indicate that there is often heterogeneity between studies.
-$p$-original allows for such heterogeneity, as governed by a parameter $\tau$.
-We cannot accurately estimate the level of heterogeneity for an effect meta-analytically as we have only a small number of replications per study.
-Instead, we impute a heterogeneity value of $\tau=.21$ SMD, which is the average level of heterogeneity found by @olsson-collentine2020 in prior multi-site replications in psychology.
-
 As our primary comparison, we compare the effect size of the original study to the meta-analytic effect of the totality of the replications (first replication, rescue, and additional if found).
-The value of $p$-original thus represents how likely an effect size equal to or more extreme than the original effect size is to occur if it comes from a distribution of population effect sizes defined by the mean and standard error of the replications (combined meta-analytically) with a between-population standard deviation of $\tau=.21$.
+The value of $p$-original represents how likely an effect size equal to or more extreme than the original effect size is to occur if it comes from a distribution of population effect sizes defined by the mean and standard error of the replications (combined meta-analytically) with a between-population standard deviation of $\tau=.21$ [imputed from @olsson-collentine2020].
 That is, it $p$-original is a measure of the statistical consistency of the original result with the totality of the replications, assuming a given level of heterogeneity of effects between studies.
@@
 However, there were other cases where the first replications had issues with a small sample or deviations in the implementation, and the rescue addressed these issues but still failed to replicate the original results.
-We can't predict what replication failures are likely to resolve given another, more thoughtful try, beyond the suggestion to review studies for best practices in experimental design and sampling [e.g., @frank2024].
+We can't predict what replication failures are likely to resolve given another, more thoughtful try, beyond the suggestion to review studies for best practices in experimental design and sampling [e.g., @experimentology2024].
 
@@
 However, this selection bias is likely to correlate with how graduate students and other early career researchers choose what topics to work on and what studies to build on.
-Nevertheless, our estimate is still broadly consistent with that of ManyLabs 5 [29% vs. 22%; @ebersole20202]
+Nevertheless, our estimate is still broadly consistent with that of ManyLabs 5 [29% vs. 22%, @ebersole2020].
 
@@
 
-TODO
+We thank the students from previous years of PSYCH 251 who graciously agreed to let us re-replicate their projects and shared their work with us.
+We thank the other members of 251 teaching team and students for feedback on projects.
+[DO we thank the departments that gave us money for projects?]
 
@@
 
-TODO
+VB and MCF did conceptualization. BP did project administration, VB did formal analysis, and MCF did supervision.
+
+Authors other than VB, BP, and MCF each designed, conducted, analyzed, and wrote up one of the projects -- these authors did investigation, formal analysis, and visualization.
+
+VB wrote the first draft, BP and MCF did editing, and all authors reviewed the final manuscript.
 

### 2024-04-01 manuscript/manuscript.Rmd
links

@@
 :::
-<!-- TODO FIX CITATION / BIB INFO (re OSC for RP:P but only after we unlink from zotero) -->
 <!-- TODO compile everything into OSF repo & link -->
@@
 
-A spreadsheet of projects, individual project write-ups (both first replications and rescues), links to individual project data and analyses for rescue projects, and the analytic code for this paper are all available at TODO OSF LINK GOES HERE.
+A spreadsheet of projects, individual project write-ups (both first replications and rescues), links to individual project data and analyses for rescue projects, and the analytic code for this paper are all available at https://osf.io/cyk5w/.
 
@@
 Each project was also individually pre-registered by the student conducting it.
-The overall analysis is at LINK, individual pre-registrations are linked from LINK.
+The overall analysis is pre-registered at https://osf.io/5qz7v, individual pre-registrations are linked from TODO LINK.
 We note one deviation from our pre-registration here: we pre-registered visual comparisons between original, first replication, and rescue projects using prediction intervals.
@@
 We thank the other members of 251 teaching team and students for feedback on projects.
-[DO we thank the departments that gave us money for projects?]
+Data collection was supported by funding from the Stanford Departments of Psychology and Philosophy, Graduate School of Education, and the Symbolic Systems program.
 
@@
 
-VB and MCF did conceptualization. BP did project administration, VB did formal analysis, and MCF did supervision.
+VB and MCF contributed to conceptualization. BP contributed to project administration, VB contributed to formal analysis, and MCF contributed to supervision.
 
-Authors other than VB, BP, and MCF each designed, conducted, analyzed, and wrote up one of the projects -- these authors did investigation, formal analysis, and visualization.
+Authors other than VB, BP, and MCF each designed, conducted, analyzed, and wrote up one of the projects -- these authors contributed to investigation, formal analysis, and visualization.
 

### 2024-04-02 manuscript/manuscript.Rmd
pass for nitpicks and typos

@@
 <!--Or maybe the main effect of interest may be null, but you found a significant effect interaction that wasn't hypothesized.-->
-Whatever the details of the replication failure, you are left with a question: Should you try again and run a re-replication, or should you give up and pick a different study to extend?
+Whatever the details of the replication failure, you are left with a question: Should you try again and run a re-replication, or should you give up and pick a different study to build upon?
 
@@
 Another possibility is that the original reported effect size might be inflated due to some combination of heterogeneity, $p$-hacking, low power, and publication bias.
-A consequence of inflated effect sizes is that replication studies might select a sample size with appropriate sttaistical power for the reported effect size and then have too small a sample to reliably detect the (true) smaller effect.
+A consequence of inflated effect sizes is that replication studies might select a sample size with appropriate statistical power for the reported effect size and then have too small a sample to reliably detect the (true) smaller effect.
 Replication studies might also end up underpowered due to unexpected attrition or noise in the replication sample.
 
-Other reasons for replication failure are also primarily due to the replication study. 
+Some other reasons for replication failure are  primarily due to the replication study. 
 A replication could observe different results from the original due to methodological differences. 
@@
 A difference in the details of recruitment (e.g., online versus in-person) might mean that particular details of a study implementation would no longer be appropriate, or the data quality controls and attention checks might be inadequate.
-If there are differences in time, place, or subject population between the two studies, corresponding changes to the materials, instructions, or procedure could be needed to provide an adaptation of the experimental paradigm to a new context.
+If there are differences in time, place, or subject population between the two studies, corresponding changes to the materials, instructions, or procedure could be needed to provide an adaptation of the experimental paradigm to the new context.
 Such adaptation creates yet more challenges in interpretation: too many changes could cause differing results, but so could not enough changes. 
@@
 One estimate comes from @ebersole2020.
-After the original RP:P result of a replication rate around 40% [@openscienceconsortium], @gilbert2016 raised concerns that methodological differences might explain low replication rate.
-In 11 of the RP:P studies, the original authors had raised concerns about protocol fidelity prior to data-collection.
+After the original RP:P study reported of a replication rate around 40% [@openscienceconsortium], @gilbert2016 raised concerns that methodological differences might explain the low replication rate.
+In 11 of the RP:P studies, the original authors had raised concerns about protocol fidelity prior to data collection.
 Of these 11 with concerns, 10 failed to obtain significant results in the RP:P replication. 
@@
 On the other hand, early career researchers may also be prone to a different distribution of causes of initial replication failure.
-Thus, it is an open question what the re-replication rate is for failed replications of early career researchers.
-Further, estimating this rate could inform researhcers' decisions on what to do next after failed replications.
+Thus, it is an open question what the re-replication rate is for failed replications by early career researchers.
+Further, estimating this rate could inform researchers' decisions on what to do next after failed replications.
 
 Here, we investigate re-replication in the context of graduate student replication class projects.
-Students in a graduate methods class on experimental methods in psychology were given the option to "rescue" an experiment that a student in a prior year had previously failed to replicate as their class project [first replications reported in @boyce2023].
+Students in a graduate-level class on experimental methods in psychology were given the option to "rescue" an experiment that a student in a prior year had previously failed to replicate as their class project [first replications reported in @boyce2023].
 The focus of the class was best practices in experimental design; thus, students looked at both the original paper and the failed replication to examine potential issues in the replication that they could fix in their rescue project.
-In the present paper, we report the results of `r num_proj` re-replication rescue projects. We find that a minority of projects (5/17, 29%) successful recovered the original effect.
+In the present paper, we report the results of `r num_proj` re-replication rescue projects. We find that a minority of projects (5/17, 29%) successfully recovered the original effect.
 
@@
 PSYCH 251 is a graduate-level experimental methods class taught by MCF.
-In previous years, students have conducted replication projects [as reported in @boyce2023 and @hawkins2018].
+In previous years, students have conducted replication projects [@boyce2023; @hawkins2018].
 In Fall 2023, students were offered the option to complete a "rescue" project where they re-replicated one of the unsuccessful replications from a previous year.
 Students could also opt to do a normal replication instead.
-If they opted for a rescue, they were given the option to participate in a collaborative meta-science project and earn authorship on the current paper based on 1) completing a rescue project, 2) reviewing another student's rescue project for analytic errors, and 3) reviewing and approving the final manuscript.
+If they opted for a rescue, they were given the option to participate in a collaborative meta-science project and earn authorship on the current paper based on 1) completing a rescue project, 2) reviewing another student's rescue project for reproducibility, and 3) reviewing and approving the final manuscript.
 We report on the result of `r num_proj` rescue projects that opted to be part of the paper and completed data collection.
 
-A spreadsheet of projects, individual project write-ups (both first replications and rescues), links to individual project data and analyses for rescue projects, and the analytic code for this paper are all available at https://osf.io/cyk5w/.
+A spreadsheet of projects, individual project write-ups (both first replications and rescues), individual project data and analyses for rescue projects, and the analytic code for this paper are all available at https://osf.io/cyk5w/.
 
@@
 The experiments that were re-replicated were chosen from studies that failed to replicate in @boyce2023.
-We created an initial list of `r nrow(filtered)` rescue-eligible studies that 1) had received a subjective replication success score of 0, .25 or .5 (on a 0--1 scale) in @boyce2023, 2) had a Github repository available (github repositories were used in class starting in academic year 2015-2016), and 3) where the original experiment had 200 or fewer participants (to ensure we could afford to match or increase the sample size based on the class budget).
+We created an initial list of `r nrow(filtered)` rescue-eligible studies that 1) had received a subjective replication success score of 0, .25, or .5 (on a 0--1 scale) in @boyce2023, 2) had a Github repository available (Github repositories were used in class starting in academic year 2015-2016), and 3) where the original experiment had 200 or fewer participants (to ensure we could afford to match or increase the sample size based on the class budget).
 We then contacted the replication project authors for permission to share their report and repository with a new student and include it as a supplement on a resulting paper.
@@
 @tarampi2016 had participants do a timed navigation task where they wrote L or R to indicate which way to turn at each intersection on a paper map.
-The replication ported this experiment online and had participants click a drop down menu to select left or write for each turn.
-The rescue removed the unwieldy dropdown menus and opted to have participants press keys on the keyboard to indicate the direction of a turn, which seemed like a more natural interface.
+The replication ported this experiment online and had participants click a drop down menu to select left or right for each turn.
+The rescue removed the unwieldy drop down menus and opted to have participants press keys on the keyboard to indicate the direction of a turn, which seemed like a more natural interface.
 Once experimental designs and analytic plans were approved by class TAs (VB and BP), students pre-registered and ran their samples.
@@
 
-We followed @boyce2023 in the properties of the studies we measure and how we quantify replication success. 
+We followed @boyce2023 in the properties of the studies we measured and how we quantified replication success. 
 Each project was rated on the basis of subjective replication success (on a 0--1 scale) by both MCF and one of VB and BP.
@@
 
-We measure statistical consistency using $p$-original, the $p$-value on the null hypothesis that one study's population effect comes from the same distribution of population effects as another study or studies [@mathurNewStatisticalMetrics2020a] If we assume no heterogeneity between studies, then this is the same as asking how consistent one study's estimate of the population-level effect is with another study's estimate of the population-level effect.
+We measured statistical consistency using $p$-original, the $p$-value on the null hypothesis that one study's population effect comes from the same distribution of population effects as another study or studies [@mathurNewStatisticalMetrics2020a] If we assume no heterogeneity between studies, then this is the same as asking how consistent one study's estimate of the population-level effect is with another study's estimate of the population-level effect.
 However, meta-analyses of closely related studies, such as those from different sites of multi-site replications, indicate that there is often heterogeneity between studies.
@@
 We cannot accurately estimate the level of heterogeneity for an effect meta-analytically as we have only a small number of replications per study.
-Instead, we impute a heterogeneity value of $\tau=.21$ SMD, which is the average level of heterogeneity found by @olsson-collentine2020 in prior multi-site replications in psychology.
+Instead, we imputed a heterogeneity value of $\tau=.21$ SMD, which is the average level of heterogeneity found by @olsson-collentine2020 in prior multi-site replications in psychology.
 
@@
 For instance, if an original study compared between two critical conditions but also had a baseline control, we did not count the participants in the baseline condition if a replication did not include this condition.
-We also recorded whether each study was conducted online using crowd-sourced platform or not.
+We also recorded whether each study was conducted online using a crowd-sourced platform or not.
 
@@
 Across the `r nrow(subj)` rescue projects, `r nrow(success)` mostly or fully replicated the original results according to the subjective replication ratings.
-`r pluck(tallied,2,1)` had a rating of 0, `r pluck(tallied, 2,2)` got a rating of .75, and `r pluck(tallied, 2,3)` got a rating of 1.
+`r pluck(tallied,2,1)` got a rating of 0, `r pluck(tallied, 2,2)` got a rating of .75, and `r pluck(tallied, 2,3)` got a rating of 1.
 Thus, a first pass answer to the question "how often can a failed replication be salvaged?" is `r round(nrow(success)/nrow(subj)*100)`% (bootstrapped 95% CI: `r round(bootstrap[2]*100)`% - `r round(bootstrap[3]*100)`%) of the time.
@@
         panel.grid.major.x = element_blank(), 
-        panel.grid.minor.x=element_blank()
+        panel.grid.minor.x=element_blank(),
+        legend.title=element_blank(),
+        legend.text=element_text(size=10)
         )+
@@
         )+
-  labs(y="Standarized mean difference", x="")
+  labs(y="Standarized mean difference", x="", )
 
@@
 As a complement to subjective replication ratings, we also statistically compared the effect sizes of the rescue, first replication, and original study on one preregistered key measure per study [again following @boyce2023].
-Though we did not conduct a systematic review of the literature to identify all possible replications, we also consider the effect sizes obtained in additional replications when we were aware of them (either from other class projects, or external replications in the literature),
+Though we did not conduct a systematic review of the literature to identify all possible replications, we also consider the effect sizes obtained in additional replications when we were aware of them (either from other class projects, or external replications in the literature).
 
@@
 
-all |> ungroup() |>  left_join(names) |> select(Paper=name_pretty, `All reps`=orig_v_other, "Rescue" = orig_v_rescue, "Non-rescue"=orig_v_not_rescue, "Other reps"=rescue_v_reps) |> knitr::kable(format="latex", booktabs=T, linesep="", caption="P-original values between different sets of experiments.
+all |> ungroup() |>  left_join(names) |> select(Paper=name_pretty, `All reps`=orig_v_other, "Rescue" = orig_v_rescue, "Non-rescue"=orig_v_not_rescue, "Other reps"=rescue_v_reps) |> knitr::kable(format="latex", booktabs=T, linesep="", caption="$P$-original values between different sets of experiments.
 The primary analysis is between the original result and the meta-analytic aggregation of all replications.
-All p-originals assume an imputed heterogeneity value of tau=.21.", digits=3) |>
-  add_header_above(c(" "=1, "Original and"=3, "Rescue and"=1)) |> add_header_above(c(" "=1, "P-original comparing between"=4))
+All $p$-original values assume an imputed heterogeneity value of $\\tau$=.21.", digits=3) |>
+  add_header_above(c(" "=1, "Original and"=3, "Rescue and"=1)) |> add_header_above(c(" "=1, "p-original comparing between"=4))
 
@@
 For instance, two studies may both find that condition 1 results in a significantly higher outcome measure than condition 2, but the effect magnitudes may be sufficiently different that they are statistically unlikely to have come from the same population.
-On the other hand, one study may find a statistically significant, but imprecisely estimated effect in a small sample, and second study may find a near-zero (null) effect, but the effect estimates from the two studies may be statistically compatible, despite one supporting a hypothesized difference and the other not.
+On the other hand, one study may find a statistically significant, but imprecisely estimated effect in a small sample, and a second study may find a near-zero (null) effect, but the effect estimates from the two studies may be statistically compatible, despite one supporting a hypothesized difference and the other not.
 
@@
 The value of $p$-original represents how likely an effect size equal to or more extreme than the original effect size is to occur if it comes from a distribution of population effect sizes defined by the mean and standard error of the replications (combined meta-analytically) with a between-population standard deviation of $\tau=.21$ [imputed from @olsson-collentine2020].
-That is, it $p$-original is a measure of the statistical consistency of the original result with the totality of the replications, assuming a given level of heterogeneity of effects between studies.
+That is, $p$-original is a measure of the statistical consistency of the original result with the totality of the replications, assuming a given level of heterogeneity of effects between studies.
 Smaller $p$-original values indicate more inconsistency.
@@
 As secondary measures, we calculated the $p$-original values between a) the original and the rescue, b) the original and non-rescue replications, and c) the rescue and other replications.
-For a) the original versus the rescue, median value of $p$-original was `r rescue_summ$median |> round(2)` [IQR: `r rescue_summ$low |> round(2)` - `r rescue_summ$high|> round(2)`], and `r round(rescue_summ$less_than*100)`% of the $p$-original values were less than .05.
-For b) the original versus all the non-rescue replications, median value of $p$-original was `r rep_summ$median |> round(2)` [IQR: `r rep_summ$low |> round(2)` - `r rep_summ$high |> round(2)`], and `r round(rep_summ$less_than*100)`% of the $p$-original values were less than .05.
-For c) the rescue versus the other replications, median value of $p$-original was `r rescue_rep_summ$median |> round(2)` [IQR: `r rescue_rep_summ$low |> round(2)` - `r rescue_rep_summ$high |> round(2)`], and `r round(rescue_rep_summ$less_than*100)`% of the $p$-original values were less than .05.
+For a) the original versus the rescue, the median value of $p$-original was `r rescue_summ$median |> round(2)` [IQR: `r rescue_summ$low |> round(2)` - `r rescue_summ$high|> round(2)`], and `r round(rescue_summ$less_than*100)`% of the $p$-original values were less than .05.
+For b) the original versus all the non-rescue replications, the median value of $p$-original was `r rep_summ$median |> round(2)` [IQR: `r rep_summ$low |> round(2)` - `r rep_summ$high |> round(2)`], and `r round(rep_summ$less_than*100)`% of the $p$-original values were less than .05.
+For c) the rescue versus the other replications, the median value of $p$-original was `r rescue_rep_summ$median |> round(2)` [IQR: `r rescue_rep_summ$low |> round(2)` - `r rescue_rep_summ$high |> round(2)`], and `r round(rescue_rep_summ$less_than*100)`% of the $p$-original values were less than .05.
 
@@
 
-Overall, allowing for a heterogeneity level of $\tau$=.21 SMD, a number of original effects are not statistically consistent with rescues and replication effects.
+Overall, allowing for a heterogeneity level of $\tau$=.21 SMD, a number of original effects are not statistically consistent with rescue and replication effects.
 The pattern of inconsistency does not align with which studies were rated as having replicated.
@@
 
-Given the mix of successful and unsuccessful rescues, we discuss a few projects where we have speculations about why they turned out the way they did.
+Given the mix of successful and unsuccessful rescue projects, we discuss a few projects where we have speculations about why they turned out the way they did.
 
 The rescue of @krauss2003 was successful despite an unsuccessful replication.
-This study looked at the influence of a guided thinking on whether or not people gave correct justifications (drawn or written) for their answer on the Monty Hall problem.
+This study looked at the influence of guided thinking on whether or not people gave correct justifications (drawn or written) for their answer on the Monty Hall problem.
 The original paper reported correct justification from 2/67 (`r round(2/67*100)`%) in the control condition and 13/34 (`r round(13/34*100)`%) in the guided thinking condition.
@@
 Collectively, we believe these changes brought the rescue closer to the intent of the original.
-The rescue had 1/40 (`r round(1/40*100)`%) correct justifications in the control group and 6/35 (`r round(6/35*100)`%) in the guided thinking group.
+The rescue had 1/40 (`r round(1/40*100)`%) correct justifications in the control condition and 6/35 (`r round(6/35*100)`%) in the guided thinking condition.
 This effect was significant, though smaller than the effect in the original.
@@
 
-\@child2018 studied reading times for passages of text with different emotional valences written from either a third-person or second-person perspective.
+@child2018 studied reading times for passages of text with different emotional valences written from either a third-person or second-person perspective.
 They found a significant interaction between perspective and valence: participants read positively-valenced passages faster than negatively-valenced passages, but only when they were written from a second-person perspective.
@@
 In our sample, the odds of a re-replication working are low [consistent with @ebersole2020].
-Especially if there is not a clear, identifiable candidate for replication failure, it may be more efficient to select another result to build on.
+Especially if there is not a clear, identifiable candidate cause for replication failure, it may be more efficient to select another result to build on.
 
@@
 We thank the students from previous years of PSYCH 251 who graciously agreed to let us re-replicate their projects and shared their work with us.
-We thank the other members of 251 teaching team and students for feedback on projects.
+We thank the other members of the PSYCH 251 teaching team and students for feedback on projects.
 Data collection was supported by funding from the Stanford Departments of Psychology and Philosophy, Graduate School of Education, and the Symbolic Systems program.
@@
 
-VB and MCF contributed to conceptualization. BP contributed to project administration, VB contributed to formal analysis, and MCF contributed to supervision.
+VB and MCF conceptualized the study. BP contributed project administration, VB contributed formal analysis, and MCF contributed supervision.
 
-Authors other than VB, BP, and MCF each designed, conducted, analyzed, and wrote up one of the projects -- these authors contributed to investigation, formal analysis, and visualization.
+Authors other than VB, BP, and MCF each designed, conducted, analyzed, and wrote up one of the rescue projects -- these authors contributed to investigation, formal analysis, and visualization.
 
-VB wrote the first draft, BP and MCF did editing, and all authors reviewed the final manuscript.
+VB wrote the first draft, BP and MCF contributed editing, and all authors reviewed the final manuscript.
 

### 2024-04-02 first-replication-reports/RPubs - 251_replication_final_files/embed.js
add reportsadd reportsadd reportsadd reportsadd reportsadd reportsadd reportsadd reportsadd reports

@@ -1,0 +1,51 @@
+(function () {
+    'use strict';
+    var _config = window.disqus_config;
+    window.disqus_config = function () {
+        if (_config) {
+            try {
+                _config.call(this);
+            } catch(err) {
+                console.error('There was a problem with the Disqus configuration.', err);
+            }
+        }
+        this.server_side = {
+  "disable_ads_android":"",
+  "inthread_repeat_comment_count":"8",
+  "default_placement_url":"",
+  "inthread_placement_url":"",
+  "under_ccpa":"1",
+  "can_disable_ads":"",
+  "lazyload_viewports":"2",
+  "service":"dynamic",
+  "sourceless_iframe":"1",
+  "experiment":"network_default",
+  "inthread_count_children":"True",
+  "under_gdpr":"",
+  "inthread_multiple_ads":"True",
+  "bin":"embed:promoted_discovery:dynamic:network_default:fallthrough",
+  "bottom_placement_url":"//tempest.services.disqus.com/ads-iframe/taboola/?position=bottom&shortname=rpubs&experiment=network_default&variant=fallthrough&service=dynamic",
+  "variant":"fallthrough",
+  "forum_id":"1423073",
+  "recommendations_placement_url":"//tempest.services.disqus.com/ads-iframe/taboola_1x1/?position=recommendations&shortname=rpubs&experiment=network_default&variant=fallthrough&service=dynamic",
+  "top_placement_url":"//tempest.services.disqus.com/ads-iframe/taboola/?position=top&shortname=rpubs&experiment=network_default&variant=fallthrough&service=dynamic",
+  "inthread_trailing_comment_count":"0",
+  "is_private":"",
+  "skeleton_frame_enabled":"",
+  "disable_ads_ios":"",
+  "recs_outside_embed_enabled":"1",
+  "forum":{
+    "id":1423073,
+    "disable_disqus_branding":false,
+    "recommendation_placement":"top",
+    "recommendations_feature_enabled":true
+  },
+  "sandbox_ads":"1",
+  "inthread_leading_comment_count":"1",
+  "t":"1712093856"
+};
+    };
[…]

### 2024-04-02 first-replication-reports/RPubs - DocumenReplication_251_final_files/embed.js

@@ -1,0 +1,51 @@
+(function () {
+    'use strict';
+    var _config = window.disqus_config;
+    window.disqus_config = function () {
+        if (_config) {
+            try {
+                _config.call(this);
+            } catch(err) {
+                console.error('There was a problem with the Disqus configuration.', err);
+            }
+        }
+        this.server_side = {
+  "disable_ads_android":"",
+  "inthread_repeat_comment_count":"8",
+  "default_placement_url":"",
+  "inthread_placement_url":"",
+  "under_ccpa":"1",
+  "can_disable_ads":"",
+  "lazyload_viewports":"2",
+  "service":"dynamic",
+  "sourceless_iframe":"1",
+  "experiment":"prebidrenderfix",
+  "inthread_count_children":"True",
+  "under_gdpr":"",
+  "inthread_multiple_ads":"True",
+  "bin":"embed:promoted_discovery:dynamic:prebidrenderfix:active",
+  "bottom_placement_url":"//tempest.services.disqus.com/ads-iframe/taboola/?position=bottom&shortname=rpubs&experiment=prebidrenderfix&variant=active&service=dynamic",
+  "variant":"active",
+  "forum_id":"1423073",
+  "recommendations_placement_url":"//tempest.services.disqus.com/ads-iframe/taboola_1x1/?position=recommendations&shortname=rpubs&experiment=prebidrenderfix&variant=active&service=dynamic",
+  "top_placement_url":"//tempest.services.disqus.com/ads-iframe/taboola/?position=top&shortname=rpubs&experiment=prebidrenderfix&variant=active&service=dynamic",
+  "inthread_trailing_comment_count":"0",
+  "is_private":"",
+  "skeleton_frame_enabled":"",
+  "disable_ads_ios":"",
+  "recs_outside_embed_enabled":"1",
+  "forum":{
+    "id":1423073,
+    "disable_disqus_branding":false,
+    "recommendation_placement":"top",
+    "recommendations_feature_enabled":true
+  },
+  "sandbox_ads":"1",
+  "inthread_leading_comment_count":"1",
+  "t":"1712093732"
+};
+    };
+})();
[…]

### 2024-04-02 first-replication-reports/RPubs - Hopkins2016 Writeup - Final Report_files/recommendations.js

@@ -1,0 +1,38 @@
+(function () {
+    'use strict';
+    var _config = window.disqus_recommendations_config;
+    window.disqus_recommendations_config = function () {
+        if (_config) {
+            try {
+                _config.call(this);
+            } catch(err) {
+                console.error('There was a problem with the Disqus configuration.', err);
+            }
+        }
+        this.server_side = {
+  "bin":"embed:promoted_discovery:dynamic:prebidrenderfix:active",
+  "disable_ads_ios":"",
+  "recs_outside_embed_enabled":"1",
+  "forum":{
+    "id":1423073,
+    "disable_disqus_branding":false,
+    "recommendation_placement":"top",
+    "recommendations_feature_enabled":true
+  },
+  "service":"dynamic",
+  "disable_ads_android":"",
+  "sourceless_iframe":"1",
+  "variant":"active",
+  "forum_id":"1423073",
+  "recommendations_placement_url":"//tempest.services.disqus.com/ads-iframe/taboola_1x1/?position=recommendations&shortname=rpubs&experiment=prebidrenderfix&variant=active&service=dynamic",
+  "experiment":"prebidrenderfix",
+  "default_placement_url":"",
+  "t":"1712093794",
+  "can_disable_ads":"",
+  "skeleton_frame_enabled":""
+};
+    };
+})();
[…]

### 2024-04-02 first-replication-reports/RPubs - Replication Report for &#39;Development of Holistic Episodic Recollection&#39; by Ngo et al. (2019, Psychological Science)_files/recommendations.js

@@ -1,0 +1,38 @@
+(function () {
+    'use strict';
+    var _config = window.disqus_recommendations_config;
+    window.disqus_recommendations_config = function () {
+        if (_config) {
+            try {
+                _config.call(this);
+            } catch(err) {
+                console.error('There was a problem with the Disqus configuration.', err);
+            }
+        }
+        this.server_side = {
+  "bin":"embed:promoted_discovery:dynamic:network_default:fallthrough",
+  "disable_ads_ios":"",
+  "recs_outside_embed_enabled":"1",
+  "forum":{
+    "id":1423073,
+    "disable_disqus_branding":false,
+    "recommendation_placement":"top",
+    "recommendations_feature_enabled":true
+  },
+  "service":"dynamic",
+  "disable_ads_android":"",
+  "sourceless_iframe":"1",
+  "variant":"fallthrough",
+  "forum_id":"1423073",
+  "recommendations_placement_url":"//tempest.services.disqus.com/ads-iframe/taboola_1x1/?position=recommendations&shortname=rpubs&experiment=network_default&variant=fallthrough&service=dynamic",
+  "experiment":"network_default",
+  "default_placement_url":"",
+  "t":"1712093856",
+  "can_disable_ads":"",
+  "skeleton_frame_enabled":""
+};
+    };
+})();
[…]

### 2024-04-02 first-replication-reports/RPubs - Replication report_files/embed.js

@@ -1,0 +1,51 @@
+(function () {
+    'use strict';
+    var _config = window.disqus_config;
+    window.disqus_config = function () {
+        if (_config) {
+            try {
+                _config.call(this);
+            } catch(err) {
+                console.error('There was a problem with the Disqus configuration.', err);
+            }
+        }
+        this.server_side = {
+  "disable_ads_android":"",
+  "inthread_repeat_comment_count":"8",
+  "default_placement_url":"",
+  "inthread_placement_url":"",
+  "under_ccpa":"1",
+  "can_disable_ads":"",
+  "lazyload_viewports":"2",
+  "service":"dynamic",
+  "sourceless_iframe":"1",
+  "experiment":"network_default",
+  "inthread_count_children":"True",
+  "under_gdpr":"",
+  "inthread_multiple_ads":"True",
+  "bin":"embed:promoted_discovery:dynamic:network_default:fallthrough",
+  "bottom_placement_url":"//tempest.services.disqus.com/ads-iframe/taboola/?position=bottom&shortname=rpubs&experiment=network_default&variant=fallthrough&service=dynamic",
+  "variant":"fallthrough",
+  "forum_id":"1423073",
+  "recommendations_placement_url":"//tempest.services.disqus.com/ads-iframe/taboola_1x1/?position=recommendations&shortname=rpubs&experiment=network_default&variant=fallthrough&service=dynamic",
+  "top_placement_url":"//tempest.services.disqus.com/ads-iframe/taboola/?position=top&shortname=rpubs&experiment=network_default&variant=fallthrough&service=dynamic",
+  "inthread_trailing_comment_count":"0",
+  "is_private":"",
+  "skeleton_frame_enabled":"",
+  "disable_ads_ios":"",
+  "recs_outside_embed_enabled":"1",
+  "forum":{
+    "id":1423073,
+    "disable_disqus_branding":false,
+    "recommendation_placement":"top",
+    "recommendations_feature_enabled":true
+  },
+  "sandbox_ads":"1",
+  "inthread_leading_comment_count":"1",
+  "t":"1712093794"
+};
+    };
[…]

### 2024-04-02 first-replication-reports/RPubs - craig2014_files/recommendations.js

@@ -1,0 +1,38 @@
+(function () {
+    'use strict';
+    var _config = window.disqus_recommendations_config;
+    window.disqus_recommendations_config = function () {
+        if (_config) {
+            try {
+                _config.call(this);
+            } catch(err) {
+                console.error('There was a problem with the Disqus configuration.', err);
+            }
+        }
+        this.server_side = {
+  "bin":"embed:promoted_discovery:dynamic:prebidrenderfix:active",
+  "disable_ads_ios":"",
+  "recs_outside_embed_enabled":"1",
+  "forum":{
+    "id":1423073,
+    "disable_disqus_branding":false,
+    "recommendation_placement":"top",
+    "recommendations_feature_enabled":true
+  },
+  "service":"dynamic",
+  "disable_ads_android":"",
+  "sourceless_iframe":"1",
+  "variant":"active",
+  "forum_id":"1423073",
+  "recommendations_placement_url":"//tempest.services.disqus.com/ads-iframe/taboola_1x1/?position=recommendations&shortname=rpubs&experiment=prebidrenderfix&variant=active&service=dynamic",
+  "experiment":"prebidrenderfix",
+  "default_placement_url":"",
+  "t":"1712093732",
+  "can_disable_ads":"",
+  "skeleton_frame_enabled":""
+};
+    };
+})();
[…]

### 2024-04-02 individual-rescue-reports/RPubs - Gong rescue_files/embed.js

@@ -1,0 +1,51 @@
+(function () {
+    'use strict';
+    var _config = window.disqus_config;
+    window.disqus_config = function () {
+        if (_config) {
+            try {
+                _config.call(this);
+            } catch(err) {
+                console.error('There was a problem with the Disqus configuration.', err);
+            }
+        }
+        this.server_side = {
+  "disable_ads_android":"",
+  "inthread_repeat_comment_count":"8",
+  "default_placement_url":"",
+  "inthread_placement_url":"",
+  "under_ccpa":"1",
+  "can_disable_ads":"",
+  "lazyload_viewports":"2",
+  "service":"dynamic",
+  "sourceless_iframe":"1",
+  "experiment":"prebidrenderfix",
+  "inthread_count_children":"True",
+  "under_gdpr":"",
+  "inthread_multiple_ads":"True",
+  "bin":"embed:promoted_discovery:dynamic:prebidrenderfix:active",
+  "bottom_placement_url":"//tempest.services.disqus.com/ads-iframe/taboola/?position=bottom&shortname=rpubs&experiment=prebidrenderfix&variant=active&service=dynamic",
+  "variant":"active",
+  "forum_id":"1423073",
+  "recommendations_placement_url":"//tempest.services.disqus.com/ads-iframe/taboola_1x1/?position=recommendations&shortname=rpubs&experiment=prebidrenderfix&variant=active&service=dynamic",
+  "top_placement_url":"//tempest.services.disqus.com/ads-iframe/taboola/?position=top&shortname=rpubs&experiment=prebidrenderfix&variant=active&service=dynamic",
+  "inthread_trailing_comment_count":"0",
+  "is_private":"",
+  "skeleton_frame_enabled":"",
+  "disable_ads_ios":"",
+  "recs_outside_embed_enabled":"1",
+  "forum":{
+    "id":1423073,
+    "disable_disqus_branding":false,
+    "recommendation_placement":"top",
+    "recommendations_feature_enabled":true
+  },
+  "sandbox_ads":"1",
+  "inthread_leading_comment_count":"1",
+  "t":"1712096107"
+};
+    };
+})();
[…]

### 2024-04-02 individual-rescue-reports/RPubs - Gong rescue_files/recommendations.js

@@ -1,0 +1,38 @@
+(function () {
+    'use strict';
+    var _config = window.disqus_recommendations_config;
+    window.disqus_recommendations_config = function () {
+        if (_config) {
+            try {
+                _config.call(this);
+            } catch(err) {
+                console.error('There was a problem with the Disqus configuration.', err);
+            }
+        }
+        this.server_side = {
+  "bin":"embed:promoted_discovery:dynamic:prebidrenderfix:active",
+  "disable_ads_ios":"",
+  "recs_outside_embed_enabled":"1",
+  "forum":{
+    "id":1423073,
+    "disable_disqus_branding":false,
+    "recommendation_placement":"top",
+    "recommendations_feature_enabled":true
+  },
+  "service":"dynamic",
+  "disable_ads_android":"",
+  "sourceless_iframe":"1",
+  "variant":"active",
+  "forum_id":"1423073",
+  "recommendations_placement_url":"//tempest.services.disqus.com/ads-iframe/taboola_1x1/?position=recommendations&shortname=rpubs&experiment=prebidrenderfix&variant=active&service=dynamic",
+  "experiment":"prebidrenderfix",
+  "default_placement_url":"",
+  "t":"1712096122",
+  "can_disable_ads":"",
+  "skeleton_frame_enabled":""
+};
+    };
+})();
[…]

### 2024-04-02 reconstruct_effect_sizes/denis_es.Rmd
add other stuff

---
title: "Denis"
output: html_notebook
---

```{r}
library(tidyverse)
library(here)
```
We want an anova on general recognition of objects in wake v sleep x neg v neutral

It didn't come out so I checked other things

note that denis reports a hit - false alarm value but that very much isn't what payne does, so we try overall/general/specific on hit rate alone  to try to understand

```{r}
overall <- read_csv(here("reconstruct_effect_sizes/Expt1_OverallRecognition.csv")) |> 
  select(id, delay_cond, starts_with("hit")) |> 
  pivot_longer(starts_with("hit")) |> 
  rename(overall=value)

combined <- read_csv(here("reconstruct_effect_sizes/Expt1_SpecificRecognition.csv")) |> 
    select(id, delay_cond, starts_with("hit")) |> 
  pivot_longer(starts_with("hit")) |> 
  rename(specific=value) |> 
  left_join(overall) |> 
  separate(name, into=c(NA, "valence", "target")) |> 
  mutate(general=(overall-specific)/(1-specific))

test <- combined |> filter(!is.na(general))|> filter(! id %in% c("p1025", "p1032", "p1038", "p1050", "p1073", "p1104", "p1132", "p1239")) #can't handle NAs for general, so remove those participants

```

```{r}
# check 3-ways
library(ez)
anova_3way_obj = ezANOVA(
    #data=combined,
    data = test,
    #dv = .(overall),
    #dv = .(specific),
    dv= .(general),
    wid = .(id), 
    within = .(valence,target),
    between = .(delay_cond)
)

anova_3way_obj

#valence, target, valence x target on overall and specific
# cond x valence x target on specific only

#target, valence x target on general
```

```{r}

library(ez)
anova_2way_obj = ezANOVA(
    #data=combined |> filter(target=="object"),
    data = test |> filter(target=="object"),
    #dv = .(overall),
    #dv = .(specific),
    dv= .(general),
    wid = .(id), 
    within = .(valence),
    between = .(delay_cond)
)

anova_2way_obj

#valence on overall, specific, general

test |> filter(target=="object") |> group_by(valence, delay_cond) |> summarize(m=mean(general))
```

### 2024-04-02 reconstruct_effect_sizes/hopkins_es.Rmd
add other stuff

--- 2024-02-27 code/hopkins_es.Rmd
@@
 ```
-Key effect is that explantion level predicts rating (this is in an lm, but we're doing it outside for SMD here)
+Key effect is that explanation level predicts rating (this is in an lm, but we're doing it outside for SMD here)
 
@@
 ```{r}
-dat <- read_csv(here("hopkins_raw.csv")) |>  # this has 147 unique IDs so seems likely to be the mturk sample post attention check?
+dat <- read_csv(here("reconstruct_effect_sizes/hopkins_raw.csv")) |>  # this has 147 unique IDs so seems likely to be the mturk sample post attention check?
   select(ID, rating, condition) |> 

### 2024-04-02 reconstruct_effect_sizes/schechtman_es.Rmd
add other stuff

--- 2024-02-28 code/schechtman_es.Rmd
@@
 
-thing1 <- readMat(here("DataTest1.mat"))
+thing1 <- readMat(here("reconstruct_effect_sizes/DataTest1.mat"))
 
@@
 
-thing2 <- readMat(here("DataTest2.mat"))
+thing2 <- readMat(here("reconstruct_effect_sizes/DataTest2.mat"))
 
@@
 
-thing3 <- readMat(here("DataTest1_cases 4 13 18 omitted.mat")) # has 1-22
+thing3 <- readMat(here("reconstruct_effect_sizes/DataTest1_cases 4 13 18 omitted.mat")) # has 1-22
 
@@
 # figure out rescue
-full_data <- read_csv(here("subject_data_final_full_processed.csv"))
+full_data <- read_csv(here("reconstruct_effect_sizes/subject_data_final_full_processed.csv"))
 

### 2024-04-03 manuscript/manuscript.Rmd
typos and missing bib entries

@@
 bibliography: ["251rescue.bib"] # Replace with one or more of your own bibtex files. Better BibTeX for Zotero is your friend
-csl: apa7.csl # Use any CSL style. See https://www.zotero.org/styles for a good list. Ignored if citation_package: natbib
+csl: apa7.csl # Use any CSL
+nocite: |
+  @krauss2003, @ngo2019, @todd2016, @jara-ettinger2022, @porter2016, @birch2007, @child2018, @chou2016, @craig2014, @gong2019, @haimovitz2016, @hopkins2016, @paxton2012, @payne2008, @schechtman2010, @tarampi2016, @yeshurun2003
 link-citations: TRUE
@@
 For the goals of large-scale replication projects, it doesn't matter why any particular study failed to replicate, because the aim is to estimate the proportion of replication effects in a literature.
-In contrast, howver, when individual scientists attempt to replicate an effect with the goal of building on it, they do care about why an individual replication failed.
+In contrast, however, when individual scientists attempt to replicate an effect with the goal of building on it, they do care about why an individual replication failed.
 In an uncertain literature, scientists might not want to commit resources to studying extensions of an effect without first checking that they can measure that effect themselves.
@@
 Each project was also individually pre-registered by the student conducting it.
-The overall analysis is pre-registered at https://osf.io/5qz7v, individual pre-registrations are linked from TODO LINK.
+The overall analysis is pre-registered at https://osf.io/5qz7v, individual pre-registrations are linked from https://osf.io/vkbfw.
 We note one deviation from our pre-registration here: we pre-registered visual comparisons between original, first replication, and rescue projects using prediction intervals.
@@
 Students were required to think of reasons the first replication might not have worked, and address them if they could.
-A list of possible reasons and solutions TODO LINK was given to students.
+A list of possible reasons and solutions was given to students (https://osf.io/dfwk2).
 In general, we encouraged students to add manipulation checks as appropriate, and to adapt their materials to online studies, which may benefit from attention checks and/or shorter duration.
@@
 The rescue, powered using 2.5x the original sample [as recommended by @simonsohn2015], recovered a clear effect (albeit a much smaller one).
-There are reasons to think that some effect sizes in the literature may be inflated [@openscienceconsortium, @camerer2018], and it is also possible that changes to experiments or switches to online could result in noisier samples and thus smaller effect sizes.
+There are reasons to think that some effect sizes in the literature may be inflated [@openscienceconsortium; @camerer2018], and it is also possible that changes to experiments or switches to online could result in noisier samples and thus smaller effect sizes.
 Therefore, replications with smaller samples than the original (even if powered to the original effect size), may not be very diagnostic, and could potentially benefit from a re-replication.

### 2024-04-11 first-replication-reports/RPubs - Replication Report_files/embed.js
add one replication file

@@ -1,0 +1,51 @@
+(function () {
+    'use strict';
+    var _config = window.disqus_config;
+    window.disqus_config = function () {
+        if (_config) {
+            try {
+                _config.call(this);
+            } catch(err) {
+                console.error('There was a problem with the Disqus configuration.', err);
+            }
+        }
+        this.server_side = {
+  "disable_ads_android":"",
+  "inthread_repeat_comment_count":"8",
+  "default_placement_url":"",
+  "inthread_placement_url":"",
+  "under_ccpa":"1",
+  "can_disable_ads":"",
+  "lazyload_viewports":"2",
+  "service":"dynamic",
+  "sourceless_iframe":"1",
+  "experiment":"prebidrenderfix",
+  "inthread_count_children":"True",
+  "under_gdpr":"",
+  "inthread_multiple_ads":"True",
+  "bin":"embed:promoted_discovery:dynamic:prebidrenderfix:active",
+  "bottom_placement_url":"//tempest.services.disqus.com/ads-iframe/taboola/?position=bottom&shortname=rpubs&experiment=prebidrenderfix&variant=active&service=dynamic",
+  "variant":"active",
+  "forum_id":"1423073",
+  "recommendations_placement_url":"//tempest.services.disqus.com/ads-iframe/taboola_1x1/?position=recommendations&shortname=rpubs&experiment=prebidrenderfix&variant=active&service=dynamic",
+  "top_placement_url":"//tempest.services.disqus.com/ads-iframe/taboola/?position=top&shortname=rpubs&experiment=prebidrenderfix&variant=active&service=dynamic",
+  "inthread_trailing_comment_count":"0",
+  "is_private":"",
+  "skeleton_frame_enabled":"",
+  "disable_ads_ios":"",
+  "recs_outside_embed_enabled":"1",
+  "forum":{
+    "id":1423073,
+    "disable_disqus_branding":false,
+    "recommendation_placement":"top",
+    "recommendations_feature_enabled":true
+  },
+  "sandbox_ads":"1",
+  "inthread_leading_comment_count":"1",
+  "t":"1712874376"
+};
+    };
+})();
[…]

### 2024-04-11 first-replication-reports/RPubs - Replication Report_files/recommendations.js

@@ -1,0 +1,38 @@
+(function () {
+    'use strict';
+    var _config = window.disqus_recommendations_config;
+    window.disqus_recommendations_config = function () {
+        if (_config) {
+            try {
+                _config.call(this);
+            } catch(err) {
+                console.error('There was a problem with the Disqus configuration.', err);
+            }
+        }
+        this.server_side = {
+  "bin":"embed:promoted_discovery:dynamic:prebidrenderfix:active",
+  "disable_ads_ios":"",
+  "recs_outside_embed_enabled":"1",
+  "forum":{
+    "id":1423073,
+    "disable_disqus_branding":false,
+    "recommendation_placement":"top",
+    "recommendations_feature_enabled":true
+  },
+  "service":"dynamic",
+  "disable_ads_android":"",
+  "sourceless_iframe":"1",
+  "variant":"active",
+  "forum_id":"1423073",
+  "recommendations_placement_url":"//tempest.services.disqus.com/ads-iframe/taboola_1x1/?position=recommendations&shortname=rpubs&experiment=prebidrenderfix&variant=active&service=dynamic",
+  "experiment":"prebidrenderfix",
+  "default_placement_url":"",
+  "t":"1712874450",
+  "can_disable_ads":"",
+  "skeleton_frame_enabled":""
+};
+    };
+})();
[…]

### 2024-04-11 manuscript/manuscript.Rmd
more typo hunting

@@
 In psychology, large scale replication projects have found that around half of studies successfully replicate. 
-Across 100 studies with positive results, the reproducibility project in psychology (RP:P) replicated 36 - 47% depending on the metric for replication success [@openscienceconsortium].
+Across 100 studies with positive results, the reproducibility project in psychology (RP:P) replicated 36%-47% depending on the metric for replication success [@openscienceconsortium].
 With large multi-site samples, Many Labs 1 replicated 11/13 effects (84.6%), Many Labs 2 replicated 14/28 effects (50%), and Many Labs 3 replicated 3/10 effects (30%) [@klein2014; @klein2018; @ebersole2016].
@@
 
-For the goals of large-scale replication projects, it doesn't matter why any particular study failed to replicate, because the aim is to estimate the proportion of replication effects in a literature.
+For the goals of large-scale replication projects, it does not matter why any particular study failed to replicate, because the aim is to estimate the proportion of replication effects in a literature.
 In contrast, however, when individual scientists attempt to replicate an effect with the goal of building on it, they do care about why an individual replication failed.
@@
 Re-replication can serve as a way to test explanations for replication failure.
-While it's possible to speculate after the fact about potential causes of a single replication failure, in most circumstances these causes are hard to discern (absent clear evidence of errors).
+While it is possible to speculate after the fact about potential causes of a single replication failure, in most circumstances these causes are hard to discern (absent clear evidence of errors).
 In contrast, a second replication provides a chance to test explanations by making modifications -- as well as giving another chance for researchers to measure an effect of interest.
@@
 In general, we encouraged students to add manipulation checks as appropriate, and to adapt their materials to online studies, which may benefit from attention checks and/or shorter duration.
-For instance, the rescue of @paxton2012 switched from using the cognitive reflection task (CRT) which many online participants are over-familiar with for the newer CRT-2 which is less overused but attempts to measure the same construct [@thomson2016].
+For instance, the rescue of @paxton2012 switched from using the cognitive reflection task (CRT) which many online participants are over-familiar with to using the newer CRT-2 which is less overused but attempts to measure the same construct [@thomson2016].
 The rescue of @jara-ettinger2022 discovered that the replication had accidentally used an illustrated version of the stimuli rather than the photographic stimuli used in the original and used the photographic stimuli instead.
@@
 
-All of the correlations are presented in Figure \@ref(tab:cor-table).
+All of the correlations are presented in Table \@ref(tab:cor-table).
 The number of rescues is small, and many of these predictors are correlated, so we caution against over interpretation.
@@
 The replication found 0/8 correct justifications in the control and 0/11 in the guided thinking condition.
-While we can't know for sure what caused the non-replication, there were clear problems observable from the small final sample and low-quality responses.
+While we cannot know for sure what caused the non-replication, there were clear problems observable from the small final sample and low-quality responses.
 The rescue targeted these issues by adding a pre-screening that ensured participants were not familiar with the Monty Hall problem, switched the name of the problem (to reduce googling for answers), and had participants upload drawings for their justifications.
@@
 
-In some cases, increasing sample size and fixing internal validity issues in the replication seems to have led to a successful rescue (although we can't establish causality even in these cases).
+In some cases, increasing sample size and fixing internal validity issues in the replication seems to have led to a successful rescue (although we cannot establish causality even in these cases).
 However, there were other cases where the first replications had issues with a small sample or deviations in the implementation, and the rescue addressed these issues but still failed to replicate the original results.
-We can't predict what replication failures are likely to resolve given another, more thoughtful try, beyond the suggestion to review studies for best practices in experimental design and sampling [e.g., @experimentology2024].
+We cannot predict what replication failures are likely to resolve given another, more thoughtful try, beyond the suggestion to review studies for best practices in experimental design and sampling [e.g., @experimentology2024].
 

### 2024-04-12 manuscript/manuscript.Rmd
fix figure by adding a period

@@
                  "Krauss & Wang 2003",
-                 "Jara-Ettinger et al 2022")
+                 "Jara-Ettinger et al. 2022")
 smd_scale_big <- ggplot(for_plotting_d |> inner_join(big) |> 

### 2024-04-17 manuscript/manuscript.Rmd
more typos

@@
     affiliation: Psych
-  - name: Adani Abutto
+  - name: Adani B. Abutto
     affiliation: Psych
-  - name: Emily Chen
+  - name: Emily M. Chen
     affiliation: Psych
@@
   - name: Alexander Pereira
-    affiliation: Philosophy
+    affiliation: [Psych, Philosophy]
   - name: Jordan Troutman
@@
 In an uncertain literature, scientists might not want to commit resources to studying extensions of an effect without first checking that they can measure that effect themselves.
-For those individual scientists, it is much more important whether the replication failure is due to a fixable issue with the the replication or an intrinsic feature of the original result.
+For those individual scientists, it is much more important whether the replication failure is due to a fixable issue with  the replication or an intrinsic feature of the original result.
 
@@
 The original paper reported correct justification from 2/67 (`r round(2/67*100)`%) in the control condition and 13/34 (`r round(13/34*100)`%) in the guided thinking condition.
-The first replication struggled to recruit participants who were naive to the problem (an exclusion criterion), and many participants give very short text responses in the provided text box (only textual responses were allowed).
+The first replication struggled to recruit participants who were naive to the problem (an exclusion criterion), and many participants gave very short text responses in the provided text box (only textual responses were allowed).
 The replication found 0/8 correct justifications in the control and 0/11 in the guided thinking condition.
 While we cannot know for sure what caused the non-replication, there were clear problems observable from the small final sample and low-quality responses.
-The rescue targeted these issues by adding a pre-screening that ensured participants were not familiar with the Monty Hall problem, switched the name of the problem (to reduce googling for answers), and had participants upload drawings for their justifications.
+The rescue targeted these issues by adding a pre-screening that ensured participants were not familiar with the Monty Hall problem, reskinned the problem and changed its name (to reduce googling for answers), and had participants upload drawings for their justifications.
 Collectively, we believe these changes brought the rescue closer to the intent of the original.
@@
 There are reasons to think that some effect sizes in the literature may be inflated [@openscienceconsortium; @camerer2018], and it is also possible that changes to experiments or switches to online could result in noisier samples and thus smaller effect sizes.
-Therefore, replications with smaller samples than the original (even if powered to the original effect size), may not be very diagnostic, and could potentially benefit from a re-replication.
+Therefore, replications with smaller samples than the original (even if powered to the original effect size), may not be very diagnostic and could potentially benefit from a re-replication.
 

### 2024-04-19 individual-rescue-reports/RPubs - PSYCH 252 Rescue Final_files/embed.js
add reports, check numbers

@@ -1,0 +1,51 @@
+(function () {
+    'use strict';
+    var _config = window.disqus_config;
+    window.disqus_config = function () {
+        if (_config) {
+            try {
+                _config.call(this);
+            } catch(err) {
+                console.error('There was a problem with the Disqus configuration.', err);
+            }
+        }
+        this.server_side = {
+  "disable_ads_android":"",
+  "inthread_repeat_comment_count":"8",
+  "default_placement_url":"",
+  "inthread_placement_url":"",
+  "under_ccpa":"1",
+  "can_disable_ads":"",
+  "lazyload_viewports":"2",
+  "service":"dynamic",
+  "sourceless_iframe":"1",
+  "experiment":"network_default",
+  "inthread_count_children":"True",
+  "under_gdpr":"",
+  "inthread_multiple_ads":"True",
+  "bin":"embed:promoted_discovery:dynamic:network_default:fallthrough",
+  "bottom_placement_url":"//tempest.services.disqus.com/ads-iframe/taboola/?position=bottom&shortname=rpubs&experiment=network_default&variant=fallthrough&service=dynamic",
+  "variant":"fallthrough",
+  "forum_id":"1423073",
+  "recommendations_placement_url":"//tempest.services.disqus.com/ads-iframe/taboola_1x1/?position=recommendations&shortname=rpubs&experiment=network_default&variant=fallthrough&service=dynamic",
+  "top_placement_url":"//tempest.services.disqus.com/ads-iframe/taboola/?position=top&shortname=rpubs&experiment=network_default&variant=fallthrough&service=dynamic",
+  "inthread_trailing_comment_count":"0",
+  "is_private":"",
+  "skeleton_frame_enabled":"",
+  "disable_ads_ios":"",
+  "recs_outside_embed_enabled":"1",
+  "forum":{
+    "id":1423073,
+    "disable_disqus_branding":false,
+    "recommendation_placement":"top",
+    "recommendations_feature_enabled":true
+  },
+  "sandbox_ads":"1",
+  "inthread_leading_comment_count":"1",
+  "t":"1713547939"
+};
+    };
[…]

### 2024-04-19 individual-rescue-reports/RPubs - PSYCH 252 Rescue Final_files/recommendations.js

@@ -1,0 +1,38 @@
+(function () {
+    'use strict';
+    var _config = window.disqus_recommendations_config;
+    window.disqus_recommendations_config = function () {
+        if (_config) {
+            try {
+                _config.call(this);
+            } catch(err) {
+                console.error('There was a problem with the Disqus configuration.', err);
+            }
+        }
+        this.server_side = {
+  "bin":"embed:promoted_discovery:dynamic:network_default:fallthrough",
+  "disable_ads_ios":"",
+  "recs_outside_embed_enabled":"1",
+  "forum":{
+    "id":1423073,
+    "disable_disqus_branding":false,
+    "recommendation_placement":"top",
+    "recommendations_feature_enabled":true
+  },
+  "service":"dynamic",
+  "disable_ads_android":"",
+  "sourceless_iframe":"1",
+  "variant":"fallthrough",
+  "forum_id":"1423073",
+  "recommendations_placement_url":"//tempest.services.disqus.com/ads-iframe/taboola_1x1/?position=recommendations&shortname=rpubs&experiment=network_default&variant=fallthrough&service=dynamic",
+  "experiment":"network_default",
+  "default_placement_url":"",
+  "t":"1713547954",
+  "can_disable_ads":"",
+  "skeleton_frame_enabled":""
+};
+    };
+})();
[…]

### 2024-04-19 individual-rescue-reports/RPubs - PSYCH251 Final Project_files/a_data_004/config.js

@@ -1,1 +1,0 @@
-define({"tos_exempt_forums_shortnames":["somememes","qrt-dev","qrt-test","qrt-prd","myracehorse","test-prisamedia","wradio-colombia","kathimerini","https-www-kathimerini-gr","el-pais-1","diarioas","www-spectator-co-uk","https-new-dev-spectator-co-uk","drt-prd","drt-test","xoff-prd","xoffroad-test","tne-prod"],"register":{"ENABLE_CAPTCHA":true},"max_post_edit_days":7,"lounge":{"follow_channel_prompt_views":1,"motd_admin_url":"https://about.disqus.com/disqus-101","viglink":{"experiment_version":"v5","version":"v4"},"tracking":{"iframe_limit":5,"list":[{"url":"//referrer.disqus.com/juggler/stat.gif?event=data_tracker","forced_forums":["disqus"],"rate":0,"type":"img"}]},"font_options":[{"category":"serif","name":"Lora"},{"category":"sans-serif","name":"Montserrat"},{"category":"sans-serif","name":"Mulish"},{"category":"sans-serif","name":"Nunito"},{"category":"sans-serif","name":"Open+Sans"},{"category":"sans-serif","name":"Poppins"},{"category":"sans-serif","name":"Roboto"},{"category":"serif","name":"Roboto+Slab"},{"category":"sans-serif","name":"Source+Sans+Pro"},{"category":"serif","name":"Source+Serif+Pro"},{"category":"serif","name":"Spectral"},{"category":"sans-serif","name":"IBM+Plex+Sans"}],"cc_v2_start":"2023-04-18T17:50:00","motd_home_title":"Disqus Channels are live! ","motd_admin_title":"Introducing Disqus 101 best practice guides! \ud83d\udcda","motd_home_url":"https://disqus.com/channels/","REALTIME":{"BACKOFF_INTERVAL":4,"MAX_HANDSHAKE_FAILS":1,"XHR_ENABLED":false,"THREAD_STALE_DAYS":1},"motd_marketing_cta":"Explore now \u00bb","switches":{"customer_pulse_analytics":{"username":["orazumov_zeta","michaelyakovlev","commenting_privacy","andrei_ivanov_disqus","aivanov"]},"custom_reactions":true,"home_ads":{"channelDiscussions":true},"home_ads_prevented":{"forum":["iphoneincanada","thehill-v4","nmax","too
[…]

### 2024-04-19 individual-rescue-reports/RPubs - PSYCH251 Final Project_files/a_data_004/lounge.load.ba2637fd4af0519dea536ba02afb8ad1.js

@@ -1,1 +1,0 @@
-!function(){"use strict";var a=window.document,b={STYLES:"https://c.disquscdn.com/next/embed/styles/lounge.6f4270d496185595177ba1c5f1663b6a.css",RTL_STYLES:"https://c.disquscdn.com/next/embed/styles/lounge_rtl.0b3825e84072c4a261c0714ca087af09.css","lounge/main":"https://c.disquscdn.com/next/embed/lounge.bundle.066f15afb0175127f04c551b24a99310.js","remote/config":"https://disqus.com/next/config.js","common/vendor_extensions/highlight":"https://c.disquscdn.com/next/embed/highlight.6fbf348532f299e045c254c49c4dbedf.js"};window.require={baseUrl:"https://c.disquscdn.com/next/current/embed/embed",paths:["lounge/main","remote/config","common/vendor_extensions/highlight"].reduce(function(a,c){return a[c]=b[c].slice(0,-3),a},{})};var c=a.createElement("script");c.onload=function(){require(["common/main"],function(a){a.init("lounge",b)})},c.src="https://c.disquscdn.com/next/embed/common.bundle.a59842d31742a609955eb402e17bb0c3.js",a.body.appendChild(c)}();

### 2024-04-19 individual-rescue-reports/RPubs - PSYCH251 Final Project_files/embed.js

@@ -1,51 +1,0 @@
-(function () {
-    'use strict';
-    var _config = window.disqus_config;
-    window.disqus_config = function () {
-        if (_config) {
-            try {
-                _config.call(this);
-            } catch(err) {
-                console.error('There was a problem with the Disqus configuration.', err);
-            }
-        }
-        this.server_side = {
-  "disable_ads_android":"",
-  "inthread_repeat_comment_count":"8",
-  "default_placement_url":"",
-  "inthread_placement_url":"",
-  "under_ccpa":"1",
-  "can_disable_ads":"",
-  "lazyload_viewports":"2",
-  "service":"dynamic",
-  "sourceless_iframe":"1",
-  "experiment":"prebidrenderfix",
-  "inthread_count_children":"True",
-  "under_gdpr":"",
-  "inthread_multiple_ads":"True",
-  "bin":"embed:promoted_discovery:dynamic:prebidrenderfix:active",
-  "bottom_placement_url":"//tempest.services.disqus.com/ads-iframe/taboola/?position=bottom&shortname=rpubs&experiment=prebidrenderfix&variant=active&service=dynamic",
-  "variant":"active",
-  "forum_id":"1423073",
-  "recommendations_placement_url":"//tempest.services.disqus.com/ads-iframe/taboola_1x1/?position=recommendations&shortname=rpubs&experiment=prebidrenderfix&variant=active&service=dynamic",
-  "top_placement_url":"//tempest.services.disqus.com/ads-iframe/taboola/?position=top&shortname=rpubs&experiment=prebidrenderfix&variant=active&service=dynamic",
-  "inthread_trailing_comment_count":"0",
-  "is_private":"",
-  "skeleton_frame_enabled":"",
-  "disable_ads_ios":"",
-  "recs_outside_embed_enabled":"1",
-  "forum":{
-    "id":1423073,
-    "disable_disqus_branding":false,
-    "recommendation_placement":"top",
-    "recommendations_feature_enabled":true
-  },
-  "sandbox_ads":"1",
-  "inthread_leading_comment_count":"1",
-  "t":"1712096107"
-};
-    };
-})();
[…]

### 2024-04-19 individual-rescue-reports/RPubs - PSYCH251 Final Project_files/recommendations.js

@@ -1,38 +1,0 @@
-(function () {
-    'use strict';
-    var _config = window.disqus_recommendations_config;
-    window.disqus_recommendations_config = function () {
-        if (_config) {
-            try {
-                _config.call(this);
-            } catch(err) {
-                console.error('There was a problem with the Disqus configuration.', err);
-            }
-        }
-        this.server_side = {
-  "bin":"embed:promoted_discovery:dynamic:prebidrenderfix:active",
-  "disable_ads_ios":"",
-  "recs_outside_embed_enabled":"1",
-  "forum":{
-    "id":1423073,
-    "disable_disqus_branding":false,
-    "recommendation_placement":"top",
-    "recommendations_feature_enabled":true
-  },
-  "service":"dynamic",
-  "disable_ads_android":"",
-  "sourceless_iframe":"1",
-  "variant":"active",
-  "forum_id":"1423073",
-  "recommendations_placement_url":"//tempest.services.disqus.com/ads-iframe/taboola_1x1/?position=recommendations&shortname=rpubs&experiment=prebidrenderfix&variant=active&service=dynamic",
-  "experiment":"prebidrenderfix",
-  "default_placement_url":"",
-  "t":"1712096122",
-  "can_disable_ads":"",
-  "skeleton_frame_enabled":""
-};
-    };
-})();
[…]

### 2024-04-19 individual-rescue-reports/RPubs - Replication of Experiment 1 by Child, Oakhill, &amp; Garnham (2018, Language, Cognition and Neuroscience)_files/embed.js

@@ -1,0 +1,51 @@
+(function () {
+    'use strict';
+    var _config = window.disqus_config;
+    window.disqus_config = function () {
+        if (_config) {
+            try {
+                _config.call(this);
+            } catch(err) {
+                console.error('There was a problem with the Disqus configuration.', err);
+            }
+        }
+        this.server_side = {
+  "disable_ads_android":"",
+  "inthread_repeat_comment_count":"8",
+  "default_placement_url":"",
+  "inthread_placement_url":"",
+  "under_ccpa":"1",
+  "can_disable_ads":"",
+  "lazyload_viewports":"2",
+  "service":"dynamic",
+  "sourceless_iframe":"1",
+  "experiment":"network_default",
+  "inthread_count_children":"True",
+  "under_gdpr":"",
+  "inthread_multiple_ads":"True",
+  "bin":"embed:promoted_discovery:dynamic:network_default:fallthrough",
+  "bottom_placement_url":"//tempest.services.disqus.com/ads-iframe/taboola/?position=bottom&shortname=rpubs&experiment=network_default&variant=fallthrough&service=dynamic",
+  "variant":"fallthrough",
+  "forum_id":"1423073",
+  "recommendations_placement_url":"//tempest.services.disqus.com/ads-iframe/taboola_1x1/?position=recommendations&shortname=rpubs&experiment=network_default&variant=fallthrough&service=dynamic",
+  "top_placement_url":"//tempest.services.disqus.com/ads-iframe/taboola/?position=top&shortname=rpubs&experiment=network_default&variant=fallthrough&service=dynamic",
+  "inthread_trailing_comment_count":"0",
+  "is_private":"",
+  "skeleton_frame_enabled":"",
+  "disable_ads_ios":"",
+  "recs_outside_embed_enabled":"1",
+  "forum":{
+    "id":1423073,
+    "disable_disqus_branding":false,
+    "recommendation_placement":"top",
+    "recommendations_feature_enabled":true
+  },
+  "sandbox_ads":"1",
+  "inthread_leading_comment_count":"1",
+  "t":"1713547121"
+};
+    };
[…]

### 2024-04-19 individual-rescue-reports/RPubs - Replication of Experiment 1 by Child, Oakhill, &amp; Garnham (2018, Language, Cognition and Neuroscience)_files/recommendations.js

@@ -1,0 +1,38 @@
+(function () {
+    'use strict';
+    var _config = window.disqus_recommendations_config;
+    window.disqus_recommendations_config = function () {
+        if (_config) {
+            try {
+                _config.call(this);
+            } catch(err) {
+                console.error('There was a problem with the Disqus configuration.', err);
+            }
+        }
+        this.server_side = {
+  "bin":"embed:promoted_discovery:dynamic:network_default:fallthrough",
+  "disable_ads_ios":"",
+  "recs_outside_embed_enabled":"1",
+  "forum":{
+    "id":1423073,
+    "disable_disqus_branding":false,
+    "recommendation_placement":"top",
+    "recommendations_feature_enabled":true
+  },
+  "service":"dynamic",
+  "disable_ads_android":"",
+  "sourceless_iframe":"1",
+  "variant":"fallthrough",
+  "forum_id":"1423073",
+  "recommendations_placement_url":"//tempest.services.disqus.com/ads-iframe/taboola_1x1/?position=recommendations&shortname=rpubs&experiment=network_default&variant=fallthrough&service=dynamic",
+  "experiment":"network_default",
+  "default_placement_url":"",
+  "t":"1713547122",
+  "can_disable_ads":"",
+  "skeleton_frame_enabled":""
+};
+    };
+})();
[…]

### 2024-04-19 individual-rescue-reports/RPubs - Replication of Experiment 1 perspective-taking tasks by Tamrapi, Heydari &amp; Hegarty (2016, Psychological Science)_files/embed.js

@@ -1,0 +1,51 @@
+(function () {
+    'use strict';
+    var _config = window.disqus_config;
+    window.disqus_config = function () {
+        if (_config) {
+            try {
+                _config.call(this);
+            } catch(err) {
+                console.error('There was a problem with the Disqus configuration.', err);
+            }
+        }
+        this.server_side = {
+  "disable_ads_android":"",
+  "inthread_repeat_comment_count":"8",
+  "default_placement_url":"",
+  "inthread_placement_url":"",
+  "under_ccpa":"",
+  "can_disable_ads":"",
+  "lazyload_viewports":"2",
+  "service":"dynamic",
+  "sourceless_iframe":"1",
+  "experiment":"network_default",
+  "inthread_count_children":"True",
+  "under_gdpr":"",
+  "inthread_multiple_ads":"True",
+  "bin":"embed:promoted_discovery:dynamic:network_default:fallthrough",
+  "bottom_placement_url":"//tempest.services.disqus.com/ads-iframe/taboola/?position=bottom&shortname=rpubs&experiment=network_default&variant=fallthrough&service=dynamic",
+  "variant":"fallthrough",
+  "forum_id":"1423073",
+  "recommendations_placement_url":"//tempest.services.disqus.com/ads-iframe/taboola_1x1/?position=recommendations&shortname=rpubs&experiment=network_default&variant=fallthrough&service=dynamic",
+  "top_placement_url":"//tempest.services.disqus.com/ads-iframe/taboola/?position=top&shortname=rpubs&experiment=network_default&variant=fallthrough&service=dynamic",
+  "inthread_trailing_comment_count":"0",
+  "is_private":"",
+  "skeleton_frame_enabled":"",
+  "disable_ads_ios":"",
+  "recs_outside_embed_enabled":"1",
+  "forum":{
+    "id":1423073,
+    "disable_disqus_branding":false,
+    "recommendation_placement":"top",
+    "recommendations_feature_enabled":true
+  },
+  "sandbox_ads":"1",
+  "inthread_leading_comment_count":"1",
+  "t":"1713547382"
+};
+    };
[…]

### 2024-04-19 individual-rescue-reports/RPubs - Replication of Experiment 1 perspective-taking tasks by Tamrapi, Heydari &amp; Hegarty (2016, Psychological Science)_files/recommendations.js

@@ -1,0 +1,38 @@
+(function () {
+    'use strict';
+    var _config = window.disqus_recommendations_config;
+    window.disqus_recommendations_config = function () {
+        if (_config) {
+            try {
+                _config.call(this);
+            } catch(err) {
+                console.error('There was a problem with the Disqus configuration.', err);
+            }
+        }
+        this.server_side = {
+  "bin":"embed:promoted_discovery:dynamic:network_default:fallthrough",
+  "disable_ads_ios":"",
+  "recs_outside_embed_enabled":"1",
+  "forum":{
+    "id":1423073,
+    "disable_disqus_branding":false,
+    "recommendation_placement":"top",
+    "recommendations_feature_enabled":true
+  },
+  "service":"dynamic",
+  "disable_ads_android":"",
+  "sourceless_iframe":"1",
+  "variant":"fallthrough",
+  "forum_id":"1423073",
+  "recommendations_placement_url":"//tempest.services.disqus.com/ads-iframe/taboola_1x1/?position=recommendations&shortname=rpubs&experiment=network_default&variant=fallthrough&service=dynamic",
+  "experiment":"network_default",
+  "default_placement_url":"",
+  "t":"1713547391",
+  "can_disable_ads":"",
+  "skeleton_frame_enabled":""
+};
+    };
+})();
[…]

### 2024-04-19 individual-rescue-reports/RPubs - Rescue Replication of Development of Holistic Episodic Recollection by Ngo et al. (2019, Psychological Science)_files/embed.js

@@ -1,0 +1,51 @@
+(function () {
+    'use strict';
+    var _config = window.disqus_config;
+    window.disqus_config = function () {
+        if (_config) {
+            try {
+                _config.call(this);
+            } catch(err) {
+                console.error('There was a problem with the Disqus configuration.', err);
+            }
+        }
+        this.server_side = {
+  "disable_ads_android":"",
+  "inthread_repeat_comment_count":"8",
+  "default_placement_url":"",
+  "inthread_placement_url":"",
+  "under_ccpa":"",
+  "can_disable_ads":"",
+  "lazyload_viewports":"2",
+  "service":"dynamic",
+  "sourceless_iframe":"1",
+  "experiment":"network_default",
+  "inthread_count_children":"True",
+  "under_gdpr":"",
+  "inthread_multiple_ads":"True",
+  "bin":"embed:promoted_discovery:dynamic:network_default:fallthrough",
+  "bottom_placement_url":"//tempest.services.disqus.com/ads-iframe/taboola/?position=bottom&shortname=rpubs&experiment=network_default&variant=fallthrough&service=dynamic",
+  "variant":"fallthrough",
+  "forum_id":"1423073",
+  "recommendations_placement_url":"//tempest.services.disqus.com/ads-iframe/taboola_1x1/?position=recommendations&shortname=rpubs&experiment=network_default&variant=fallthrough&service=dynamic",
+  "top_placement_url":"//tempest.services.disqus.com/ads-iframe/taboola/?position=top&shortname=rpubs&experiment=network_default&variant=fallthrough&service=dynamic",
+  "inthread_trailing_comment_count":"0",
+  "is_private":"",
+  "skeleton_frame_enabled":"",
+  "disable_ads_ios":"",
+  "recs_outside_embed_enabled":"1",
+  "forum":{
+    "id":1423073,
+    "disable_disqus_branding":false,
+    "recommendation_placement":"top",
+    "recommendations_feature_enabled":true
+  },
+  "sandbox_ads":"1",
+  "inthread_leading_comment_count":"1",
+  "t":"1713547660"
+};
+    };
[…]

### 2024-04-19 individual-rescue-reports/RPubs - Rescue Replication of Development of Holistic Episodic Recollection by Ngo et al. (2019, Psychological Science)_files/recommendations.js

@@ -1,0 +1,38 @@
+(function () {
+    'use strict';
+    var _config = window.disqus_recommendations_config;
+    window.disqus_recommendations_config = function () {
+        if (_config) {
+            try {
+                _config.call(this);
+            } catch(err) {
+                console.error('There was a problem with the Disqus configuration.', err);
+            }
+        }
+        this.server_side = {
+  "bin":"embed:promoted_discovery:dynamic:network_default:fallthrough",
+  "disable_ads_ios":"",
+  "recs_outside_embed_enabled":"1",
+  "forum":{
+    "id":1423073,
+    "disable_disqus_branding":false,
+    "recommendation_placement":"top",
+    "recommendations_feature_enabled":true
+  },
+  "service":"dynamic",
+  "disable_ads_android":"",
+  "sourceless_iframe":"1",
+  "variant":"fallthrough",
+  "forum_id":"1423073",
+  "recommendations_placement_url":"//tempest.services.disqus.com/ads-iframe/taboola_1x1/?position=recommendations&shortname=rpubs&experiment=network_default&variant=fallthrough&service=dynamic",
+  "experiment":"network_default",
+  "default_placement_url":"",
+  "t":"1713547721",
+  "can_disable_ads":"",
+  "skeleton_frame_enabled":""
+};
+    };
+})();
[…]

### 2024-05-02 manuscript/manuscript.Rmd
fix typos, unsuccessful fight with CSL stuff
to render from latex you need to delete the {0}{1} after CSLReferences
... sigh

@@
         )+
-  labs(y="Standarized mean difference", x="")
+  labs(y="Standardized mean difference", x="")
 
@@
         )+
-  labs(y="Standarized mean difference", x="", )
+  labs(y="Standardized mean difference", x="", )
 
@@
 While we cannot know for sure what caused the non-replication, there were clear problems observable from the small final sample and low-quality responses.
-The rescue targeted these issues by adding a pre-screening that ensured participants were not familiar with the Monty Hall problem, reskinned the problem and changed its name (to reduce googling for answers), and had participants upload drawings for their justifications.
+The rescue targeted these issues by adding a pre-screening that ensured participants were not familiar with the Monty Hall problem, changed the content items for the problem and changed its name (to reduce googling for answers), and had participants upload drawings for their justifications.
 Collectively, we believe these changes brought the rescue closer to the intent of the original.
@@
 There are reasons to think that some effect sizes in the literature may be inflated [@openscienceconsortium; @camerer2018], and it is also possible that changes to experiments or switches to online could result in noisier samples and thus smaller effect sizes.
-Therefore, replications with smaller samples than the original (even if powered to the original effect size), may not be very diagnostic and could potentially benefit from a re-replication.
+Therefore, replications with smaller samples than the original (even if powered to the original effect size), may not be very diagnostic, and could potentially benefit from a re-replication.
 
@@
 <!-- Use this magic to place references here. -->
-
-::: {#refs}
-:::

### 2024-05-02 individual-rescue-reports/RPubs - Craig 2014 Rescue_files/embed.js
fixed a typo in data entry added (incomplete?) reports

@@ -1,0 +1,51 @@
+(function () {
+    'use strict';
+    var _config = window.disqus_config;
+    window.disqus_config = function () {
+        if (_config) {
+            try {
+                _config.call(this);
+            } catch(err) {
+                console.error('There was a problem with the Disqus configuration.', err);
+            }
+        }
+        this.server_side = {
+  "disable_ads_android":"",
+  "inthread_repeat_comment_count":"8",
+  "default_placement_url":"",
+  "inthread_placement_url":"",
+  "under_ccpa":"1",
+  "can_disable_ads":"",
+  "lazyload_viewports":"2",
+  "service":"dynamic",
+  "sourceless_iframe":"1",
+  "experiment":"network_default",
+  "inthread_count_children":"True",
+  "under_gdpr":"",
+  "inthread_multiple_ads":"True",
+  "bin":"embed:promoted_discovery:dynamic:network_default:fallthrough",
+  "bottom_placement_url":"//tempest.services.disqus.com/ads-iframe/taboola/?position=bottom&shortname=rpubs&experiment=network_default&variant=fallthrough&service=dynamic",
+  "variant":"fallthrough",
+  "forum_id":"1423073",
+  "recommendations_placement_url":"//tempest.services.disqus.com/ads-iframe/taboola_1x1/?position=recommendations&shortname=rpubs&experiment=network_default&variant=fallthrough&service=dynamic",
+  "top_placement_url":"//tempest.services.disqus.com/ads-iframe/taboola/?position=top&shortname=rpubs&experiment=network_default&variant=fallthrough&service=dynamic",
+  "inthread_trailing_comment_count":"0",
+  "is_private":"",
+  "skeleton_frame_enabled":"",
+  "disable_ads_ios":"",
+  "recs_outside_embed_enabled":"1",
+  "forum":{
+    "id":1423073,
+    "disable_disqus_branding":false,
+    "recommendation_placement":"top",
+    "recommendations_feature_enabled":true
+  },
+  "sandbox_ads":"1",
+  "inthread_leading_comment_count":"1",
+  "t":"1714687111"
+};
+    };
[…]

### 2024-05-02 individual-rescue-reports/RPubs - Final Project Proposal II_files/a_data_005/lounge.load.006bbc905574fc5153c7814eb2dc65a8.js

@@ -1,0 +1,1 @@
+!function(){"use strict";var a=window.document,b={STYLES:"https://c.disquscdn.com/next/embed/styles/lounge.a2345915325acf798c871e4957e4ea9f.css",RTL_STYLES:"https://c.disquscdn.com/next/embed/styles/lounge_rtl.1541fd3334c2492f03169f02e4abc09c.css","lounge/main":"https://c.disquscdn.com/next/embed/lounge.bundle.a932f0de230f1d945f3274de9e901830.js","remote/config":"https://disqus.com/next/config.js","common/vendor_extensions/highlight":"https://c.disquscdn.com/next/embed/highlight.6fbf348532f299e045c254c49c4dbedf.js"};window.require={baseUrl:"https://c.disquscdn.com/next/current/embed/embed",paths:["lounge/main","remote/config","common/vendor_extensions/highlight"].reduce(function(a,c){return a[c]=b[c].slice(0,-3),a},{})};var c=a.createElement("script");c.onload=function(){require(["common/main"],function(a){a.init("lounge",b)})},c.src="https://c.disquscdn.com/next/embed/common.bundle.a59842d31742a609955eb402e17bb0c3.js",a.body.appendChild(c)}();

### 2024-05-02 individual-rescue-reports/RPubs - Final Project Proposal II_files/recommendations.js

@@ -1,0 +1,38 @@
+(function () {
+    'use strict';
+    var _config = window.disqus_recommendations_config;
+    window.disqus_recommendations_config = function () {
+        if (_config) {
+            try {
+                _config.call(this);
+            } catch(err) {
+                console.error('There was a problem with the Disqus configuration.', err);
+            }
+        }
+        this.server_side = {
+  "bin":"embed:promoted_discovery:dynamic:network_default:fallthrough",
+  "disable_ads_ios":"",
+  "recs_outside_embed_enabled":"1",
+  "forum":{
+    "id":1423073,
+    "disable_disqus_branding":false,
+    "recommendation_placement":"top",
+    "recommendations_feature_enabled":true
+  },
+  "service":"dynamic",
+  "disable_ads_android":"",
+  "sourceless_iframe":"1",
+  "variant":"fallthrough",
+  "forum_id":"1423073",
+  "recommendations_placement_url":"//tempest.services.disqus.com/ads-iframe/taboola_1x1/?position=recommendations&shortname=rpubs&experiment=network_default&variant=fallthrough&service=dynamic",
+  "experiment":"network_default",
+  "default_placement_url":"",
+  "t":"1714687245",
+  "can_disable_ads":"",
+  "skeleton_frame_enabled":""
+};
+    };
+})();
[…]

### 2024-05-02 individual-rescue-reports/RPubs - PSYCH251 Replication Rescue Project - Full Report_files/a_data_005/config.js

@@ -1,0 +1,1 @@
+define({"tos_exempt_forums_shortnames":["somememes","qrt-dev","qrt-test","qrt-prd","myracehorse","test-prisamedia","wradio-colombia","kathimerini","https-www-kathimerini-gr","el-pais-1","diarioas","www-spectator-co-uk","https-new-dev-spectator-co-uk","drt-prd","drt-test","xoff-prd","xoffroad-test","tne-prod","prod-expresso"],"register":{"ENABLE_CAPTCHA":true},"max_post_edit_days":7,"lounge":{"follow_channel_prompt_views":1,"motd_admin_url":"https://blog.disqus.com/new-disqus-wordpress-plugin-v3-1","viglink":{"experiment_version":"v5","version":"v4"},"tracking":{"iframe_limit":5,"list":[{"url":"//referrer.disqus.com/juggler/stat.gif?event=data_tracker","forced_forums":["disqus"],"rate":0,"type":"img"}]},"font_options":[{"category":"serif","name":"Lora"},{"category":"sans-serif","name":"Montserrat"},{"category":"sans-serif","name":"Mulish"},{"category":"sans-serif","name":"Nunito"},{"category":"sans-serif","name":"Open+Sans"},{"category":"sans-serif","name":"Poppins"},{"category":"sans-serif","name":"Roboto"},{"category":"serif","name":"Roboto+Slab"},{"category":"sans-serif","name":"Source+Sans+Pro"},{"category":"serif","name":"Source+Serif+Pro"},{"category":"serif","name":"Spectral"},{"category":"sans-serif","name":"IBM+Plex+Sans"}],"cc_v2_start":"2023-04-18T17:50:00","motd_home_title":"\ud83c\udf17 New Science & Nature Channel is live! \ud83c\udf17 ","motd_admin_title":"Announcing a fresh update to our WordPress plugin! \ud83d\udcda","motd_home_url":"https://disqus.com/channel/discussscienceandnature/","REALTIME":{"BACKOFF_INTERVAL":4,"MAX_HANDSHAKE_FAILS":1,"XHR_ENABLED":false,"THREAD_STALE_DAYS":1},"motd_marketing_cta":"Join the fun \u00bb","switches":{"customer_pulse_analytics":{"username":["orazumov_zeta","michaelyakovlev","commenting_privacy","andrei_ivanov_disqus","aivanov"]},"custom_reactions":true,"home_ad
[…]

### 2024-05-02 individual-rescue-reports/RPubs - PSYCH251 Replication Rescue Project - Full Report_files/recommendations.js

@@ -1,0 +1,38 @@
+(function () {
+    'use strict';
+    var _config = window.disqus_recommendations_config;
+    window.disqus_recommendations_config = function () {
+        if (_config) {
+            try {
+                _config.call(this);
+            } catch(err) {
+                console.error('There was a problem with the Disqus configuration.', err);
+            }
+        }
+        this.server_side = {
+  "bin":"embed:promoted_discovery:dynamic:network_default:fallthrough",
+  "disable_ads_ios":"",
+  "recs_outside_embed_enabled":"1",
+  "forum":{
+    "id":1423073,
+    "disable_disqus_branding":false,
+    "recommendation_placement":"top",
+    "recommendations_feature_enabled":true
+  },
+  "service":"dynamic",
+  "disable_ads_android":"",
+  "sourceless_iframe":"1",
+  "variant":"fallthrough",
+  "forum_id":"1423073",
+  "recommendations_placement_url":"//tempest.services.disqus.com/ads-iframe/taboola_1x1/?position=recommendations&shortname=rpubs&experiment=network_default&variant=fallthrough&service=dynamic",
+  "experiment":"network_default",
+  "default_placement_url":"",
+  "t":"1714686873",
+  "can_disable_ads":"",
+  "skeleton_frame_enabled":""
+};
+    };
+})();
[…]

### 2024-05-02 individual-rescue-reports/RPubs - Paxton et al., (2012) Experiment 1 Rescue_files/embed.js

@@ -1,0 +1,51 @@
+(function () {
+    'use strict';
+    var _config = window.disqus_config;
+    window.disqus_config = function () {
+        if (_config) {
+            try {
+                _config.call(this);
+            } catch(err) {
+                console.error('There was a problem with the Disqus configuration.', err);
+            }
+        }
+        this.server_side = {
+  "disable_ads_android":"",
+  "inthread_repeat_comment_count":"8",
+  "default_placement_url":"",
+  "inthread_placement_url":"",
+  "under_ccpa":"1",
+  "can_disable_ads":"",
+  "lazyload_viewports":"2",
+  "service":"dynamic",
+  "sourceless_iframe":"1",
+  "experiment":"network_default",
+  "inthread_count_children":"True",
+  "under_gdpr":"",
+  "inthread_multiple_ads":"True",
+  "bin":"embed:promoted_discovery:dynamic:network_default:fallthrough",
+  "bottom_placement_url":"//tempest.services.disqus.com/ads-iframe/taboola/?position=bottom&shortname=rpubs&experiment=network_default&variant=fallthrough&service=dynamic",
+  "variant":"fallthrough",
+  "forum_id":"1423073",
+  "recommendations_placement_url":"//tempest.services.disqus.com/ads-iframe/taboola_1x1/?position=recommendations&shortname=rpubs&experiment=network_default&variant=fallthrough&service=dynamic",
+  "top_placement_url":"//tempest.services.disqus.com/ads-iframe/taboola/?position=top&shortname=rpubs&experiment=network_default&variant=fallthrough&service=dynamic",
+  "inthread_trailing_comment_count":"0",
+  "is_private":"",
+  "skeleton_frame_enabled":"",
+  "disable_ads_ios":"",
+  "recs_outside_embed_enabled":"1",
+  "forum":{
+    "id":1423073,
+    "disable_disqus_branding":false,
+    "recommendation_placement":"top",
+    "recommendations_feature_enabled":true
+  },
+  "sandbox_ads":"1",
+  "inthread_leading_comment_count":"1",
+  "t":"1714687193"
+};
+    };
[…]

### 2024-05-02 individual-rescue-reports/RPubs - Paxton et al., (2012) Experiment 1 Rescue_files/recommendations.js

@@ -1,0 +1,38 @@
+(function () {
+    'use strict';
+    var _config = window.disqus_recommendations_config;
+    window.disqus_recommendations_config = function () {
+        if (_config) {
+            try {
+                _config.call(this);
+            } catch(err) {
+                console.error('There was a problem with the Disqus configuration.', err);
+            }
+        }
+        this.server_side = {
+  "bin":"embed:promoted_discovery:dynamic:network_default:fallthrough",
+  "disable_ads_ios":"",
+  "recs_outside_embed_enabled":"1",
+  "forum":{
+    "id":1423073,
+    "disable_disqus_branding":false,
+    "recommendation_placement":"top",
+    "recommendations_feature_enabled":true
+  },
+  "service":"dynamic",
+  "disable_ads_android":"",
+  "sourceless_iframe":"1",
+  "variant":"fallthrough",
+  "forum_id":"1423073",
+  "recommendations_placement_url":"//tempest.services.disqus.com/ads-iframe/taboola_1x1/?position=recommendations&shortname=rpubs&experiment=network_default&variant=fallthrough&service=dynamic",
+  "experiment":"network_default",
+  "default_placement_url":"",
+  "t":"1714687163",
+  "can_disable_ads":"",
+  "skeleton_frame_enabled":""
+};
+    };
+})();
[…]

### 2024-05-02 individual-rescue-reports/RPubs - Replication of Sleep Preferentially Enhances Memory for Emotional Components of Scenes by Payne, Stickgold, Swanberg and Kensinger (2008, Psychological Science) Pilot B 12-5_files/embed.js

@@ -1,0 +1,51 @@
+(function () {
+    'use strict';
+    var _config = window.disqus_config;
+    window.disqus_config = function () {
+        if (_config) {
+            try {
+                _config.call(this);
+            } catch(err) {
+                console.error('There was a problem with the Disqus configuration.', err);
+            }
+        }
+        this.server_side = {
+  "disable_ads_android":"",
+  "inthread_repeat_comment_count":"8",
+  "default_placement_url":"",
+  "inthread_placement_url":"",
+  "under_ccpa":"",
+  "can_disable_ads":"",
+  "lazyload_viewports":"2",
+  "service":"dynamic",
+  "sourceless_iframe":"1",
+  "experiment":"network_default",
+  "inthread_count_children":"True",
+  "under_gdpr":"",
+  "inthread_multiple_ads":"True",
+  "bin":"embed:promoted_discovery:dynamic:network_default:fallthrough",
+  "bottom_placement_url":"//tempest.services.disqus.com/ads-iframe/taboola/?position=bottom&shortname=rpubs&experiment=network_default&variant=fallthrough&service=dynamic",
+  "variant":"fallthrough",
+  "forum_id":"1423073",
+  "recommendations_placement_url":"//tempest.services.disqus.com/ads-iframe/taboola_1x1/?position=recommendations&shortname=rpubs&experiment=network_default&variant=fallthrough&service=dynamic",
+  "top_placement_url":"//tempest.services.disqus.com/ads-iframe/taboola/?position=top&shortname=rpubs&experiment=network_default&variant=fallthrough&service=dynamic",
+  "inthread_trailing_comment_count":"0",
+  "is_private":"",
+  "skeleton_frame_enabled":"",
+  "disable_ads_ios":"",
+  "recs_outside_embed_enabled":"1",
+  "forum":{
+    "id":1423073,
+    "disable_disqus_branding":false,
+    "recommendation_placement":"top",
+    "recommendations_feature_enabled":true
+  },
+  "sandbox_ads":"1",
+  "inthread_leading_comment_count":"1",
+  "t":"1714686816"
+};
+    };
[…]

### 2024-06-12 manuscript/coverletter/collabra1.tex
submit collabra

\documentclass{stanfordletter}
%\makelabels
\usepackage{url}
\begin{document}
	\name{Veronica Boyce}
	\signature{\vspace{-35pt} Veronica Boyce, \\ on behalf of the author team}

	\begin{letter}{Professor Don van Ravenzwaaij \\ Editor-in-Chief \\ Collabra: Psychology }

          \opening{Dear Dr. van Ravenzwaaij,} 
          This submission contains the manuscript ``Estimating the replicability of psychology experiments after an initial failure to replicate'' which we are submitting to Collabra: Psychology for publication as an original research report.

          The manuscript reports on 17 re-replications of psychology experiments for which an original replication had failed.  The original failures to replicate come from Boyce et al. 2023 (\url{https://doi.org/10.1098/rsos.231240}), and the current work is a follow-up to that study.

          As a practical matter, scientists in disciplines with low replicability rates (like psychology) will often face the question of what to do after a failed replication attempt. When does it make sense to try again and when does it make sense to move on? There is a very limited literature on how successful re-replications that attempt to ``rescue'' a failed replication are -- we are only aware of Many Labs 5 (Ebersole et al. 2020) which re-replicated 11 experiments from the Reproducibility Project: Psychology (Open Science Consortium, 2015) in high-resource settings with expert input.

          We build on this by looking at the rate of re-replication when both the first replication and re-replication are from early career researchers. Our current study provides an estimate of how often one can successfully ``rescue'' an effect after a failed replication by addressing possible causes of the first replication's failure. In 5/17 of these ``rescue'' projects (29\%), the ``rescue'' study mostly or fully replicated the original results, albeit with a smaller effect size; in the other 12, the second replication also failed.

          We speculate that successful rescue projects were due to larger sample sizes or methodological changes such as attention checks. and we discuss some of the individual projects as case studies.

          This work has been uploaded to the preprint server PsyArxiv at \url{https://osf.io/preprints/psyarxiv/an3yb}.

          This manuscript is not under review at any other venue. Please let us know if you need any further information in
          connection with this submission.

          We look forward to hearing from you regarding the manuscript!

          \closing{Sincerely,}

%		Please provide a cover letter either as a file or pasted into the box when indicated. Cover letters should be no more than 1-page of A4 in length. Cover letters are only made available to the Editors.
%		
%		A good cover letter can help the Editor understand how the study relates to previously published work, and your motivations for completing the study and submitting it to Royal Society Open Science.
%		
%		Your cover should ideally include:
%		
%		An explanation of how your work is appropriate for Royal Society Open Science;
%		A summary of the scientific validity of the work. We do not make judgements about impact or interest in the journal, but we do expect papers to be high-quality, and to represent a meaningful advance in the field;
%		The reason for choosing the selected article type;
%		Any previous interactions you have had with Royal Society Open Science editorial office staff or Editors regarding the submitted manuscript (for instance, at a conference);
%		We welcome the use of preprint servers, but we encourage you to declare it if you have uploaded the manuscript to a preprint server prior to submitting to the journal;
%		Where applicable, a short explanation of the sampling techniques used, statistical tests employed, and sample sizes chosen (ie the statistical power of the study);
%		Any other matters you would like to make the Editors aware of.
%		
%		If similar papers to yours have been recently published in Royal Society Open Science, you may wish to include a link to one or more of these publications in your cover letter as additional context for choosing the journal to publish your study.
%		
%		Your cover letter should not be a repetition of your paper’s abstract or introduction. Your manuscript may be returned to you if you duplicate your abstract or introduction in your cover letter.
%		
%		As you will be asked to include preferred or non-preferred referee suggestions elsewhere in the submission process, you do not need to include these details in your cover letter, unless there are specific matters you wish to highlight to the Editors regarding your suggestions.
%		
%		Finally, prior to submitting your manuscript and cover letter, it is recommended that you not only check your spelling but that you have included the correct journal title within the cover letter. 
	\end{letter}

\end{document}

### 2024-06-12 manuscript/manuscript_anon.Rmd
submit collabra

--- 2024-05-02 manuscript/manuscript.Rmd
@@
 author:
-  - name: Veronica Boyce
-    affiliation: Psych
-    footnote:
-      - corresp
-  - name: Ben Prystawski
-    affiliation: Psych
-  - name: Adani B. Abutto
-    affiliation: Psych
-  - name: Emily M. Chen
-    affiliation: Psych
-  - name: Ziwen Chen
-    affiliation: GSB
-  - name: Howard Chiu
-    affiliation: Edu
-  - name: Irmak Ergin
-    affiliation: Psych
-  - name: Anmol Gupta
-    affiliation: Psych
-  - name: Chuqi Hu
-    affiliation: Symsys
-  - name: Bendix Kemmann
-    affiliation: Philosophy
-  - name: Nastasia Klevak
-    affiliation: Psych
-  - name: Verity Y. Q. Lua
-    affiliation: Psych
-  - name: Mateus M. Mazzaferro
-    affiliation: Edu
-  - name: Khaing Mon
-    affiliation: Symsys
-  - name: Dan Ogunbamowo
-    affiliation: Psych
-  - name: Alexander Pereira
-    affiliation: [Psych, Philosophy]
-  - name: Jordan Troutman
-    affiliation: CS
-  - name: Sarah Tung
-    affiliation: Psych
-  - name: Raphael Uricher
-    affiliation: Psych
-  - name: Michael C. Frank
-    affiliation: Psych
-address:
-  - code: Psych
-    address: Department of Psychology, Stanford University
-  - code: GSB
-    address: Graduate School of Business, Stanford University
-  - code: Edu
-    address: Graduate School of Education, Stanford University
-  - code: Symsys
-    address: Symbolic Systems Program, Stanford University
-  - code: Philosophy
-    address: Department of Philosophy, Stanford University
-  - code: CS
-    address: Department of Computer Science, Stanford University
-footnote:
-  - code: corresp
-    text: "Corresponding author. Email: vboyce@stanford.edu"
+  - name: anonymous
 bibliography: ["251rescue.bib"] # Replace with one or more of your own bibtex files. Better BibTeX for Zotero is your friend
@@
 Even when a significant effect was recovered, the effect size was much diminished [@ebersole2020].
-<!-- We could frame @ebersole2020 as an attempt to recover the original effects of the 9 studies with significant original effects and non-significant RP:P effects by a combination of high power and design tweaks.
--->
 The re-replication success rate was thus 2/9 (22%) for studies with non-significant first replications, under favorable, high-resource circumstances.
-
-<!-- While it is tempting to speculate on the reasons for failed replications, the @gilbert2016 and @ebersole2020 example shows these speculations on causes of replication failure do not always pan out in re-replication outcomes.
--->
 
@@
 
-PSYCH 251 is a graduate-level experimental methods class taught by MCF.
+[class name] is a graduate-level experimental methods class taught by [anonymous].
 In previous years, students have conducted replication projects [@boyce2023; @hawkins2018].
@@
 
-A spreadsheet of projects, individual project write-ups (both first replications and rescues), individual project data and analyses for rescue projects, and the analytic code for this paper are all available at https://osf.io/cyk5w/.
+A spreadsheet of projects, individual project write-ups (both first replications and rescues), individual project data and analyses for rescue projects, and the analytic code for this paper are all available at https://osf.io/cyk5w/?view_only=620212fb6b55490d9ae3a555e7b58eca.
 
@@
 The rescue removed the unwieldy drop down menus and opted to have participants press keys on the keyboard to indicate the direction of a turn, which seemed like a more natural interface.
-Once experimental designs and analytic plans were approved by class TAs (VB and BP), students pre-registered and ran their samples.
+Once experimental designs and analytic plans were approved by class TAs [anonymized], students pre-registered and ran their samples.
 
-With one exception, samples were collected on Prolific [the rescue of @yeshurun2003 ran in-person on the Stanford student subject pool].
+With one exception, samples were collected on Prolific [the rescue of @yeshurun2003 ran in-person on the [anonymized university] student subject pool].
 We tried to power studies adequately [with a target of 2.5x original following @simonsohn2015], but due to cost constraints, not all studies were powered at this level.
@@
 We followed @boyce2023 in the properties of the studies we measured and how we quantified replication success. 
-Each project was rated on the basis of subjective replication success (on a 0--1 scale) by both MCF and one of VB and BP.
+Each project was rated on the basis of subjective replication success (on a 0--1 scale) by both [anonymous] and one of [also anonymous].
 We thought about replication in terms of general match in key study results (direction, magnitude, and significance), rather than focusing on any singular numeric result or significance cut-off.
@@
 
-<!--Visualizations of the statistical consistency between the original and each replication are shown in TODO FIGURE.
-The range around the open circle is the 95% predictive interval, representing the interval where, assuming that both are drawn from the same distribution, the replication will fall 95% of the time, given the precision (standard deviation) of the replication [@patil2016].
-We again impute a heterogeneity value of $\tau=.21$ SMD for the construction of the prediction intervals.-->
-
-<!--* We will use p-original to evaluate how consistent the original effect size is with the totality of replications.
-We expect there to be a small number of replications, so we will impute the heterogeneity value as in https://osf.io/preprints/psyarxiv/dpyn6/.
--->
-
 Overall, allowing for a heterogeneity level of $\tau$=.21 SMD, a number of original effects are not statistically consistent with rescue and replication effects.
@@
 Table \@ref(tab:tab-size) shows the closeness of each first replication and rescue according to the classification scheme from @lebel2018.
-<!-- TODO CLOSENESS NUMBERS SHOULD BE DOUBLE CHECKED AND FIRST REPS REVISED AS NEEDED -->
 
@@
 That said, it is possible that different results might be obtained in better-resourced settings, by scientists with more expertise and more time.
-<!-- were false positives, we merely claim the original results do not support cumulative research by early-career researchers under the constrained conditions we tested. -->
 
@@
 
+# Contributions {.unnumbered}
+
+- Contributed to conception and design: VB and MCF
+- Contributed to acquisition of data: all authors except VB, BP, and MCF
+- Contributed to analysis and interpretation of data: all authors
+- Drafted and/or revised the article: VB, BP, and MCF
+- Approved the submitted version for publication: all authors
+
+<!--VB and MCF conceptualized the study. BP contributed project administration, VB contributed formal analysis, and MCF contributed supervision.
+
+Authors other than VB, BP, and MCF each designed, conducted, analyzed, and wrote up one of the rescue projects -- these authors contributed to investigation, formal analysis, and visualization.
+
+VB wrote the first draft, BP and MCF contributed editing, and all authors reviewed the final manuscript.-->
+
 # Acknowledgements {.unnumbered}
@@
 We thank the other members of the PSYCH 251 teaching team and students for feedback on projects.
+
+# Funding {.unnumbered}
 Data collection was supported by funding from the Stanford Departments of Psychology and Philosophy, Graduate School of Education, and the Symbolic Systems program.
 
-# Author Contributions {.unnumbered}
+# Competing Interests {.unnumbered}
+The authors declare no competing interests.
 
-VB and MCF conceptualized the study. BP contributed project administration, VB contributed formal analysis, and MCF contributed supervision.
+# Data accessibility {.unnumbered}
 
-Authors other than VB, BP, and MCF each designed, conducted, analyzed, and wrote up one of the rescue projects -- these authors contributed to investigation, formal analysis, and visualization.
-
-VB wrote the first draft, BP and MCF contributed editing, and all authors reviewed the final manuscript.
+A spreadsheet of projects, individual project write-ups (both first replications and rescues), individual project data and analyses for rescue projects, and the analytic code for this paper are all available at https://osf.io/cyk5w.
 

### 2024-06-12 manuscript/title_page.Rmd
submit collabra

--- 2024-04-17 manuscript/manuscript.Rmd
@@
   - code: Psych
-    address: Department of Psychology, Stanford University
+    address: Department of Psychology, Stanford University, Stanford, CA, USA
   - code: GSB
-    address: Graduate School of Business, Stanford University
+    address: Graduate School of Business, Stanford University, Stanford, CA, USA
   - code: Edu
-    address: Graduate School of Education, Stanford University
+    address: Graduate School of Education, Stanford University, Stanford, CA, USA
   - code: Symsys
-    address: Symbolic Systems Program, Stanford University
+    address: Symbolic Systems Program, Stanford University, Stanford, CA, USA
   - code: Philosophy
-    address: Department of Philosophy, Stanford University
+    address: Department of Philosophy, Stanford University, Stanford, CA, USA
   - code: CS
-    address: Department of Computer Science, Stanford University
+    address: Department of Computer Science, Stanford University, Stanford, CA, USA
 footnote:
@@
 csl: apa7.csl # Use any CSL
-nocite: |
-  @krauss2003, @ngo2019, @todd2016, @jara-ettinger2022, @porter2016, @birch2007, @child2018, @chou2016, @craig2014, @gong2019, @haimovitz2016, @hopkins2016, @paxton2012, @payne2008, @schechtman2010, @tarampi2016, @yeshurun2003
 link-citations: TRUE
@@
 
-```{r setup, include=FALSE}
-knitr::opts_chunk$set(echo = FALSE) # By default, hide code; set to TRUE to see code
-#knitr::opts_chunk$set(fig.pos = 'th') # Places figures at top or here
-knitr::opts_chunk$set(out.width = '100%', dpi=300,
-                      fig.width=8, fig.width=8) # Figure resolution and size
-knitr::opts_chunk$set(fig.env="figure") # Latex figure environment
-
-options(knitr.table.format="latex") # For kable tables to work without setting format option
-
-knitr::opts_chunk$set(echo=F, warning=F, message=F)#dev = "png", dev.args = list(type = "cairo-png")
- library("papaja")
-library("bookdown")
-library("rticles")
- library(here)
- library(tidyverse)
- library(brms)
-library(tidybayes)
-library(kableExtra)
-library(viridis)
-library(cowplot)
-library(ggthemes)
-library(reshape2)
-library(knitr)
-library(kableExtra)
-library(metafor)
-#r_refs("r-references.bib", append=F)
-theme_set(theme_bw())
-options(knitr.table.format = "pdf")
-
-model_location="code/models"
-
-```
-
-```{r}
-
-library(tidyverse)
-library(testthat)
-all_projects <- read_csv("https://raw.githubusercontent.com/vboyce/251-254-MA/main/data/raw_data.csv")
-
-filtered <- all_projects |>
-  mutate(sub_rep=ifelse(replicated_instructor_code==replicated_report_code, 
-                 replicated_report_code, 
-                 adjudicated_replication_code)) |> 
-  filter(sub_rep %in% c(0,.25, .5)) |> 
-  filter(include!="no") |> 
-  filter(target_N <=200) |> 
-  filter(academic_year %in% c("2015-2016", "2016-2017", "2017-2018", "2018-2019", 
-                              "2019-2020", "2020-2021","2021-2022", "2022-2023")) 
-# what we really want is whether there was a github, but that column is private and so not in the public raw data
-# but 2015 is the first year where we have github links
-
-#test_that("number of rows in filtered", {expect_equal(nrow(filtered),49)})
-
-#given this sample, we then sought original replicator permission, 
-#since it would involve sharing their repo and write-up with a new student
-#which wouldn't have been anticipated at original classtime
-
-#we heard back from 29 students of the 49 we attempted to contact 
-#(1 we couldn't contact due to email bouncing) 
-#2 responses were negative, rest were positive, for 27 options
-
-approved <- c("krauss2003","yeshurun2003", "daffner2000", "ngo2019",
-              "child2018", "schechtman2010", "payne2008", "paxton2012",
-              "hart2018", "lewis2015", "tarampi2016", "jara-ettinger2022",
-              "porter_2016_1", "hopkins2016", "birch2007_2", "gong2019",
-              "correll2007", "pilditch2019", "daw2011", "dehaene2009",
-              "sofer2015", "todd2016_1", "chou2016", "mani2013", 
-              "haimovitz2016_2", "haimovitz2016_1", "craig2014")
-options <- filtered |> filter(target_lastauthor_year %in% approved)
-
-#test_that("number of rows in options", {expect_equal(nrow(options),27)})
-
-# students were then given this list and the opportunity to choose what to do
-
-# projects that we believe are being rescued (as of Oct 23)
-
-chosen <- c("birch2007_2", "jara-ettinger2022", "porter_2016_1",
-            "hopkins2016", "yeshurun2003", "craig2014", "tarampi2016", 
-            "mani2013", "krauss2003", "schechtman2010", "child2018",
-            "haimovitz2016_1", "todd2016_1", "haimovitz2016_2", "payne2008", 
-            "paxton2012", "dehaene2009", "chou2016", "ngo2019", "gong2019")
-
-rescue_started <- options |> filter(target_lastauthor_year %in% chosen)
-
-#test_that("number of rows in final sample", {expect_equal(nrow(final_sample),21)})
-
-```
-
-```{r}
-d <- read_csv(here("data", "combined_data.csv")) |> 
-  select(target_lastauthor_year, type, on_turk, repeated_measure, N, raw_stat, 
-         same_direction, replication_score, closeness, subfield, target_year, stanford_internal, 
-         open_data, open_materials, within_between, single_vignette, cost, name_pretty)
-
-source(here("code","helper","parse_stats.R"))
-
-parsed_d <- d |> 
-  mutate(raw_stat=gsub(" ","",raw_stat),
-         calc=pmap(list(raw_stat, within_between,N), do_parsing)) |> 
-  unnest(cols=c(calc), names_sep="_") |> 
-    mutate(
-    calc_d_calc=case_when(
-      type=="original" ~ abs(calc_d_calc),
-      same_direction=="yes" ~ abs(calc_d_calc),
-      same_direction=="no" ~ -abs(calc_d_calc),
-      T ~ as.numeric(NA)
-      ),
-    calc_ES=case_when(
-      type=="original" ~ abs(calc_ES),
-      same_direction=="yes" ~ abs(calc_ES),
-      same_direction=="no" ~ -abs(calc_ES),
-      T ~ as.numeric(NA)
-      ),
-    type=factor(type, levels=c("original", "rep1", "rescue", "additional"))
-    ) |> 
-  rowwise()
-
-num_proj <- parsed_d |> filter(type=="rescue") |> nrow()
-
-cost <- parsed_d |> filter(type=="rescue") |> ungroup() |>  summarize(total=sum(cost, na.rm=T))
-```
-
-<!---------------------- Abstract --------------------->
-
-::: {.abstract data-latex="" lang="en"}
-When a replication fails, scientists have to decide whether to make a second attempt or move on.
-Psychology researchers who attempt to replicate studies often face this decision, given the empirical rate of replication success in psychology, which is lower than desired.
-Here, we report 17 re-replications of experiments for which an original replication had failed.
-In 5/17 of these "rescue" projects (29%), the "rescue" study mostly or fully replicated the original results, albeit with a smaller effect size; in the other 12, the second replication was also judged to have failed.
-We speculate that successful rescue projects were due to larger sample sizes or methodological changes such as attention checks.
-In the absence of obvious weaknesses in a failed replication study's sample or procedure, however, it may be most efficient to stop pursuing an effect after a single failed replication.
-:::
-<!-- TODO compile everything into OSF repo & link -->
-<!-- TODO link individual pre-reg's in repo -->
-<!-- TODO link overall pre-reg -->
-<!-- TODO include in repo & link the reasons for replication failure that were offered to students -->
-<!-- TODO redo/double check closeness scores for first rep and rescues  -->
-<!-- TODO author contributions, acknowledgements -->
-
-# Introduction
-
-Imagine you are a graduate student, and you run a replication of a study that you are interested in building upon in your research.
-The replication fails. Perhaps the interaction you hoped for is directionally correct, but the point estimate is small and the confidence interval definitely overlaps 0, with a $p$-value of .3.
-Or perhaps the interaction is numerically in the wrong direction and the main effects look different.
-<!--Or maybe the main effect of interest may be null, but you found a significant effect interaction that wasn't hypothesized.-->
-Whatever the details of the replication failure, you are left with a question: Should you try again and run a re-replication, or should you give up and pick a different study to build upon?
-
-In psychology, large scale replication projects have found that around half of studies successfully replicate. 
-Across 100 studies with positive results, the reproducibility project in psychology (RP:P) replicated 36%-47% depending on the metric for replication success [@openscienceconsortium].
-With large multi-site samples, Many Labs 1 replicated 11/13 effects (84.6%), Many Labs 2 replicated 14/28 effects (50%), and Many Labs 3 replicated 3/10 effects (30%) [@klein2014; @klein2018; @ebersole2016].
-@camerer2018 examined 21 behavioral social science studies and successfully replicated 12-14 of them (57%-67%) depending on the metric used.
-@boyce2023 reported an average subjective replication score of 49% for 176 replications primary in psychology.
-
-Psychology is not the only discipline where many studies do not replicate.
-Large scale replication projects in other disciplines have found 39/97 of studies with positive effects (40%) replicating in cancer biology [@errington2021], 11/18 studies (61%) replicating in economics [@camerer2016], and 31/40 studies (78%) replicating in experimental philosophy [@cova2021].
-Across these disciplines, and especially in psychology, large-scale replications indicate a substantial chance of scientists encountering failed replications if they try to replicate published findings.
-
-Replications can fail for many reasons, having to do with the original study or the replication. 
-<!-- In principle, any difference between the original study and replication could be a root cause of the difference in their outcomes.
-But in practice, the relationship between original and replication is not symmetric, and many causes of replication failure can be attributed either more to the original study or more to the replication.
--->
-Starting with the original study, one potential reason for replication failure is that the original result is fragile in some way.
-It could be a statistically unlikely result that was achieved through chance or $p$-hacking, or it could be sensitive to the exact conditions and time it was run under ("hidden moderators").
-Another possibility is that the original reported effect size might be inflated due to some combination of heterogeneity, $p$-hacking, low power, and publication bias.
-A consequence of inflated effect sizes is that replication studies might select a sample size with appropriate statistical power for the reported effect size and then have too small a sample to reliably detect the (true) smaller effect.
-Replication studies might also end up underpowered due to unexpected attrition or noise in the replication sample.
-
-Some other reasons for replication failure are  primarily due to the replication study. 
-A replication could observe different results from the original due to methodological differences. 
-These differences in design could be intentional adaptations, unavoidable changes from lack of access to the original instructions or materials, or changes that were not expected to be critical. 
-A difference in the details of recruitment (e.g., online versus in-person) might mean that particular details of a study implementation would no longer be appropriate, or the data quality controls and attention checks might be inadequate.
-If there are differences in time, place, or subject population between the two studies, corresponding changes to the materials, instructions, or procedure could be needed to provide an adaptation of the experimental paradigm to the new context.
-Such adaptation creates yet more challenges in interpretation: too many changes could cause differing results, but so could not enough changes. 
-In sum, when replications fail, we generally do not know why they failed, although we may speculate.
-
-For the goals of large-scale replication projects, it does not matter why any particular study failed to replicate, because the aim is to estimate the proportion of replication effects in a literature.
-In contrast, however, when individual scientists attempt to replicate an effect with the goal of building on it, they do care about why an individual replication failed.
-In an uncertain literature, scientists might not want to commit resources to studying extensions of an effect without first checking that they can measure that effect themselves.
-For those individual scientists, it is much more important whether the replication failure is due to a fixable issue with  the replication or an intrinsic feature of the original result.
-
-Re-replication can serve as a way to test explanations for replication failure.
-While it is possible to speculate after the fact about potential causes of a single replication failure, in most circumstances these causes are hard to discern (absent clear evidence of errors).
-In contrast, a second replication provides a chance to test explanations by making modifications -- as well as giving another chance for researchers to measure an effect of interest.
-But what are the chances that a re-replication succeeds?
-
-<!-- is hard to diagnose for certain what made for the difference in the results.
-An exception might be if a specific error in one study or the other is found, such that the results were not what was thought (analytic error) or the data was not what was thought (experimental error).
-Aside from these rare cases, we usually can't know whether the replication failure is fixable just by looking at the replication failure itself.
--->
-
-<!-- Re-replication has not been studied much, so it is uncertain how often re-replications recover the results of an original study.
-That is, it is not well known how definitive a first replication failure is.
--->
-Relatively few studies have estimated re-replication success. 
-One estimate comes from @ebersole2020.
-After the original RP:P study reported of a replication rate around 40% [@openscienceconsortium], @gilbert2016 raised concerns that methodological differences might explain the low replication rate.
-In 11 of the RP:P studies, the original authors had raised concerns about protocol fidelity prior to data collection.
-Of these 11 with concerns, 10 failed to obtain significant results in the RP:P replication. 
-Thus, @ebersole2020 re-replicated 10 of these 11 in larger samples, using both the RP:P protocol and a new protocol revised under advice of the original authors or other experts.
-This study thus tested whether larger sample sizes and/or "better" methodologies would "rescue" the failed RP:P replications.
-The result was that 2 of the 10 revised protocols found a significant result (but not the 1/11 that originally was successful).
-Even when a significant effect was recovered, the effect size was much diminished [@ebersole2020].
-<!-- We could frame @ebersole2020 as an attempt to recover the original effects of the 9 studies with significant original effects and non-significant RP:P effects by a combination of high power and design tweaks.
--->
-The re-replication success rate was thus 2/9 (22%) for studies with non-significant first replications, under favorable, high-resource circumstances.
-
-<!-- While it is tempting to speculate on the reasons for failed replications, the @gilbert2016 and @ebersole2020 example shows these speculations on causes of replication failure do not always pan out in re-replication outcomes.
--->
-
-While @ebersole2020 looked at re-replication success rate in a high resource setting with access to large, multi-site samples and expert input, most early career scientists do not have those kinds of resources to devote to re-replication attempts.
-On the other hand, early career researchers may also be prone to a different distribution of causes of initial replication failure.
-Thus, it is an open question what the re-replication rate is for failed replications by early career researchers.
-Further, estimating this rate could inform researchers' decisions on what to do next after failed replications.
-
-Here, we investigate re-replication in the context of graduate student replication class projects.
-Students in a graduate-level class on experimental methods in psychology were given the option to "rescue" an experiment that a student in a prior year had previously failed to replicate as their class project [first replications reported in @boyce2023].
-The focus of the class was best practices in experimental design; thus, students looked at both the original paper and the failed replication to examine potential issues in the replication that they could fix in their rescue project.
-In the present paper, we report the results of `r num_proj` re-replication rescue projects. We find that a minority of projects (5/17, 29%) successfully recovered the original effect.
-
-# Methods
-
-PSYCH 251 is a graduate-level experimental methods class taught by MCF.
-In previous years, students have conducted replication projects [@boyce2023; @hawkins2018].
-In Fall 2023, students were offered the option to complete a "rescue" project where they re-replicated one of the unsuccessful replications from a previous year.
-Students could also opt to do a normal replication instead.
-If they opted for a rescue, they were given the option to participate in a collaborative meta-science project and earn authorship on the current paper based on 1) completing a rescue project, 2) reviewing another student's rescue project for reproducibility, and 3) reviewing and approving the final manuscript.
-We report on the result of `r num_proj` rescue projects that opted to be part of the paper and completed data collection.
-
-A spreadsheet of projects, individual project write-ups (both first replications and rescues), individual project data and analyses for rescue projects, and the analytic code for this paper are all available at https://osf.io/cyk5w/.
-
-Our analysis plan was pre-registered after students had selected projects, but before final data collection on the projects.
-Each project was also individually pre-registered by the student conducting it.
-The overall analysis is pre-registered at https://osf.io/5qz7v, individual pre-registrations are linked from https://osf.io/vkbfw.
-We note one deviation from our pre-registration here: we pre-registered visual comparisons between original, first replication, and rescue projects using prediction intervals.
-Prediction intervals depend on both the original effect size and variance and the variance of the comparison (replication or rescue) study [@patil2016].
-Thus we cannot show a single prediction interval for the original study, but would have to show a prediction interval between each pair of studies.
-We thought this analysis would not offer additional clarity and hence we did not perform it.
-
-## Sample
-
-The experiments that were re-replicated were chosen from studies that failed to replicate in @boyce2023.
-We created an initial list of `r nrow(filtered)` rescue-eligible studies that 1) had received a subjective replication success score of 0, .25, or .5 (on a 0--1 scale) in @boyce2023, 2) had a Github repository available (Github repositories were used in class starting in academic year 2015-2016), and 3) where the original experiment had 200 or fewer participants (to ensure we could afford to match or increase the sample size based on the class budget).
-We then contacted the replication project authors for permission to share their report and repository with a new student and include it as a supplement on a resulting paper.
-This left `r length(approved)` options for the students to choose from.
-`r length(chosen)` students chose to do rescue projects, and
-`r length(chosen)-num_proj` students did not finish their project or did not indicate interest in being part of this paper, leaving a final sample of `r num_proj` rescue projects.
-
-```{r}
-rel_size <- parsed_d |> filter(type %in% c("original", "rescue")) |> select(target_lastauthor_year, type, N)  |> 
-  pivot_wider(names_from=type, values_from=N) |> mutate(multiplier=rescue/original)
-
-lowest <- quantile(rel_size$multiplier, 0)
-low <- quantile(rel_size$multiplier, .25)
-mid <- quantile(rel_size$multiplier, .5)
-m <- mean(rel_size$multiplier)
-high <- quantile(rel_size$multiplier, .75)
-highest <- quantile(rel_size$multiplier, 1)
-
-```
-
-```{r}
-subj <- parsed_d |> filter(type=="rescue") |> mutate(binary_success=ifelse(replication_score>.5,1,0))
-
-tallied <- subj|> group_by(replication_score) |> tally()
-
-success <- filter(subj, binary_success==1)
-
-d <- read_csv(here("data", "combined_data.csv")) |> filter(type=="rescue")
-
-irr <- cor.test(d$TA_rep_score, d$MCF_rep_score, method="spearman")$estimate
-
-bootstrap <- subj$binary_success |> Hmisc::smean.cl.boot()
-```
-
-```{r}
-boyce2023_sample <- read_csv(here("data/boyce_2023_data.csv")) |> select(sub_rep)
-
-percent_rep <- boyce2023_sample |> mutate(is_rep=ifelse(sub_rep>.5,1,0)) |> summarize(m=mean(is_rep))
-
-overall <- (percent_rep[1])+(1-percent_rep[1])*nrow(success)/nrow(subj)
-```
-## Procedure
-
-Students conducted their rescue projects over the course of the 10-week class.
-Once they had chosen a project we gave them access to the original replicators' write-up and repository, which often included the data, experiment code, and analytic code.
-In many cases, students were also given the contact information of the original replicator (a few original replicators opted not to be contacted by students).
-
-Students were required to think of reasons the first replication might not have worked, and address them if they could.
-A list of possible reasons and solutions was given to students (https://osf.io/dfwk2).
-In general, we encouraged students to add manipulation checks as appropriate, and to adapt their materials to online studies, which may benefit from attention checks and/or shorter duration.
-For instance, the rescue of @paxton2012 switched from using the cognitive reflection task (CRT) which many online participants are over-familiar with to using the newer CRT-2 which is less overused but attempts to measure the same construct [@thomson2016].
-The rescue of @jara-ettinger2022 discovered that the replication had accidentally used an illustrated version of the stimuli rather than the photographic stimuli used in the original and used the photographic stimuli instead.
-@tarampi2016 had participants do a timed navigation task where they wrote L or R to indicate which way to turn at each intersection on a paper map.
-The replication ported this experiment online and had participants click a drop down menu to select left or right for each turn.
-The rescue removed the unwieldy drop down menus and opted to have participants press keys on the keyboard to indicate the direction of a turn, which seemed like a more natural interface.
-Once experimental designs and analytic plans were approved by class TAs (VB and BP), students pre-registered and ran their samples.
-
-With one exception, samples were collected on Prolific [the rescue of @yeshurun2003 ran in-person on the Stanford student subject pool].
-We tried to power studies adequately [with a target of 2.5x original following @simonsohn2015], but due to cost constraints, not all studies were powered at this level.
-The rescues had on average `r round(m,2)` times the original sample post-exclusion (median: `r round(mid,2)`, IQR: `r round(low,2)` - `r round(high,2)`, minimum: `r round(lowest, 2)`, maximum: `r round(highest,2)`, see Table \@ref(tab:tab-size) for all sample sizes).
-Across the `r num_proj-1` Prolific studies, we spent \$`r pluck(cost,1,1) |> round()`, for an average of \$`r (pluck(cost,1,1)/(num_proj-1)) |> round()` per project.
-
-## Coding of results
-
-We followed @boyce2023 in the properties of the studies we measured and how we quantified replication success. 
-Each project was rated on the basis of subjective replication success (on a 0--1 scale) by both MCF and one of VB and BP.
-We thought about replication in terms of general match in key study results (direction, magnitude, and significance), rather than focusing on any singular numeric result or significance cut-off.
-Interrater reliability was `r irr |> round(3)`; disagreements were minor (at no point greater than .25) and were resolved through discussion.
-
-As a complement to the subjective rating of overall success, we statistically compared one key measure of interest for each study, following @boyce2023.
-In order to statistically compare the key measures, we needed effect sizes reported in the same way for each original study, first replication, and rescue.
-When effects were not reported in consistent ways across original and replications, we recalculated effects from raw data when necessary to obtain comparable values.
-
-We measured statistical consistency using $p$-original, the $p$-value on the null hypothesis that one study's population effect comes from the same distribution of population effects as another study or studies [@mathurNewStatisticalMetrics2020a] If we assume no heterogeneity between studies, then this is the same as asking how consistent one study's estimate of the population-level effect is with another study's estimate of the population-level effect.
-However, meta-analyses of closely related studies, such as those from different sites of multi-site replications, indicate that there is often heterogeneity between studies.
-$p$-original allows for such heterogeneity, as governed by a parameter $\tau$.
-We cannot accurately estimate the level of heterogeneity for an effect meta-analytically as we have only a small number of replications per study.
-Instead, we imputed a heterogeneity value of $\tau=.21$ SMD, which is the average level of heterogeneity found by @olsson-collentine2020 in prior multi-site replications in psychology.
-
-We recorded the same set of potential correlates that were used in @boyce2023 for original, first replication, and rescue (these were already rated for original and first replication).
-These potential correlates included the subfield of the study (cognitive, social, or other psychology), its publication year, experimental design features including whether it was a within- or between-subject design, whether each condition was instantiated with one vignette or multiple, how many items each participant saw, and whether there were open materials and open data.
-
-For the original study and each replication, we recorded the number of participants post-exclusions.
-For studies where some extra conditions were dropped in some replications, we counted only the participants in the key conditions all replications had for comparability.
-For instance, if an original study compared between two critical conditions but also had a baseline control, we did not count the participants in the baseline condition if a replication did not include this condition.
-We also recorded whether each study was conducted online using a crowd-sourced platform or not.
-
-# Results
-
-## Overall replication rate
-
-<!-- When a replication fails to obtain the same results, one may have intuitions about what may have gone wrong -- these rescue projects test how often addressing these potential issues in fact works.
--->
-
-Our primary question of interest was how many of the `r num_proj` rescue projects succeeded at replicating the results in the original study.
-Across the `r nrow(subj)` rescue projects, `r nrow(success)` mostly or fully replicated the original results according to the subjective replication ratings.
-`r pluck(tallied,2,1)` got a rating of 0, `r pluck(tallied, 2,2)` got a rating of .75, and `r pluck(tallied, 2,3)` got a rating of 1.
-Thus, a first pass answer to the question "how often can a failed replication be salvaged?" is `r round(nrow(success)/nrow(subj)*100)`% (bootstrapped 95% CI: `r round(bootstrap[2]*100)`% - `r round(bootstrap[3]*100)`%) of the time.
-
-In the original replication sample from @boyce2023, `r boyce2023_sample |> filter(sub_rep>.5) |> nrow()` out of `r boyce2023_sample |> nrow()` replications (`r round(percent_rep*100)`%) mostly or fully replicated (i.e.
-received a subjective replication score of .75 or 1).
-Note that @boyce2023 report the average replication score as a percent success (49%), but given that we considered studies with a subjective score of .5 as eligible to be rescued, we recomputed the success rate where scores of 0, .25, and .5 are considered failures and .75 and 1 successes.
-If the re-replication rate in our sample is representative of the re-replication rate for the initially non-replicating studies, then the combined chance of mostly or fully replicating in a first replication or one follow-up replication is `r round(overall*100)`%.
-
-## Effect size comparison
-
-```{r smd, fig.cap="Standardized effect sizes of original studies, first replications, rescues, and additional replications if available.
-Due to the large effect size of a couple studies, large effect studies are shown in a separate panel.
-In a few cases, the first replication's key effect was non-zero in the same direction as the original; however, in these cases the larger pattern of results was not fully consistent between original and first replication.
-"}
-
-#test on just one
-colors <- c("Original study"="black", "First replication"="#377EB8", "Rescue"="#E41A1C", "Additional replication"="#984EA3")
-shape <- c("Original study"=21,"First replication"=22,"Rescue"=23,"Additional replication"=24)
-
-big <- parsed_d |> filter(type=="original") |> filter(calc_d_calc>1|target_lastauthor_year=="yeshurun2003") |> select(target_lastauthor_year)
-for_plotting_d <- parsed_d |> filter(!is.na(calc_d_calc)) |> 
-  mutate(point=calc_d_calc, low=calc_d_calc-1.96*calc_d_calc_se, high=calc_d_calc+1.96*calc_d_calc_se) |> 
-  mutate(type=case_when(
-    type=="original" ~ "Original study",
-    type=="rep1" ~ "First replication",
-    type=="rescue" ~ "Rescue",
-    type=="additional" ~ "Additional replication"
-  ),
-  type=factor(type, levels=c("Original study", "First replication", "Rescue", "Additional replication")))
-
-smd_scale_small <- ggplot(for_plotting_d |> anti_join(big),aes(x=reorder(name_pretty, point, FUN=max),y=point,ymin=low,ymax=high,shape=type, color=type, fill=type, group=desc(type)))+
-  geom_errorbar(size=.5,width=0, position=position_dodge(width=.5))+
-  geom_point(position=position_dodge(width=.5))+
- coord_flip()+
-  scale_size_area()+
-  geom_hline(yintercept=0,color="black")+
-    scale_color_manual(values=colors, aesthetics=c("color", "fill"))+
-  scale_shape_manual(values=shape)+
-  theme(legend.position = "bottom", 
-        panel.grid.major.x = element_blank(), 
-        panel.grid.minor.x=element_blank(),
-        legend.title=element_blank(),
-        legend.text=element_text(size=10)
-        )+
-  labs(y="Standarized mean difference", x="")
-
-level_order = c("Yeshurun & Levy 2003",
-                "Ngo et al. 2019", 
-                 "Krauss & Wang 2003",
-                 "Jara-Ettinger et al. 2022")
-smd_scale_big <- ggplot(for_plotting_d |> inner_join(big) |> 
-                          mutate(name_pretty=factor(name_pretty, levels=level_order)), aes(x=name_pretty,y=point,ymin=low,ymax=high,shape=type, color=type, fill=type, group=desc(type)))+
-  geom_errorbar(size=.5,width=0, position=position_dodge(width=.5))+
-  geom_point(position=position_dodge(width=.5))+
- coord_flip()+
-  scale_size_area()+
-  geom_hline(yintercept=0,color="black")+
-    scale_color_manual(values=colors, aesthetics=c("color", "fill"))+
-    scale_shape_manual(values=shape)+
-  theme(legend.position = "none", 
-        panel.grid.major.x = element_blank(), 
-        panel.grid.minor.x=element_blank()
-        )+
-  labs(y="Standarized mean difference", x="", )
-
-#smd_scale_big
-#smd_scale_small
-
-plot_grid(smd_scale_big, smd_scale_small, rel_heights=c(.4,1), nrow=2)
-```
-
-As a complement to subjective replication ratings, we also statistically compared the effect sizes of the rescue, first replication, and original study on one preregistered key measure per study [again following @boyce2023].
-Though we did not conduct a systematic review of the literature to identify all possible replications, we also consider the effect sizes obtained in additional replications when we were aware of them (either from other class projects, or external replications in the literature).
-
-We standardized all effect sizes into standardized mean difference (SMD) units.
-One potential issue with comparisons using SMD is that noisier measures will have smaller standardized effect sizes even if the effect on the original scale is the same.
-In general, the replication and rescue effect sizes were smaller than the original effect sizes, and in a few cases the effects were in the opposite direction (Figure \@ref(fig:smd)).
-
-```{r}
-
-do_d_rma <- function(df) {
-  if(!any(is.na(df$d))){
-  r<- rma(yi=df$d, sei=df$d_se, slab=df$type)
-  return(tibble(rma_d_est=r$beta[,1], rma_d_se=r$se))
-  }
-  return(tibble(rma_d_est=NA, rma_d_se=NA))
-
-}
-
-do_p_orig <- function(es, es_se, rep_es, rep_se){
-  if(!is.na(es)&!is.na(es_se)&!is.na(rep_es)&!is.na(rep_se)){
-    return(Replicate::p_orig(es, es_se**2,rep_es, t2=0.21**2, rep_se**2))
-  }
-  return(NA)
-}
-
-orig <- parsed_d |> filter(type=="original") |> select(target_lastauthor_year, d=calc_d_calc, d_se=calc_d_calc_se)
-
-orig_v_others <- parsed_d |> select(target_lastauthor_year, type, d=calc_d_calc, d_se=calc_d_calc_se) |> 
-  filter(type!="original") |> 
-  group_by(target_lastauthor_year) |> 
-  nest() |> 
-  mutate(d_rma_result=map(data, do_d_rma)) |> 
-  unnest_wider(d_rma_result) |> 
-  left_join(orig) |> 
-  rowwise() |> 
-  mutate(d_p_orig=do_p_orig(d, d_se, rma_d_est, rma_d_se))
-
-orig_v_rescue <- parsed_d |>   filter(type=="rescue") |> 
-  select(target_lastauthor_year, type, res_d=calc_d_calc, res_d_se=calc_d_calc_se) |> 
-  left_join(orig) |> 
-  rowwise() |> 
-  mutate(d_p_orig=do_p_orig(d, d_se, res_d, res_d_se))
-
-orig_v_not_rescue <- parsed_d |> select(target_lastauthor_year, type, d=calc_d_calc, d_se=calc_d_calc_se) |> 
-  filter(type!="original", type!="rescue") |> 
-  group_by(target_lastauthor_year) |> 
-  nest() |> 
-  mutate(d_rma_result=map(data, do_d_rma)) |> 
-  unnest_wider(d_rma_result) |> 
-  left_join(orig) |> 
-  rowwise() |> 
-  mutate(d_p_orig=do_p_orig(d, d_se, rma_d_est, rma_d_se))
-
-rescue_only <- parsed_d |> filter(type=="rescue") |> select(target_lastauthor_year, d=calc_d_calc, d_se=calc_d_calc_se)
-
-rescue_v_reps <- parsed_d |> select(target_lastauthor_year, type, d=calc_d_calc, d_se=calc_d_calc_se) |> 
-  filter(type!="original", type!="rescue") |> 
-  group_by(target_lastauthor_year) |> 
-  nest() |> 
-  mutate(d_rma_result=map(data, do_d_rma)) |> 
-  unnest_wider(d_rma_result) |> 
-  left_join(rescue_only) |> 
-  rowwise() |> 
-  mutate(d_p_orig=do_p_orig(d, d_se, rma_d_est, rma_d_se))
-
- all <- orig_v_others |> select(target_lastauthor_year, orig_v_other=d_p_orig) |> 
-  left_join(orig_v_rescue |> select(target_lastauthor_year, orig_v_rescue=d_p_orig)) |> 
-  left_join(orig_v_not_rescue |> select(target_lastauthor_year, orig_v_not_rescue=d_p_orig)) |> 
-  left_join(rescue_v_reps |> select(target_lastauthor_year, rescue_v_reps=d_p_orig))
-
-main_summ <- all |> ungroup() |> select(orig_v_other) |>
-  summarize(median=median(orig_v_other, na.rm=T),
-            low=quantile(orig_v_other, .25, na.rm=T),
-            high=quantile(orig_v_other, .75, na.rm=T),
-            less_than=sum(orig_v_other<.05, na.rm=T)/sum(!is.na(orig_v_other)))
-
-rescue_summ <- all |> ungroup() |> select(orig_v_rescue) |>
-  summarize(median=median(orig_v_rescue, na.rm=T),
-            low=quantile(orig_v_rescue, .25, na.rm=T),
-            high=quantile(orig_v_rescue, .75, na.rm=T),
-            less_than=sum(orig_v_rescue<.05, na.rm=T)/sum(!is.na(orig_v_rescue)))
-
-rep_summ <- all |> ungroup() |> select(orig_v_not_rescue) |>
-  summarize(median=median(orig_v_not_rescue, na.rm=T),
-            low=quantile(orig_v_not_rescue, .25, na.rm=T),
-            high=quantile(orig_v_not_rescue, .75, na.rm=T),
-            less_than=sum(orig_v_not_rescue<.05, na.rm=T)/sum(!is.na(orig_v_not_rescue)))
-
-rescue_rep_summ <- all |> ungroup() |> select(rescue_v_reps) |>
-  summarize(median=median(rescue_v_reps, na.rm=T),
-            low=quantile(rescue_v_reps, .25, na.rm=T),
-            high=quantile(rescue_v_reps, .75, na.rm=T),
-            less_than=sum(rescue_v_reps<.05, na.rm=T)/sum(!is.na(rescue_v_reps)))
-```
-
-```{r tab-porig}
-names <- parsed_d |> select(target_lastauthor_year, name_pretty) |> unique()
-
-all |> ungroup() |>  left_join(names) |> select(Paper=name_pretty, `All reps`=orig_v_other, "Rescue" = orig_v_rescue, "Non-rescue"=orig_v_not_rescue, "Other reps"=rescue_v_reps) |> knitr::kable(format="latex", booktabs=T, linesep="", caption="$P$-original values between different sets of experiments.
-The primary analysis is between the original result and the meta-analytic aggregation of all replications.
-All $p$-original values assume an imputed heterogeneity value of $\\tau$=.21.", digits=3) |>
-  add_header_above(c(" "=1, "Original and"=3, "Rescue and"=1)) |> add_header_above(c(" "=1, "p-original comparing between"=4))
-
-```
-
-Scientists' intuitions about whether a replication is successful and whether an effect provides support for a hypothesis (including heuristic cutoffs like p\<.05) do not always align with measures of statistical consistency [@patil2016].
-For instance, two studies may both find that condition 1 results in a significantly higher outcome measure than condition 2, but the effect magnitudes may be sufficiently different that they are statistically unlikely to have come from the same population.
-On the other hand, one study may find a statistically significant, but imprecisely estimated effect in a small sample, and a second study may find a near-zero (null) effect, but the effect estimates from the two studies may be statistically compatible, despite one supporting a hypothesized difference and the other not.
-
-As our primary comparison, we compare the effect size of the original study to the meta-analytic effect of the totality of the replications (first replication, rescue, and additional if found).
-The value of $p$-original represents how likely an effect size equal to or more extreme than the original effect size is to occur if it comes from a distribution of population effect sizes defined by the mean and standard error of the replications (combined meta-analytically) with a between-population standard deviation of $\tau=.21$ [imputed from @olsson-collentine2020].
-That is, $p$-original is a measure of the statistical consistency of the original result with the totality of the replications, assuming a given level of heterogeneity of effects between studies.
-Smaller $p$-original values indicate more inconsistency.
-
-The median value of $p$-original between an original study and its replications was `r main_summ$median |> round(2)` [IQR: `r main_summ$low |> round(2)` - `r main_summ$high |> round(2)`].
-`r round(main_summ$less_than*100)`% of the $p$-original values were less than .05, indicating by conventional thresholds a rejection of the null hypothesis that the original comes from the same distribution of population effects as the replications.
-Individual $p$-original values for each study are shown in Table \@ref(tab:tab-porig).
-
-As secondary measures, we calculated the $p$-original values between a) the original and the rescue, b) the original and non-rescue replications, and c) the rescue and other replications.
-For a) the original versus the rescue, the median value of $p$-original was `r rescue_summ$median |> round(2)` [IQR: `r rescue_summ$low |> round(2)` - `r rescue_summ$high|> round(2)`], and `r round(rescue_summ$less_than*100)`% of the $p$-original values were less than .05.
-For b) the original versus all the non-rescue replications, the median value of $p$-original was `r rep_summ$median |> round(2)` [IQR: `r rep_summ$low |> round(2)` - `r rep_summ$high |> round(2)`], and `r round(rep_summ$less_than*100)`% of the $p$-original values were less than .05.
-For c) the rescue versus the other replications, the median value of $p$-original was `r rescue_rep_summ$median |> round(2)` [IQR: `r rescue_rep_summ$low |> round(2)` - `r rescue_rep_summ$high |> round(2)`], and `r round(rescue_rep_summ$less_than*100)`% of the $p$-original values were less than .05.
-
-<!--Visualizations of the statistical consistency between the original and each replication are shown in TODO FIGURE.
-The range around the open circle is the 95% predictive interval, representing the interval where, assuming that both are drawn from the same distribution, the replication will fall 95% of the time, given the precision (standard deviation) of the replication [@patil2016].
-We again impute a heterogeneity value of $\tau=.21$ SMD for the construction of the prediction intervals.-->
-
-<!--* We will use p-original to evaluate how consistent the original effect size is with the totality of replications.
-We expect there to be a small number of replications, so we will impute the heterogeneity value as in https://osf.io/preprints/psyarxiv/dpyn6/.
--->
-
-Overall, allowing for a heterogeneity level of $\tau$=.21 SMD, a number of original effects are not statistically consistent with rescue and replication effects.
-The pattern of inconsistency does not align with which studies were rated as having replicated.
-In all cases, the point estimate of the re-replication is smaller than, or in the opposite direction of, the original effect on the key measure of interest.
-
-```{r}
-do_d_predInt_het <- function(df){
-  if(!is.na(df$d)&!is.na(df$d_se)&!is.na(df$rep_d)&!is.na(df$rep_d_se)){
-    yio=df$d
-    vio=df$d_se**2
-    yir=df$rep_d
-    vir=df$rep_d_se**2
-    t2=.21**2
-    pooled.SE = sqrt(vio + vir + t2)
-    PILo.sens = yio - qnorm(0.975) * pooled.SE
-    PIHi.sens = yio + qnorm(0.975) * pooled.SE
-    PIinside.sens = (yir > PILo.sens) & (yir < PIHi.sens)
-    return(tibble(d_low=PILo.sens, d_high=PIHi.sens, d_inside=PIinside.sens))
-  }
-  return(tibble(d_low=NA,d_high=NA, d_inside=NA))
-}
-
-```
-
-```{r}
-orig <- parsed_d |> filter(type=="original") |> select(target_lastauthor_year, d=calc_d_calc, d_se=calc_d_calc_se, es=calc_ES, es_se=calc_SE)
-
-predInts_het <- parsed_d |> 
-  filter(type!="original") |> 
-  group_by(target_lastauthor_year, name_pretty) |> 
-  select(target_lastauthor_year, type, rep_d=calc_d_calc, rep_d_se=calc_d_calc_se, rep_es=calc_ES, rep_es_se=calc_SE) |> 
-  left_join(orig) |> 
-  group_by(target_lastauthor_year,type) |> 
-  nest() |> 
-  mutate(d_pred_int=map(data,do_d_predInt_het)) |> 
-  unnest_wider(d_pred_int) |> 
-  unnest_wider(data)
-
-```
-
-## Correlates of rescue success
-
-```{r cor-table}
-
-original <- parsed_d |> filter(type=="original") |> 
-  rename_with(~str_c("original_",.), .cols=-target_lastauthor_year)
-
-rep1 <- parsed_d |> filter(type=="rep1") |> select(target_lastauthor_year, rep_N=N)
-
-for_cor <- subj |> left_join(original) |> left_join(rep1) |> 
-  mutate(
-  social=ifelse(subfield=="social", 1,0),
-  other_psych=ifelse(subfield=="other-psych",1,0), 
-  is_within=ifelse(within_between=="within", 1,0), 
-  change_platform=ifelse(on_turk==original_on_turk, 0,1),
-  log_trials=log(repeated_measure),
-  log_sample=log(N),
-  log_ratio_ss=log(N/original_N),
-  rep_1_log_sample=log(rep_N),
-  log_ratio_rep1_orig=log(rep_N/original_N),
-  log_ratio_rescue_rep1=log(N/rep_N),
-  open_data=ifelse(open_data=="yes",1,0),
-  open_mat=ifelse(open_materials=="yes", 1,0),
-  stanford=ifelse(stanford_internal=="yes",1,0)) |> 
-  filter(!is.na(replication_score))
-
-sub_cor <- function(var, stat = "estimate") {
-  if (stat == "estimate") {
-    cor.test(for_cor$replication_score, pull(for_cor, {{var}}))$estimate
-  } else {
-    cor.test(for_cor$replication_score, pull(for_cor, {{var}}))$p.value
-  }
-}
-
-preds <- c("open_data",  "open_mat", "stanford", "change_platform", 
-           "log_ratio_ss", "is_within", "single_vignette", "log_sample", 
-           "log_trials", "social", "other_psych", "rep_1_log_sample", "log_ratio_rep1_orig", "log_ratio_rescue_rep1")
-
-cors <- tibble(preds = preds) |>
-  mutate(r = sapply(preds, function(x) sub_cor(x, stat = "estimate")),
-         p = sapply(preds, function(x) sub_cor(x, stat = "p"))) |>
-
-  mutate(Predictors=factor(preds, levels=c("social", "other_psych", "is_within", "single_vignette", "change_platform", "open_data", "open_mat", "stanford", "pub_year", "log_trials", "log_sample", "log_ratio_ss", "rep_1_log_sample", "log_ratio_rep1_orig", "log_ratio_rescue_rep1"), labels=c("Social", "Other psych", "Within subjects", "Single vignette", "Switch to online", "Open data", "Open materials", "Stanford", "Publication year", "Log trials", "Log original sample size", "Log rescue/original sample size", "Log replication sample size", "Log replication/original sample size", "Log rescue/replication sample size"))) |> arrange(Predictors) |> select(Predictors, r, p)
-
-library(kableExtra)
-knitr::kable(cors, digits = 3, align='rcc', format="latex", booktabs=T, linesep="", caption="Correlations between an individual predictor and the subjective replication score of the rescue project.
-The first set of predictors were pre-registered based on the correlates used in Boyce et al.
-(2023).
-The last three predictors were added post-hoc.") |> row_spec(11, hline_after=T)
-
-```
-
-Are there signals in the features of original or replication studies that predict whether a re-replication will succeed?
-To address this question, we report correlations between the set of predictor variables used in @boyce2023 and the subjective replication scores of the rescues.
-We also added some (non-preregistered) predictors related to the sample size of the first replication, after seeing the successful re-replications of @ngo2019 and @krauss2003, both of which had small replication samples and larger rescue samples.
-
-All of the correlations are presented in Table \@ref(tab:cor-table).
-The number of rescues is small, and many of these predictors are correlated, so we caution against over interpretation.
-
-The strongest correlates of rescue success were open materials, a small sample size on the first replication, a small sample size on the first replication relative to the original sample size, and a large rescue sample size relative to the first replication.
-None of the pre-registered correlates meet the conventional significance threshold; the two correlates based on ratios that reflect a relatively smaller replication sample size are marginally significant.
-
-Small replication samples relative to original and rescue could be due to both a) powering a replication according to a reported large effect size or b) difficulties with recruitment or high exclusion rates leading to a smaller than intended sample.
-Since relative sizes of the studies may play a role in replication success and how probative replications are, we show the sample sizes in Table \@ref(tab:tab-size).
-
-An additional factor that influences the interpretation of a replication is how close the replication's methods were to the original.
-In the rescue projects, we aimed to have methods be as close as was feasible or appropriate.
-However, rescue projects varied in how close the re-replications actually were, often due to limitations in the availability of original stimuli and original instructions, in addition to the use of primarily online subject pools.
-Table \@ref(tab:tab-size) shows the closeness of each first replication and rescue according to the classification scheme from @lebel2018.
-<!-- TODO CLOSENESS NUMBERS SHOULD BE DOUBLE CHECKED AND FIRST REPS REVISED AS NEEDED -->
-
-```{r tab-size}
-parsed_d |> select(name_pretty, type, N, closeness, replication_score) |> 
-  filter(type!="additional") |> 
-  pivot_wider(names_from="type", values_from=c(N, closeness, replication_score)) |> 
-  select(paper=name_pretty, replication_score_rescue, N_original, N_rep1, N_rescue,
-         "Replication \\\\  closeness"=closeness_rep1, closeness_rescue) |> arrange(replication_score_rescue|> desc()) |> knitr::kable(align="lllll", format="latex", booktabs=T, linesep="", caption="Comparison of sample size for original, replication, and rescue samples and measures of closeness for replication and rescue samples.", col.names=c("", "", "Original", "Replication", "Rescue", "Replication", "Rescue")) |> add_header_above(c("Paper"=1, "Score"=1, "N"=3, "closeness"=2))
-
-```
-
-Overall, we do not have a clear picture of why certain studies replicated in the rescue sample and others did not, other than a few cases where fixing sample size issues may have helped.
-
-## Case studies
-
-Given the mix of successful and unsuccessful rescue projects, we discuss a few projects where we have speculations about why they turned out the way they did.
-
-The rescue of @krauss2003 was successful despite an unsuccessful replication.
-This study looked at the influence of guided thinking on whether or not people gave correct justifications (drawn or written) for their answer on the Monty Hall problem.
-The original paper reported correct justification from 2/67 (`r round(2/67*100)`%) in the control condition and 13/34 (`r round(13/34*100)`%) in the guided thinking condition.
-The first replication struggled to recruit participants who were naive to the problem (an exclusion criterion), and many participants gave very short text responses in the provided text box (only textual responses were allowed).
-The replication found 0/8 correct justifications in the control and 0/11 in the guided thinking condition.
-While we cannot know for sure what caused the non-replication, there were clear problems observable from the small final sample and low-quality responses.
-The rescue targeted these issues by adding a pre-screening that ensured participants were not familiar with the Monty Hall problem, reskinned the problem and changed its name (to reduce googling for answers), and had participants upload drawings for their justifications.
-Collectively, we believe these changes brought the rescue closer to the intent of the original.
-The rescue had 1/40 (`r round(1/40*100)`%) correct justifications in the control condition and 6/35 (`r round(6/35*100)`%) in the guided thinking condition.
-This effect was significant, though smaller than the effect in the original.
-
-@ngo2019 was a second successful rescue.
-The original study found a large effect; hence the first replication, powering for 80% power on the reported effect, recruited a small sample of 12 people.
-This small study failed to find the original effect.
-The rescue, powered using 2.5x the original sample [as recommended by @simonsohn2015], recovered a clear effect (albeit a much smaller one).
-There are reasons to think that some effect sizes in the literature may be inflated [@openscienceconsortium; @camerer2018], and it is also possible that changes to experiments or switches to online could result in noisier samples and thus smaller effect sizes.
-Therefore, replications with smaller samples than the original (even if powered to the original effect size), may not be very diagnostic and could potentially benefit from a re-replication.
-
-Not all rescues of small replications succeeded, however.
-@payne2008 was a study of the effects of sleep on memory consolidation.
-They  showed participants a number of images and then hours later (after either sleep or no sleep) measured their recall for parts of the images.
-The first replication struggled to recruit participants to complete a followup session after sleep and only reported a sample size of 23 (the original had 48).
-The rescue attempted to recruit a larger sample (target 88), but also experienced difficulties getting participants to complete the second part of the experiment 12 hours after the first, managing also only to recruit 23 people.
-The lesson here may be that sleep research is difficult to conduct online.
-However, an online replication by @denis2022 reports qualitatively similar (but quantitatively smaller) results to @payne2008 on related but not identical measures.
-
-@child2018 studied reading times for passages of text with different emotional valences written from either a third-person or second-person perspective.
-They found a significant interaction between perspective and valence: participants read positively-valenced passages faster than negatively-valenced passages, but only when they were written from a second-person perspective.
-The first replication used a similar sample size to the original study (40) and found an effect that trended in the same direction, but was substantially smaller.
-The rescuer identified several possible reasons for this failure, foremost among them that the replication was conducted online while the original was conducted in person.
-It is reasonable to expect online studies of reading time to be noisier than in-person studies because the environments participants completed the study in varied much more online.
-The rescue attempt was still online, but used a much larger sample size to account for noisier data.
-Still, the rescue found a non-significant effect that trended in the opposite direction from the original and first replication.
-Even though the first replication trended in the same direction and there was an identifiable reason for the smaller effect size, increasing sample size did not rescue the effect.
-
-# Discussion
-
-Faced with a failed replication, should investigators devote more time to continued replications? There are limited data that inform this decision. 
-To address this gap, we presented the results of `r num_proj` new replications that attempted to "rescue" previous failed replications by identifying and ameliorating possible causes of non-replication.
-`r nrow(success)` of these rescue projects (`r round(nrow(success)/num_proj*100)`%) mostly or fully replicated the original results.
-
-In some cases, increasing sample size and fixing internal validity issues in the replication seems to have led to a successful rescue (although we cannot establish causality even in these cases).
-However, there were other cases where the first replications had issues with a small sample or deviations in the implementation, and the rescue addressed these issues but still failed to replicate the original results.
-We cannot predict what replication failures are likely to resolve given another, more thoughtful try, beyond the suggestion to review studies for best practices in experimental design and sampling [e.g., @experimentology2024].
-
-The rescues all showed smaller effect sizes than their original studies, regardless of whether the pattern of effects replicated.
-A large minority of replications had effect sizes that were statistically inconsistent with the original effect, even accounting for expected levels of heterogeneity between studies.
-These diminished and inconsistent effects suggest that even if a re-replication "works", it may be difficult to build upon as follow-up studies will need large samples to detect small effects.
-
-The reported rescue projects are a small sample of replications, leading to highly uncertain estimates. 
-They are also chosen non-randomly, as they have been selected for twice based on student interest -- once for the original replication and again for the rescue.
-However, this selection bias is likely to correlate with how graduate students and other early career researchers choose what topics to work on and what studies to build on.
-Nevertheless, our estimate is still broadly consistent with that of ManyLabs 5 [29% vs. 22%, @ebersole2020].
-
-In cases where re-replications failed, we do not believe any conclusions are licensed about the status of the original results.
-Students conducting rescue projects put substantial effort into trying to set up rescues that had a good chance of success, but projects were constrained by budget limitations, a short timeline, and the constraint that most data collection needed to occur online.
-These limitations are representative of the sort of resource limitations often faced by early-career researchers.
-That said, it is possible that different results might be obtained in better-resourced settings, by scientists with more expertise and more time.
-<!-- were false positives, we merely claim the original results do not support cumulative research by early-career researchers under the constrained conditions we tested. -->
-
-We opened  with a question about what an early-career psychology researcher should do given a failed replication: should they try again or give up and move on?
-In our sample, the odds of a re-replication working are low [consistent with @ebersole2020].
-Especially if there is not a clear, identifiable candidate cause for replication failure, it may be more efficient to select another result to build on.
-
-# Acknowledgements {.unnumbered}
-
-We thank the students from previous years of PSYCH 251 who graciously agreed to let us re-replicate their projects and shared their work with us.
-We thank the other members of the PSYCH 251 teaching team and students for feedback on projects.
-Data collection was supported by funding from the Stanford Departments of Psychology and Philosophy, Graduate School of Education, and the Symbolic Systems program.
-
-# Author Contributions {.unnumbered}
-
-VB and MCF conceptualized the study. BP contributed project administration, VB contributed formal analysis, and MCF contributed supervision.
-
-Authors other than VB, BP, and MCF each designed, conducted, analyzed, and wrote up one of the rescue projects -- these authors contributed to investigation, formal analysis, and visualization.
-
-VB wrote the first draft, BP and MCF contributed editing, and all authors reviewed the final manuscript.
-
-# References {.unnumbered}
-
-<!-- Use this magic to place references here. -->
-
-::: {#refs}
-:::
+\* Corresponding author. Email: vboyce@stanford.edu

### 2024-07-24 manuscript/coverletter/collabra_response.tex
drafting response

\documentclass{stanfordletter}
%\makelabels

\makelabels
\usepackage{todonotes}
\usepackage{varioref}
\usepackage{xr}
\externaldocument[paper-]{../revision}
\usepackage[american]{babel}
\usepackage{csquotes}
\usepackage[backend=biber,style=apa,doi=false,url=false,hyperref=true,apamaxprtauth=30,uniquename=false]{biblatex}
\usepackage{framed}
\DeclareLanguageMapping{american}{american-apa}
%\bibliography{../draft0}
\newcommand{\citet}[1]{\textcite{#1}}
\newcommand{\citep}[1]{\parencite{#1}}

\newcommand{\theysaid}[1]{\begin{leftbar} \noindent 
		\textsl{ #1}\end{leftbar}}
\newcommand{\revised}[1]{\begin{quote}	#1 \end{quote}}

\usepackage{longtable,booktabs,array}
\usepackage{float}
\begin{document}
	\name{Veronica Boyce}
\signature{\vspace{-35pt} Veronica Boyce, \\ on behalf of the author team}

\begin{letter}{Professor Don van Ravenzwaaij \\ Editor-in-Chief \\ Collabra: Psychology }

	\opening{Dear Dr. van Ravenzwaaij,}

		\theysaid{I have now received two very thorough reviews of your manuscript, “Estimating the replicability of psychology experiments after an initial failure to replicate”, from experts in the field. I also independently read the manuscript before consulting these reviews. The reviewers (self-identified as Daniel Lakens and Rink Hoekstra) had mostly positive reactions to your manuscript. I agree that your manuscript has important strengths and also that there are some issues that need to be addressed. I therefore encourage you to submit a revised version for further consideration at Collabra: Psychology.}

		Thank you for your helpful comments! We have copied the reviews here and respond to them point by point, including quotes from the revised manuscript.

		\theysaid{To summarize what I perceive to be the main points of attention:}

		\theysaid{(1) data accessibility/availability: I shared reviewer \#1’s experience of several broken links, or links that had restricted access. I understand how this might happen with so many different projects, but if this article is to be published, all of these issues will need to be fixed. I strongly urge you, or one of your co-authors, to spend an afternoon clicking on all the links (and also on the links in the links: the preregistration documents include links that do not always work as well) and repair everything that does not work. I’m partial to reviewer \#1’s suggestion of a master-R-markdown, but I will not insist as long as everything works in the end.}

		%TODO check links

		We have checked that the links in %TODO foobar
		all work, and updated the README to be much more detailed.

		Unfortunately, we don't have a way to edit the individual pre-registrations, but we believe all the necessary information for the rescues is now available.

		I also address some of reviewer 1's specific repo-related concerns below; I suspect many of them would have been ameliorated had the reviewer been able to download the repo.

		\theysaid{(2) limitations/quality control: your discussion section, although admirably short, does not address any potential limitations your study has. I share reviewer \#1’s assessment that relative inexperience of the replicators is at least a potential limitation (but see https://journals.sagepub.com/doi/full/10.1177/1475725719857659, which you may wish to cite). There are several other points that reviewer \#1 is concerned about. You may not agree with all of them, so feel free to argue your case when you don’t, but across the board I do think a bit more engagement with these points is essential.}

		%TODO discussion section

		We have expanded the discussion section and re-organized it to have a more explicit discussion of limitations.

		Thank you for the reference, which we have incorporated, and we have included more information on the changes to the discussion below, in our response to reviewer 1.

		Also, see below for our changes and rebuttals to reviewer 1's thoughts.

		\theysaid{(3) implications: reviewer \#2 wonders how your results inform decisions on which papers to ‘rescue’. The final paragraph of the Discussion of your current submission only scratched the surface here. What to do? How valuable are these rescue attempts? Should we do more of them, or should we focus on ‘first’ replications, or should we not do them at all?}

		%TODO discussion section
		We have expanded the discussion section to discuss the larger picture of different circumstances that motivate replications and rescues. We discuss the changes more below in response to reviewer 2's points.

		\theysaid{In your resubmission, please include a document with a point-by-point response to both the points I list here and the reviewers’ comments, outlining each change made in your manuscript or providing a suitable rebuttal. Please ensure that your revised files adhere to our author guidelines, and that the files are fully copyedited/proofed prior to upload. Please also ensure that all necessary copyright permissions have been obtained. This may be the last opportunity for major editing, therefore please fully check your file prior to re-submission.}

		\theysaid{Reviewer 1}

		\theysaid{The authors report the result of replication studies performed as part of an educational project. The results vary – some are relatively similar, of clear null replications, but others show a surprising amount of variability, possibly due to time and resource constraints, or a lack of experience. The main research question is what the probability is that failed studies can be rescued. The authors suggest this probability is rather low, but I think the current study does not really allow such generalizable conclusions. As Many Labs 5, the set of studies is not representative of the population. I have a number of observations that will hopefully help to improve the manuscript.}

		\theysaid{Data needs to be shared in a reproducible manner}
		\theysaid{Regrettably I could not download the files from github – some filenames that have been uploaded are too long, and both cloning the repo as downloading at a zip file give errors (on my windows machine). }

		We are sorry this error occurred, and that reviewer 1 didn't realize the files could be downloaded directly from the OSF copy (linked in the paper).  as the inability of reviewer 1 seems to have resulted in misunderstandings about the usability of files in the repo (which are much more understandable when opened on a computer).

		From googling, we believe this to be a windows issue, and to prevent this problem for future users we have added a note at the top of the README directing readers for how to address or sidestep the problem, namely:

		\revised{Note: If you are a windows user and get an error about overly long file names, please see [this stackoverflow post](https://stackoverflow.com/questions/22575662/filename-too-long-in-git-for-windows) or [this github issue](https://github.com/desktop/desktop/issues/17882) for how to fix it. Alternatively, you can download a zip of the repo from [the osf copy](https://osf.io/cyk5w/files/github) by clicking "Download this folder".}

		\theysaid{The repository is also not organized well enough to make it easy to see all the information. It needs to be restructured, with an actual read me, a clear folder structure, all files should be interoperable, etc. 
		}

		We think the structure is actually pretty clear, but we apologize that the README was not more detailed. We have rewritten the README to be much more explicit about how to reproduce the paper as well as what all the folders and files contain.

		See  https://github.com/langcog/251-rescue-projects/tree/main for the revised README.

		\theysaid{The reports are written in some sort of Rpubs format which consists of many files, but nothing I clicked lead to a readable file – I am quite certain this is not how these files should be exported and shared.}

		As we now clarify in the updated README, these are archival copies of the reports (which were posted to Rpubs). From a cloned/downloaded copy of the repo, the html files can be opened in a browser to see the reports.

		 \revised{\begin{verbatim}
		 		### First-replication-reports and Individual-rescue-reports
		 		* archival copies of the reports from individual projects, in case the rpubs links break or are overwritten
		 		* to view, download the repo and open the html files in a browser

		 	\end{verbatim}}

		\theysaid{In the process.Rmd file, data is downloaded from a google drive https://docs.google.com/spreadsheets/d/12A4DblSbX\_0tHP1mTVJhjNboI1YDngidkNWiSy0sN0g/edit\#gid=0 which I have no access to. }

		This is in an eval=F section, and process.Rmd both runs and knits without access to the file. However, to avoid future confusions, we have made the google spreadsheet openly viewable.

		\theysaid{It is clear this all needs to be checked by a reviewer before the manuscript can be accepted. I would strongly urge the author to add all files as reproducible markdown files (the manuscript, but also the individual data reports).}

		The manuscript is written in an Rmd file that is reproducible. Each of the individual rescue projects was also written in a Rmd or qmd reproducible report (included in the individual project repos included in individual-rescue-projects/). We have now clarified this in the README.

		\revised{ \begin{verbatim}
			The overall manuscript can be reproduced by knitting manuscript/manuscript.Rmd
			* This file reads data from data/combined_data.csv and data/boyce_2023_data.csv
			* This file uses code/helper/parse_stats.R \end{verbatim}}

		\revised{\begin{verbatim}
				### First-replication-projects and Individual-rescue-projects
			* include the individual replication and rescue projects (aka github repos) respectively
			* the rescue projects repos have been checked and include data, code/reproducible report, and the materials to run the experiment\end{verbatim}}

		\theysaid{ The latter can also be exported as PDF is need by, with the raw data and code in the same folder. I believe papers like this require a high quality standard – I would want to see all details if this was a single study, and I want to see all detail of every study when this is a large scale replication project. Ideally, there is a single master file that 1) writes all reproducible original replication reports and rescue reports, 2) takes the output from these reports and compiles the manuscript that has been submitted.}

		We hope that our updated README now makes it clear where to find all of the details of all of the rescue projects as well as the sourcing for the overall manuscript.

		%TODO bug students whose stuff wasn't all there

		\theysaid{Focus on the qualitative data}
		\theysaid{It is interesting to see the results of these projects, as they show the messiness of results when quality control is less strict than in other replication projects. In some ways, the current set of studies can be regarded as a lower bound of replication success under very challenging conditions. Moreover, the qualitative insights when describing the individual studies (which should be extended) is quite educational. For example, it shows the importance of sharing materials, and provides an impetus to require material sharing when a paper is published.}

		We agree that the frustration of original materials not being available or original instructions not being available is education and hopefully serves as an impetus for more sharing.

		\theysaid{ I think a number of improvements to the manuscript are warranted, but I believe that the final result is worth sharing with the scientific community. Because there are no line numbers, the author will perhaps need to search a bit for where my comments apply.
		The case studies section is the most interesting part, but it should be extended to all studies.
		 There are not too many studies, and some can be discussed briefly if results are consistent non-replications. This section should also proceed the quantitative analyses. It is so clear that some studies were incompetently performed that I personally no longer care about the quantitative analyses of these replications. Several of the studies with ugely diverging effect sizes are not discussed at all: Tarampi, Haimowitz, Porter (why did the rescue succeed?).}

		 %TODO extend the case study

		 We thank the reviewer for this idea. We have added brief mentions of the topics and outcomes of each of the studies. We disagree about the ordering, as some readers may be more interested in the bottom line overall results than the individual studies. To support the different tastes, we have added an overview of subsections at the beginning of results so that interested readers could skip to the casestudies if desired.

		 %TODO add mention of the casestudies existance

		\theysaid{Be careful with generalizations}
		\theysaid{In the conclusions the authors generalize beyond the context of students doing replications, to investigators doing replications. However, I do not believe this project allows for such generalizations.}

		This reviewer seems to strongly distinguish between students and investigators. Perhaps this is from a misconception of who we are talking about when we talk about students (perhaps due to differences in training in different areas). To clarify, these were replications done primarily by first year PhD students at an elite US institution. Many publications (including in top journals) are in fact done by PhD students, under the supervision of professors. We checked the google scholars of the rescuers here and 7/17 of them (40\%) already had peer-reviewed journal publications, in some cases multiple. These students are or will soon be publishing in the literature. We agree that they may not have extensive expertise, but we think they and thus their rescue projects are reasonably representative of work by early career researchers with limited resources.

		\theysaid{The replication studies were often not done very well, or with severe limitations (lack of original materials, or switching to an online sample) and when we discuss whether an investigator should further pursuit a research line after a failed replications, it seems fair to at least first assume they will perform a very close replication (even closer than many studies reported here).}

		The original replications were performed under limitations, such as time limits and online samples, which we acknowledge, but which we believe is common when early career researchers build on existing work.

		As for when original materials aren't available, when they aren't available, the replications are as close as they can be, which may be not very close. Replicators did what they could given the external constrain of unavailable materials.

		[TODO not really sure what to say here]

		\theysaid{Experimental design of replication studies}
		\theysaid{The authors state they attempted to adequately power studies, but they refer to trying to achieve 2.5 times the sample size in the original study (ignoring the sample size and effect size in the replication study). But there are no details on what the original effect sizes were and how much power the replication studies had. There is only a mention of sample sizes, not of effect sizes. We only learn much later that several of the first replication studies had substantial challenges in recruiting sufficient participants, and had smaller sample sizes than the originals.}

		[TODO not sure what to do here]

		\theysaid{Subjective replication probability is unclear}
		\theysaid{The subjective replication probability coded as 0, 0.25, 0.75 and 1 is extremely confusing. It should be dropped.}

		We disagree. This coding was used in the paper this is follow-up to (https://royalsocietypublishing.org/doi/full/10.1098/rsos.231240) because it was the coding done at the time of (most) of the original replications.

		There are many metrics for what counts as a successful replication, but many of them depend on a key-statistic. As discussed in Hawkins et al 2018 (https://journals.sagepub.com/doi/full/10.1177/2515245917740427) and Boyce et al 2023 (https://royalsocietypublishing.org/doi/full/10.1098/rsos.231240), original papers often report a number of effects, and it is not always clear which one is the most key. Additionally, often the pattern of interest is dependent on multiple numeric effects (ex. two main effects and their interaction). Thus we think the holistic, subjective assessment of whether or not a study replicated is important, although we also do analyze the key effect as well.

		\theysaid{ When I look at the studies the authors seem to have used this score as some sort of count of properties of the original and replication. For example, a replication study that yielded a significant result but was statistically smaller must have gotten a .5 score. }

		As we write the in the methods section, ``Each project was rated on the basis of subjective replication success (on a 0--1 scale) by both MCF and one of VB and BP.
		We thought about replication in terms of general match in key study results (direction, magnitude, and significance), rather than focusing on any singular numeric result or significance cut-off.''

		\theysaid{
		It would be more useful if the authors just listed the raw properties (was the study significant, was it statistically different from the original, etc). For example, the authors discuss the Krauss replication as succesful, but in Figure 1 it looks like the 95\% CI overlaps with 0. So, it was not statistically significant? Why is it considered to have replicated?}

		Whether a replication is statistically significant in the same direction as the original is one metric that is sometimes used as a measure of replicability, but as TODO CITE SOME PEOPLE SAYING THIS IS DUMB. Patil 2016, Simonsohn 2015, ANdrews and Kasy 2019 are potential cites here!

		As we discuss in the case study section, the Krauss paper reported correct justification from 2/67 in the control condition and 13/34 in the guided thinking condition.  The rescue had 1/40  correct justifications in the control condition and 6/35 in the guided thinking condition. This effect was significant, though smaller than the effect in the original.

		The effect sizes shown are SMDs, but in order to show everything on the same scale, we had to force everything onto that scale, even if it required a lot of conversions requiring approximations. For assessing individual studies it makes more sense to look at their raw results, rather the converted results.

		\theysaid{Statistical analysis}
		\theysaid{Upon first read I was not too enthusiastic about using a replication metric that incorporated heterogeneity. It seems a weird choice to treat unknown variability across studies as statistical uncertainty. Surely, in the end a replication study should mean that we observe the same effect size, and that we understand the topic sufficiently to observe a similar effect repeatedly. However, Figure 1 convinced me that in this context something else needs to be done, as the variability is simple huge. In part this must be due to the students doing the replications. I wonder if the authors redid all analyses and checked for mistakes. Some differences are just too large. We also know from the published literature that there is fraud in student projects, and I wonder if this has been checked.}

		We are fairly confident that there is not fraud as a) committing fraud would have been strictly more work than not and b) students had no incentive to commit fraud. During the class, students submitted their projects for a number of checkpoints. Thus, we know that students had working implementations of the studies because the TAs went through every experiment and gave feedback. Additionally, students had to have working code that ran on their pilot data before they were approved for data collection. We also know that the students ran studies on the class Prolific account because we can see how many participants were recruited and paid for each study. Thus, we know data was collected. Students knew that their grades in no way depended on what results they got (i.e. whether the study replicated), so had no incentive to change the data they had collected.

		Finally, don't you think that if students were going to commit fraud, they'd make the study work better? Even the studies that did rescue had smaller effect sizes than the original studies.

		We also have a larger sample of student replication studies conducted in previous years of the class, and these found a similar rate of replication as previous studies such as RP:P (see Boyce et al 2023).

		\theysaid{For the additional replications it would be good to know if they were class projects or replications by more experienced researchers. For example, I assume at least one is from the RP:P. The authors could cite the studies that are in the literature, and indicate class projects with a different symbol in the figure than the triangle, or using an open triangle. }

		Thanks for this suggestion. In our added case study expansion, we now mention the additional studies and where they come from, citing those from the published literature.

		%TODO this ^

		\theysaid{This needs a finer grained analysis – also because the authors choose to include these replications they are aware of in the meta-analysis to evaluate the results. If these replications are not registered reports, and they come from the published literature, their effects may be biased. If they are from the same authors, they might be biased. If they are done by students, they might be more variable due to some lack of expertise.}

		\theysaid{I do not really like the comparisons of the original against all replications, because sometimes there is so much variability between the studies, it feels weird to meta-analyze them, and it is an example of garbage in, garbage out.}

		I think there may be a misunderstanding here -- we aren't doing meta-analyses because we aren't interested in the aggregate effect size across the original and replications.

		When we discuss the "meta-analytic" mean of some studies that is because the measures of consistency we use (p-original) is between two things, so to compare more than two, some have to be pooled (which does make use of meta-analysis to do the pooling to get an aggregate mean and spread). As described in Mathur and VanderWeele 2020 (https://rss.onlinelibrary.wiley.com/doi/full/10.1111/rssa.12572) which introduces the statistic of p-original, it uses the point estimate and standard error of the original compared to the average population effect size in the replications and standard error thereof. As they mention, the most common way to get the average population effect size is via a random effects meta analysis.

		\theysaid{ First, I do not like the addition of additional replications. No systematic search has been done, so these studies might differ in some ways, and bias the overal effect size estimate. These additional studies can be mentioned, but, we should also see meta-analytic effect sizes without these replications.This can easily be presented in a table with different columns.}

		As we are only interested in studies that are direct replications of the original, it's easy to do a systematic search, and in fact the rescuers did one for each study.

		%TODO add
		We understand the concern about wanting to see just the replication and rescue, so we have added a column to TABLE TODO with this.

		We again note that there appears to be a confusion over what is presented as we never present meta-analytic effect sizes for the reasons discussed above.

		 \theysaid{This can easily be presented in a table with different columns. Currently, only the p-values are reported – this is insufficient. We should see the meta-analytic effect sizes and their confidence intervals. I assume some are incredibly wide due to the widely varying effect sizes, and hence lead to a low p-value.}

		 Again, it seems like there may be confusion here -- the "p-values" presented here are "p-original" which is p-value like in that it's a measure of how likely an estimate would be to be at least as extreme as observed given a "null" distribution. It is a measure of statistical (in-)consistency on the effect sizes, not a measure of how close to zero the effect sizes are.

		 \theysaid{It would also be good to see measures of heterogeneity (even if tests for heterogeneity have low power with few studies). It is a bit weird all tests assume the same tau, when this is clearly not correct. I understand the idea – it is difficult to know the true tau – but this solution seems suboptimal.}

		We have too few datapoints to meaningfully estimate the heterogeneity from our data (Mathur and VanderWeele suggest using the calculated tau if there are 10 or more replications); however, we also know the heterogeneity is not 0, so our best option is to use an estimated measure of heterogeneity, as is done as a sensitivity analysis in Errington et al 2021 and Boyce et al 2023.

		\theysaid{Minor points}
		\theysaid{Why is the median p-orig value reported? What does this tell us? I think this part of section 3.2 can be deleted.}

		P-original is a measure of the statistical (in-)consistency between the original and the replications. We present the median and IQR as a way to summarize the overall levels of inconsistency between original and replication in our sample of studies.

		\theysaid{Not all predictors are explained. What does the predictor ‘ Stanford’ mean? Or log trials? Please explain all predictors, otherwise it is no use to report them.}

		We apologize for this oversight and have added to the caption short descriptions for these two as well as a cross reference to where the predictors are discussed at length in Boyce et al 2023.

		%TODO DO THIS 
		\theysaid{It is the open science collaborations, not consortium.}

		Oops, thank you for bringing this to our attention, we have fixed it.

		\theysaid{All studies replicated should be reported in the reference list.}
		We re-confirmed that all the original studies were present in the reference list.

		\theysaid{Signed, Daniel Lakens}

		%TODO VERONICA IS HERE IN DRAFTING RESPONSES
		\theysaid{Reviewer 2}

		\theysaid{Thanks for the opportunity to review this paper.}

		\theysaid{I believe this is a well-written paper, with an interesting question: Should investigators devote more time to continued replications?
		In the paper, the authors try to “rescue” papers after an original failure to replicate. They show that in their relatively small sample of 17 studies, 5 could be rescued, and the others couldn’t, suggesting that rescuing studies has a high failure rate.}

		\theysaid{I do believe this is an interesting finding, although not completely surprising: in a world in which it is already hard to replicate studies, it make sense that it is even harder to rescue an outcome after a failed replication attempt. But the effort of the authors shows this elegantly, and it also shows, maybe surprisingly to some, that studies actually can be rescued, despite failed replication attempts earlier. In the debates on these issues so far, a failed replication is sometimes presented as the end of the discussion, and indirectly this study shows that it doesn’t have to be. I think the data leave room for multiple sometimes seemingly contradictory conclusions: one could argue that we should be careful in spending our limited resources on trying to rescuing a study that was already unsuccessfully replicated, whereas another could say that the difficulty in finding the right subjects can sometimes affect results in such a way that we should be careful in taking the failed replication too seriously.}

		\theysaid{So in general, I think the findings are interesting, and I think the authors did a good job in writing this up. What I am less convinced about is how this should inform decisions on rescuing papers. What does the general picture (a large majority of studies could not be rescued) tell me as a researcher who is contemplating rescuing a particular study? Since I assume that the selection of studies to be potentially rescued won’t be random, I probably already have reasons why I want to rescue this study. Either I am involved in the issue (I may be one of the people believing the original effect, or I may be even one of the authors of the original study), or I have reasons to believe that something went wrong in the replication study. Or I could believe that if the effect were true, this would be so important to know that it is worth taking the relatively large risk of a failure.}

		\theysaid{What I am trying to say is that the decision to re-replicate is most likely determined by many factors. The fact that on average (so, when picking a to be rescued study randomly) this probability is slim, should in my opinion only be a relatively small part of this decision. To me, this doesn’t disqualify this study, but I think it would be useful if the authors would acknowledge this somehow when discussing the implications of their findings.}

		\theysaid{One minor issue:}
		\theysaid{In the description of Figure 1, it is said that “the first replication’s key effect was non-zero”. I would expect all effects to be non-zero, so that’s not really informative. I guess what the authors mean is that supported for the original effect was found in the replication, or something along these lines}

		\theysaid{So in general, I think this is a neat little paper, which, in my opinion, could benefit from adding a little bit more discussion/depth in the end on what its outcomes could entail.}

		\theysaid{I always sign my reviews,
		Rink Hoekstra}

		We again would like to thank both the editor and the reviewers for their thoughtful and prompt reviews. We hope that our changes to the manuscript and the documentation of our repository offer the necessary clarifications and nuance.

          \closing{Sincerely,}
	\end{letter}

\end{document}

### 2024-07-27 manuscript/coverletter/collabra_response.tex
work on response edits

@@
 
-		As we are only interested in studies that are direct replications of the original, it's easy to do a systematic search, and in fact the rescuers did one for each study.
+		As we are only interested in studies that are direct replications of the original, we think we got them. 
+		%TODO how to navigate this s
 
@@
 
+		%TODO FIX
 		Oops, thank you for bringing this to our attention, we have fixed it.
@@
 
-		%TODO VERONICA IS HERE IN DRAFTING RESPONSES
 		\theysaid{Reviewer 2}
@@
 
+		This point is well taken and we have expanded our discussion to acknowledge the larger space of factors and decisions at play with replications and rescues and the motivations to do them. 
+		%TODO make not suck
+
 		\theysaid{One minor issue:}
@@
 
+		%TODO FIX
+		We have clarified this. 
 		\theysaid{So in general, I think this is a neat little paper, which, in my opinion, could benefit from adding a little bit more discussion/depth in the end on what its outcomes could entail.}

### 2024-07-27 manuscript/manuscript.Rmd
work on response edits

@@
 
-#test_that("number of rows in final sample", {expect_equal(nrow(final_sample),21)})
-
 ```
@@
 source(here("code","helper","parse_stats.R"))
+```
 
+```{r}
 parsed_d <- d |> 
@@
 In psychology, large scale replication projects have found that around half of studies successfully replicate. 
-Across 100 studies with positive results, the reproducibility project in psychology (RP:P) replicated 36%-47% depending on the metric for replication success [@openscienceconsortium].
+Across 100 studies with positive results, the reproducibility project in psychology (RP:P) replicated 36%-47% depending on the metric for replication success [@opensciencecollaboration].
 With large multi-site samples, Many Labs 1 replicated 11/13 effects (84.6%), Many Labs 2 replicated 14/28 effects (50%), and Many Labs 3 replicated 3/10 effects (30%) [@klein2014; @klein2018; @ebersole2016].
@@
 One estimate comes from @ebersole2020.
-After the original RP:P study reported of a replication rate around 40% [@openscienceconsortium], @gilbert2016 raised concerns that methodological differences might explain the low replication rate.
+After the original RP:P study reported of a replication rate around 40% [@opensciencecollaboration], @gilbert2016 raised concerns that methodological differences might explain the low replication rate.
 In 11 of the RP:P studies, the original authors had raised concerns about protocol fidelity prior to data collection.
@@
 Due to the large effect size of a couple studies, large effect studies are shown in a separate panel.
-In a few cases, the first replication's key effect was non-zero in the same direction as the original; however, in these cases the larger pattern of results was not fully consistent between original and first replication.
+In a few cases, the first replication's key effect was in the same direction as the original with a 95% CI that did not overlap 0; however, in these cases the larger pattern of results was not fully consistent between original and first replication.
 "}
@@
 
+orig_v_rr <- parsed_d |> select(target_lastauthor_year, type, d=calc_d_calc, d_se=calc_d_calc_se) |> 
+  filter(type=="rescue"|type=="rep1") |> 
+  group_by(target_lastauthor_year) |> 
+  nest() |> 
+  mutate(d_rma_result=map(data, do_d_rma)) |> 
+  unnest_wider(d_rma_result) |> 
+  left_join(orig) |> 
+  rowwise() |> 
+  mutate(d_p_orig=do_p_orig(d, d_se, rma_d_est, rma_d_se))
+
 orig_v_rescue <- parsed_d |>   filter(type=="rescue") |> 
@@
  all <- orig_v_others |> select(target_lastauthor_year, orig_v_other=d_p_orig) |> 
+   left_join(orig_v_rr |> select(target_lastauthor_year, orig_v_rr=d_p_orig)) |> 
   left_join(orig_v_rescue |> select(target_lastauthor_year, orig_v_rescue=d_p_orig)) |> 
@@
             less_than=sum(orig_v_other<.05, na.rm=T)/sum(!is.na(orig_v_other)))
+
+rr_summ <- all |> ungroup() |> select(orig_v_rr) |>
+  summarize(median=median(orig_v_rr, na.rm=T),
+            low=quantile(orig_v_rr, .25, na.rm=T),
+            high=quantile(orig_v_rr, .75, na.rm=T),
+            less_than=sum(orig_v_rr<.05, na.rm=T)/sum(!is.na(orig_v_rr)))
 
@@
 
-all |> ungroup() |>  left_join(names) |> select(Paper=name_pretty, `All reps`=orig_v_other, "Rescue" = orig_v_rescue, "Non-rescue"=orig_v_not_rescue, "Other reps"=rescue_v_reps) |> knitr::kable(format="latex", booktabs=T, linesep="", caption="$P$-original values between different sets of experiments.
+all |> ungroup() |>  left_join(names) |> select(Paper=name_pretty, `All reps`=orig_v_other, "1st rep and Rescue"=orig_v_rr, "Rescue" = orig_v_rescue, "Non-rescue"=orig_v_not_rescue, "Other reps"=rescue_v_reps) |> knitr::kable(format="latex", booktabs=T, linesep="", caption="$P$-original values between different sets of experiments.
 The primary analysis is between the original result and the meta-analytic aggregation of all replications.
 All $p$-original values assume an imputed heterogeneity value of $\\tau$=.21.", digits=3) |>
-  add_header_above(c(" "=1, "Original and"=3, "Rescue and"=1)) |> add_header_above(c(" "=1, "p-original comparing between"=4))
+  add_header_above(c(" "=1, "Original and"=4, "Rescue and"=1)) |> add_header_above(c(" "=1, "p-original comparing between"=5))
 
@@
 
-As secondary measures, we calculated the $p$-original values between a) the original and the rescue, b) the original and non-rescue replications, and c) the rescue and other replications.
-For a) the original versus the rescue, the median value of $p$-original was `r rescue_summ$median |> round(2)` [IQR: `r rescue_summ$low |> round(2)` - `r rescue_summ$high|> round(2)`], and `r round(rescue_summ$less_than*100)`% of the $p$-original values were less than .05.
-For b) the original versus all the non-rescue replications, the median value of $p$-original was `r rep_summ$median |> round(2)` [IQR: `r rep_summ$low |> round(2)` - `r rep_summ$high |> round(2)`], and `r round(rep_summ$less_than*100)`% of the $p$-original values were less than .05.
-For c) the rescue versus the other replications, the median value of $p$-original was `r rescue_rep_summ$median |> round(2)` [IQR: `r rescue_rep_summ$low |> round(2)` - `r rescue_rep_summ$high |> round(2)`], and `r round(rescue_rep_summ$less_than*100)`% of the $p$-original values were less than .05.
+As secondary measures, we calculated the $p$-original values between a) the original and just the first replication and rescue, b) the original and the rescue, c) the original and non-rescue replications, and d) the rescue and other replications.
+For a) the original versus the rescue, the median value of $p$-original was `r rr_summ$median |> round(2)` [IQR: `r rr_summ$low |> round(2)` - `r rr_summ$high|> round(2)`], and `r round(rr_summ$less_than*100)`% of the $p$-original values were less than .05.
+For b) the original versus the rescue, the median value of $p$-original was `r rescue_summ$median |> round(2)` [IQR: `r rescue_summ$low |> round(2)` - `r rescue_summ$high|> round(2)`], and `r round(rescue_summ$less_than*100)`% of the $p$-original values were less than .05.
+For c) the original versus all the non-rescue replications, the median value of $p$-original was `r rep_summ$median |> round(2)` [IQR: `r rep_summ$low |> round(2)` - `r rep_summ$high |> round(2)`], and `r round(rep_summ$less_than*100)`% of the $p$-original values were less than .05.
+For d) the rescue versus the other replications, the median value of $p$-original was `r rescue_rep_summ$median |> round(2)` [IQR: `r rescue_rep_summ$low |> round(2)` - `r rescue_rep_summ$high |> round(2)`], and `r round(rescue_rep_summ$less_than*100)`% of the $p$-original values were less than .05.
 
@@
 
-  mutate(Predictors=factor(preds, levels=c("social", "other_psych", "is_within", "single_vignette", "change_platform", "open_data", "open_mat", "stanford", "pub_year", "log_trials", "log_sample", "log_ratio_ss", "rep_1_log_sample", "log_ratio_rep1_orig", "log_ratio_rescue_rep1"), labels=c("Social", "Other psych", "Within subjects", "Single vignette", "Switch to online", "Open data", "Open materials", "Stanford", "Publication year", "Log trials", "Log original sample size", "Log rescue/original sample size", "Log replication sample size", "Log replication/original sample size", "Log rescue/replication sample size"))) |> arrange(Predictors) |> select(Predictors, r, p)
+  mutate(Predictors=factor(preds, levels=c("social", "other_psych", "is_within", "single_vignette", "change_platform", "open_data", "open_mat", "stanford", "pub_year", "log_trials", "log_sample", "log_ratio_ss", "rep_1_log_sample", "log_ratio_rep1_orig", "log_ratio_rescue_rep1"), labels=c("Social", "Other psych", "Within subjects", "Single vignette", "Switch to online", "Open data", "Open materials", "Original authors at Stanford", "Publication year", "Log number of trials", "Log original sample size", "Log rescue/original sample size", "Log replication sample size", "Log replication/original sample size", "Log rescue/replication sample size"))) |> arrange(Predictors) |> select(Predictors, r, p)
 
@@
 The first set of predictors were pre-registered based on the correlates used in Boyce et al.
+(2023).
+Original authors at Stanford refers to at the time of the first replication as this may mean the first replication was not independent.
+For details about how the predictors were coded, see the Methods section of Boyce et al.
 (2023).
@@
 The rescue, powered using 2.5x the original sample [as recommended by @simonsohn2015], recovered a clear effect (albeit a much smaller one).
-There are reasons to think that some effect sizes in the literature may be inflated [@openscienceconsortium; @camerer2018], and it is also possible that changes to experiments or switches to online could result in noisier samples and thus smaller effect sizes.
+There are reasons to think that some effect sizes in the literature may be inflated [@opensciencecollaboration; @camerer2018], and it is also possible that changes to experiments or switches to online could result in noisier samples and thus smaller effect sizes.
 Therefore, replications with smaller samples than the original (even if powered to the original effect size), may not be very diagnostic, and could potentially benefit from a re-replication.
@@
 
+## Limitations
+
 The reported rescue projects are a small sample of replications, leading to highly uncertain estimates. 
-They are also chosen non-randomly, as they have been selected for twice based on student interest -- once for the original replication and again for the rescue.
+Additionally, they are also chosen non-randomly, as they have been selected for twice based on student interest -- once for the original replication and again for the rescue.
 However, this selection bias is likely to correlate with how graduate students and other early career researchers choose what topics to work on and what studies to build on.
@@
 That said, it is possible that different results might be obtained in better-resourced settings, by scientists with more expertise and more time.
+
+Due to the limited number of replications that are conducted and systematically reported, and the even smaller number of re-replications reported, there is a lot of uncertainty in how much replicability varies across features of the original experiment and replications.
+## Conclusion
 <!-- were false positives, we merely claim the original results do not support cumulative research by early-career researchers under the constrained conditions we tested. -->

### 2024-07-30 manuscript/manuscript.Rmd
trying to fill in discussion and case reports...
but it's not very good

@@
 
+We first discuss the overall rate of replication in the rescue projects, followed by looking at the relative effect sizes of the rescues and correlates of rescue success.
+In the last subsection we describe the topic of each studies and focus on a few interesting case studies.
+
 ## Overall replication rate
@@
 
-all |> ungroup() |>  left_join(names) |> select(Paper=name_pretty, `All reps`=orig_v_other, "1st rep and Rescue"=orig_v_rr, "Rescue" = orig_v_rescue, "Non-rescue"=orig_v_not_rescue, "Other reps"=rescue_v_reps) |> knitr::kable(format="latex", booktabs=T, linesep="", caption="$P$-original values between different sets of experiments.
+all |> ungroup() |>  left_join(names) |> select(Paper=name_pretty, `All reps`=orig_v_other, "1st Rep and Rescue"=orig_v_rr, "Rescue" = orig_v_rescue, "Non-rescue"=orig_v_not_rescue, "Other reps"=rescue_v_reps) |> knitr::kable(format="latex", booktabs=T, linesep="", caption="$P$-original values between different sets of experiments.
 The primary analysis is between the original result and the meta-analytic aggregation of all replications.
@@
 As secondary measures, we calculated the $p$-original values between a) the original and just the first replication and rescue, b) the original and the rescue, c) the original and non-rescue replications, and d) the rescue and other replications.
-For a) the original versus the rescue, the median value of $p$-original was `r rr_summ$median |> round(2)` [IQR: `r rr_summ$low |> round(2)` - `r rr_summ$high|> round(2)`], and `r round(rr_summ$less_than*100)`% of the $p$-original values were less than .05.
+For a) the original versus the first replication and the rescue, the median value of $p$-original was `r rr_summ$median |> round(2)` [IQR: `r rr_summ$low |> round(2)` - `r rr_summ$high|> round(2)`], and `r round(rr_summ$less_than*100)`% of the $p$-original values were less than .05.
 For b) the original versus the rescue, the median value of $p$-original was `r rescue_summ$median |> round(2)` [IQR: `r rescue_summ$low |> round(2)` - `r rescue_summ$high|> round(2)`], and `r round(rescue_summ$less_than*100)`% of the $p$-original values were less than .05.
@@
 
-Given the mix of successful and unsuccessful rescue projects, we discuss a few projects where we have speculations about why they turned out the way they did.
+Given the mix of successful and unsuccessful rescue projects, we briefly discuss all the projects and go more in depth on a few projects where we have speculations about why they turned out the way they did.
 
@@
 The rescue, powered using 2.5x the original sample [as recommended by @simonsohn2015], recovered a clear effect (albeit a much smaller one).
+An additional replication from the literature, @ngo2021 successfully replicated @ngo2019.
 There are reasons to think that some effect sizes in the literature may be inflated [@opensciencecollaboration; @camerer2018], and it is also possible that changes to experiments or switches to online could result in noisier samples and thus smaller effect sizes.
@@
 However, an online replication by @denis2022 reports qualitatively similar (but quantitatively smaller) results to @payne2008 on related but not identical measures.
+@denis2022 which has an overlapping author team to @payne2008 is included here as an additional replication.
 
@@
 Even though the first replication trended in the same direction and there was an identifiable reason for the smaller effect size, increasing sample size did not rescue the effect.
+
+@birch2007 is about a false belief task comparing ignorance and plausible knowledge conditions.
+The first replication, an additional class replication, and the rescue all found effects directionally consistent with the original, but much smaller.
+
+@craig2014 had White Americans read an article about shifting racial demographics in the US, either with or without a framing that assuaged the potential threat, and found that reading the un-assuaged version led to the endorsement of more conservative positions.
+
+@gong2019 looked at the interplay between age and willingness to donate in older adults in Hong Kong and found a three-way interaction between age, type of donation, and relationship to recipient.
+Neither the replication that sampled US adults nor the rescue that sampled East Asian adults recovered this interaction.
+
+@haimovitz2016 manipulated parents' mindsets with "failure-is-enhancing" or "failure-is-debilitating" primes and looked at their reactions to a hypothetical situation in which a child received a failing grade.
+The first replication was directionally consistent with the original, but an additional class replication was not.
+The rescue added manipulation checks which passed, but did not recover the target effect.
+
+@hopkins2016 examined whether people prefer reductive explanations to horizontal explanations.
+While the original found a preference for reductive explanations, the replication and rescue both did not.
+
+@jara-ettinger2022 looked at shape bias in US adults across 3 shape exemplars and found a preference to extend nouns on the basis of shape over color or material.
+The replication and rescue both found an above chance preference for shape, but with widely different item-level effects and relative preferences for color and material.
+
+@paxton2012 found that participants who completed the CRT before the moral judgement task gave more utilitarian answers than those who did the moral judgment task before the CRT.
+Neither the replication nor the rescue found this effect.
+
+@porter2016 looked at how linguistic intergroup bias influences judgments of shared group membership.
+The replication was directionally against the original, the rescue found that effect, although the manipulation check failed.
+@schechtman2010 looked at how widely people generalize tones that previously have been paired with losses or gains, and found that the loss-paired tones were generalized more.
+The first replication and rescue both found the same main effect, but with a very different pattern over distance.
+
+As discussed in methods, @tarampi2016 had participants do a timed navigation task and found an interaction between participant gender and the framing of the task (social or spatial) on performance.
+Neither first replication nor rescue recovered the interaction.
+@todd2016 looked at participants speed at classifying toys and guns as a function of whether they had just need a White or Black boy's face.
+@todd2016 found an interaction where Black faces primed faster "gun" responses and White faces faster "toy" responses.
+When we reached out to the original authors, they offered to run a parallel rescue on their student subject pool, which we have here as an additional replication.
+The first replication did not find the interaction, but both the better-powered rescue did.
+
+@yeshurun2003 looked at the relationship between spatial attention and temporal resolution.
+They measured the threshold where two flashes of light are percieved as one flash versus two as a function of whether the location of the flashes was pre-cued or not.
+@yeshurun2003 found that cueing led to less temporal resolution.
+This was independently replicated by @chica2009, but was not replicated by either the student replication or the rescue.
 
@@
 A large minority of replications had effect sizes that were statistically inconsistent with the original effect, even accounting for expected levels of heterogeneity between studies.
-These diminished and inconsistent effects suggest that even if a re-replication "works", it may be difficult to build upon as follow-up studies will need large samples to detect small effects.
 
@@
 The reported rescue projects are a small sample of replications, leading to highly uncertain estimates. 
-Additionally, they are also chosen non-randomly, as they have been selected for twice based on student interest -- once for the original replication and again for the rescue.
+Additionally, they were chosen non-randomly, as they were doubly selected for based on student interest -- once for the original replication and again for the rescue.
 However, this selection bias is likely to correlate with how graduate students and other early career researchers choose what topics to work on and what studies to build on.
@@
 ## Conclusion
-<!-- were false positives, we merely claim the original results do not support cumulative research by early-career researchers under the constrained conditions we tested. -->
+Overall, the diminished and inconsistent effects we found in the rescues suggest that even if a re-replication "works", it may be difficult to build upon as follow-up studies will need large samples to detect small effects.
+
+Replications are done for many reasons, and researchers often have some prior beliefs about whether a replication will succeed.
+These beliefs may influence how a researcher interprets a failed replication and thus whether they think it's worth trying to rescue.
+For instance, a researcher who has high credence in the main result is more likely to attribute failure to specific details in the replication and thus want to rescue by tweaking these details.
+On the other side, a researcher who is dubious of the methods, results, or statistical approaches, or who has experienced failures to replicate and extend the work, may be quicker to interpret a failure as a more definitive negative result.
+Interpretations may also depend on the perceived strength of the replication and what effect size is cared about.
+
+While we focus here on a narrow type of replication and rescue, that done by an early career researcher with the goal of establishing whether this is a result *they* can build on, it exists as part of a wider ecosystem of replications that are done for different reasons with different properties.
 

### 2024-08-01 manuscript/manuscript.Rmd
Moved individual project summaries to appendix and added more detail

@@
 :::
+
 <!-- TODO compile everything into OSF repo & link -->
+
 <!-- TODO link individual pre-reg's in repo -->
+
 <!-- TODO link overall pre-reg -->
+
 <!-- TODO include in repo & link the reasons for replication failure that were offered to students -->
+
 <!-- TODO redo/double check closeness scores for first rep and rescues  -->
+
 <!-- TODO author contributions, acknowledgements -->
@@
 Imagine you are a graduate student, and you run a replication of a study that you are interested in building upon in your research.
-The replication fails. Perhaps the interaction you hoped for is directionally correct, but the point estimate is small and the confidence interval definitely overlaps 0, with a $p$-value of .3.
+The replication fails.
+Perhaps the interaction you hoped for is directionally correct, but the point estimate is small and the confidence interval definitely overlaps 0, with a $p$-value of .3.
 Or perhaps the interaction is numerically in the wrong direction and the main effects look different.
-<!--Or maybe the main effect of interest may be null, but you found a significant effect interaction that wasn't hypothesized.-->
-Whatever the details of the replication failure, you are left with a question: Should you try again and run a re-replication, or should you give up and pick a different study to build upon?
+<!--Or maybe the main effect of interest may be null, but you found a significant effect interaction that wasn't hypothesized.--> Whatever the details of the replication failure, you are left with a question: Should you try again and run a re-replication, or should you give up and pick a different study to build upon?
 
@@
 But in practice, the relationship between original and replication is not symmetric, and many causes of replication failure can be attributed either more to the original study or more to the replication.
--->
-Starting with the original study, one potential reason for replication failure is that the original result is fragile in some way.
+--> Starting with the original study, one potential reason for replication failure is that the original result is fragile in some way.
 It could be a statistically unlikely result that was achieved through chance or $p$-hacking, or it could be sensitive to the exact conditions and time it was run under ("hidden moderators").
@@
 -->
+
 Relatively few studies have estimated re-replication success.
@@
 <!-- We could frame @ebersole2020 as an attempt to recover the original effects of the 9 studies with significant original effects and non-significant RP:P effects by a combination of high power and design tweaks.
--->
-The re-replication success rate was thus 2/9 (22%) for studies with non-significant first replications, under favorable, high-resource circumstances.
+--> The re-replication success rate was thus 2/9 (22%) for studies with non-significant first replications, under favorable, high-resource circumstances.
 
@@
 The focus of the class was best practices in experimental design; thus, students looked at both the original paper and the failed replication to examine potential issues in the replication that they could fix in their rescue project.
-In the present paper, we report the results of `r num_proj` re-replication rescue projects. We find that a minority of projects (5/17, 29%) successfully recovered the original effect.
+In the present paper, we report the results of `r num_proj` re-replication rescue projects.
+We find that a minority of projects (5/17, 29%) successfully recovered the original effect.
 
@@
 
-A spreadsheet of projects, individual project write-ups (both first replications and rescues), individual project data and analyses for rescue projects, and the analytic code for this paper are all available at https://osf.io/cyk5w/.
+A spreadsheet of projects, individual project write-ups (both first replications and rescues), individual project data and analyses for rescue projects, and the analytic code for this paper are all available at <https://osf.io/cyk5w/>.
 
@@
 Each project was also individually pre-registered by the student conducting it.
-The overall analysis is pre-registered at https://osf.io/5qz7v, individual pre-registrations are linked from https://osf.io/vkbfw.
+The overall analysis is pre-registered at <https://osf.io/5qz7v>, individual pre-registrations are linked from <https://osf.io/vkbfw>.
 We note one deviation from our pre-registration here: we pre-registered visual comparisons between original, first replication, and rescue projects using prediction intervals.
@@
 This left `r length(approved)` options for the students to choose from.
-`r length(chosen)` students chose to do rescue projects, and
-`r length(chosen)-num_proj` students did not finish their project or did not indicate interest in being part of this paper, leaving a final sample of `r num_proj` rescue projects.
+`r length(chosen)` students chose to do rescue projects, and `r length(chosen)-num_proj` students did not finish their project or did not indicate interest in being part of this paper, leaving a final sample of `r num_proj` rescue projects.
 
@@
 ```
+
 ## Procedure
@@
 Students were required to think of reasons the first replication might not have worked, and address them if they could.
-A list of possible reasons and solutions was given to students (https://osf.io/dfwk2).
+A list of possible reasons and solutions was given to students (<https://osf.io/dfwk2>).
 In general, we encouraged students to add manipulation checks as appropriate, and to adapt their materials to online studies, which may benefit from attention checks and/or shorter duration.
-For instance, the rescue of @paxton2012 switched from using the cognitive reflection task (CRT) which many online participants are over-familiar with to using the newer CRT-2 which is less overused but attempts to measure the same construct [@thomson2016].
+For instance, the rescue of @paxton2012 switched from using the Cognitive Teflection Test (CRT) which many online participants are over-familiar with to using the newer CRT-2 which is less overused but attempts to measure the same construct [@thomson2016].
 The rescue of @jara-ettinger2022 discovered that the replication had accidentally used an illustrated version of the stimuli rather than the photographic stimuli used in the original and used the photographic stimuli instead.
@@
 We first discuss the overall rate of replication in the rescue projects, followed by looking at the relative effect sizes of the rescues and correlates of rescue success.
-In the last subsection we describe the topic of each studies and focus on a few interesting case studies.
+In the last subsection we describe several interesting case studies.
 
@@
 
-Given the mix of successful and unsuccessful rescue projects, we briefly discuss all the projects and go more in depth on a few projects where we have speculations about why they turned out the way they did.
+Given the mix of successful and unsuccessful rescue projects, we discuss in depth a few projects where we have speculations about why they turned out the way they did.
+Brief descriptions of the projects not covered in this section be found in the Appendix.
 
@@
 
-@birch2007 is about a false belief task comparing ignorance and plausible knowledge conditions.
-The first replication, an additional class replication, and the rescue all found effects directionally consistent with the original, but much smaller.
-
-@craig2014 had White Americans read an article about shifting racial demographics in the US, either with or without a framing that assuaged the potential threat, and found that reading the un-assuaged version led to the endorsement of more conservative positions.
-
-@gong2019 looked at the interplay between age and willingness to donate in older adults in Hong Kong and found a three-way interaction between age, type of donation, and relationship to recipient.
-Neither the replication that sampled US adults nor the rescue that sampled East Asian adults recovered this interaction.
-
-@haimovitz2016 manipulated parents' mindsets with "failure-is-enhancing" or "failure-is-debilitating" primes and looked at their reactions to a hypothetical situation in which a child received a failing grade.
-The first replication was directionally consistent with the original, but an additional class replication was not.
-The rescue added manipulation checks which passed, but did not recover the target effect.
-
-@hopkins2016 examined whether people prefer reductive explanations to horizontal explanations.
-While the original found a preference for reductive explanations, the replication and rescue both did not.
-
-@jara-ettinger2022 looked at shape bias in US adults across 3 shape exemplars and found a preference to extend nouns on the basis of shape over color or material.
-The replication and rescue both found an above chance preference for shape, but with widely different item-level effects and relative preferences for color and material.
-
-@paxton2012 found that participants who completed the CRT before the moral judgement task gave more utilitarian answers than those who did the moral judgment task before the CRT.
-Neither the replication nor the rescue found this effect.
-
-@porter2016 looked at how linguistic intergroup bias influences judgments of shared group membership.
-The replication was directionally against the original, the rescue found that effect, although the manipulation check failed.
-@schechtman2010 looked at how widely people generalize tones that previously have been paired with losses or gains, and found that the loss-paired tones were generalized more.
-The first replication and rescue both found the same main effect, but with a very different pattern over distance.
-
-As discussed in methods, @tarampi2016 had participants do a timed navigation task and found an interaction between participant gender and the framing of the task (social or spatial) on performance.
-Neither first replication nor rescue recovered the interaction.
-@todd2016 looked at participants speed at classifying toys and guns as a function of whether they had just need a White or Black boy's face.
-@todd2016 found an interaction where Black faces primed faster "gun" responses and White faces faster "toy" responses.
-When we reached out to the original authors, they offered to run a parallel rescue on their student subject pool, which we have here as an additional replication.
-The first replication did not find the interaction, but both the better-powered rescue did.
-
-@yeshurun2003 looked at the relationship between spatial attention and temporal resolution.
-They measured the threshold where two flashes of light are percieved as one flash versus two as a function of whether the location of the flashes was pre-cued or not.
-@yeshurun2003 found that cueing led to less temporal resolution.
-This was independently replicated by @chica2009, but was not replicated by either the student replication or the rescue.
-
 # Discussion
 
-Faced with a failed replication, should investigators devote more time to continued replications? There are limited data that inform this decision. 
+Faced with a failed replication, should investigators devote more time to continued replications?
+There are limited data that inform this decision.
 To address this gap, we presented the results of `r num_proj` new replications that attempted to "rescue" previous failed replications by identifying and ameliorating possible causes of non-replication.
@@
 Due to the limited number of replications that are conducted and systematically reported, and the even smaller number of re-replications reported, there is a lot of uncertainty in how much replicability varies across features of the original experiment and replications.
+
 ## Conclusion
+
 Overall, the diminished and inconsistent effects we found in the rescues suggest that even if a re-replication "works", it may be difficult to build upon as follow-up studies will need large samples to detect small effects.
@@
 
-VB and MCF conceptualized the study. BP contributed project administration, VB contributed formal analysis, and MCF contributed supervision.
+VB and MCF conceptualized the study.
+BP contributed project administration, VB contributed formal analysis, and MCF contributed supervision.
 
@@
 <!-- Use this magic to place references here. -->
+<div id="refs"></div>
+
+# Appendix {.unnumbered}
+
+@birch2007 is about a false belief task comparing ignorance and plausible knowledge conditions.
+The first replication and an additional class replication both found results directionally consistent with the original, but much smaller.
+The rescue used a much larger sample size than both the original and the first replication and added an additional check to make sure the probabilities participants reported add up to 100%.
+The rescue result was directionally consistent with the original and prior replications, but did not find a significant effect.
+
+@craig2014 had White Americans read an article about shifting racial demographics in the US, either with or without a framing that assuaged the potential threat, and found that reading the un-assuaged version led to the endorsement of more conservative positions.
+The first replication did not find a significant difference between conditions, and the rescuer speculated that this was due to a smaller sample size and a skew toward liberal political beliefs in the participant pool.
+The rescue recruited the same number of participants as the original study and dropped one of the conditions to increase power.
+Despite the increased power, the rescue did not replicate the original paper's finding.
+
+@gong2019 looked at the interplay between age and willingness to donate in older adults in Hong Kong and found a three-way interaction between age, type of donation, and relationship to recipient.
+The first replication sampled US adults and did not find a significant interaction.
+The rescuer thought that cultural differences may have played a role and specifically sampled Asian American adults.
+The rescue did not recover the interaction.
+
+@haimovitz2016 manipulated parents' mindsets with "failure-is-enhancing" or "failure-is-debilitating" primes and looked at their reactions to a hypothetical situation in which a child received a failing grade.
+The first replication was directionally inconsistent with the original, but an additional class replication was consistent.
+The rescue added manipulation checks which were not present in the original study or either replications.
+The manipulation checks passed, but the rescue study did not recover the target effect.
+
+@hopkins2016 examined whether people prefer reductive explanations, which explain a result in one science with a more "fundamental" science, to horizontal explanations, which explain a result in one science in terms of the same science.
+While the original study found a preference for reductive explanations, the first replication did not.
+The replication's effective sample size was smaller than the original because a large proportion of participants failed the attention check.
+The rescue increased made the attention check slightly easier and recruited a larger sample to account for failures, but still did not replicate the original effect.
+
+@jara-ettinger2022 looked at shape bias in US adults across 3 shape exemplars and found a preference to extend nouns on the basis of shape over color or material.
+The replication found an above-chance preference for shape, but with very high item-level variability.
+The rescuer found that the first replication used stylized versions of the original stimuli taken from a different part of the paper.
+The rescue used the same images of stimuli as the original, but still found strong item-level effects and relative preferences for color and material.
+
+@paxton2012 found that participants who completed the Cognitive Reflection Test (CRT) before the moral judgement task gave more utilitarian answers than those who did the moral judgment task before the CRT.
+The replication rewrote some of the CRT questions, adding a sub-condition where some of the questions featured characters with specific names.
+The first replication failed to find an effect.
+The rescuer removed the sub-condition and used questions from the CRT-2, out of concern that Prolific participants would be familiar with the original CRT questions.
+The rescue also failed to find the effect.
+
+@porter2016 looked at how linguistic intergroup bias influences judgments of shared group membership.
+The first replication was directionally against the original result.
+The rescuer obtained the direct wordings of the questions from the authors of the original paper, and noticed that they were substantially different from questions in the first replication.
+The rescue used the same wordings as the original paper and replicated the effect, although the manipulation check failed.
+
+@schechtman2010 looked at how widely people generalize tones that previously have been paired with losses or gains, and found that the loss-paired tones were generalized more.
+The first replication found a statistically significant effect in the opposite direction of the original study.
+It also found that people took much longer to learn which tones were associated with gains vs. losses compared to the original.
+The rescuer made several changes, including asking questions about the sound quality of the participant's computer.
+The original study was conducted in person while the replication and rescue were online, so differences in speaker and headphone quality might have played a role in the different result.
+The replication found an effect in the same direction as the 1st replication (contrary to the original study).
+
+As discussed in methods, @tarampi2016 had participants do a timed navigation task and found an interaction between participant gender and the framing of the task (social or spatial) on performance.
+The result from the first replication was both statistically insignificant and directionally inconsistent.
+The original study was conducted in person, while the replication was conducted online, which might have contributed to the inconsistency.
+The rescue was also conducted online, but the rescuer made a series of user interface changes, a comprehension check, and exclusion criteria to ensure that participants understood the instructions, found the task convenient to interact with, and were engaged throughout the experiment.
+Still, the rescue did not recover the interaction.
+
+@todd2016 looked at participants speed at classifying toys and guns as a function of whether they had just need a White or Black boy's face.
+@todd2016 found an interaction where Black faces primed faster "gun" responses and White faces faster "toy" responses.
+When we reached out to the original authors, they offered to run a parallel rescue on their student subject pool, which we have here as an additional replication.
+The first replication did not find the interaction, but both the better-powered rescue and the original authors' replication did.
+
+@yeshurun2003 looked at the relationship between spatial attention and temporal resolution.
+They measured the threshold where two flashes of light are percieved as one flash versus two as a function of whether the location of the flashes was pre-cued or not.
+@yeshurun2003 found that cueing led to less temporal resolution.
+This was independently replicated by @chica2009, but was not replicated by either the student replication or the rescue.
+Both the replication and rescue used in-person participants because the study relies on precise timing and details of the screen which are difficult to control online.
+The first replication had a smaller sample size than the original, while the rescue matched the original study's sample size.

### 2024-08-01 manuscript/manuscript.tex
Moved individual project summaries to appendix and added more detail

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
\PassOptionsToPackage{dvipsnames,svgnames,x11names}{xcolor}
%
\documentclass[
  english,
  a4paper,
]{article}
\usepackage{amsmath,amssymb}
\usepackage{lmodern}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  pdftitle={Estimating the replicability of psychology experiments after an initial failure to replicate},
  pdflang={en},
  colorlinks=true,
  linkcolor={blue},
  filecolor={Maroon},
  citecolor={blue},
  urlcolor={blue},
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage[margin=25mm]{geometry}
\usepackage{longtable,booktabs,array}
\usepackage{calc} % for calculating minipage widths
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\usepackage{footnote} % For some unknown reason, footnotehyper clashes with French
\makesavenoteenv{longtable}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{5}
% definitions for citeproc citations
\NewDocumentCommand\citeproctext{}{}
\NewDocumentCommand\citeproc{mm}{%
	\begingroup\def\citeproctext{#2}\cite{#1}\endgroup}
\makeatletter
% allow citations to break across lines
\let\@cite@ofmt\@firstofone
% avoid brackets around text for \cite:
\def\@biblabel#1{}
\def\@cite#1#2{{#1\if@tempswa , #2\fi}}
\makeatother
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newenvironment{CSLReferences}[2] % #1 hanging-indent, #2 entry-spacing
{\begin{list}{}{%
			\setlength{\itemindent}{0pt}
			\setlength{\leftmargin}{0pt}
			\setlength{\parsep}{0pt}
			% turn on hanging indent if param 1 is 1
			\ifodd #1
			\setlength{\leftmargin}{\cslhangindent}
			\setlength{\itemindent}{-1\cslhangindent}
			\fi
			% set entry spacing
			\setlength{\itemsep}{#2\baselineskip}}}
	{\end{list}}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{\hfill\break\parbox[t]{\linewidth}{\strut\ignorespaces#1\strut}}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{\strut#1\strut}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{\strut#1\strut}}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}

%%%%%%%% START HEADER PARTIAL %%%%%%%%%%%%

% Formatting of tables & knitr::kable and kableExtra functionality
\usepackage{float}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}

% Line numbering

% endfloat stuff

% fancyhdr pagestyle

% Environment for keywords
\makeatletter
\newcommand\keywordsname{Keywords}
\newenvironment*{keywords}[1][\keywordsname]{\if@twocolumn \else \small \quotation \fi \begin{center} \textbf{\textit{#1} \\}}{\end{center}\if@twocolumn \else \small \endquotation \fi}
\newenvironment*{keywordsinline}[1][\keywordsname]{\if@twocolumn \else \small \quotation \fi \begin{center} \textbf{\textit{#1}: }}{\end{center}\if@twocolumn \else \small \endquotation \fi}
\makeatother

% Environment for abstract that takes new abstract name
\newenvironment{renameableabstract}[1][\abstractname]{\let\oldabstractname\abstractname \renewcommand{\abstractname}{#1} \begin{abstract}}{\end{abstract} \renewcommand{\abstractname}{\oldabstractname}}

%%%%%%%% END HEADER PARTIAL %%%%%%%%%%%%

\usepackage{tikz}
\usetikzlibrary{positioning,chains}
\usepackage{setspace}\singlespacing
\renewcommand{\textfraction}{0.00}
\renewcommand{\topfraction}{1}
\renewcommand{\bottomfraction}{1}
\renewcommand{\floatpagefraction}{1}
\setcounter{topnumber}{3}
\setcounter{bottomnumber}{3}
\setcounter{totalnumber}{4}
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage[normalem]{ulem}
\usepackage{makecell}
\usepackage{xcolor}
\ifXeTeX
  % Load polyglossia as late as possible: uses bidi with RTL langages (e.g. Hebrew, Arabic)
  \usepackage{polyglossia}
  \setmainlanguage[]{}
\else
  \usepackage[main=english]{babel}
% get rid of language-specific shorthands (see #6817):
\let\LanguageShortHands\languageshorthands
\def\languageshorthands#1{}
\fi
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi

\title{Estimating the replicability of psychology experiments after an initial failure to replicate}

%%%%%%% START AUTHOR PARTIAL %%%%%%%%%%%%%%%

%%%%% Authors, affiliations and author notes stuff %%%%%

% Macros for creating and referencing stored reference
\makeatletter
\def\MyNewLabel#1#2#3{\expandafter\gdef\csname #1@#2\endcsname{#3}}

\def\MyRef#1#2{\@ifundefined{#1@#2}{???}{\csname #1@#2\endcsname}}

\newcommand*\ifcounter[1]{%
  \ifcsname c@#1\endcsname
    \expandafter\@firstoftwo
  \else
    \expandafter\@secondoftwo
  \fi
}
\makeatother

% Create labels for Addresses if the are given by code
\MyNewLabel{ADDRTXT}{Psych}{Department of Psychology, Stanford University}
\MyNewLabel{ADDRTXT}{GSB}{Graduate School of Business, Stanford University}
\MyNewLabel{ADDRTXT}{Edu}{Graduate School of Education, Stanford University}
\MyNewLabel{ADDRTXT}{Symsys}{Symbolic Systems Program, Stanford University}
\MyNewLabel{ADDRTXT}{Philosophy}{Department of Philosophy, Stanford University}
\MyNewLabel{ADDRTXT}{CS}{Department of Computer Science, Stanford University}

% Create labels for Footnotes if they are given by code
\MyNewLabel{ANOTETXT}{corresp}{Corresponding author. Email: \href{mailto:vboyce@stanford.edu}{\nolinkurl{vboyce@stanford.edu}}}

%%% Special footnotes for addresses and author footnotes
\usepackage{bigfoot}
\DeclareNewFootnote{Addr}[arabic] % Only used for NOT authblk
\DeclareNewFootnote{ANote}[fnsymbol]

%%% Address and author notes as a function of format %%%
 % Use authblk for affiliations %%%%%%%%%%%
\usepackage{authblk}

% Always separate by commas
\renewcommand\Authsep{, }
\renewcommand\Authand{, }
\renewcommand\Authands{, }

% Counter for addresses and footnotes
\newcounter{addrcnt}

% thanks definition that doesnt produce superscript marks
\makeatletter
\newcommand*\createaddrlblbycode[1]{%
  \ifcounter{ADDRLBL@#1}
    {}
    {\refstepcounter{addrcnt}\newcounter{ADDRLBL@#1}\setcounter{ADDRLBL@#1}{\value{addrcnt}}}%
}

\newcommand*\addrlblbycode[1]{\arabic{ADDRLBL@#1}}

\newcommand*\addrbycode[1]{%
  \ifcounter{ADDR@#1}
    {}
    {\newcounter{ADDR@#1}%
     \affil[\addrlblbycode{#1}]{\MyRef{ADDRTXT}{#1}}}%
}

\newcommand*\createanotelblbycode[1]{%
  \ifcounter{ANOTELBL@#1}
    {}
    {\refstepcounter{footnoteANote}\newcounter{ANOTELBL@#1}\setcounter{ANOTELBL@#1}{\value{footnoteANote}}}%
}

\newcommand*\anotelblbycode[1]{\fnsymbol{ANOTELBL@#1}}

\newcommand*\anotebycode[1]{%
  \ifcounter{ANOTE@#1}
    {}
    {\newcounter{ANOTE@#1}%
     \footnotetextANote[\value{ANOTELBL@#1}]{\MyRef{ANOTETXT}{#1}}}%
}
\makeatother

\createaddrlblbycode{Psych}

\createanotelblbycode{corresp}

\author[%
\addrlblbycode{Psych}%
,%
$\anotelblbycode{corresp}$%
]{Veronica Boyce}

\addrbycode{Psych}

\createaddrlblbycode{Psych}

\author[%
\addrlblbycode{Psych}%
]{Ben Prystawski}

\addrbycode{Psych}

\createaddrlblbycode{Psych}

\author[%
\addrlblbycode{Psych}%
]{Adani B. Abutto}

\addrbycode{Psych}

\createaddrlblbycode{Psych}

\author[%
\addrlblbycode{Psych}%
]{Emily M. Chen}

\addrbycode{Psych}

\createaddrlblbycode{GSB}

\author[%
\addrlblbycode{GSB}%
]{Ziwen Chen}

\addrbycode{GSB}

\createaddrlblbycode{Edu}

\author[%
\addrlblbycode{Edu}%
]{Howard Chiu}

\addrbycode{Edu}

\createaddrlblbycode{Psych}

\author[%
\addrlblbycode{Psych}%
]{Irmak Ergin}

\addrbycode{Psych}

\createaddrlblbycode{Psych}

\author[%
\addrlblbycode{Psych}%
]{Anmol Gupta}

\addrbycode{Psych}

\createaddrlblbycode{Symsys}

\author[%
\addrlblbycode{Symsys}%
]{Chuqi Hu}

\addrbycode{Symsys}

\createaddrlblbycode{Philosophy}

\author[%
\addrlblbycode{Philosophy}%
]{Bendix Kemmann}

\addrbycode{Philosophy}

\createaddrlblbycode{Psych}

\author[%
\addrlblbycode{Psych}%
]{Nastasia Klevak}

\addrbycode{Psych}

\createaddrlblbycode{Psych}

\author[%
\addrlblbycode{Psych}%
]{Verity Y. Q. Lua}

\addrbycode{Psych}

\createaddrlblbycode{Edu}

\author[%
\addrlblbycode{Edu}%
]{Mateus M. Mazzaferro}

\addrbycode{Edu}

\createaddrlblbycode{Symsys}

\author[%
\addrlblbycode{Symsys}%
]{Khaing Mon}

\addrbycode{Symsys}

\createaddrlblbycode{Psych}

\author[%
\addrlblbycode{Psych}%
]{Dan Ogunbamowo}

\addrbycode{Psych}

\createaddrlblbycode{Psych}
\createaddrlblbycode{Philosophy}

\author[%
\addrlblbycode{Psych}%
,%
\addrlblbycode{Philosophy}%
]{Alexander Pereira}

\addrbycode{Psych}
\addrbycode{Philosophy}

\createaddrlblbycode{CS}

\author[%
\addrlblbycode{CS}%
]{Jordan Troutman}

\addrbycode{CS}

\createaddrlblbycode{Psych}

\author[%
\addrlblbycode{Psych}%
]{Sarah Tung}

\addrbycode{Psych}

\createaddrlblbycode{Psych}

\author[%
\addrlblbycode{Psych}%
]{Raphael Uricher}

\addrbycode{Psych}

\createaddrlblbycode{Psych}

\author[%
\addrlblbycode{Psych}%
]{Michael C. Frank}

\addrbycode{Psych}

%endif(authblk)

%%%%%%%%% END AUTHOR PARTIAL %%%%%%%%

\date{}

\begin{document}
\maketitle

%%%%%%%%%% START AFTER TITLE PARTIAL %%%%%%%%%%%%%

%%%%%%%%%% END AFTER TITLE PARTIAL %%%%%%%%%%%%%

\begin{otherlanguage}{english}

\begin{abstract}
When a replication fails, scientists have to decide whether to make a second attempt or move on.
Psychology researchers who attempt to replicate studies often face this decision, given the empirical rate of replication success in psychology, which is lower than desired.
Here, we report 17 re-replications of experiments for which an original replication had failed.
In 5/17 of these ``rescue'' projects (29\%), the ``rescue'' study mostly or fully replicated the original results, albeit with a smaller effect size; in the other 12, the second replication was also judged to have failed.
We speculate that successful rescue projects were due to larger sample sizes or methodological changes such as attention checks.
In the absence of obvious weaknesses in a failed replication study's sample or procedure, however, it may be most efficient to stop pursuing an effect after a single failed replication.

\end{abstract}

\end{otherlanguage}

\section{Introduction}\label{introduction}

Imagine you are a graduate student, and you run a replication of a study that you are interested in building upon in your research.
The replication fails.
Perhaps the interaction you hoped for is directionally correct, but the point estimate is small and the confidence interval definitely overlaps 0, with a \(p\)-value of .3.
Or perhaps the interaction is numerically in the wrong direction and the main effects look different.
Whatever the details of the replication failure, you are left with a question: Should you try again and run a re-replication, or should you give up and pick a different study to build upon?

In psychology, large scale replication projects have found that around half of studies successfully replicate.
Across 100 studies with positive results, the reproducibility project in psychology (RP:P) replicated 36\%-47\% depending on the metric for replication success (\citeproc{ref-opensciencecollaboration}{Open Science Collaboration, 2015}).
With large multi-site samples, Many Labs 1 replicated 11/13 effects (84.6\%), Many Labs 2 replicated 14/28 effects (50\%), and Many Labs 3 replicated 3/10 effects (30\%) (\citeproc{ref-ebersole2016}{Ebersole et al., 2016}; \citeproc{ref-klein2014}{Klein et al., 2014}; \citeproc{ref-klein2018}{Klein et al., 2018}).
Camerer et al. (\citeproc{ref-camerer2018}{2018}) examined 21 behavioral social science studies and successfully replicated 12-14 of them (57\%-67\%) depending on the metric used.
Boyce et al. (\citeproc{ref-boyce2023}{2023}) reported an average subjective replication score of 49\% for 176 replications primary in psychology.

Psychology is not the only discipline where many studies do not replicate.
Large scale replication projects in other disciplines have found 39/97 of studies with positive effects (40\%) replicating in cancer biology (\citeproc{ref-errington2021}{Errington et al., 2021}), 11/18 studies (61\%) replicating in economics (\citeproc{ref-camerer2016}{Camerer et al., 2016}), and 31/40 studies (78\%) replicating in experimental philosophy (\citeproc{ref-cova2021}{Cova et al., 2021}).
Across these disciplines, and especially in psychology, large-scale replications indicate a substantial chance of scientists encountering failed replications if they try to replicate published findings.

Replications can fail for many reasons, having to do with the original study or the replication.
Starting with the original study, one potential reason for replication failure is that the original result is fragile in some way.
It could be a statistically unlikely result that was achieved through chance or \(p\)-hacking, or it could be sensitive to the exact conditions and time it was run under (``hidden moderators'').
Another possibility is that the original reported effect size might be inflated due to some combination of heterogeneity, \(p\)-hacking, low power, and publication bias.
A consequence of inflated effect sizes is that replication studies might select a sample size with appropriate statistical power for the reported effect size and then have too small a sample to reliably detect the (true) smaller effect.
Replication studies might also end up underpowered due to unexpected attrition or noise in the replication sample.

Some other reasons for replication failure are primarily due to the replication study.
A replication could observe different results from the original due to methodological differences.
These differences in design could be intentional adaptations, unavoidable changes from lack of access to the original instructions or materials, or changes that were not expected to be critical.
A difference in the details of recruitment (e.g., online versus in-person) might mean that particular details of a study implementation would no longer be appropriate, or the data quality controls and attention checks might be inadequate.
If there are differences in time, place, or subject population between the two studies, corresponding changes to the materials, instructions, or procedure could be needed to provide an adaptation of the experimental paradigm to the new context.
Such adaptation creates yet more challenges in interpretation: too many changes could cause differing results, but so could not enough changes.
In sum, when replications fail, we generally do not know why they failed, although we may speculate.

For the goals of large-scale replication projects, it does not matter why any particular study failed to replicate, because the aim is to estimate the proportion of replication effects in a literature.
In contrast, however, when individual scientists attempt to replicate an effect with the goal of building on it, they do care about why an individual replication failed.
In an uncertain literature, scientists might not want to commit resources to studying extensions of an effect without first checking that they can measure that effect themselves.
For those individual scientists, it is much more important whether the replication failure is due to a fixable issue with the replication or an intrinsic feature of the original result.

Re-replication can serve as a way to test explanations for replication failure.
While it is possible to speculate after the fact about potential causes of a single replication failure, in most circumstances these causes are hard to discern (absent clear evidence of errors).
In contrast, a second replication provides a chance to test explanations by making modifications -- as well as giving another chance for researchers to measure an effect of interest.
But what are the chances that a re-replication succeeds?

Relatively few studies have estimated re-replication success.
One estimate comes from Ebersole et al. (\citeproc{ref-ebersole2020}{2020}).
After the original RP:P study reported of a replication rate around 40\% (\citeproc{ref-opensciencecollaboration}{Open Science Collaboration, 2015}), Gilbert et al. (\citeproc{ref-gilbert2016}{2016}) raised concerns that methodological differences might explain the low replication rate.
In 11 of the RP:P studies, the original authors had raised concerns about protocol fidelity prior to data collection.
Of these 11 with concerns, 10 failed to obtain significant results in the RP:P replication.
Thus, Ebersole et al. (\citeproc{ref-ebersole2020}{2020}) re-replicated 10 of these 11 in larger samples, using both the RP:P protocol and a new protocol revised under advice of the original authors or other experts.
This study thus tested whether larger sample sizes and/or ``better'' methodologies would ``rescue'' the failed RP:P replications.
The result was that 2 of the 10 revised protocols found a significant result (but not the 1/11 that originally was successful).
Even when a significant effect was recovered, the effect size was much diminished (\citeproc{ref-ebersole2020}{Ebersole et al., 2020}).
The re-replication success rate was thus 2/9 (22\%) for studies with non-significant first replications, under favorable, high-resource circumstances.

While Ebersole et al. (\citeproc{ref-ebersole2020}{2020}) looked at re-replication success rate in a high resource setting with access to large, multi-site samples and expert input, most early career scientists do not have those kinds of resources to devote to re-replication attempts.
On the other hand, early career researchers may also be prone to a different distribution of causes of initial replication failure.
Thus, it is an open question what the re-replication rate is for failed replications by early career researchers.
Further, estimating this rate could inform researchers' decisions on what to do next after failed replications.

Here, we investigate re-replication in the context of graduate student replication class projects.
Students in a graduate-level class on experimental methods in psychology were given the option to ``rescue'' an experiment that a student in a prior year had previously failed to replicate as their class project (first replications reported in \citeproc{ref-boyce2023}{Boyce et al., 2023}).
The focus of the class was best practices in experimental design; thus, students looked at both the original paper and the failed replication to examine potential issues in the replication that they could fix in their rescue project.
In the present paper, we report the results of 17 re-replication rescue projects.
We find that a minority of projects (5/17, 29\%) successfully recovered the original effect.

\section{Methods}\label{methods}

PSYCH 251 is a graduate-level experimental methods class taught by MCF.
In previous years, students have conducted replication projects (\citeproc{ref-boyce2023}{Boyce et al., 2023}; \citeproc{ref-hawkins2018}{Hawkins et al., 2018}).
In Fall 2023, students were offered the option to complete a ``rescue'' project where they re-replicated one of the unsuccessful replications from a previous year.
Students could also opt to do a normal replication instead.
If they opted for a rescue, they were given the option to participate in a collaborative meta-science project and earn authorship on the current paper based on 1) completing a rescue project, 2) reviewing another student's rescue project for reproducibility, and 3) reviewing and approving the final manuscript.
We report on the result of 17 rescue projects that opted to be part of the paper and completed data collection.

A spreadsheet of projects, individual project write-ups (both first replications and rescues), individual project data and analyses for rescue projects, and the analytic code for this paper are all available at \url{https://osf.io/cyk5w/}.

Our analysis plan was pre-registered after students had selected projects, but before final data collection on the projects.
Each project was also individually pre-registered by the student conducting it.
The overall analysis is pre-registered at \url{https://osf.io/5qz7v}, individual pre-registrations are linked from \url{https://osf.io/vkbfw}.
We note one deviation from our pre-registration here: we pre-registered visual comparisons between original, first replication, and rescue projects using prediction intervals.
Prediction intervals depend on both the original effect size and variance and the variance of the comparison (replication or rescue) study (\citeproc{ref-patil2016}{Patil et al., 2016}).
Thus we cannot show a single prediction interval for the original study, but would have to show a prediction interval between each pair of studies.
We thought this analysis would not offer additional clarity and hence we did not perform it.

\subsection{Sample}\label{sample}

The experiments that were re-replicated were chosen from studies that failed to replicate in Boyce et al. (\citeproc{ref-boyce2023}{2023}).
We created an initial list of 49 rescue-eligible studies that 1) had received a subjective replication success score of 0, .25, or .5 (on a 0--1 scale) in Boyce et al. (\citeproc{ref-boyce2023}{2023}), 2) had a Github repository available (Github repositories were used in class starting in academic year 2015-2016), and 3) where the original experiment had 200 or fewer participants (to ensure we could afford to match or increase the sample size based on the class budget).
We then contacted the replication project authors for permission to share their report and repository with a new student and include it as a supplement on a resulting paper.
This left 27 options for the students to choose from.
20 students chose to do rescue projects, and 3 students did not finish their project or did not indicate interest in being part of this paper, leaving a final sample of 17 rescue projects.

\subsection{Procedure}\label{procedure}

Students conducted their rescue projects over the course of the 10-week class.
Once they had chosen a project we gave them access to the original replicators' write-up and repository, which often included the data, experiment code, and analytic code.
In many cases, students were also given the contact information of the original replicator (a few original replicators opted not to be contacted by students).

Students were required to think of reasons the first replication might not have worked, and address them if they could.
A list of possible reasons and solutions was given to students (\url{https://osf.io/dfwk2}).
In general, we encouraged students to add manipulation checks as appropriate, and to adapt their materials to online studies, which may benefit from attention checks and/or shorter duration.
For instance, the rescue of Paxton et al. (\citeproc{ref-paxton2012}{2012}) switched from using the Cognitive Teflection Test (CRT) which many online participants are over-familiar with to using the newer CRT-2 which is less overused but attempts to measure the same construct (\citeproc{ref-thomson2016}{Thomson \& Oppenheimer, 2016}).
The rescue of Jara-Ettinger et al. (\citeproc{ref-jara-ettinger2022}{2022}) discovered that the replication had accidentally used an illustrated version of the stimuli rather than the photographic stimuli used in the original and used the photographic stimuli instead.
Tarampi et al. (\citeproc{ref-tarampi2016}{2016}) had participants do a timed navigation task where they wrote L or R to indicate which way to turn at each intersection on a paper map.
The replication ported this experiment online and had participants click a drop down menu to select left or right for each turn.
The rescue removed the unwieldy drop down menus and opted to have participants press keys on the keyboard to indicate the direction of a turn, which seemed like a more natural interface.
Once experimental designs and analytic plans were approved by class TAs (VB and BP), students pre-registered and ran their samples.

With one exception, samples were collected on Prolific (the rescue of \citeproc{ref-yeshurun2003}{Yeshurun \& Levy, 2003} ran in-person on the Stanford student subject pool).
We tried to power studies adequately (with a target of 2.5x original following \citeproc{ref-simonsohn2015}{Simonsohn, 2015}), but due to cost constraints, not all studies were powered at this level.
The rescues had on average 1.48 times the original sample post-exclusion (median: 1.07, IQR: 0.94 - 2.4, minimum: 0.48, maximum: 2.96, see Table \ref{tab:tab-size} for all sample sizes).
Across the 16 Prolific studies, we spent \$5471, for an average of \$342 per project.

\subsection{Coding of results}\label{coding-of-results}

We followed Boyce et al. (\citeproc{ref-boyce2023}{2023}) in the properties of the studies we measured and how we quantified replication success.
Each project was rated on the basis of subjective replication success (on a 0--1 scale) by both MCF and one of VB and BP.
We thought about replication in terms of general match in key study results (direction, magnitude, and significance), rather than focusing on any singular numeric result or significance cut-off.
Interrater reliability was 0.9; disagreements were minor (at no point greater than .25) and were resolved through discussion.

As a complement to the subjective rating of overall success, we statistically compared one key measure of interest for each study, following Boyce et al. (\citeproc{ref-boyce2023}{2023}).
In order to statistically compare the key measures, we needed effect sizes reported in the same way for each original study, first replication, and rescue.
When effects were not reported in consistent ways across original and replications, we recalculated effects from raw data when necessary to obtain comparable values.

We measured statistical consistency using \(p\)-original, the \(p\)-value on the null hypothesis that one study's population effect comes from the same distribution of population effects as another study or studies (\citeproc{ref-mathurNewStatisticalMetrics2020a}{Mathur \& VanderWeele, 2020}) If we assume no heterogeneity between studies, then this is the same as asking how consistent one study's estimate of the population-level effect is with another study's estimate of the population-level effect.
However, meta-analyses of closely related studies, such as those from different sites of multi-site replications, indicate that there is often heterogeneity between studies.
\(p\)-original allows for such heterogeneity, as governed by a parameter \(\tau\).
We cannot accurately estimate the level of heterogeneity for an effect meta-analytically as we have only a small number of replications per study.
Instead, we imputed a heterogeneity value of \(\tau=.21\) SMD, which is the average level of heterogeneity found by Olsson-Collentine et al. (\citeproc{ref-olsson-collentine2020}{2020}) in prior multi-site replications in psychology.

We recorded the same set of potential correlates that were used in Boyce et al. (\citeproc{ref-boyce2023}{2023}) for original, first replication, and rescue (these were already rated for original and first replication).
These potential correlates included the subfield of the study (cognitive, social, or other psychology), its publication year, experimental design features including whether it was a within- or between-subject design, whether each condition was instantiated with one vignette or multiple, how many items each participant saw, and whether there were open materials and open data.

For the original study and each replication, we recorded the number of participants post-exclusions.
For studies where some extra conditions were dropped in some replications, we counted only the participants in the key conditions all replications had for comparability.
For instance, if an original study compared between two critical conditions but also had a baseline control, we did not count the participants in the baseline condition if a replication did not include this condition.
We also recorded whether each study was conducted online using a crowd-sourced platform or not.

\section{Results}\label{results}

We first discuss the overall rate of replication in the rescue projects, followed by looking at the relative effect sizes of the rescues and correlates of rescue success.
In the last subsection we describe several interesting case studies.

\subsection{Overall replication rate}\label{overall-replication-rate}

Our primary question of interest was how many of the 17 rescue projects succeeded at replicating the results in the original study.
Across the 17 rescue projects, 5 mostly or fully replicated the original results according to the subjective replication ratings.
12 got a rating of 0, 2 got a rating of .75, and 3 got a rating of 1.
Thus, a first pass answer to the question ``how often can a failed replication be salvaged?'' is 29\% (bootstrapped 95\% CI: 6\% - 53\%) of the time.

In the original replication sample from Boyce et al. (\citeproc{ref-boyce2023}{2023}), 76 out of 176 replications (43\%) mostly or fully replicated (i.e.~received a subjective replication score of .75 or 1).
Note that Boyce et al. (\citeproc{ref-boyce2023}{2023}) report the average replication score as a percent success (49\%), but given that we considered studies with a subjective score of .5 as eligible to be rescued, we recomputed the success rate where scores of 0, .25, and .5 are considered failures and .75 and 1 successes.
If the re-replication rate in our sample is representative of the re-replication rate for the initially non-replicating studies, then the combined chance of mostly or fully replicating in a first replication or one follow-up replication is 60\%.

\subsection{Effect size comparison}\label{effect-size-comparison}

\begin{figure}
\includegraphics[width=1\linewidth]{manuscript_files/figure-latex/smd-1} \caption{Standardized effect sizes of original studies, first replications, rescues, and additional replications if available. Due to the large effect size of a couple studies, large effect studies are shown in a separate panel. In a few cases, the first replication's key effect was in the same direction as the original with a 95\% CI that did not overlap 0; however, in these cases the larger pattern of results was not fully consistent between original and first replication.  }\label{fig:smd}
\end{figure}

As a complement to subjective replication ratings, we also statistically compared the effect sizes of the rescue, first replication, and original study on one preregistered key measure per study (again following \citeproc{ref-boyce2023}{Boyce et al., 2023}).
Though we did not conduct a systematic review of the literature to identify all possible replications, we also consider the effect sizes obtained in additional replications when we were aware of them (either from other class projects, or external replications in the literature).

We standardized all effect sizes into standardized mean difference (SMD) units.
One potential issue with comparisons using SMD is that noisier measures will have smaller standardized effect sizes even if the effect on the original scale is the same.
In general, the replication and rescue effect sizes were smaller than the original effect sizes, and in a few cases the effects were in the opposite direction (Figure \ref{fig:smd}).

\begin{table}

\caption{\label{tab:tab-porig}$P$-original values between different sets of experiments. The primary analysis is between the original result and the meta-analytic aggregation of all replications. All $p$-original values assume an imputed heterogeneity value of $\tau$=.21.}
\centering
\begin{tabular}[t]{lrrrrr}
\toprule
\multicolumn{1}{c}{ } & \multicolumn{5}{c}{p-original comparing between} \\
\cmidrule(l{3pt}r{3pt}){2-6}
\multicolumn{1}{c}{ } & \multicolumn{4}{c}{Original and} & \multicolumn{1}{c}{Rescue and} \\
\cmidrule(l{3pt}r{3pt}){2-5} \cmidrule(l{3pt}r{3pt}){6-6}
Paper & All reps & 1st Rep and Rescue & Rescue & Non-rescue & Other reps\\
\midrule
Birch \& Bloom 2007 & 0.192 & 0.189 & 0.194 & 0.191 & 0.989\\
Child et al. 2018 & 0.669 & 0.669 & 0.641 & 0.858 & 0.778\\
Chou et al. 2016 & 0.055 & 0.055 & 0.101 & 0.005 & 0.231\\
Craig \& Richeson 2014 & 0.145 & 0.145 & 0.001 & 0.302 & 0.020\\
Gong et al. 2019 & 0.262 & 0.262 & 0.057 & 0.511 & 0.228\\
Haimovitz \& Dweck 2016 & 0.068 & 0.018 & 0.018 & 0.180 & 0.867\\
Hopkins et al. 2016 & 0.290 & 0.290 & 0.654 & 0.004 & 0.015\\
Jara-Ettinger et al. 2022 & 0.014 & 0.014 & 0.000 & 0.006 & 0.000\\
Krauss \& Wang 2003 & 0.271 & 0.271 & 0.519 & 0.139 & 0.311\\
Ngo et al. 2019 & 0.106 & 0.000 & 0.000 & 0.385 & 0.257\\
Paxton et al. 2012 & 0.011 & 0.011 & 0.005 & 0.023 & 0.649\\
Payne et al. 2008 & 0.023 & 0.071 & 0.031 & 0.079 & 0.895\\
Porter et al. 2016 & 0.370 & 0.370 & 0.905 & 0.002 & 0.003\\
Schechtman et al. 2010 & 0.712 & 0.712 & 0.654 & 0.770 & 0.877\\
Tarampi et al. 2016 & 0.000 & 0.000 & 0.000 & 0.000 & 0.145\\
Todd et al. 2016 & 0.062 & 0.100 & 0.124 & 0.058 & 0.778\\
Yeshurun \& Levy 2003 & 0.614 & 0.007 & 0.017 & 0.943 & 0.474\\
\bottomrule
\end{tabular}
\end{table}

Scientists' intuitions about whether a replication is successful and whether an effect provides support for a hypothesis (including heuristic cutoffs like p\textless.05) do not always align with measures of statistical consistency (\citeproc{ref-patil2016}{Patil et al., 2016}).
For instance, two studies may both find that condition 1 results in a significantly higher outcome measure than condition 2, but the effect magnitudes may be sufficiently different that they are statistically unlikely to have come from the same population.
On the other hand, one study may find a statistically significant, but imprecisely estimated effect in a small sample, and a second study may find a near-zero (null) effect, but the effect estimates from the two studies may be statistically compatible, despite one supporting a hypothesized difference and the other not.

As our primary comparison, we compare the effect size of the original study to the meta-analytic effect of the totality of the replications (first replication, rescue, and additional if found).
The value of \(p\)-original represents how likely an effect size equal to or more extreme than the original effect size is to occur if it comes from a distribution of population effect sizes defined by the mean and standard error of the replications (combined meta-analytically) with a between-population standard deviation of \(\tau=.21\) (imputed from \citeproc{ref-olsson-collentine2020}{Olsson-Collentine et al., 2020}).
That is, \(p\)-original is a measure of the statistical consistency of the original result with the totality of the replications, assuming a given level of heterogeneity of effects between studies.
Smaller \(p\)-original values indicate more inconsistency.

The median value of \(p\)-original between an original study and its replications was 0.15 {[}IQR: 0.05 - 0.29{]}.
24\% of the \(p\)-original values were less than .05, indicating by conventional thresholds a rejection of the null hypothesis that the original comes from the same distribution of population effects as the replications.
Individual \(p\)-original values for each study are shown in Table \ref{tab:tab-porig}.

As secondary measures, we calculated the \(p\)-original values between a) the original and just the first replication and rescue, b) the original and the rescue, c) the original and non-rescue replications, and d) the rescue and other replications.
For a) the original versus the first replication and the rescue, the median value of \(p\)-original was 0.1 {[}IQR: 0.01 - 0.27{]}, and 35\% of the \(p\)-original values were less than .05.
For b) the original versus the rescue, the median value of \(p\)-original was 0.06 {[}IQR: 0.01 - 0.52{]}, and 47\% of the \(p\)-original values were less than .05.
For c) the original versus all the non-rescue replications, the median value of \(p\)-original was 0.14 {[}IQR: 0.01 - 0.38{]}, and 35\% of the \(p\)-original values were less than .05.
For d) the rescue versus the other replications, the median value of \(p\)-original was 0.31 {[}IQR: 0.14 - 0.78{]}, and 24\% of the \(p\)-original values were less than .05.

Overall, allowing for a heterogeneity level of \(\tau\)=.21 SMD, a number of original effects are not statistically consistent with rescue and replication effects.
The pattern of inconsistency does not align with which studies were rated as having replicated.
In all cases, the point estimate of the re-replication is smaller than, or in the opposite direction of, the original effect on the key measure of interest.

\subsection{Correlates of rescue success}\label{correlates-of-rescue-success}

\begin{table}

\caption{\label{tab:cor-table}Correlations between an individual predictor and the subjective replication score of the rescue project. The first set of predictors were pre-registered based on the correlates used in Boyce et al. (2023). Original authors at Stanford refers to at the time of the first replication as this may mean the first replication was not independent. For details about how the predictors were coded, see the Methods section of Boyce et al. (2023). The last three predictors were added post-hoc.}
\centering
\begin{tabular}[t]{rcc}
\toprule
Predictors & r & p\\
\midrule
Social & 0.133 & 0.612\\
Other psych & -0.295 & 0.250\\
Within subjects & 0.210 & 0.418\\
Single vignette & -0.030 & 0.910\\
Switch to online & 0.175 & 0.501\\
Open data & 0.231 & 0.373\\
Open materials & 0.471 & 0.057\\
Original authors at Stanford & -0.233 & 0.369\\
Log number of trials & 0.005 & 0.985\\
Log original sample size & 0.027 & 0.919\\
Log rescue/original sample size & 0.024 & 0.927\\
\midrule\\
Log replication sample size & -0.258 & 0.317\\
Log replication/original sample size & -0.487 & 0.048\\
Log rescue/replication sample size & 0.490 & 0.046\\
\bottomrule
\end{tabular}
\end{table}

Are there signals in the features of original or replication studies that predict whether a re-replication will succeed?
To address this question, we report correlations between the set of predictor variables used in Boyce et al. (\citeproc{ref-boyce2023}{2023}) and the subjective replication scores of the rescues.
We also added some (non-preregistered) predictors related to the sample size of the first replication, after seeing the successful re-replications of Ngo et al. (\citeproc{ref-ngo2019}{2019}) and Krauss \& Wang (\citeproc{ref-krauss2003}{2003}), both of which had small replication samples and larger rescue samples.

All of the correlations are presented in Table \ref{tab:cor-table}.
The number of rescues is small, and many of these predictors are correlated, so we caution against over interpretation.

The strongest correlates of rescue success were open materials, a small sample size on the first replication, a small sample size on the first replication relative to the original sample size, and a large rescue sample size relative to the first replication.
None of the pre-registered correlates meet the conventional significance threshold; the two correlates based on ratios that reflect a relatively smaller replication sample size are marginally significant.

Small replication samples relative to original and rescue could be due to both a) powering a replication according to a reported large effect size or b) difficulties with recruitment or high exclusion rates leading to a smaller than intended sample.
Since relative sizes of the studies may play a role in replication success and how probative replications are, we show the sample sizes in Table \ref{tab:tab-size}.

An additional factor that influences the interpretation of a replication is how close the replication's methods were to the original.
In the rescue projects, we aimed to have methods be as close as was feasible or appropriate.
However, rescue projects varied in how close the re-replications actually were, often due to limitations in the availability of original stimuli and original instructions, in addition to the use of primarily online subject pools.
Table \ref{tab:tab-size} shows the closeness of each first replication and rescue according to the classification scheme from LeBel et al. (\citeproc{ref-lebel2018}{2018}).

\begin{table}

\caption{\label{tab:tab-size}Comparison of sample size for original, replication, and rescue samples and measures of closeness for replication and rescue samples.}
\centering
\begin{tabular}[t]{lllllll}
\toprule
\multicolumn{1}{c}{Paper} & \multicolumn{1}{c}{Score} & \multicolumn{3}{c}{N} & \multicolumn{2}{c}{closeness} \\
\cmidrule(l{3pt}r{3pt}){1-1} \cmidrule(l{3pt}r{3pt}){2-2} \cmidrule(l{3pt}r{3pt}){3-5} \cmidrule(l{3pt}r{3pt}){6-7}
 &  & Original & Replication & Rescue & Replication & Rescue\\
\midrule
Krauss \& Wang 2003 & 1.00 & 101 & 19 & 75 & close & very close\\
Ngo et al. 2019 & 1.00 & 31 & 12 & 77 & very close & very close\\
Todd et al. 2016 & 1.00 & 63 & 26 & 55 & very close & very close\\
Jara-Ettinger et al. 2022 & 0.75 & 144 & 147 & 426 & exact & exact\\
Porter et al. 2016 & 0.75 & 145 & 168 & 136 & close & close\\
Birch \& Bloom 2007 & 0.00 & 103 & 73 & 247 & very close & very close\\
Child et al. 2018 & 0.00 & 35 & 40 & 98 & very close & very close\\
Chou et al. 2016 & 0.00 & 100 & 158 & 252 & very close & very close\\
Craig \& Richeson 2014 & 0.00 & 121 & 76 & 127 & exact & exact\\
Gong et al. 2019 & 0.00 & 155 & 90 & 137 & far & far\\
Haimovitz \& Dweck 2016 & 0.00 & 132 & 97 & 141 & exact & exact\\
Hopkins et al. 2016 & 0.00 & 147 & 93 & 161 & very close & very close\\
Paxton et al. 2012 & 0.00 & 92 & 82 & 160 & close & close\\
Payne et al. 2008 & 0.00 & 48 & 23 & 23 & far & very close\\
Schechtman et al. 2010 & 0.00 & 22 & 20 & 21 & close & close\\
Tarampi et al. 2016 & 0.00 & 139 & 212 & 166 & close & very close\\
Yeshurun \& Levy 2003 & 0.00 & 18 & 10 & 18 & close & very close\\
\bottomrule
\end{tabular}
\end{table}

Overall, we do not have a clear picture of why certain studies replicated in the rescue sample and others did not, other than a few cases where fixing sample size issues may have helped.

\subsection{Case studies}\label{case-studies}

Given the mix of successful and unsuccessful rescue projects, we discuss in depth a few projects where we have speculations about why they turned out the way they did.
Brief descriptions of the projects not covered in this section be found in the Appendix.

The rescue of Krauss \& Wang (\citeproc{ref-krauss2003}{2003}) was successful despite an unsuccessful replication.
This study looked at the influence of guided thinking on whether or not people gave correct justifications (drawn or written) for their answer on the Monty Hall problem.
The original paper reported correct justification from 2/67 (3\%) in the control condition and 13/34 (38\%) in the guided thinking condition.
The first replication struggled to recruit participants who were naive to the problem (an exclusion criterion), and many participants gave very short text responses in the provided text box (only textual responses were allowed).
The replication found 0/8 correct justifications in the control and 0/11 in the guided thinking condition.
While we cannot know for sure what caused the non-replication, there were clear problems observable from the small final sample and low-quality responses.
The rescue targeted these issues by adding a pre-screening that ensured participants were not familiar with the Monty Hall problem, changed the content items for the problem and changed its name (to reduce googling for answers), and had participants upload drawings for their justifications.
Collectively, we believe these changes brought the rescue closer to the intent of the original.
The rescue had 1/40 (2\%) correct justifications in the control condition and 6/35 (17\%) in the guided thinking condition.
This effect was significant, though smaller than the effect in the original.

Ngo et al. (\citeproc{ref-ngo2019}{2019}) was a second successful rescue.
The original study found a large effect; hence the first replication, powering for 80\% power on the reported effect, recruited a small sample of 12 people.
This small study failed to find the original effect.
The rescue, powered using 2.5x the original sample (as recommended by \citeproc{ref-simonsohn2015}{Simonsohn, 2015}), recovered a clear effect (albeit a much smaller one).
An additional replication from the literature, Ngo \& Newcombe (\citeproc{ref-ngo2021}{2021}) successfully replicated Ngo et al. (\citeproc{ref-ngo2019}{2019}).
There are reasons to think that some effect sizes in the literature may be inflated (\citeproc{ref-camerer2018}{Camerer et al., 2018}; \citeproc{ref-opensciencecollaboration}{Open Science Collaboration, 2015}), and it is also possible that changes to experiments or switches to online could result in noisier samples and thus smaller effect sizes.
Therefore, replications with smaller samples than the original (even if powered to the original effect size), may not be very diagnostic, and could potentially benefit from a re-replication.

Not all rescues of small replications succeeded, however.
Payne et al. (\citeproc{ref-payne2008}{2008}) was a study of the effects of sleep on memory consolidation.
They showed participants a number of images and then hours later (after either sleep or no sleep) measured their recall for parts of the images.
The first replication struggled to recruit participants to complete a followup session after sleep and only reported a sample size of 23 (the original had 48).
The rescue attempted to recruit a larger sample (target 88), but also experienced difficulties getting participants to complete the second part of the experiment 12 hours after the first, managing also only to recruit 23 people.
The lesson here may be that sleep research is difficult to conduct online.
However, an online replication by Denis et al. (\citeproc{ref-denis2022}{2022}) reports qualitatively similar (but quantitatively smaller) results to Payne et al. (\citeproc{ref-payne2008}{2008}) on related but not identical measures.
Denis et al. (\citeproc{ref-denis2022}{2022}) which has an overlapping author team to Payne et al. (\citeproc{ref-payne2008}{2008}) is included here as an additional replication.

Child et al. (\citeproc{ref-child2018}{2018}) studied reading times for passages of text with different emotional valences written from either a third-person or second-person perspective.
They found a significant interaction between perspective and valence: participants read positively-valenced passages faster than negatively-valenced passages, but only when they were written from a second-person perspective.
The first replication used a similar sample size to the original study (40) and found an effect that trended in the same direction, but was substantially smaller.
The rescuer identified several possible reasons for this failure, foremost among them that the replication was conducted online while the original was conducted in person.
It is reasonable to expect online studies of reading time to be noisier than in-person studies because the environments participants completed the study in varied much more online.
The rescue attempt was still online, but used a much larger sample size to account for noisier data.
Still, the rescue found a non-significant effect that trended in the opposite direction from the original and first replication.
Even though the first replication trended in the same direction and there was an identifiable reason for the smaller effect size, increasing sample size did not rescue the effect.

\section{Discussion}\label{discussion}

Faced with a failed replication, should investigators devote more time to continued replications?
There are limited data that inform this decision.
To address this gap, we presented the results of 17 new replications that attempted to ``rescue'' previous failed replications by identifying and ameliorating possible causes of non-replication.
5 of these rescue projects (29\%) mostly or fully replicated the original results.

In some cases, increasing sample size and fixing internal validity issues in the replication seems to have led to a successful rescue (although we cannot establish causality even in these cases).
However, there were other cases where the first replications had issues with a small sample or deviations in the implementation, and the rescue addressed these issues but still failed to replicate the original results.
We cannot predict what replication failures are likely to resolve given another, more thoughtful try, beyond the suggestion to review studies for best practices in experimental design and sampling (e.g., \citeproc{ref-experimentology2024}{Frank et al., 2024}).

The rescues all showed smaller effect sizes than their original studies, regardless of whether the pattern of effects replicated.
A large minority of replications had effect sizes that were statistically inconsistent with the original effect, even accounting for expected levels of heterogeneity between studies.

\subsection{Limitations}\label{limitations}

The reported rescue projects are a small sample of replications, leading to highly uncertain estimates.
Additionally, they were chosen non-randomly, as they were doubly selected for based on student interest -- once for the original replication and again for the rescue.
However, this selection bias is likely to correlate with how graduate students and other early career researchers choose what topics to work on and what studies to build on.
Nevertheless, our estimate is still broadly consistent with that of ManyLabs 5 (29\% vs.~22\%, \citeproc{ref-ebersole2020}{Ebersole et al., 2020}).

In cases where re-replications failed, we do not believe any conclusions are licensed about the status of the original results.
Students conducting rescue projects put substantial effort into trying to set up rescues that had a good chance of success, but projects were constrained by budget limitations, a short timeline, and the constraint that most data collection needed to occur online.
These limitations are representative of the sort of resource limitations often faced by early-career researchers.
That said, it is possible that different results might be obtained in better-resourced settings, by scientists with more expertise and more time.

Due to the limited number of replications that are conducted and systematically reported, and the even smaller number of re-replications reported, there is a lot of uncertainty in how much replicability varies across features of the original experiment and replications.

\subsection{Conclusion}\label{conclusion}

Overall, the diminished and inconsistent effects we found in the rescues suggest that even if a re-replication ``works'', it may be difficult to build upon as follow-up studies will need large samples to detect small effects.

Replications are done for many reasons, and researchers often have some prior beliefs about whether a replication will succeed.
These beliefs may influence how a researcher interprets a failed replication and thus whether they think it's worth trying to rescue.
For instance, a researcher who has high credence in the main result is more likely to attribute failure to specific details in the replication and thus want to rescue by tweaking these details.
On the other side, a researcher who is dubious of the methods, results, or statistical approaches, or who has experienced failures to replicate and extend the work, may be quicker to interpret a failure as a more definitive negative result.
Interpretations may also depend on the perceived strength of the replication and what effect size is cared about.

While we focus here on a narrow type of replication and rescue, that done by an early career researcher with the goal of establishing whether this is a result \emph{they} can build on, it exists as part of a wider ecosystem of replications that are done for different reasons with different properties.

We opened with a question about what an early-career psychology researcher should do given a failed replication: should they try again or give up and move on?
In our sample, the odds of a re-replication working are low (consistent with \citeproc{ref-ebersole2020}{Ebersole et al., 2020}).
Especially if there is not a clear, identifiable candidate cause for replication failure, it may be more efficient to select another result to build on.

\section*{Acknowledgements}\label{acknowledgements}
\addcontentsline{toc}{section}{Acknowledgements}

We thank the students from previous years of PSYCH 251 who graciously agreed to let us re-replicate their projects and shared their work with us.
We thank the other members of the PSYCH 251 teaching team and students for feedback on projects.
Data collection was supported by funding from the Stanford Departments of Psychology and Philosophy, Graduate School of Education, and the Symbolic Systems program.

\section*{Author Contributions}\label{author-contributions}
\addcontentsline{toc}{section}{Author Contributions}

VB and MCF conceptualized the study.
BP contributed project administration, VB contributed formal analysis, and MCF contributed supervision.

Authors other than VB, BP, and MCF each designed, conducted, analyzed, and wrote up one of the rescue projects -- these authors contributed to investigation, formal analysis, and visualization.

VB wrote the first draft, BP and MCF contributed editing, and all authors reviewed the final manuscript.

\section*{References}\label{references}
\addcontentsline{toc}{section}{References}

\phantomsection\label{refs}
\begin{CSLReferences}{1}{0}
\bibitem[\citeproctext]{ref-birch2007}
Birch, S., \& Bloom, P. (2007). \emph{The {Curse} of {Knowledge} in {Reasoning About False Beliefs}}. \url{https://journals.sagepub.com/doi/abs/10.1111/j.1467-9280.2007.01909.x}

\bibitem[\citeproctext]{ref-boyce2023}
Boyce, V., Mathur, M., \& Frank, M. C. (2023). \emph{Eleven years of student replication projects provide evidence on the correlates of replicability in psychology}. \url{https://doi.org/10.1098/rsos.231240}

\bibitem[\citeproctext]{ref-camerer2016}
Camerer, C. F., Dreber, A., Forsell, E., Ho, T.-H., Huber, J., Johannesson, M., Kirchler, M., Almenberg, J., Altmejd, A., Chan, T., Heikensten, E., Holzmeister, F., Imai, T., Isaksson, S., Nave, G., Pfeiffer, T., Razen, M., \& Wu, H. (2016). Evaluating replicability of laboratory experiments in economics. \emph{Science}, \emph{351}(6280), 1433--1436. \url{https://doi.org/10.1126/science.aaf0918}

\bibitem[\citeproctext]{ref-camerer2018}
Camerer, C. F., Dreber, A., Holzmeister, F., Ho, T.-H., Huber, J., Johannesson, M., Kirchler, M., Nave, G., Nosek, B. A., Pfeiffer, T., Altmejd, A., Buttrick, N., Chan, T., Chen, Y., Forsell, E., Gampa, A., Heikensten, E., Hummer, L., Imai, T., \ldots{} Wu, H. (2018). Evaluating the replicability of social science experiments in {Nature} and {Science} between 2010 and 2015. \emph{Nature Human Behaviour}, \emph{2}(9), 637--644. \url{https://doi.org/10.1038/s41562-018-0399-z}

\bibitem[\citeproctext]{ref-chica2009}
Chica, A. B., \& Christie, J. (2009). Spatial attention does improve temporal discrimination. \emph{Attention, Perception, \& Psychophysics}, \emph{71}(2), 273--280.

\bibitem[\citeproctext]{ref-child2018}
Child, S., Oakhill, J., \& Garnham, A. (2018). You're the emotional one: The role of perspective for emotion processing in reading comprehension. \emph{Language, Cognition and Neuroscience}, \emph{33}(7), 878--889. \url{https://doi.org/10.1080/23273798.2018.1431397}

\bibitem[\citeproctext]{ref-chou2016}
Chou, E., Parmar, B., \& Galinsky, A. (2016). \emph{Economic {Insecurity Increases Physical Pain}}. \url{https://journals.sagepub.com/doi/full/10.1177/0956797615625640}

\bibitem[\citeproctext]{ref-cova2021}
Cova, F., Strickland, B., Abatista, A., Allard, A., Andow, J., Attie, M., Beebe, J., Berniūnas, R., Boudesseul, J., Colombo, M., Cushman, F., Diaz, R., N'Djaye Nikolai Van Dongen, N., Dranseika, V., Earp, B. D., Torres, A. G., Hannikainen, I., Hernández-Conde, J. V., Hu, W., \ldots{} Zhou, X. (2021). Estimating the {Reproducibility} of {Experimental Philosophy}. \emph{Review of Philosophy and Psychology}, \emph{12}(1), 9--44. \url{https://doi.org/10.1007/s13164-018-0400-9}

\bibitem[\citeproctext]{ref-craig2014}
Craig, M. A., \& Richeson, J. A. (2014). On the {Precipice} of a {``{Majority-Minority}''} {America}: {Perceived Status Threat From} the {Racial Demographic Shift Affects White Americans}' {Political Ideology}. \emph{Psychological Science}, \emph{25}(6), 1189--1197. \url{https://doi.org/10.1177/0956797614527113}

\bibitem[\citeproctext]{ref-denis2022}
Denis, D., Sanders, K. E. G., Kensinger, E. A., \& Payne, J. D. (2022). Sleep preferentially consolidates negative aspects of human memory: {Well-powered} evidence from two large online experiments. \emph{Proceedings of the National Academy of Sciences}, \emph{119}(44), e2202657119. \url{https://doi.org/10.1073/pnas.2202657119}

\bibitem[\citeproctext]{ref-ebersole2016}
Ebersole, C. R., Atherton, O. E., Belanger, A. L., Skulborstad, H. M., Allen, J. M., Banks, J. B., Baranski, E., Bernstein, M. J., Bonfiglio, D. B. V., Boucher, L., Brown, E. R., Budiman, N. I., Cairo, A. H., Capaldi, C. A., Chartier, C. R., Chung, J. M., Cicero, D. C., Coleman, J. A., Conway, J. G., \ldots{} Nosek, B. A. (2016). Many {Labs} 3: {Evaluating} participant pool quality across the academic semester via replication. \emph{Journal of Experimental Social Psychology}, \emph{67}, 68--82. \url{https://doi.org/10.1016/j.jesp.2015.10.012}

\bibitem[\citeproctext]{ref-ebersole2020}
Ebersole, C. R., Mathur, M. B., Baranski, E., Bart-Plange, D.-J., Buttrick, N. R., Chartier, C. R., Corker, K. S., Corley, M., Hartshorne, J. K., IJzerman, H., Lazarević, L. B., Rabagliati, H., Ropovik, I., Aczel, B., Aeschbach, L. F., Andrighetto, L., Arnal, J. D., Arrow, H., Babincak, P., \ldots{} Nosek, B. A. (2020). Many {Labs} 5: {Testing Pre-Data-Collection Peer Review} as an {Intervention} to {Increase Replicability}. \emph{Advances in Methods and Practices in Psychological Science}, \emph{3}(3), 309--331. \url{https://doi.org/10.1177/2515245920958687}

\bibitem[\citeproctext]{ref-errington2021}
Errington, T. M., Mathur, M., Soderberg, C. K., Denis, A., Perfito, N., Iorns, E., \& Nosek, B. A. (2021). Investigating the replicability of preclinical cancer biology. \emph{eLife}, \emph{10}, e71601. \url{https://doi.org/10.7554/eLife.71601}

\bibitem[\citeproctext]{ref-experimentology2024}
Frank, M. C., Braginsky, M., Cachia, J., Coles, N., Hardwicke, T. E., Hawkins, R. D., Mathur, M. B., \& Williams, R. (2024). \emph{Experimentology: {An} {Open} {Science} {Approach} to {Experimental} {Psychology} {Methods}}. MIT Press. \url{https://doi.org/10.7551/mitpress/14810.001.0001}

\bibitem[\citeproctext]{ref-gilbert2016}
Gilbert, D. T., King, G., Pettigrew, S., \& Wilson, T. D. (2016). Comment on {``{Estimating} the reproducibility of psychological science.''} \emph{Science}, \emph{351}(6277), 1037--1037. \url{https://doi.org/10.1126/science.aad7243}

\bibitem[\citeproctext]{ref-gong2019}
Gong, X., Zhang, F., \& Fung, H. H. (2019). Are {Older Adults More Willing} to {Donate}? {The Roles} of {Donation Form} and {Social Relationship}. \emph{The Journals of Gerontology: Series B}, \emph{74}(3), 440--448. \url{https://doi.org/10.1093/geronb/gbx099}

\bibitem[\citeproctext]{ref-haimovitz2016}
Haimovitz, K., \& Dweck, C. S. (2016). What predicts children's fixed and growth intelligence mind-sets? {Not} their parents' views of intelligence but their parents' views of failure. \emph{Psychological Science}, \emph{27}(6), 859--869. \url{https://doi.org/10.1177/0956797616639727}

\bibitem[\citeproctext]{ref-hawkins2018}
Hawkins, R. X. D., Smith, E. N., Au, C., Arias, J. M., Hermann, E., Keil, M., Lampinen, A., Raposo, S., Salehi, S., Salloum, J., Tan, J., \& Frank, M. C. (2018). \emph{Improving the {Replicability} of {Psychological Science Through Pedagogy}}. 41.

\bibitem[\citeproctext]{ref-hopkins2016}
Hopkins, E. J., Weisberg, D. S., \& Taylor, J. C. V. (2016). The seductive allure is a reductive allure: {People} prefer scientific explanations that contain logically irrelevant reductive information. \emph{Cognition}, \emph{155}, 67--76. \url{https://doi.org/10.1016/j.cognition.2016.06.011}

\bibitem[\citeproctext]{ref-jara-ettinger2022}
Jara-Ettinger, J., Levy, R., Sakel, J., Huanca, T., \& Gibson, E. (2022). The origins of the shape bias: {Evidence} from the {Tsimane}'. \emph{Journal of Experimental Psychology: General}, \emph{151}(10), 2437--2447. \url{https://doi.org/10.1037/xge0001195}

\bibitem[\citeproctext]{ref-klein2014}
Klein, R. A., Ratliff, K. A., Vianello, M., Adams, R. B., Bahník, Š., Bernstein, M. J., Bocian, K., Brandt, M. J., Brooks, B., Brumbaugh, C. C., Cemalcilar, Z., Chandler, J., Cheong, W., Davis, W. E., Devos, T., Eisner, M., Frankowska, N., Furrow, D., Galliani, E. M., \ldots{} Nosek, B. A. (2014). Investigating {Variation} in {Replicability}: {A} {``{Many Labs}''} {Replication Project}. \emph{Social Psychology}, \emph{45}(3), 142--152. \url{https://doi.org/10.1027/1864-9335/a000178}

\bibitem[\citeproctext]{ref-klein2018}
Klein, R. A., Vianello, M., Hasselman, F., Adams, B. G., Adams, R. B., Alper, S., Aveyard, M., Axt, J. R., Babalola, M. T., Bahník, Š., Batra, R., Berkics, M., Bernstein, M. J., Berry, D. R., Bialobrzeska, O., Binan, E. D., Bocian, K., Brandt, M. J., Busching, R., \ldots{} Nosek, B. A. (2018). Many {Labs} 2: {Investigating Variation} in {Replicability Across Samples} and {Settings}. \emph{Advances in Methods and Practices in Psychological Science}, \emph{1}(4), 443--490. \url{https://doi.org/10.1177/2515245918810225}

\bibitem[\citeproctext]{ref-krauss2003}
Krauss, S., \& Wang, X. T. (2003). The psychology of the {Monty Hall} problem: {Discovering} psychological mechanisms for solving a tenacious brain teaser. \emph{Journal of Experimental Psychology: General}, \emph{132}(1), 3--22. \url{https://doi.org/10.1037/0096-3445.132.1.3}

\bibitem[\citeproctext]{ref-lebel2018}
LeBel, E. P., McCarthy, R. J., Earp, B. D., Elson, M., \& Vanpaemel, W. (2018). \emph{A {Unified Framework} to {Quantify} the {Credibility} of {Scientific Findings}}.

\bibitem[\citeproctext]{ref-mathurNewStatisticalMetrics2020a}
Mathur, M. B., \& VanderWeele, T. J. (2020). New statistical metrics for multisite replication projects. \emph{Journal of the Royal Statistical Society: Series A (Statistics in Society)}, \emph{183}(3), 1145--1166. \url{https://doi.org/10.1111/rssa.12572}

\bibitem[\citeproctext]{ref-ngo2019}
Ngo, C. T., Horner, A. J., Newcombe, N. S., \& Olson, I. R. (2019). Development of {Holistic Episodic Recollection}. \emph{Psychological Science}, \emph{30}(12), 1696--1706. \url{https://doi.org/10.1177/0956797619879441}

\bibitem[\citeproctext]{ref-ngo2021}
Ngo, C. T., \& Newcombe, N. S. (2021). Relational binding and holistic retrieval in ageing. \emph{Memory}, \emph{29}(9), 1197--1205. \url{https://doi.org/10.1080/09658211.2021.1974047}

\bibitem[\citeproctext]{ref-olsson-collentine2020}
Olsson-Collentine, A., Wicherts, J. M., \& Van Assen, M. A. L. M. (2020). Heterogeneity in direct replications in psychology and its association with effect size. \emph{Psychological Bulletin}, \emph{146}(10), 922--940. \url{https://doi.org/10.1037/bul0000294}

\bibitem[\citeproctext]{ref-opensciencecollaboration}
Open Science Collaboration. (2015). Estimating the reproducibility of psychological science. \emph{Science}. \url{https://www.science.org/doi/full/10.1126/science.aac4716?casa_token=IJ35TwwlcjsAAAAA\%3AqiP68QbVAHleIg9zD3WugKWuV6Oa5rswS0VQnDsCq5I14ME4WIQabNGVD_T6SBSuAt6voVHNnWc0sw}

\bibitem[\citeproctext]{ref-patil2016}
Patil, P., Peng, R. D., \& Leek, J. T. (2016). What {Should Researchers Expect When They Replicate Studies}? {A Statistical View} of {Replicability} in {Psychological Science}. \emph{Perspectives on Psychological Science: A Journal of the Association for Psychological Science}, \emph{11}(4), 539--544. \url{https://doi.org/10.1177/1745691616646366}

\bibitem[\citeproctext]{ref-paxton2012}
Paxton, J. M., Ungar, L., \& Greene, J. D. (2012). Reflection and {Reasoning} in {Moral Judgment}. \emph{Cognitive Science}, \emph{36}(1), 163--177. \url{https://doi.org/10.1111/j.1551-6709.2011.01210.x}

\bibitem[\citeproctext]{ref-payne2008}
Payne, J. D., Stickgold, R., Swanberg, K., \& Kensinger, E. A. (2008). Sleep {Preferentially Enhances Memory} for {Emotional Components} of {Scenes}. \emph{Psychological Science}, \emph{19}(8), 781--788. \url{https://doi.org/10.1111/j.1467-9280.2008.02157.x}

\bibitem[\citeproctext]{ref-porter2016}
Porter, S. C., Rheinschmidt-Same, M., \& Richeson, J. A. (2016). Inferring {Identity From Language}: {Linguistic Intergroup Bias Informs Social Categorization}. \emph{Psychological Science}, \emph{27}(1), 94--102. \url{https://doi.org/10.1177/0956797615612202}

\bibitem[\citeproctext]{ref-schechtman2010}
Schechtman, E., Laufer, O., \& Paz, R. (2010). Negative {Valence Widens Generalization} of {Learning}. \emph{The Journal of Neuroscience}, \emph{30}(31), 10460--10464. \url{https://doi.org/10.1523/JNEUROSCI.2377-10.2010}

\bibitem[\citeproctext]{ref-simonsohn2015}
Simonsohn, U. (2015). Small {Telescopes}: {Detectability} and the {Evaluation} of {Replication Results}. \emph{Psychological Science}, \emph{26}(5), 559--569. \url{https://doi.org/10.1177/0956797614567341}

\bibitem[\citeproctext]{ref-tarampi2016}
Tarampi, M., Heydari, N., \& Hegarty, M. (2016). \emph{A {Tale} of {Two Types} of {Perspective Taking}: {Sex Differences} in {Spatial Ability}}. \url{https://journals.sagepub.com/doi/full/10.1177/0956797616667459}

\bibitem[\citeproctext]{ref-thomson2016}
Thomson, K. S., \& Oppenheimer, D. M. (2016). Investigating an alternate form of the cognitive reflection test. \emph{Judgment and Decision Making}, \emph{11}(1), 99--113. \url{https://doi.org/10.1017/S1930297500007622}

\bibitem[\citeproctext]{ref-todd2016}
Todd, A., Thiem, K., \& Neel, R. (2016). \emph{Does {Seeing Faces} of {Young Black Boys Facilitate} the {Identification} of {Threatening Stimuli}?} \url{https://journals.sagepub.com/doi/full/10.1177/0956797615624492}

\bibitem[\citeproctext]{ref-yeshurun2003}
Yeshurun, Y., \& Levy, L. (2003). Transient {Spatial Attention Degrades Temporal Resolution}. \emph{Psychological Science}, \emph{14}(3), 225--231. \url{https://doi.org/10.1111/1467-9280.02436}

\end{CSLReferences}

\section*{Appendix}\label{appendix}
\addcontentsline{toc}{section}{Appendix}

Birch \& Bloom (\citeproc{ref-birch2007}{2007}) is about a false belief task comparing ignorance and plausible knowledge conditions.
The first replication and an additional class replication both found results directionally consistent with the original, but much smaller.
The rescue used a much larger sample size than both the original and the first replication and added an additional check to make sure the probabilities participants reported add up to 100\%.
The rescue result was directionally consistent with the original and prior replications, but did not find a significant effect.

Craig \& Richeson (\citeproc{ref-craig2014}{2014}) had White Americans read an article about shifting racial demographics in the US, either with or without a framing that assuaged the potential threat, and found that reading the un-assuaged version led to the endorsement of more conservative positions.
The first replication did not find a significant difference between conditions, and the rescuer speculated that this was due to a smaller sample size and a skew toward liberal political beliefs in the participant pool.
The rescue recruited the same number of participants as the original study and dropped one of the conditions to increase power.
Despite the increased power, the rescue did not replicate the original paper's finding.

Gong et al. (\citeproc{ref-gong2019}{2019}) looked at the interplay between age and willingness to donate in older adults in Hong Kong and found a three-way interaction between age, type of donation, and relationship to recipient.
The first replication sampled US adults and did not find a significant interaction.
The rescuer thought that cultural differences may have played a role and specifically sampled Asian American adults.
The rescue did not recover the interaction.

Haimovitz \& Dweck (\citeproc{ref-haimovitz2016}{2016}) manipulated parents' mindsets with ``failure-is-enhancing'' or ``failure-is-debilitating'' primes and looked at their reactions to a hypothetical situation in which a child received a failing grade.
The first replication was directionally inconsistent with the original, but an additional class replication was consistent.
The rescue added manipulation checks which were not present in the original study or either replications.
The manipulation checks passed, but the rescue study did not recover the target effect.

Hopkins et al. (\citeproc{ref-hopkins2016}{2016}) examined whether people prefer reductive explanations, which explain a result in one science with a more ``fundamental'' science, to horizontal explanations, which explain a result in one science in terms of the same science.
While the original study found a preference for reductive explanations, the first replication did not.
The replication's effective sample size was smaller than the original because a large proportion of participants failed the attention check.
The rescue increased made the attention check slightly easier and recruited a larger sample to account for failures, but still did not replicate the original effect.

Jara-Ettinger et al. (\citeproc{ref-jara-ettinger2022}{2022}) looked at shape bias in US adults across 3 shape exemplars and found a preference to extend nouns on the basis of shape over color or material.
The replication found an above-chance preference for shape, but with very high item-level variability.
The rescuer found that the first replication used stylized versions of the original stimuli taken from a different part of the paper.
The rescue used the same images of stimuli as the original, but still found strong item-level effects and relative preferences for color and material.

Paxton et al. (\citeproc{ref-paxton2012}{2012}) found that participants who completed the Cognitive Reflection Test (CRT) before the moral judgement task gave more utilitarian answers than those who did the moral judgment task before the CRT.
The replication rewrote some of the CRT questions, adding a sub-condition where some of the questions featured characters with specific names.
The first replication failed to find an effect.
The rescuer removed the sub-condition and used questions from the CRT-2, out of concern that Prolific participants would be familiar with the original CRT questions.
The rescue also failed to find the effect.

Porter et al. (\citeproc{ref-porter2016}{2016}) looked at how linguistic intergroup bias influences judgments of shared group membership.
The first replication was directionally against the original result.
The rescuer obtained the direct wordings of the questions from the authors of the original paper, and noticed that they were substantially different from questions in the first replication.
The rescue used the same wordings as the original paper and replicated the effect, although the manipulation check failed.

Schechtman et al. (\citeproc{ref-schechtman2010}{2010}) looked at how widely people generalize tones that previously have been paired with losses or gains, and found that the loss-paired tones were generalized more.
The first replication found a statistically significant effect in the opposite direction of the original study.
It also found that people took much longer to learn which tones were associated with gains vs.~losses compared to the original.
The rescuer made several changes, including asking questions about the sound quality of the participant's computer.
The original study was conducted in person while the replication and rescue were online, so differences in speaker and headphone quality might have played a role in the different result.
The replication found an effect in the same direction as the 1st replication (contrary to the original study).

As discussed in methods, Tarampi et al. (\citeproc{ref-tarampi2016}{2016}) had participants do a timed navigation task and found an interaction between participant gender and the framing of the task (social or spatial) on performance.
The result from the first replication was both statistically insignificant and directionally inconsistent.
The original study was conducted in person, while the replication was conducted online, which might have contributed to the inconsistency.
The rescue was also conducted online, but the rescuer made a series of user interface changes, a comprehension check, and exclusion criteria to ensure that participants understood the instructions, found the task convenient to interact with, and were engaged throughout the experiment.
Still, the rescue did not recover the interaction.

Todd et al. (\citeproc{ref-todd2016}{2016}) looked at participants speed at classifying toys and guns as a function of whether they had just need a White or Black boy's face.
Todd et al. (\citeproc{ref-todd2016}{2016}) found an interaction where Black faces primed faster ``gun'' responses and White faces faster ``toy'' responses.
When we reached out to the original authors, they offered to run a parallel rescue on their student subject pool, which we have here as an additional replication.
The first replication did not find the interaction, but both the better-powered rescue and the original authors' replication did.

Yeshurun \& Levy (\citeproc{ref-yeshurun2003}{2003}) looked at the relationship between spatial attention and temporal resolution.
They measured the threshold where two flashes of light are percieved as one flash versus two as a function of whether the location of the flashes was pre-cued or not.
Yeshurun \& Levy (\citeproc{ref-yeshurun2003}{2003}) found that cueing led to less temporal resolution.
This was independently replicated by Chica \& Christie (\citeproc{ref-chica2009}{2009}), but was not replicated by either the student replication or the rescue.
Both the replication and rescue used in-person participants because the study relies on precise timing and details of the screen which are difficult to control online.
The first replication had a smaller sample size than the original, while the rescue matched the original study's sample size.

\end{document}

### 2024-08-06 individual-rescue-reports/RPubs - Craig 2014 Rescue_files/a_data_004/recommendations.bundle.c32c8fc7358a20ee5907be6e81b685a8.js
update copies of reports

@@ -1,3 +1,0 @@
-define("core/utils/getEmbeddedData",[],function(){"use strict";return function(a){var b=window.document.getElementById("disqus-"+a);try{return b&&JSON.parse(b.textContent||b.innerHTML)}catch(c){return null}}}),define("core/utils/urls",[],function(){"use strict";var a={},b=window.document.createElement("a");return a.getOrigin=function(a){b.href=a;var c=b.href.split("/");return c[0]+"//"+c[2]},a.getHostName=function(a){return b.href=a,b.hostname},a.getDomainPart=function(b,c){"undefined"==typeof c&&(c=0);var d=a.getHostName(b),e=d.split(".").reverse();return e[c]},a.getQuery=function(a){return b.href=a,b.search},a.getPathname=function(a){return b.href=a,b.pathname},a}),define("core/frameBus",["jquery","underscore","backbone","core/utils/urls"],function(a,b,c,d){"use strict";var e=window.opener||window.parent,f=window.name,g=window.document.referrer,h={};h.client=d.getOrigin(window.document.location.href),h.secureClient=h.client.replace(/^\w+:\/\//,"https://"),h.host=g?d.getOrigin(g):h.client;var i={origins:h,messageHandler:function(a){a=a.originalEvent;var b;try{b=JSON.parse(a.data)}catch(c){return}b.name&&"!"===b.name[0]&&a.origin!==h.client&&a.origin!==h.secureClient||"client"===b.scope&&i.trigger(b.name,b.data)},postMessage:function(a){a=JSON.stringify(a),e.postMessage(a,"*")},sendHostMessage:function(a,b){b=b||[],i.postMessage({scope:"host",sender:f,name:a,data:b})}};return b.extend(i,c.Events),a(window).on("message",i.messageHandler),a(window).on("unload",function(){i.sendHostMessage("die")}),window.DISQUS=window.DISQUS||{},window.DISQUS.Bus=i,i}),define("core/bus",["backbone","underscore","core/frameBus"],function(a,b,c){"use strict";var d=b.extend({},a.Events);return d.frame=c,d}),define("core/utils/cookies",[],function(){"use strict";var a={_doc:window.document,create:function(b,c,d){d||(d={});var e=b+"="+c+"; path="+(d.path||"/"),f=d.domain,g=d.expiresIn;if(f&&(e+="; domain=."+f),"[object Number]"===Object.prototype.toString.call(g)){var h=new Date((new
[…]

### 2024-08-06 individual-rescue-reports/RPubs - Craig 2014 Rescue_files/embed.js

@@ -1,51 +1,0 @@
-(function () {
-    'use strict';
-    var _config = window.disqus_config;
-    window.disqus_config = function () {
-        if (_config) {
-            try {
-                _config.call(this);
-            } catch(err) {
-                console.error('There was a problem with the Disqus configuration.', err);
-            }
-        }
-        this.server_side = {
-  "disable_ads_android":"",
-  "inthread_repeat_comment_count":"8",
-  "default_placement_url":"",
-  "inthread_placement_url":"",
-  "under_ccpa":"1",
-  "can_disable_ads":"",
-  "lazyload_viewports":"2",
-  "service":"dynamic",
-  "sourceless_iframe":"1",
-  "experiment":"network_default",
-  "inthread_count_children":"True",
-  "under_gdpr":"",
-  "inthread_multiple_ads":"True",
-  "bin":"embed:promoted_discovery:dynamic:network_default:fallthrough",
-  "bottom_placement_url":"//tempest.services.disqus.com/ads-iframe/taboola/?position=bottom&shortname=rpubs&experiment=network_default&variant=fallthrough&service=dynamic",
-  "variant":"fallthrough",
-  "forum_id":"1423073",
-  "recommendations_placement_url":"//tempest.services.disqus.com/ads-iframe/taboola_1x1/?position=recommendations&shortname=rpubs&experiment=network_default&variant=fallthrough&service=dynamic",
-  "top_placement_url":"//tempest.services.disqus.com/ads-iframe/taboola/?position=top&shortname=rpubs&experiment=network_default&variant=fallthrough&service=dynamic",
-  "inthread_trailing_comment_count":"0",
-  "is_private":"",
-  "skeleton_frame_enabled":"",
-  "disable_ads_ios":"",
-  "recs_outside_embed_enabled":"1",
-  "forum":{
-    "id":1423073,
-    "disable_disqus_branding":false,
-    "recommendation_placement":"top",
-    "recommendations_feature_enabled":true
-  },
-  "sandbox_ads":"1",
-  "inthread_leading_comment_count":"1",
-  "t":"1714687111"
-};
-    };
[…]

### 2024-08-06 individual-rescue-reports/RPubs - Craig 2014 Rescue_files/launchpad-liveramp.js

@@ -1,1 +1,0 @@
-var launchPad=document.createElement("script"),launchPadConfiguration=(launchPad.async=!0,launchPad.defer=!0,!function(){var r,i,o,t;"function"!=typeof window.__launchpad&&(r=[],i=window,o=i.document,t=i.__launchpad?i.__launchpad.start:function(){},!i.__launchpad)&&function t(){var e,a=!!i.frames.__launchpadLocator;return a||(o.body?((e=o.createElement("iframe")).style.cssText="display:none",e.name="__launchpadLocator",o.body.appendChild(e)):setTimeout(t,5)),!a}()&&(i.__launchpad=function(t,e,a,o){if(!(t=[t,e,a,o]).length)return r;"ping"===t[0]?"function"==typeof t[2]&&t[2]({loaded:!1,apiVersion:"1.0"},!0):r.push(t)},i.__launchpad.commandQueue=r,i.__launchpad.start=t,i.addEventListener("message",function(a){var o="string"==typeof a.data,t={};try{t=o?JSON.parse(a.data):a.data}catch(t){}var r=t.__launchpadCall;r&&i.__launchpad(r.command,r.version,function(t,e){a.source&&(t={__launchpadReturn:{returnValue:t,success:e,callId:r.callId,command:r.command}},o&&(t=JSON.stringify(t)),a.source.postMessage(t,"*"))},r.parameter)},!1))}(),{logging:!1,atsRules:[{id:"4368de8c-8137-47b9-9e3f-42e90dd3c206",triggers:[{type:"LOAD_EVENT",loadEvent:"PAGE_VIEW"},{type:"PAGE_VIEW",rules:[{operation:"CONTAINS",value:"https://Disqus.com",attribute:"PAGE_URL"},{operation:"CONTAINS",value:"https://dailyfaceoff.com",attribute:"PAGE_URL"},{operation:"CONTAINS",value:"https://arcamax.com",attribute:"PAGE_URL"},{operation:"CONTAINS",value:"https://lingojam.com",attribute:"PAGE_URL"},{operation:"CONTAINS",value:"https://petapixel.com",attribute:"PAGE_URL"},{operation:"CONTAINS",value:"https://steelersdepot.com",attribute:"PAGE_URL"},{operation:"CONTAINS",value:"https://mediaite.com",attribute:"PAGE_URL"},{operation:"CONTAINS",value:"https://wweek.com",attribute:"PAGE_URL"},{operation:"CONTAINS",value:"https://awfulannouncing.com",attribut
[…]

### 2024-08-06 individual-rescue-reports/RPubs - Craig 2014 Rescue_files/recommendations.js

@@ -1,38 +1,0 @@
-(function () {
-    'use strict';
-    var _config = window.disqus_recommendations_config;
-    window.disqus_recommendations_config = function () {
-        if (_config) {
-            try {
-                _config.call(this);
-            } catch(err) {
-                console.error('There was a problem with the Disqus configuration.', err);
-            }
-        }
-        this.server_side = {
-  "bin":"embed:promoted_discovery:dynamic:network_default:fallthrough",
-  "disable_ads_ios":"",
-  "recs_outside_embed_enabled":"1",
-  "forum":{
-    "id":1423073,
-    "disable_disqus_branding":false,
-    "recommendation_placement":"top",
-    "recommendations_feature_enabled":true
-  },
-  "service":"dynamic",
-  "disable_ads_android":"",
-  "sourceless_iframe":"1",
-  "variant":"fallthrough",
-  "forum_id":"1423073",
-  "recommendations_placement_url":"//tempest.services.disqus.com/ads-iframe/taboola_1x1/?position=recommendations&shortname=rpubs&experiment=network_default&variant=fallthrough&service=dynamic",
-  "experiment":"network_default",
-  "default_placement_url":"",
-  "t":"1714687163",
-  "can_disable_ads":"",
-  "skeleton_frame_enabled":""
-};
-    };
-})();
[…]

### 2024-08-06 individual-rescue-reports/RPubs - Replication of Sleep Preferentially Enhances Memory for Emotional Components of Scenes by Payne, Stickgold, Swanberg and Kensinger (2008, Psychological Science) Pilot B 12-5_files/a_data_004/recommendations.load.6e12c4d0f5433c912853f0925725b0e0.js

@@ -1,1 +1,0 @@
-!function(){"use strict";var a=window.document,b={STYLES:"https://c.disquscdn.com/next/recommendations/styles/recommendations.10022a97346f1c6e3798931bbd8e4bb5.css",RTL_STYLES:"https://c.disquscdn.com/next/recommendations/styles/recommendations_rtl.9c3ccad48c24340222b5a85c20ea36b8.css","recommendations/main":"https://c.disquscdn.com/next/recommendations/recommendations.bundle.c32c8fc7358a20ee5907be6e81b685a8.js","remote/config":"https://disqus.com/next/config.js"};window.require={baseUrl:"https://c.disquscdn.com/next/current/recommendations/recommendations",paths:["recommendations/main","remote/config"].reduce(function(a,c){var d=-3;return a[c]=b[c].slice(0,d),a},{})};var c=a.createElement("script");c.onload=function(){require(["common/main"],function(a){a.init("recommendations",b)})},c.src="https://c.disquscdn.com/next/recommendations/common.bundle.b14156ac25e5c5b28459f997165c5d76.js",a.body.appendChild(c)}();

### 2024-08-06 individual-rescue-reports/RPubs - Replication of Sleep Preferentially Enhances Memory for Emotional Components of Scenes by Payne, Stickgold, Swanberg and Kensinger (2008, Psychological Science) Pilot B 12-5_files/a_data_005/config.js

@@ -1,1 +1,0 @@
-define({"tos_exempt_forums_shortnames":["somememes","qrt-dev","qrt-test","qrt-prd","myracehorse","test-prisamedia","wradio-colombia","kathimerini","https-www-kathimerini-gr","el-pais-1","diarioas","www-spectator-co-uk","https-new-dev-spectator-co-uk","drt-prd","drt-test","xoff-prd","xoffroad-test","tne-prod","prod-expresso"],"register":{"ENABLE_CAPTCHA":true},"max_post_edit_days":7,"lounge":{"follow_channel_prompt_views":1,"motd_admin_url":"https://blog.disqus.com/new-disqus-wordpress-plugin-v3-1","viglink":{"experiment_version":"v5","version":"v4"},"tracking":{"iframe_limit":5,"list":[{"url":"//referrer.disqus.com/juggler/stat.gif?event=data_tracker","forced_forums":["disqus"],"rate":0,"type":"img"}]},"font_options":[{"category":"serif","name":"Lora"},{"category":"sans-serif","name":"Montserrat"},{"category":"sans-serif","name":"Mulish"},{"category":"sans-serif","name":"Nunito"},{"category":"sans-serif","name":"Open+Sans"},{"category":"sans-serif","name":"Poppins"},{"category":"sans-serif","name":"Roboto"},{"category":"serif","name":"Roboto+Slab"},{"category":"sans-serif","name":"Source+Sans+Pro"},{"category":"serif","name":"Source+Serif+Pro"},{"category":"serif","name":"Spectral"},{"category":"sans-serif","name":"IBM+Plex+Sans"}],"cc_v2_start":"2023-04-18T17:50:00","motd_home_title":"\ud83c\udf17 New Science & Nature Channel is live! \ud83c\udf17 ","motd_admin_title":"Announcing a fresh update to our WordPress plugin! \ud83d\udcda","motd_home_url":"https://disqus.com/channel/discussscienceandnature/","REALTIME":{"BACKOFF_INTERVAL":4,"MAX_HANDSHAKE_FAILS":1,"XHR_ENABLED":false,"THREAD_STALE_DAYS":1},"motd_marketing_cta":"Join the fun \u00bb","switches":{"customer_pulse_analytics":{"username":["orazumov_zeta","michaelyakovlev","commenting_privacy","andrei_ivanov_disqus","aivanov"]},"custom_reactions":true,"home_ad
[…]

### 2024-08-06 individual-rescue-reports/RPubs - Replication of Sleep Preferentially Enhances Memory for Emotional Components of Scenes by Payne, Stickgold, Swanberg and Kensinger (2008, Psychological Science) Pilot B 12-5_files/a_data_005/lounge.load.006bbc905574fc5153c7814eb2dc65a8.js

@@ -1,1 +1,0 @@
-!function(){"use strict";var a=window.document,b={STYLES:"https://c.disquscdn.com/next/embed/styles/lounge.a2345915325acf798c871e4957e4ea9f.css",RTL_STYLES:"https://c.disquscdn.com/next/embed/styles/lounge_rtl.1541fd3334c2492f03169f02e4abc09c.css","lounge/main":"https://c.disquscdn.com/next/embed/lounge.bundle.a932f0de230f1d945f3274de9e901830.js","remote/config":"https://disqus.com/next/config.js","common/vendor_extensions/highlight":"https://c.disquscdn.com/next/embed/highlight.6fbf348532f299e045c254c49c4dbedf.js"};window.require={baseUrl:"https://c.disquscdn.com/next/current/embed/embed",paths:["lounge/main","remote/config","common/vendor_extensions/highlight"].reduce(function(a,c){return a[c]=b[c].slice(0,-3),a},{})};var c=a.createElement("script");c.onload=function(){require(["common/main"],function(a){a.init("lounge",b)})},c.src="https://c.disquscdn.com/next/embed/common.bundle.a59842d31742a609955eb402e17bb0c3.js",a.body.appendChild(c)}();

### 2024-08-06 individual-rescue-reports/RPubs - Replication of Sleep Preferentially Enhances Memory for Emotional Components of Scenes by Payne, Stickgold, Swanberg and Kensinger (2008, Psychological Science) Pilot B 12-5_files/embed.js

@@ -1,51 +1,0 @@
-(function () {
-    'use strict';
-    var _config = window.disqus_config;
-    window.disqus_config = function () {
-        if (_config) {
-            try {
-                _config.call(this);
-            } catch(err) {
-                console.error('There was a problem with the Disqus configuration.', err);
-            }
-        }
-        this.server_side = {
-  "disable_ads_android":"",
-  "inthread_repeat_comment_count":"8",
-  "default_placement_url":"",
-  "inthread_placement_url":"",
-  "under_ccpa":"",
-  "can_disable_ads":"",
-  "lazyload_viewports":"2",
-  "service":"dynamic",
-  "sourceless_iframe":"1",
-  "experiment":"network_default",
-  "inthread_count_children":"True",
-  "under_gdpr":"",
-  "inthread_multiple_ads":"True",
-  "bin":"embed:promoted_discovery:dynamic:network_default:fallthrough",
-  "bottom_placement_url":"//tempest.services.disqus.com/ads-iframe/taboola/?position=bottom&shortname=rpubs&experiment=network_default&variant=fallthrough&service=dynamic",
-  "variant":"fallthrough",
-  "forum_id":"1423073",
-  "recommendations_placement_url":"//tempest.services.disqus.com/ads-iframe/taboola_1x1/?position=recommendations&shortname=rpubs&experiment=network_default&variant=fallthrough&service=dynamic",
-  "top_placement_url":"//tempest.services.disqus.com/ads-iframe/taboola/?position=top&shortname=rpubs&experiment=network_default&variant=fallthrough&service=dynamic",
-  "inthread_trailing_comment_count":"0",
-  "is_private":"",
-  "skeleton_frame_enabled":"",
-  "disable_ads_ios":"",
-  "recs_outside_embed_enabled":"1",
-  "forum":{
-    "id":1423073,
-    "disable_disqus_branding":false,
-    "recommendation_placement":"top",
-    "recommendations_feature_enabled":true
-  },
-  "sandbox_ads":"1",
-  "inthread_leading_comment_count":"1",
-  "t":"1714686816"
-};
-    };
[…]

### 2024-08-06 individual-rescue-reports/RPubs - Replication of Sleep Preferentially Enhances Memory for Emotional Components of Scenes by Payne, Stickgold, Swanberg and Kensinger (2008, Psychological Science) Pilot B 12-5_files/recommendations.js

@@ -1,38 +1,0 @@
-(function () {
-    'use strict';
-    var _config = window.disqus_recommendations_config;
-    window.disqus_recommendations_config = function () {
-        if (_config) {
-            try {
-                _config.call(this);
-            } catch(err) {
-                console.error('There was a problem with the Disqus configuration.', err);
-            }
-        }
-        this.server_side = {
-  "bin":"embed:promoted_discovery:dynamic:network_default:fallthrough",
-  "disable_ads_ios":"",
-  "recs_outside_embed_enabled":"1",
-  "forum":{
-    "id":1423073,
-    "disable_disqus_branding":false,
-    "recommendation_placement":"top",
-    "recommendations_feature_enabled":true
-  },
-  "service":"dynamic",
-  "disable_ads_android":"",
-  "sourceless_iframe":"1",
-  "variant":"fallthrough",
-  "forum_id":"1423073",
-  "recommendations_placement_url":"//tempest.services.disqus.com/ads-iframe/taboola_1x1/?position=recommendations&shortname=rpubs&experiment=network_default&variant=fallthrough&service=dynamic",
-  "experiment":"network_default",
-  "default_placement_url":"",
-  "t":"1714686873",
-  "can_disable_ads":"",
-  "skeleton_frame_enabled":""
-};
-    };
-})();
[…]

### 2024-08-06 manuscript/manuscript.Rmd
redraft discussion

@@
 Given the mix of successful and unsuccessful rescue projects, we discuss in depth a few projects where we have speculations about why they turned out the way they did.
-Brief descriptions of the projects not covered in this section be found in the Appendix.
+Brief descriptions of the projects not covered in this section can be found in the Appendix.
 
@@
 In cases where re-replications failed, we do not believe any conclusions are licensed about the status of the original results.
+The rescue projects (and first replications) were primarily conducted by first year PhD students, in a program where it is expected that PhD students author peer-reviewed papers, and where some of the rescuers already had publications.
+Thus, while we refer to the rescuers as students, they are investigators doing experiments that become part of the literature.
 Students conducting rescue projects put substantial effort into trying to set up rescues that had a good chance of success, but projects were constrained by budget limitations, a short timeline, and the constraint that most data collection needed to occur online.
-These limitations are representative of the sort of resource limitations often faced by early-career researchers.
-That said, it is possible that different results might be obtained in better-resourced settings, by scientists with more expertise and more time.
+Additionally, while many students had done research before and were learning best-practices for experiments, they were not experts in the particular paradigms.
+These limitations are representative of the sort of knowledge and resource limitations often faced by early-career researchers.
+That said, it is possible that different results might be obtained in better-resourced settings, by scientists with more expertise, more time, or more privileged knowledge about how the original experiments were conducted.
 
-Due to the limited number of replications that are conducted and systematically reported, and the even smaller number of re-replications reported, there is a lot of uncertainty in how much replicability varies across features of the original experiment and replications.
+Due to the limited number of replications that are conducted and systematically reported, and the even smaller number of re-replications reported, there is substantial uncertainty in how much replicability varies across features of the original experiment and replications.
 
@@
 
-Replications are done for many reasons, and researchers often have some prior beliefs about whether a replication will succeed.
-These beliefs may influence how a researcher interprets a failed replication and thus whether they think it's worth trying to rescue.
-For instance, a researcher who has high credence in the main result is more likely to attribute failure to specific details in the replication and thus want to rescue by tweaking these details.
-On the other side, a researcher who is dubious of the methods, results, or statistical approaches, or who has experienced failures to replicate and extend the work, may be quicker to interpret a failure as a more definitive negative result.
-Interpretations may also depend on the perceived strength of the replication and what effect size is cared about.
+We have focused here on a narrow type of replication and rescue: that done by an early career researcher with the goal of establishing whether this is a result *they* can build on.
+We acknowledge that this type of replication exists as part of a wider ecosystem of replications that have different properties and are done for different reasons.
 
-While we focus here on a narrow type of replication and rescue, that done by an early career researcher with the goal of establishing whether this is a result *they* can build on, it exists as part of a wider ecosystem of replications that are done for different reasons with different properties.
+In many cases, researchers may have strong prior beliefs about where a replication will succeed, and these priors may influence a researchers interpretation of a failed replication, and thus their calculations about where a re-replication will succeed or is worth attempting.
+For instance, a researcher who has high credence in the main result is more likely to attribute failure to specific details in the replication, and thus may want to do a rescue where those details are adjusted.
+On the other hand, a researcher who is dubious of the methods, results, or statistical approaches in an experiment, or who has previously failed to extend the work, may be quicker to interpret a non-replication as a more definitive negative result.
+What a researcher chooses to do may also depend on the perceived strength of the replication, what size effects they think are relevant, and how important they think the target effect is.
+Thus, in some cases, when to re-replicate may be a question of prior beliefs and perceived utility rather than just likelihood of a re-replication succeeding.
 
@@
 
+Write-ups of individual rescue and replication projects can be found in the repository at https://osf.io/cyk5w/.
+
 @birch2007 is about a false belief task comparing ignorance and plausible knowledge conditions.
-The first replication and an additional class replication both found results directionally consistent with the original, but much smaller.
+The first replication and an additional class replication both found results in the same direction as the original result, but much smaller. 
 The rescue used a much larger sample size than both the original and the first replication and added an additional check to make sure the probabilities participants reported add up to 100%.
-The rescue result was directionally consistent with the original and prior replications, but did not find a significant effect.
+The rescue result was in the same direction as the original and prior replications, but did not find a significant effect.
 
@@
 @haimovitz2016 manipulated parents' mindsets with "failure-is-enhancing" or "failure-is-debilitating" primes and looked at their reactions to a hypothetical situation in which a child received a failing grade.
-The first replication was directionally inconsistent with the original, but an additional class replication was consistent.
+The first replication found a point estimate in the opposite direction to the original effect, but an additional class replication found a directionally consistent effect.
 The rescue added manipulation checks which were not present in the original study or either replications.
@@
 
-@jara-ettinger2022 looked at shape bias in US adults across 3 shape exemplars and found a preference to extend nouns on the basis of shape over color or material.
+@jara-ettinger2022 looked at shape bias in US adults across 3 shape exemplars and found a preference to extend nouns on the basis of shape rather than color or material.
 The replication found an above-chance preference for shape, but with very high item-level variability.
@@
 @porter2016 looked at how linguistic intergroup bias influences judgments of shared group membership.
-The first replication was directionally against the original result.
+The first replication found an effect directionally inconsistent with the original result.
 The rescuer obtained the direct wordings of the questions from the authors of the original paper, and noticed that they were substantially different from questions in the first replication.
@@
 The original study was conducted in person while the replication and rescue were online, so differences in speaker and headphone quality might have played a role in the different result.
-The replication found an effect in the same direction as the 1st replication (contrary to the original study).
+The rescue found an effect in the same direction as the 1st replication (contrary to the original study).
 
@@
 @yeshurun2003 looked at the relationship between spatial attention and temporal resolution.
-They measured the threshold where two flashes of light are percieved as one flash versus two as a function of whether the location of the flashes was pre-cued or not.
+They measured the threshold where two flashes of light are perceived as one flash versus two as a function of whether the location of the flashes was pre-cued or not.
 @yeshurun2003 found that cueing led to less temporal resolution.

### 2024-08-06 manuscript/manuscript.tex
redraft discussion

@@
 12 got a rating of 0, 2 got a rating of .75, and 3 got a rating of 1.
-Thus, a first pass answer to the question ``how often can a failed replication be salvaged?'' is 29\% (bootstrapped 95\% CI: 6\% - 53\%) of the time.
+Thus, a first pass answer to the question ``how often can a failed replication be salvaged?'' is 29\% (bootstrapped 95\% CI: 12\% - 53\%) of the time.
 
@@
 In cases where re-replications failed, we do not believe any conclusions are licensed about the status of the original results.
+The rescue projects (and first replications) were primarily conducted by first year PhD students, in a program where it is expected that PhD students author peer-reviewed papers, and where some of the rescuers already had publications.
+Thus, while we refer to the rescuers as students, they are investigators doing experiments that become part of the literature.
 Students conducting rescue projects put substantial effort into trying to set up rescues that had a good chance of success, but projects were constrained by budget limitations, a short timeline, and the constraint that most data collection needed to occur online.
-These limitations are representative of the sort of resource limitations often faced by early-career researchers.
-That said, it is possible that different results might be obtained in better-resourced settings, by scientists with more expertise and more time.
-
-Due to the limited number of replications that are conducted and systematically reported, and the even smaller number of re-replications reported, there is a lot of uncertainty in how much replicability varies across features of the original experiment and replications.
+Additionally, while many students had done research before and were learning best-practices for experiments, they were not experts in the particular paradigms.
+These limitations are representative of the sort of knowledge and resource limitations often faced by early-career researchers.
+That said, it is possible that different results might be obtained in better-resourced settings, by scientists with more expertise, more time, or more privileged knowledge about how the original experiments were conducted.
+
+Due to the limited number of replications that are conducted and systematically reported, and the even smaller number of re-replications reported, there is substantial uncertainty in how much replicability varies across features of the original experiment and replications.
 
@@
 
-Replications are done for many reasons, and researchers often have some prior beliefs about whether a replication will succeed.
-These beliefs may influence how a researcher interprets a failed replication and thus whether they think it's worth trying to rescue.
-For instance, a researcher who has high credence in the main result is more likely to attribute failure to specific details in the replication and thus want to rescue by tweaking these details.
-On the other side, a researcher who is dubious of the methods, results, or statistical approaches, or who has experienced failures to replicate and extend the work, may be quicker to interpret a failure as a more definitive negative result.
-Interpretations may also depend on the perceived strength of the replication and what effect size is cared about.
-
-While we focus here on a narrow type of replication and rescue, that done by an early career researcher with the goal of establishing whether this is a result \emph{they} can build on, it exists as part of a wider ecosystem of replications that are done for different reasons with different properties.
+We have focused here on a narrow type of replication and rescue: that done by an early career researcher with the goal of establishing whether this is a result \emph{they} can build on.
+We acknowledge that this type of replication exists as part of a wider ecosystem of replications that have different properties and are done for different reasons.
+
+In many cases, researchers may have strong prior beliefs about where a replication will succeed, and these priors may influence a researchers interpretation of a failed replication, and thus their calculations about where a re-replication will succeed or is worth attempting.
+For instance, a researcher who has high credence in the main result is more likely to attribute failure to specific details in the replication, and thus may want to do a rescue where those details are adjusted.
+On the other hand, a researcher who is dubious of the methods, results, or statistical approaches in an experiment, or who has previously failed to extend the work, may be quicker to interpret a non-replication as a more definitive negative result.
+What a researcher chooses to do may also depend on the perceived strength of the replication, what size effects they think are relevant, and how important they think the target effect is.
+Thus, in some cases, when to re-replicate may be a question of prior beliefs and perceived utility rather than just likelihood of a re-replication succeeding.
 
@@
 
+Write-ups of individual rescue and replication projects can be found in the repository at \url{https://osf.io/cyk5w/}.
+
 Birch \& Bloom (\citeproc{ref-birch2007}{2007}) is about a false belief task comparing ignorance and plausible knowledge conditions.
-The first replication and an additional class replication both found results directionally consistent with the original, but much smaller.
+The first replication and an additional class replication both found results in the same direction as the original result, but much smaller.
 The rescue used a much larger sample size than both the original and the first replication and added an additional check to make sure the probabilities participants reported add up to 100\%.
-The rescue result was directionally consistent with the original and prior replications, but did not find a significant effect.
+The rescue result was in the same direction as the original and prior replications, but did not find a significant effect.
 
@@
 Haimovitz \& Dweck (\citeproc{ref-haimovitz2016}{2016}) manipulated parents' mindsets with ``failure-is-enhancing'' or ``failure-is-debilitating'' primes and looked at their reactions to a hypothetical situation in which a child received a failing grade.
-The first replication was directionally inconsistent with the original, but an additional class replication was consistent.
+The first replication found a point estimate in the opposite direction to the original effect, but an additional class replication found a directionally consistent effect.
 The rescue added manipulation checks which were not present in the original study or either replications.
@@
 Jara-Ettinger et al.
-(\citeproc{ref-jara-ettinger2022}{2022}) looked at shape bias in US adults across 3 shape exemplars and found a preference to extend nouns on the basis of shape over color or material.
+(\citeproc{ref-jara-ettinger2022}{2022}) looked at shape bias in US adults across 3 shape exemplars and found a preference to extend nouns on the basis of shape rather than color or material.
 The replication found an above-chance preference for shape, but with very high item-level variability.
@@
 Porter et al. (\citeproc{ref-porter2016}{2016}) looked at how linguistic intergroup bias influences judgments of shared group membership.
-The first replication was directionally against the original result.
+The first replication found an effect directionally inconsistent with the original result.
 The rescuer obtained the direct wordings of the questions from the authors of the original paper, and noticed that they were substantially different from questions in the first replication.
@@
 Yeshurun \& Levy (\citeproc{ref-yeshurun2003}{2003}) looked at the relationship between spatial attention and temporal resolution.
-They measured the threshold where two flashes of light are percieved as one flash versus two as a function of whether the location of the flashes was pre-cued or not.
+They measured the threshold where two flashes of light are perceived as one flash versus two as a function of whether the location of the flashes was pre-cued or not.
 Yeshurun \& Levy (\citeproc{ref-yeshurun2003}{2003}) found that cueing led to less temporal resolution.

### 2024-08-08 manuscript/manuscript.Rmd
final edits?

@@
 Due to the large effect size of a couple studies, large effect studies are shown in a separate panel.
-In a few cases, the first replication's key effect was in the same direction as the original with a 95% CI that did not overlap 0; however, in these cases the larger pattern of results was not fully consistent between original and first replication.
+In a few cases, the first replication's key effect was in the same direction as the original with a 95% CI that did not overlap 0; however, in these cases the larger pattern of results was not consistent between original and first replication.
 "}
@@
 
-As secondary measures, we calculated the $p$-original values between a) the original and just the first replication and rescue, b) the original and the rescue, c) the original and non-rescue replications, and d) the rescue and other replications.
+As secondary measures, we calculated the $p$-original values between a) the original and just the first replication and rescue (i.e.
+excluding additional replications), b) the original and the rescue, c) the original and non-rescue replications, and d) the rescue and other replications.
 For a) the original versus the first replication and the rescue, the median value of $p$-original was `r rr_summ$median |> round(2)` [IQR: `r rr_summ$low |> round(2)` - `r rr_summ$high|> round(2)`], and `r round(rr_summ$less_than*100)`% of the $p$-original values were less than .05.
@@
 
+In cases where re-replications failed, we do not believe any conclusions are licensed about the status of the original results.
+
 ## Limitations
@@
 
-In cases where re-replications failed, we do not believe any conclusions are licensed about the status of the original results.
-The rescue projects (and first replications) were primarily conducted by first year PhD students, in a program where it is expected that PhD students author peer-reviewed papers, and where some of the rescuers already had publications.
+One potentially salient limitation of our work here is that the rescue projects (and the first replications) were primarily conducted by first year PhD students; hence the generality of our conclusions to other investigators is unknown.
+We believe, however, that this is more of an apparent than an actual limitation.
+Students were enrolled in a highly-competitive graduate program where it is expected that PhD students author peer-reviewed papers; several of the rescuers already had published first-authored peer reviewed articles.
 Thus, while we refer to the rescuers as students, they are investigators doing experiments that become part of the literature.
+
 Students conducting rescue projects put substantial effort into trying to set up rescues that had a good chance of success, but projects were constrained by budget limitations, a short timeline, and the constraint that most data collection needed to occur online.
-Additionally, while many students had done research before and were learning best-practices for experiments, they were not experts in the particular paradigms.
+Additionally, while most students had done research before and were learning best practices for experiments, they were not experts in the particular paradigms they were implementing.
 These limitations are representative of the sort of knowledge and resource limitations often faced by early-career researchers.
@@
 For instance, a researcher who has high credence in the main result is more likely to attribute failure to specific details in the replication, and thus may want to do a rescue where those details are adjusted.
-On the other hand, a researcher who is dubious of the methods, results, or statistical approaches in an experiment, or who has previously failed to extend the work, may be quicker to interpret a non-replication as a more definitive negative result.
+On the other hand, a researcher who is dubious of the methods, results, or statistical approaches in an experiment, or who has previously failed to extend the experimental result, may be quicker to interpret a non-replication as a more definitive negative result.
 What a researcher chooses to do may also depend on the perceived strength of the replication, what size effects they think are relevant, and how important they think the target effect is.

### 2024-08-08 manuscript/manuscript.tex
final edits?

@@
 Due to the large effect size of a couple studies, large effect studies are shown in a separate panel.
-In a few cases, the first replication's key effect was in the same direction as the original with a 95\% CI that did not overlap 0; however, in these cases the larger pattern of results was not fully consistent between original and first replication.
+In a few cases, the first replication's key effect was in the same direction as the original with a 95\% CI that did not overlap 0; however, in these cases the larger pattern of results was not consistent between original and first replication.
 }\label{fig:smd}
@@
 
-As secondary measures, we calculated the \(p\)-original values between a) the original and just the first replication and rescue, b) the original and the rescue, c) the original and non-rescue replications, and d) the rescue and other replications.
+As secondary measures, we calculated the \(p\)-original values between a) the original and just the first replication and rescue (i.e.~excluding additional replications), b) the original and the rescue, c) the original and non-rescue replications, and d) the rescue and other replications.
 For a) the original versus the first replication and the rescue, the median value of \(p\)-original was 0.1 {[}IQR: 0.01 - 0.27{]}, and 35\% of the \(p\)-original values were less than .05.
@@
 
+In cases where re-replications failed, we do not believe any conclusions are licensed about the status of the original results.
+
 \subsection{Limitations}\label{limitations}

### 2024-08-08 manuscript/coverletter/collabra_response.tex
had forgotten to describe chou2016 in appendix, fixed

@@
 
-		We have checked that the links in %TODO foobar
+		We have checked that the links data/combined\_data.csv
 		all work, and updated the README to be much more detailed.
 
-		Unfortunately, we don't have a way to edit the individual pre-registrations, but we believe all the necessary information for the rescues is now available.
+		Unfortunately, we don't have a way to edit the individual pre-registrations, but we believe all the necessary information for the rescues is now available, linked from the data sheet.
 
@@
 
-		 \revised{\begin{verbatim}
-		 		### First-replication-reports and Individual-rescue-reports
-		 		* archival copies of the reports from individual projects, in case the rpubs links break or are overwritten
-		 		* to view, download the repo and open the html files in a browser
+		% \revised{\begin{verbatim}
+		 %		### First-replication-reports and Individual-rescue-reports
+		 %		* archival copies of the reports from individual projects, in case the rpubs links break or are overwritten
+		 %		* to view, download the repo and open the html files in a browser
 
-		 	\end{verbatim}}
+		 %	\end{verbatim}}
 
@@
 
-		\revised{ \begin{verbatim}
-			The overall manuscript can be reproduced by knitting manuscript/manuscript.Rmd
-			* This file reads data from data/combined_data.csv and data/boyce_2023_data.csv
-			* This file uses code/helper/parse_stats.R \end{verbatim}}
+	%	\revised{ \begin{verbatim}
+	%		The overall manuscript can be reproduced by knitting manuscript/manuscript.Rmd
+	%		* This file reads data from data/combined_data.csv and data/boyce_2023_data.csv
+	%		* This file uses code/helper/parse_stats.R \end{verbatim}}
 
-		\revised{\begin{verbatim}
-				### First-replication-projects and Individual-rescue-projects
-			* include the individual replication and rescue projects (aka github repos) respectively
-			* the rescue projects repos have been checked and include data, code/reproducible report, and the materials to run the experiment\end{verbatim}}
+	%	\revised{\begin{verbatim}
+	%			### First-replication-projects and Individual-rescue-projects
+	%		* include the individual replication and rescue projects (aka github repos) respectively
+	%		* the rescue projects repos have been checked and include data, code/reproducible report, and the materials to run the experiment\end{verbatim}}
 

### 2024-08-08 manuscript/manuscript.Rmd
had forgotten to describe chou2016 in appendix, fixed

@@
 
+@chou2016 studied whether a sense of control affects how much one feels physical pain.
+Participants were asked to recall experiences where they had either a low or high amount of control and then to report their level of physical pain.
+The first replication closely followed the methods of the original, but added a manipulation check borrowed from a different experiment in @chou2016.
+The manipulation check was successful, but there were no significant difference in pain level between the two groups.
+The rescue added pre-survey questions about pain levels to confirm that participants in the two groups had the same baseline understanding of pain.
+The rescue also did not find a significant difference in pain level between groups.
+
 @craig2014 had White Americans read an article about shifting racial demographics in the US, either with or without a framing that assuaged the potential threat, and found that reading the un-assuaged version led to the endorsement of more conservative positions.

### 2024-08-08 manuscript/manuscript.tex
had forgotten to describe chou2016 in appendix, fixed

@@
 
+Chou et al.
+(\citeproc{ref-chou2016}{2016}) studied whether a sense of control affects how much one feels physical pain.
+Participants were asked to recall experiences where they had either a low or high amount of control and then to report their level of physical pain.
+The first replication closely followed the methods of the original, but added a manipulation check borrowed from a different experiment in Chou et al.
+(\citeproc{ref-chou2016}{2016}).
+The manipulation check was successful, but there were no significant difference in pain level between the two groups.
+The rescue added pre-survey questions about pain levels to confirm that participants in the two groups had the same baseline understanding of pain.
+The rescue also did not find a significant difference in pain level between groups.
+
 Craig \& Richeson (\citeproc{ref-craig2014}{2014}) had White Americans read an article about shifting racial demographics in the US, either with or without a framing that assuaged the potential threat, and found that reading the un-assuaged version led to the endorsement of more conservative positions.

### 2024-08-08 manuscript/coverletter/collabra_response.tex
work on response letter

@@
 \usepackage{float}
+
+\providecommand{\tightlist}{%
+	\setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
+
+\usepackage{hyperref}
 \begin{document}
@@
 
-		I also address some of reviewer 1's specific repo-related concerns below; I suspect many of them would have been ameliorated had the reviewer been able to download the repo.
+		I also address reviewer 1's specific repository-related concerns more below; I suspect many of them would have been ameliorated had the reviewer been able to download the repository files.
 
@@
 
-		We have expanded the discussion section and re-organized it to have a more explicit discussion of limitations.
+		We have added an explicit ``Limitations'' subsection to the discussion, which we discuss further below in our response to reviewer 1.
 
-		Thank you for the reference, which we have incorporated, and we have included more information on the changes to the discussion below, in our response to reviewer 1.
-
-		Also, see below for our changes and rebuttals to reviewer 1's thoughts.
+		Also, see below for our changes and rebuttals to reviewer 1's other points.
 
@@
 
-		%TODO discussion section
-		We have expanded the discussion section to discuss the larger picture of different circumstances that motivate replications and rescues.
+		We have expanded the last part of the discussion section to acknowledge the much larger picture of different circumstances that motivate replications and rescues, and how these might be influenced by the prior beliefs of the investigators.
 We discuss the changes more below in response to reviewer 2's points.
@@
 		We are sorry this error occurred, and that reviewer 1 didn't realize the files could be downloaded directly from the OSF copy (linked in the paper).
-as the inability of reviewer 1 seems to have resulted in misunderstandings about the usability of files in the repo (which are much more understandable when opened on a computer).
+The inability of reviewer 1 to download and open the files seems to have resulted in misunderstandings about the usability of files in the repo (which are much more understandable when opened on a computer).
 
-		From googling, we believe this to be a windows issue, and to prevent this problem for future users we have added a note at the top of the README directing readers for how to address or sidestep the problem, namely:
+		From googling, we believe the long files names issue to be a windows issue, and to prevent this problem for future users we have added a note at the top of the README directing readers for how to address or sidestep the problem, namely:
 
-		\revised{Note: If you are a windows user and get an error about overly long file names, please see [this stackoverflow post](https://stackoverflow.com/questions/22575662/filename-too-long-in-git-for-windows) or [this github issue](https://github.com/desktop/desktop/issues/17882) for how to fix it.
-Alternatively, you can download a zip of the repo from [the osf copy](https://osf.io/cyk5w/files/github) by clicking "Download this folder".}
+		\revised{Note: If you are a windows user and get an error about overly long file names, please see [this stackoverflow post] (https://stackoverflow.com/questions/22575662/filename-too-long-in-git-for-windows) or [this github issue] (https://github.com/desktop/desktop/issues/17882) for how to fix it.
+Alternatively, you can download a zip of the repo from [the osf copy] (https://osf.io/cyk5w/files/github) by clicking "Download this folder".}
+
+		Hopefully this warning will prevent future difficulties with accessing the repository.
 
@@
 
-		See  https://github.com/langcog/251-rescue-projects/tree/main for the revised README.
+		See  https://github.com/langcog/251-rescue-projects/tree/main for the revised README, which I also quote here:
+
+		\revised{
+		\textbf{\large 251-rescue-projects}\label{rescue-projects}
+
+			\textbf{Note:} If you are a windows user and get an error about overly
+			long file names, please see
+			\href{https://stackoverflow.com/questions/22575662/filename-too-long-in-git-for-windows}{this
+				stackoverflow post} or
+			\href{https://github.com/desktop/desktop/issues/17882}{this github
+				issue} for how to fix it. Alternatively, you can download a zip of the
+			repo from \href{https://osf.io/cyk5w/files/github}{the osf copy} by
+			clicking ``Download this folder''.
+
+			\textbf{\large Reproducing this project}\label{reproducing-this-project}
+
+			The preregistration for this project is at https://osf.io/5qz7v
+
+			The overall manuscript can be reproduced by knitting
+			manuscript/manuscript.Rmd 
+			\begin{itemize}
+				\tightlist
+				\item 
+				This file reads data from
+				data/combined\_data.csv and data/boyce\_2023\_data.csv
+				\item  
+				This file uses
+				code/helper/parse\_stats.R
+			\end{itemize}
+
+			\textbf{data/combined\_data.csv has links to the write-ups,
+				pre-registrations, and projects (code/data) for the replications and
+				rescues.} Additionally, the project repos are contained in
+			first-replication-projects and individual-rescue-projects. Archival
+			copies of the write-ups are in first-replication-reports and
+			individual-rescue-reports (download/clone the repo and then open the
+			html files in a web browser to view them).
+
+			The numeric results in data/combined\_data.csv (effect size measures,
+			sample sizes, number of trials) were coded off of the papers and
+			reports. Where the effect size measures were not presented in the needed
+			format, recalculations were done (see reconstruct\_effect\_sizes for
+			data and code for these).
+
+			\textbf{\large Folder structure}\label{folder-structure}
+
+			\textit{Code}\label{code}
+
+			\begin{itemize}
+				\tightlist
+				\item
+				initial\_criteria.R describes the process for determining which
+				projects were eligible for rescue
+				\item
+				process.Rmd is a draft analysis script
+
+				\begin{itemize}
+					\tightlist
+					\item
+					it pulls the coded data from our google sheet and merges it with
+					study-level variables from Boyce 2023 replication data to write
+					data/combined\_data.csv
+					\item
+					it checks that we don't have parsing errors in our data format
+					\item
+					it does analyses (those in the manuscript have their analysis
+					duplicated in manuscript/manuscript.Rmd)
+				\end{itemize}
+				\item
+				helper/parse\_stats.R parses our raw effect size format and calculates
+				standardized effect sizes and helper/stats.R wraps p\_original and
+				prediction\_interval functions (used by process.Rmd but not
+				manuscript.Rmd)
+			\end{itemize}
+
+			\textit{Data}\label{data}
+
+			\begin{itemize}
+				\tightlist
+				\item
+				combined\_data.csv is the raw data coding sheet with links to
+				pre-registrations, etc
+				\item
+				parsed\_data.csv is a saved intermediate that has the results of
+				parsing effect sizes and computing standardized effect sizes
+				\item
+				boyce\_2023\_data.csv is a copy of data from
+				\href{https://royalsocietypublishing.org/doi/full/10.1098/rsos.231240}{Boyce
+					et al 2023} which reports on the first replications
+			\end{itemize}
+
+			\textit{Manuscript}\label{manuscript}
+
+			\begin{itemize}
+				\tightlist
+				\item
+				manuscript.Rmd is the manuscript, with analysis code embedded
+				\item
+				manuscript.pdf is the result of knitting manuscript.Rmd
+				\item
+				251rescue.bib is the bibliography
+				\item
+				apa7.csl, generic\_article\_template.tex are helper files for
+				formatting the manuscript
+				\item
+				coverletter/, title\_page.Rmd, and manuscript\_anon.Rmd are leftovers
+				of the submission process
+			\end{itemize}
+
+			\textit{First-replication-projects and
+				Individual-rescue-projects}\label{first-replication-projects-and-individual-rescue-projects}
+
+			\begin{itemize}
+				\tightlist
+				\item
+				include the individual replication and rescue projects (aka github
+				repos) respectively
+				\item
+				the rescue projects repos have been checked and include data,
+				code/reproducible report, and the materials to run the experiment
+			\end{itemize}
+
+			\textit{First-replication-reports and
+				Individual-rescue-reports}\label{first-replication-reports-and-individual-rescue-reports}
+
+			\begin{itemize}
+				\tightlist
+				\item
+				archival copies of the reports from individual projects, in case the
+				rpubs links break or are overwritten
+				\item
+				to view, download the repo and open the html files in a browser
+			\end{itemize}
+
+			\textit{reconstruct\_effect\_sizes}\label{reconstruct_effect_sizes}
+
+			In a few cases, the effect size information we needed for comparable
+			SMDs was not available from published papers or project write-ups, and
+			we had to construct it. 
+			\begin{itemize}
+				\tightlist\item schectman\_es.Rmd calculates the effect size
+			for the original
+			\href{https://www.ncbi.nlm.nih.gov/pmc/articles/PMC6634660/}{Schechtman
+				et al.} The original paper reports a p-value but not exact values, but
+			the authors were kind enough to send their matlab data files. This uses
+			the three DataTest.mat files. Additionally, we looked at the
+				rescue data to recalculate trial counts
+				(subject\_data\_final\_full\_processed.csv) 
+				\item 
+			\href{https://www.pnas.org/doi/pdf/10.1073/pnas.2202657119}{Denis et al}
+			is an additonal replication of Payne et al 2008; however the analysis
+			reported in the paper is not the same as the analysis Payne et al used.
+			Luckily data was available, so we calculate the corresponding result in
+			denis\_es.Rmd using data in Expt1\_OverallRecognition.csv and
+			Expt1\_SpecificRecognition.csv. 
+			\item  For Hopkins et al, the main effect of
+			interest is a coefficient in a linear model. However, coefficients
+			cannot be converted to SMD easily, so we calculate the mean and sds
+			instead in hopkins\_es.Rmd. The original data is in hopkins\_raw.csv,
+			the replication and rescue data is sourced from their github repos.
+		\end{itemize}
+
+			\textit{So you want to rescue a project
+				\ldots{}}\label{so-you-want-to-rescue-a-project}
+
+			\begin{itemize}
+				\item
+				this is a copy of a list of potential reasons for replication failures
+				shared with the rescuers in the early stages of the rescues
+			\end{itemize}
+		}
 
@@
 
-		As we now clarify in the updated README, these are archival copies of the reports (which were posted to Rpubs).
+		As we now clarify in the updated README (quoted above), these are archival copies of the reports (which were posted to Rpubs).
 From a cloned/downloaded copy of the repo, the html files can be opened in a browser to see the reports.
-
-		% \revised{\begin{verbatim}
-		 %		### First-replication-reports and Individual-rescue-reports
-		 %		* archival copies of the reports from individual projects, in case the rpubs links break or are overwritten
-		 %		* to view, download the repo and open the html files in a browser
-
-		 %	\end{verbatim}}
 
@@
 		The manuscript is written in an Rmd file that is reproducible.
-Each of the individual rescue projects was also written in a Rmd or qmd reproducible report (included in the individual project repos included in individual-rescue-projects/).
+Each of the individual rescue projects was also written in a Rmd or Qmd reproducible report (included in the individual project repos included in individual-rescue-projects/).
 We have now clarified this in the README.
-
-	%	\revised{ \begin{verbatim}
-	%		The overall manuscript can be reproduced by knitting manuscript/manuscript.Rmd
-	%		* This file reads data from data/combined_data.csv and data/boyce_2023_data.csv
-	%		* This file uses code/helper/parse_stats.R \end{verbatim}}
-
-	%	\revised{\begin{verbatim}
-	%			### First-replication-projects and Individual-rescue-projects
-	%		* include the individual replication and rescue projects (aka github repos) respectively
-	%		* the rescue projects repos have been checked and include data, code/reproducible report, and the materials to run the experiment\end{verbatim}}
 
@@
 
-		%TODO bug students whose stuff wasn't all there
-
 		\theysaid{Focus on the qualitative data}
@@
 
-		We agree that the frustration of original materials not being available or original instructions not being available is education and hopefully serves as an impetus for more sharing.
+		We agree that the frustration of original materials not being available or original instructions not being available is educational and hopefully serves as an impetus for more sharing.
 
@@
 
-		 %TODO extend the case study
+		 %TODO update after MS is potentially revised
 
-		 We thank the reviewer for this idea.
-We have added brief mentions of the topics and outcomes of each of the studies.
+		 We thank the reviewer for this idea. We have added an Appendix with brief descriptions of the topics and outcomes of each of the studies.
+
 		  We disagree about the ordering, as some readers may be more interested in the bottom line overall results than the individual studies.
-To support the different tastes, we have added an overview of subsections at the beginning of results so that interested readers could skip to the casestudies if desired.
 
-		 %TODO add mention of the casestudies existance
+		 The contents of the Appendix is now as follows:
+
+		 \revised{
+
+		 	Write-ups of individual rescue and replication projects can be found in the repository at \url{https://osf.io/cyk5w/}.
+		 	\newline
+
+		 	Birch \& Bloom (2007) is about a false belief task comparing ignorance and plausible knowledge conditions.
+		 	The first replication and an additional class replication both found results in the same direction as the original result, but much smaller.
+		 	The rescue used a much larger sample size than both the original and the first replication and added an additional check to make sure the probabilities participants reported add up to 100\%.
+		 	The rescue result was in the same direction as the original and prior replications, but did not find a significant effect.
+		 	\newline
+
+		 	Chou et al.
+(2016) studied whether a sense of control affects how much one feels physical pain.
+Participants were asked to recall experiences where they had either a low or high amount of control and then to report their level of physical pain.
+The first replication closely followed the methods of the original, but added a manipulation check borrowed from a different experiment in Chou et al.
+(2016).
+The manipulation check was successful, but there were no significant difference in pain level between the two groups.
+The rescue added pre-survey questions about pain levels to confirm that participants in the two groups had the same baseline understanding of pain.
+The rescue also did not find a significant difference in pain level between groups.
+		 	\newline
+
+		 	Craig \& Richeson (2014) had White Americans read an article about shifting racial demographics in the US, either with or without a framing that assuaged the potential threat, and found that reading the un-assuaged version led to the endorsement of more conservative positions.
+		 	The first replication did not find a significant difference between conditions, and the rescuer speculated that this was due to a smaller sample size and a skew toward liberal political beliefs in the participant pool.
+		 	The rescue recruited the same number of participants as the original study and dropped one of the conditions to increase power.
+		 	Despite the increased power, the rescue did not replicate the original paper's finding.
+		 	\newline
+
+		 	Gong et al.
+(2019) looked at the interplay between age and willingness to donate in older adults in Hong Kong and found a three-way interaction between age, type of donation, and relationship to recipient.
+		 	The first replication sampled US adults and did not find a significant interaction.
+		 	The rescuer thought that cultural differences may have played a role and specifically sampled Asian American adults.
+		 	The rescue did not recover the interaction.
+		 	\newline
+
+		 	Haimovitz \& Dweck (2016) manipulated parents' mindsets with ``failure-is-enhancing'' or ``failure-is-debilitating'' primes and looked at their reactions to a hypothetical situation in which a child received a failing grade.
+		 	The first replication found a point estimate in the opposite direction to the original effect, but an additional class replication found a directionally consistent effect.
+		 	The rescue added manipulation checks which were not present in the original study or either replications.
+		 	The manipulation checks passed, but the rescue study did not recover the target effect.
+		 	\newline
+
+		 	Hopkins et al.
+(2016) examined whether people prefer reductive explanations, which explain a result in one science with a more ``fundamental'' science, to horizontal explanations, which explain a result in one science in terms of the same science.
+		 	While the original study found a preference for reductive explanations, the first replication did not.
+		 	The replication's effective sample size was smaller than the original because a large proportion of participants failed the attention check.
+		 	The rescue increased made the attention check slightly easier and recruited a larger sample to account for failures, but still did not replicate the original effect.
+		 	\newline
+
+		 	Jara-Ettinger et al. (2022) looked at shape bias in US adults across 3 shape exemplars and found a preference to extend nouns on the basis of shape rather than color or material.
+		 	The replication found an above-chance preference for shape, but with very high item-level variability.
+		 	The rescuer found that the first replication used stylized versions of the original stimuli taken from a different part of the paper.
+		 	The rescue used the same images of stimuli as the original, but still found strong item-level effects and relative preferences for color and material.
+		 	\newline
+
+		 	Paxton et al.
+(2012) found that participants who completed the Cognitive Reflection Test (CRT) before the moral judgement task gave more utilitarian answers than those who did the moral judgment task before the CRT.
+		 	The replication rewrote some of the CRT questions, adding a sub-condition where some of the questions featured characters with specific names.
+		 	The first replication failed to find an effect.
+		 	The rescuer removed the sub-condition and used questions from the CRT-2, out of concern that Prolific participants would be familiar with the original CRT questions.
+		 	The rescue also failed to find the effect.
+		 	\newline
+
+		 	Porter et al. (2016) looked at how linguistic intergroup bias influences judgments of shared group membership.
+		 	The first replication found an effect directionally inconsistent with the original result.
+		 	The rescuer obtained the direct wordings of the questions from the authors of the original paper, and noticed that they were substantially different from questions in the first replication.
+		 	The rescue used the same wordings as the original paper and replicated the effect, although the manipulation check failed.
+		 	\newline
+
+		 	Schechtman et al. (2010) looked at how widely people generalize tones that previously have been paired with losses or gains, and found that the loss-paired tones were generalized more.
+		 	The first replication found a statistically significant effect in the opposite direction of the original study.
+		 	It also found that people took much longer to learn which tones were associated with gains vs.~losses compared to the original.
+		 	The rescuer made several changes, including asking questions about the sound quality of the participant's computer.
+		 	The original study was conducted in person while the replication and rescue were online, so differences in speaker and headphone quality might have played a role in the different result.
+		 	The rescue found an effect in the same direction as the 1st replication (contrary to the original study).
+		 	\newline
+
+		 	As discussed in methods, Tarampi et al.
+(2016) had participants do a timed navigation task and found an interaction between participant gender and the framing of the task (social or spatial) on performance.
+		 	The result from the first replication was both statistically insignificant and directionally inconsistent.
+		 	The original study was conducted in person, while the replication was conducted online, which might have contributed to the inconsistency.
+		 	The rescue was also conducted online, but the rescuer made a series of user interface changes, a comprehension check, and exclusion criteria to ensure that participants understood the instructions, found the task convenient to interact with, and were engaged throughout the experiment.
+		 	Still, the rescue did not recover the interaction.
+		 	\newline
+
+		 	Todd et al. (2016) looked at participants speed at classifying toys and guns as a function of whether they had just need a White or Black boy's face.
+		 	Todd et al. (2016) found an interaction where Black faces primed faster ``gun'' responses and White faces faster ``toy'' responses.
+		 	When we reached out to the original authors, they offered to run a parallel rescue on their student subject pool, which we have here as an additional replication.
+		 	The first replication did not find the interaction, but both the better-powered rescue and the original authors' replication did.
+		 	\newline
+
+		 	Yeshurun \& Levy (2003) looked at the relationship between spatial attention and temporal resolution.
+		 	They measured the threshold where two flashes of light are perceived as one flash versus two as a function of whether the location of the flashes was pre-cued or not.
+		 	Yeshurun \& Levy (2003) found that cueing led to less temporal resolution.
+		 	This was independently replicated by Chica \& Christie (2009), but was not replicated by either the student replication or the rescue.
+		 	Both the replication and rescue used in-person participants because the study relies on precise timing and details of the screen which are difficult to control online.
+		 	The first replication had a smaller sample size than the original, while the rescue matched the original study's sample size.
+
+		 }
 

### 2024-08-08 manuscript/manuscript.Rmd
work on response letter

@@
 In general, we encouraged students to add manipulation checks as appropriate, and to adapt their materials to online studies, which may benefit from attention checks and/or shorter duration.
-For instance, the rescue of @paxton2012 switched from using the Cognitive Teflection Test (CRT) which many online participants are over-familiar with to using the newer CRT-2 which is less overused but attempts to measure the same construct [@thomson2016].
+For instance, the rescue of @paxton2012 switched from using the Cognitive Reflection Test (CRT) which many online participants are over-familiar with to using the newer CRT-2 which is less overused but attempts to measure the same construct [@thomson2016].
 The rescue of @jara-ettinger2022 discovered that the replication had accidentally used an illustrated version of the stimuli rather than the photographic stimuli used in the original and used the photographic stimuli instead.

### 2024-08-08 manuscript/manuscript.tex
work on response letter

@@
 For instance, the rescue of Paxton et al.
-(\citeproc{ref-paxton2012}{2012}) switched from using the Cognitive Teflection Test (CRT) which many online participants are over-familiar with to using the newer CRT-2 which is less overused but attempts to measure the same construct (\citeproc{ref-thomson2016}{Thomson \& Oppenheimer, 2016}).
+(\citeproc{ref-paxton2012}{2012}) switched from using the Cognitive Reflection Test (CRT) which many online participants are over-familiar with to using the newer CRT-2 which is less overused but attempts to measure the same construct (\citeproc{ref-thomson2016}{Thomson \& Oppenheimer, 2016}).
 The rescue of Jara-Ettinger et al.

### 2024-08-09 manuscript/coverletter/collabra_response.tex
work on response letter

@@
 Perhaps this is from a misconception of who we are talking about when we talk about students (perhaps due to differences in training in different areas).
+
 		To clarify, these were replications done primarily by first year PhD students at an elite US institution.
 Many publications (including in top journals) are in fact done by PhD students, under the supervision of professors.
-We checked the google scholars of the rescuers here and 7/17 of them (40\%) already had peer-reviewed journal publications, in some cases multiple.
+We checked the google scholars of the rescuers here and 7/17 of them (40\%) already had peer-reviewed journal publications, several of which were first-authored.
 These students are or will soon be publishing in the literature.
 We agree that they may not have extensive expertise, but we think they and thus their rescue projects are reasonably representative of work by early career researchers with limited resources.
+
+		Since ``student'' can bring to mind different populations for different people, we have clarified in our limitations section who the rescuers were and how we think this is likely to generalize to other early career researchers (i.e.
+many of the people conducting research) but may not generalize to experts.
+
+		The limitations section reads:
+
+		\revised{
+			The reported rescue projects are a small sample of replications, leading to highly uncertain estimates.
+			Additionally, they were chosen non-randomly, as they were doubly selected for based on student interest -- once for the original replication and again for the rescue.
+			However, this selection bias is likely to correlate with how graduate students and other early career researchers choose what topics to work on and what studies to build on.
+			Nevertheless, our estimate is still broadly consistent with that of ManyLabs 5 (29\% vs.~22\%, Ebersole et al., 2020).
+			\newline
+
+			One potentially salient limitation of our work here is that the rescue projects (and the first replications) were primarily conducted by first year PhD students; hence the generality of our conclusions to other investigators is unknown.
+We believe, however, that this is more of an apparent than an actual limitation.
+Students were enrolled in a highly-competitive graduate program where it is expected that PhD students author peer-reviewed papers; several of the rescuers already had published first-authored peer reviewed articles.
+Thus, while we refer to the rescuers as students, they are investigators doing experiments that become part of the literature.
+			\newline
+
+			Students conducting rescue projects put substantial effort into trying to set up rescues that had a good chance of success, but projects were constrained by budget limitations, a short timeline, and the constraint that most data collection needed to occur online.
+Additionally, while most students had done research before and were learning best practices for experiments, they were not experts in the particular paradigms they were implementing.
+These limitations are representative of the sort of knowledge and resource limitations often faced by early-career researchers.
+That said, it is possible that different results might be obtained in better-resourced settings, by scientists with more expertise, more time, or more privileged knowledge about how the original experiments were conducted.
+			\newline
+
+			Due to the limited number of replications that are conducted and systematically reported, and the even smaller number of re-replications reported, there is substantial uncertainty in how much replicability varies across features of the original experiment and replications.}
 
@@
 		The original replications were performed under limitations, such as time limits and online samples, which we acknowledge, but which we believe is common when early career researchers build on existing work.
+They may be limited in what resources (time, money, access to populations) are available, and so what results are accessible to them is relevant.
 
-		As for when original materials aren't available, when they aren't available, the replications are as close as they can be, which may be not very close.
-Replicators did what they could given the external constrain of unavailable materials.
-
-		[TODO not really sure what to say here]
+		As for when original materials aren't available, the replications are as close as they can be, which may be not very close.
+Replicators did what they could given the external constraint of unavailable materials.
 
@@
 
-		[TODO not sure what to do here]
+		The idea behind 2.5x sample size is that it gives the replication an 80\% chance of correctly rejecting the null hypothesis of an effect that the original was 33\% powered for.
+This standard has the convenience of being agnostic to the type of experiment and test being conducted (unlike calculating effect sizes or calculating power, which both can be difficult and very sensitive to design).
+This 2.5x is a target for answering is there an effect big enough for the original study to have reasonably detected.
 
@@
 two main effects and their interaction).
-Thus we think the holistic, subjective assessment of whether or not a study replicated is important, although we also do analyze the key effect as well.
+Thus we think the holistic, subjective assessment of whether or not a study replicated is important, although we also do analyze a key effect as well.
 
@@
 
-		As we write the in the methods section, ``Each project was rated on the basis of subjective replication success (on a 0--1 scale) by both MCF and one of VB and BP.
+		As we wrote the in the methods section, ``Each project was rated on the basis of subjective replication success (on a 0--1 scale) by both MCF and one of VB and BP.
 		We thought about replication in terms of general match in key study results (direction, magnitude, and significance), rather than focusing on any singular numeric result or significance cut-off.''
@@
 
-		Whether a replication is statistically significant in the same direction as the original is one metric that is sometimes used as a measure of replicability, but as TODO CITE SOME PEOPLE SAYING THIS IS DUMB.
-Patil 2016, Simonsohn 2015, ANdrews and Kasy 2019 are potential cites here!
+		Whether a replication is statistically significant in the same direction as the original is one metric that is sometimes used as a measure of replicability, but as noted by Patil et al 2016 (doi.org/10.1177/1745691616646366), it isn't a very good one as differences in where $p<.05$ can arise from sampling variation.
 
@@
 
-		The effect sizes shown are SMDs, but in order to show everything on the same scale, we had to force everything onto that scale, even if it required a lot of conversions requiring approximations.
+		The effect sizes shown are SMDs, but in order to show the effects on the same scale, we had to coerce all the numbers onto the same scale, even if it required approximations as part of the conversions.
 For assessing individual studies it makes more sense to look at their raw results, rather the converted results.
@@
 Thus, we know that students had working implementations of the studies because the TAs went through every experiment and gave feedback.
-Additionally, students had to have working code that ran on their pilot data before they were approved for data collection.
+Additionally, students had to have working code that ran on their pilot data before they were approved for running the main data collection.
 We also know that the students ran studies on the class Prolific account because we can see how many participants were recruited and paid for each study.
@@
 
-		Thanks for this suggestion. In our added case study expansion, we now mention the additional studies and where they come from, citing those from the published literature.
-
-		%TODO this ^
+		Thanks for this suggestion.
+In the case study section and the appendix, when we describe studies where there were additional replications, we now mention the additional studies and where they come from, citing those from the published literature.
 
@@
 
-		I think there may be a misunderstanding here -- we aren't doing meta-analyses because we aren't interested in the aggregate effect size across the original and replications.
+		I think there may be a misunderstanding here -- we aren't doing meta-analyses in order to aggregate effect size across the the original and replications.
 
-		When we discuss the "meta-analytic" mean of some studies that is because the measures of consistency we use (p-original) is between two things, so to compare more than two, some have to be pooled (which does make use of meta-analysis to do the pooling to get an aggregate mean and spread).
+		When we discuss the ``meta-analytic'' mean of some studies that is because the measures of consistency we use (p-original) is between two things, so to compare more than two, some have to be pooled (which does make use of meta-analysis to do the pooling to get an aggregate mean and spread).
 As described in Mathur and VanderWeele 2020 (https://rss.onlinelibrary.wiley.com/doi/full/10.1111/rssa.12572) which introduces the statistic of p-original, it uses the point estimate and standard error of the original compared to the average population effect size in the replications and standard error thereof.
@@
 
-		As we are only interested in studies that are direct replications of the original, we think we got them. 
-		%TODO how to navigate this s
+		Students did search for direct replications of the studies, which if they are in the published literature are likely to be found.
+It is possible that there happen to be direct replications that aren't labeled as such that we could have missed, and of course, there could be unpublished or grey literature replications.
 
-		%TODO add
-		We understand the concern about wanting to see just the replication and rescue, so we have added a column to TABLE TODO with this.
+		We understand the concern about wanting to see just the replication and rescue, so we have added a column to Table 1 with this information.
+
+		New Table 1 shown below:
+
+			\begin{tabular}[t]{lrrrrr}
+				\toprule
+				\multicolumn{1}{c}{ } & \multicolumn{5}{c}{p-original comparing between} \\
+				\cmidrule(l{3pt}r{3pt}){2-6}
+				\multicolumn{1}{c}{ } & \multicolumn{4}{c}{Original and} & \multicolumn{1}{c}{Rescue and} \\
+				\cmidrule(l{3pt}r{3pt}){2-5} \cmidrule(l{3pt}r{3pt}){6-6}
+				Paper & All reps & 1st Rep and Rescue & Rescue & Non-rescue & Other reps\\
+				\midrule
+				Birch \& Bloom 2007 & 0.192 & 0.189 & 0.194 & 0.191 & 0.989\\
+				Child et al. 2018 & 0.669 & 0.669 & 0.641 & 0.858 & 0.778\\
+				Chou et al. 2016 & 0.055 & 0.055 & 0.101 & 0.005 & 0.231\\
+				Craig \& Richeson 2014 & 0.145 & 0.145 & 0.001 & 0.302 & 0.020\\
+				Gong et al. 2019 & 0.262 & 0.262 & 0.057 & 0.511 & 0.228\\
+				Haimovitz \& Dweck 2016 & 0.068 & 0.018 & 0.018 & 0.180 & 0.867\\
+				Hopkins et al. 2016 & 0.290 & 0.290 & 0.654 & 0.004 & 0.015\\
+				Jara-Ettinger et al. 2022 & 0.014 & 0.014 & 0.000 & 0.006 & 0.000\\
+				Krauss \& Wang 2003 & 0.271 & 0.271 & 0.519 & 0.139 & 0.311\\
+				Ngo et al. 2019 & 0.106 & 0.000 & 0.000 & 0.385 & 0.257\\
+				Paxton et al. 2012 & 0.011 & 0.011 & 0.005 & 0.023 & 0.649\\
+				Payne et al. 2008 & 0.023 & 0.071 & 0.031 & 0.079 & 0.895\\
+				Porter et al. 2016 & 0.370 & 0.370 & 0.905 & 0.002 & 0.003\\
+				Schechtman et al. 2010 & 0.712 & 0.712 & 0.654 & 0.770 & 0.877\\
+				Tarampi et al. 2016 & 0.000 & 0.000 & 0.000 & 0.000 & 0.145\\
+				Todd et al. 2016 & 0.062 & 0.100 & 0.124 & 0.058 & 0.778\\
+				Yeshurun \& Levy 2003 & 0.614 & 0.007 & 0.017 & 0.943 & 0.474\\
+				\bottomrule
+			\end{tabular}
 
@@
 
-		 Again, it seems like there may be confusion here -- the "p-values" presented here are "p-original" which is p-value like in that it's a measure of how likely an estimate would be to be at least as extreme as observed given a "null" distribution.
+		 Again, it seems like there may be confusion here -- the ``p-values'' presented here are ``p-original'' which is p-value like in that it's a measure of how likely an estimate would be to be at least as extreme as observed given a ``null'' distribution.
 It is a measure of statistical (in-)consistency on the effect sizes, not a measure of how close to zero the effect sizes are.
@@
 
-		We apologize for this oversight and have added to the caption short descriptions for these two as well as a cross reference to where the predictors are discussed at length in Boyce et al 2023.
+		We apologize for this oversight. We have changed these row names to ``Original authors at Stanford'' and 
+		``Log number of trials''.
+We have also amended the caption to clarify the reason for Stanford being relevant as well as provide a reference to where the predictors are discussed at length in Boyce et al 2023.
+The revised caption reads:
 
-		%TODO DO THIS 
+		\revised{Correlations between an individual predictor and the subjective replication score of the rescue project.
+The first set of predictors were pre-registered based on the correlates used in Boyce et al.
+(2023).
+Original authors at Stanford refers to at the time of the first replication as this may mean the first replication was not independent.
+For details about how the predictors were coded, see the Methods section of Boyce et al.
+(2023).
+The last three predictors were added post-hoc.}
+
 		\theysaid{It is the open science collaborations, not consortium.}
 
-		%TODO FIX
 		Oops, thank you for bringing this to our attention, we have fixed it.
@@
 
-		This point is well taken and we have expanded our discussion to acknowledge the larger space of factors and decisions at play with replications and rescues and the motivations to do them. 
-		%TODO make not suck
+		This point is well taken and we have expanded our discussion to acknowledge the larger space of factors at play with replications and rescues and the motivations to do them.
+
+		The concluding part of the discussion now reads:
+
+		\revised{Overall, the diminished and inconsistent effects we found in the rescues suggest that even if a re-replication ``works'', it may be difficult to build upon as follow-up studies will need large samples to detect small effects.
+			\newline
+
+			We have focused here on a narrow type of replication and rescue: that done by an early career researcher with the goal of establishing whether this is a result \emph{they} can build on.
+We acknowledge that this type of replication exists as part of a wider ecosystem of replications that have different properties and are done for different reasons.
+			\newline
+
+			In many cases, researchers may have strong prior beliefs about where a replication will succeed, and these priors may influence a researchers interpretation of a failed replication, and thus their calculations about where a re-replication will succeed or is worth attempting.
+For instance, a researcher who has high credence in the main result is more likely to attribute failure to specific details in the replication, and thus may want to do a rescue where those details are adjusted.
+On the other hand, a researcher who is dubious of the methods, results, or statistical approaches in an experiment, or who has previously failed to extend the experimental result, may be quicker to interpret a non-replication as a more definitive negative result.
+What a researcher chooses to do may also depend on the perceived strength of the replication, what size effects they think are relevant, and how important they think the target effect is.
+Thus, in some cases, when to re-replicate may be a question of prior beliefs and perceived utility rather than just likelihood of a re-replication succeeding.
+			\newline
+
+			We opened with a question about what an early-career psychology researcher should do given a failed replication: should they try again or give up and move on?
+			In our sample, the odds of a re-replication working are low (consistent with Ebersole et al., 2020).
+			Especially if there is not a clear, identifiable candidate cause for replication failure, it may be more efficient to select another result to build on.
+		}
 
@@
 
-		%TODO FIX
-		We have clarified this. 
+		Thank you for this point, we have now clarified that what we meant was had a confidence interval not overlapping 0. The caption now reads
+
+		\revised{Standardized effect sizes of original studies, first replications, rescues, and additional replications if available.
+Due to the large effect size of a couple studies, large effect studies are shown in a separate panel.
+In a few cases, the first replication's key effect was in the same direction as the original with a 95\% CI that did not overlap 0; however, in these cases the larger pattern of results was not consistent between original and first replication.
+}
+
 		\theysaid{So in general, I think this is a neat little paper, which, in my opinion, could benefit from adding a little bit more discussion/depth in the end on what its outcomes could entail.}
@@
 
-		We again would like to thank both the editor and the reviewers for their thoughtful and prompt reviews.
+		We would like to reiterate our thanks both the editor and the reviewers for their thoughtful and prompt reviews.
 We hope that our changes to the manuscript and the documentation of our repository offer the necessary clarifications and nuance.

### 2024-08-09 manuscript/coverletter/collabra_response.tex
Mike's edits, some linking

--- 2024-08-08 manuscript/coverletter/collabra_response.tex
@@
 
-\makelabels
+%\makelabels
 \usepackage{todonotes}
@@
 \DeclareLanguageMapping{american}{american-apa}
-%\bibliography{../draft0}
 \newcommand{\citet}[1]{\textcite{#1}}
@@
 
+\usepackage{longtable,booktabs,array}
+\usepackage{float}
+
+\providecommand{\tightlist}{%
+	\setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
+
+\newcounter{section}
+
+\newcommand{\section}[1]{
+	\bigskip
+	{\normalfont\Large\bfseries #1}}
+
 \newcommand{\theysaid}[1]{\begin{leftbar} \noindent 
 		\textsl{ #1}\end{leftbar}}
+
 \newcommand{\revised}[1]{\begin{quote}	#1 \end{quote}}
 
-\usepackage{longtable,booktabs,array}
-\usepackage{float}
+\usepackage{hyperref}
 \begin{document}
@@
 
+		We would like to reiterate our thanks both the editor and the reviewers for their thoughtful and prompt reviews.
+We hope that our changes to the manuscript and the documentation of our repository offer the necessary clarifications and nuance.
+
+		\closing{Sincerely,}
+
+	\section{Editor}
+
 	\theysaid{To summarize what I perceive to be the main points of attention:}
@@
 
-		I also address some of reviewer 1's specific repo-related concerns below; I suspect many of them would have been ameliorated had the reviewer been able to download the repo.
+	We also address reviewer 1's specific repository-related concerns more below; we suspect many of them would have been ameliorated had the reviewer been able to download the repository files (which, as noted below, are likely due to a known technical issue with github and Windows systems).
 
@@
 
-		We have expanded the discussion section and re-organized it to have a more explicit discussion of limitations.
+	We have added an explicit ``Limitations'' subsection to the discussion, which we discuss further below in our response to reviewer 1.
 
-		Thank you for the reference, which we have incorporated, and we have included more information on the changes to the discussion below, in our response to reviewer 1.
-
-		Also, see below for our changes and rebuttals to reviewer 1's thoughts.
+	Also, see below for our changes and rebuttals to reviewer 1's other points.
 
@@
 
-		%TODO discussion section
-		We have expanded the discussion section to discuss the larger picture of different circumstances that motivate replications and rescues.
+	We have expanded the last part of the discussion section to acknowledge the much larger picture of different circumstances that motivate replications and rescues, and how these might be influenced by the prior beliefs of the investigators.
 We discuss the changes more below in response to reviewer 2's points.
@@
 
-		\theysaid{Reviewer 1}
+	\section{Reviewer 1}
 
-		\theysaid{The authors report the result of replication studies performed as part of an educational project.
+	% \theysaid{The authors report the result of replication studies performed as part of an educational project.
 The results vary – some are relatively similar, of clear null replications, but others show a surprising amount of variability, possibly due to time and resource constraints, or a lack of experience.
@@
 
-		\theysaid{Data needs to be shared in a reproducible manner}
+	% \theysaid{Data needs to be shared in a reproducible manner}
 	\theysaid{Regrettably I could not download the files from github – some filenames that have been uploaded are too long, and both cloning the repo as downloading at a zip file give errors (on my windows machine).
@@
 	We are sorry this error occurred, and that reviewer 1 didn't realize the files could be downloaded directly from the OSF copy (linked in the paper).
-as the inability of reviewer 1 seems to have resulted in misunderstandings about the usability of files in the repo (which are much more understandable when opened on a computer).
+The inability of reviewer 1 to download and open the files seems to have resulted in misunderstandings about the usability of files in the repo, which are much more understandable when opened on a computer.
 
-		From googling, we believe this to be a windows issue, and to prevent this problem for future users we have added a note at the top of the README directing readers for how to address or sidestep the problem, namely:
+	From googling, we believe the long files names issue to be a Windows issue, and to prevent this problem for future users we have added a note at the top of the README directing readers for how to address or sidestep the problem, namely:
 
-		\revised{Note: If you are a windows user and get an error about overly long file names, please see [this stackoverflow post](https://stackoverflow.com/questions/22575662/filename-too-long-in-git-for-windows) or [this github issue](https://github.com/desktop/desktop/issues/17882) for how to fix it.
-Alternatively, you can download a zip of the repo from [the osf copy](https://osf.io/cyk5w/files/github) by clicking "Download this folder".}
+	\revised{Note: If you are a windows user and get an error about overly long file names, please see \href{https://stackoverflow.com/questions/22575662/filename-too-long-in-git-for-windows}{this stackoverflow post} or \href{https://github.com/desktop/desktop/issues/17882} {this github issue} for how to fix it.
+Alternatively, you can download a zip of the repo from \href{https://osf.io/cyk5w/files/github}{the osf copy} by clicking "Download this folder".}
+
+	Hopefully this warning will prevent future difficulties with accessing the repository.
 
@@
 
-		We think the structure is actually pretty clear, but we apologize that the README was not more detailed.
+	We think the folder structure is actually pretty clear (e.g., \texttt{first-replication-projects} directory contains the first replication projects), but we apologize that the README was not more detailed.
 We have rewritten the README to be much more explicit about how to reproduce the paper as well as what all the folders and files contain.
 
-		See  https://github.com/langcog/251-rescue-projects/tree/main for the revised README.
+	See  \url{https://github.com/langcog/251-rescue-projects/tree/main} for the revised README.
 
@@
 
-		As we now clarify in the updated README, these are archival copies of the reports (which were posted to Rpubs).
-From a cloned/downloaded copy of the repo, the html files can be opened in a browser to see the reports.
+	As we now clarify in the updated README, these are archival copies of the reports, which were originally posted to the Rpubs sharing website.
+From a cloned/downloaded copy of the repo, the html files can be opened in any web browser to see the reports.
 
-		% \revised{\begin{verbatim}
-		 %		### First-replication-reports and Individual-rescue-reports
-		 %		* archival copies of the reports from individual projects, in case the rpubs links break or are overwritten
-		 %		* to view, download the repo and open the html files in a browser
+	\theysaid{In the process.Rmd file, data is downloaded from a google drive https://docs.google.com/spreadsheets/d/12A4DblSbX\_0tHP1mTVJhjNboI1YDngidkNWiSy0sN0g/edit\#gid=0 which I have no access to. }
 
-		 %	\end{verbatim}}
-
-		\theysaid{In the process.Rmd file, data is downloaded from a google drive https://docs.google.com/spreadsheets/d/12A4DblSbX\_0tHP1mTVJhjNboI1YDngidkNWiSy0sN0g/edit\#gid=0 which I have no access to.
-}
-
-		This is in an eval=F section, and process.Rmd both runs and knits without access to the file. However, to avoid future confusions, we have made the google spreadsheet openly viewable.
+	It is common in RMarkdown files to add sections for documentation that do not need to be run every time to reproduce the result.
+Such sections are often marked \texttt{eval=F} and they do not evaluate.
+The piece of code referenced above is in such a section.
+\texttt{process.Rmd} both runs and knits without access to the file.
+However, to avoid future confusions, we have made the google spreadsheet openly viewable.
 
@@
 
-		The manuscript is written in an Rmd file that is reproducible.
-Each of the individual rescue projects was also written in a Rmd or qmd reproducible report (included in the individual project repos included in individual-rescue-projects/).
+	We apologize for any confusion about organization, but the manuscript is indeed written in an Rmd file that is fully  reproducible and is available in the repository.
+Each of the individual rescue projects was also written in a Rmd or Qmd reproducible report (included in the individual project repositories that are included in \texttt{individual-rescue-projects/}).
 We have now clarified this in the README.
-
-	%	\revised{ \begin{verbatim}
-	%		The overall manuscript can be reproduced by knitting manuscript/manuscript.Rmd
-	%		* This file reads data from data/combined_data.csv and data/boyce_2023_data.csv
-	%		* This file uses code/helper/parse_stats.R \end{verbatim}}
-
-	%	\revised{\begin{verbatim}
-	%			### First-replication-projects and Individual-rescue-projects
-	%		* include the individual replication and rescue projects (aka github repos) respectively
-	%		* the rescue projects repos have been checked and include data, code/reproducible report, and the materials to run the experiment\end{verbatim}}
 
@@
 
-		%TODO bug students whose stuff wasn't all there
-
-		\theysaid{Focus on the qualitative data}
+	% \theysaid{Focus on the qualitative data}
 	\theysaid{It is interesting to see the results of these projects, as they show the messiness of results when quality control is less strict than in other replication projects.
@@
 
-		We agree that the frustration of original materials not being available or original instructions not being available is education and hopefully serves as an impetus for more sharing.
+	We agree that the frustration of original materials not being available or original instructions not being available is educational and hopefully serves as an impetus for more sharing.
 
@@
 
-		 %TODO extend the case study
+	%TODO update after MS is potentially revised
 
-		 We thank the reviewer for this idea.
-We have added brief mentions of the topics and outcomes of each of the studies.
-We disagree about the ordering, as some readers may be more interested in the bottom line overall results than the individual studies.
-To support the different tastes, we have added an overview of subsections at the beginning of results so that interested readers could skip to the casestudies if desired.
+	We thank the reviewer for this idea. We have added an Appendix with brief descriptions of the topics and outcomes of each of the studies.
 
-		 %TODO add mention of the casestudies existance
+	We disagree, however, about the ordering of quantitative and qualitative results.
+The quantitative results come directly from our preregistration and so should go first.
+In addition, we expect many readers will be more interested in the ``bottom line'' results than in the individual studies.
 
-		\theysaid{Be careful with generalizations}
+	% \theysaid{Be careful with generalizations}
 	\theysaid{In the conclusions the authors generalize beyond the context of students doing replications, to investigators doing replications.
@@
 
-		This reviewer seems to strongly distinguish between students and investigators.
-Perhaps this is from a misconception of who we are talking about when we talk about students (perhaps due to differences in training in different areas).
-To clarify, these were replications done primarily by first year PhD students at an elite US institution.
-Many publications (including in top journals) are in fact done by PhD students, under the supervision of professors.
-We checked the google scholars of the rescuers here and 7/17 of them (40\%) already had peer-reviewed journal publications, in some cases multiple.
-These students are or will soon be publishing in the literature.
-We agree that they may not have extensive expertise, but we think they and thus their rescue projects are reasonably representative of work by early career researchers with limited resources.
+	We appreciate the cautionary note, but we disagree about the generalizations that can be made from student work.
+In particular, the source of the disagreement may be the strong distinction the reviewer makes between between students and investigators.
+Perhaps this distinction comes from a misconception of who we are talking about when we talk about ``students,'' perhaps due to geographic or national differences in research training.
+
+	To clarify, the replication rescues we report were performed primarily by first-year PhD students at an elite US institution, with a few more senior PhD students as well.
+These students were supervised and their work was reviewed by senior PhD students with research methods expertise and by the faculty instructor of the course.
+This supervision arrangement intentionally mirrors how research is typically conducted, even down to the multiple presentations of their replication projects that students give to the class (mirroring review and discussion in lab meetings).
+We expect that the reviewer would agree that many publications are in fact produced in exactly this way -- by PhD students, under the supervision of professors.
+
+	We checked the google scholar pages of the student rescuers who are authors on our paper; 7/17 of them (40\%) already had peer-reviewed journal publications during the course, several of which were first-authored.
+These students are -- or will soon be -- publishing in the literature.
+We agree that they may not have extensive expertise, but we think they -- and thus their rescue projects -- are reasonably representative of work by early career researchers with limited resources.
+
+	Since ``student'' can bring to mind different populations for different people, we have clarified in our limitations section who the rescuers were and how we think this is likely to generalize to other early career researchers (i.e.
+many of the people conducting research) but may not generalize to experts.
 
@@
 
-		The original replications were performed under limitations, such as time limits and online samples, which we acknowledge, but which we believe is common when early career researchers build on existing work.
+	We disagree with the reviewer's characterization of our replication studies.
+There were some limitations for the original replications, including time limits and online samples.
+We believe these limits are common when early career researchers build on existing work: They may be limited in what resources (time, money, access to populations) are available, and so what results are accessible to them is relevant.
 
-		As for when original materials aren't available, when they aren't available, the replications are as close as they can be, which may be not very close.
-Replicators did what they could given the external constrain of unavailable materials.
+	As for when original materials aren't available, we believe that this limitation characterizes a vast amount of the replication literature.
+Unfortunately, materials availability is a severe issue.
+The extent to which this limitation affected our work is exactly the same as the extent to which it affects other investigators in non-student samples.
+Thus, if anything we would expect that this characteristic \emph{increases} the generality of our findings.
 
-		[TODO not really sure what to say here]
-
-		\theysaid{Experimental design of replication studies}
+	% \theysaid{Experimental design of replication studies}
 	\theysaid{The authors state they attempted to adequately power studies, but they refer to trying to achieve 2.5 times the sample size in the original study (ignoring the sample size and effect size in the replication study).
@@
 
-		[TODO not sure what to do here]
+	The idea behind 2.5x sample size is that it gives the replication an 80\% chance of correctly rejecting the null hypothesis of an effect that the original was 33\% powered for (see \href{https://doi.org/10.1177/0956797614567341}{Simonsohn, 2015, Psych Science}).
+This standard has the convenience of being agnostic to the type of experiment and test being conducted (unlike calculating effect sizes or calculating power, which both can be difficult to compute for complex designs and for cases where original data are not available).
+Per the Simonsohn proposal, the 2.5x multiplier is a target for answering the question, ``is there an effect big enough that the original study could have reasonably detected it.''
 
-		\theysaid{Subjective replication probability is unclear}
+	% \theysaid{Subjective replication probability is unclear}
 	\theysaid{The subjective replication probability coded as 0, 0.25, 0.75 and 1 is extremely confusing. It should be dropped.}
 
-		We disagree.
-This coding was used in the paper this is follow-up to (https://royalsocietypublishing.org/doi/full/10.1098/rsos.231240) because it was the coding done at the time of (most) of the original replications.
+	We apologize, but we are not sure what is confusing about a holistic, rating-based metric for replication success.
+Indeed, the Replication Project in Psychology (Open Science Collaboration, 2015) included in its outcomes a subjective replication score.
+The current coding scheme was used in the paper that the current paper builds on ( \href{https://royalsocietypublishing.org/doi/full/10.1098/rsos.231240}{Boyce et al 2023}) because it was the coding done at the time of (most of) the original replications.
 
-		There are many metrics for what counts as a successful replication, but many of them depend on a key-statistic.
-As discussed in Hawkins et al 2018 (https://journals.sagepub.com/doi/full/10.1177/2515245917740427) and Boyce et al 2023 (https://royalsocietypublishing.org/doi/full/10.1098/rsos.231240), original papers often report a number of effects, and it is not always clear which one is the most key.
-Additionally, often the pattern of interest is dependent on multiple numeric effects (ex.
+	There are many statistical metrics for what counts as a successful replication, including methods such as confidence interval overlap or the methods that we use in our quantitative results (e.g.
+p-original).
+The key issue with these measures is that they depend on the selection of a single key statistic for compariosn.
+As discussed in \href{https://journals.sagepub.com/doi/full/10.1177/2515245917740427}{Hawkins et al 2018} and Boyce et al 2023, original papers often report a number of effects, and it is not always clear which one is the most key.
+Additionally, often the theoretical pattern of interest -- as indicated by the authors -- is dependent on multiple numeric effects (ex.
 two main effects and their interaction).
-Thus we think the holistic, subjective assessment of whether or not a study replicated is important, although we also do analyze the key effect as well.
+Thus, although we also analyze a key effect as well, we think the holistic, subjective assessment of whether or not a study replicated is an important part of our analysis.
+
+	Finally, analysis of subjective replication ratings is one of our pre-registered analyses and so we do not believe it is appropriate to omit it.
 
@@
 
-		As we write the in the methods section, ``Each project was rated on the basis of subjective replication success (on a 0--1 scale) by both MCF and one of VB and BP.
+	We don't think this is a fair characterization of our rating scheme (which we have used in prior work, as discussed above).
+
+	As we wrote the in the methods section, ``Each project was rated on the basis of subjective replication success (on a 0--1 scale) by both MCF and one of VB and BP.
 	We thought about replication in terms of general match in key study results (direction, magnitude, and significance), rather than focusing on any singular numeric result or significance cut-off.''
@@
 
-		Whether a replication is statistically significant in the same direction as the original is one metric that is sometimes used as a measure of replicability, but as TODO CITE SOME PEOPLE SAYING THIS IS DUMB.
-Patil 2016, Simonsohn 2015, ANdrews and Kasy 2019 are potential cites here!
+	Whether a replication is statistically significant in the same direction as the original is one metric that is sometimes used as a measure of replicability, but, as noted by \href{https://journals.sagepub.com/doi/10.1177/1745691616646366}{Patil et al 2016}, it isn't a very good one: one study may have an effect size very similar to another but one might be p < .05 and the other might be p > .05.
 
@@
 
-		The effect sizes shown are SMDs, but in order to show everything on the same scale, we had to force everything onto that scale, even if it required a lot of conversions requiring approximations.
-For assessing individual studies it makes more sense to look at their raw results, rather the converted results.
+	Regarding Figure 1, the effect sizes shown are standardized mean differences (SMD; Cohen's $d$).
+In order to show effects on the same graph, we had to coerce all the numbers to be SMDs, even if this conversion required approximations (as in the case of the Krauss paper, where the results are proportions).
+For assessing the statistical significance of individual studies it makes more sense to look at their raw results, rather the CIs in Figure 1, which are approximately correct but not the best basis for inference.
 
-		\theysaid{Statistical analysis}
+	% \theysaid{Statistical analysis}
 	\theysaid{Upon first read I was not too enthusiastic about using a replication metric that incorporated heterogeneity.
@@
 
-		We are fairly confident that there is not fraud as a) committing fraud would have been strictly more work than not and b) students had no incentive to commit fraud.
+	We note that the heterogeneity metric has been used frequently to quantify variation in replication success, notably in \href{doi.org/10.1073/pnas.2403490121}{Holzmeister et al.
+(2024)}, which provides a framework for thinking about heterogeneity as stemming from population variation, design variation, and analytic variation.
+
+	Regarding other sources of heterogeneity, including error and fraud, we think these are relatively unlikely.
+First, while we did not recode student analyses from scratch, teaching assistants reviewed student code several times, and remarked on stylistic issues and potential errors.
+Further, most analyses were quite straightforward.
+
+	We are also quite confident that there is not fraud in our sample.
+Committing fraud would have been strictly more work than actually doing the work, and further, there was no incentive to do so.
 During the class, students submitted their projects for a number of checkpoints.
 Thus, we know that students had working implementations of the studies because the TAs went through every experiment and gave feedback.
-Additionally, students had to have working code that ran on their pilot data before they were approved for data collection.
+Additionally, students had to have working code that ran on their pilot data before they were approved for running the main data collection.
 We also know that the students ran studies on the class Prolific account because we can see how many participants were recruited and paid for each study.
-Thus, we know data was collected.
-Students knew that their grades in no way depended on what results they got (i.e.
+Thus, we know code was written, the experiment worked, and the data was collected.
+Students also knew that their grades in no way depended on what results they got (i.e.
 whether the study replicated), so had no incentive to change the data they had collected.
 
-		Finally, don't you think that if students were going to commit fraud, they'd make the study work better? Even the studies that did rescue had smaller effect sizes than the original studies.
+	Finally, don't you think that if students were going to commit fraud, they'd make their study work \emph{better}? Even the studies that did rescue had smaller effect sizes than the original studies.
 
-		We also have a larger sample of student replication studies conducted in previous years of the class, and these found a similar rate of replication as previous studies such as RP:P (see Boyce et al 2023).
+	Finally, regarding student error: in our prior work, we have a larger sample of 176 student replication studies, and these studies found a similar rate of replication as previous studies such as RP:P (see Boyce et al 2023).
+If error rates were substantially different, we'd expect lower replication.
 
@@
 
-		Thanks for this suggestion. In our added case study expansion, we now mention the additional studies and where they come from, citing those from the published literature.
-
-		%TODO this ^
+	Thanks for this suggestion.
+In the case study section and the appendix, when we describe studies where there were additional replications, we now mention the additional studies and where they come from, citing those from the published literature.
 
@@
 
-		I think there may be a misunderstanding here -- we aren't doing meta-analyses because we aren't interested in the aggregate effect size across the original and replications.
+	We think there may be a misunderstanding here -- we aren't doing meta-analyses in order to aggregate effect size across the the original and replications.
 
-		When we discuss the "meta-analytic" mean of some studies that is because the measures of consistency we use (p-original) is between two things, so to compare more than two, some have to be pooled (which does make use of meta-analysis to do the pooling to get an aggregate mean and spread).
-As described in Mathur and VanderWeele 2020 (https://rss.onlinelibrary.wiley.com/doi/full/10.1111/rssa.12572) which introduces the statistic of p-original, it uses the point estimate and standard error of the original compared to the average population effect size in the replications and standard error thereof.
+	When we discuss the ``meta-analytic'' mean of some studies that is because the measures of consistency we use (p-original) is a measure of the consistency of two things.
+Thus, to compare more than two replications, some have to be pooled; we use meta-analysis to do the pooling to get an aggregate mean and standard error.
+As described in \href{https://rss.onlinelibrary.wiley.com/doi/full/10.1111/rssa.12572}{Mathur and VanderWeele 2020}, which introduces the p-original statistic, we uses the point estimate and standard error of the original compared to the average population effect size in the replications and standard error thereof.
 As they mention, the most common way to get the average population effect size is via a random effects meta analysis.
 
-		\theysaid{ First, I do not like the addition of additional replications.
-No systematic search has been done, so these studies might differ in some ways, and bias the overal effect size estimate.
+	\theysaid{First, I do not like the addition of additional replications.
+No systematic search has been done, so these studies might differ in some ways, and bias the overall effect size estimate.
 These additional studies can be mentioned, but, we should also see meta-analytic effect sizes without these replications.This can easily be presented in a table with different columns.}
 
-		As we are only interested in studies that are direct replications of the original, we think we got them. 
-		%TODO how to navigate this s
+	Students did search for direct replications of the studies, which if they are in the published literature are likely to be found.
+It is possible that there happen to be direct replications that aren't labeled as such that we could have missed, and of course, there could be unpublished or grey literature replications.
 
-		%TODO add
-		We understand the concern about wanting to see just the replication and rescue, so we have added a column to TABLE TODO with this.
+	We understand the concern about wanting to see just the replication and rescue, so we have added a column to Table 1 with this information.
+
+	% New Table 1 shown below:
+
+	% 	\begin{tabular}[t]{lrrrrr}
+		% 		\toprule
+		% 		\multicolumn{1}{c}{ } & \multicolumn{5}{c}{p-original comparing between} \\
+		% 		\cmidrule(l{3pt}r{3pt}){2-6}
+		% 		\multicolumn{1}{c}{ } & \multicolumn{4}{c}{Original and} & \multicolumn{1}{c}{Rescue and} \\
+		% 		\cmidrule(l{3pt}r{3pt}){2-5} \cmidrule(l{3pt}r{3pt}){6-6}
+		% 		Paper & All reps & 1st Rep and Rescue & Rescue & Non-rescue & Other reps\\
+		% 		\midrule
+		% 		Birch \& Bloom 2007 & 0.192 & 0.189 & 0.194 & 0.191 & 0.989\\
+		% 		Child et al. 2018 & 0.669 & 0.669 & 0.641 & 0.858 & 0.778\\
+		% 		Chou et al. 2016 & 0.055 & 0.055 & 0.101 & 0.005 & 0.231\\
+		% 		Craig \& Richeson 2014 & 0.145 & 0.145 & 0.001 & 0.302 & 0.020\\
+		% 		Gong et al. 2019 & 0.262 & 0.262 & 0.057 & 0.511 & 0.228\\
+		% 		Haimovitz \& Dweck 2016 & 0.068 & 0.018 & 0.018 & 0.180 & 0.867\\
+		% 		Hopkins et al. 2016 & 0.290 & 0.290 & 0.654 & 0.004 & 0.015\\
+		% 		Jara-Ettinger et al. 2022 & 0.014 & 0.014 & 0.000 & 0.006 & 0.000\\
+		% 		Krauss \& Wang 2003 & 0.271 & 0.271 & 0.519 & 0.139 & 0.311\\
+		% 		Ngo et al. 2019 & 0.106 & 0.000 & 0.000 & 0.385 & 0.257\\
+		% 		Paxton et al. 2012 & 0.011 & 0.011 & 0.005 & 0.023 & 0.649\\
+		% 		Payne et al. 2008 & 0.023 & 0.071 & 0.031 & 0.079 & 0.895\\
+		% 		Porter et al. 2016 & 0.370 & 0.370 & 0.905 & 0.002 & 0.003\\
+		% 		Schechtman et al. 2010 & 0.712 & 0.712 & 0.654 & 0.770 & 0.877\\
+		% 		Tarampi et al. 2016 & 0.000 & 0.000 & 0.000 & 0.000 & 0.145\\
+		% 		Todd et al. 2016 & 0.062 & 0.100 & 0.124 & 0.058 & 0.778\\
+		% 		Yeshurun \& Levy 2003 & 0.614 & 0.007 & 0.017 & 0.943 & 0.474\\
+		% 		\bottomrule
+		% 	\end{tabular}
 
 	We again note that there appears to be a confusion over what is presented as we never present meta-analytic effect sizes for the reasons discussed above.
+We agree that such effect sizes wouldn't be easily interpretable.
 
@@
 
-		 Again, it seems like there may be confusion here -- the "p-values" presented here are "p-original" which is p-value like in that it's a measure of how likely an estimate would be to be at least as extreme as observed given a "null" distribution.
-It is a measure of statistical (in-)consistency on the effect sizes, not a measure of how close to zero the effect sizes are.
+	Again, it seems like there may be confusion here -- the ``p-values'' presented here are ``p-original.'' p-original is a p-value, in that it's a measure of how likely an estimate would be to be at least as extreme as observed given a ``null'' distribution.
+But it is a measure of statistical (in-)consistency of the effect sizes, not a measure of how close to zero the effect sizes are.
+It does not correspond to a classical meta-analytic hypothesis test.
 
@@
 
-		We have too few datapoints to meaningfully estimate the heterogeneity from our data (Mathur and VanderWeele suggest using the calculated tau if there are 10 or more replications); however, we also know the heterogeneity is not 0, so our best option is to use an estimated measure of heterogeneity, as is done as a sensitivity analysis in Errington et al 2021 and Boyce et al 2023.
+	We have too few datapoints to meaningfully estimate the heterogeneity from our data (Mathur and VanderWeele 2020 suggest using the calculated tau if there are 10 or more replications); however, we also know the heterogeneity is not 0, so our best option is to use an estimated measure of heterogeneity, as is done as a sensitivity analysis in \href{https://elifesciences.org/articles/71601}{Errington et al 2021} and Boyce et al 2023.
 
-		\theysaid{Minor points}
+	% \theysaid{Minor points}
 	\theysaid{Why is the median p-orig value reported? What does this tell us? I think this part of section 3.2 can be deleted.}
@@
 
-		We apologize for this oversight and have added to the caption short descriptions for these two as well as a cross reference to where the predictors are discussed at length in Boyce et al 2023.
+	We apologize for this oversight. We have changed these row names to ``Original authors at Stanford'' and 
+	``Log number of trials''.
+We have also amended the caption to clarify the reason for Stanford being relevant as well as provide a reference to where the predictors are discussed at length in Boyce et al 2023.
 
-		%TODO DO THIS 
+	% The revised caption reads:
+
+	% \revised{Correlations between an individual predictor and the subjective replication score of the rescue project.
+The first set of predictors were pre-registered based on the correlates used in Boyce et al.
+(2023).
+Original authors at Stanford refers to at the time of the first replication as this may mean the first replication was not independent.
+For details about how the predictors were coded, see the Methods section of Boyce et al.
+(2023).
+The last three predictors were added post-hoc.}
+
 	\theysaid{It is the open science collaborations, not consortium.}
 
-		%TODO FIX
 	Oops, thank you for bringing this to our attention, we have fixed it.
@@
 
-		\theysaid{Signed, Daniel Lakens}
+	% \theysaid{Signed, Daniel Lakens}
 
-		\theysaid{Reviewer 2}
+	\section{Reviewer 2}
 
-		\theysaid{Thanks for the opportunity to review this paper.}
+	% \theysaid{Thanks for the opportunity to review this paper.}
 
-		\theysaid{I believe this is a well-written paper, with an interesting question: Should investigators devote more time to continued replications?
-		In the paper, the authors try to “rescue” papers after an original failure to replicate.
+	% \theysaid{I believe this is a well-written paper, with an interesting question: Should investigators devote more time to continued replications?
+		% In the paper, the authors try to “rescue” papers after an original failure to replicate.
 They show that in their relatively small sample of 17 studies, 5 could be rescued, and the others couldn’t, suggesting that rescuing studies has a high failure rate.}
 
-		\theysaid{I do believe this is an interesting finding, although not completely surprising: in a world in which it is already hard to replicate studies, it make sense that it is even harder to rescue an outcome after a failed replication attempt.
+	% \theysaid{I do believe this is an interesting finding, although not completely surprising: in a world in which it is already hard to replicate studies, it make sense that it is even harder to rescue an outcome after a failed replication attempt.
 But the effort of the authors shows this elegantly, and it also shows, maybe surprisingly to some, that studies actually can be rescued, despite failed replication attempts earlier.
@@
 
-		\theysaid{So in general, I think the findings are interesting, and I think the authors did a good job in writing this up.
+	% \theysaid{So in general, I think the findings are interesting, and I think the authors did a good job in writing this up.
 What I am less convinced about is how this should inform decisions on rescuing papers.
@@
 
-		\theysaid{What I am trying to say is that the decision to re-replicate is most likely determined by many factors.
+	\theysaid{[...] the decision to re-replicate is most likely determined by many factors.
 The fact that on average (so, when picking a to be rescued study randomly) this probability is slim, should in my opinion only be a relatively small part of this decision.
@@
 
-		This point is well taken and we have expanded our discussion to acknowledge the larger space of factors and decisions at play with replications and rescues and the motivations to do them. 
-		%TODO make not suck
+	This point is well taken and we have expanded our discussion to acknowledge the larger space of factors at play with replications and rescues and the motivations to do them.
 
-		\theysaid{One minor issue:}
+	% \revised{Overall, the diminished and inconsistent effects we found in the rescues suggest that even if a re-replication ``works'', it may be difficult to build upon as follow-up studies will need large samples to detect small effects.
+		% 	\newline
+
+		% 	We have focused here on a narrow type of replication and rescue: that done by an early career researcher with the goal of establishing whether this is a result \emph{they} can build on.
+We acknowledge that this type of replication exists as part of a wider ecosystem of replications that have different properties and are done for different reasons.
+		% 	\newline
+
+		% 	In many cases, researchers may have strong prior beliefs about where a replication will succeed, and these priors may influence a researchers interpretation of a failed replication, and thus their calculations about where a re-replication will succeed or is worth attempting.
+For instance, a researcher who has high credence in the main result is more likely to attribute failure to specific details in the replication, and thus may want to do a rescue where those details are adjusted.
+On the other hand, a researcher who is dubious of the methods, results, or statistical approaches in an experiment, or who has previously failed to extend the experimental result, may be quicker to interpret a non-replication as a more definitive negative result.
+What a researcher chooses to do may also depend on the perceived strength of the replication, what size effects they think are relevant, and how important they think the target effect is.
+Thus, in some cases, when to re-replicate may be a question of prior beliefs and perceived utility rather than just likelihood of a re-replication succeeding.
+		% 	\newline
+
+		% 	We opened with a question about what an early-career psychology researcher should do given a failed replication: should they try again or give up and move on?
+		% 	In our sample, the odds of a re-replication working are low (consistent with Ebersole et al., 2020).
+		% 	Especially if there is not a clear, identifiable candidate cause for replication failure, it may be more efficient to select another result to build on.
+		% }
+
+	% \theysaid{One minor issue:}
 	\theysaid{In the description of Figure 1, it is said that “the first replication’s key effect was non-zero”.
@@
 
-		%TODO FIX
-		We have clarified this. 
-		\theysaid{So in general, I think this is a neat little paper, which, in my opinion, could benefit from adding a little bit more discussion/depth in the end on what its outcomes could entail.}
+	Thank you for this point, we have now clarified that what we meant was had a confidence interval not overlapping 0. 
+	% The caption now reads
 
-		\theysaid{I always sign my reviews,
-		Rink Hoekstra}
+	% \revised{Standardized effect sizes of original studies, first replications, rescues, and additional replications if available.
+Due to the large effect size of a couple studies, large effect studies are shown in a separate panel.
+In a few cases, the first replication's key effect was in the same direction as the original with a 95\% CI that did not overlap 0; however, in these cases the larger pattern of results was not consistent between original and first replication.
+}
 
-		We again would like to thank both the editor and the reviewers for their thoughtful and prompt reviews.
-We hope that our changes to the manuscript and the documentation of our repository offer the necessary clarifications and nuance.
+	% \theysaid{So in general, I think this is a neat little paper, which, in my opinion, could benefit from adding a little bit more discussion/depth in the end on what its outcomes could entail.}
 
-          \closing{Sincerely,}
+	% \theysaid{I always sign my reviews,
+		% Rink Hoekstra}
+
 		\end{letter}

### 2024-08-09 manuscript/coverletter/collabra_response.tex
amend response

@@
 
-	Finally, don't you think that if students were going to commit fraud, they'd make their study work \emph{better}? Even the studies that did rescue had smaller effect sizes than the original studies.
+Finally, we think that if students were going to commit fraud, they would likely fraudulently cause their study succeed.
+We didn't observe this pattern, however.
+Even the studies that did have successful rescues had smaller effect sizes than the original studies.
 
-	Finally, regarding student error: in our prior work, we have a larger sample of 176 student replication studies, and these studies found a similar rate of replication as previous studies such as RP:P (see Boyce et al 2023).
-If error rates were substantially different, we'd expect lower replication.
+Regarding student error: in our prior work, we have a larger sample of $\sim$175 student replication studies, and these studies found a similar rate of replication as previous studies such as RP:P (see Boyce et al 2023).
+If error rates were substantially different for students, we'd expect this to have manifested itself as lower replication rates, which we didn't observe in that study.
+There are many other differences between our work and RPP, but numerically we see a higher replication rate than RPP rather than the reverse, so error is unlikely to be a major determinant of student replication failure.
 

### 2024-10-09 manuscript/manuscript.Rmd
try excel data format

@@
 author:
-  - name: Veronica Boyce
-    affiliation: Psych
-    footnote:
-      - corresp
-  - name: Ben Prystawski
-    affiliation: Psych
-  - name: Adani B. Abutto
-    affiliation: Psych
-  - name: Emily M. Chen
-    affiliation: Psych
-  - name: Ziwen Chen
-    affiliation: GSB
-  - name: Howard Chiu
-    affiliation: Edu
-  - name: Irmak Ergin
-    affiliation: Psych
-  - name: Anmol Gupta
-    affiliation: Psych
-  - name: Chuqi Hu
-    affiliation: Symsys
-  - name: Bendix Kemmann
-    affiliation: Philosophy
-  - name: Nastasia Klevak
-    affiliation: Psych
-  - name: Verity Y. Q. Lua
-    affiliation: Psych
-  - name: Mateus M. Mazzaferro
-    affiliation: Edu
-  - name: Khaing Mon
-    affiliation: Symsys
-  - name: Dan Ogunbamowo
-    affiliation: Psych
-  - name: Alexander Pereira
-    affiliation: [Psych, Philosophy]
-  - name: Jordan Troutman
-    affiliation: CS
-  - name: Sarah Tung
-    affiliation: Psych
-  - name: Raphael Uricher
-    affiliation: Psych
-  - name: Michael C. Frank
-    affiliation: Psych
-address:
-  - code: Psych
-    address: Department of Psychology, Stanford University
-  - code: GSB
-    address: Graduate School of Business, Stanford University
-  - code: Edu
-    address: Graduate School of Education, Stanford University
-  - code: Symsys
-    address: Symbolic Systems Program, Stanford University
-  - code: Philosophy
-    address: Department of Philosophy, Stanford University
-  - code: CS
-    address: Department of Computer Science, Stanford University
-footnote:
-  - code: corresp
-    text: "Corresponding author. Email: vboyce@stanford.edu"
+  - Anonymous
+# author:
+#   - name: Veronica Boyce
+#     affiliation: Psych
+#     footnote:
+#       - corresp
+#   - name: Ben Prystawski
+#     affiliation: Psych
+#   - name: Adani B. Abutto
+#     affiliation: Psych
+#   - name: Emily M. Chen
+#     affiliation: Psych
+#   - name: Ziwen Chen
+#     affiliation: GSB
+#   - name: Howard Chiu
+#     affiliation: Edu
+#   - name: Irmak Ergin
+#     affiliation: Psych
+#   - name: Anmol Gupta
+#     affiliation: Psych
+#   - name: Chuqi Hu
+#     affiliation: Symsys
+#   - name: Bendix Kemmann
+#     affiliation: Philosophy
+#   - name: Nastasia Klevak
+#     affiliation: Psych
+#   - name: Verity Y. Q. Lua
+#     affiliation: Psych
+#   - name: Mateus M. Mazzaferro
+#     affiliation: Edu
+#   - name: Khaing Mon
+#     affiliation: Symsys
+#   - name: Dan Ogunbamowo
+#     affiliation: Psych
+#   - name: Alexander Pereira
+#     affiliation: [Psych, Philosophy]
+#   - name: Jordan Troutman
+#     affiliation: CS
+#   - name: Sarah Tung
+#     affiliation: Psych
+#   - name: Raphael Uricher
+#     affiliation: Psych
+#   - name: Michael C. Frank
+#     affiliation: Psych
+# address:
+#   - code: Psych
+#     address: Department of Psychology, Stanford University
+#   - code: GSB
+#     address: Graduate School of Business, Stanford University
+#   - code: Edu
+#     address: Graduate School of Education, Stanford University
+#   - code: Symsys
+#     address: Symbolic Systems Program, Stanford University
+#   - code: Philosophy
+#     address: Department of Philosophy, Stanford University
+#   - code: CS
+#     address: Department of Computer Science, Stanford University
+#footnote:
+#  - code: corresp
+#    text: "Corresponding author. Email: vboyce@stanford.edu"
 bibliography: ["251rescue.bib"] # Replace with one or more of your own bibtex files. Better BibTeX for Zotero is your friend
@@
 
+# Conflicts of Interest {.unnumbered}
+
+The authors report no conflicts of interest.
+
 # Author Contributions {.unnumbered}
@@
 The first replication sampled US adults and did not find a significant interaction.
-The rescuer thought that cultural differences may have played a role and specifically sampled Asian American adults.
+The rescuer thought that cultural differences may have played a role and specifically sampled adults who reported their ethnicity as East Asian.
 The rescue did not recover the interaction.

### 2024-10-09 manuscript/manuscript.tex
try excel data format

@@
   pdftitle={Estimating the replicability of psychology experiments after an initial failure to replicate},
+  pdfauthor={Anonymous},
   pdflang={en},
@@
 % Create labels for Addresses if the are given by code
-\MyNewLabel{ADDRTXT}{Psych}{Department of Psychology, Stanford University}
-\MyNewLabel{ADDRTXT}{GSB}{Graduate School of Business, Stanford University}
-\MyNewLabel{ADDRTXT}{Edu}{Graduate School of Education, Stanford University}
-\MyNewLabel{ADDRTXT}{Symsys}{Symbolic Systems Program, Stanford University}
-\MyNewLabel{ADDRTXT}{Philosophy}{Department of Philosophy, Stanford University}
-\MyNewLabel{ADDRTXT}{CS}{Department of Computer Science, Stanford University}
 
 % Create labels for Footnotes if they are given by code
-\MyNewLabel{ANOTETXT}{corresp}{Corresponding author. Email: \href{mailto:vboyce@stanford.edu}{\nolinkurl{vboyce@stanford.edu}}}
 
@@
 
-\createaddrlblbycode{Psych}
-
-\createanotelblbycode{corresp}
-
 \author[%
-\addrlblbycode{Psych}%
-,%
-$\anotelblbycode{corresp}$%
-]{Veronica Boyce}
-
-\addrbycode{Psych}
-
-\createaddrlblbycode{Psych}
-
-\author[%
-\addrlblbycode{Psych}%
-]{Ben Prystawski}
-
-\addrbycode{Psych}
-
-\createaddrlblbycode{Psych}
-
-\author[%
-\addrlblbycode{Psych}%
-]{Adani B. Abutto}
-
-\addrbycode{Psych}
-
-\createaddrlblbycode{Psych}
-
-\author[%
-\addrlblbycode{Psych}%
-]{Emily M. Chen}
-
-\addrbycode{Psych}
-
-\createaddrlblbycode{GSB}
-
-\author[%
-\addrlblbycode{GSB}%
-]{Ziwen Chen}
-
-\addrbycode{GSB}
-
-\createaddrlblbycode{Edu}
-
-\author[%
-\addrlblbycode{Edu}%
-]{Howard Chiu}
-
-\addrbycode{Edu}
-
-\createaddrlblbycode{Psych}
-
-\author[%
-\addrlblbycode{Psych}%
-]{Irmak Ergin}
-
-\addrbycode{Psych}
-
-\createaddrlblbycode{Psych}
-
-\author[%
-\addrlblbycode{Psych}%
-]{Anmol Gupta}
-
-\addrbycode{Psych}
-
-\createaddrlblbycode{Symsys}
-
-\author[%
-\addrlblbycode{Symsys}%
-]{Chuqi Hu}
-
-\addrbycode{Symsys}
-
-\createaddrlblbycode{Philosophy}
-
-\author[%
-\addrlblbycode{Philosophy}%
-]{Bendix Kemmann}
-
-\addrbycode{Philosophy}
-
-\createaddrlblbycode{Psych}
-
-\author[%
-\addrlblbycode{Psych}%
-]{Nastasia Klevak}
-
-\addrbycode{Psych}
-
-\createaddrlblbycode{Psych}
-
-\author[%
-\addrlblbycode{Psych}%
-]{Verity Y. Q. Lua}
-
-\addrbycode{Psych}
-
-\createaddrlblbycode{Edu}
-
-\author[%
-\addrlblbycode{Edu}%
-]{Mateus M. Mazzaferro}
-
-\addrbycode{Edu}
-
-\createaddrlblbycode{Symsys}
-
-\author[%
-\addrlblbycode{Symsys}%
-]{Khaing Mon}
-
-\addrbycode{Symsys}
-
-\createaddrlblbycode{Psych}
-
-\author[%
-\addrlblbycode{Psych}%
-]{Dan Ogunbamowo}
-
-\addrbycode{Psych}
-
-\createaddrlblbycode{Psych}
-\createaddrlblbycode{Philosophy}
-
-\author[%
-\addrlblbycode{Psych}%
-,%
-\addrlblbycode{Philosophy}%
-]{Alexander Pereira}
-
-\addrbycode{Psych}
-\addrbycode{Philosophy}
-
-\createaddrlblbycode{CS}
-
-\author[%
-\addrlblbycode{CS}%
-]{Jordan Troutman}
-
-\addrbycode{CS}
-
-\createaddrlblbycode{Psych}
-
-\author[%
-\addrlblbycode{Psych}%
-]{Sarah Tung}
-
-\addrbycode{Psych}
-
-\createaddrlblbycode{Psych}
-
-\author[%
-\addrlblbycode{Psych}%
-]{Raphael Uricher}
-
-\addrbycode{Psych}
-
-\createaddrlblbycode{Psych}
-
-\author[%
-\addrlblbycode{Psych}%
-]{Michael C. Frank}
-
-\addrbycode{Psych}
+]{}
 
@@
 Hopkins et al. 2016 & 0.290 & 0.290 & 0.654 & 0.004 & 0.015\\
-Jara-Ettinger et al. 2022 & 0.014 & 0.014 & 0.000 & 0.006 & 0.000\\
+Jara-Ettinger et al. 2022 & 0.009 & 0.009 & 0.000 & 0.004 & 0.000\\
 Krauss \& Wang 2003 & 0.271 & 0.271 & 0.519 & 0.139 & 0.311\\
@@
 For b) the original versus the rescue, the median value of \(p\)-original was 0.06 {[}IQR: 0.01 - 0.52{]}, and 47\% of the \(p\)-original values were less than .05.
-For c) the original versus all the non-rescue replications, the median value of \(p\)-original was 0.14 {[}IQR: 0.01 - 0.38{]}, and 35\% of the \(p\)-original values were less than .05.
+For c) the original versus all the non-rescue replications, the median value of \(p\)-original was 0.14 {[}IQR: 0 - 0.38{]}, and 35\% of the \(p\)-original values were less than .05.
 For d) the rescue versus the other replications, the median value of \(p\)-original was 0.31 {[}IQR: 0.14 - 0.78{]}, and 24\% of the \(p\)-original values were less than .05.
@@
 \midrule\\
-Log replication sample size & -0.258 & 0.317\\
-Log replication/original sample size & -0.487 & 0.048\\
-Log rescue/replication sample size & 0.490 & 0.046\\
+Log replication sample size & -0.261 & 0.311\\
+Log replication/original sample size & -0.493 & 0.045\\
+Log rescue/replication sample size & 0.493 & 0.044\\
 \bottomrule
@@
 Todd et al. 2016 & 1.00 & 63 & 26 & 55 & very close & very close\\
-Jara-Ettinger et al. 2022 & 0.75 & 144 & 147 & 426 & exact & exact\\
+Jara-Ettinger et al. 2022 & 0.75 & 144 & 142 & 426 & exact & exact\\
 Porter et al. 2016 & 0.75 & 145 & 168 & 136 & close & close\\
@@
 Data collection was supported by funding from the Stanford Departments of Psychology and Philosophy, Graduate School of Education, and the Symbolic Systems program.
+
+\section*{Conflicts of Interest}\label{conflicts-of-interest}
+\addcontentsline{toc}{section}{Conflicts of Interest}
+
+The authors report no conflicts of interest.
 

### 2024-10-09 code/process.Rmd
edit pass on results
submit collabra
trying again at link behavior

--- 2024-02-16 code/process.Rmd
@@
 ```{r setup, include=FALSE}
-knitr::opts_chunk$set(echo = FALSE, warning=F, message=F)
+knitr::opts_chunk$set(echo = FALSE, warning = F, message = F)
 knitr::opts_chunk$set(dev = "png", dev.args = list(type = "cairo-png"))
@@
 
-model_location="code/models"
+model_location <- "code/models"
 ```
@@
 f <- googledrive::as_dribble("https://docs.google.com/spreadsheets/d/12A4DblSbX_0tHP1mTVJhjNboI1YDngidkNWiSy0sN0g/edit#gid=0")
-googledrive::drive_download(f, path=here("data","raw_data.xlsx"), overwrite=T)
+googledrive::drive_download(f, path = here("data", "raw_data.xlsx"), overwrite = T)
 
-raw_expts <- readxl::read_xlsx(here("data","raw_data.xlsx"), sheet="expt-level", skip=0)
+raw_expts <- readxl::read_xlsx(here("data", "raw_data.xlsx"), sheet = "expt-level", skip = 0)
 
-raw_orig <- readxl::read_xlsx(here("data", "raw_data.xlsx"), sheet="original")
+raw_orig <- readxl::read_xlsx(here("data", "raw_data.xlsx"), sheet = "original")
 
-ready <- raw_expts |> left_join(raw_orig) |> write_csv(here("data", "combined_data.csv"))
+ready <- raw_expts |>
+  left_join(raw_orig) |>
+  write_csv(here("data", "combined_data.csv"))
 
+for_pretty <- ready |>
+  knitr::kable(format = "pipe") |>
+  write_lines(here("data", "combined_data.md"))
 ```
@@
 d <- read_csv(here("data", "combined_data.csv")) |>
-  select(target_lastauthor_year, type, on_turk, repeated_measure, N, raw_stat, 
+  select(
+    target_lastauthor_year, type, on_turk, repeated_measure, N, raw_stat,
     same_direction, replication_score, closeness, subfield, target_year, stanford_internal,
-         open_data, open_materials, within_between, single_vignette)
-
+    open_data, open_materials, within_between, single_vignette, name_pretty
+  )
 ```
@@
 ```{r}
-source(here("code","helper","parse_stats.R"))
+source(here("code", "helper", "parse_stats.R"))
 ```
@@
 parsed_d <- d |>
-  mutate(raw_stat=gsub(" ","",raw_stat),
-         calc=pmap(list(raw_stat, within_between,N), do_parsing)) |> 
-  unnest(cols=c(calc), names_sep="_") |> 
   mutate(
-    calc_d_calc=case_when(
-      type=="original" ~ abs(calc_d_calc),
-      same_direction=="yes" ~ abs(calc_d_calc),
-      same_direction=="no" ~ -abs(calc_d_calc),
+    raw_stat = gsub(" ", "", raw_stat),
+    calc = pmap(list(raw_stat, within_between, N), do_parsing)
+  ) |>
+  unnest(cols = c(calc), names_sep = "_") |>
+  mutate(
+    calc_d_calc = case_when(
+      type == "original" ~ abs(calc_d_calc),
+      same_direction == "yes" ~ abs(calc_d_calc),
+      same_direction == "no" ~ -abs(calc_d_calc),
       T ~ as.numeric(NA)
     ),
-    calc_ES=case_when(
-      type=="original" ~ abs(calc_ES),
-      same_direction=="yes" ~ abs(calc_ES),
-      same_direction=="no" ~ -abs(calc_ES),
+    calc_ES = case_when(
+      type == "original" ~ abs(calc_ES),
+      same_direction == "yes" ~ abs(calc_ES),
+      same_direction == "no" ~ -abs(calc_ES),
       T ~ as.numeric(NA)
     ),
-    type=factor(type, levels=c("original", "rep1", "rescue", "additional"))
+    type = factor(type, levels = c("original", "rep1", "rescue", "additional"))
   ) |>
@@
 ```{r}
+parsed_d |>
+  filter(is.na(calc_ES) & (is.na(calc_d_calc))) |>
+  select(target_lastauthor_year, type, raw_stat)
 
-parsed_d |> filter(is.na(calc_ES)&(is.na(calc_d_calc))) |>  select(target_lastauthor_year, type, raw_stat)
+parsed_d |>
+  filter(is.na(calc_SE) & (is.na(calc_d_calc_se))) |>
+  select(target_lastauthor_year, type, raw_stat)
 
-parsed_d |> filter(is.na(calc_SE)&(is.na(calc_d_calc_se))) |>  select(target_lastauthor_year, type, raw_stat)
-
+# everything is parsing, yay!
+parsed_d |> write_csv(here("data/parsed_data.csv"))
 ```
@@
 ```{r, fig.height=6, fig.width=8}
-#test on just one
-colors <- c("original"="black", "rep1"="#377EB8", "rescue"="#E41A1C", "additional"="#984EA3")
-for_plotting <- parsed_d |> filter(is.na(calc_d_calc)&!is.na(calc_ES)) |> 
-  mutate(point=calc_ES, low=calc_ES-1.96*calc_SE, high=calc_ES+1.96*calc_SE)
+# test on just one
+colors <- c("original" = "black", "rep1" = "#377EB8", "rescue" = "#E41A1C", "additional" = "#984EA3")
+for_plotting <- parsed_d |>
+  filter(is.na(calc_d_calc) & !is.na(calc_ES)) |>
+  mutate(point = calc_ES, low = calc_ES - 1.96 * calc_SE, high = calc_ES + 1.96 * calc_SE)
 
-for_plotting_d <- parsed_d |> filter(!is.na(calc_d_calc)) |> 
-  mutate(point=calc_d_calc, low=calc_d_calc-1.96*calc_d_calc_se, high=calc_d_calc+1.96*calc_d_calc_se)
+for_plotting_d <- parsed_d |>
+  filter(!is.na(calc_d_calc)) |>
+  mutate(point = calc_d_calc, low = calc_d_calc - 1.96 * calc_d_calc_se, high = calc_d_calc + 1.96 * calc_d_calc_se)
 
-orig_scale <- ggplot(for_plotting,aes(x=target_lastauthor_year,y=point,ymin=low,ymax=high, color=type, shape=type, group=desc(type)))+
-  geom_errorbar(size=.5,width=.25, position=position_dodge(width=.4))+
-  geom_point(position=position_dodge(width=.4))+
-  coord_flip(ylim=c(-1.1,2))+
-  scale_size_area()+
-  geom_hline(yintercept=0,color="black")+
-  theme(legend.position = "none",
+orig_scale <- ggplot(for_plotting, aes(x = target_lastauthor_year, y = point, ymin = low, ymax = high, color = type, shape = type, group = desc(type))) +
+  geom_errorbar(size = .5, width = .25, position = position_dodge(width = .4)) +
+  geom_point(position = position_dodge(width = .4)) +
+  coord_flip() +
+  scale_size_area() +
+  geom_hline(yintercept = 0, color = "black") +
+  theme(
+    legend.position = "none",
     panel.grid.major.x = element_blank(),
-        panel.grid.minor.x=element_blank()
-        )+
-  scale_color_manual(values=colors)+
-  labs(y="effect size on original scale", x="")
+    panel.grid.minor.x = element_blank()
+  ) +
+  scale_color_manual(values = colors) +
+  labs(y = "effect size on original scale", x = "")
 
-smd_scale <- ggplot(for_plotting_d,aes(x=target_lastauthor_year,y=point,ymin=low,ymax=high,shape=type, color=type, group=desc(type)))+
-  geom_errorbar(size=.5,width=0, position=position_dodge(width=.5))+
-  geom_point(position=position_dodge(width=.5))+
-  coord_flip(ylim=c(-1.1,2))+
-  scale_size_area()+
-  geom_hline(yintercept=0,color="black")+
-    scale_color_manual(values=colors)+
-  theme(legend.position = "bottom", 
+smd_scale <- ggplot(for_plotting_d, aes(x = target_lastauthor_year, y = point, ymin = low, ymax = high, shape = type, color = type, group = desc(type))) +
+  geom_errorbar(size = .5, width = 0, position = position_dodge(width = .5)) +
+  geom_point(position = position_dodge(width = .5)) +
+  coord_flip(ylim = c(-1.1, 1.5)) +
+  scale_size_area() +
+  geom_hline(yintercept = 0, color = "black") +
+  scale_color_manual(values = colors) +
+  theme(
+    legend.position = "bottom",
     panel.grid.major.x = element_blank(),
-        panel.grid.minor.x=element_blank()
-        )+
-  labs(y="Standarized mean difference", x="")
+    panel.grid.minor.x = element_blank()
+  ) +
+  labs(y = "Standarized mean difference", x = "")
 
-plot_grid(orig_scale, smd_scale, nrow=2, rel_heights=c(.3,1))
-
+plot_grid(orig_scale, smd_scale, nrow = 2, rel_heights = c(.3, 1))
 ```
@@
 ```{r}
-subj <- parsed_d |> filter(type=="rescue") |> mutate(binary_success=ifelse(replication_score>.5,1,0))
+subj <- parsed_d |>
+  filter(type == "rescue") |>
+  mutate(binary_success = ifelse(replication_score > .5, 1, 0))
 
-tallied <- subj|> group_by(replication_score) |> tally()
+tallied <- subj |>
+  group_by(replication_score) |>
+  tally()
 
 tallied
-success <- filter(subj, binary_success==1)
+success <- filter(subj, binary_success == 1)
 
-d <- read_csv(here("data", "combined_data.csv")) |> filter(type=="rescue")
+d <- read_csv(here("data", "combined_data.csv")) |> filter(type == "rescue")
 
-irr <- cor.test(d$TA_rep_score, d$MCF_rep_score, method="spearman")$estimate
+irr <- cor.test(d$TA_rep_score, d$MCF_rep_score, method = "spearman")$estimate
 irr
@@
 ```{r}
-original <- parsed_d |> filter(type=="original") |> 
-  rename_with(~str_c("original_",.), .cols=-target_lastauthor_year)
+original <- parsed_d |>
+  filter(type == "original") |>
+  rename_with(~ str_c("original_", .), .cols = -target_lastauthor_year)
 
-rep1 <- parsed_d |> filter(type=="rep1") |> select(target_lastauthor_year, rep_N=N)
+rep1 <- parsed_d |>
+  filter(type == "rep1") |>
+  select(target_lastauthor_year, rep_N = N)
 
-for_cor <- subj |> left_join(original) |> left_join(rep1) |> 
+for_cor <- subj |>
+  left_join(original) |>
+  left_join(rep1) |>
   mutate(
-  social=ifelse(subfield=="social", 1,0),
-  other_psych=ifelse(subfield=="other-psych",1,0), 
-  is_within=ifelse(within_between=="within", 1,0), 
-  change_platform=ifelse(on_turk==original_on_turk, 0,1),
-  log_trials=log(repeated_measure),
-  log_sample=log(N),
-  log_ratio_ss=log(N/original_N),
-  rep_1_log_sample=log(rep_N),
-  log_ratio_rep1_orig=log(rep_N/original_N),
-  log_ratio_rescue_rep1=log(N/rep_N),
-  open_data=ifelse(open_data=="yes",1,0),
-  open_mat=ifelse(open_materials=="yes", 1,0),
-  stanford=ifelse(stanford_internal=="yes",1,0)) |> 
+    social = ifelse(subfield == "social", 1, 0),
+    other_psych = ifelse(subfield == "other-psych", 1, 0),
+    is_within = ifelse(within_between == "within", 1, 0),
+    change_platform = ifelse(on_turk == original_on_turk, 0, 1),
+    log_trials = log(repeated_measure),
+    log_sample = log(N),
+    log_ratio_ss = log(N / original_N),
+    rep_1_log_sample = log(rep_N),
+    log_ratio_rep1_orig = log(rep_N / original_N),
+    log_ratio_rescue_rep1 = log(N / rep_N),
+    open_data = ifelse(open_data == "yes", 1, 0),
+    open_mat = ifelse(open_materials == "yes", 1, 0),
+    stanford = ifelse(stanford_internal == "yes", 1, 0)
+  ) |>
   filter(!is.na(replication_score))
@@
   if (stat == "estimate") {
-    cor.test(for_cor$replication_score, pull(for_cor, {{var}}))$estimate
+    cor.test(for_cor$replication_score, pull(for_cor, {{ var }}))$estimate
   } else {
-    cor.test(for_cor$replication_score, pull(for_cor, {{var}}))$p.value
+    cor.test(for_cor$replication_score, pull(for_cor, {{ var }}))$p.value
   }
@@
 
-preds <- c("open_data",  "open_mat", "stanford", "change_platform", 
+preds <- c(
+  "open_data", "open_mat", "stanford", "change_platform",
   "log_ratio_ss", "is_within", "single_vignette", "log_sample",
-           "log_trials", "social", "other_psych", "rep_1_log_sample", "log_ratio_rep1_orig", "log_ratio_rescue_rep1")
+  "log_trials", "social", "other_psych", "rep_1_log_sample", "log_ratio_rep1_orig", "log_ratio_rescue_rep1"
+)
 
 cors <- tibble(preds = preds) |>
-  mutate(r = sapply(preds, function(x) sub_cor(x, stat = "estimate")),
-         p = sapply(preds, function(x) sub_cor(x, stat = "p"))) |>
-
-  mutate(Predictors=factor(preds, levels=c("social", "other_psych", "is_within", "single_vignette", "change_platform", "open_data", "open_mat", "stanford", "pub_year", "log_trials", "log_sample", "log_ratio_ss", "rep_1_log_sample", "log_ratio_rep1_orig", "log_ratio_rescue_rep1"), labels=c("Social", "Other psych", "Within subjects", "Single vignette", "Switch to online", "Open data", "Open materials", "Stanford", "Publication year", "Log trials", "Log original sample size", "Log rep/orig sample", "rep_1_log_sample", "log_ratio_rep1_orig", "log_ratio_rescue_rep1"))) |> arrange(Predictors) |> select(Predictors, r, p)
+  mutate(
+    r = sapply(preds, function(x) sub_cor(x, stat = "estimate")),
+    p = sapply(preds, function(x) sub_cor(x, stat = "p"))
+  ) |>
+  mutate(Predictors = factor(preds, levels = c("social", "other_psych", "is_within", "single_vignette", "change_platform", "open_data", "open_mat", "stanford", "pub_year", "log_trials", "log_sample", "log_ratio_ss", "rep_1_log_sample", "log_ratio_rep1_orig", "log_ratio_rescue_rep1"), labels = c("Social", "Other psych", "Within subjects", "Single vignette", "Switch to online", "Open data", "Open materials", "Stanford", "Publication year", "Log trials", "Log original sample size", "Log rep/orig sample", "rep_1_log_sample", "log_ratio_rep1_orig", "log_ratio_rescue_rep1"))) |>
+  arrange(Predictors) |>
+  select(Predictors, r, p)
 
 library(kableExtra)
-knitr::kable(cors, digits = 3, align='rcc') |> kable_styling(full_width=F, htmltable_class = "lightable-classic-2") 
-#cors
+knitr::kable(cors, digits = 3, align = "rcc") |> kable_styling(full_width = F, htmltable_class = "lightable-classic-2")
+# cors
 ```
@@
 ```{r}
-parsed_d |> select(target_lastauthor_year, type, N, closeness, replication_score) |> 
-  filter(type!="additional") |> 
-  pivot_wider(names_from="type", values_from=c(N, closeness, replication_score)) |> 
-  select(paper=target_lastauthor_year, rescue_score=replication_score_rescue, N_original, N_rep1, N_rescue,
-         closeness_rep1, closeness_rescue) |> arrange(rescue_score |> desc())
-
+parsed_d |>
+  select(target_lastauthor_year, type, N, closeness, replication_score) |>
+  filter(type != "additional") |>
+  pivot_wider(names_from = "type", values_from = c(N, closeness, replication_score)) |>
+  select(
+    paper = target_lastauthor_year, rescue_score = replication_score_rescue, N_original, N_rep1, N_rescue,
+    closeness_rep1, closeness_rescue
+  ) |>
+  arrange(rescue_score |> desc())
 ```
@@
 ```{r}
-source(here("code","helper","stats.R"))
+source(here("code", "helper", "stats.R"))
 ```
@@
 do_rma <- function(df) {
-  if(!any(is.na(df$es))){
-  r<- rma(yi=df$es, sei=df$es_se, slab=df$type)
-  return(tibble(rma_est=r$beta[,1],rma_se=r$se))
+  if (!any(is.na(df$es))) {
+    r <- rma(yi = df$es, sei = df$es_se, slab = df$type)
+    return(tibble(rma_est = r$beta[, 1], rma_se = r$se))
   }
-  return(tibble(rma_est=NA, rma_se=NA))
+  return(tibble(rma_est = NA, rma_se = NA))
 }
@@
 do_d_rma <- function(df) {
-  if(!any(is.na(df$d))){
-  r<- rma(yi=df$d, sei=df$d_se, slab=df$type)
-  return(tibble(rma_d_est=r$beta[,1], rma_d_se=r$se))
+  if (!any(is.na(df$d))) {
+    r <- rma(yi = df$d, sei = df$d_se, slab = df$type)
+    return(tibble(rma_d_est = r$beta[, 1], rma_d_se = r$se))
   }
-  return(tibble(rma_d_est=NA, rma_d_se=NA))
-
+  return(tibble(rma_d_est = NA, rma_d_se = NA))
 }
 
-do_p_orig <- function(es, es_se, rep_es, rep_se){
-  if(!is.na(es)&!is.na(es_se)&!is.na(rep_es)&!is.na(rep_se)){
-    return(Replicate::p_orig(es, es_se**2,rep_es, t2=0.21**2, rep_se**2))
+do_p_orig <- function(es, es_se, rep_es, rep_se) {
+  if (!is.na(es) & !is.na(es_se) & !is.na(rep_es) & !is.na(rep_se)) {
+    return(Replicate::p_orig(es, es_se**2, rep_es, t2 = 0.21**2, rep_se**2))
   }
@@
 }
-
 ```
@@
 ```{r}
+orig <- parsed_d |>
+  filter(type == "original") |>
+  select(target_lastauthor_year, d = calc_d_calc, d_se = calc_d_calc_se, es = calc_ES, es_se = calc_SE)
 
-orig <- parsed_d |> filter(type=="original") |> select(target_lastauthor_year, d=calc_d_calc, d_se=calc_d_calc_se, es=calc_ES, es_se=calc_SE)
-
-orig_v_others <- parsed_d |> select(target_lastauthor_year, type, d=calc_d_calc, d_se=calc_d_calc_se, es=calc_ES, es_se=calc_SE) |> 
-  filter(type!="original") |> 
+orig_v_others <- parsed_d |>
+  select(target_lastauthor_year, type, d = calc_d_calc, d_se = calc_d_calc_se, es = calc_ES, es_se = calc_SE) |>
+  filter(type != "original") |>
   group_by(target_lastauthor_year) |>
   nest() |>
-  mutate(rma_result=map(data, do_rma),
-         d_rma_result=map(data, do_d_rma)) |> 
+  mutate(
+    rma_result = map(data, do_rma),
+    d_rma_result = map(data, do_d_rma)
+  ) |>
   unnest_wider(rma_result) |>
@@
   rowwise() |>
-  mutate(d_p_orig=do_p_orig(d, d_se, rma_d_est, rma_d_se))
-
+  mutate(d_p_orig = do_p_orig(d, d_se, rma_d_est, rma_d_se))
 ```
@@
 ```{r}
-orig_v_rescue <- parsed_d |>   filter(type=="rescue") |> 
-  select(target_lastauthor_year, type, res_d=calc_d_calc, res_d_se=calc_d_calc_se, res_es=calc_ES, res_es_se=calc_SE) |>
-
+orig_v_rescue <- parsed_d |>
+  filter(type == "rescue") |>
+  select(target_lastauthor_year, type, res_d = calc_d_calc, res_d_se = calc_d_calc_se, res_es = calc_ES, res_es_se = calc_SE) |>
   left_join(orig) |>
   rowwise() |>
-  mutate(d_p_orig=do_p_orig(d, d_se, res_d, res_d_se))
-
+  mutate(d_p_orig = do_p_orig(d, d_se, res_d, res_d_se))
 ```
@@
 ```{r}
-orig_v_not_rescue <- parsed_d |> select(target_lastauthor_year, type, d=calc_d_calc, d_se=calc_d_calc_se, es=calc_ES, es_se=calc_SE) |> 
-  filter(type!="original", type!="rescue") |> 
-  filter(target_lastauthor_year!="krauss2003") |> # have to avoid the divide by 0 error
+orig_v_not_rescue <- parsed_d |>
+  select(target_lastauthor_year, type, d = calc_d_calc, d_se = calc_d_calc_se, es = calc_ES, es_se = calc_SE) |>
+  filter(type != "original", type != "rescue") |>
+  filter(target_lastauthor_year != "krauss2003") |> # have to avoid the divide by 0 error
   group_by(target_lastauthor_year) |>
   nest() |>
-  mutate(rma_result=map(data, do_rma),
-         d_rma_result=map(data, do_d_rma)) |> 
+  mutate(
+    rma_result = map(data, do_rma),
+    d_rma_result = map(data, do_d_rma)
+  ) |>
   unnest_wider(rma_result) |>
@@
 ```{r}
-rescue_only <- parsed_d |> filter(type=="rescue") |> select(target_lastauthor_year, d=calc_d_calc, d_se=calc_d_calc_se, es=calc_ES, es_se=calc_SE)
+rescue_only <- parsed_d |>
+  filter(type == "rescue") |>
+  select(target_lastauthor_year, d = calc_d_calc, d_se = calc_d_calc_se, es = calc_ES, es_se = calc_SE)
 
-rescue_v_reps <- parsed_d |> select(target_lastauthor_year, type, d=calc_d_calc, d_se=calc_d_calc_se, es=calc_ES, es_se=calc_SE) |> 
-  filter(type!="original", type!="rescue") |> 
-  filter(target_lastauthor_year!="krauss2003") |> # have to avoid the divide by 0 error
+rescue_v_reps <- parsed_d |>
+  select(target_lastauthor_year, type, d = calc_d_calc, d_se = calc_d_calc_se, es = calc_ES, es_se = calc_SE) |>
+  filter(type != "original", type != "rescue") |>
+  filter(target_lastauthor_year != "krauss2003") |> # have to avoid the divide by 0 error
   group_by(target_lastauthor_year) |>
   nest() |>
-  mutate(rma_result=map(data, do_rma),
-         d_rma_result=map(data, do_d_rma)) |> 
+  mutate(
+    rma_result = map(data, do_rma),
+    d_rma_result = map(data, do_d_rma)
+  ) |>
   unnest_wider(rma_result) |>
@@
 ```{r}
- all <- orig_v_others |> select(target_lastauthor_year, orig_v_other=d_p_orig) |> 
-  left_join(orig_v_rescue |> select(target_lastauthor_year, orig_v_rescue=d_p_orig)) |> 
-  left_join(orig_v_not_rescue |> select(target_lastauthor_year, orig_v_not_rescue=d_p_orig)) |> 
-  left_join(rescue_v_reps |> select(target_lastauthor_year, rescue_v_reps=d_p_orig)) |> 
-  rename(paper=target_lastauthor_year)
+all <- orig_v_others |>
+  select(target_lastauthor_year, orig_v_other = d_p_orig) |>
+  left_join(orig_v_rescue |> select(target_lastauthor_year, orig_v_rescue = d_p_orig)) |>
+  left_join(orig_v_not_rescue |> select(target_lastauthor_year, orig_v_not_rescue = d_p_orig)) |>
+  left_join(rescue_v_reps |> select(target_lastauthor_year, rescue_v_reps = d_p_orig)) |>
+  rename(paper = target_lastauthor_year)
 
 all
-
 ```
@@
 ```{r}
-do_predInt <- function(df){
-  if(!is.na(df$es)&!is.na(df$es_se)&!is.na(df$rep_es)&!is.na(df$rep_es_se)){
-    a <- Replicate::pred_int(df$es, df$es_se**2,df$rep_es, df$rep_es_se**2)
-    return(tibble(low=a$int.lo, high=a$int.hi, inside=a$rep.inside))
+do_predInt <- function(df) {
+  if (!is.na(df$es) & !is.na(df$es_se) & !is.na(df$rep_es) & !is.na(df$rep_es_se)) {
+    a <- Replicate::pred_int(df$es, df$es_se**2, df$rep_es, df$rep_es_se**2)
+    return(tibble(low = a$int.lo, high = a$int.hi, inside = a$rep.inside))
   }
-  return(tibble(low=NA,high=NA, inside=NA))
+  return(tibble(low = NA, high = NA, inside = NA))
 }
 
-do_d_predInt <- function(df){
-  if(!is.na(df$d)&!is.na(df$d_se)&!is.na(df$rep_d)&!is.na(df$rep_d_se)){
-    a <- Replicate::pred_int(df$d, df$d_se**2,df$rep_d, df$rep_d_se**2)
-    return(tibble(d_low=a$int.lo, d_high=a$int.hi, d_inside=a$rep.inside))
+do_d_predInt <- function(df) {
+  if (!is.na(df$d) & !is.na(df$d_se) & !is.na(df$rep_d) & !is.na(df$rep_d_se)) {
+    a <- Replicate::pred_int(df$d, df$d_se**2, df$rep_d, df$rep_d_se**2)
+    return(tibble(d_low = a$int.lo, d_high = a$int.hi, d_inside = a$rep.inside))
   }
-  return(tibble(d_low=NA,d_high=NA, d_inside=NA))
+  return(tibble(d_low = NA, d_high = NA, d_inside = NA))
 }
-
 ```
@@
 ```{r}
-orig <- parsed_d |> filter(type=="original") |> select(target_lastauthor_year, d=calc_d_calc, d_se=calc_d_calc_se, es=calc_ES, es_se=calc_SE)
+orig <- parsed_d |>
+  filter(type == "original") |>
+  select(target_lastauthor_year, d = calc_d_calc, d_se = calc_d_calc_se, es = calc_ES, es_se = calc_SE)
 
 predInts <- parsed_d |>
-  filter(type!="original") |> 
+  filter(type != "original") |>
   group_by(target_lastauthor_year) |>
-  select(target_lastauthor_year, type, rep_d=calc_d_calc, rep_d_se=calc_d_calc_se, rep_es=calc_ES, rep_es_se=calc_SE) |> 
+  select(target_lastauthor_year, type, rep_d = calc_d_calc, rep_d_se = calc_d_calc_se, rep_es = calc_ES, rep_es_se = calc_SE) |>
   left_join(orig) |>
-  group_by(target_lastauthor_year,type) |> 
+  group_by(target_lastauthor_year, type) |>
   nest() |>
-  mutate(pred_int=map(data, do_predInt),
-         d_pred_int=map(data,do_d_predInt)) |> 
+  mutate(
+    pred_int = map(data, do_predInt),
+    d_pred_int = map(data, do_d_predInt)
+  ) |>
   unnest_wider(pred_int) |>
@@
   unnest_wider(data)
-
 ```
@@
 ```{r, fig.height=8, fig.width=6}
-colors <- c("original"="black", "rep1"="#377EB8", "rescue"="#E41A1C", "additional"="#984EA3")
+colors <- c("original" = "black", "rep1" = "#377EB8", "rescue" = "#E41A1C", "additional" = "#984EA3")
 
-orig_scale <- ggplot(predInts |> filter(is.na(d_inside)&!is.na(inside)), aes(x=target_lastauthor_year, y=rep_es, ymin=low, ymax=high, color=type, group=desc(type), shape=type))+
-  geom_errorbar(size=.5,width=.25, position=position_dodge(width=.4), color="black")+
-  geom_point(position=position_dodge(width=.4))+
-  geom_point(aes(y=es), color="black", position=position_dodge(width=.4), shape=1)+
-  coord_flip()+
-  scale_size_area()+
-  geom_hline(yintercept=0,color="black")+
-  theme(legend.position = "none",
+orig_scale <- ggplot(predInts |> filter(is.na(d_inside) & !is.na(inside)), aes(x = target_lastauthor_year, y = rep_es, ymin = low, ymax = high, color = type, group = desc(type), shape = type)) +
+  geom_errorbar(size = .5, width = .25, position = position_dodge(width = .4), color = "black") +
+  geom_point(position = position_dodge(width = .4)) +
+  geom_point(aes(y = es), color = "black", position = position_dodge(width = .4), shape = 1) +
+  coord_flip() +
+  scale_size_area() +
+  geom_hline(yintercept = 0, color = "black") +
+  theme(
+    legend.position = "none",
     panel.grid.major.x = element_blank(),
-        panel.grid.minor.x=element_blank()
-        )+
-  scale_color_manual(values=colors)+
-  labs(y="predInts on original scale", x="")
+    panel.grid.minor.x = element_blank()
+  ) +
+  scale_color_manual(values = colors) +
+  labs(y = "predInts on original scale", x = "")
 
-smd_scale <- ggplot(predInts |> filter(!is.na(d_inside)), aes(x=target_lastauthor_year, y=rep_d, ymin=d_low, ymax=d_high, color=type, group=desc(type), shape=type))+
-  geom_errorbar(size=.5,width=.25, position=position_dodge(width=.4), color="black")+
-  geom_point(position=position_dodge(width=.4))+
-  geom_point(aes(y=d), color="black", position=position_dodge(width=.4), shape=1)+
-  coord_flip()+
-  scale_size_area()+
-  geom_hline(yintercept=0,color="black")+
-  theme(legend.position = "none",
+smd_scale <- ggplot(predInts |> filter(!is.na(d_inside)), aes(x = target_lastauthor_year, y = rep_d, ymin = d_low, ymax = d_high, color = type, group = desc(type), shape = type)) +
+  geom_errorbar(size = .5, width = .25, position = position_dodge(width = .4), color = "black") +
+  geom_point(position = position_dodge(width = .4)) +
+  geom_point(aes(y = d), color = "black", position = position_dodge(width = .4), shape = 1) +
+  coord_flip() +
+  scale_size_area() +
+  geom_hline(yintercept = 0, color = "black") +
+  theme(
+    legend.position = "none",
     panel.grid.major.x = element_blank(),
-        panel.grid.minor.x=element_blank()
-        )+
-  scale_color_manual(values=colors)+
-  labs(y="predInts on SMD scale", x="")
+    panel.grid.minor.x = element_blank()
+  ) +
+  scale_color_manual(values = colors) +
+  labs(y = "predInts on SMD scale", x = "")
 
-plot_grid(orig_scale, smd_scale, nrow=2, rel_heights=c(.3,1))
-
+plot_grid(orig_scale, smd_scale, nrow = 2, rel_heights = c(.3, 1))
 ```
@@
 ```{r}
-do_d_predInt_het <- function(df){
-  if(!is.na(df$d)&!is.na(df$d_se)&!is.na(df$rep_d)&!is.na(df$rep_d_se)){
-    yio=df$d
-    vio=df$d_se**2
-    yir=df$rep_d
-    vir=df$rep_d_se**2
-    t2=.21**2
-    pooled.SE = sqrt(vio + vir + t2)
-    PILo.sens = yio - qnorm(0.975) * pooled.SE
-    PIHi.sens = yio + qnorm(0.975) * pooled.SE
-    PIinside.sens = (yir > PILo.sens) & (yir < PIHi.sens)
-    return(tibble(d_low=PILo.sens, d_high=PIHi.sens, d_inside=PIinside.sens))
+do_d_predInt_het <- function(df) {
+  if (!is.na(df$d) & !is.na(df$d_se) & !is.na(df$rep_d) & !is.na(df$rep_d_se)) {
+    yio <- df$d
+    vio <- df$d_se**2
+    yir <- df$rep_d
+    vir <- df$rep_d_se**2
+    t2 <- .21**2
+    pooled.SE <- sqrt(vio + vir + t2)
+    PILo.sens <- yio - qnorm(0.975) * pooled.SE
+    PIHi.sens <- yio + qnorm(0.975) * pooled.SE
+    PIinside.sens <- (yir > PILo.sens) & (yir < PIHi.sens)
+    return(tibble(d_low = PILo.sens, d_high = PIHi.sens, d_inside = PIinside.sens))
   }
-  return(tibble(d_low=NA,d_high=NA, d_inside=NA))
+  return(tibble(d_low = NA, d_high = NA, d_inside = NA))
 }
-
 ```
@@
 ```{r}
-orig <- parsed_d |> filter(type=="original") |> select(target_lastauthor_year, d=calc_d_calc, d_se=calc_d_calc_se, es=calc_ES, es_se=calc_SE)
+orig <- parsed_d |>
+  filter(type == "original") |>
+  select(target_lastauthor_year, d = calc_d_calc, d_se = calc_d_calc_se, es = calc_ES, es_se = calc_SE)
 
 predInts_het <- parsed_d |>
-  filter(type!="original") |> 
+  filter(type != "original") |>
   group_by(target_lastauthor_year) |>
-  select(target_lastauthor_year, type, rep_d=calc_d_calc, rep_d_se=calc_d_calc_se, rep_es=calc_ES, rep_es_se=calc_SE) |> 
+  select(target_lastauthor_year, type, rep_d = calc_d_calc, rep_d_se = calc_d_calc_se, rep_es = calc_ES, rep_es_se = calc_SE) |>
   left_join(orig) |>
-  group_by(target_lastauthor_year,type) |> 
+  group_by(target_lastauthor_year, type) |>
   nest() |>
-  mutate(d_pred_int=map(data,do_d_predInt_het)) |> 
+  mutate(d_pred_int = map(data, do_d_predInt_het)) |>
   unnest_wider(d_pred_int) |>
   unnest_wider(data)
-
 ```
@@
 ```{r, fig.height=8, fig.width=6}
-colors <- c("original"="black", "rep1"="#377EB8", "rescue"="#E41A1C", "additional"="#984EA3")
+colors <- c("original" = "black", "rep1" = "#377EB8", "rescue" = "#E41A1C", "additional" = "#984EA3")
 
- ggplot(predInts_het |> filter(!is.na(d_inside)), aes(x=target_lastauthor_year, y=rep_d, ymin=d_low, ymax=d_high, color=type, group=desc(type), shape=type))+
-  geom_errorbar(size=.5,width=.25, position=position_dodge(width=.4), color="black")+
-  geom_point(position=position_dodge(width=.4))+
-  geom_point(aes(y=d), color="black", position=position_dodge(width=.4), shape=1)+
-  coord_flip()+
-  scale_size_area()+
-  geom_hline(yintercept=0,color="black")+
-  theme(legend.position = "none",
+ggplot(predInts_het |> filter(!is.na(d_inside)), aes(x = target_lastauthor_year, y = rep_d, ymin = d_low, ymax = d_high, color = type, group = desc(type), shape = type)) +
+  geom_errorbar(size = .5, width = .25, position = position_dodge(width = .4), color = "black") +
+  geom_point(position = position_dodge(width = .4)) +
+  geom_point(aes(y = d), color = "black", position = position_dodge(width = .4), shape = 1) +
+  coord_flip() +
+  scale_size_area() +
+  geom_hline(yintercept = 0, color = "black") +
+  theme(
+    legend.position = "none",
     panel.grid.major.x = element_blank(),
-        panel.grid.minor.x=element_blank()
-        )+
-  scale_color_manual(values=colors)+
-  labs(y="predInts on SMD scale", x="")
-
+    panel.grid.minor.x = element_blank()
+  ) +
+  scale_color_manual(values = colors) +
+  labs(y = "predInts on SMD scale", x = "")
 ```

### 2024-10-09 code/process.Rmd
continued link futzing

@@
 for_pretty <- ready |>
+
+  select(
+    target_lastauthor_year,
+    type,
+    short_cite,
+    write_up_link,
+    github_link,
+    original_article_link=article_link,
+    `pre-registration`,
+    on_turk, 
+    repeated_measure,
+    N,
+    test_description,
+    raw_stat,
+    same_direction,
+    MCF_rep_score,
+    TA_rep_score,
+    replication_score,
+    closeness,
+    original_study_number=study_number,
+    subfield,
+    target_year,
+    stanford_internal,
+    open_data,
+    open_materials,
+    within_between,
+    single_vignette,
+  ) |> 
   knitr::kable(format = "pipe") |>
+  kableExtra::column_spec(1:6, width="20em") |> 
   write_lines(here("data", "combined_data.md")) 

### 2024-10-09 code/process.Rmd
still looking at formatting

--- 2024-10-09 code/process.Rmd
@@
 for_pretty <- ready |>
+
+  select(
+    target_lastauthor_year,
+    type,
+    short_cite,
+    write_up_link,
+    github_link,
+   `pre-registration`,
+    original_article_link=article_link,
+
+    on_turk, 
+    repeated_measure,
+    N,
+    test_description,
+    raw_stat,
+    same_direction,
+    MCF_rep_score,
+    TA_rep_score,
+    replication_score,
+    closeness,
+    original_study_number=study_number,
+    subfield,
+    target_year,
+    stanford_internal,
+    open_data,
+    open_materials,
+    within_between,
+    single_vignette,
+  ) |> 
   knitr::kable(format = "pipe") |>
+  kableExtra::column_spec(1:7, width="20em") |> 
+   kableExtra::column_spec(11, width="30em")  
   write_lines(here("data", "combined_data.md")) 

### 2024-10-09 code/process.Rmd
another attempt

--- 2024-10-09 code/process.Rmd
@@
 for_pretty <- ready |>
+
+  select(
+    target_lastauthor_year,
+    type,
+    short_cite,
+    write_up_link,
+    github_link,
+   `pre-registration`,
+    original_article_link=article_link,
+
+    on_turk, 
+    repeated_measure,
+    N,
+    raw_stat,
+    same_direction,
+    MCF_rep_score,
+    TA_rep_score,
+    replication_score,
+    closeness,
+    original_study_number=study_number,
+    subfield,
+    target_year,
+    stanford_internal,
+    open_data,
+    open_materials,
+    within_between,
+    single_vignette,
+  ) |> 
   knitr::kable(format = "pipe") |>

### 2024-10-10 code/process.Rmd
trying to make osf links

@@
 
-for_pretty <- ready |>
-
+for_pretty_github <- ready |>
   select(
@@
   write_lines(here("data", "combined_data.md"))
+
 ```

### 2024-10-11 manuscript/manuscript.Rmd
proofread manuscript (and auto-formatted R code)

@@
 knitr::opts_chunk$set(echo = FALSE) # By default, hide code; set to TRUE to see code
-#knitr::opts_chunk$set(fig.pos = 'th') # Places figures at top or here
-knitr::opts_chunk$set(out.width = '100%', dpi=300,
-                      fig.width=8, fig.width=8) # Figure resolution and size
-knitr::opts_chunk$set(fig.env="figure") # Latex figure environment
-
-options(knitr.table.format="latex") # For kable tables to work without setting format option
-
-knitr::opts_chunk$set(echo=F, warning=F, message=F)#dev = "png", dev.args = list(type = "cairo-png")
+# knitr::opts_chunk$set(fig.pos = 'th') # Places figures at top or here
+knitr::opts_chunk$set(
+  out.width = "100%", dpi = 300,
+  fig.width = 8, fig.width = 8
+) # Figure resolution and size
+knitr::opts_chunk$set(fig.env = "figure") # Latex figure environment
+
+options(knitr.table.format = "latex") # For kable tables to work without setting format option
+
+knitr::opts_chunk$set(echo = F, warning = F, message = F) # dev = "png", dev.args = list(type = "cairo-png")
 library("papaja")
@@
 library(metafor)
-#r_refs("r-references.bib", append=F)
+# r_refs("r-references.bib", append=F)
 theme_set(theme_bw())
@@
 
-model_location="code/models"
-
+model_location <- "code/models"
 ```
@@
 ```{r}
-
 library(tidyverse)
@@
 filtered <- all_projects |>
-  mutate(sub_rep=ifelse(replicated_instructor_code==replicated_report_code, 
+  mutate(sub_rep = ifelse(replicated_instructor_code == replicated_report_code,
     replicated_report_code,
-                 adjudicated_replication_code)) |> 
-  filter(sub_rep %in% c(0,.25, .5)) |> 
-  filter(include!="no") |> 
-  filter(target_N <=200) |> 
-  filter(academic_year %in% c("2015-2016", "2016-2017", "2017-2018", "2018-2019", 
-                              "2019-2020", "2020-2021","2021-2022", "2022-2023")) 
+    adjudicated_replication_code
+  )) |>
+  filter(sub_rep %in% c(0, .25, .5)) |>
+  filter(include != "no") |>
+  filter(target_N <= 200) |>
+  filter(academic_year %in% c(
+    "2015-2016", "2016-2017", "2017-2018", "2018-2019",
+    "2019-2020", "2020-2021", "2021-2022", "2022-2023"
+  ))
 # what we really want is whether there was a github, but that column is private and so not in the public raw data
@@
 
-#test_that("number of rows in filtered", {expect_equal(nrow(filtered),49)})
-
-#given this sample, we then sought original replicator permission, 
-#since it would involve sharing their repo and write-up with a new student
-#which wouldn't have been anticipated at original classtime
-
-#we heard back from 29 students of the 49 we attempted to contact 
-#(1 we couldn't contact due to email bouncing) 
-#2 responses were negative, rest were positive, for 27 options
-
-approved <- c("krauss2003","yeshurun2003", "daffner2000", "ngo2019",
+# test_that("number of rows in filtered", {expect_equal(nrow(filtered),49)})
+
+# given this sample, we then sought original replicator permission,
+# since it would involve sharing their repo and write-up with a new student
+# which wouldn't have been anticipated at original classtime
+
+# we heard back from 29 students of the 49 we attempted to contact
+# (1 we couldn't contact due to email bouncing)
+# 2 responses were negative, rest were positive, for 27 options
+
+approved <- c(
+  "krauss2003", "yeshurun2003", "daffner2000", "ngo2019",
   "child2018", "schechtman2010", "payne2008", "paxton2012",
@@
   "sofer2015", "todd2016_1", "chou2016", "mani2013",
-              "haimovitz2016_2", "haimovitz2016_1", "craig2014")
+  "haimovitz2016_2", "haimovitz2016_1", "craig2014"
+)
 options <- filtered |> filter(target_lastauthor_year %in% approved)
 
-#test_that("number of rows in options", {expect_equal(nrow(options),27)})
+# test_that("number of rows in options", {expect_equal(nrow(options),27)})
 
@@
 
-chosen <- c("birch2007_2", "jara-ettinger2022", "porter_2016_1",
+chosen <- c(
+  "birch2007_2", "jara-ettinger2022", "porter_2016_1",
   "hopkins2016", "yeshurun2003", "craig2014", "tarampi2016",
@@
   "haimovitz2016_1", "todd2016_1", "haimovitz2016_2", "payne2008",
-            "paxton2012", "dehaene2009", "chou2016", "ngo2019", "gong2019")
+  "paxton2012", "dehaene2009", "chou2016", "ngo2019", "gong2019"
+)
 
 rescue_started <- options |> filter(target_lastauthor_year %in% chosen)
-
 ```
@@
 d <- read_csv(here("data", "combined_data.csv")) |>
-  select(target_lastauthor_year, type, on_turk, repeated_measure, N, raw_stat, 
+  select(
+    target_lastauthor_year, type, on_turk, repeated_measure, N, raw_stat,
     same_direction, replication_score, closeness, subfield, target_year, stanford_internal,
-         open_data, open_materials, within_between, single_vignette, cost, name_pretty)
-
-source(here("code","helper","parse_stats.R"))
+    open_data, open_materials, within_between, single_vignette, cost, name_pretty
+  )
+
+source(here("code", "helper", "parse_stats.R"))
 ```
@@
 
-num_proj <- parsed_d |> filter(type=="rescue") |> nrow()
-
-cost <- parsed_d |> filter(type=="rescue") |> ungroup() |>  summarize(total=sum(cost, na.rm=T))
+num_proj <- parsed_d |>
+  filter(type == "rescue") |>
+  nrow()
+
+cost <- parsed_d |>
+  filter(type == "rescue") |>
+  ungroup() |>
+  summarize(total = sum(cost, na.rm = T))
 ```
@@
 
-Imagine you are a graduate student, and you run a replication of a study that you are interested in building upon in your research.
+Imagine you are a graduate student and you run a replication of a study that you are interested in building upon in your research.
 The replication fails.
-Perhaps the interaction you hoped for is directionally correct, but the point estimate is small and the confidence interval definitely overlaps 0, with a $p$-value of .3.
+Perhaps the interaction you hoped for is directionally correct, but the point estimate is small and the confidence interval definitely contains 0, with a $p$-value of .3.
 Or perhaps the interaction is numerically in the wrong direction and the main effects look different.
@@
 Large scale replication projects in other disciplines have found 39/97 of studies with positive effects (40%) replicating in cancer biology [@errington2021], 11/18 studies (61%) replicating in economics [@camerer2016], and 31/40 studies (78%) replicating in experimental philosophy [@cova2021].
-Across these disciplines, and especially in psychology, large-scale replications indicate a substantial chance of scientists encountering failed replications if they try to replicate published findings.
-
-Replications can fail for many reasons, having to do with the original study or the replication.
+Across these disciplines, and especially in psychology, large-scale replications indicate that the probability of scientists failing to replicate published findings is substantial.
+
+Replications can fail for many reasons. Some reasons for replication failure have to do with the original study, while others have to do with how the replication was conducted.
 <!-- In principle, any difference between the original study and replication could be a root cause of the difference in their outcomes.
 But in practice, the relationship between original and replication is not symmetric, and many causes of replication failure can be attributed either more to the original study or more to the replication.
---> Starting with the original study, one potential reason for replication failure is that the original result is fragile in some way.
+--> One potential reason is that the original result is fragile in some way.
 It could be a statistically unlikely result that was achieved through chance or $p$-hacking, or it could be sensitive to the exact conditions and time it was run under ("hidden moderators").
-Another possibility is that the original reported effect size might be inflated due to some combination of heterogeneity, $p$-hacking, low power, and publication bias.
-A consequence of inflated effect sizes is that replication studies might select a sample size with appropriate statistical power for the reported effect size and then have too small a sample to reliably detect the (true) smaller effect.
+Another possibility is that the original reported effect size is inflated due to some combination of heterogeneity, $p$-hacking, low power, and publication bias.
+If effect sizes are inflated, replication studies that select a sample size with appropriate statistical power for the reported effect size will have too small a sample to reliably detect the (true) smaller effect.
 Replication studies might also end up underpowered due to unexpected attrition or noise in the replication sample.
 
-Some other reasons for replication failure are primarily due to the replication study.
+Other reasons for replication failure are primarily due to the design of the replication study.
 A replication could observe different results from the original due to methodological differences.
-These differences in design could be intentional adaptations, unavoidable changes from lack of access to the original instructions or materials, or changes that were not expected to be critical.
-A difference in the details of recruitment (e.g., online versus in-person) might mean that particular details of a study implementation would no longer be appropriate, or the data quality controls and attention checks might be inadequate.
-If there are differences in time, place, or subject population between the two studies, corresponding changes to the materials, instructions, or procedure could be needed to provide an adaptation of the experimental paradigm to the new context.
-Such adaptation creates yet more challenges in interpretation: too many changes could cause differing results, but so could not enough changes.
+These differences include intentional adaptations, unavoidable changes from lack of access to the original instructions or materials, or changes that the replicators did not expect to be critical.
+A difference in the details of recruitment, such as a change from recruiting participants in person to online, might mean that particular details of a study implementation would no longer be appropriate, or the data quality controls might be inadequate.
+If there are differences in time, place, or subject population between the two studies, researchers may need to change the materials, instructions, or procedure to adapt the experimental paradigm to the new context.
+Such adaptation creates more challenges in interpretation: too many changes could cause differing results, but so could too few changes.
 In sum, when replications fail, we generally do not know why they failed, although we may speculate.
 
-For the goals of large-scale replication projects, it does not matter why any particular study failed to replicate, because the aim is to estimate the proportion of replication effects in a literature.
-In contrast, however, when individual scientists attempt to replicate an effect with the goal of building on it, they do care about why an individual replication failed.
+For the goals of large-scale replication projects, it does not matter why any particular study failed to replicate, because the aim is to estimate the proportion of effects that replicate in a literature.
+In contrast, when individual scientists attempt to replicate an effect with the goal of building on it, they care why an individual replication failed.
 In an uncertain literature, scientists might not want to commit resources to studying extensions of an effect without first checking that they can measure that effect themselves.
-For those individual scientists, it is much more important whether the replication failure is due to a fixable issue with the replication or an intrinsic feature of the original result.
-
+For those individual scientists, it is much more important to know whether the replication failure is due to a fixable issue with their replication attempt or an intrinsic feature of the original result.
+
+While it is possible to speculate after the fact about potential causes of a single replication failure, in most circumstances these causes are hard to discern (absent clear evidence of errors).
 Re-replication can serve as a way to test explanations for replication failure.
-While it is possible to speculate after the fact about potential causes of a single replication failure, in most circumstances these causes are hard to discern (absent clear evidence of errors).
-In contrast, a second replication provides a chance to test explanations by making modifications -- as well as giving another chance for researchers to measure an effect of interest.
+Re-replications can make making modifications to the first replication and give another chance for researchers to measure an effect of interest.
 But what are the chances that a re-replication succeeds?
@@
 <!-- We could frame @ebersole2020 as an attempt to recover the original effects of the 9 studies with significant original effects and non-significant RP:P effects by a combination of high power and design tweaks.
---> The re-replication success rate was thus 2/9 (22%) for studies with non-significant first replications, under favorable, high-resource circumstances.
+--> The re-replication success rate was thus 2/9 (22%) for studies with non-significant first replications under favorable, high-resource circumstances.
 
@@
 
-While @ebersole2020 looked at re-replication success rate in a high resource setting with access to large, multi-site samples and expert input, most early career scientists do not have those kinds of resources to devote to re-replication attempts.
+While @ebersole2020 looked at re-replication success rate in a high resource setting with access to large, multi-site samples and expert input, most early career scientists do not have comparable resources to devote to re-replication attempts.
 On the other hand, early career researchers may also be prone to a different distribution of causes of initial replication failure.
@@
 The focus of the class was best practices in experimental design; thus, students looked at both the original paper and the failed replication to examine potential issues in the replication that they could fix in their rescue project.
-In the present paper, we report the results of `r num_proj` re-replication rescue projects.
+In the present paper, we report the results of `r num_proj` rescue projects.
 We find that a minority of projects (5/17, 29%) successfully recovered the original effect.
@@
 If they opted for a rescue, they were given the option to participate in a collaborative meta-science project and earn authorship on the current paper based on 1) completing a rescue project, 2) reviewing another student's rescue project for reproducibility, and 3) reviewing and approving the final manuscript.
-We report on the result of `r num_proj` rescue projects that opted to be part of the paper and completed data collection.
-
-A spreadsheet of projects, individual project write-ups (both first replications and rescues), individual project data and analyses for rescue projects, and the analytic code for this paper are all available at <https://osf.io/cyk5w/>.
+We report on the result of the `r num_proj` rescue projects by students who completed data collection and opted to be a part of the paper.
+
+A spreadsheet of projects, individual project write-ups (both first replications and rescues), individual project data and analyses for rescue projects, and the analytic code for this paper are all available at <https://osf.io/cyk5w>.
 
@@
 ```{r}
-rel_size <- parsed_d |> filter(type %in% c("original", "rescue")) |> select(target_lastauthor_year, type, N)  |> 
-  pivot_wider(names_from=type, values_from=N) |> mutate(multiplier=rescue/original)
+rel_size <- parsed_d |>
+  filter(type %in% c("original", "rescue")) |>
+  select(target_lastauthor_year, type, N) |>
+  pivot_wider(names_from = type, values_from = N) |>
+  mutate(multiplier = rescue / original)
 
@@
 highest <- quantile(rel_size$multiplier, 1)
-
 ```
@@
 ```{r}
-subj <- parsed_d |> filter(type=="rescue") |> mutate(binary_success=ifelse(replication_score>.5,1,0))
-
-tallied <- subj|> group_by(replication_score) |> tally()
-
-success <- filter(subj, binary_success==1)
-
-d <- read_csv(here("data", "combined_data.csv")) |> filter(type=="rescue")
-
-irr <- cor.test(d$TA_rep_score, d$MCF_rep_score, method="spearman")$estimate
+subj <- parsed_d |>
+  filter(type == "rescue") |>
+  mutate(binary_success = ifelse(replication_score > .5, 1, 0))
+
+tallied <- subj |>
+  group_by(replication_score) |>
+  tally()
+
+success <- filter(subj, binary_success == 1)
+
+d <- read_csv(here("data", "combined_data.csv")) |> filter(type == "rescue")
+
+irr <- cor.test(d$TA_rep_score, d$MCF_rep_score, method = "spearman")$estimate
 
@@
 
-percent_rep <- boyce2023_sample |> mutate(is_rep=ifelse(sub_rep>.5,1,0)) |> summarize(m=mean(is_rep))
-
-overall <- (percent_rep[1])+(1-percent_rep[1])*nrow(success)/nrow(subj)
+percent_rep <- boyce2023_sample |>
+  mutate(is_rep = ifelse(sub_rep > .5, 1, 0)) |>
+  summarize(m = mean(is_rep))
+
+overall <- (percent_rep[1]) + (1 - percent_rep[1]) * nrow(success) / nrow(subj)
 ```
@@
 A list of possible reasons and solutions was given to students (<https://osf.io/dfwk2>).
-In general, we encouraged students to add manipulation checks as appropriate, and to adapt their materials to online studies, which may benefit from attention checks and/or shorter duration.
-For instance, the rescue of @paxton2012 switched from using the Cognitive Reflection Test (CRT) which many online participants are over-familiar with to using the newer CRT-2 which is less overused but attempts to measure the same construct [@thomson2016].
+In general, we encouraged students to add manipulation checks as appropriate and to adapt their materials to online studies, which may benefit from attention checks and/or shorter duration.
+For instance, the rescue of @paxton2012 switched from using the Cognitive Reflection Test (CRT) which many online participants are over-familiar with to using the newer CRT-2 which is used less but attempts to measure the same construct [@thomson2016].
 The rescue of @jara-ettinger2022 discovered that the replication had accidentally used an illustrated version of the stimuli rather than the photographic stimuli used in the original and used the photographic stimuli instead.
@@
 
-For the original study and each replication, we recorded the number of participants post-exclusions.
-For studies where some extra conditions were dropped in some replications, we counted only the participants in the key conditions all replications had for comparability.
+For the original study and each replication, we recorded the number of participants after exclusions.
+For studies where extra conditions were dropped in some replications, we counted only the participants in the key conditions all replications had for comparability.
 For instance, if an original study compared between two critical conditions but also had a baseline control, we did not count the participants in the baseline condition if a replication did not include this condition.
@@
 
-We first discuss the overall rate of replication in the rescue projects, followed by looking at the relative effect sizes of the rescues and correlates of rescue success.
+We first discuss the overall rate of replication in the rescue projects, then we look at the relative effect sizes of the rescues and correlates of rescue success.
 In the last subsection we describe several interesting case studies.
@@
 ```{r smd, fig.cap="Standardized effect sizes of original studies, first replications, rescues, and additional replications if available.
-Due to the large effect size of a couple studies, large effect studies are shown in a separate panel.
-In a few cases, the first replication's key effect was in the same direction as the original with a 95% CI that did not overlap 0; however, in these cases the larger pattern of results was not consistent between original and first replication.
-"}
-
-#test on just one
-colors <- c("Original study"="black", "First replication"="#377EB8", "Rescue"="#E41A1C", "Additional replication"="#984EA3")
-shape <- c("Original study"=21,"First replication"=22,"Rescue"=23,"Additional replication"=24)
-
-big <- parsed_d |> filter(type=="original") |> filter(calc_d_calc>1|target_lastauthor_year=="yeshurun2003") |> select(target_lastauthor_year)
-for_plotting_d <- parsed_d |> filter(!is.na(calc_d_calc)) |> 
-  mutate(point=calc_d_calc, low=calc_d_calc-1.96*calc_d_calc_se, high=calc_d_calc+1.96*calc_d_calc_se) |> 
-  mutate(type=case_when(
-    type=="original" ~ "Original study",
-    type=="rep1" ~ "First replication",
-    type=="rescue" ~ "Rescue",
-    type=="additional" ~ "Additional replication"
+Due to the large effect size of some studies, studies with large effects are shown in a separate panel.
+In a few cases, the first replication's key effect was in the same direction as the original with a 95% CI that did not contain 0.
+However, in these cases the larger pattern of results was not consistent between original and first replication."}
+# test on just one
+colors <- c("Original study" = "black", "First replication" = "#377EB8", "Rescue" = "#E41A1C", "Additional replication" = "#984EA3")
+shape <- c("Original study" = 21, "First replication" = 22, "Rescue" = 23, "Additional replication" = 24)
+
+big <- parsed_d |>
+  filter(type == "original") |>
+  filter(calc_d_calc > 1 | target_lastauthor_year == "yeshurun2003") |>
+  select(target_lastauthor_year)
+for_plotting_d <- parsed_d |>
+  filter(!is.na(calc_d_calc)) |>
+  mutate(point = calc_d_calc, low = calc_d_calc - 1.96 * calc_d_calc_se, high = calc_d_calc + 1.96 * calc_d_calc_se) |>
+  mutate(
+    type = case_when(
+      type == "original" ~ "Original study",
+      type == "rep1" ~ "First replication",
+      type == "rescue" ~ "Rescue",
+      type == "additional" ~ "Additional replication"
     ),
-  type=factor(type, levels=c("Original study", "First replication", "Rescue", "Additional replication")))
-
-smd_scale_small <- ggplot(for_plotting_d |> anti_join(big),aes(x=reorder(name_pretty, point, FUN=max),y=point,ymin=low,ymax=high,shape=type, color=type, fill=type, group=desc(type)))+
-  geom_errorbar(size=.5,width=0, position=position_dodge(width=.5))+
-  geom_point(position=position_dodge(width=.5))+
- coord_flip()+
-  scale_size_area()+
-  geom_hline(yintercept=0,color="black")+
-    scale_color_manual(values=colors, aesthetics=c("color", "fill"))+
-  scale_shape_manual(values=shape)+
-  theme(legend.position = "bottom", 
+    type = factor(type, levels = c("Original study", "First replication", "Rescue", "Additional replication"))
+  )
+
+smd_scale_small <- ggplot(for_plotting_d |> anti_join(big), aes(x = reorder(name_pretty, point, FUN = max), y = point, ymin = low, ymax = high, shape = type, color = type, fill = type, group = desc(type))) +
+  geom_errorbar(size = .5, width = 0, position = position_dodge(width = .5)) +
+  geom_point(position = position_dodge(width = .5)) +
+  coord_flip() +
+  scale_size_area() +
+  geom_hline(yintercept = 0, color = "black") +
+  scale_color_manual(values = colors, aesthetics = c("color", "fill")) +
+  scale_shape_manual(values = shape) +
+  theme(
+    legend.position = "bottom",
     panel.grid.major.x = element_blank(),
-        panel.grid.minor.x=element_blank(),
-        legend.title=element_blank(),
-        legend.text=element_text(size=10)
-        )+
-  labs(y="Standardized mean difference", x="")
-
-level_order = c("Yeshurun & Levy 2003",
+    panel.grid.minor.x = element_blank(),
+    legend.title = element_blank(),
+    legend.text = element_text(size = 10)
+  ) +
+  labs(y = "Standardized mean difference", x = "")
+
+level_order <- c(
+  "Yeshurun & Levy 2003",
   "Ngo et al. 2019",
   "Krauss & Wang 2003",
-                 "Jara-Ettinger et al. 2022")
+  "Jara-Ettinger et al. 2022"
+)
 smd_scale_big <- ggplot(for_plotting_d |> inner_join(big) |>
-                          mutate(name_pretty=factor(name_pretty, levels=level_order)), aes(x=name_pretty,y=point,ymin=low,ymax=high,shape=type, color=type, fill=type, group=desc(type)))+
-  geom_errorbar(size=.5,width=0, position=position_dodge(width=.5))+
-  geom_point(position=position_dodge(width=.5))+
- coord_flip()+
-  scale_size_area()+
-  geom_hline(yintercept=0,color="black")+
-    scale_color_manual(values=colors, aesthetics=c("color", "fill"))+
-    scale_shape_manual(values=shape)+
-  theme(legend.position = "none", 
+  mutate(name_pretty = factor(name_pretty, levels = level_order)), aes(x = name_pretty, y = point, ymin = low, ymax = high, shape = type, color = type, fill = type, group = desc(type))) +
+  geom_errorbar(size = .5, width = 0, position = position_dodge(width = .5)) +
+  geom_point(position = position_dodge(width = .5)) +
+  coord_flip() +
+  scale_size_area() +
+  geom_hline(yintercept = 0, color = "black") +
+  scale_color_manual(values = colors, aesthetics = c("color", "fill")) +
+  scale_shape_manual(values = shape) +
+  theme(
+    legend.position = "none",
     panel.grid.major.x = element_blank(),
-        panel.grid.minor.x=element_blank()
-        )+
-  labs(y="Standardized mean difference", x="", )
-
-#smd_scale_big
-#smd_scale_small
-
-plot_grid(smd_scale_big, smd_scale_small, rel_heights=c(.4,1), nrow=2)
+    panel.grid.minor.x = element_blank()
+  ) +
+  labs(y = "Standardized mean difference", x = "", )
+
+# smd_scale_big
+# smd_scale_small
+
+plot_grid(smd_scale_big, smd_scale_small, rel_heights = c(.4, 1), nrow = 2)
 ```
@@
 As a complement to subjective replication ratings, we also statistically compared the effect sizes of the rescue, first replication, and original study on one preregistered key measure per study [again following @boyce2023].
-Though we did not conduct a systematic review of the literature to identify all possible replications, we also consider the effect sizes obtained in additional replications when we were aware of them (either from other class projects, or external replications in the literature).
+Though we did not conduct a systematic review of the literature to identify all possible replications, we also considered the effect sizes obtained in additional replications when we were aware of them (either from other class projects, or external replications in the literature).
 
@@
 ```{r}
-
 do_d_rma <- function(df) {
-  if(!any(is.na(df$d))){
-  r<- rma(yi=df$d, sei=df$d_se, slab=df$type)
-  return(tibble(rma_d_est=r$beta[,1], rma_d_se=r$se))
+  if (!any(is.na(df$d))) {
+    r <- rma(yi = df$d, sei = df$d_se, slab = df$type)
+    return(tibble(rma_d_est = r$beta[, 1], rma_d_se = r$se))
   }
-  return(tibble(rma_d_est=NA, rma_d_se=NA))
-
+  return(tibble(rma_d_est = NA, rma_d_se = NA))
 }
 
-do_p_orig <- function(es, es_se, rep_es, rep_se){
-  if(!is.na(es)&!is.na(es_se)&!is.na(rep_es)&!is.na(rep_se)){
-    return(Replicate::p_orig(es, es_se**2,rep_es, t2=0.21**2, rep_se**2))
+do_p_orig <- function(es, es_se, rep_es, rep_se) {
+  if (!is.na(es) & !is.na(es_se) & !is.na(rep_es) & !is.na(rep_se)) {
+    return(Replicate::p_orig(es, es_se**2, rep_es, t2 = 0.21**2, rep_se**2))
   }
@@
 
-orig <- parsed_d |> filter(type=="original") |> select(target_lastauthor_year, d=calc_d_calc, d_se=calc_d_calc_se)
-
-orig_v_others <- parsed_d |> select(target_lastauthor_year, type, d=calc_d_calc, d_se=calc_d_calc_se) |> 
-  filter(type!="original") |> 
+orig <- parsed_d |>
+  filter(type == "original") |>
+  select(target_lastauthor_year, d = calc_d_calc, d_se = calc_d_calc_se)
+
+orig_v_others <- parsed_d |>
+  select(target_lastauthor_year, type, d = calc_d_calc, d_se = calc_d_calc_se) |>
+  filter(type != "original") |>
   group_by(target_lastauthor_year) |>
   nest() |>
-  mutate(d_rma_result=map(data, do_d_rma)) |> 
+  mutate(d_rma_result = map(data, do_d_rma)) |>
   unnest_wider(d_rma_result) |>
@@
   rowwise() |>
-  mutate(d_p_orig=do_p_orig(d, d_se, rma_d_est, rma_d_se))
-
-orig_v_rr <- parsed_d |> select(target_lastauthor_year, type, d=calc_d_calc, d_se=calc_d_calc_se) |> 
-  filter(type=="rescue"|type=="rep1") |> 
+  mutate(d_p_orig = do_p_orig(d, d_se, rma_d_est, rma_d_se))
+
+orig_v_rr <- parsed_d |>
+  select(target_lastauthor_year, type, d = calc_d_calc, d_se = calc_d_calc_se) |>
+  filter(type == "rescue" | type == "rep1") |>
   group_by(target_lastauthor_year) |>
   nest() |>
-  mutate(d_rma_result=map(data, do_d_rma)) |> 
+  mutate(d_rma_result = map(data, do_d_rma)) |>
   unnest_wider(d_rma_result) |>
@@
   rowwise() |>
-  mutate(d_p_orig=do_p_orig(d, d_se, rma_d_est, rma_d_se))
-
-orig_v_rescue <- parsed_d |>   filter(type=="rescue") |> 
-  select(target_lastauthor_year, type, res_d=calc_d_calc, res_d_se=calc_d_calc_se) |> 
+  mutate(d_p_orig = do_p_orig(d, d_se, rma_d_est, rma_d_se))
+
+orig_v_rescue <- parsed_d |>
+  filter(type == "rescue") |>
+  select(target_lastauthor_year, type, res_d = calc_d_calc, res_d_se = calc_d_calc_se) |>
   left_join(orig) |>
   rowwise() |>
-  mutate(d_p_orig=do_p_orig(d, d_se, res_d, res_d_se))
-
-orig_v_not_rescue <- parsed_d |> select(target_lastauthor_year, type, d=calc_d_calc, d_se=calc_d_calc_se) |> 
-  filter(type!="original", type!="rescue") |> 
+  mutate(d_p_orig = do_p_orig(d, d_se, res_d, res_d_se))
+
+orig_v_not_rescue <- parsed_d |>
+  select(target_lastauthor_year, type, d = calc_d_calc, d_se = calc_d_calc_se) |>
+  filter(type != "original", type != "rescue") |>
   group_by(target_lastauthor_year) |>
   nest() |>
-  mutate(d_rma_result=map(data, do_d_rma)) |> 
+  mutate(d_rma_result = map(data, do_d_rma)) |>
   unnest_wider(d_rma_result) |>
@@
   rowwise() |>
-  mutate(d_p_orig=do_p_orig(d, d_se, rma_d_est, rma_d_se))
-
-rescue_only <- parsed_d |> filter(type=="rescue") |> select(target_lastauthor_year, d=calc_d_calc, d_se=calc_d_calc_se)
-
-rescue_v_reps <- parsed_d |> select(target_lastauthor_year, type, d=calc_d_calc, d_se=calc_d_calc_se) |> 
-  filter(type!="original", type!="rescue") |> 
+  mutate(d_p_orig = do_p_orig(d, d_se, rma_d_est, rma_d_se))
+
+rescue_only <- parsed_d |>
+  filter(type == "rescue") |>
+  select(target_lastauthor_year, d = calc_d_calc, d_se = calc_d_calc_se)
+
+rescue_v_reps <- parsed_d |>
+  select(target_lastauthor_year, type, d = calc_d_calc, d_se = calc_d_calc_se) |>
+  filter(type != "original", type != "rescue") |>
   group_by(target_lastauthor_year) |>
   nest() |>
-  mutate(d_rma_result=map(data, do_d_rma)) |> 
+  mutate(d_rma_result = map(data, do_d_rma)) |>
   unnest_wider(d_rma_result) |>
@@
   rowwise() |>
-  mutate(d_p_orig=do_p_orig(d, d_se, rma_d_est, rma_d_se))
-
- all <- orig_v_others |> select(target_lastauthor_year, orig_v_other=d_p_orig) |> 
-   left_join(orig_v_rr |> select(target_lastauthor_year, orig_v_rr=d_p_orig)) |> 
-  left_join(orig_v_rescue |> select(target_lastauthor_year, orig_v_rescue=d_p_orig)) |> 
-  left_join(orig_v_not_rescue |> select(target_lastauthor_year, orig_v_not_rescue=d_p_orig)) |> 
-  left_join(rescue_v_reps |> select(target_lastauthor_year, rescue_v_reps=d_p_orig))
-
-main_summ <- all |> ungroup() |> select(orig_v_other) |>
-  summarize(median=median(orig_v_other, na.rm=T),
-            low=quantile(orig_v_other, .25, na.rm=T),
-            high=quantile(orig_v_other, .75, na.rm=T),
-            less_than=sum(orig_v_other<.05, na.rm=T)/sum(!is.na(orig_v_other)))
-
-rr_summ <- all |> ungroup() |> select(orig_v_rr) |>
-  summarize(median=median(orig_v_rr, na.rm=T),
-            low=quantile(orig_v_rr, .25, na.rm=T),
-            high=quantile(orig_v_rr, .75, na.rm=T),
-            less_than=sum(orig_v_rr<.05, na.rm=T)/sum(!is.na(orig_v_rr)))
-
-rescue_summ <- all |> ungroup() |> select(orig_v_rescue) |>
-  summarize(median=median(orig_v_rescue, na.rm=T),
-            low=quantile(orig_v_rescue, .25, na.rm=T),
-            high=quantile(orig_v_rescue, .75, na.rm=T),
-            less_than=sum(orig_v_rescue<.05, na.rm=T)/sum(!is.na(orig_v_rescue)))
-
-rep_summ <- all |> ungroup() |> select(orig_v_not_rescue) |>
-  summarize(median=median(orig_v_not_rescue, na.rm=T),
-            low=quantile(orig_v_not_rescue, .25, na.rm=T),
-            high=quantile(orig_v_not_rescue, .75, na.rm=T),
-            less_than=sum(orig_v_not_rescue<.05, na.rm=T)/sum(!is.na(orig_v_not_rescue)))
-
-rescue_rep_summ <- all |> ungroup() |> select(rescue_v_reps) |>
-  summarize(median=median(rescue_v_reps, na.rm=T),
-            low=quantile(rescue_v_reps, .25, na.rm=T),
-            high=quantile(rescue_v_reps, .75, na.rm=T),
-            less_than=sum(rescue_v_reps<.05, na.rm=T)/sum(!is.na(rescue_v_reps)))
+  mutate(d_p_orig = do_p_orig(d, d_se, rma_d_est, rma_d_se))
+
+all <- orig_v_others |>
+  select(target_lastauthor_year, orig_v_other = d_p_orig) |>
+  left_join(orig_v_rr |> select(target_lastauthor_year, orig_v_rr = d_p_orig)) |>
+  left_join(orig_v_rescue |> select(target_lastauthor_year, orig_v_rescue = d_p_orig)) |>
+  left_join(orig_v_not_rescue |> select(target_lastauthor_year, orig_v_not_rescue = d_p_orig)) |>
+  left_join(rescue_v_reps |> select(target_lastauthor_year, rescue_v_reps = d_p_orig))
+
+main_summ <- all |>
+  ungroup() |>
+  select(orig_v_other) |>
+  summarize(
+    median = median(orig_v_other, na.rm = T),
+    low = quantile(orig_v_other, .25, na.rm = T),
+    high = quantile(orig_v_other, .75, na.rm = T),
+    less_than = sum(orig_v_other < .05, na.rm = T) / sum(!is.na(orig_v_other))
+  )
+
+rr_summ <- all |>
+  ungroup() |>
+  select(orig_v_rr) |>
+  summarize(
+    median = median(orig_v_rr, na.rm = T),
+    low = quantile(orig_v_rr, .25, na.rm = T),
+    high = quantile(orig_v_rr, .75, na.rm = T),
+    less_than = sum(orig_v_rr < .05, na.rm = T) / sum(!is.na(orig_v_rr))
+  )
+
+rescue_summ <- all |>
+  ungroup() |>
+  select(orig_v_rescue) |>
+  summarize(
+    median = median(orig_v_rescue, na.rm = T),
+    low = quantile(orig_v_rescue, .25, na.rm = T),
+    high = quantile(orig_v_rescue, .75, na.rm = T),
+    less_than = sum(orig_v_rescue < .05, na.rm = T) / sum(!is.na(orig_v_rescue))
+  )
+
+rep_summ <- all |>
+  ungroup() |>
+  select(orig_v_not_rescue) |>
+  summarize(
+    median = median(orig_v_not_rescue, na.rm = T),
+    low = quantile(orig_v_not_rescue, .25, na.rm = T),
+    high = quantile(orig_v_not_rescue, .75, na.rm = T),
+    less_than = sum(orig_v_not_rescue < .05, na.rm = T) / sum(!is.na(orig_v_not_rescue))
+  )
+
+rescue_rep_summ <- all |>
+  ungroup() |>
+  select(rescue_v_reps) |>
+  summarize(
+    median = median(rescue_v_reps, na.rm = T),
+    low = quantile(rescue_v_reps, .25, na.rm = T),
+    high = quantile(rescue_v_reps, .75, na.rm = T),
+    less_than = sum(rescue_v_reps < .05, na.rm = T) / sum(!is.na(rescue_v_reps))
+  )
 ```
@@
 ```{r tab-porig}
-names <- parsed_d |> select(target_lastauthor_year, name_pretty) |> unique()
-
-all |> ungroup() |>  left_join(names) |> select(Paper=name_pretty, `All reps`=orig_v_other, "1st Rep and Rescue"=orig_v_rr, "Rescue" = orig_v_rescue, "Non-rescue"=orig_v_not_rescue, "Other reps"=rescue_v_reps) |> knitr::kable(format="latex", booktabs=T, linesep="", caption="$P$-original values between different sets of experiments.
+names <- parsed_d |>
+  select(target_lastauthor_year, name_pretty) |>
+  unique()
+
+all |>
+  ungroup() |>
+  left_join(names) |>
+  select(Paper = name_pretty, `All reps` = orig_v_other, "1st Rep and Rescue" = orig_v_rr, "Rescue" = orig_v_rescue, "Non-rescue" = orig_v_not_rescue, "Other reps" = rescue_v_reps) |>
+  knitr::kable(format = "latex", booktabs = T, linesep = "", caption = "$P$-original values between different sets of experiments.
 The primary analysis is between the original result and the meta-analytic aggregation of all replications.
-All $p$-original values assume an imputed heterogeneity value of $\\tau$=.21.", digits=3) |>
-  add_header_above(c(" "=1, "Original and"=4, "Rescue and"=1)) |> add_header_above(c(" "=1, "p-original comparing between"=5))
-
+All $p$-original values assume an imputed heterogeneity value of $\\tau$=.21.", digits = 3) |>
+  add_header_above(c(" " = 1, "Original and" = 4, "Rescue and" = 1)) |>
+  add_header_above(c(" " = 1, "p-original comparing between" = 5))
 ```
@@
 The value of $p$-original represents how likely an effect size equal to or more extreme than the original effect size is to occur if it comes from a distribution of population effect sizes defined by the mean and standard error of the replications (combined meta-analytically) with a between-population standard deviation of $\tau=.21$ [imputed from @olsson-collentine2020].
-That is, $p$-original is a measure of the statistical consistency of the original result with the totality of the replications, assuming a given level of heterogeneity of effects between studies.
+That is, $p$-original measures the statistical consistency of the original result with the totality of the replications, assuming a given level of heterogeneity of effects between studies.
 Smaller $p$-original values indicate more inconsistency.
@@
 
-As secondary measures, we calculated the $p$-original values between a) the original and just the first replication and rescue (i.e.
+As secondary measures, we calculated the $p$-original values between a) the original and the first replication and rescue (i.e.
 excluding additional replications), b) the original and the rescue, c) the original and non-rescue replications, and d) the rescue and other replications.
@@
 ```{r}
-orig <- parsed_d |> filter(type=="original") |> select(target_lastauthor_year, d=calc_d_calc, d_se=calc_d_calc_se, es=calc_ES, es_se=calc_SE)
+orig <- parsed_d |>
+  filter(type == "original") |>
+  select(target_lastauthor_year, d = calc_d_calc, d_se = calc_d_calc_se, es = calc_ES, es_se = calc_SE)
 
 predInts_het <- parsed_d |>
-  filter(type!="original") |> 
+  filter(type != "original") |>
   group_by(target_lastauthor_year, name_pretty) |>
-  select(target_lastauthor_year, type, rep_d=calc_d_calc, rep_d_se=calc_d_calc_se, rep_es=calc_ES, rep_es_se=calc_SE) |> 
+  select(target_lastauthor_year, type, rep_d = calc_d_calc, rep_d_se = calc_d_calc_se, rep_es = calc_ES, rep_es_se = calc_SE) |>
   left_join(orig) |>
-  group_by(target_lastauthor_year,type) |> 
+  group_by(target_lastauthor_year, type) |>
   nest() |>
-  mutate(d_pred_int=map(data,do_d_predInt_het)) |> 
+  mutate(d_pred_int = map(data, do_d_predInt_het)) |>
   unnest_wider(d_pred_int) |>
   unnest_wider(data)
-
 ```
@@
 ```{r cor-table}
-
-original <- parsed_d |> filter(type=="original") |> 
-  rename_with(~str_c("original_",.), .cols=-target_lastauthor_year)
-
-rep1 <- parsed_d |> filter(type=="rep1") |> select(target_lastauthor_year, rep_N=N)
-
-for_cor <- subj |> left_join(original) |> left_join(rep1) |> 
+original <- parsed_d |>
+  filter(type == "original") |>
+  rename_with(~ str_c("original_", .), .cols = -target_lastauthor_year)
+
+rep1 <- parsed_d |>
+  filter(type == "rep1") |>
+  select(target_lastauthor_year, rep_N = N)
+
+for_cor <- subj |>
+  left_join(original) |>
+  left_join(rep1) |>
   mutate(
-  social=ifelse(subfield=="social", 1,0),
-  other_psych=ifelse(subfield=="other-psych",1,0), 
-  is_within=ifelse(within_between=="within", 1,0), 
-  change_platform=ifelse(on_turk==original_on_turk, 0,1),
-  log_trials=log(repeated_measure),
-  log_sample=log(N),
-  log_ratio_ss=log(N/original_N),
-  rep_1_log_sample=log(rep_N),
-  log_ratio_rep1_orig=log(rep_N/original_N),
-  log_ratio_rescue_rep1=log(N/rep_N),
-  open_data=ifelse(open_data=="yes",1,0),
-  open_mat=ifelse(open_materials=="yes", 1,0),
-  stanford=ifelse(stanford_internal=="yes",1,0)) |> 
+    social = ifelse(subfield == "social", 1, 0),
+    other_psych = ifelse(subfield == "other-psych", 1, 0),
+    is_within = ifelse(within_between == "within", 1, 0),
+    change_platform = ifelse(on_turk == original_on_turk, 0, 1),
+    log_trials = log(repeated_measure),
+    log_sample = log(N),
+    log_ratio_ss = log(N / original_N),
+    rep_1_log_sample = log(rep_N),
+    log_ratio_rep1_orig = log(rep_N / original_N),
+    log_ratio_rescue_rep1 = log(N / rep_N),
+    open_data = ifelse(open_data == "yes", 1, 0),
+    open_mat = ifelse(open_materials == "yes", 1, 0),
+    stanford = ifelse(stanford_internal == "yes", 1, 0)
+  ) |>
   filter(!is.na(replication_score))
@@
 
-preds <- c("open_data",  "open_mat", "stanford", "change_platform", 
+preds <- c(
+  "open_data", "open_mat", "stanford", "change_platform",
   "log_ratio_ss", "is_within", "single_vignette", "log_sample",
-           "log_trials", "social", "other_psych", "rep_1_log_sample", "log_ratio_rep1_orig", "log_ratio_rescue_rep1")
+  "log_trials", "social", "other_psych", "rep_1_log_sample", "log_ratio_rep1_orig", "log_ratio_rescue_rep1"
+)
 
 cors <- tibble(preds = preds) |>
-  mutate(r = sapply(preds, function(x) sub_cor(x, stat = "estimate")),
-         p = sapply(preds, function(x) sub_cor(x, stat = "p"))) |>
-
-  mutate(Predictors=factor(preds, levels=c("social", "other_psych", "is_within", "single_vignette", "change_platform", "open_data", "open_mat", "stanford", "pub_year", "log_trials", "log_sample", "log_ratio_ss", "rep_1_log_sample", "log_ratio_rep1_orig", "log_ratio_rescue_rep1"), labels=c("Social", "Other psych", "Within subjects", "Single vignette", "Switch to online", "Open data", "Open materials", "Original authors at Stanford", "Publication year", "Log number of trials", "Log original sample size", "Log rescue/original sample size", "Log replication sample size", "Log replication/original sample size", "Log rescue/replication sample size"))) |> arrange(Predictors) |> select(Predictors, r, p)
+  mutate(
+    r = sapply(preds, function(x) sub_cor(x, stat = "estimate")),
+    p = sapply(preds, function(x) sub_cor(x, stat = "p"))
+  ) |>
+  mutate(Predictors = factor(preds, levels = c("social", "other_psych", "is_within", "single_vignette", "change_platform", "open_data", "open_mat", "stanford", "pub_year", "log_trials", "log_sample", "log_ratio_ss", "rep_1_log_sample", "log_ratio_rep1_orig", "log_ratio_rescue_rep1"), labels = c("Social", "Other psych", "Within subjects", "Single vignette", "Switch to online", "Open data", "Open materials", "Original authors at Stanford", "Publication year", "Log number of trials", "Log original sample size", "Log rescue/original sample size", "Log replication sample size", "Log replication/original sample size", "Log rescue/replication sample size"))) |>
+  arrange(Predictors) |>
+  select(Predictors, r, p)
 
 library(kableExtra)
-knitr::kable(cors, digits = 3, align='rcc', format="latex", booktabs=T, linesep="", caption="Correlations between an individual predictor and the subjective replication score of the rescue project.
+knitr::kable(cors, digits = 3, align = "rcc", format = "latex", booktabs = T, linesep = "", caption = "Correlations between an individual predictor and the subjective replication score of the rescue project.
 The first set of predictors were pre-registered based on the correlates used in Boyce et al.
@@
 (2023).
-The last three predictors were added post-hoc.") |> row_spec(11, hline_after=T)
-
+The last three predictors were added post-hoc.") |> row_spec(11, hline_after = T)
 ```
@@
 All of the correlations are presented in Table \@ref(tab:cor-table).
-The number of rescues is small, and many of these predictors are correlated, so we caution against over interpretation.
+The number of rescues is small, and many of these predictors are correlated, so we caution against over-interpretation.
 
@@
 ```{r tab-size}
-parsed_d |> select(name_pretty, type, N, closeness, replication_score) |> 
-  filter(type!="additional") |> 
-  pivot_wider(names_from="type", values_from=c(N, closeness, replication_score)) |> 
-  select(paper=name_pretty, replication_score_rescue, N_original, N_rep1, N_rescue,
-         "Replication \\\\  closeness"=closeness_rep1, closeness_rescue) |> arrange(replication_score_rescue|> desc()) |> knitr::kable(align="lllll", format="latex", booktabs=T, linesep="", caption="Comparison of sample size for original, replication, and rescue samples and measures of closeness for replication and rescue samples.", col.names=c("", "", "Original", "Replication", "Rescue", "Replication", "Rescue")) |> add_header_above(c("Paper"=1, "Score"=1, "N"=3, "closeness"=2))
-
+parsed_d |>
+  select(name_pretty, type, N, closeness, replication_score) |>
+  filter(type != "additional") |>
+  pivot_wider(names_from = "type", values_from = c(N, closeness, replication_score)) |>
+  select(
+    paper = name_pretty, replication_score_rescue, N_original, N_rep1, N_rescue,
+    "Replication \\\\  closeness" = closeness_rep1, closeness_rescue
+  ) |>
+  arrange(replication_score_rescue |> desc()) |>
+  knitr::kable(align = "lllll", format = "latex", booktabs = T, linesep = "", caption = "Comparison of sample size for original, replication, and rescue samples and measures of closeness for replication and rescue samples.", col.names = c("", "", "Original", "Replication", "Rescue", "Replication", "Rescue")) |>
+  add_header_above(c("Paper" = 1, "Score" = 1, "N" = 3, "closeness" = 2))
 ```
@@
 The rescue of @krauss2003 was successful despite an unsuccessful replication.
-This study looked at the influence of guided thinking on whether or not people gave correct justifications (drawn or written) for their answer on the Monty Hall problem.
-The original paper reported correct justification from 2/67 (`r round(2/67*100)`%) in the control condition and 13/34 (`r round(13/34*100)`%) in the guided thinking condition.
+This study looked at the influence of guided thinking on whether people gave correct justifications (drawn or written) for their answer on the Monty Hall problem.
+The original paper reported correct justifications from 2/67 (`r round(2/67*100)`%) participants in the control condition and 13/34 (`r round(13/34*100)`%) in the guided thinking condition.
 The first replication struggled to recruit participants who were naive to the problem (an exclusion criterion), and many participants gave very short text responses in the provided text box (only textual responses were allowed).
@@
 The rescue targeted these issues by adding a pre-screening that ensured participants were not familiar with the Monty Hall problem, changed the content items for the problem and changed its name (to reduce googling for answers), and had participants upload drawings for their justifications.
-Collectively, we believe these changes brought the rescue closer to the intent of the original.
+We believe these changes collectively brought the rescue closer to the intent of the original.
 The rescue had 1/40 (`r round(1/40*100)`%) correct justifications in the control condition and 6/35 (`r round(6/35*100)`%) in the guided thinking condition.
@@
 An additional replication from the literature, @ngo2021 successfully replicated @ngo2019.
-There are reasons to think that some effect sizes in the literature may be inflated [@opensciencecollaboration; @camerer2018], and it is also possible that changes to experiments or switches to online could result in noisier samples and thus smaller effect sizes.
+There are reasons to think that some effect sizes in the literature may be inflated [@opensciencecollaboration; @camerer2018], and it is also possible that changes to experiments or moving data collection online could result in noisier samples and thus smaller effect sizes.
 Therefore, replications with smaller samples than the original (even if powered to the original effect size), may not be very diagnostic, and could potentially benefit from a re-replication.
@@
 They showed participants a number of images and then hours later (after either sleep or no sleep) measured their recall for parts of the images.
-The first replication struggled to recruit participants to complete a followup session after sleep and only reported a sample size of 23 (the original had 48).
-The rescue attempted to recruit a larger sample (target 88), but also experienced difficulties getting participants to complete the second part of the experiment 12 hours after the first, managing also only to recruit 23 people.
+The first replication struggled to recruit participants to complete a followup session after sleep and reported a sample size of only 23 (the original had 48).
+The rescue attempted to recruit a larger sample (target 88), but experienced difficulties getting participants to complete the second part of the experiment 12 hours after the first, also managing to recruit only 23 people.
 The lesson here may be that sleep research is difficult to conduct online.
 However, an online replication by @denis2022 reports qualitatively similar (but quantitatively smaller) results to @payne2008 on related but not identical measures.
-@denis2022 which has an overlapping author team to @payne2008 is included here as an additional replication.
+@denis2022, which has an overlapping author team to @payne2008, is included here as an additional replication.
 
@@
 The reported rescue projects are a small sample of replications, leading to highly uncertain estimates.
-Additionally, they were chosen non-randomly, as they were doubly selected for based on student interest -- once for the original replication and again for the rescue.
-However, this selection bias is likely to correlate with how graduate students and other early career researchers choose what topics to work on and what studies to build on.
+Additionally, they were chosen non-randomly, as they were doubly selected for based on student interest---once for the original replication and again for the rescue.
+However, this selection bias is likely to correlate with how graduate students and other early-career researchers choose what topics to work on and what studies to build on.
 Nevertheless, our estimate is still broadly consistent with that of ManyLabs 5 [29% vs. 22%, @ebersole2020].
 
-One potentially salient limitation of our work here is that the rescue projects (and the first replications) were primarily conducted by first year PhD students; hence the generality of our conclusions to other investigators is unknown.
+One potentially salient limitation of our work here is that the rescue projects (and the first replications) were primarily conducted by first-year PhD students; hence the generality of our conclusions to other investigators is unknown.
 We believe, however, that this is more of an apparent than an actual limitation.
-Students were enrolled in a highly-competitive graduate program where it is expected that PhD students author peer-reviewed papers; several of the rescuers already had published first-authored peer reviewed articles.
+Students were enrolled in a highly competitive graduate program where it is expected that PhD students author peer-reviewed papers; several of the rescuers already had published first-authored peer reviewed articles.
 Thus, while we refer to the rescuers as students, they are investigators doing experiments that become part of the literature.
@@
 
-We have focused here on a narrow type of replication and rescue: that done by an early career researcher with the goal of establishing whether this is a result *they* can build on.
+We have focused here on a narrow type of replication and rescue: that done by an early-career researcher with the goal of establishing whether *they* can build on a result.
 We acknowledge that this type of replication exists as part of a wider ecosystem of replications that have different properties and are done for different reasons.

### 2024-10-14 manuscript/coverletter/collabra_response_2.tex
cover letter

\documentclass{stanfordletter}
%\makelabels

%\makelabels
\usepackage{todonotes}
\usepackage{varioref}
\usepackage{xr}
\externaldocument[paper-]{../revision}
\usepackage[american]{babel}
\usepackage{csquotes}
\usepackage[backend=biber,style=apa,doi=false,url=false,hyperref=true,apamaxprtauth=30,uniquename=false]{biblatex}
\usepackage{framed}
\DeclareLanguageMapping{american}{american-apa}
\newcommand{\citet}[1]{\textcite{#1}}
\newcommand{\citep}[1]{\parencite{#1}}

\usepackage{longtable,booktabs,array}
\usepackage{float}

\providecommand{\tightlist}{%
	\setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}

\newcounter{section}

\newcommand{\section}[1]{
	\bigskip
	{\normalfont\Large\bfseries #1}}

\newcommand{\theysaid}[1]{\begin{leftbar} \noindent 
		\textsl{ #1}\end{leftbar}}

\newcommand{\revised}[1]{\begin{quote}	#1 \end{quote}}

\usepackage{hyperref}
\begin{document}
	\name{Veronica Boyce}
	\signature{\vspace{-35pt} Veronica Boyce, \\ on behalf of the author team}

	\begin{letter}{Professor Don van Ravenzwaaij \\ Editor-in-Chief \\ Collabra: Psychology }

		\opening{Dear Dr. van Ravenzwaaij,}

		Thank you for your decision letter. We are glad that our edits improved the manuscript, and we thank you for your additional comments, which we have addressed.

		\theysaid{There are some remaining considerations with data accessibility. The file combined\_data.csv contains a number of links in the columns write\_up\_link and github\_link, but none of them are hyperlinked (neither when I access the file directly on OSF, nor when I download it and open locally).}

		This is a good point. Unfortunately, we can't put links in a csv because it's a plain text file format, but we have added a clickable links document for each of the 3 ways someone might access the data. 
		\begin{itemize}
			\item Downloading: We added a .xlsx version of combined\_data that has hyperlinks. 
			\item View on Github: We added a markdown format table, which github renders into a table with clickable links (\url{https://github.com/langcog/251-rescue-projects/blob/main/data/combined_data.md}).
			\item View on OSF: The best format we could find where OSF will display clickable hyperlinks was a pdf with a table of projects and links (\url{https://osf.io/r2d6q}). 
		\end{itemize}

	We have added bolded text to our README linking to these different ways of viewing the links in a hyperlinked format.

	\theysaid{Related, picking for instance https://rpubs.com/troutman/rescue\_final, when I attempt to click on the link for Code and Data (https://github.com/psych251/chou2016\_rescue), I get a message that github refuses to connect.}

	Thanks for bringing this up. We believe it's due to how the security measures of GitHub and OSF, not allowing pages in their domains to be embedded (which is how RPubs tries to open links). We don't know how to fix this, but we have added a note about it to the README saying that one needs to right-click to open the links in a new tab.

	\theysaid{Ideally, I’d like the links to pre-registration and to code \& data to be added to the combined\_data.csv spreadsheet.}

	The non-clickable links are in the combined\_data.csv spreadsheet, and now the same spreadsheet (with clickable links) is downloadable as combined\_data.xlsx or viewable on GitHub as combined\_data.md, and we have documented this in the README.

	\theysaid{Last small thing, your revised text contains several typos and grammatical errors.}

	Thanks for pointing this out, and I apologize for these errors. Another author (who was not the one who introduced the errors) has now proofread the manuscript twice to correct typos and amend grammatical errors and confusing wording.

			\closing{Sincerely,}

		\pagebreak

		\end{letter}

\end{document}

### 2024-10-14 manuscript/manuscript.Rmd
second proofreading pass

@@
 
-In psychology, large scale replication projects have found that around half of studies successfully replicate.
+In psychology, large-scale replication projects have found that around half of studies successfully replicate.
 Across 100 studies with positive results, the reproducibility project in psychology (RP:P) replicated 36%-47% depending on the metric for replication success [@opensciencecollaboration].
@@
 Psychology is not the only discipline where many studies do not replicate.
-Large scale replication projects in other disciplines have found 39/97 of studies with positive effects (40%) replicating in cancer biology [@errington2021], 11/18 studies (61%) replicating in economics [@camerer2016], and 31/40 studies (78%) replicating in experimental philosophy [@cova2021].
+Large-scale replication projects in other disciplines have found 39/97 of studies with positive effects (40%) replicating in cancer biology [@errington2021], 11/18 studies (61%) replicating in economics [@camerer2016], and 31/40 studies (78%) replicating in experimental philosophy [@cova2021].
 Across these disciplines, and especially in psychology, large-scale replications indicate that the probability of scientists failing to replicate published findings is substantial.
@@
 These differences include intentional adaptations, unavoidable changes from lack of access to the original instructions or materials, or changes that the replicators did not expect to be critical.
-A difference in the details of recruitment, such as a change from recruiting participants in person to online, might mean that particular details of a study implementation would no longer be appropriate, or the data quality controls might be inadequate.
+A difference in the details of recruitment, such as changing from recruiting participants in person to online, might mean that particular details of a study implementation are no longer appropriate, or the data quality controls are inadequate.
 If there are differences in time, place, or subject population between the two studies, researchers may need to change the materials, instructions, or procedure to adapt the experimental paradigm to the new context.
@@
 Re-replication can serve as a way to test explanations for replication failure.
-Re-replications can make making modifications to the first replication and give another chance for researchers to measure an effect of interest.
+Re-replications can make modifications to the first replication and give another chance for researchers to measure an effect of interest.
 But what are the chances that a re-replication succeeds?
@@
 
-While @ebersole2020 looked at re-replication success rate in a high resource setting with access to large, multi-site samples and expert input, most early career scientists do not have comparable resources to devote to re-replication attempts.
-On the other hand, early career researchers may also be prone to a different distribution of causes of initial replication failure.
-Thus, it is an open question what the re-replication rate is for failed replications by early career researchers.
-Further, estimating this rate could inform researchers' decisions on what to do next after failed replications.
+While @ebersole2020 looked at re-replication success rate in a high-resource setting with access to large, multi-site samples and expert input, most early-career scientists do not have comparable resources to devote to re-replication attempts.
+On the other hand, early-career researchers may also be prone to a different distribution of causes of initial replication failure.
+Thus, it is an open question what the re-replication rate is for failed replications by early-career researchers.
+Further, estimating this rate could inform researchers' decisions on what to do next when a replication fails.
 
@@
 PSYCH 251 is a graduate-level experimental methods class taught by MCF.
-In previous years, students have conducted replication projects [@boyce2023; @hawkins2018].
+In previous years, students conducted replication projects [@boyce2023; @hawkins2018].
 In Fall 2023, students were offered the option to complete a "rescue" project where they re-replicated one of the unsuccessful replications from a previous year.
@@
 
-Students were required to think of reasons the first replication might not have worked, and address them if they could.
+Students were required to think of reasons why the first replication might not have worked, and address them if they could.
 A list of possible reasons and solutions was given to students (<https://osf.io/dfwk2>).
@@
 @tarampi2016 had participants do a timed navigation task where they wrote L or R to indicate which way to turn at each intersection on a paper map.
-The replication ported this experiment online and had participants click a drop down menu to select left or right for each turn.
-The rescue removed the unwieldy drop down menus and opted to have participants press keys on the keyboard to indicate the direction of a turn, which seemed like a more natural interface.
+The replication ported this experiment online and had participants use a dropdown menu to select left or right for each turn.
+The rescue removed the unwieldy dropdown menus and opted to have participants press keys on the keyboard to indicate the direction of a turn, which seemed like a more natural interface.
 Once experimental designs and analytic plans were approved by class TAs (VB and BP), students pre-registered and ran their samples.
 
-With one exception, samples were collected on Prolific [the rescue of @yeshurun2003 ran in-person on the Stanford student subject pool].
-We tried to power studies adequately [with a target of 2.5x original following @simonsohn2015], but due to cost constraints, not all studies were powered at this level.
+With one exception, samples were collected on Prolific [the rescue of @yeshurun2003 ran in person on the Stanford student subject pool].
+We tried to power studies adequately [with a target sample size of 2.5x the original study following @simonsohn2015], but due to cost constraints, not all studies were powered at this level.
 The rescues had on average `r round(m,2)` times the original sample post-exclusion (median: `r round(mid,2)`, IQR: `r round(low,2)` - `r round(high,2)`, minimum: `r round(lowest, 2)`, maximum: `r round(highest,2)`, see Table \@ref(tab:tab-size) for all sample sizes).
@@
 In order to statistically compare the key measures, we needed effect sizes reported in the same way for each original study, first replication, and rescue.
-When effects were not reported in consistent ways across original and replications, we recalculated effects from raw data when necessary to obtain comparable values.
+When effects were not reported in consistent ways across original and replications, we recalculated effects from raw data to obtain comparable values.
 
@@
 We recorded the same set of potential correlates that were used in @boyce2023 for original, first replication, and rescue (these were already rated for original and first replication).
-These potential correlates included the subfield of the study (cognitive, social, or other psychology), its publication year, experimental design features including whether it was a within- or between-subject design, whether each condition was instantiated with one vignette or multiple, how many items each participant saw, and whether there were open materials and open data.
+These potential correlates included the subfield of the study (cognitive, social, or other psychology), its publication year, experimental design features including whether it used a within- or between-subject design, whether each condition was instantiated with one vignette or multiple, how many items each participant saw, and whether there were open materials and open data.
 
@@
 For instance, if an original study compared between two critical conditions but also had a baseline control, we did not count the participants in the baseline condition if a replication did not include this condition.
-We also recorded whether each study was conducted online using a crowd-sourced platform or not.
+We also recorded whether each study was conducted using an online crowdsourcing platform or not.
 
@@
 For instance, two studies may both find that condition 1 results in a significantly higher outcome measure than condition 2, but the effect magnitudes may be sufficiently different that they are statistically unlikely to have come from the same population.
-On the other hand, one study may find a statistically significant, but imprecisely estimated effect in a small sample, and a second study may find a near-zero (null) effect, but the effect estimates from the two studies may be statistically compatible, despite one supporting a hypothesized difference and the other not.
+On the other hand, one study may find a statistically significant, but imprecisely estimated, effect in a small sample, and a second study may find a near-zero (null) effect.
+The effect estimates from the two studies might be statistically compatible, despite one supporting a hypothesized difference and the other not.
 
@@
 library(kableExtra)
-knitr::kable(cors, digits = 3, align = "rcc", format = "latex", booktabs = T, linesep = "", caption = "Correlations between an individual predictor and the subjective replication score of the rescue project.
+knitr::kable(cors, digits = 3, align = "rcc", format = "latex", booktabs = T, linesep = "", caption = "Correlations between individual predictors and the subjective replication score of the rescue project.
 The first set of predictors were pre-registered based on the correlates used in Boyce et al.
 (2023).
-Original authors at Stanford refers to at the time of the first replication as this may mean the first replication was not independent.
+Original authors at Stanford refers to whether the any of the study's authors were affiliated with Stanford at the time of the first replication, as this may mean the first replication was not independent.
 For details about how the predictors were coded, see the Methods section of Boyce et al.
@@
 
-The strongest correlates of rescue success were open materials, a small sample size on the first replication, a small sample size on the first replication relative to the original sample size, and a large rescue sample size relative to the first replication.
+The strongest correlates of rescue success were open materials, a small sample size in the first replication, a small sample size in the first replication relative to the original sample size, and a large rescue sample size relative to the first replication.
 None of the pre-registered correlates meet the conventional significance threshold; the two correlates based on ratios that reflect a relatively smaller replication sample size are marginally significant.
 
-Small replication samples relative to original and rescue could be due to both a) powering a replication according to a reported large effect size or b) difficulties with recruitment or high exclusion rates leading to a smaller than intended sample.
+Small replication samples relative to original and rescue could be due to both a) powering a replication according to a reported large effect size or b) difficulties with recruitment or high exclusion rates leading to a sample size smaller than intended.
 Since relative sizes of the studies may play a role in replication success and how probative replications are, we show the sample sizes in Table \@ref(tab:tab-size).
@@
 The rescuer identified several possible reasons for this failure, foremost among them that the replication was conducted online while the original was conducted in person.
-It is reasonable to expect online studies of reading time to be noisier than in-person studies because the environments participants completed the study in varied much more online.
+It is reasonable to expect online studies of reading time to be noisier than in-person studies because the environments participants completed the study in vary much more online.
 The rescue attempt was still online, but used a much larger sample size to account for noisier data.
@@
 We believe, however, that this is more of an apparent than an actual limitation.
-Students were enrolled in a highly competitive graduate program where it is expected that PhD students author peer-reviewed papers; several of the rescuers already had published first-authored peer reviewed articles.
+Students were enrolled in a highly competitive graduate program where it is expected that PhD students author peer-reviewed papers.
+Several of the rescuers had already published first-authored peer reviewed articles.
 Thus, while we refer to the rescuers as students, they are investigators doing experiments that become part of the literature.
@@
 
-In many cases, researchers may have strong prior beliefs about where a replication will succeed, and these priors may influence a researchers interpretation of a failed replication, and thus their calculations about where a re-replication will succeed or is worth attempting.
+In many cases, researchers may have strong prior beliefs about where a replication will succeed, and these priors may influence a researcher's interpretation of a failed replication, and thus their calculations about where a re-replication will succeed or is worth attempting.
 For instance, a researcher who has high credence in the main result is more likely to attribute failure to specific details in the replication, and thus may want to do a rescue where those details are adjusted.

### 2024-10-15 manuscript/coverletter/collabra_response_2.tex
futzing for resubmit

@@
 
-	We have added bolded text to our README linking to these different ways of viewing the links in a hyperlinked format.
+	We have changed the link to the paper for the pre-registration to point to the clickable links on OSF.
+We have added text to our README linking to these different ways of viewing the links in a hyperlinked format.
 

### 2024-10-15 manuscript/manuscript.Rmd
futzing for resubmit

@@
 author:
-  - Anonymous
-# author:
-#   - name: Veronica Boyce
-#     affiliation: Psych
-#     footnote:
-#       - corresp
-#   - name: Ben Prystawski
-#     affiliation: Psych
-#   - name: Adani B. Abutto
-#     affiliation: Psych
-#   - name: Emily M. Chen
-#     affiliation: Psych
-#   - name: Ziwen Chen
-#     affiliation: GSB
-#   - name: Howard Chiu
-#     affiliation: Edu
-#   - name: Irmak Ergin
-#     affiliation: Psych
-#   - name: Anmol Gupta
-#     affiliation: Psych
-#   - name: Chuqi Hu
-#     affiliation: Symsys
-#   - name: Bendix Kemmann
-#     affiliation: Philosophy
-#   - name: Nastasia Klevak
-#     affiliation: Psych
-#   - name: Verity Y. Q. Lua
-#     affiliation: Psych
-#   - name: Mateus M. Mazzaferro
-#     affiliation: Edu
-#   - name: Khaing Mon
-#     affiliation: Symsys
-#   - name: Dan Ogunbamowo
-#     affiliation: Psych
-#   - name: Alexander Pereira
-#     affiliation: [Psych, Philosophy]
-#   - name: Jordan Troutman
-#     affiliation: CS
-#   - name: Sarah Tung
-#     affiliation: Psych
-#   - name: Raphael Uricher
-#     affiliation: Psych
-#   - name: Michael C. Frank
-#     affiliation: Psych
-# address:
-#   - code: Psych
-#     address: Department of Psychology, Stanford University
-#   - code: GSB
-#     address: Graduate School of Business, Stanford University
-#   - code: Edu
-#     address: Graduate School of Education, Stanford University
-#   - code: Symsys
-#     address: Symbolic Systems Program, Stanford University
-#   - code: Philosophy
-#     address: Department of Philosophy, Stanford University
-#   - code: CS
-#     address: Department of Computer Science, Stanford University
-#footnote:
-#  - code: corresp
-#    text: "Corresponding author. Email: vboyce@stanford.edu"
+  - name: Veronica Boyce
+    affiliation: Psych
+    footnote:
+     - corresp
+  - name: Ben Prystawski
+    affiliation: Psych
+  - name: Adani B. Abutto
+    affiliation: Psych
+  - name: Emily M. Chen
+    affiliation: Psych
+  - name: Ziwen Chen
+    affiliation: GSB
+  - name: Howard Chiu
+    affiliation: Edu
+  - name: Irmak Ergin
+    affiliation: Psych
+  - name: Anmol Gupta
+    affiliation: Psych
+  - name: Chuqi Hu
+    affiliation: Symsys
+  - name: Bendix Kemmann
+    affiliation: Philosophy
+  - name: Nastasia Klevak
+    affiliation: Psych
+  - name: Verity Y. Q. Lua
+    affiliation: Psych
+  - name: Mateus M. Mazzaferro
+    affiliation: Edu
+  - name: Khaing Mon
+    affiliation: Symsys
+  - name: Dan Ogunbamowo
+    affiliation: Psych
+  - name: Alexander Pereira
+    affiliation: [Psych, Philosophy]
+  - name: Jordan Troutman
+    affiliation: CS
+  - name: Sarah Tung
+    affiliation: Psych
+  - name: Raphael Uricher
+    affiliation: Psych
+  - name: Michael C. Frank
+    affiliation: Psych
+address:
+  - code: Psych
+    address: Department of Psychology, Stanford University
+  - code: GSB
+    address: Graduate School of Business, Stanford University
+  - code: Edu
+    address: Graduate School of Education, Stanford University
+  - code: Symsys
+    address: Symbolic Systems Program, Stanford University
+  - code: Philosophy
+    address: Department of Philosophy, Stanford University
+  - code: CS
+    address: Department of Computer Science, Stanford University
+footnote:
+ - code: corresp
+   text: "Corresponding author. Email: vboyce@stanford.edu"
 bibliography: ["251rescue.bib"] # Replace with one or more of your own bibtex files. Better BibTeX for Zotero is your friend
@@
 Each project was also individually pre-registered by the student conducting it.
-The overall analysis is pre-registered at <https://osf.io/5qz7v>, individual pre-registrations are linked from <https://osf.io/vkbfw>.
+The overall analysis is pre-registered at <https://osf.io/5qz7v>, individual pre-registrations are linked from <https://osf.io/r2d6q>.
 We note one deviation from our pre-registration here: we pre-registered visual comparisons between original, first replication, and rescue projects using prediction intervals.
@@
 In general, we encouraged students to add manipulation checks as appropriate and to adapt their materials to online studies, which may benefit from attention checks and/or shorter duration.
-For instance, the rescue of @paxton2012 switched from using the Cognitive Reflection Test (CRT) which many online participants are over-familiar with to using the newer CRT-2 which is used less but attempts to measure the same construct [@thomson2016].
+For instance, the rescue of @paxton2012 switched from using the Cognitive Reflection Test (CRT) which many online participants are over-familiar with to using the newer CRT-2, which is used less but attempts to measure the same construct [@thomson2016].
 The rescue of @jara-ettinger2022 discovered that the replication had accidentally used an illustrated version of the stimuli rather than the photographic stimuli used in the original and used the photographic stimuli instead.

### 2024-10-15 manuscript/manuscript.tex
futzing for resubmit

--- 2024-08-08 manuscript/manuscript.tex
@@
 
+\newcommand\blfootnote[1]{%
+	\begingroup
+	\renewcommand\thefootnote{}\footnote{#1}%
+	\addtocounter{footnote}{-1}%
+	\endgroup
+}
+
 \begin{document}
 \maketitle
-
+\blfootnote{* Corresponding author. Email: \href{mailto:vboyce@stanford.edu}{\nolinkurl{vboyce@stanford.edu}}}
 %%%%%%%%%% START AFTER TITLE PARTIAL %%%%%%%%%%%%%
@@
 
-Imagine you are a graduate student, and you run a replication of a study that you are interested in building upon in your research.
+Imagine you are a graduate student and you run a replication of a study that you are interested in building upon in your research.
 The replication fails.
-Perhaps the interaction you hoped for is directionally correct, but the point estimate is small and the confidence interval definitely overlaps 0, with a \(p\)-value of .3.
+Perhaps the interaction you hoped for is directionally correct, but the point estimate is small and the confidence interval definitely contains 0, with a \(p\)-value of .3.
 Or perhaps the interaction is numerically in the wrong direction and the main effects look different.
@@
 
-In psychology, large scale replication projects have found that around half of studies successfully replicate.
+In psychology, large-scale replication projects have found that around half of studies successfully replicate.
 Across 100 studies with positive results, the reproducibility project in psychology (RP:P) replicated 36\%-47\% depending on the metric for replication success (\citeproc{ref-opensciencecollaboration}{Open Science Collaboration, 2015}).
@@
 Psychology is not the only discipline where many studies do not replicate.
-Large scale replication projects in other disciplines have found 39/97 of studies with positive effects (40\%) replicating in cancer biology (\citeproc{ref-errington2021}{Errington et al., 2021}), 11/18 studies (61\%) replicating in economics (\citeproc{ref-camerer2016}{Camerer et al., 2016}), and 31/40 studies (78\%) replicating in experimental philosophy (\citeproc{ref-cova2021}{Cova et al., 2021}).
-Across these disciplines, and especially in psychology, large-scale replications indicate a substantial chance of scientists encountering failed replications if they try to replicate published findings.
-
-Replications can fail for many reasons, having to do with the original study or the replication.
-Starting with the original study, one potential reason for replication failure is that the original result is fragile in some way.
+Large-scale replication projects in other disciplines have found 39/97 of studies with positive effects (40\%) replicating in cancer biology (\citeproc{ref-errington2021}{Errington et al., 2021}), 11/18 studies (61\%) replicating in economics (\citeproc{ref-camerer2016}{Camerer et al., 2016}), and 31/40 studies (78\%) replicating in experimental philosophy (\citeproc{ref-cova2021}{Cova et al., 2021}).
+Across these disciplines, and especially in psychology, large-scale replications indicate that the probability of scientists failing to replicate published findings is substantial.
+
+Replications can fail for many reasons. Some reasons for replication failure have to do with the original study, while others have to do with how the replication was conducted.
+One potential reason is that the original result is fragile in some way.
 It could be a statistically unlikely result that was achieved through chance or \(p\)-hacking, or it could be sensitive to the exact conditions and time it was run under (``hidden moderators'').
-Another possibility is that the original reported effect size might be inflated due to some combination of heterogeneity, \(p\)-hacking, low power, and publication bias.
-A consequence of inflated effect sizes is that replication studies might select a sample size with appropriate statistical power for the reported effect size and then have too small a sample to reliably detect the (true) smaller effect.
+Another possibility is that the original reported effect size is inflated due to some combination of heterogeneity, \(p\)-hacking, low power, and publication bias.
+If effect sizes are inflated, replication studies that select a sample size with appropriate statistical power for the reported effect size will have too small a sample to reliably detect the (true) smaller effect.
 Replication studies might also end up underpowered due to unexpected attrition or noise in the replication sample.
 
-Some other reasons for replication failure are primarily due to the replication study.
+Other reasons for replication failure are primarily due to the design of the replication study.
 A replication could observe different results from the original due to methodological differences.
-These differences in design could be intentional adaptations, unavoidable changes from lack of access to the original instructions or materials, or changes that were not expected to be critical.
-A difference in the details of recruitment (e.g., online versus in-person) might mean that particular details of a study implementation would no longer be appropriate, or the data quality controls and attention checks might be inadequate.
-If there are differences in time, place, or subject population between the two studies, corresponding changes to the materials, instructions, or procedure could be needed to provide an adaptation of the experimental paradigm to the new context.
-Such adaptation creates yet more challenges in interpretation: too many changes could cause differing results, but so could not enough changes.
+These differences include intentional adaptations, unavoidable changes from lack of access to the original instructions or materials, or changes that the replicators did not expect to be critical.
+A difference in the details of recruitment, such as changing from recruiting participants in person to online, might mean that particular details of a study implementation are no longer appropriate, or the data quality controls are inadequate.
+If there are differences in time, place, or subject population between the two studies, researchers may need to change the materials, instructions, or procedure to adapt the experimental paradigm to the new context.
+Such adaptation creates more challenges in interpretation: too many changes could cause differing results, but so could too few changes.
 In sum, when replications fail, we generally do not know why they failed, although we may speculate.
 
-For the goals of large-scale replication projects, it does not matter why any particular study failed to replicate, because the aim is to estimate the proportion of replication effects in a literature.
-In contrast, however, when individual scientists attempt to replicate an effect with the goal of building on it, they do care about why an individual replication failed.
+For the goals of large-scale replication projects, it does not matter why any particular study failed to replicate, because the aim is to estimate the proportion of effects that replicate in a literature.
+In contrast, when individual scientists attempt to replicate an effect with the goal of building on it, they care why an individual replication failed.
 In an uncertain literature, scientists might not want to commit resources to studying extensions of an effect without first checking that they can measure that effect themselves.
-For those individual scientists, it is much more important whether the replication failure is due to a fixable issue with the replication or an intrinsic feature of the original result.
-
+For those individual scientists, it is much more important to know whether the replication failure is due to a fixable issue with their replication attempt or an intrinsic feature of the original result.
+
+While it is possible to speculate after the fact about potential causes of a single replication failure, in most circumstances these causes are hard to discern (absent clear evidence of errors).
 Re-replication can serve as a way to test explanations for replication failure.
-While it is possible to speculate after the fact about potential causes of a single replication failure, in most circumstances these causes are hard to discern (absent clear evidence of errors).
-In contrast, a second replication provides a chance to test explanations by making modifications -- as well as giving another chance for researchers to measure an effect of interest.
+Re-replications can make modifications to the first replication and give another chance for researchers to measure an effect of interest.
 But what are the chances that a re-replication succeeds?
@@
 Even when a significant effect was recovered, the effect size was much diminished (\citeproc{ref-ebersole2020}{Ebersole et al., 2020}).
-The re-replication success rate was thus 2/9 (22\%) for studies with non-significant first replications, under favorable, high-resource circumstances.
+The re-replication success rate was thus 2/9 (22\%) for studies with non-significant first replications under favorable, high-resource circumstances.
 
 While Ebersole et al.
-(\citeproc{ref-ebersole2020}{2020}) looked at re-replication success rate in a high resource setting with access to large, multi-site samples and expert input, most early career scientists do not have those kinds of resources to devote to re-replication attempts.
-On the other hand, early career researchers may also be prone to a different distribution of causes of initial replication failure.
-Thus, it is an open question what the re-replication rate is for failed replications by early career researchers.
-Further, estimating this rate could inform researchers' decisions on what to do next after failed replications.
+(\citeproc{ref-ebersole2020}{2020}) looked at re-replication success rate in a high-resource setting with access to large, multi-site samples and expert input, most early-career scientists do not have comparable resources to devote to re-replication attempts.
+On the other hand, early-career researchers may also be prone to a different distribution of causes of initial replication failure.
+Thus, it is an open question what the re-replication rate is for failed replications by early-career researchers.
+Further, estimating this rate could inform researchers' decisions on what to do next when a replication fails.
 
@@
 The focus of the class was best practices in experimental design; thus, students looked at both the original paper and the failed replication to examine potential issues in the replication that they could fix in their rescue project.
-In the present paper, we report the results of 17 re-replication rescue projects.
+In the present paper, we report the results of 17 rescue projects.
 We find that a minority of projects (5/17, 29\%) successfully recovered the original effect.
@@
 PSYCH 251 is a graduate-level experimental methods class taught by MCF.
-In previous years, students have conducted replication projects (\citeproc{ref-boyce2023}{Boyce et al., 2023}; \citeproc{ref-hawkins2018}{Hawkins et al., 2018}).
+In previous years, students conducted replication projects (\citeproc{ref-boyce2023}{Boyce et al., 2023}; \citeproc{ref-hawkins2018}{Hawkins et al., 2018}).
 In Fall 2023, students were offered the option to complete a ``rescue'' project where they re-replicated one of the unsuccessful replications from a previous year.
@@
 If they opted for a rescue, they were given the option to participate in a collaborative meta-science project and earn authorship on the current paper based on 1) completing a rescue project, 2) reviewing another student's rescue project for reproducibility, and 3) reviewing and approving the final manuscript.
-We report on the result of 17 rescue projects that opted to be part of the paper and completed data collection.
-
-A spreadsheet of projects, individual project write-ups (both first replications and rescues), individual project data and analyses for rescue projects, and the analytic code for this paper are all available at \url{https://osf.io/cyk5w/}.
+We report on the result of the 17 rescue projects by students who completed data collection and opted to be a part of the paper.
+
+A spreadsheet of projects, individual project write-ups (both first replications and rescues), individual project data and analyses for rescue projects, and the analytic code for this paper are all available at \url{https://osf.io/cyk5w}.
 
@@
 Each project was also individually pre-registered by the student conducting it.
-The overall analysis is pre-registered at \url{https://osf.io/5qz7v}, individual pre-registrations are linked from \url{https://osf.io/vkbfw}.
+The overall analysis is pre-registered at \url{https://osf.io/5qz7v}, individual pre-registrations are linked from \url{https://osf.io/r2d6q}.
 We note one deviation from our pre-registration here: we pre-registered visual comparisons between original, first replication, and rescue projects using prediction intervals.
@@
 
-Students were required to think of reasons the first replication might not have worked, and address them if they could.
+Students were required to think of reasons why the first replication might not have worked, and address them if they could.
 A list of possible reasons and solutions was given to students (\url{https://osf.io/dfwk2}).
-In general, we encouraged students to add manipulation checks as appropriate, and to adapt their materials to online studies, which may benefit from attention checks and/or shorter duration.
+In general, we encouraged students to add manipulation checks as appropriate and to adapt their materials to online studies, which may benefit from attention checks and/or shorter duration.
 For instance, the rescue of Paxton et al.
-(\citeproc{ref-paxton2012}{2012}) switched from using the Cognitive Reflection Test (CRT) which many online participants are over-familiar with to using the newer CRT-2 which is less overused but attempts to measure the same construct (\citeproc{ref-thomson2016}{Thomson \& Oppenheimer, 2016}).
+(\citeproc{ref-paxton2012}{2012}) switched from using the Cognitive Reflection Test (CRT) which many online participants are over-familiar with to using the newer CRT-2, which is used less but attempts to measure the same construct (\citeproc{ref-thomson2016}{Thomson \& Oppenheimer, 2016}).
 The rescue of Jara-Ettinger et al.
@@
 Tarampi et al. (\citeproc{ref-tarampi2016}{2016}) had participants do a timed navigation task where they wrote L or R to indicate which way to turn at each intersection on a paper map.
-The replication ported this experiment online and had participants click a drop down menu to select left or right for each turn.
-The rescue removed the unwieldy drop down menus and opted to have participants press keys on the keyboard to indicate the direction of a turn, which seemed like a more natural interface.
+The replication ported this experiment online and had participants use a dropdown menu to select left or right for each turn.
+The rescue removed the unwieldy dropdown menus and opted to have participants press keys on the keyboard to indicate the direction of a turn, which seemed like a more natural interface.
 Once experimental designs and analytic plans were approved by class TAs (VB and BP), students pre-registered and ran their samples.
 
-With one exception, samples were collected on Prolific (the rescue of \citeproc{ref-yeshurun2003}{Yeshurun \& Levy, 2003} ran in-person on the Stanford student subject pool).
-We tried to power studies adequately (with a target of 2.5x original following \citeproc{ref-simonsohn2015}{Simonsohn, 2015}), but due to cost constraints, not all studies were powered at this level.
+With one exception, samples were collected on Prolific (the rescue of \citeproc{ref-yeshurun2003}{Yeshurun \& Levy, 2003} ran in person on the Stanford student subject pool).
+We tried to power studies adequately (with a target sample size of 2.5x the original study following \citeproc{ref-simonsohn2015}{Simonsohn, 2015}), but due to cost constraints, not all studies were powered at this level.
 The rescues had on average 1.48 times the original sample post-exclusion (median: 1.07, IQR: 0.94 - 2.4, minimum: 0.48, maximum: 2.96, see Table \ref{tab:tab-size} for all sample sizes).
@@
 (\citeproc{ref-boyce2023}{2023}) for original, first replication, and rescue (these were already rated for original and first replication).
-These potential correlates included the subfield of the study (cognitive, social, or other psychology), its publication year, experimental design features including whether it was a within- or between-subject design, whether each condition was instantiated with one vignette or multiple, how many items each participant saw, and whether there were open materials and open data.
-
-For the original study and each replication, we recorded the number of participants post-exclusions.
-For studies where some extra conditions were dropped in some replications, we counted only the participants in the key conditions all replications had for comparability.
+These potential correlates included the subfield of the study (cognitive, social, or other psychology), its publication year, experimental design features including whether it used a within- or between-subject design, whether each condition was instantiated with one vignette or multiple, how many items each participant saw, and whether there were open materials and open data.
+
+For the original study and each replication, we recorded the number of participants after exclusions.
+For studies where extra conditions were dropped in some replications, we counted only the participants in the key conditions all replications had for comparability.
 For instance, if an original study compared between two critical conditions but also had a baseline control, we did not count the participants in the baseline condition if a replication did not include this condition.
-We also recorded whether each study was conducted online using a crowd-sourced platform or not.
+We also recorded whether each study was conducted using an online crowdsourcing platform or not.
 
@@
 \includegraphics[width=1\linewidth]{manuscript_files/figure-latex/smd-1} \caption{Standardized effect sizes of original studies, first replications, rescues, and additional replications if available.
-Due to the large effect size of a couple studies, large effect studies are shown in a separate panel.
-In a few cases, the first replication's key effect was in the same direction as the original with a 95\% CI that did not overlap 0; however, in these cases the larger pattern of results was not consistent between original and first replication.
-}\label{fig:smd}
+Due to the large effect size of some studies, studies with large effects are shown in a separate panel.
+In a few cases, the first replication's key effect was in the same direction as the original with a 95\% CI that did not contain 0.
+However, in these cases the larger pattern of results was not consistent between original and first replication.}\label{fig:smd}
 \end{figure}
@@
 As a complement to subjective replication ratings, we also statistically compared the effect sizes of the rescue, first replication, and original study on one preregistered key measure per study (again following \citeproc{ref-boyce2023}{Boyce et al., 2023}).
-Though we did not conduct a systematic review of the literature to identify all possible replications, we also consider the effect sizes obtained in additional replications when we were aware of them (either from other class projects, or external replications in the literature).
+Though we did not conduct a systematic review of the literature to identify all possible replications, we also considered the effect sizes obtained in additional replications when we were aware of them (either from other class projects, or external replications in the literature).
 
@@
 The value of \(p\)-original represents how likely an effect size equal to or more extreme than the original effect size is to occur if it comes from a distribution of population effect sizes defined by the mean and standard error of the replications (combined meta-analytically) with a between-population standard deviation of \(\tau=.21\) (imputed from \citeproc{ref-olsson-collentine2020}{Olsson-Collentine et al., 2020}).
-That is, \(p\)-original is a measure of the statistical consistency of the original result with the totality of the replications, assuming a given level of heterogeneity of effects between studies.
+That is, \(p\)-original measures the statistical consistency of the original result with the totality of the replications, assuming a given level of heterogeneity of effects between studies.
 Smaller \(p\)-original values indicate more inconsistency.
@@
 
-As secondary measures, we calculated the \(p\)-original values between a) the original and just the first replication and rescue (i.e.~excluding additional replications), b) the original and the rescue, c) the original and non-rescue replications, and d) the rescue and other replications.
+As secondary measures, we calculated the \(p\)-original values between a) the original and the first replication and rescue (i.e.~excluding additional replications), b) the original and the rescue, c) the original and non-rescue replications, and d) the rescue and other replications.
 For a) the original versus the first replication and the rescue, the median value of \(p\)-original was 0.1 {[}IQR: 0.01 - 0.27{]}, and 35\% of the \(p\)-original values were less than .05.
 For b) the original versus the rescue, the median value of \(p\)-original was 0.06 {[}IQR: 0.01 - 0.52{]}, and 47\% of the \(p\)-original values were less than .05.
-For c) the original versus all the non-rescue replications, the median value of \(p\)-original was 0.14 {[}IQR: 0.01 - 0.38{]}, and 35\% of the \(p\)-original values were less than .05.
+For c) the original versus all the non-rescue replications, the median value of \(p\)-original was 0.14 {[}IQR: 0 - 0.38{]}, and 35\% of the \(p\)-original values were less than .05.
 For d) the rescue versus the other replications, the median value of \(p\)-original was 0.31 {[}IQR: 0.14 - 0.78{]}, and 24\% of the \(p\)-original values were less than .05.
@@
 
-\caption{\label{tab:cor-table}Correlations between an individual predictor and the subjective replication score of the rescue project.
+\caption{\label{tab:cor-table}Correlations between individual predictors and the subjective replication score of the rescue project.
 The first set of predictors were pre-registered based on the correlates used in Boyce et al.
 (2023).
-Original authors at Stanford refers to at the time of the first replication as this may mean the first replication was not independent.
+Original authors at Stanford refers to whether the any of the study's authors were affiliated with Stanford at the time of the first replication, as this may mean the first replication was not independent.
 For details about how the predictors were coded, see the Methods section of Boyce et al.
@@
 All of the correlations are presented in Table \ref{tab:cor-table}.
-The number of rescues is small, and many of these predictors are correlated, so we caution against over interpretation.
-
-The strongest correlates of rescue success were open materials, a small sample size on the first replication, a small sample size on the first replication relative to the original sample size, and a large rescue sample size relative to the first replication.
+The number of rescues is small, and many of these predictors are correlated, so we caution against over-interpretation.
+
+The strongest correlates of rescue success were open materials, a small sample size in the first replication, a small sample size in the first replication relative to the original sample size, and a large rescue sample size relative to the first replication.
 None of the pre-registered correlates meet the conventional significance threshold; the two correlates based on ratios that reflect a relatively smaller replication sample size are marginally significant.
 
-Small replication samples relative to original and rescue could be due to both a) powering a replication according to a reported large effect size or b) difficulties with recruitment or high exclusion rates leading to a smaller than intended sample.
+Small replication samples relative to original and rescue could be due to both a) powering a replication according to a reported large effect size or b) difficulties with recruitment or high exclusion rates leading to a sample size smaller than intended.
 Since relative sizes of the studies may play a role in replication success and how probative replications are, we show the sample sizes in Table \ref{tab:tab-size}.
@@
 The rescue of Krauss \& Wang (\citeproc{ref-krauss2003}{2003}) was successful despite an unsuccessful replication.
-This study looked at the influence of guided thinking on whether or not people gave correct justifications (drawn or written) for their answer on the Monty Hall problem.
-The original paper reported correct justification from 2/67 (3\%) in the control condition and 13/34 (38\%) in the guided thinking condition.
+This study looked at the influence of guided thinking on whether people gave correct justifications (drawn or written) for their answer on the Monty Hall problem.
+The original paper reported correct justifications from 2/67 (3\%) participants in the control condition and 13/34 (38\%) in the guided thinking condition.
 The first replication struggled to recruit participants who were naive to the problem (an exclusion criterion), and many participants gave very short text responses in the provided text box (only textual responses were allowed).
@@
 The rescue targeted these issues by adding a pre-screening that ensured participants were not familiar with the Monty Hall problem, changed the content items for the problem and changed its name (to reduce googling for answers), and had participants upload drawings for their justifications.
-Collectively, we believe these changes brought the rescue closer to the intent of the original.
+We believe these changes collectively brought the rescue closer to the intent of the original.
 The rescue had 1/40 (2\%) correct justifications in the control condition and 6/35 (17\%) in the guided thinking condition.
@@
 An additional replication from the literature, Ngo \& Newcombe (\citeproc{ref-ngo2021}{2021}) successfully replicated Ngo et al. (\citeproc{ref-ngo2019}{2019}).
-There are reasons to think that some effect sizes in the literature may be inflated (\citeproc{ref-camerer2018}{Camerer et al., 2018}; \citeproc{ref-opensciencecollaboration}{Open Science Collaboration, 2015}), and it is also possible that changes to experiments or switches to online could result in noisier samples and thus smaller effect sizes.
+There are reasons to think that some effect sizes in the literature may be inflated (\citeproc{ref-camerer2018}{Camerer et al., 2018}; \citeproc{ref-opensciencecollaboration}{Open Science Collaboration, 2015}), and it is also possible that changes to experiments or moving data collection online could result in noisier samples and thus smaller effect sizes.
 Therefore, replications with smaller samples than the original (even if powered to the original effect size), may not be very diagnostic, and could potentially benefit from a re-replication.
@@
 They showed participants a number of images and then hours later (after either sleep or no sleep) measured their recall for parts of the images.
-The first replication struggled to recruit participants to complete a followup session after sleep and only reported a sample size of 23 (the original had 48).
-The rescue attempted to recruit a larger sample (target 88), but also experienced difficulties getting participants to complete the second part of the experiment 12 hours after the first, managing also only to recruit 23 people.
+The first replication struggled to recruit participants to complete a followup session after sleep and reported a sample size of only 23 (the original had 48).
+The rescue attempted to recruit a larger sample (target 88), but experienced difficulties getting participants to complete the second part of the experiment 12 hours after the first, also managing to recruit only 23 people.
 The lesson here may be that sleep research is difficult to conduct online.
@@
 (\citeproc{ref-payne2008}{2008}) on related but not identical measures.
-Denis et al. (\citeproc{ref-denis2022}{2022}) which has an overlapping author team to Payne et al. (\citeproc{ref-payne2008}{2008}) is included here as an additional replication.
+Denis et al. (\citeproc{ref-denis2022}{2022}), which has an overlapping author team to Payne et al. (\citeproc{ref-payne2008}{2008}), is included here as an additional replication.
 
@@
 The reported rescue projects are a small sample of replications, leading to highly uncertain estimates.
-Additionally, they were chosen non-randomly, as they were doubly selected for based on student interest -- once for the original replication and again for the rescue.
-However, this selection bias is likely to correlate with how graduate students and other early career researchers choose what topics to work on and what studies to build on.
+Additionally, they were chosen non-randomly, as they were doubly selected for based on student interest---once for the original replication and again for the rescue.
+However, this selection bias is likely to correlate with how graduate students and other early-career researchers choose what topics to work on and what studies to build on.
 Nevertheless, our estimate is still broadly consistent with that of ManyLabs 5 (29\% vs.~22\%, \citeproc{ref-ebersole2020}{Ebersole et al., 2020}).
 
-One potentially salient limitation of our work here is that the rescue projects (and the first replications) were primarily conducted by first year PhD students; hence the generality of our conclusions to other investigators is unknown.
+One potentially salient limitation of our work here is that the rescue projects (and the first replications) were primarily conducted by first-year PhD students; hence the generality of our conclusions to other investigators is unknown.
 We believe, however, that this is more of an apparent than an actual limitation.
-Students were enrolled in a highly-competitive graduate program where it is expected that PhD students author peer-reviewed papers; several of the rescuers already had published first-authored peer reviewed articles.
+Students were enrolled in a highly competitive graduate program where it is expected that PhD students author peer-reviewed papers.
+Several of the rescuers had already published first-authored peer reviewed articles.
 Thus, while we refer to the rescuers as students, they are investigators doing experiments that become part of the literature.
@@
 
-We have focused here on a narrow type of replication and rescue: that done by an early career researcher with the goal of establishing whether this is a result \emph{they} can build on.
+We have focused here on a narrow type of replication and rescue: that done by an early-career researcher with the goal of establishing whether \emph{they} can build on a result.
 We acknowledge that this type of replication exists as part of a wider ecosystem of replications that have different properties and are done for different reasons.
 
-In many cases, researchers may have strong prior beliefs about where a replication will succeed, and these priors may influence a researchers interpretation of a failed replication, and thus their calculations about where a re-replication will succeed or is worth attempting.
+In many cases, researchers may have strong prior beliefs about where a replication will succeed, and these priors may influence a researcher's interpretation of a failed replication, and thus their calculations about where a re-replication will succeed or is worth attempting.
 For instance, a researcher who has high credence in the main result is more likely to attribute failure to specific details in the replication, and thus may want to do a rescue where those details are adjusted.
